### 2023-03-05 chapters/01-introduction.tex
Thesis template and basic EDA in datasets

\chapter{Introduction}
\textbf{Following is very coarse draft!}
Manufacturing is experiencing a shift in the traditional asset operational status evaluation and utilization. The goal is to promote safety and production efficiency when the useful life of machine moving parts is extended. In the factories and logistics where this sort of equipment is vital, there is a trend to be able to monitor the health of the machinery parts and above that to diagnose the fault in time to repair it without additional costs. Vibrations are the most nonintrusive way where such faults can be sensed and appear distinctly for an analyst to identify the root cause of the malfunction.

In critical circumstances, such measurements are already in place in some form, but in order to reach wider acceptance, and not remain just a quirk/trend system has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.

The thesis is structured in a following manner. In Chapter 1 we explore the theoretical (analytical) model view, mechanical maintenance approaches, and industry standards where common fault identification is described. Chapter 2 is all about taking vibration measurements (procuring) and transforming them into features meaningful in automatic fault pattern recognition. The methods for ranking are reviewed to obtain the most important and correlated features with machine health status. We delve into modes of diagnosis based on reduced relevant indicators in chapter 3. Chapter 4 takes a look into IoT communication infrastructure limiting the data throughput and devices that can be deployed (accommodate) in the factory environment. Chapter 5 defines measurement vectors and proposes processing steps to diagnose the reoccurring failure, RUL (remaining useful life), and fault types. The approach taken is evaluated and deployed in Chapter 6.

### 2023-03-05 chapters/02-analysis.tex
Thesis template and basic EDA in datasets

\chapter{Problem analysis}

\section{Physics of rotating machines}

	\subsection{Vibration fault types}
	There are a few methods of machinery fault identification in vibrational signals based on domain expertise. Data points can be viewed in the time domain and frequency domain. Either as individual stationary profiles obtained during the short duration in the time of measurement, or multiple spaced-out observations with the intent to highlight the long-term trend, e.g. shown in a waterfall plot \cite{ziaran_technicka_2013}. The descriptor variable can be any meaningful statistical quantity, e.g. peak-to-peak, RMS, crest factor, kurtosis, which can be applied to recorded samples or frequency bands.

Mechanical faults manifest themselves in the vibration signal at various frequencies. In the low-frequency range (up to 1 kHz) shaft's unbalance, misalignment, bend, crack, and mechanical looseness is present. High frequencies (up to 16 kHz or more) contain bearings faults and gear faults.

Under fault-free circumstances, shaft speed appears as the strongest frequency component. In case of shaft and gear imbalance or damage, synchronous multiples of shaft frequency (harmonics) are amplified. When rub, bad drive belts and chains, or looseness is occurring in the machine then sub-synchronous harmonics or even non-synchronous frequencies appear \cite{mohanty_machinery_2015}.  Therefore it is useful to rescale the horizontal axis to RPM or orders of rotational speed. Complementary methods of fault symptom identification are phase and orbital analysis \cite{scheffer_practical_2004}.

	\subsection{Band saw anatomy}

\section{Condition monitoring}

	\subsection{Maintenance strategies}
	% Reactive, Proactive, Predictive

	\subsection{Technical standards}
	The maintenance procedure usually involves data acquisition cards inside handheld devices with accelerometer sensor probes then mounted firmly to the machine frame by either screwing in, magnets or wax \cite{ziaran_technicka_2013}. The probe placement in axial and perpendicular radial directions is standardized in ISO 20816. The severity of vibrations is mostly assessed in units of velocity ($mm/s$), but acceleration ($m/s^2$) and displacement ($\mu m$) are also used. Based on the observed vibration intensity and one of the four classes of machines (I, II, III, IV) by output power and size, zones (A, B, C, D) for accepted levels are proposed. It is customary to establish operational limits in the form of alarms and trips \cite{iso_20816}.

Standard ISO 13373 categorizes three types of vibration monitoring systems: permanent, semi-permanent, and mobile. More importantly, a structured diagnostic approach is developed here complete with recommendations for formalizing diagnostic techniques \cite{iso_13373}. The next step is the signal analysis with the use of proper units and transformations is the subject of the ISO 18431 \cite{iso_18431}.

	\subsection{Sensor placement}

\section{Feature engineering}
	Feature selection vs. extraction

	\subsection{Signal denoising and filtering}
	Blind source separation, PCA, ICA

	\subsection{Time-frequency features}
	Time Synchronous Averaging of Real FFT
	vs. FastCWT - Synchrosqueezing

	\subsection{Harmonics identification}
	Cepstrum + Harmonic Product Spectrum + Peak identification

	\subsection{Feature importance ranking}

\section{Semi-supervised learning in diagnostics}
	Label propagation

	\subsection{Clustering techniques}
	BIRCH, DBSCAN, SVM

	\subsection{Sketch streaming algorithms}

\section{IoT in Industry 4.0}

	\subsection{Microcontrollers}
	% ARM Cortex

	\subsection{Wireless protocols}
	% IEEE 802.11, IEEE 802.15.4e - IoT Mesh protocols: WirelessHART, ISA100.11a, OpenThread
	% Formats: CoAP + CBOR

Cite \cite{sample}.

### 2023-03-05 chapters/03-design.tex
Thesis template and basic EDA in datasets

\chapter{Design}

\section{Research questions}
\begin{enumerate}
\item \emph{Which time-frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?}
\item \emph{What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?}
\item \emph{How can the machinery faults be continuously identified based on collected events?}
\end{enumerate}

\section{Infrastructure}
 \begin{itemize}
\item \textbf{Input:} Samples from acceleration in 3-axis, RPM, Noise background
\item \textbf{Output is either:} machine overall status, type of fault, remaining useful life
\item \textbf{Output for domain expert}: Annotation interface, Control chart of trend features, Power frequency spectrum, Waterfall plot
 \end{itemize}

\begin{enumerate}
\item MEMS accelerometers are placed on at least two distinict measurement points in two perpendicular axis and one sensor in base for denoising. Rotational speed is captured at the same time too. 
\item Sensors are triggered in regular intervals (every 15 minutes) to collect sample recording from the band saw. Configurable parameters set based on experiments: sampling frequency, dynamic range, window type (Hamming) and size (based on resolution), PSD estimation method (Welch)
\item \textbf{Features} are computed and compared to recent measurements. If there is an statistically significant change the whole summary is send, otherwise keepalive notification is send.
\item Possible local communication between sensors to pre-compute clustering information
\item Database stores history of measurements
\item \textbf{Diagnosis panel runs clustering} with introduction of annotations to notify the operator about observed fault and imminent failure of the machine.
\end{enumerate}

### 2023-03-05 chapters/appendix/B-plan-of-work.tex
Thesis template and basic EDA in datasets

\thispagestyle{empty}
\chapter{Plan of work}
\pagenumbering{arabic}
\renewcommand*{\thepage}{B-\arabic{page}}

\section{Winter semester}

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Consultation with the supervisor on directions of the future work based on literature review during previous semester. Meeting schedule is established.
\\ \hline
\nth{2} week         & Outline of key sections of the analysis part of the thesis.
\\ \hline
\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering in condition monitoring.
 \\ \hline
\nth{4} week         & TBD (Descibe machinery physics and maintanance strategies.)
 \\ \hline

\end{tabular}
\end{table}

\clearpage
\newpage

\section{Summer semester}

\clearpage

### 2023-03-05 research-objective/main.tex
Thesis template and basic EDA in datasets

\documentclass[11pt, a4paper, english]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}

\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage[fleqn]{amsmath}
\usepackage{pdfpages}
\usepackage{csquotes}
\usepackage{longtable}

\usepackage{nomencl}
\usepackage{makeidx}
\usepackage{expl3}
\usepackage{etoolbox}
%\preto\tabular{\shorthandoff{-}}

\usepackage[style=iso-numeric, backend=biber]{biblatex}
\renewcommand*{\bibfont}{\small}
\addbibresource{literature.bib}

\newcommand{\University}[0] {Slovenská technická univerzita v Bratislave}
\newcommand{\UniversityEN}[0] {Slovak University of Technology in Bratislava}
\newcommand{\Faculty}[0] {Fakulta informatiky a informačných technológií}
\newcommand{\FacultyEN}[0] {Faculty of Informatics and Information Technologies}
\newcommand{\Thesis}[0] {Diplomová práca}
\newcommand{\ThesisEN}[0] {Research objective for Master’s thesis}
\newcommand{\Title}[0] {Vibrodiagnostika strojov s priemyselným internetom vecí}
\newcommand{\TitleEN}[0] {Machinery vibrodiagnostics \\ with the industrial internet of things}
\newcommand{\Author}[0] {Bc. Miroslav Hájek}
\newcommand{\Supervisor}[0] {Ing. Marcel Baláž, PhD.}
\newcommand{\DepartmentalAdvisor}[0] {Ing. Jakub Findura}
\newcommand{\Consultant}[0] {Ing. Lukáš Doubravský}
\newcommand{\Date}[0] {December 2022}
\newcommand{\StudyProgramme}[0] {Informatika}
\newcommand{\StudyProgrammeEN}[0] {Informatics}
\newcommand{\StudyField}[0] {Informatika}
\newcommand{\StudyFieldEN}[0] {Computer Science}
\newcommand{\Institute}[0] {Institute of Computer Engineering and Applied Informatics}

\defbibenvironment{bibassignment}
  {\list
     {}
     {\setlength{\leftmargin}{\bibhang}%
      \setlength{\itemindent}{-\leftmargin}%
      \setlength{\itemsep}{\bibitemsep}%
      \setlength{\parsep}{\bibparsep}}}
  {\endlist}
  {\item}

\title{
	\textbf{\TitleEN} \\ \vspace{0.2em} 
	\large \emph{\Title\;(SK)} \\ 
	\vspace{0.7em} \large Master's thesis research objective
}
\author{Bc. Miroslav Hájek \\ \small{Masters student} \and Ing. Marcel Baláž, PhD. \\ \small{Thesis supervisor}}
\date{}

\pagenumbering{gobble}
\begin{document}
\newgeometry{top=2.5cm, bottom=3cm, right=3.5cm, left=3.5cm}

\begin{refsection}
\maketitle
\setstretch{1.25}

\pagenumbering{arabic}
\section{Motivation} 
The industry strives to keep manufacturing processes as smooth and efficient as possible. Achieving optimal operation is dependent on maintaining various-sized equipment with moving parts always in satisfactory condition. Regular monitoring is imperative in ensuring the deteriorated parts are not significantly impacting the performance of the machine.

The scope of usage for rotating machines in particular is considerable with potentially high economic or environmental impact in case of unexpected failure. The scheduled downtime is less costly than unplanned. This applies everywhere from electricity production in turbines, as well as pumps in the oil and gas pipelines to motors in vehicles just to illustrate. The prevalent source of machinery breakage according to many surveys are bearings \cite{goel_methodology_2022}.  The standard mode of operation is that a motor of some kind has to exert force via the shaft, belt, or gearbox onto the appliance be it a compressor, pump, fan, or conveyor.

Mechanical faults can be proactively revealed by measuring vibrations because different deteriorations are signified by their characteristic pattern in the signal. This allows us to examine the inner parts of the machine without physically opening it. Ideally to have a holistic overview of the running assets very many reliable self-sufficient sensors would need to be deployed. It entails additional difficulties with managing the informational infrastructure which is a separate research area in its own right \cite{wang_toward_2019}. However, our focus leans towards retrieving relevant diagnostics from the volume of continuously collected data for personnel to act on the acquired knowledge.

\section{Methods in machinery diagnostics}
The long-term effect of condition-based maintenance (CBM) as a form of predictive maintenance is not immediately apparent to the business at the onset. Corrective maintenance can be afforded in less critical operations, which means replacing the defect after the failure. In other cases, at least scheduled maintenance is employed monthly, quarterly, or biannually which is performed by a skilled technician.

\subsection{Technical standards}
The maintenance procedure usually involves data acquisition cards inside handheld devices with accelerometer sensor probes then mounted firmly to the machine frame by either screwing in, magnets or wax \cite{ziaran_technicka_2013}. The probe placement in axial and perpendicular radial directions is standardized in ISO 20816. The severity of vibrations is mostly assessed in units of velocity ($mm/s$), but acceleration ($m/s^2$) and displacement ($\mu m$) are also used. Based on the observed vibration intensity and one of the four classes of machines (I, II, III, IV) by output power and size, zones (A, B, C, D) for accepted levels are proposed. It is customary to establish operational limits in the form of alarms and trips \cite{iso_20816}.

Standard ISO 13373 categorizes three types of vibration monitoring systems: permanent, semi-permanent, and mobile. More importantly, a structured diagnostic approach is developed here complete with recommendations for formalizing diagnostic techniques \cite{iso_13373}. The next step is the signal analysis with the use of proper units and transformations is the subject of the ISO 18431 \cite{iso_18431}.

\subsection{Fault identification}
There are a few methods of machinery fault identification in vibrational signals based on domain expertise. Data points can be viewed in the time domain and frequency domain. Either as individual stationary profiles obtained during the short duration in the time of measurement, or multiple spaced-out observations with the intent to highlight the long-term trend, e.g. shown in a waterfall plot \cite{ziaran_technicka_2013}. The descriptor variable can be any meaningful statistical quantity, e.g. peak-to-peak, RMS, crest factor, kurtosis, which can be applied to recorded samples or frequency bands.

Mechanical faults manifest themselves in the vibration signal at various frequencies. In the low-frequency range (up to 1 kHz) shaft's unbalance, misalignment, bend, crack, and mechanical looseness is present. High frequencies (up to 16 kHz or more) contain bearings faults and gear faults.

Under fault-free circumstances, shaft speed appears as the strongest frequency component. In case of shaft and gear imbalance or damage, synchronous multiples of shaft frequency (harmonics) are amplified. When rub, bad drive belts and chains, or looseness is occurring in the machine then sub-synchronous harmonics or even non-synchronous frequencies appear \cite{mohanty_machinery_2015}.  Therefore it is useful to rescale the horizontal axis to RPM or orders of rotational speed. Complementary methods of fault symptom identification are phase and orbital analysis \cite{scheffer_practical_2004}.

Nowadays the software suites in use to analyze acquired measurements depend on the tool vendors because of established ecosystems. Notable solutions include Brüel \& Kjaer Data Acquisition (DAQ) Software, DDS Software by Adash, Emerson CSI with Machinery Health Manager, SKF @ptitude Analyst, or National Instruments LabView.

\section{Data processing strategies}
The machine vibrations are measured at the sampling frequency adhering to the Nyquist theorem predominantly using MEMS or piezoelectric accelerometer with its dynamic range, sensitivity, axial and frequency responses  \cite{ziaran_technicka_2013}. Simultaneously, the shaft revolutions are recorded to distinguish balancing issues from the effect of other machinery parts.

Proper analysis of the underlying cause of frequency excitations demands knowledge of machine construction and its kinematic model. Unfortunately, the internals are not generally extensively described by the manufacturers so the exact gear ratios or number of bearing balls have to be examined by taking the equipment apart.

The large-scale factory monitoring brings the issue of the sheer volume of excess raw data being captured. Feature selection and extraction techniques can help to determine a subset of instances sufficiently representing the original features in the case of selection, or the dimensionality reduction projection in the case of extraction \cite{kreidl_technicka_2006}. The desired result is lossy compression because some elements are found to have a negligible contribution to the overall diagnosis. The example from speech processing where reduction of the transmission bandwidth is founded in feature extraction are Mel-frequency cepstral coefficients \cite{rabiner_introduction_2007}.

\subsection{Vibration signal processing}
When RPM stays constant, the signal is mostly stationary with exception of background wideband noise from the environment and narrowband interference from machine frame shake or alternating current frequency in electric motors. More close-by sensors can eliminate the noise with a correlation of their spectra. Wear and tear causes the stationary signal to gradually change its content and increase its amplitude. New machines of a similar model to one probed by the sensor should be deemed as a reference for statistically setting alert levels divided into frequency bands.

The important features to be kept can be learned out of raw sampled data \cite{luo_early_2019}. Another approach is to preprocess the frequency spectrum based on domain knowledge to speed up the decisions and retain only the important bits. The vibration signal can be manipulated with in spectral domain in several steps:

\begin{enumerate}
	\item \textbf{Frequency-domain transformations}: The fast Fourier transform algorithm computes Discrete Fourier Transform (DFT) and Discrete Cosine Transform (DCT). The signal has to undergo windowing to maintain the condition of stationarity and to increase the signal-to-noise ratio. The computation is sped up with real FFT which reorders the vector of real numbers to enable the transformation to be half in length. The continuous wavelet transform (CWT) is a time-frequency representation encoding the lower frequencies with less time resolution as compared to higher frequencies. Recently, a fast real-time algorithm for CWT has been invented \cite{arts_fast_2022}.

	\item \textbf{Synchrosqueezing transform}: Enhancement of peaks in the time-frequency spectrum is achieved by decomposing natural oscillating modes into amplitude and frequency-modulated components \cite{meignen_synchrosqueezing_2019}. Synchrosqueezing creates sharper contours over regions where the phase is constant. The instantaneous frequency value is reassigned to the centroid of the CWT time-frequency region. The method was originally associated with wavelets, but can also be applied to a Fourier basis \cite{yu_concentrated_2020}.

	\item \textbf{Denoising}: The accelerometer signal is traditionally noisy. The factors include the indirect transfer of mechanical energy from moving parts to the frame and interference from other equipment mounted nearby onto the same base. Additive white noise can be suppressed based on its recorded fingerprints or with an adaptive filter \cite{nandi_condition_2019}. The thresholds of attenuation are set for each frequency band based on the mean power of noise spectral components. The content of vibration signals is often a mixture of several sources and the signal-to-noise ratio is therefore very poor. Blind source separation (BSS) aids in the recovery of statistically independent signals from external influences \cite{nandi_condition_2019}.

	The narrowband noise can be dealt with using band-notch filters. The peaks in the spectrum can be cleared of wobbles by convolving a low pass filter with appropriate cut-off frequency which in effect creates a low-resolution envelope around the spectral waveform. The selected machinery part's manifestation from the rest is separated by time synchronous averaging. The segments are averaged after the alignment with the pulse generated on each revolution \cite{bechhoefer_review_2009}.

	\item \textbf{Harmonics identification}: The peaks in the frequency spectrum signify the periodic movement of various machinery parts. These local maxima can be marked using peak-finding algorithms. The most simple and effective strategy is spotting the point with the highest value in their neighborhood \cite{adikaram_non-parametric_2016}. Supplementary constraints filter out sudden level jumps in between discrete frequency bins with parameters such as prominence and isolation. In the radar field, the noise is suppressed by Constant False Alarm Rate (CFAR) algorithms with adaptive threshold related to background variance around the cell under the test (CUT) \cite{hatem_comparative_2018}.

	 The increased magnitude of harmonics or sidebands appearing also as peaks can suggest component degradation. It provides a succinct means to describe peaks in relation to their fundamental frequency. Harmonic series and modulation sideband detection is an exhaustive search process when estimation error is considered \cite{gerber_identification_2013}. The pitch detection methods namely autocorrelation, cepstral analysis \cite{rabiner_introduction_2007}, and harmonic product spectrum are basic methods to obtain fundamentals in the signal time slice. The caution must be taken to segment the spectrum reasonably in order to keep as much of the fault characteristic information as is necessary \cite{yonggang_time_2020}.
\end{enumerate}

\subsection{Machine learning fault diagnosis}
The methodology to choose time-frequency features is valid only when meaningful conclusions can be drawn about the rotational machinery's health status. The distinction between the good and in need of repair is not clear cut in practice, but significant empirical expert domain knowledge is developed \cite{ziaran_technicka_2013} \cite{kreidl_technicka_2006} \cite{scheffer_practical_2004} and underlying mathematical models of spring-damper mechanical systems are described.

In its essence, fault diagnostics is a supervised learning problem of multiclass classification because the vibration signals are a combination of any number of rotating elements evaluated as a specific machine condition. Each machine is unique to some degree because of natural imprecisions in its construction.

The machine learning model would have to be trained to each kind of machine from the beginning or poses the means to adapt to considerably different conditions, covering cases from single-phase electric motors, and air compressors to the steam turbine. It is not feasible here to label datasets beforehand to then be fed into the supervised learning algorithm. The other perspective in diagnosis is to observe the dynamic behavior of the mechanical system over time. The notable changes are differentiated with clustering as anomalous or novel  \cite{hu_intelligent_2012} \cite{caldero_multi-channel_2019}. This strategy allows operators to annotate the fault during the operations to be recognizable faster another time.

The portability of the diagnostics model among the machines and the explainability of output decisions to a trained technician and vibration analyst are the key attributes of the intelligent system to be a benefit across the manufacturing plant. The following methods are prospective in working with a little amount of initial data and can utilize the domain expertise to some extent:

\begin{itemize}
\item \textbf{Clustering}: It is an unsupervised learning method subject to distance or density metrics to assign group membership.  The most known clustering algorithms are K-Means, Local Outlier Factor (LOF), Local Correlation Integral  (LOCI), and Density-based spatial clustering of applications with noise (DBSCAN) \cite{aggarwal_outlier_2016}. These algorithms are not particularly effective when data is coming incrementally and its amount is growing unboundedly.

Although the online or single pass variants exist. BIRCH algorithm (Balanced iterative reducing and clustering using hierarchies) can dynamically cluster large datasets by design. In fuzzy clustering, the region boundaries are not sharp. The association with the category is then percentage wise which is tremendous utilized in image segmentation.

\item \textbf{Fuzzy logic expert system}: The rule base to guide experts in fault identification can be reused with some modifications in a computer-assisted setting, too. The imprecise expressions written in terms of linguistic variables (e.g. frequency, severity, sideband)  and predicates (e.g. little, medium, high) have to be fuzzified to quantify the membership of each statement inside fuzzy sets. Out of the variables' truthness in each category and set of rules, the resulting similarity with the underlying condition is inferred with logical operators within the Mamdani system. Then the quantities are defuzzified to deliver the human-readable outcome \cite{chen_introduction_2001}.

Fuzzy logic has been applied to machinery fault diagnostics with considerable potential \cite{mechefske_objective_1998}. However, in recent years there has been a shift away from fuzzy logic \cite{hullermeier_does_2015} to approaches based on probability theory such as Bayesian learning and Bayesian networks. The membership function construction in fuzzy logic is hard to pinpoint and statistics are used anyway.

\item \textbf{Deep neural networks}: The recurrent (RNN) based autoencoders with various hidden unit architectures (GRU, LSTM, PLSTM) trained in an unsupervised manner are currently achieving accuracies up to 70\% on publically available datasets \cite{yu_analysis_2021}. The comprehensibility of classification is being investigated with explainable AI (XAI) algorithms on convolutional neural networks (CNN). The XAI techniques compared involve GradCAM, LRP, and LIME. A large number of features is marked relevant to classification which is not desired \cite{mey_explainable_2022}. Inconsistency in machine running conditions causing the data recollection for neural network training is addressed with transfer learning and knowledge transfer \cite{maurya_condition-based_2021}.
\end{itemize}

\section{Research questions}
Instead of recording complete signals as is, a process should be devised that records only key descriptions based on vibrational signal specifics, namely different machine parts. This event based view can notify operators about fault symptoms based on general rules as well as machine specific behavior over time. To that end we come up with objectives for our research from the overview in the area:

\begin{enumerate}
\item \emph{Which time-frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?}
\item \emph{What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?}
\item \emph{How can the machinery faults be continuously identified based on collected events?}
\end{enumerate}

Similar ideas of fault feature extraction focus mainly on empirical wavelet transform modifications \cite{li_fault_2019} and spectral negentropy \cite{xu_adaptive_2019}.

\section{Evaluation on available datasets}
Evaluation of research questions demands that some datasets of machinery normal and faulty states be analyzed and computational complexity and accuracy be evaluated based on them. The following list provides freely available options to address this issue: 
\begin{itemize}
	\item \textbf{NASA Bearing Dataset}\footnote{https://www.kaggle.com/datasets/vinayak123tyagi/bearing-dataset}:  Each data set describes a test-to-failure experiment and consists of files that are 1-second snapshots recorded at specific intervals with the sampling rate set at 20 kHz. Four bearings were installed on a shaft. The rotation speed was kept constant at 2000 RPM by an AC motor coupled to the shaft via rub belts. A radial load of 6000 lbs is applied onto the shaft and bearing by a spring mechanism. 	\item \textbf{CWRU Bearing Dataset}\footnote{https://www.kaggle.com/datasets/brjapon/cwru-bearing-datasets}: There were 3 accelerometers installed on 3 positions. The test ran under the following conditions: 1 HP load applied to the motor, Shaft rotating speed of 1772 RPM, and 48 kHz sampling frequency of the accelerometers.
	\item \textbf{Vibration Analysis on Rotating Shaft}\footnote{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}: Datasets for 4 different unbalance strengths and one without unbalance were recorded at 4 kHz. The rotation speed was varied between approx. 630 and 2330 RPM in the training datasets and between approx. 1060 and 1900 RPM in the testing datasets.
\end{itemize}

Additionally, custom datasets for chosen machines could be eventually created in collaborations based on precise experiment specifications. We reached out to colleagues at the Faculty of Mechanical Engineering (SjF STU) specifically to prof.~Ing. Stanislav Žiaran,~CSc. and Ing.~Ondrej Chlebo,~PhD. who could provide domain expertise consultation if such need arises. There is also a chance of being able to obtain vibration data from wood processing factory or dormitory washing machines via business partnerships.

\newpage
\printbibliography[title={Literature}, keyword=important]
\end{refsection}

\newpage
\setstretch{1.5}
\section*{Návrh zadania diplomovej práce}
\begin{longtable}{l l}
\textbf{Názov práce:} & \Title \\
\textbf{Študent:}     & \Author \\
\textbf{Študijný program:} &  Inteligentné softvérové systémy \\
\textbf{Oblasti problematiky:} &  Internet vecí, Spracovanie signálov, Feature engineering \\
\end{longtable}

\small{
Monitorovanie prevádzkového stavu rotačných strojov za účelom včasného odhalenia poškodení je dôležité pre plynulý priebeh priemyselných procesov bez náhleho zlyhania kľúčového technického vybavenia. Nadmerné vibrácie alebo graduálna či náhla zmena ich charakteru sú spoľahlivými indikátormi opotrebenia dielcov. V mnohých prípadoch bývajú zavedené iba pravidelné pôchodzkové merania s následným vyhodnotením časových a frekvenčných priebehov kvalifikovaným personálom. Kontinuálna diagnostika a prediktívna údržba rozširujúca sa so zariadeniami IIoT spôsobuje enormný nárast objemu zaznamenaných dát. Sledovanie výchyliek operátorom a manuálna identifikácia súčiastok vyžadujúcich údržbu v celom závode sa tak stáva prakticky nerealizovateľná.

Preskúmajte spôsoby zisťovania bežných poškodení strojov z vibračných signálov a analyzujte algoritmy na redukciu množstva posielaných dát zo senzorov vzhľadom na osobitosti aplikačnej domény. Navrhnite reprezentáciu údajov na základe typických čŕt signálu, ktorá zníži výpočtové nároky na zvyšok komunikačného reťazca. Zvolený spôsob predspracovania má zároveň umožniť diagnostiku poškodení zvoleného stroja. Implementuje vaše riešenie s ohľadom na možné nasadenie na prostriedkami limitovanú senzorovú jednotku. Následne posúďte efektívnosť, porovnajte dosiahnuté presnosti diagnostiky a verifikujte voči zaužívaným postupom.
}

\printbibliography[
	heading=subbibliography, 
	env=bibassignment,
	title={Literatúra}, 
	keyword=assignment
]
\nocite{*}

\end{document}

### 2023-03-17 chapters/02-analysis.tex
Add notes as direct citations from articles

@@
 
-\section{Physics of rotating machines}
+\section{Condition monitoring}
+
+What are predicted variables - result of diagnoses
+\begin{itemize}
+\item - Presence of the Fault
+\item Type of fault present (different characteristics - e.g. frequency content)
+\item Remaining Useful Life (time until failure) - machines of the same type and different degradation curves
+\end{itemize}
+
+\textbf{Remainig useful life models} (RUL) - is the expected life or usage time remaining before the machine requires repair or replacement.
+\url{https://www.mathworks.com/help/predmaint/ug/rul-estimation-using-rul-estimator-models.html}
+\begin{itemize}
+\item Similarity - run to failure history of similiar machines in database
+\item Degradation - known failure threshold (warning, alert threshold)
+\item Survival  - life-span of components and correlated variables
+\end{itemize}
+
+\cite{jung_vibration_2017}
+\begin{itemize}
+\item Indirect Measurement: indirect and approximate measurement over the vibration phenomenon of the target equipment.
+\item Noisy and Unaligned Observations: well aligned / may contain huge amount of noise.
+\item Variance on Initial Status: initial status of the target equipment different from each other.
+\item Diversity on Lifetime model: the usage and lifetime model -  number of unknown and external factors.
+\end{itemize}
+
+\subsection{Maintenance strategies}
+Difference between fault (degrating performace of the machine - higher friction and power consumption) and failure (machine is unusable). \cite{mohanty_machinery_2015} (picture)
+\begin{itemize}
+\item Reactive - run equipment until failure occurs - low stakes operation. Failure can have negative economic impact or can damage adjacent parts
+\item Preventive - predetermined schedule when assets are diagnosed and repairs are made.
+Crutial to set appropiate maintanance interval.
+Good parts are replaced before they are completely worn out, preventing critical failure, but creating unneccesary waste.
+Sometimes faults are not detected soon enough.
+\item Predictive - model of expected lifetime, warns about unexpected faults before they become too serious and before affecting the machine.
+\end{itemize}
+
+Wear process curve \cite{mohanty_machinery_2015} Bath tub curve (page 10)
+\begin{itemize}
+	\item Initial - large roughness
+	\item Normal - contact area fomred
+	\item Severe - high friction
+\end{itemize}
+
+Rotordynamics (chapter 4) (p. 29)  - p.97 - Fault types, p.127 - faults in electric motors
+
+In order to understand, and correctly diagnose the vibratory characteristics of rotating machinery, it is essential for the machinery diagnostician to understand the physics of dynamic motion.
+This includes the influence of stiffness and damping on the frequency of an oscillating mass — as well as the interrelationship between frequency, displacement, velocity, and acceleration of a body in motion.
+\cite{eisenmann_machinery_1997}
+\begin{itemize}
+\item Forced Vibration Mechanism
+	\begin{itemize}
+	\item Mass Unbalance
+	\item Misalignment
+	\item 	Shaft Bow
+	\item Gyroscopic
+	\item Gear Contact
+	\item Rotor Rubs
+	\item Electrical Excitations
+	\item External Excitations
+	\end{itemize}
+\item Free Vibration Mechanism
+	\begin{itemize}
+	\item Oil Whirl
+	\item Oil or Steam Whip
+	\item  Internal Friction
+	\item Rotor Resonance
+	\item Structural Resonances
+	\item Acoustic Resonances
+	\item Aerodynamic Excitations
+	\item Hydrodynamic Excitations
+	\end{itemize}
+\end{itemize}
 
@@
 
-	\subsection{Band saw anatomy}
-
-\section{Condition monitoring}
-
-	\subsection{Maintenance strategies}
-	% Reactive, Proactive, Predictive
+\begin{itemize}
+\item Bearing faults - vibration on each rotation of rolling elements, CFC (characteric fault frequencies with impulse
+\item Rotor bar faults - current will not flow - forces diffrent on both sides of rotor
+\item Eccentricity Faults - uneven air gap between stator rotor
+\item Misalignment - parralel / angular
+\item Cavitation - pumps
+\item Gearbox fault -broken teeth
+\end{itemize}
+measuring vibration with current, thermal, flux is improvement, +acoustic elminited (detect similiar faults)
+vibration is better alone, then other methods alone (80 vs. <60%)
+ \cite{goel_methodology_2022}
 
@@
 
-	\subsection{Sensor placement}
+ISO-10816 Vibration Severity Chart
+Typical faults produce unusual low-frequency vibrations (10 to 1000 Hz).
+Imbalances, misalignments and looseness are recorded at frequencies up to 300 Hz.
+
+\paragraph{Sensor placement}
 
 \section{Feature engineering}
-	Feature selection vs. extraction
+\subsection{Feature extraction}
+Statistical features in Time-domain (and correlation to blade wear) \cite{zhuo_research_2022} \cite{zheng_feature_2018}
+\begin{itemize}
+	\item 	Root mean square (0.98)
+	\item Mean (0.17)
+	\item Amplitude (0.81)
+	\item Kurtosis (0.042)
+	\item Peak to peak (0.463)
+	\item Signal strength (0.119)
+	\item Standard deviation (0.908)
+	\item Peak value (0.488)
+	\item Shape factor (0.007)
+	\item Skewness (0.118)
+	\item Avearge signal level (0.46)
+	\item Crest factor (0.056, spikeness of the signal - rms/amplitude)
+\end{itemize}
+Selection according to high correlation (graph: sawn-trough section vs feature)
+Features in time domain with high correlaction: RMS, Standard deviation, Amplitude
 
-	\subsection{Signal denoising and filtering}
+Statistical features in Frequency domain (PSD analysis) r >= 0.8 db3 analysis
+\begin{itemize}
+	\item 	Root mean square (0.402)
+	\item Mean (0.497)
+	\item Peak frequency (0.670)
+	\item Kurtosis (0.852)
+	\item Peak to peak (0.076)
+	\item Standard deviation (0.799)
+	\item Peak value (0.787)
+	\item Shape factor (0.851)
+	\item Skewness (0.819)
+	\item Frequency centroid (0.775)
+\end{itemize}
+skewness (PSD\_S), kurtosis (PSD\_k), and shape factor (PSD\_Sf),
+centroid frequency (FFT\_fc), wavelet packet energy entropy (WPD\_EP) = 0.85
+- The WPD energy E8, E10, and E12
+- Energy ratios P8 and P13 of frequency bands 8 and 13
+
+Spectral features \cite{peeters_large_2004} - 1. Spectral shape description
+\begin{itemize}
+\item Coherence function - correlation between two signals PSD
+\item  Spectral centroid - barycenter of the spectrum (weighted mean of the frequencies present in the signal, with their magnitudes as the weights)
+\item Spectral spread
+\item Spectral skewness
+\item Spectral kurtosis
+\item Spectral slope - comupted with linear regression - amount of decresing of the spectral amplitude
+\item Spectral roll-off - 95\% of the signal energy is contained below this frequency
+\item 2. Temporal variation of spectrum - spectral flux - correlation of normalized cross-correlation between two succesive amplitude spectra
+\end{itemize}
+
+Harmonic features
+\begin{itemize}
+\item Fundamental frequency  - Maximu likelihood algorithm
+\item Noisiness - ratio - energy of noise to the total energy
+\item Inharmonicity - energy weighted difference of the spectral components from the multiple of fundamental frequency
+\item Harmonic Spectral Deviation - deviation of amplite harmonics peaks from global spectral envelope
+\end{itemize}
+
+\textbf{Harmonic peak feature} - \cite{jung_vibration_2017}- group of pairs of significant peaks’ value and frequency in PSD. Harmonic peak distance Dij
+
+\begin{itemize}
+\item Standardization - Min-max scaler, Standard scaler (clustering - feature have different scales)
+\item Transformation - Log transformation, Box-Cox
+\end{itemize}
+
+major drawbacks of PSD
+\begin{itemize}
+	\item PSD is a highdimensional feature (i.e., 1024 dimensions in our case) that often generates singular matrix = regression algorithms.
+	\item PSD feature is unreliable due to a large random fluctuation in their amplitudes over frequency due to measurement noise inherent in MEMS sensor.
+\end{itemize}
+
+\subsubsection{Signal denoising and filtering}
 Blind source separation, PCA, ICA
+vibration analysis tools:
+\begin{itemize}
+\item ICA (independent component analysis),
+\item TFA (time-frequency analysis),
+\item ED (energy distribution) and
+\item CD (change detection)
+\end{itemize}
 
-	\subsection{Time-frequency features}
+\subsubsection{Time-frequency features}
+The PSD is the overall expectation of the AE signal. It needs to be calculated by estimation methods. The estimation of the power spectrum is realized by Welch method (cite)
+
 Time Synchronous Averaging of Real FFT
@@
 
-	\subsection{Harmonics identification}
+\subsubsection{Harmonics identification}
 Cepstrum + Harmonic Product Spectrum + Peak identification
 
-	\subsection{Feature importance ranking}
+\subsection{Feature selection}
+Feature importance ranking of Numeric features - Filtering
+\begin{itemize}
+\item High correlation with predictor - band saw blade width of flank face --- to signal statistics
+\item Low correlation (Decorrelation) among predictors themselves - if they are correlated they produce same response
+\item ANOVA with F-Test - Variance of the feature - high variance - is high response
+\item Linearly dependent features are a waste of space and computation power because the information could have been encoded in much fewer features. \cite{zheng_feature_2018} - solve by PCA
+\end{itemize}
 
-\section{Semi-supervised learning in diagnostics}
-	Label propagation
+Vibration levels are dependent on the type of work (load) of the machine (cite)
+\begin{itemize}
+\item \textbf{Sawing process database}: it contains basic information such as sawing machine tools model, band saw blade model, sawing parameters, and the material and size of the workpiece to match the relevant online monitoring model.
+\item \textbf{Online monitoring model database}: it stores online monitoring models of band saw blade wear based on different sawing processes.
+\end{itemize}
 
-	\subsection{Clustering techniques}
-	BIRCH, DBSCAN, SVM
+\section{Diagnostics techniques}
+\url{https://scikit-learn.org/stable/modules/outlier_detection.html#outlier-detection}
+\subsection{Novelty detection}
+\textbf{Fault or no fault} - anomaly detection solutions - unsupervised \cite{torres_automatic_2022}. mean shift clustering algorithm
+\begin{itemize}
+\item Robust Covariance  (Mahalanobis distance)
+\item One-class SVM with non-linear kernel (RBF) - classifying new data as similar or different to the training set
+\item Local outlier factor - local density deviation of a given data point with respect to its neighbours
+\item Isolation forest
+\end{itemize}
 
-	\subsection{Sketch streaming algorithms}
+\textbf{Types of faults - clustering}
+\begin{itemize}
+\item BIRCH
+\item DBSCAN - density based params:
+	minPts (the minimum number of data points that need to be clustered together for an area to be considered high-density)
+	eps (the distance used to determine if a data point is in the same area as other data points).
+\item OPTICS - better DBSCAN -  clusters in data of varying density
+\end{itemize}
+
+\subsection{Label propagation in semi-supervised learning}
+
+Transductive Support vector machine(TSVM),
+Label Propagation Algorithm(LPA)
 
 \section{IoT in Industry 4.0}
+	Wireless protocols limitation: IEEE 802.11, IEEE 802.15.4e, OpenThread
+	Power consumption
+	Devices and sensors
 
-	\subsection{Microcontrollers}
-	% ARM Cortex
-
-	\subsection{Wireless protocols}
-	% IEEE 802.11, IEEE 802.15.4e - IoT Mesh protocols: WirelessHART, ISA100.11a, OpenThread
-	% Formats: CoAP + CBOR
-
-Cite \cite{sample}.
+	The Fig.
+1 shows a generalist architecture supported in the context of Industry 4.0, fault detection systems in electrical machines based on vibration analysis  The Operational Technology (OT) and Information Technology (IT) parts were aligned to design an Industrial Control System (ICS) in the laboratory, for acquiring, controlling and monitoring the operating status of rotating machines, producing reports, automatic alerts and recommending actions to take as a prescriptive maintenance system.
+\cite{torres_automatic_2022}

### 2023-03-25 chapters/02-analysis.tex
Target literature to relevant areas and explore CbM and online clustering

@@
 \section{Condition monitoring}
+\cite{thomson_theory_1993}
+- All bodies possessing mass and elasticity are capable of vibration.
+Thus, most engineering machines and structures experience vibration to some degree, and their design generally requires consideration of their oscillatory behavior.
+- s.58 - rotor unbalance 
+- Chapter 12 (Classical methods) - The exact analysis for the vibration of systems of many degrees of freedom is generally difficult and its associated calculations are laborious.
+Many DOF - the results beyond the first few normal modes are often unreliable and meaningless.
+For this purpose, Rayleigh's method (fundamental frequency of multi-DOF systems) and Dunkerley's equation are of great value and importance.
+In many vibrational systems, we can consider the mass to be lumped.
+A shaft transmitting torque with several pulleys along its length is an example.
+Holzer devised a simple procedure for the calculation of the natural frequencies of such a system.
+Holzer's method was extended to beam vibration by Myklestad and both methods have been matricized into a transfer matrix procedure by Pestel.
+
+\cite{ziaran_technicka_2013}
+p.36 - Regular measurement of mechanical oscilatory motion we can find out beginning of the fault (or future failure) and monitor its progress. Method of trend tracking - extrapolation.
+p.40 - normal level, level indicating significant change, level coresponding to fix
+p.50 - the total magnitude of the oscillation can be compared with reference values set by norms or defined for each type of the machine.
+p.54 - oscillation measurement allows us to quantify dynamic load capacity of mechanical systems a its analysis.
+p.100 - principles of oscillation measurement - choice of sensor type, exclusion of errors caused by resonance, placement and direction of the sensor, mounting of acceleration sensor, the influence of the environment
+p.110 - types of signals - periodic, quasiperiodic, nonstationary
+p.114 - transmission of the oscillation signal through the environment - through discontinuity and construction
+p.139 - signal averaging - linear, exponencial, peak based
+p.148 - kurtosis - high kurtosis means more extreme values - peaks 
+p. 153 - Vibroacustic diagnosis is one of the most important methods of early identification of component faults
+p.165 - severity levels for vibrartion amplitudes (same as in ISO standard). 
+p.178 - reference mask
+p.185 - overview of root causes of machine faults - imbalance, misalignment,  resonance, excentricity, loosnessnes, 
+p.243 - displacement, speed, acceleration
+p.253 - Quanitative evaluation criteria - band A, B, C, D
+p.256 - warning, alarm
+p.261 - characteristics of typical faults
+
+ \cite{davies_techniques_2012}
+p.36 - Condition monitoring is much more than a maintenance scheduling tool.
+Condition monitoring is thus a management technique that uses the regular evaluation of the actual operating condition of plant equipment, production systems and plant management functions, to optimize total plant operation.
+The output of a condition monitoring programme is data.
+Until action is taken to resolve the deviations or problems revealed by the programme, plant performance cannot be improved
+p.40 - This data is compared to either a baseline reading taken from a new machine or to vibration severity charts to determine the relative condition of the machine.
+Normally an unfiltered broadband measurement that provides the total vibration energy between 10 and 10000 Hertz (Hz) is used
+p.38 - Condition monitoring utilizing vibration signature analysis for example is predicated on two basic facts: 
+- 'All common failure modes have distinct vibration frequency components that can be isolated and identified.'
+-  'The amplitude of each distinct vibration component will remain constant unless there is a change in the operating dynamics of the machine train.'
+p.
+269 - Whenever vibration occurs, there are actually four forces involved that determine the characteristics of the vibration.
+These forces are: 1.
+the exciting force, such as unbalance or misalignment; 2.
+the mass of the vibrating system; 3.
+the stiffness of the vibrating system; 4.
+the damping characteristics of the vibrating system.
+p. 294 - Even machines in the best of condition will have some vibration and noise associated with their operation due to minor defects. It is therefore important to remember that:
+ 1. every machine will have a level of vibration and noise which is regarded as inherent normal; 
+ 2. when machinery noise and vibration increase or become excessive, some mechanical defect or operating problem is usually the reason; 
+ 3. each mechanical defect generates vibration and noise in its own unique way.
+p.
+300 -machinery vibration signatures taken in the horizontal, vertical and axial directions at each bearing point on the machine; imbalance will show up predominantly in the horizontal or vertical directions, whereas misalignment will reveal relatively high amplitudes in the axial direction.
+p. 301 
+- When selecting the measurement parameter for analysis, there are two factors to consider. First, why is the reading being taken? Secondly, what is the frequency of the vibration?
+- For general machinery analysis, use velocity whenever possible.
+Amplitude readings in velocity are directly comparable to severity without the need to cross refer amplitude with frequency.
+Where vibration frequencies are very low (approximately below 600 CPM
+p.
+308 - The crest factor, defined as the ratio of the peak to RMS levels, has been proposed as a trending parameter as it includes both parameters (Braun, 1980).
+However, investigations by the author have shown that this parameter usually increases marginally with incipient failure, and subsequently decreases due to the gradually increasing RMS value typical of progressive failure.
+Quite often, the trend recorded by this parameter has been found to be similar to another time domain parameter, the Kurtosis factor
+p.312 Kurtosis - sensitive to failure in rolling element bearings (Dyer and Stewart, 1978).
+However, an independent evaluation of this technique (Mathew and Alfredson, 1984) has shown that high Kurtosis values would only be obtained if the original time waveform was of an impulsive nature
+p.326 - evaluate changes occurring in the signature spectrum is to form a spectral mask. This is derived from the baseline signature, plus an allowable tolerance limit (Randall, 1981a)
 
@@
 \subsection{Maintenance strategies}
-Difference between fault (degrating performace of the machine - higher friction and power consumption) and failure (machine is unusable). \cite{mohanty_machinery_2015} (picture)
+\cite{mohanty_machinery_2015}
+Difference between fault (degrating performace of the machine - higher friction and power consumption) and failure (machine is unusable). (picture)
+reaction-based, time-based, or condition-based maintenance
 \begin{itemize}
@@
 Sometimes faults are not detected soon enough.
+industrial average life statistics, such as Mean Time To Failure (MTTF),
 \item Predictive - model of expected lifetime, warns about unexpected faults before they become too serious and before affecting the machine.
 \end{itemize}
+
+- During operation, machines give out information or signals in the form of noise, vibration, temperature, lubricating oil condition, quality and quantity of the motor current drawn, and the like
+- Once the faults have been detected and diagnosed, the next question is how long the machine will last in the present condition or what is the remaining useful life (RUL) of the machine under observation.
 
@@
 
+Campbell diagram, Bode plot, forced spring-mass-damper system
+
 In order to understand, and correctly diagnose the vibratory characteristics of rotating machinery, it is essential for the machinery diagnostician to understand the physics of dynamic motion.
 This includes the influence of stiffness and damping on the frequency of an oscillating mass — as well as the interrelationship between frequency, displacement, velocity, and acceleration of a body in motion.
+p.395 - Common malfunction   F = ma, torque, $$F_centrifugal = m * r(deviation) * RPM^2$$, $$v = v_0 + \int a$$
+The synchronous, or running speed, or fundamental, or 1X motion of a rotating element is an inherent characteristic of every machine.
+It should be recognized that all machines function with some level of residual unbalance.
+The radial forces from an eccentric element will vary with the speed squared as described by expression
+\begin{itemize}
+\item SYNCHRONOUS RESPONSE (p.395) - physically impossible to produce a perfectly straight and concentric rotor.vibration response is inversely proportional to the restraint or stiffness when the applied force is held constant
+\item MASS UNBALANCE (p.398) - Mass unbalance represents the most common type of synchronous excitation on rotating machinery.
+Every rotor consists of a shaft plus a series of integral disks.
+high dimensional tolerances, a residual unbalance is present in each element.
+Centrifugal force
+\item BENT OR BOWED SHAFT (p.400) - Bent rotors and shaft bows represent another major class of synchronous 1X motion.
+It was previously mentioned that all machine parts contain some finite amount of residual unbalance.
+In a similar manner, all assembled horizontal rotors (and some vertical rotors), will exhibit varying degrees of rotor bows.
+\item ECCENTRICITY  (p.406) - Large machine elements or high rotational speeds are the most susceptible to high forces due to an eccentric element. many motor problems only appear under load.
+\item SHAFT PRELOADS (p.410) - The presence of various types of unidirectional forces acting upon the rotating mechanical system is a normal and expected characteristic of machinery.
+Just as residual unbalance, rotor bows, and component eccentricity are inherent with the assembly of rotating elements, the presence of shaft preloads are an unavoidable part of assembled mechanical equipment.
+Gravitational preloads
+\item RESONANT RESPONSE (p.416) - Machines and structures all contain natural frequencies that are essentially a function of stiffness and mass.
+f = sqrt(k/m) lowest order resonant frequency.
+For more complex mechanical systems an entire family of resonant responses must be addressed.
+The range of natural frequencies may vary from 60 CPM (1 Hz) for the foundation and support systems, to 1,800,000 CPM (30,000 Hz) for turbine blade The actual number of system natural frequencies may vary from 20 to 50 or more.
+Campbell diagram  -  natural frequencies (or eigenfrequencies)
+
+Rotodynamics
+$$ \mathbf{M} \frac{\partial^2 \mathbf{q}(t)}{\partial t^2} + (\mathbf{C} + \mathbf{G})\frac{\partial\mathbf{q}(t)}{\partial t} + (\mathbf{K} + \mathbf{N})\mathbf{q}(t) = \mathbf{f}(t) $$
+    M is the symmetric Mass matrix
+    C is the symmetric damping matrix
+    G is the skew-symmetric gyroscopic matrix
+    K is the symmetric bearing or seal stiffness matrix
+    N is the gyroscopic matrix of deflection for inclusion of e.g., centrifugal elements.
+in which q is the generalized coordinates of the rotor in inertial coordinates and f is a forcing function, usually including the unbalance.
+axially symmetric rotor rotating at a constant spin speed $\Omega$.
+The gyroscopic matrix G is proportional to spin speed $\Omega$.
+The general solution to the above equation involves complex eigenvectors which are spin speed dependent.
+\item ROTOR RUBS (p.440) - The physical contact between rotating elements and stationary machine parts can generate a variety of rub conditions In the frequency domain, the intermittent rub looks like a loose bearing housing with integer fractions of rotative speed (e.g., X/2, X/3, or X/ 4) plus a string of fractional frequencies (e.g.
+3X/2, 5X/2, 7X/2, etc.)
+\item CRACKED SHAFT -Machines that are subjected to frequent startups and shutdowns appear to be more susceptible to shaft cracks due to the increased number of cycles through the rotor resonance(s), plus the process heating and cooling.
+Cracks may originate at high stress points such as the square corners
+\end{itemize}
+p.704 - maintenance activities may be categorized as either reaction-based, time-based, or condition-based maintenance
+
+Machinery Diagnostic Methodology (s.747)
+\begin{itemize}
+	\item Diagnostic objectives - solving the problem
+	\item Mechanical inspection - hands on examination of the machinery
+	\item DATA ACQUISITION AND PROCESSING - requires the assembly of the proper transducers and test instrumentation.
+ata acquired is really a function of the specific machine, the associated problem, and the individual test plan
+	\item Data interpretation - summary and correlation of all pertinent data acquired during the project.
+This includes the mechanical configuration, process and maintenance history, field testing data, plus any supportive calculations or analytical models
+
+The 30,000 horsepower gas turbine behaves quite differently from a similarly rated steam turbine.
+Hence, the data must be interpreted in accordance with the physical characteristics of the particular machine type and the operating environment.
+One approach is to view the data in terms of normal behavior for a particular machine type, and then look for the abnormalities in response characteristics.
+\end{itemize}
  \cite{eisenmann_machinery_1997}
@@
 \end{itemize}
+
+\cite{popescu_blind_2010}
+- The analysis of the behavior of such signals reveals that the most of the changes that occur are either changes in the mean level, or changes in spectral characteristics.
+In this framework, the problem of segmentation between ‘‘homogenous” part of the signals (or detection of changes in signals) arises more or less explicitly
+- the key for their common success resides in the proper design of the statistical criteria according to which separation is forced
+- It can be noted a moving of the spectra to the low frequency area, with increased values of the PSD, after the fault produced
 
@@
 
+% -----------------------------------------------------------------------------------------------------------------------
 \section{Feature engineering}
@@
 
+Transform -> SVD vs. FFT vs. EMD
 Statistical features in Frequency domain (PSD analysis) r >= 0.8 db3 analysis
@@
 
+\cite{lagrange_robust_2010}
+measure the \textbf{spectral flatness} of the ratio between the observations (the peaks) with respect to the model (the spectral envelope):
+
 \subsubsection{Signal denoising and filtering}
-Blind source separation, PCA, ICA
+PCA on features to find most separation - Singular Value Decomposition (QR algorithm) - eigenvalue algorithm , 
+ICA - FastICA to separate sources
 vibration analysis tools:
@@
 \item ED (energy distribution) and
-\item CD (change detection)
 \end{itemize}
@@
 The PSD is the overall expectation of the AE signal. It needs to be calculated by estimation methods. The estimation of the power spectrum is realized by Welch method (cite)
-
-Time Synchronous Averaging of Real FFT
-vs. FastCWT - Synchrosqueezing
+Time Synchronous Averaging of Real FFT vs. FastCWT - Synchrosqueezing
 
 \subsubsection{Harmonics identification}
-Cepstrum + Harmonic Product Spectrum + Peak identification
+Cepstrum (for  gearboxes)
+Peak identification
 
@@
 
+% -----------------------------------------------------------------------------------------------------------------------
 \section{Diagnostics techniques}
-\url{https://scikit-learn.org/stable/modules/outlier_detection.html#outlier-detection}
+Inbalanced data, Feature space
+Scale  -  Normalize and log transform
+multi class classification - dynamic
+
 \subsection{Novelty detection}
 \textbf{Fault or no fault} - anomaly detection solutions - unsupervised \cite{torres_automatic_2022}. mean shift clustering algorithm
+\textbf{Types of faults - clustering} - Multimodal non-Gaussian multivariate probability distribution
+
 \begin{itemize}
-\item Robust Covariance  (Mahalanobis distance)
-\item One-class SVM with non-linear kernel (RBF) - classifying new data as similar or different to the training set
-\item Local outlier factor - local density deviation of a given data point with respect to its neighbours
-\item Isolation forest
+\item \textbf{DenStream} - (based on DBSCAN)  density based params: - continous regions of high density
+	minPts (the minimum number of data points that need to be clustered together for an area to be considered high-density)
+	eps (the distance used to determine if a data point is in the same area as other data points). - compare to MAD. OPTICS for not same density.
+\item \textbf{IForestASD - Isolation Forest Algorithm for Stream Data method} - isolation teqnique (map feature space to anomaly score) - how many uniform splits does it take before point is isolated (alone in group)
+\item \textbf{Label propagation algorithm} - Temporal Label Propagation - Graph-Based Methods in semi-supervised learning (p.9)
 \end{itemize}
 
-\textbf{Types of faults - clustering}
+\cite{chapelle_semi-supervised_2006}
+p.5
 \begin{itemize}
-\item BIRCH
-\item DBSCAN - density based params:
-	minPts (the minimum number of data points that need to be clustered together for an area to be considered high-density)
-	eps (the distance used to determine if a data point is in the same area as other data points).
-\item OPTICS - better DBSCAN -  clusters in data of varying density
+\item Semi-supervised smoothness assumption: If two points x1,x2 in a high-density region are close, then so should be the corresponding outputs y1,y2. 
+\item Cluster assumption: If points are in the same cluster, they are likely to be of the same class.
+\item The cluster assumption can be formulated in an equivalent way: Low density separation: The decision boundary should lie in a low-density region.
+\item Manifold assumption: The (high-dimensional) data lie (roughly) on a low-dimensional manifold.
+\item Consider as an example supervised learning, where predictions of labels y corresponding to some objects x are desired.
+Generative models estimate the density of x as an intermediate step, while discriminative methods directly estimate the labels.
 \end{itemize}
 
-\subsection{Label propagation in semi-supervised learning}
+Classification can be treated as a special case of estimating the joint density P (x,y), but this is wasteful since x will always be given at prediction time, so there is no need to estimate the input distribution.
+The terminology “unsupervised learning” is a bit unfortunate: the term density 1.
+We restrict ourselves to classification scenarios in this chapter estimation should probably be preferred.
+Traditionally, many techniques for density estimation propose a latent (unobserved) class variable y and estimate P (x) as mixture distribution
 
-Transductive Support vector machine(TSVM),
-Label Propagation Algorithm(LPA)
+The semi-supervised learning problem belongs to the supervised category, since the goal is to minimize the classification error, and an estimate of P(x) is not sought after
 
 \section{IoT in Industry 4.0}
-	Wireless protocols limitation: IEEE 802.11, IEEE 802.15.4e, OpenThread
-	Power consumption
-	Devices and sensors
+	Devices and sensors + Wireless protocols limitation: IEEE 802.15.4e, OpenThread
+	RAMI 4.0 \cite{torres_automatic_2022}
 
-	The Fig.
-1 shows a generalist architecture supported in the context of Industry 4.0, fault detection systems in electrical machines based on vibration analysis  The Operational Technology (OT) and Information Technology (IT) parts were aligned to design an Industrial Control System (ICS) in the laboratory, for acquiring, controlling and monitoring the operating status of rotating machines, producing reports, automatic alerts and recommending actions to take as a prescriptive maintenance system.
-\cite{torres_automatic_2022}
+\url{https://riverml.xyz/0.15.0/}

### 2023-03-25 chapters/appendix/B-plan-of-work.tex
Target literature to relevant areas and explore CbM and online clustering

@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week         & Consultation with the supervisor on directions of the future work based on literature review during previous semester. Meeting schedule is established.
+\nth{1} week         & Consultation with the supervisor on directions of the future work based on literature review during previous semester.
 \\ \hline
-\nth{2} week         & Outline of key sections of the analysis part of the thesis.
+\nth{2} week         & Outline the key sections of the analysis part in the thesis.
 \\ \hline
-\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering in condition monitoring.
+\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering methodology in condition monitoring.
  \\ \hline
-\nth{4} week         & TBD (Descibe machinery physics and maintanance strategies.)
+\nth{4} week         & Summarize notes from condition monitoring articles and videorecordings of tutorials and conferences.
+ \\ \hline
+\nth{5} week         & Research transformation of vibration signal to feature space using time-frequency, harmonic and energy statistical metrics. Progress report meeting with the supervisor.
+ \\ \hline
+\nth{6} week         & Find articles and take notes about unsupervised and semi-supervised techniques in streaming data for machinery diagnostics, in order to gather information about suitable features.
+ \\ \hline
+\nth{7} week         & TBD (Narrow down wide variety applicable methods for signal decomposition)
+ \\ \hline
+ \nth{8} week         & TBD (Write thesis section on condition monitoring and machinery fault types)
  \\ \hline

### 2023-03-29 chapters/02-analysis.tex
Begin feature extraction literature notes

@@
 
-Wear process curve \cite{mohanty_machinery_2015} Bath tub curve (page 10)
+Wear process curve Bath tub curve (page 10)
 \begin{itemize}
@@
 \end{itemize}
+
+p.11 - Failure Modes Effects and Criticality Analysis (FMECA) FMECA is a methodology widely used in the industry to identify and analyze all potential failure modes of the various parts of a system
+p.30 - Simple Rigid Rotor-Disc System (Jeffcott rotor) - shaft that rotates and is supported at two ends by bearings with disc
+p.26 - machines are designed so that the system’s natural or resonance frequencies are not close to the machine’s operating speed.
+p.93 - In a majority of the rotating machinery, vibration monitoring is preferred.
+This is due to the fact that every dynamic machine component will manifest itself in the measured vibration response of the machine at its characteristic frequencies.
+Bearing Coupling, Motor, Mechanical drive
+p.93 - vibrations at any location should be measured in three mutually perpendicular directions.
+Simultaneous measurement of the vibration in three directions can be done using a triaxial accelerometer.
+It  is always desirable to record the rotating speed of the  shafts at the instant that vibration measurements are  done, because all the predominant frequencies in the vibration spectra are related to the rotating speeds of the shaft
+p.97 - Eccentric rotors occur when the geometric center of the rotor does not coincide with the center line through the support bearings.
+crack growth rate is determined by the famous Paris equation, which depends on the material type and type of loading
+Unbalance is due to a net uneven distribution of the mass of a rotating component about its axi
+p.
+101 - looseness manifests as high levels of impulsive vibrations in the time domain.
+The typical frequency domain characteristics of looseness in rotating machines is the presence of vibration peaks at fractional harmonics of the rotational speed and their harmonics.
+
+p. 216 Appendix A1: Vibration-Based Machinery Fault Identification
+Shaft/Rotor Unbalance , Misalignment, Looseness, Rub, Crack, Bearings Journal, Rolling Element, Fan/Blowers, Pulley/Belt, Electrical Motor
+Appendix A2: Vibration Severity Levels
 
@@
 
-ISO-10816 Vibration Severity Chart
+ISO-10816 Vibration Severity Chart (include table)
+
 Typical faults produce unusual low-frequency vibrations (10 to 1000 Hz).
@@
 
-\paragraph{Sensor placement}
+\subsection{Sensor placement}  
+- Frequency Limitations Resulting from Mounted Resonance of an Accelerometer, Jack D. Peters
+- Axial, Radial (Standard)
+- Mounting resonance is a direct result of lowering the accelerometers natural frequency and occurs as the result of reduced stiffness or increased mass. $f_n = \frac{1}{2\pi}\sqrt{\frac{k}{m}}$
+- Under ideal circumstances, the accelerometer mounting should provide total use of the transmission region
+p.4 - Probe tip (500 Hz), Curved surface magnet (2 kHz), Quick disconnect (6.5 kHz), Flat magnet (10 kHz), Adhesive mount (10 - 15 kHz), Stud mount (15 kHz)
 
@@
 \section{Feature engineering}
+
 \subsection{Feature extraction}
+\cite{goumas_classification_2002}
+	- Mapping measurement sapce into feature space
+	- Pattern classification - partitioning feature space into decision subspaces
+	- Feature vector - point in N-dimensional feature space - assign to pattern class
+	- Classification of N-dimensional feature space with M classes may be viewed as a problem of defining hyperplanes to divide N-dimensional Euclidian space into M regions.
+	- Pattern recognition stages: measurements, feature extraction, classification
+	- Washing machines 500 Hz, 20 signals
+	- 8 measurement poinst - Vibrartion on lower part of machine is atenuated because of contant effect with ground - p.7
+	Types of machines in population:		
+		- z machines - no fault, 
+		- b machines - electric motor clamping screws problems
+		- p machines - counter weight distorted (loose, broken)
+	- Daubechies Wavelet function 4 (D4) with fifth-level decomposition FWT  - Detail coeficient (abrupt changes as local variations in coef.) and last-level approx. coef.
+	- Autocorrelation function from coeficients - p.8 -> Moving average filter
+	- S1, S2 result of moving average filtering on cD1, cD2 (DWT detail coeficients) 
+	- Karhunen–Loève transform - PCA transformsoriginal variables into new set of uncorrelated variables called Principal components (PCs) - p.9
+	- Bayesian classification, 87\% - Naive Bayes
+
+Aggarwal - Data clustering
+In feature selection, original subsets of the features are selected.
+In dimensionality reduction, linear combinations of features may be used in techniques such as principal component analysis in order to further enhance the feature selection effect.
+The advantage of the former is greater interpretability, whereas the advantage of the latter is that a lesser number of transformed directions is required for the representation process.
+
+Feature extraction - PCA on features to find most separation 
+	- Reduce dimensionality 
+	- Singular Value Decomposition (QR algorithm) - eigenvalue algorithm ,
+
+p.232 - Streams typically have massive volume, and it is often not possible to store the data explicitly on disk.
+Therefore, the data needs to be processed in a single pass, in which all the summary information required for the clustering process needs to be stored and maintained.
+
 Statistical features in Time-domain (and correlation to blade wear) \cite{zhuo_research_2022} \cite{zheng_feature_2018}
+
+p. 254 furthest point algorithm - local clustering at each node and merges these different clusters into a single global clustering at low communication cost.
+
 \begin{itemize}
@@
 
-Transform -> SVD vs. FFT vs. EMD
 Statistical features in Frequency domain (PSD analysis) r >= 0.8 db3 analysis
@@
 
-\textbf{Harmonic peak feature} - \cite{jung_vibration_2017}- group of pairs of significant peaks’ value and frequency in PSD. Harmonic peak distance Dij
+\cite{lagrange_robust_2010}
+measure the \textbf{spectral flatness} of the ratio between the observations (the peaks) with respect to the model (the spectral envelope)
+
+\cite{jung_vibration_2017}
+\textbf{Harmonic peak feature} - 
+- RUL estimation - Harmonic peak distance is score from baseline - create probability density functions (with Recursive RANSAC regression algorithm - because of noisy distribution) of zones A,  BC, D
+and cut on transition to zone D (around >0.21 Peak distance)
+- group of pairs of significant peaks’ value and frequency in PSD (p, f)
+- Distance is euclidian based - closest peak frequency and value
+- Harmonic peak distance - compare baseline harmonic peak feature (20 peaks - points where its first order differential changes from positive to negative-  from smooth spectrum by 16 point Hann window)
+
+\cite{li_fault_2019}
+p.8 - rolling element bearing equation mechanics
+Detect bearing faults - impulses (transients)
+Maximum Correlated Kurtosis Deconvolution (MCKD)
+	- FIR filter maximizing the CK (Kurtosis) of the impulses - Result coeficients of the filter
+Empirical Wavelet Transform 
+	- address the mode mixing or over-estimation phenomenon of the EMD
+	- EWT divides the spectrum into several portions, and each portion corresponds to a mode centered at the specific frequency and compact support, such as AM-FM signal
+Algorithm MKCD-EWT
+	- De-noise the signal by MCKD.
+	- Spectrum segmentation. Calculate the envelope curve of the amplitude spectrum of the de-noising signal.
+	- Signal decomposition. Design the wavelet filter banks
+	- IMF (Intrinsic Mode Function) selection. Calculate the kurtosis of each sub-signal
+	- Feature extraction. Calculate the squared envelope spectrum and \textbf{teager energy operator} spectrum of the chosen mode
+- Highest kurtosis values of these modes IMF1 - 4 in the largest IMF
+
+Teager-Kaiser operator (TKEO)
+Teager Energy Operator (TEO)
+$x(t)  = (dx/dt)^2+ x(t)(d^2x/dt^2) $
+$[x[n]] = x^2[n] + x[n - 1]x[n + 1]$
+
+\cite{yu_concentrated_2020}
+- spectral kurtosis (SK) method, synchrosqueezing transform (SST)
+- Transient-extracting operator (TEO) - from Dirac delta
+- transient-extracting transform (TET)
+$ TEO(t, \omega) = \delta(t − t_0(t, \omega))$
+$ Te(t, \omega) = G(t, \omega) \cdot TEO(t, \omega) $
+
+\subsection{Power spectral density segmentation}
+
+Denoising
+SNR - The traditional approach to calculating SNR is to measure the average Active level, subtract the average Inactive
+level, and divide that result by the peak level of noise witnessed on the Inactive level.
 
 \begin{itemize}
+\item Shift mean - remove by averaging filter
 \item Standardization - Min-max scaler, Standard scaler (clustering - feature have different scales)
 \item Transformation - Log transformation, Box-Cox
+\item Adaptive Noise Canceling -  least mean squares (LMS) filter - stocahstic signals
+\item ICA (independent component analysis) - FastICA, JADE - denoising from enviroment - Same as Adaptive Noise Cancelation, 		- exploitation of the spatial diversity provided by many sensors and is the fundamental basis of BSS.
+finding an estimate S (n) of the sources X (n) by adapting an unknown separating function which leads to independence of S (n).
+	- instantaneous model can hold when the structure under investigation has a high rigidity and a small size.
+aim of the problem; i.e., to "nd a linear transformation, which relies on independent components (sources) contributing to the observations of a mixture of them
+	- In short, the BSS problem cannot be solved by using only second order statistics because independence is a stronger condition than uncorrelation.
+	- real recordings, it is very diffcult to measure the separation quality.
+Here, prior knowledge about the sources was used; that is, harmonic frequencies in relation to the mechanical components as well as the signals recorded on each source separately in the real environment (the reference).
+	- 20000 samples were considered for each frequency channel to perform separation (fs = 500 Hz) -> 40 s
+\item TSA - 
+	- TSA and show that noise reduction is 1/sqrt(number of revolutions). 
+	- The third topic examines TSA techniques when no tachometer signal is available. 
+	- it allows the vibration signature of the gear under analysis to be separated from other gears and noise sources in the gearbox
+	- phase information can be provided through a n per revolution tachometer signal (such as a Hall sensor or optical encoder) or though demodulation of gear mesh signatures
+
+	\cite{bechhoefer_review_2009}
+\end{itemize}
+
+\begin{itemize}
+\item Averaging - Time Synchronous Averaging, Welch method
+\item TFA (time-frequency analysis) - Real FFT
+\item, Empirical Mode Decomposition na Intrinsic Modes - EMD/EEMD - Each IMF represents a narrow band frequency - amplitude modulation that is often related to a specific physical process (mode mixing phenomenon),\cite{wang_computational_2014}
+
+\item SST - originally introduced in the context of audio signal analysis and is shown to be an alternative to EMD -  \cite{herrera_applications_2014}
+
+\item Fast CWT
+\item Synchrosqueezing - SST - extension of the wavelet transform incorporating elements of empirical mode decomposition and frequency reassignment techniques
+\item EWT 
+\item Peak identification, Spectral Envelope
 \end{itemize}
@@
 \end{itemize}
-
-\cite{lagrange_robust_2010}
-measure the \textbf{spectral flatness} of the ratio between the observations (the peaks) with respect to the model (the spectral envelope):
-
-\subsubsection{Signal denoising and filtering}
-PCA on features to find most separation - Singular Value Decomposition (QR algorithm) - eigenvalue algorithm , 
-ICA - FastICA to separate sources
-vibration analysis tools:
-\begin{itemize}
-\item ICA (independent component analysis),
-\item TFA (time-frequency analysis),
-\item ED (energy distribution) and
-\end{itemize}
-
-\subsubsection{Time-frequency features}
-The PSD is the overall expectation of the AE signal. It needs to be calculated by estimation methods. The estimation of the power spectrum is realized by Welch method (cite)
-Time Synchronous Averaging of Real FFT vs. FastCWT - Synchrosqueezing
-
-\subsubsection{Harmonics identification}
-Cepstrum (for  gearboxes)
-Peak identification
 
@@
 \end{itemize}
+
+Feature selection (for classification) - SelectKBest
+\begin{itemize}
+	\item Variance threshold
+	\item Pearson correlation coeficient
+	(Filter methods:)
+	\item ANOVA F-value
+	\item Mutual information (MI) - Information Gain
+	\item Fisher's score
+	\item Spectral Feature Selection (SPEC) algorithm
+\end{itemize}
+		-  selects subset of highly discriminant features. In other words, it selects features that are capable of discriminating samples that belong to different classes.
+		- Unlabeled data poses yet another challenge in feature selection.
+In such cases, defining relevancy becomes unclear.
+However, we still believe that selecting subset(s) of features may help improve unsupervised learning,
+		- With the existence of a large number of features, learning models tend to overfit and their learning performance degenerates
+p.30 - However, feature selection is superior in terms of better readability and interpretability since it maintains the original feature values in the reduced space, 
+while feature extraction transforms the data from the original space into a new space with lower dimension, which cannot be linked to the features in the original space.
+Feature selection is: filter model, wrapper model, embedded model, hybrid model
+
+Feature selection algorithms fall into one of the three categories: 
+- subset selection -  returns a subset of selected features identified by the index of the feature 
+- feature weighting- returns weight corresponding to each feature (generalization of subset selection  0 - 1) ;
+- hybrid of subset selection and feature weighting - returns a ranked subset of features.
 
@@
 \textbf{Fault or no fault} - anomaly detection solutions - unsupervised \cite{torres_automatic_2022}. mean shift clustering algorithm
-\textbf{Types of faults - clustering} - Multimodal non-Gaussian multivariate probability distribution
+\textbf{Types of faults - clustering, classification} - Multimodal non-Gaussian multivariate probability distribution
 
@@
 \section{IoT in Industry 4.0}
-	Devices and sensors + Wireless protocols limitation: IEEE 802.15.4e, OpenThread
-	RAMI 4.0 \cite{torres_automatic_2022}
+	Devices and sensors + Wireless protocols limitation: IEEE 802.15.4e, OpenThread \cite{torres_automatic_2022}
 

### 2023-03-30 chapters/02-analysis.tex
Extract sample frequency features and notes to separate file

--- 2023-03-17 chapters/02-analysis.tex
@@
 
-What are predicted variables - result of diagnoses
-\begin{itemize}
-\item - Presence of the Fault
-\item Type of fault present (different characteristics - e.g. frequency content)
-\item Remaining Useful Life (time until failure) - machines of the same type and different degradation curves
-\end{itemize}
-
-\textbf{Remainig useful life models} (RUL) - is the expected life or usage time remaining before the machine requires repair or replacement.
-\url{https://www.mathworks.com/help/predmaint/ug/rul-estimation-using-rul-estimator-models.html}
-\begin{itemize}
-\item Similarity - run to failure history of similiar machines in database
-\item Degradation - known failure threshold (warning, alert threshold)
-\item Survival  - life-span of components and correlated variables
-\end{itemize}
-
-\cite{jung_vibration_2017}
-\begin{itemize}
-\item Indirect Measurement: indirect and approximate measurement over the vibration phenomenon of the target equipment.
-\item Noisy and Unaligned Observations: well aligned / may contain huge amount of noise.
-\item Variance on Initial Status: initial status of the target equipment different from each other.
-\item Diversity on Lifetime model: the usage and lifetime model -  number of unknown and external factors.
-\end{itemize}
-
 \subsection{Maintenance strategies}
-Difference between fault (degrating performace of the machine - higher friction and power consumption) and failure (machine is unusable). \cite{mohanty_machinery_2015} (picture)
-\begin{itemize}
-\item Reactive - run equipment until failure occurs - low stakes operation. Failure can have negative economic impact or can damage adjacent parts
-\item Preventive - predetermined schedule when assets are diagnosed and repairs are made.
-Crutial to set appropiate maintanance interval.
-Good parts are replaced before they are completely worn out, preventing critical failure, but creating unneccesary waste.
-Sometimes faults are not detected soon enough.
-\item Predictive - model of expected lifetime, warns about unexpected faults before they become too serious and before affecting the machine.
-\end{itemize}
-
-Wear process curve \cite{mohanty_machinery_2015} Bath tub curve (page 10)
-\begin{itemize}
-	\item Initial - large roughness
-	\item Normal - contact area fomred
-	\item Severe - high friction
-\end{itemize}
-
-Rotordynamics (chapter 4) (p. 29)  - p.97 - Fault types, p.127 - faults in electric motors
-
-In order to understand, and correctly diagnose the vibratory characteristics of rotating machinery, it is essential for the machinery diagnostician to understand the physics of dynamic motion.
-This includes the influence of stiffness and damping on the frequency of an oscillating mass — as well as the interrelationship between frequency, displacement, velocity, and acceleration of a body in motion.
-\cite{eisenmann_machinery_1997}
-\begin{itemize}
-\item Forced Vibration Mechanism
-	\begin{itemize}
-	\item Mass Unbalance
-	\item Misalignment
-	\item 	Shaft Bow
-	\item Gyroscopic
-	\item Gear Contact
-	\item Rotor Rubs
-	\item Electrical Excitations
-	\item External Excitations
-	\end{itemize}
-\item Free Vibration Mechanism
-	\begin{itemize}
-	\item Oil Whirl
-	\item Oil or Steam Whip
-	\item  Internal Friction
-	\item Rotor Resonance
-	\item Structural Resonances
-	\item Acoustic Resonances
-	\item Aerodynamic Excitations
-	\item Hydrodynamic Excitations
-	\end{itemize}
-\end{itemize}
 
 \subsection{Vibration fault types}
-There are a few methods of machinery fault identification in vibrational signals based on domain expertise.
-Data points can be viewed in the time domain and frequency domain.
-Either as individual stationary profiles obtained during the short duration in the time of measurement, or multiple spaced-out observations with the intent to highlight the long-term trend, e.g.
-shown in a waterfall plot \cite{ziaran_technicka_2013}.
-The descriptor variable can be any meaningful statistical quantity, e.g.
-peak-to-peak, RMS, crest factor, kurtosis, which can be applied to recorded samples or frequency bands.
-
-Mechanical faults manifest themselves in the vibration signal at various frequencies.
-In the low-frequency range (up to 1 kHz) shaft's unbalance, misalignment, bend, crack, and mechanical looseness is present.
-High frequencies (up to 16 kHz or more) contain bearings faults and gear faults.
-
-Under fault-free circumstances, shaft speed appears as the strongest frequency component.
-In case of shaft and gear imbalance or damage, synchronous multiples of shaft frequency (harmonics) are amplified.
-When rub, bad drive belts and chains, or looseness is occurring in the machine then sub-synchronous harmonics or even non-synchronous frequencies appear \cite{mohanty_machinery_2015}.
-Therefore it is useful to rescale the horizontal axis to RPM or orders of rotational speed.
-Complementary methods of fault symptom identification are phase and orbital analysis \cite{scheffer_practical_2004}.
-
-\begin{itemize}
-\item Bearing faults - vibration on each rotation of rolling elements, CFC (characteric fault frequencies with impulse
-\item Rotor bar faults - current will not flow - forces diffrent on both sides of rotor
-\item Eccentricity Faults - uneven air gap between stator rotor
-\item Misalignment - parralel / angular
-\item Cavitation - pumps
-\item Gearbox fault -broken teeth
-\end{itemize}
-measuring vibration with current, thermal, flux is improvement, +acoustic elminited (detect similiar faults)
-vibration is better alone, then other methods alone (80 vs. <60%)
- \cite{goel_methodology_2022}
 
 \subsection{Technical standards}
-The maintenance procedure usually involves data acquisition cards inside handheld devices with accelerometer sensor probes then mounted firmly to the machine frame by either screwing in, magnets or wax \cite{ziaran_technicka_2013}.
-The probe placement in axial and perpendicular radial directions is standardized in ISO 20816.
-The severity of vibrations is mostly assessed in units of velocity ($mm/s$), but acceleration ($m/s^2$) and displacement ($\mu m$) are also used.
-Based on the observed vibration intensity and one of the four classes of machines (I, II, III, IV) by output power and size, zones (A, B, C, D) for accepted levels are proposed.
-It is customary to establish operational limits in the form of alarms and trips \cite{iso_20816}.
 
-Standard ISO 13373 categorizes three types of vibration monitoring systems: permanent, semi-permanent, and mobile.
-More importantly, a structured diagnostic approach is developed here complete with recommendations for formalizing diagnostic techniques \cite{iso_13373}.
-The next step is the signal analysis with the use of proper units and transformations is the subject of the ISO 18431 \cite{iso_18431}.
-
-ISO-10816 Vibration Severity Chart
-Typical faults produce unusual low-frequency vibrations (10 to 1000 Hz).
-Imbalances, misalignments and looseness are recorded at frequencies up to 300 Hz.
-
-\paragraph{Sensor placement}
+\subsection{Sensor placement}
 
 \section{Feature engineering}
+
 \subsection{Feature extraction}
-Statistical features in Time-domain (and correlation to blade wear) \cite{zhuo_research_2022} \cite{zheng_feature_2018}
-\begin{itemize}
-	\item 	Root mean square (0.98)
-	\item Mean (0.17)
-	\item Amplitude (0.81)
-	\item Kurtosis (0.042)
-	\item Peak to peak (0.463)
-	\item Signal strength (0.119)
-	\item Standard deviation (0.908)
-	\item Peak value (0.488)
-	\item Shape factor (0.007)
-	\item Skewness (0.118)
-	\item Avearge signal level (0.46)
-	\item Crest factor (0.056, spikeness of the signal - rms/amplitude)
-\end{itemize}
-Selection according to high correlation (graph: sawn-trough section vs feature)
-Features in time domain with high correlaction: RMS, Standard deviation, Amplitude
 
-Statistical features in Frequency domain (PSD analysis) r >= 0.8 db3 analysis
-\begin{itemize}
-	\item 	Root mean square (0.402)
-	\item Mean (0.497)
-	\item Peak frequency (0.670)
-	\item Kurtosis (0.852)
-	\item Peak to peak (0.076)
-	\item Standard deviation (0.799)
-	\item Peak value (0.787)
-	\item Shape factor (0.851)
-	\item Skewness (0.819)
-	\item Frequency centroid (0.775)
-\end{itemize}
-skewness (PSD\_S), kurtosis (PSD\_k), and shape factor (PSD\_Sf),
-centroid frequency (FFT\_fc), wavelet packet energy entropy (WPD\_EP) = 0.85
-- The WPD energy E8, E10, and E12
-- Energy ratios P8 and P13 of frequency bands 8 and 13
-
-Spectral features \cite{peeters_large_2004} - 1. Spectral shape description
-\begin{itemize}
-\item Coherence function - correlation between two signals PSD
-\item  Spectral centroid - barycenter of the spectrum (weighted mean of the frequencies present in the signal, with their magnitudes as the weights)
-\item Spectral spread
-\item Spectral skewness
-\item Spectral kurtosis
-\item Spectral slope - comupted with linear regression - amount of decresing of the spectral amplitude
-\item Spectral roll-off - 95\% of the signal energy is contained below this frequency
-\item 2. Temporal variation of spectrum - spectral flux - correlation of normalized cross-correlation between two succesive amplitude spectra
-\end{itemize}
-
-Harmonic features
-\begin{itemize}
-\item Fundamental frequency  - Maximu likelihood algorithm
-\item Noisiness - ratio - energy of noise to the total energy
-\item Inharmonicity - energy weighted difference of the spectral components from the multiple of fundamental frequency
-\item Harmonic Spectral Deviation - deviation of amplite harmonics peaks from global spectral envelope
-\end{itemize}
-
-\textbf{Harmonic peak feature} - \cite{jung_vibration_2017}- group of pairs of significant peaks’ value and frequency in PSD. Harmonic peak distance Dij
-
-\begin{itemize}
-\item Standardization - Min-max scaler, Standard scaler (clustering - feature have different scales)
-\item Transformation - Log transformation, Box-Cox
-\end{itemize}
-
-major drawbacks of PSD
-\begin{itemize}
-	\item PSD is a highdimensional feature (i.e., 1024 dimensions in our case) that often generates singular matrix = regression algorithms.
-	\item PSD feature is unreliable due to a large random fluctuation in their amplitudes over frequency due to measurement noise inherent in MEMS sensor.
-\end{itemize}
-
-\subsubsection{Signal denoising and filtering}
-Blind source separation, PCA, ICA
-vibration analysis tools:
-\begin{itemize}
-\item ICA (independent component analysis),
-\item TFA (time-frequency analysis),
-\item ED (energy distribution) and
-\item CD (change detection)
-\end{itemize}
-
-\subsubsection{Time-frequency features}
-The PSD is the overall expectation of the AE signal. It needs to be calculated by estimation methods. The estimation of the power spectrum is realized by Welch method (cite)
-
-Time Synchronous Averaging of Real FFT
-vs. FastCWT - Synchrosqueezing
-
-\subsubsection{Harmonics identification}
-Cepstrum + Harmonic Product Spectrum + Peak identification
+\subsection{Power spectral density segmentation}
 
 \subsection{Feature selection}
-Feature importance ranking of Numeric features - Filtering
-\begin{itemize}
-\item High correlation with predictor - band saw blade width of flank face --- to signal statistics
-\item Low correlation (Decorrelation) among predictors themselves - if they are correlated they produce same response
-\item ANOVA with F-Test - Variance of the feature - high variance - is high response
-\item Linearly dependent features are a waste of space and computation power because the information could have been encoded in much fewer features. \cite{zheng_feature_2018} - solve by PCA
-\end{itemize}
-
-Vibration levels are dependent on the type of work (load) of the machine (cite)
-\begin{itemize}
-\item \textbf{Sawing process database}: it contains basic information such as sawing machine tools model, band saw blade model, sawing parameters, and the material and size of the workpiece to match the relevant online monitoring model.
-\item \textbf{Online monitoring model database}: it stores online monitoring models of band saw blade wear based on different sawing processes.
-\end{itemize}
 
 \section{Diagnostics techniques}
-\url{https://scikit-learn.org/stable/modules/outlier_detection.html#outlier-detection}
+
 \subsection{Novelty detection}
-\textbf{Fault or no fault} - anomaly detection solutions - unsupervised \cite{torres_automatic_2022}. mean shift clustering algorithm
-\begin{itemize}
-\item Robust Covariance  (Mahalanobis distance)
-\item One-class SVM with non-linear kernel (RBF) - classifying new data as similar or different to the training set
-\item Local outlier factor - local density deviation of a given data point with respect to its neighbours
-\item Isolation forest
-\end{itemize}
-
-\textbf{Types of faults - clustering}
-\begin{itemize}
-\item BIRCH
-\item DBSCAN - density based params:
-	minPts (the minimum number of data points that need to be clustered together for an area to be considered high-density)
-	eps (the distance used to determine if a data point is in the same area as other data points).
-\item OPTICS - better DBSCAN -  clusters in data of varying density
-\end{itemize}
-
-\subsection{Label propagation in semi-supervised learning}
-
-Transductive Support vector machine(TSVM),
-Label Propagation Algorithm(LPA)
 
 \section{IoT in Industry 4.0}
-	Wireless protocols limitation: IEEE 802.11, IEEE 802.15.4e, OpenThread
-	Power consumption
-	Devices and sensors
-
-	The Fig.
-1 shows a generalist architecture supported in the context of Industry 4.0, fault detection systems in electrical machines based on vibration analysis  The Operational Technology (OT) and Information Technology (IT) parts were aligned to design an Industrial Control System (ICS) in the laboratory, for acquiring, controlling and monitoring the operating status of rotating machines, producing reports, automatic alerts and recommending actions to take as a prescriptive maintenance system.
-\cite{torres_automatic_2022}

### 2023-04-03 chapters/02-analysis.tex
Complete maximal version of analysis outline

@@
 \section{Condition monitoring}
+Why monitor with vibrations, Wear process curve, Fault - failure, Levels are dependant on load and lifecycle stage
 
 \subsection{Maintenance strategies}
+\paragraph{Reactive}
+\paragraph{Preventive}
+\paragraph{Predictive}
+- value for the factory and assess risks asociated with potencial fault to assign them importance
+
+\paragraph{Diagnosis indicators} - what we montitor? - when it fails and early signs of faulty component
+- RUL (Remaining useful life) models - disadvantage lot of similiar machines (homogenous) or lots of runns until failure
+\begin{itemize}
+\item Similarity
+\item Degradation - used by standards
+\item Survival
+\end{itemize}
 
 \subsection{Vibration fault types}
+- frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
+- Base analytical models: Jeffcott rotor - rotor dynamics, Bearnings model
+- Resonance frequencies of each part - machine must run at speeds not aligned with resonance frequencies - Campbell diagram - task for mechanical engineers
+- Faults - reasons and frequency content
+\begin{itemize}
+\item Synchrounous response - based on RPM
+\item Mass unbalance
+\item Misalignment
+\item Eccentricity
+\item Bent or bow shaft
+\item Cracked shaft
+\item Rotor rubs - friction
+\item Looseness
+\item Auxiliery mechanical systems: Gearbox, Bearings, Belt 
+\end{itemize}
 
 \subsection{Technical standards}
+\paragraph{ISO 20816}
+Part 1
+\begin{itemize}
+\item Measurement units - displacement, velocity, acceleration
+\item RMS, and max. amplitude = severity
+\item Measurement points for sensors (axial, radial) - image, and 45 degrees
+\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
+\item Opeartional limits - Alarm, Trips
+\end{itemize}
 
-\subsection{Sensor placement}
+\paragraph{ISO 13373}
+\begin{itemize}
+\item Sensor mount type in relation to sensor resonance
+\item Data presentation - standard display formats for analysis - trends, watefall plots ...
+\item Potencial causes for faults (p. 45) - use in vibration fault types
+\end{itemize}
 
 \section{Feature engineering}
+Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
+\subsection{Preprocessing}
+\begin{itemize}
+\item Detrending - DC removal filter
+\item Denoising 
+	\begin{itemize}
+	\item Gaussian smoothing filter 
+	\item Adaptive FIR filter with LMS algorithm
+	\item Wavelet thresholding with coif2 or db2
+	\end{itemize}
+\item Time synchronous averagings
+\end{itemize}
 
@@
 
-\subsection{Power spectral density segmentation}
+\paragraph{Statistical measures}
+\begin{itemize}
+\item Standard Deviation
+\item Max. amplitude
+\item RMS amplitude
+\item Skewness
+\item Kurtosis \\
+---
+\item Spectral centroid
+\item RMS frequency
+\item Root variance frequency
+\item Spectral kurtosis / Fast kurtogram
+\item Harmonic spectral deviation \\
+---
+\item Energy
+\item Spectral negentropy
+\item TKEO - Teager-Kaiser energy operator
+\end{itemize}
+
+\paragraph{Signal decompositions - sparse approximations}
+Matching pursuit algorithm optimalization problem
+\begin{itemize}
+\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
+\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
+\item EEMD - Ensemble Empirical Mode Decomposition - to IMF - mode mixing problem
+\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
+\item EWT - Empirical Wavelet Transform - (Meyer wavelet) 
+\end{itemize}
+
+\subsection{Feature transformation}
+\begin{itemize}
+\item Principal Component Analysis (PCA)
+\item Log transformation (Box-Cox Transform) to normal distribution
+\item Normalization (min-max, standardize) 
+\end{itemize}
 
 \subsection{Feature selection}
+Filter method - SelectKBest  in evaluation phase
+\begin{itemize}
+\item Variance Threshold
+\item Pearson correlation
+\item ANOVA F-value
+\item Mutal information
+\item Fisher score
+\item Spectral feature selection algorithm (SPEC)
+\end{itemize}
 
 \section{Diagnostics techniques}
+Idenification of faulty states in data streams in semi-supervised learning
+\subsection{Novelty detection}
+\begin{itemize}
+\item DenStream (Density based clustering - DBSCAN)
+\item Half-space Trees (Isolation forest)
+\end{itemize}
 
-\subsection{Novelty detection}
+\subsection{Classification}
+\begin{itemize}
+\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity
+\item Naive Bayes + Count-min sketch
+\item Label propagation (Temporal label propagation, LabelRankT) - RBF similarity
+\end{itemize}
 
-\section{IoT in Industry 4.0}
+\section{Evaluation Datasets}
+\paragraph{MAFAULDA}
+
+\paragraph{CWRU}
+
+\section{Sensor and microcontroller}

### 2023-04-03 jupyter/mat_convert.py

@@ -1,0 +1,14 @@
+import pandas as pd
+import scipy.io
+
+filename = "file"
+mat = scipy.io.loadmat(f'{filename}.mat')
+x = pd.DataFrame({
+    'rpm': mat['X097_RPM'],
+    'drive_end': mat['X097_DE_time'],
+    'fan_end': mat['X097_FE_time']
+})
+x.to_csv(f"{filename}.csv", index=False)
+
+
+

### 2023-04-03 jupyter/naive.py

@@ -1,0 +1,29 @@
+from skmultiflow.data import SEAGenerator
+from skmultiflow.bayes import NaiveBayes
+
+# Setup a data stream
+stream = SEAGenerator(random_state=1)
+
+# Setup Naive Bayes estimator
+naive_bayes = NaiveBayes()
+
+# Setup variables to control loop and track performance
+n_samples = 0
+correct_cnt = 0
+max_samples = 200
+
+# Train the estimator with the samples provided by the data stream
+
+while n_samples < max_samples and stream.has_more_samples():
+    X, y = stream.next_sample()
+    y_pred = naive_bayes.predict(X)
+
+    if y[0] == y_pred[0]:
+        correct_cnt += 1
+
+    naive_bayes.partial_fit(X, y)
+    n_samples += 1
+
+# Display results
+print('{} samples analyzed.'.format(n_samples))
+print('Naive Bayes accuracy: {}'.format(correct_cnt / n_samples))

### 2023-04-12 chapters/02-analysis.tex
Compare spectra of different faults in MAFAULDA

@@
 \item Detrending - DC removal filter
-\item Denoising 
-	\begin{itemize}
-	\item Gaussian smoothing filter 
-	\item Adaptive FIR filter with LMS algorithm
-	\item Wavelet thresholding with coif2 or db2
-	\end{itemize}
-\item Time synchronous averagings
+\item Time synchronous averaging
 \end{itemize}
@@
 \item Spectral kurtosis / Fast kurtogram
+\item Harmonics (peaks)
+\item Spectral Envelope
 \item Harmonic spectral deviation \\
@@
 \begin{itemize}
-\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
+\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging (cite BP)
 \item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
-\item EEMD - Ensemble Empirical Mode Decomposition - to IMF - mode mixing problem
 \item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
@@
 \begin{itemize}
+\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
 \item DenStream (Density based clustering - DBSCAN)
@@
 \begin{itemize}
-\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity
-\item Naive Bayes + Count-min sketch
-\item Label propagation (Temporal label propagation, LabelRankT) - RBF similarity
+\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity /  RBF similarity
 \end{itemize}
@@
 \section{Evaluation Datasets}
-\paragraph{MAFAULDA}
+(Pictures of machines)
+
+\paragraph{MAFAULDA}\\
+SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
+50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage
 
 \paragraph{CWRU}
+2 HP (1.492 kW) Reliance Electric motor
+Bearings - Inner, Outer
+12 kHz, 48 kHz
+fan and drive end bearings
+Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway. 
+Faulted bearings were reinstalled into the test motor and vibration data was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).
+
+\paragraph{Rotating Shaft}
+Shaft -  unbalances of different sizes
+4 kHz
 

### 2023-04-22 chapters/01-introduction.tex
Put literature citation to appropriate sections

@@
 \chapter{Introduction}
-\textbf{Following is very coarse draft!}
-Manufacturing is experiencing a shift in the traditional asset operational status evaluation and utilization.
-The goal is to promote safety and production efficiency when the useful life of machine moving parts is extended.
-In the factories and logistics where this sort of equipment is vital, there is a trend to be able to monitor the health of the machinery parts and above that to diagnose the fault in time to repair it without additional costs.
-Vibrations are the most nonintrusive way where such faults can be sensed and appear distinctly for an analyst to identify the root cause of the malfunction.
+Manufacturing is experiencing a shift in the traditional practices of asset operational status evaluation and utilization.
+The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
+The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear.
+The corrective action be it repair or replacement should be taken on time in response to the key indicators.
 
-In critical circumstances, such measurements are already in place in some form, but in order to reach wider acceptance, and not remain just a quirk/trend system has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.
+The goal is to preserve required safety and production efficiency when extending the useful life of machine moving parts.
+In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to monitor in real-time the health of the machines and to proactively diagnose the fault to repair it without adding unnecessary costs.
 
-The thesis is structured in a following manner.
-In Chapter 1 we explore the theoretical (analytical) model view, mechanical maintenance approaches, and industry standards where common fault identification is described.
-Chapter 2 is all about taking vibration measurements (procuring) and transforming them into features meaningful in automatic fault pattern recognition.
-The methods for ranking are reviewed to obtain the most important and correlated features with machine health status.
-We delve into modes of diagnosis based on reduced relevant indicators in chapter 3.
-Chapter 4 takes a look into IoT communication infrastructure limiting the data throughput and devices that can be deployed (accommodate) in the factory environment.
-Chapter 5 defines measurement vectors and proposes processing steps to diagnose the reoccurring failure, RUL (remaining useful life), and fault types.
-The approach taken is evaluated and deployed in Chapter 6.
+Vibrations are the most nonintrusive way with which such faults can be sensed.
+The experts use it to distinguish faulty states and to identify the malfunction's root cause.
+In critical circumstances such as in the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place.
+To reach wider acceptance and spread, the monitoring solution has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.
+
+The main issue to consider in large-scale machinery monitoring using vibrations are lots of uninformative streams of samples not directly useful for the production line operator.
+The dashboard must aggregate these flows into trend variables with severity levels categorized based on industrial standards.
+The majority of signals are viewed once at the maximum therefore to store or even transmit them from the edge device in its entirety would be wasteful.
+The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan on battery power and preferably remain physically small to reduce the additional clutter.
+
+Attempted machine and deep learning approaches have the crucial impediment that the construction of every single machine is unique to some extent because of tolerances and variable load.
+The model must be trained specifically for the target environment to achieve the ideal performance.
+In addition, the failures are relatively rare events occurring usually in the span of multiple months.
+In these circumstances, it is hard to obtain a large enough sample of fault events quickly.
+Novelty detection is a technique that can be applied in this case.
+
+The thesis is organized in the following manner.
+In the first chapter of analysis in section 1 we explore the mechanical maintenance approaches and industry standards on common fault identification.
+Then section 2 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition.
+In section 3 we delve into modes of diagnosis based on reduced relevant indicators.
+Section 4 deals with evaluation datasets used to determine computational requirements
+on IIoT infrastructure.
+Chapter 2 defines data format and proposes processing steps to diagnose the imminent failure and different fault types.
+The approach taken is evaluated and validated in Chapter 6.

### 2023-04-22 chapters/analysis/A-CdM.tex
Put literature citation to appropriate sections

--- 2023-03-30 chapters/02-analysis.tex
@@
-\chapter{Problem analysis}
-
 \section{Condition monitoring}
+Why monitor with vibrations, 
+Wear process curve, Fault - failure, Levels are dependant on load and lifecycle stage
 
 \subsection{Maintenance strategies}
+\paragraph{Reactive}
+\paragraph{Preventive}
+\paragraph{Predictive}
+- value for the factory and assess risks asociated with potencial fault to assign them importance
+
+% Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
+\cite{torres_automatic_2022}
+% Practical Machinery Vibration Analysis and Predictive Maintenance
+\cite{scheffer_practical_2004}
+% Machinery Condition Monitoring: Principles and Practices
+\cite{mohanty_machinery_2015}
+% Techniques for Vibration Monitoring
+\cite{davies_techniques_2012}
+% Technická diagnostika
+\cite{ziaran_technicka_2013}
+% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
+\cite{cakir_experimental_2021}
+% Vibration Guide
+\cite{noauthor_vibration_2000}
+
+% Bandsaws
+% Vibration of bandsaws
+\cite{lengoc_vibration_1990}
+% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
+\cite{chen_study_2014}
+
+\paragraph{Diagnosis indicators} - what we montitor? - when it fails and early signs of faulty component
+- RUL (Remaining useful life) models - disadvantage lot of similiar machines (homogenous) or lots of runns until failure
+\begin{itemize}
+\item Similarity
+\item Degradation - used by standards
+\item Survival
+\end{itemize}
 
 \subsection{Vibration fault types}
+- frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
+- Base analytical models: Jeffcott rotor - rotor dynamics, Bearnings model
+- Resonance frequencies of each part - machine must run at speeds not aligned with resonance frequencies - Campbell diagram - task for mechanical engineers
+- Faults - reasons and frequency content
+\begin{itemize}
+\item Synchrounous response - based on RPM
+\item Mass unbalance
+\item Misalignment
+\item Eccentricity
+\item Bent or bow shaft
+\item Cracked shaft
+\item Rotor rubs - friction
+\item Looseness
+\item Auxiliery mechanical systems: Gearbox, Bearings, Belt 
+\end{itemize}
 
 \subsection{Technical standards}
+\paragraph{ISO 20816}
+% ISO 20816-1:2016 - Mechanical vibration - Measurement and evaluation of machine vibration - Part 1: General guidelines
+\cite{noauthor_iso_2016}
+Part 1
+\begin{itemize}
+\item Measurement units - displacement, velocity, acceleration
+\item RMS, and max. amplitude = severity
+\item Measurement points for sensors (axial, radial) - image, and 45 degrees
+\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
+\item Opeartional limits - Alarm, Trips
+\end{itemize}
 
-\subsection{Sensor placement}
+\paragraph{ISO 13373}
+% ISO 13373-1:2002 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 1: General procedures
+\cite{noauthor_iso_2016}
+% ISO 13373-2:2016 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 2: Processing, analysis and presentation of vibration data
+\cite{noauthor_iso_2016-1}
 
-\section{Feature engineering}
-
-\subsection{Feature extraction}
-
-\subsection{Power spectral density segmentation}
-
-\subsection{Feature selection}
-
-\section{Diagnostics techniques}
-
-\subsection{Novelty detection}
-
-\section{IoT in Industry 4.0}
+\cite{jack_d_frequency_nodate}
+\begin{itemize}
+\item Sensor mount type in relation to sensor resonance
+\item Data presentation - standard display formats for analysis - trends, watefall plots ...
+\item Potencial causes for faults (p. 45) - use in vibration fault types
+\end{itemize}

### 2023-04-22 chapters/analysis/D-Datasets.tex
Put literature citation to appropriate sections

--- 2023-03-30 chapters/02-analysis.tex
@@
-\chapter{Problem analysis}
+\section{Evaluation Datasets}
+(Pictures of machines)
 
-\section{Condition monitoring}
+\paragraph{MAFAULDA}
+SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
+50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage
 
-\subsection{Maintenance strategies}
+\cite{noauthor_mafaulda_nodate}
 
-\subsection{Vibration fault types}
+\paragraph{CWRU}
+2 HP (1.492 kW) Reliance Electric motor
+Bearings - Inner, Outer
+12 kHz, 48 kHz
+fan and drive end bearings
+Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway. 
+Faulted bearings were reinstalled into the test motor and vibration data was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).
 
-\subsection{Technical standards}
+% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
+\cite{jamil_feature-based_2021}
+% Machine Learning-Based Unbalance Detection of a Rotating Shaft Using Vibration Data
+\cite{mey_machine_2020}
 
-\subsection{Sensor placement}
+\paragraph{Rotating Shaft}
+Shaft -  unbalances of different sizes
+4 kHz
 
-\section{Feature engineering}
-
-\subsection{Feature extraction}
-
-\subsection{Power spectral density segmentation}
-
-\subsection{Feature selection}
-
-\section{Diagnostics techniques}
-
-\subsection{Novelty detection}
-
-\section{IoT in Industry 4.0}
+\section{Sensor and microcontroller}
+% Intelligent Sensor Networks: The Integration of Sensor Networks, Signal Processing and Machine Learning
+\cite{hu_intelligent_2012}

### 2023-04-23 chapters/analysis/A-CdM.tex
Section about maintanance strategies

@@
 \section{Condition monitoring}
-Why monitor with vibrations, 
-Wear process curve, Fault - failure, Levels are dependant on load and lifecycle stage
+All rotating machinery eventually fail because of the long-term strain on the individual parts or incorrent workmanship, installation or operational procedures.
+In the end, these factors cause the equipment not to fulfill its intended functionality.
+Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, wear debris analysis, ultrasonic testing, etc.
+Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+
+The defect needs to be either repaired or replaced, preferably without significant production downtime, futher damage to the other attached elements or endangerment of the responsible personnel.
+The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
+The guide to set appropriate maintenance procedures is outlined by IEC 60706-2 standard and involves reliability-centered maintenance (RCM) analysis \cite{el-thalji_predictive_2019}.
 
 \subsection{Maintenance strategies}
-\paragraph{Reactive}
-\paragraph{Preventive}
-\paragraph{Predictive}
-- value for the factory and assess risks asociated with potencial fault to assign them importance
+There are three different approaches to maintenance across the industry: reactive, preventive, and predictive \cite{scheffer_practical_2004}.
+In general, the more sophisticated methods are beneficial in a high stakes environment.
+The unexpected machine shutdown can have negative economic impact on the enterprise, resulting in the decreased product quality and demands spare parts be ready in the supply inventory at all times.
+However, in certain situations suffice to utilize a simpler maintenance program, but predictive maintenance is gains interest in the Industry 4.0 to optimize usage of assets \cite{cinar_machine_2020}.
 
-% Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
-\cite{torres_automatic_2022}
-% Practical Machinery Vibration Analysis and Predictive Maintenance
-\cite{scheffer_practical_2004}
-% Machinery Condition Monitoring: Principles and Practices
-\cite{mohanty_machinery_2015}
-% Techniques for Vibration Monitoring
-\cite{davies_techniques_2012}
-% Technická diagnostika
-\cite{ziaran_technicka_2013}
-% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
-\cite{cakir_experimental_2021}
-% Vibration Guide
-\cite{noauthor_vibration_2000}
+\paragraph{Reactive maintenance} allows machinery to run to complete failure.
+This is the most inefficient way to maintain production line.
+It requires large stock of replacement parts on site and breakage constitutes a ,,crisis management mode'' in the plant \cite{scheffer_practical_2004}.
+On demand repairs are justified for consumer products or in the factory capable to fully and quickly replace halted machine with a backup.
 
-% Bandsaws
-% Vibration of bandsaws
-\cite{lengoc_vibration_1990}
-% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
-\cite{chen_study_2014}
+\paragraph{Preventive maintenance} is performed before any issue is detected.
+Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (e.g.
+MTTF - Mean Time To Failure).
+The schedule is crucial but can result in components being replaced in good condition when further utilization is possible or too late after the machine breaks.
+In this case, conservative planning is usually the norm which means more frequent intervention \cite{mohanty_machinery_2015}.
 
-\paragraph{Diagnosis indicators} - what we montitor? - when it fails and early signs of faulty component
+\paragraph{Predictive maintenance} known as condition-based (CbM), improves the predictibility of reactive maintanace and eliminates the waste in overall resource utilization of cautious prevention.
+The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring and troublesome components are identified.
+This allows to order necessary parts in advance and organize repairs of several machines at a convinient time.
+The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves.
+\cite{davies_handbook_2012}.
+
+\subsection{Diagnosis indicators}
+\begin{figure}[h]
+\centering
+\includegraphics[width=\textwidth]{assets/P-F-Curve.png}
+\caption{P-F curve \cite{jennions_integrated_2011}}
+\end{figure}
+
+- what we montitor? - when it fails and early signs of faulty component
+- P-F Curve  = Wear process curve (Bathtub curve), 
 - RUL (Remaining useful life) models - disadvantage lot of similiar machines (homogenous) or lots of runns until failure
+% Overview of Remaining Useful Life Prediction Techniques in Through-Life Engineering Services
+\cite{okoh_overview_2014}
 \begin{itemize}
-\item Similarity
-\item Degradation - used by standards
-\item Survival
+\item Survival (Analytical-Based)
+\item Similarity (Model-based)
+\item Degradation - used by standards (Knowledge-Based)
 \end{itemize}
@@
 \subsection{Vibration fault types}
+Why monitor with vibrations,
 - frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
@@
 - Faults - reasons and frequency content
+% Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
+\cite{torres_automatic_2022}
+% Vibration Guide
+\cite{noauthor_vibration_2000}
+% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
+\cite{cakir_experimental_2021}
+% Technická diagnostika
+\cite{ziaran_technicka_2013}
+
 \begin{itemize}
@@
 \end{itemize}
+
+% Bandsaws
+% Vibration of bandsaws
+\cite{lengoc_vibration_1990}
+% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
+\cite{chen_study_2014}
 

### 2023-04-23 chapters/analysis/A-CdM.tex
Remaining useful life estimation

--- 2023-04-22 chapters/analysis/A-CdM.tex
@@
 \section{Condition monitoring}
-Why monitor with vibrations, 
-Wear process curve, Fault - failure, Levels are dependant on load and lifecycle stage
+All rotating machinery eventually fails because of the long-term strain on the individual parts or incorrect workmanship, installation, or operational procedures.
+In the end, these factors cause the equipment not to fulfill its intended functionality.
+Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, oil and particle analysis, ultrasonic testing, etc.
+Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+
+The defect needs to be either repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or endangerment of the responsible personnel.
+The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
+The guide to set appropriate maintenance procedures is outlined by IEC 60706-2 standard and involves reliability-centered maintenance (RCM) analysis \cite{el-thalji_predictive_2019}.
 
 \subsection{Maintenance strategies}
-\paragraph{Reactive}
-\paragraph{Preventive}
-\paragraph{Predictive}
-- value for the factory and assess risks asociated with potencial fault to assign them importance
+There are three different approaches to maintenance across the industry: reactive, preventive, and predictive \cite{scheffer_practical_2004}.
+In general, the more sophisticated methods are beneficial in a high-stakes environment.
+The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands spare parts be ready in the supply inventory at all times.
+However, in certain situations suffice to utilize a simpler maintenance program, but predictive maintenance gains interest in the Industry 4.0 to optimize usage of assets \cite{cinar_machine_2020}.
 
+\paragraph{Reactive maintenance} allows machinery to run to complete failure.
+This is the most inefficient way to maintain the production line.
+It requires a large stock of replacement parts on-site and breakage constitutes a `crisis management mode' in the plant \cite{scheffer_practical_2004}.
+On-demand repairs are justified for consumer products or in the factory capable of fully and quickly replacing the halted machine with a backup.
+
+\paragraph{Preventive maintenance} is performed before any issue is detected.
+Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (e.g.
+MTTF - Mean Time To Failure).
+The schedule is crucial but can result in components being replaced in good condition when further utilization is possible or too late after the machine breaks.
+In this case, conservative planning is usually the norm to keep machine always in perferct state which means more frequent intervention.
+\cite{mohanty_machinery_2015}.
+
+\paragraph{Predictive maintenance} known as condition-based (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
+The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and troublesome components are identified.
+This allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
+The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves.
+\cite{davies_handbook_2012}.
+\\
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{assets/P-F-Curve.png}
+	\caption{P-F curve represets evolution of the asset's health \cite{jennions_integrated_2011}}
+	\label{fig:p-f-curve}
+\end{figure}
+
+The P-F curve is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
+Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval \cite{bousdekis_enterprise_2021}.
+These division points are not exactly set but have statistical distribution to them.
+
+The Remaining Useful Life (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, and based on the model of the `run-to-failure' logs and usage parameters \cite{okoh_overview_2014}.
+Predictive condition monitoring aims to extend the machine lifespan to the maximum by predicting expected RUL.
+
+The high failure rate is present not only when the part is worn out, but also in the early stages soon after assembly.
+Explanations range from inadequate installation to flimsily manufactured electrical or mechanical elements.
+The time plot to failure rate is known as the bath tub curve (Fig.~\ref{fig:bath-tub-curve}).
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.9\textwidth]{assets/bath-tub-curve.png}
+	\caption{Bath tub curve \cite{mohanty_machinery_2015}}
+	\label{fig:bath-tub-curve}
+\end{figure}
+
+%TODO
+\subsection{Vibration fault types}
+\cite{scheffer_practical_2004} p.98 - 141
+
+\cite{davies_handbook_2012} p.282
 % Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
 \cite{torres_automatic_2022}
-% Practical Machinery Vibration Analysis and Predictive Maintenance
-\cite{scheffer_practical_2004}
-% Machinery Condition Monitoring: Principles and Practices
-\cite{mohanty_machinery_2015}
-% Techniques for Vibration Monitoring
-\cite{davies_techniques_2012}
+% Vibration Guide
+\cite{noauthor_vibration_2000}
+% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
+\cite{cakir_experimental_2021}
 % Technická diagnostika
 \cite{ziaran_technicka_2013}
-% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
-\cite{cakir_experimental_2021}
-% Vibration Guide
-\cite{noauthor_vibration_2000}
 
-% Bandsaws
-% Vibration of bandsaws
-\cite{lengoc_vibration_1990}
-% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
-\cite{chen_study_2014}
-
-\paragraph{Diagnosis indicators} - what we montitor? - when it fails and early signs of faulty component
-- RUL (Remaining useful life) models - disadvantage lot of similiar machines (homogenous) or lots of runns until failure
-\begin{itemize}
-\item Similarity
-\item Degradation - used by standards
-\item Survival
-\end{itemize}
-
-\subsection{Vibration fault types}
+Why monitor with vibrations,
 - frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
@@
 - Faults - reasons and frequency content
+
 \begin{itemize}

### 2023-04-24 chapters/analysis/A-CdM.tex
Intro to ISO standards

@@
 
-The defect needs to be either repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or endangerment of the responsible personnel.
+The defect needs to be either repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or any endangerment of the responsible personnel.
 The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
@@
 The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands spare parts be ready in the supply inventory at all times.
-However, in certain situations suffice to utilize a simpler maintenance program, but predictive maintenance gains interest in the Industry 4.0 to optimize usage of assets \cite{cinar_machine_2020}.
+However, in certain situations suffice to utilize a simpler maintenance program, but predictive maintenance gains interest in the Industry 4.0 to optimize assets' usage  \cite{cinar_machine_2020}.
+\bigbreak
 
-\paragraph{Reactive maintenance} allows machinery to run to complete failure.
+\textbf{Reactive maintenance} allows machinery to run to complete failure.
 This is the most inefficient way to maintain the production line.
@@
 On-demand repairs are justified for consumer products or in the factory capable of fully and quickly replacing the halted machine with a backup.
+\bigbreak
 
-\paragraph{Preventive maintenance} is performed before any issue is detected.
+\textbf{Preventive maintenance} is performed before any issue is detected.
 Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (e.g.
@@
 The schedule is crucial but can result in components being replaced in good condition when further utilization is possible or too late after the machine breaks.
-In this case, conservative planning is usually the norm to keep machine always in perferct state which means more frequent intervention.
+In this case, conservative planning is usually the norm to keep machine always in perferct state and therefore more frequent intervention.
 \cite{mohanty_machinery_2015}.
+\bigbreak
 
-\paragraph{Predictive maintenance} known as condition-based (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
+\textbf{Predictive maintenance} known as condition-based maintanance (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
 The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and troublesome components are identified.
-This allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
-The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves.
-\cite{davies_handbook_2012}.
-\\
+
+Measurable decrease in efectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
+The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
+
+\bigbreak
 
@@
 The P-F curve is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
-Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval \cite{bousdekis_enterprise_2021}.
+Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval~\cite{bousdekis_enterprise_2021}.
 These division points are not exactly set but have statistical distribution to them.
 
-The Remaining Useful Life (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, and based on the model of the `run-to-failure' logs and usage parameters \cite{okoh_overview_2014}.
+The Remaining Useful Life (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, and based on the model of the `run-to-failure' histories and usage parameters~\cite{okoh_overview_2014}.
 Predictive condition monitoring aims to extend the machine lifespan to the maximum by predicting expected RUL.
-
-The high failure rate is present not only when the part is worn out, but also in the early stages soon after assembly.
-Explanations range from inadequate installation to flimsily manufactured electrical or mechanical elements.
-The time plot to failure rate is known as the bath tub curve (Fig.~\ref{fig:bath-tub-curve}).
 
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{assets/bath-tub-curve.png}
-	\caption{Bath tub curve \cite{mohanty_machinery_2015}}
+	\includegraphics[width=0.8\textwidth]{assets/bath-tub-curve.png}
+	\caption{Bath tub curve~\cite{mohanty_machinery_2015}}
 	\label{fig:bath-tub-curve}
@@
 
-%TODO
+High failure rate is present not only at the worn out stage when the parts are fatigued or corroded, but also in the early stages soon after assembly.
+Causes can be found in the manufacturing or material defects, inadequate installation, or improper start-up procedures.
+The time plot to failure rate is known as the bath tub curve (Fig.~\ref{fig:bath-tub-curve}).
+
 \subsection{Vibration fault types}
+Mechanical problems during machinery operation bring about vibrations in the vast majority of cases.
+The cause of vibration comes out of the changing force in its magnitude or direction.
+The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure broadly categorized as \textbf{unbalance, misalignment, looseness, excentricity, and influence of the external force}~\cite{davies_handbook_2012}.
+
+However, rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum.
+Imbalance, misalignment, and looseness normally appear at frequencies up to 300 Hz.
+These low-frequency faults are associated with the movement of the shaft and primarily coincide with revolution speed and its harmonics.
+Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz.
+Higher frequencies measured traditionally to a limit of 10 kHz help notice the flaw of bearings even sooner~\cite{torres_automatic_2022}.
+
+\begin{itemize}
+\item predominant frequency
+\item synchronous frequency
+\item subsynchronous frequency
+\item fundamental frequency
+\item harmonic frequency
+\item subharmonic frequency
+\end{itemize}
+% p.294 Davies
+
 \cite{scheffer_practical_2004} p.98 - 141
@@
 Why monitor with vibrations,
-- frequency ranges 1 - 300 Hz (shaft), 300 - 1000 Hz, 1000 - 10000 Hz (early bearings)
-- Base analytical models: Jeffcott rotor - rotor dynamics, Bearnings model
 - Resonance frequencies of each part - machine must run at speeds not aligned with resonance frequencies - Campbell diagram - task for mechanical engineers
@@
 
+% Describe by frequency responses and assign them possibale faults instead
+
 \begin{itemize}
+\itemsep0pt
 \item Synchrounous response - based on RPM
@@
 \subsection{Technical standards}
-\paragraph{ISO 20816}
-% ISO 20816-1:2016 - Mechanical vibration - Measurement and evaluation of machine vibration - Part 1: General guidelines
-\cite{noauthor_iso_2016}
-Part 1
+Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards.
+The standards are concerned with each step in the process that originates with transducer placements and data acquisition.
+They prescribe conventions for setting fault severity levels and provide empirically observed vibration characteristics of common defects.
+Two relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
+\bigbreak
+
+\textbf{ISO 20816-1:2016} establishes the approach to vibration measurement and evaluation on non-rotating housing of machinery parts~\cite{noauthor_iso_2016}.
+The measurement units are agreed upon for kinematic quantities of vibrations.
+Acceleration is to be measured in meters per second squared ($m/s^2$), velocity in millimeters per second ($mm/s$), and displacement in micrometers ($\mu m$).
+It is customary to evaluate broad-band vibration velocity in terms of root mean square value (RMS), as it has relation to its signal energy~(Tab.~\ref{tab:iso20816-vibration-severity}).
+No simple direct relationship is expressible among these quantities, except in stationary signals.
+
+The vibration severity is the maximum magnitude value measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft in the axial axis.
+Multiple measurement locations, i.e.
+on several bearings or couplings, should be assessed independently.
+
 \begin{itemize}
-\item Measurement units - displacement, velocity, acceleration
-\item RMS, and max. amplitude = severity
-\item Measurement points for sensors (axial, radial) - image, and 45 degrees
-\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model
-\item Opeartional limits - Alarm, Trips
+\item Severity Criteria: vibration magnitude, change in vibration magnitude, the rate of change in vibrations)
+\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model - p.11 (maximum in all directions is severity, assess locations separately
+\item Operational limits - Alarm, Trips - p.13
 \end{itemize}
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Vibration velocity\\ RMS {[}mm/s{]}\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class I\\ Small machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class II\\ Medium machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class III\\ Large machines\\ Rigid supports\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class IV\\ Large machines\\ Flexible support\end{tabular}} \\ \hline
+0.28                                                                                 & \cellcolor[HTML]{9AFF99}                                                  & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1}
+0.45                                                                                 & \cellcolor[HTML]{9AFF99}                                                  & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1}
+0.71                                                                                 & \multirow{-3}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}               & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-2}
+1.12                                                                                 & \cellcolor[HTML]{FFFC9E}                                                  & \multirow{-4}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                 & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1} \cline{3-3}
+1.8                                                                                  & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}       & \cellcolor[HTML]{FFFC9E}                                                    & \multirow{-5}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                                  & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-2} \cline{4-4}
+2.8                                                                                  & \cellcolor[HTML]{F8A102}                                                  & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}         & \cellcolor[HTML]{FFFC9E}                                                                     & \multirow{-6}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                                   \\ \cline{1-1} \cline{3-3} \cline{5-5}
+4.5                                                                                  & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}     & \cellcolor[HTML]{F8A102}                                                    & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}                          & \cellcolor[HTML]{FFFC9E}                                                                      \\ \cline{1-2} \cline{4-4}
+7.1                                                                                  & \cellcolor[HTML]{FD6864}                                                  & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}       & \cellcolor[HTML]{F8A102}                                                                     & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}                           \\ \cline{1-1} \cline{3-3} \cline{5-5}
+11.2                                                                                 & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}                        & \cellcolor[HTML]{F8A102}                                                                      \\ \cline{1-1} \cline{4-4}
+18                                                                                   & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \cellcolor[HTML]{FD6864}                                                                     & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}                         \\ \cline{1-1} \cline{5-5}
+28                                                                                   & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \cellcolor[HTML]{FD6864}                                                                     & \cellcolor[HTML]{FD6864}                                                                      \\ \cline{1-1}
+45                                                                                   & \multirow{-5}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}       & \multirow{-4}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}         & \multirow{-3}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}                          & \multirow{-2}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}                           \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{ISO 20816 vibration serverity chart \cite{noauthor_iso_2016}}
+\label{tab:iso20816-vibration-severity}
+\end{table}
 
@@
 % ISO 13373-1:2002 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 1: General procedures
-\cite{noauthor_iso_2016}
-% ISO 13373-2:2016 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 2: Processing, analysis and presentation of vibration data
-\cite{noauthor_iso_2016-1}
+\cite{noauthor_iso_2002}
 
-\cite{jack_d_frequency_nodate}
 \begin{itemize}
-\item Sensor mount type in relation to sensor resonance
-\item Data presentation - standard display formats for analysis - trends, watefall plots ...
+\itemsep0pt
+\item Data collection - Continuos, Periodic (scanning) p.9 
+\item Monitoring programme p.12 (vibrations differ under load)
+\item Frequency range and measurement accuracy - p.20 -0.2 times of lowest rotational frequency to 3.5 highest excitation frequency (below 10 kHz) and resonance
+\item Acceleration transducer - integrate once to get velocity p.24 (0.1 - 30 kHz)
+\item Sensor mount type in relation to sensor resonance p.26 
 \item Potencial causes for faults (p. 45) - use in vibration fault types
+\item What to record about machines p.43
+\item MIMOSA code convention - location, transducer type, orientation p.49
 \end{itemize}
+
+\begin{enumerate}
+\itemsep0pt
+\item Review machinery history and establish failure modes.
+\item When vibration monitoring is not applicable check for other condition monitoring techniques or use preventive maintance routine.
+\item Select monitoring points
+\item Take preliminary vibration measurements
+\item Select vibration monitoring techniques: broadband, frequency analysis or special techniques. Set parameters of measurements units.
+\item Take baseline measurements
+\item Change levels that would warrant investigation
+\item Carry out routine condition monitoring
+\item If alarm was exceeded notify approriate personnel, review data and trends, perform diagnostic evaluation, repair as necessary.
+In case new baseline is needed continue in step of taking baseline measurements.
+\item Shut down machine when trip level is exceeded. Than proceed same as after alarm trigger.
+\end{enumerate}
+
+\newpage

### 2023-04-24 chapters/analysis/A-CdM.tex
Finish ISO 20186

@@
 \textbf{Reactive maintenance} allows machinery to run to complete failure.
-This is the most inefficient way to maintain the production line.
-It requires a large stock of replacement parts on-site and breakage constitutes a `crisis management mode' in the plant \cite{scheffer_practical_2004}.
+This is the most inappropriate way to maintain the production line, but it is straightforward.
+It requires a large stock of replacement parts on-site and breakage inflict a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
 On-demand repairs are justified for consumer products or in the factory capable of fully and quickly replacing the halted machine with a backup.
@@
 Causes can be found in the manufacturing or material defects, inadequate installation, or improper start-up procedures.
+During the stable middle phase the malfunction can occur after machine excessive overload.
 The time plot to failure rate is known as the bath tub curve (Fig.~\ref{fig:bath-tub-curve}).
@@
 
+%TODO
 Why monitor with vibrations,
@@
 Acceleration is to be measured in meters per second squared ($m/s^2$), velocity in millimeters per second ($mm/s$), and displacement in micrometers ($\mu m$).
-It is customary to evaluate broad-band vibration velocity in terms of root mean square value (RMS), as it has relation to its signal energy~(Tab.~\ref{tab:iso20816-vibration-severity}).
+It is customary to evaluate broad-band vibration velocity in terms of root mean square value (RMS), as it has a relation to its signal energy.
 No simple direct relationship is expressible among these quantities, except in stationary signals.
@@
 
-\begin{itemize}
-\item Severity Criteria: vibration magnitude, change in vibration magnitude, the rate of change in vibrations)
-\item Evaluation zones - A, B, C, D - Severity chart (Annex B) - Degradation model - p.11 (maximum in all directions is severity, assess locations separately
-\item Operational limits - Alarm, Trips - p.13
-\end{itemize}
+Criteria introduced to judge vibration severity are its absolute vibration magnitude, change in the magnitude vector, and rate of change.
+In terms of maximal magnitudes the machines of varied sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
+The table values serve as guidelines towards realistic requirements between machinemanufacturers and customers.
 
@@
 
+\emph{Zone A} is reserved for newly commissioned machines.
+\emph{Zone B} signifies suitability for long-term operation.
+In \emph{zone C} is the machine deemed in unsatisfactory condition and corrective action should be taken soon.
+Finally, in zone D vibrations can cause damage to the machine.
+The span of acceptable values differs on machine class from I through to IV with an output power of 15 kW (class I), 75 kW (class II), 10 MW (class III), or greater.
+
+The operational limits in the form of \emph{alarms} and \emph{trips} are usually established on the zone boundaries or close to them.
+Alarms are placed between zones B and C and provide a warning about reaching the threshold significant for noticeable change.
+Trips in between zones C and D urge immediate action or machine shut down.
+
+%TODO
 \paragraph{ISO 13373}

### 2023-04-25 chapters/analysis/A-CdM.tex
ISO 13373 main content describe

@@
 
-%TODO
-\paragraph{ISO 13373}
-% ISO 13373-1:2002 - Condition monitoring and diagnostics of machines - Vibration condition monitoring - Part 1: General procedures
-\cite{noauthor_iso_2002}
+\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in the vocabulary of ISO 20186.
+According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or intervals.
+Both designs can be permanently mounted, but in continuous, collection `multiplexing rate is sufficiently rapid so there is no significant data or trends lost'~\cite{noauthor_iso_2002}.
+When channels are scanned successively with gaps between data points the system is known as `scanning'.
 
-\begin{itemize}
-\itemsep0pt
-\item Data collection - Continuos, Periodic (scanning) p.9 
-\item Monitoring programme p.12 (vibrations differ under load)
-\item Frequency range and measurement accuracy - p.20 -0.2 times of lowest rotational frequency to 3.5 highest excitation frequency (below 10 kHz) and resonance
-\item Acceleration transducer - integrate once to get velocity p.24 (0.1 - 30 kHz)
-\item Sensor mount type in relation to sensor resonance p.26 
-\item Potencial causes for faults (p. 45) - use in vibration fault types
-\item What to record about machines p.43
-\item MIMOSA code convention - location, transducer type, orientation p.49
-\end{itemize}
+Measurement of vibrations should be accompanied by a description of the machine and its operating conditions.
+The machine description includes the machine identifier and its type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
+Measurement parameters such as timestamp, transducer type, sensor location and orientation in MIMOSA code, measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.) are to be recorded alongside the measurement value itself~\cite{noauthor_iso_2002}.
+
+The transducer of choice for condition monitoring is the accelerometer which can provide the acceleration value of the body and velocity after signal integration.
+However, standard cautions against double integrating for displacement.
+The recommended frequency range for an accelerometer is 0.1 Hz to 30 kHz.
+The choice of transducer mount significantly lowers its resonance frequency which is least influenced by stud mount and stiff cement mount.
+The resonance is reduced to around 8 kHz with the use of soft epoxy or permanent magnet.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.8\textwidth]{assets/transducer-response.png}
+	\caption{The transducer linear response and resonance in tolerance intervals~\cite{noauthor_iso_2002}}
+	\label{fig:tranducer-response}
+\end{figure}
+
+Broadband measurement requires `frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest' \cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100 mm/s.
+Bearings and gears diagnosis may push the upper-frequency limit even higher.
+The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$ (Fig.~\ref{fig:tranducer-response}).
+
+% Different under load 
+% Baseline measurement - what are those p.28
+% Monitoring programme p.12 (vibrations differ under load)
+% Later: Potencial causes for faults (p. 45) - use in vibration fault types
 

### 2023-04-27 chapters/analysis/A-CdM.tex
Condition monitoring complete before proofreading

@@
 The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
-The guide to set appropriate maintenance procedures is outlined by IEC 60706-2 standard and involves reliability-centered maintenance (RCM) analysis \cite{el-thalji_predictive_2019}.
+The guide to set appropriate maintenance procedures is outlined by the IEC~60706-2 standard and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
 
@@
 This is the most inappropriate way to maintain the production line, but it is straightforward.
-It requires a large stock of replacement parts on-site and breakage inflict a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
-On-demand repairs are justified for consumer products or in the factory capable of fully and quickly replacing the halted machine with a backup.
+It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
+On-demand repairs are justified if short downtime is an acceptable,  full, and quick replacement of a broken machine with a backup is possible or there is no threat of failure to the surrounding environment~\cite{ziaran_technicka_2013}.
 \bigbreak
@@
 The schedule is crucial but can result in components being replaced in good condition when further utilization is possible or too late after the machine breaks.
-In this case, conservative planning is usually the norm to keep machine always in perferct state and therefore more frequent intervention.
+In this case, conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent intervention.
 \cite{mohanty_machinery_2015}.
@@
 
-\textbf{Predictive maintenance} known as condition-based maintanance (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
+\textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
 The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and troublesome components are identified.
 
-Measurable decrease in efectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
+A measurable decrease in effectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
 The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
-
 \bigbreak
@@
 	\includegraphics[width=\textwidth]{assets/P-F-Curve.png}
-	\caption{P-F curve represets evolution of the asset's health \cite{jennions_integrated_2011}}
+	\caption{P-F curve represents the evolution of the asset's health \cite{jennions_integrated_2011}}
 	\label{fig:p-f-curve}
@@
 
-High failure rate is present not only at the worn out stage when the parts are fatigued or corroded, but also in the early stages soon after assembly.
-Causes can be found in the manufacturing or material defects, inadequate installation, or improper start-up procedures.
-During the stable middle phase the malfunction can occur after machine excessive overload.
-The time plot to failure rate is known as the bath tub curve (Fig.~\ref{fig:bath-tub-curve}).
+A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded but also in the early stages soon after assembly.
+Causes can be found in manufacturing or material defects, inadequate installation, or improper start-up procedures.
+During the stable middle phase, malfunction can occur after the machine's excessive overload.
+The time plot to failure rate is known as the bath tub curve~(Fig.~\ref{fig:bath-tub-curve}).
 
@@
 Mechanical problems during machinery operation bring about vibrations in the vast majority of cases.
+Therefore vibroacoustic diagnostics is considered one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
+
 The cause of vibration comes out of the changing force in its magnitude or direction.
-The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure broadly categorized as \textbf{unbalance, misalignment, looseness, excentricity, and influence of the external force}~\cite{davies_handbook_2012}.
+The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure broadly categorized as \textbf{unbalance, misalignment, looseness, excentricity, deformation, crack and influence of the external force} (e.g.
+friction) ~\cite{davies_handbook_2012}.
+It is important to stress that our concern are not the underlying deficiencies in mechanical parts, but the correct fault classification based on the signal waveform.
 
-However, rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum.
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{assets/complex-vibrations.png}
+	\caption{Complex machinery vibrations~\cite{davies_handbook_2012}}
+	\label{fig:machinery-vibrations}
+\end{figure}
+
+Rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase.
+Most of the occurring faults can be tied to the main rotational speed of the component under investigation (Fig.~\ref{fig:machinery-vibrations})~\cite{davies_handbook_2012}.
 Imbalance, misalignment, and looseness normally appear at frequencies up to 300 Hz.
@@
 Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz.
-Higher frequencies measured traditionally to a limit of 10 kHz help notice the flaw of bearings even sooner~\cite{torres_automatic_2022}.
+Higher frequencies measured traditionally to a limit of 10 kHz help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.
 
-\begin{itemize}
-\item predominant frequency
-\item synchronous frequency
-\item subsynchronous frequency
-\item fundamental frequency
-\item harmonic frequency
-\item subharmonic frequency
-\end{itemize}
-% p.294 Davies
+One of the methods vibration experts utilize in the identification of the damaged part from the frequency spectrum is \textbf{order analysis}.
+In essence, it is about noticing the excessive peaks at harmonic frequencies that are integer multiples of fundamental frequency (1x RPM)~(Tab.~\ref{tab:vibration-causes}):
 
-\cite{scheffer_practical_2004} p.98 - 141
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|ll|l|l|}
+\hline
+\multicolumn{2}{|l|}{\textbf{Frequency content}}                            & \textbf{Common case}                                                                                                     & \textbf{Other causes}                                                                                                                          \\ \hline
+\multicolumn{1}{|l|}{\multirow{4}{*}{Synchronous}} & 1 x RPM                & Imbalance                                                                                                                & \begin{tabular}[c]{@{}l@{}}Eccentric journals\\ Bent shaft / Misalignment\\    (high axial vibration)\\ Bad belt (if RPM of belt)\end{tabular} \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 2 x RPM                & Looseness                                                                                                                & \begin{tabular}[c]{@{}l@{}}Misalignment \\    (high axial vibration)\\ Cracked rotor\\ Bad belt (if RPM of belt)\end{tabular}                  \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 3 x RPM                & Misalignment                                                                                                             & and axial looseness                                                                                                                             \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & Many x RPM             & \begin{tabular}[c]{@{}l@{}}Bad gears\\ Severe looseness\end{tabular}                                                     & \begin{tabular}[c]{@{}l@{}}Gear teeth x RPM\\ Fan blade count x RPM\end{tabular}                                                               \\ \hline
+\multicolumn{1}{|l|}{Subsynchrous}                 & \textless 1 x RPM      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
+\multicolumn{1}{|l|}{Non-synchronous}              & \multicolumn{1}{c|}{-} & \begin{tabular}[c]{@{}l@{}}Electrical problems (x 50 Hz)\\ Reciprocating forces\\ Aerodynamic forces \\ Bad antifriction bearings\end{tabular} & Rubbing \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Expert observed likely vibration causes (based on~\cite{davies_handbook_2012,ziaran_technicka_2013,noauthor_iso_2002})}
+\label{tab:vibration-causes}
+\end{table}
 
-\cite{davies_handbook_2012} p.282
-% Automatic Anomaly Detection in Vibration Analysis Based on Machine Learning Algorithms
-\cite{torres_automatic_2022}
-% Vibration Guide
-\cite{noauthor_vibration_2000}
-% The experimental application of popular machine learning algorithms on predictive maintenance and the design of IIoT based condition monitoring system
-\cite{cakir_experimental_2021}
-% Technická diagnostika
-\cite{ziaran_technicka_2013}
-
-%TODO
-Why monitor with vibrations,
-- Resonance frequencies of each part - machine must run at speeds not aligned with resonance frequencies - Campbell diagram - task for mechanical engineers
-- Faults - reasons and frequency content
-
-% Describe by frequency responses and assign them possibale faults instead
-
-\begin{itemize}
-\itemsep0pt
-\item Synchrounous response - based on RPM
-\item Mass unbalance
-\item Misalignment
-\item Eccentricity
-\item Bent or bow shaft
-\item Cracked shaft
-\item Rotor rubs - friction
-\item Looseness
-\item Auxiliery mechanical systems: Gearbox, Bearings, Belt 
-\end{itemize}
-
-% Bandsaws
-% Vibration of bandsaws
-\cite{lengoc_vibration_1990}
-% Study on Online Detection and Fault Diagnosis of Band Saw Equipment
-\cite{chen_study_2014}
+Because of inherent tolerances in machine manufacturing and assembly, the rotational frequency always manifests itself, even in baseline signature~\cite{davies_handbook_2012, noauthor_iso_2002}.
+In the most likely scenario, some faults appear as compared to rotational frequency solely in\textbf{synchronous, subsynchronous, or non-synchronous components}.
+The defects can occur also in a predictable combination of the ones mentioned.
+Other common patterns experts look for are modulation sidebands typical for bearings and gears extractable with cepstrum analysis~\cite{ziaran_technicka_2013}.
+Therefore procedure relying on elimination narrows down unrelated causes effectively.
 
@@
 In terms of maximal magnitudes the machines of varied sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
-The table values serve as guidelines towards realistic requirements between machinemanufacturers and customers.
+The table values serve as guidelines towards realistic requirements between machine manufacturers and customers.
 
@@
 \end{adjustbox}
-\caption{ISO 20816 vibration serverity chart \cite{noauthor_iso_2016}}
+\caption{ISO 20816 vibration severity chart with typical magnitudes \cite{noauthor_iso_2016}}
 \label{tab:iso20816-vibration-severity}
@@
 Finally, in zone D vibrations can cause damage to the machine.
-The span of acceptable values differs on machine class from I through to IV with an output power of 15 kW (class I), 75 kW (class II), 10 MW (class III), or greater.
+The span of acceptable values differs on machine class from I through to IV with an output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.
 
@@
 Trips in between zones C and D urge immediate action or machine shut down.
+Both limits should not exceed 1.25 times the upper boundary or lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
 
@@
 When channels are scanned successively with gaps between data points the system is known as `scanning'.
+
+The condition monitoring programme is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant.
+Those steps can be summarized as follows ~\cite{noauthor_iso_2002}:
+\begin{enumerate}
+\itemsep0pt
+\item Review machinery history and establish failure modes.
+\item When vibration monitoring is not applicable check for other condition monitoring techniques or resort to preventive maintenance.
+\item Select monitoring points and take preliminary vibration measurements
+\item Select vibration monitoring techniques: broadband, frequency analysis, or special techniques, and set parameters of measurement units.
+\item Take baseline measurements.
+\item Change levels that would warrant investigation.
+\item Carry out routine condition monitoring.
+\item If an alarm was exceeded, notify appropriate personnel to review data and trends, perform diagnostic evaluation, and repair as necessary.
+In case a new baseline is needed continue in the step of taking baseline measurements.
+\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm trigger.
+\end{enumerate}
 
@@
 However, standard cautions against double integrating for displacement.
-The recommended frequency range for an accelerometer is 0.1 Hz to 30 kHz.
+The recommended frequency range for an accelerometer is 0.1~Hz to 30~kHz.
 The choice of transducer mount significantly lowers its resonance frequency which is least influenced by stud mount and stiff cement mount.
-The resonance is reduced to around 8 kHz with the use of soft epoxy or permanent magnet.
+The resonance is reduced to around 8~kHz with the use of soft epoxy or permanent magnet.
 
@@
 
-Broadband measurement requires `frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest' \cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100 mm/s.
+Broadband measurement requires `frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest'~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s.
 Bearings and gears diagnosis may push the upper-frequency limit even higher.
-The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$ (Fig.~\ref{fig:tranducer-response}).
+The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$~(Fig.~\ref{fig:tranducer-response}).
 
-% Different under load 
-% Baseline measurement - what are those p.28
-% Monitoring programme p.12 (vibrations differ under load)
-% Later: Potencial causes for faults (p. 45) - use in vibration fault types
+Equipment's `health' can be mischaracterized when there are significant differences in the machine's normal operating conditions.
+Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation.
+According to bath tub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period.
+The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.
 
-\begin{enumerate}
-\itemsep0pt
-\item Review machinery history and establish failure modes.
-\item When vibration monitoring is not applicable check for other condition monitoring techniques or use preventive maintance routine.
-\item Select monitoring points
-\item Take preliminary vibration measurements
-\item Select vibration monitoring techniques: broadband, frequency analysis or special techniques. Set parameters of measurements units.
-\item Take baseline measurements
-\item Change levels that would warrant investigation
-\item Carry out routine condition monitoring
-\item If alarm was exceeded notify approriate personnel, review data and trends, perform diagnostic evaluation, repair as necessary.
-In case new baseline is needed continue in step of taking baseline measurements.
-\item Shut down machine when trip level is exceeded. Than proceed same as after alarm trigger.
-\end{enumerate}
-
-\newpage
+The vibration baseline is defined by broad-band magnitudes and phases of motion vectors, waveforms in time and frequency domain, the rotational speed of the machine as well as its frequency response to different speeds during start-up and coast-down captured in the Bode plot and waterfall plot.
+Changes during the machine operation are then depicted in value trends.
+Trends can be shown of overall amplitudes or limited to frequency bands.

### 2023-04-28 thesis/chapters/01-introduction.tex
Reorganize chapter files and take notes about datasets

--- 2023-04-22 chapters/01-introduction.tex
@@
 
-The goal is to preserve required safety and production efficiency when extending the useful life of machine moving parts.
-In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to monitor in real-time the health of the machines and to proactively diagnose the fault to repair it without adding unnecessary costs.
+The goal is to preserve required safety and production efficiency while extending the useful life of mechanical rotating parts.
+In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to watch in real time the machine's health status.
+Proactive fault diagnosis is imperative to initiate a repair without adding unnecessary costs.
 
-Vibrations are the most nonintrusive way with which such faults can be sensed.
-The experts use it to distinguish faulty states and to identify the malfunction's root cause.
-In critical circumstances such as in the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place.
-To reach wider acceptance and spread, the monitoring solution has to be sufficiently independent, reliable, and as self-sufficient as the model design allows it to be.
+Vibrations are the most non-intrusive way to sense and record eventually fatal deficiencies right at the onset.
+The experts use it to distinguish faulty states and to identify the malfunction's root causes.
+In critical circumstances such as is the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place.
+The monitoring solution has to be sufficiently independent, reliable, and as self-sufficient as per model performance to reach wider acceptance and spread.
 
-The main issue to consider in large-scale machinery monitoring using vibrations are lots of uninformative streams of samples not directly useful for the production line operator.
+The main issue to consider in large-scale machinery monitoring with vibrations is that there are lots of uninformative streams of samples not directly useful for the production line operator.
 The dashboard must aggregate these flows into trend variables with severity levels categorized based on industrial standards.
 The majority of signals are viewed once at the maximum therefore to store or even transmit them from the edge device in its entirety would be wasteful.
-The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan on battery power and preferably remain physically small to reduce the additional clutter.
+The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan on battery power.
+Preferably they should also remain physically small to reduce the additional clutter.
 
@@
 The model must be trained specifically for the target environment to achieve the ideal performance.
-In addition, the failures are relatively rare events occurring usually in the span of multiple months.
-In these circumstances, it is hard to obtain a large enough sample of fault events quickly.
+In addition, the failures are relatively rare events that usually occur several months apart.
+In these circumstances, it is hard to obtain a large enough sample of fault events fast.
 Novelty detection is a technique that can be applied in this case.
 
-The thesis is organized in the following manner.
-In the first chapter of analysis in section 1 we explore the mechanical maintenance approaches and industry standards on common fault identification.
+This interim report to master's thesis is organized in the following manner.
+In the first chapter of problem analysis we explore the mechanical maintenance approaches and industry standards on common fault identification.
 Then section 2 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition.
 In section 3 we delve into modes of diagnosis based on reduced relevant indicators.
-Section 4 deals with evaluation datasets used to determine computational requirements
-on IIoT infrastructure.
+Section 4 deals with evaluation datasets used to determine computational requirements on IIoT infrastructure.
 Chapter 2 defines data format and proposes processing steps to diagnose the imminent failure and different fault types.
-The approach taken is evaluated and validated in Chapter 6.

### 2023-04-28 thesis/chapters/02-analysis-A-CdM.tex
Reorganize chapter files and take notes about datasets

--- 2023-04-27 chapters/analysis/A-CdM.tex
@@
 \section{Condition monitoring}
-All rotating machinery eventually fails because of the long-term strain on the individual parts or incorrect workmanship, installation, or operational procedures.
+All rotating machinery eventually fails because of the long-term strain on the individual parts, incorrect workmanship, installation, or operational procedures.
 In the end, these factors cause the equipment not to fulfill its intended functionality.
 Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, oil and particle analysis, ultrasonic testing, etc.
-Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+However, vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
 
@@
 The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
-The guide to set appropriate maintenance procedures is outlined by the IEC~60706-2 standard and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
+The guide to set appropriate maintenance procedures is outlined in the IEC~60706-2 standard and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
 
 \subsection{Maintenance strategies}
-There are three different approaches to maintenance across the industry: reactive, preventive, and predictive \cite{scheffer_practical_2004}.
+There are three different approaches to maintenance across the industry: \textbf{reactive, preventive, and predictive}~\cite{scheffer_practical_2004}.
 In general, the more sophisticated methods are beneficial in a high-stakes environment.
-The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands spare parts be ready in the supply inventory at all times.
-However, in certain situations suffice to utilize a simpler maintenance program, but predictive maintenance gains interest in the Industry 4.0 to optimize assets' usage  \cite{cinar_machine_2020}.
+The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands spare parts to be ready in the supply inventory at all times.
+In certain situations it suffice to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize assets' usage~\cite{cinar_machine_2020}.
 \bigbreak
 
-\textbf{Reactive maintenance} allows machinery to run to complete failure.
+\textbf{Reactive maintenance} allows machinery to run until a complete failure.
 This is the most inappropriate way to maintain the production line, but it is straightforward.
 It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
-On-demand repairs are justified if short downtime is an acceptable,  full, and quick replacement of a broken machine with a backup is possible or there is no threat of failure to the surrounding environment~\cite{ziaran_technicka_2013}.
+On-demand repairs are justified if short downtime is acceptable full and swift replacement of a broken machine with a backup is possible or there is no threat of failure to the surrounding environment~\cite{ziaran_technicka_2013}.
 \bigbreak
@@
 MTTF - Mean Time To Failure).
-The schedule is crucial but can result in components being replaced in good condition when further utilization is possible or too late after the machine breaks.
-In this case, conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent intervention.
+The schedule is crucial but can result in components being replaced in good condition creating waste or occasionally too late after the machine breaks.
+In this case conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent intervention.
 \cite{mohanty_machinery_2015}.
@@
 The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure broadly categorized as \textbf{unbalance, misalignment, looseness, excentricity, deformation, crack and influence of the external force} (e.g.
-friction) ~\cite{davies_handbook_2012}.
+friction)~\cite{davies_handbook_2012}.
 It is important to stress that our concern are not the underlying deficiencies in mechanical parts, but the correct fault classification based on the signal waveform.
@@
 \hline
-\multicolumn{2}{|l|}{\textbf{Frequency content}}                            & \textbf{Common case}                                                                                                     & \textbf{Other causes}                                                                                                                          \\ \hline
+\multicolumn{2}{|l|}{\textbf{Frequency content}}                            & \textbf{Likely reason}                                                                                                     & \textbf{Other causes}                                                                                                                          \\ \hline
 \multicolumn{1}{|l|}{\multirow{4}{*}{Synchronous}} & 1 x RPM                & Imbalance                                                                                                                & \begin{tabular}[c]{@{}l@{}}Eccentric journals\\ Bent shaft / Misalignment\\    (high axial vibration)\\ Bad belt (if RPM of belt)\end{tabular} \\ \cline{2-4}
@@
 \multicolumn{1}{|l|}{}                             & Many x RPM             & \begin{tabular}[c]{@{}l@{}}Bad gears\\ Severe looseness\end{tabular}                                                     & \begin{tabular}[c]{@{}l@{}}Gear teeth x RPM\\ Fan blade count x RPM\end{tabular}                                                               \\ \hline
-\multicolumn{1}{|l|}{Subsynchrous}                 & \textless 1 x RPM      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
+\multicolumn{1}{|l|}{Sub-synchronous}                 & \textless 1 x RPM      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
 \multicolumn{1}{|l|}{Non-synchronous}              & \multicolumn{1}{c|}{-} & \begin{tabular}[c]{@{}l@{}}Electrical problems (x 50 Hz)\\ Reciprocating forces\\ Aerodynamic forces \\ Bad antifriction bearings\end{tabular} & Rubbing \\ \hline
@@
 \item When vibration monitoring is not applicable check for other condition monitoring techniques or resort to preventive maintenance.
-\item Select monitoring points and take preliminary vibration measurements
+\item Select monitoring points and take preliminary vibration measurements.
 \item Select vibration monitoring techniques: broadband, frequency analysis, or special techniques, and set parameters of measurement units.

### 2023-04-28 thesis/chapters/02-analysis-B-features.tex
Reorganize chapter files and take notes about datasets

\section{Feature engineering}
Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
\subsection{Preprocessing}
\begin{itemize}
\item Detrending - DC removal filter
\item Adaptive noise canellation of the background noise
\item Time synchronous averaging
\end{itemize}

\subsection{Feature extraction}
% Feature Engineering for Machine Learning
\cite{zheng_feature_2018}
% Feature Engineering and Selection: A Practical Approach for Predictive Models
\cite{johnson_feature_2019}
% A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
\cite{altaf_new_2022}
% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
\cite{mostafavi_novel_2021}
% Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
\cite{brito_fault_2021}
% A large set of audio features for sound description
\cite{peeters_large_2004}
% Research on online intelligent monitoring system of band saw blade wear status based on multi‑feature fusion of acoustic emission signals
\cite{zhuo_research_2022}  
% Early Detection of Imbalance in Load and Machine In Front Load Washing Machines by Monitoring Drum Movement
\cite{mohammadi_early_2020}
% A Data Mining based Approach for Electric Motor Anomaly Detection Applied on Vibration Data
\cite{egaji_data_2020}
% Condition Monitoring with Vibration Signals
\cite{nandi_condition_2019}

% Vibration Analysis for IoT Enabled Predictive Maintenance
\cite{jung_vibration_2017}

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks) 
	% Comparative Study of Various CFAR Algorithms for Non-Homogenous Environments
	\cite{hatem_comparative_2018}
	% Multi-Scale Peak and Trough Detection Optimised for Periodic and Quasi-Periodic Neuroscience Data
	\cite{bishop_multi-scale_2018}
	% Non-Parametric Local Maxima and Minima Finder with Filtering Techniques for Bioprocess
	\cite{adikaram_non-parametric_2016}
	% Identification of harmonics and sidebands in a finite set of spectral components
	\cite{gerber_identification_2013}
	% Evaluation of Threshold-Based Algorithms for Detection of Spectral Peaks in Audio
	\cite{nunes_evaluation_2007}
	% Statistical techniques to select detection thresholds for peak signals in ice-core data
	\cite{karlof_statistical_2005}
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
	% Spectral negentropy and kurtogram performance comparison for bearing fault diagnosis
	\cite{avoci_spectral_2020}
\item TKEO - Teager-Kaiser energy operator
	%Application of Teager–Kaiser Energy Operator in the Early Fault Diagnosis of Rolling Bearings
	\cite{shi_application_2022}
\end{itemize}

\paragraph{Signal decompositions - sparse approximations}
Matching pursuit algorithm optimalization problem
\cite{song_mfbd_2021}
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
	% \cite{oulmane_automatic_2015}

\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform) 
	% The fast continuous wavelet transformation (fCWT) for real-time, high-quality, noise-resistant time–frequency analysis
	\cite{arts_fast_2022}
	% A Concentrated Time–Frequency Analysis Tool for Bearing Fault Diagnosis
	\cite{yu_concentrated_2020}
	% Applications of the synchrosqueezing transform in seismic time-frequency analysis
	\cite{herrera_applications_2014}

\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)  	
	% Wavelet Packet Feature Extraction for Vibration Monitoring		
	\cite{yen_wavelet_2000}
	% A wavelet approach to dimension reduction and classiﬁcation of hyperspectral data
	\cite{wickmann_wavelet_2007}

\item EWT - Empirical Wavelet Transform - (Meyer wavelet)
	% On the computational complexity of the empirical mode decomposition algorithm
	\cite{wang_computational_2014}
	% Novel self-adaptive vibration signal analysis: Concealed component decomposition and its application in bearing fault diagnosis
	\cite{tiwari_novel_2021}
	% The MFBD: a novel weak features extraction method for rotating machinery
	\cite{song_mfbd_2021}
	% Fault Feature Extraction and Enhancement of Rolling Element Bearings Based on Maximum Correlated Kurtosis Deconvolution and Improved Empirical Wavelet Transform
	\cite{li_fault_2019}
	% An Improved Empirical Wavelet Transform for Noisy and Non-Stationary Signal Processing
	\cite{zhuang_improved_2020}
	% Time and frequency domain scanning fault diagnosis method based on spectral negentropy and its application
	\cite{yonggang_time_2020}
	% An Adaptive Spectrum Segmentation Method to Optimize Empirical Wavelet Transform for Rolling Bearings Fault Diagnosis
	\cite{xu_adaptive_2019}
	% Improved empirical wavelet transform (EWT) and its application in non‑stationary vibration signal of transformer
	\cite{ni_improved_2022}
\end{itemize}

\subsection{Feature transformation}
\cite{zheng_feature_2018}
\begin{itemize}
\item Principal Component Analysis (PCA)
\item Log transformation (Box-Cox Transform) to normal distribution
\item Normalization (min-max, standardize) 
\end{itemize}

\subsection{Feature selection}
\cite{nandi_condition_2019}
Filter method - SelectKBest  in evaluation phase
\begin{itemize}
\item Variance Threshold
\item Pearson correlation
\item ANOVA F-value
\item Mutal information
\item Fisher score
\item Spectral feature selection algorithm (SPEC)
\end{itemize}

### 2023-04-28 thesis/chapters/02-analysis-D-datasets.tex
Reorganize chapter files and take notes about datasets

\section{Evaluation datasets}

To validate the industrial solution beforehand on comprehensive dataset we use following as a benchmark.  Faults in the wild are rare so the preparation of balanced datasets is done create deficient configuartions on purpose. Datsets MaFaulDa and CWRU bearing dataset are being used in related work and are publically available in the Comma-Separated Values format. There is also less comprehensive dataset conserning unbalance, but demostrates behaviour during revolution speed up.

\subsection{Machinery Fault Database}
(MaFaulDa)
50 kHz, 5 sec. recordings, 
Rotation speeds 10~Hz - 60~Hz (737 rpm - 3686 rpm with steps of approximately 60 rpm)

% Sensors: 
	% - Accelerometers IMI 601A01/604B31,  Range ±50 g (±490 m/s2)
	% Magnetic tachometer MT-190
	% Shure SM81 microphone with frequency range of 20-20.000 Hz
	% National Instruments NI 9234 4 channel analog acquisition modules, with sample rate of 51.2 kHz

% Normal
% Imbalance  - load values within the range from 6 g to 35 g (step of 5g)
% Misalignment (Horizontal/Vertical)
% Bearings (Overhang / Underhang) - Inner, Outer, Cage

% total of 1951 different fault scenarios for 4 different operational conditions. 
% 49 of which from the normal class, 333 from unbalance class, 498 from misalignment class and 1071 from the bearing fault.

% 2 sets of accelerometers each one associated to one bearing (inner and outer) and measuring in 3 directions

% Column 1 - tachometer signal that allows to estimate rotation frequency
% Columns 2 to 4 - underhang bearing accelerometer (axial, radiale tangential direction)
% Columns 5 to 7 - overhang bearing accelerometer (axial, radiale tangential direction)
% Column 8 - microphone

RotorKit Alignment Balance Vibration Trainer (ABVT)
\cite{pestana-viana_influence_2016}
\cite{ribeiro_rotating_2017}

 \footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}}

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.48\textwidth}
	\includegraphics[width=\textwidth]{assets/mafaulda-simulator.png}
	\caption{Schematic diagram \cite{pestana-viana_influence_2016}}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.48\textwidth}
	\includegraphics[width=\textwidth]{assets/machinery-fault-simulator.jpg}
	\caption{Mechanical construction \cite{noauthor_spectraquest_nodate}}
\end{subfigure}
\caption{Machinery Fault Simulator for MaFaulDa}
\label{fig:mafaulda-simulator}
\end{figure}

\subsection{Case Western Reserve University bearing database}
(CWRU) 
2 HP (1.492 kW) Reliance Electric motor \footnote{\url{https://engineering.case.edu/bearingdatacenter/download-data-file}}
Bearings - Inner, Outer
12 kHz, 48 kHz
fan and drive end bearings
Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway.

% Faults ranging from 0.007 inches in diameter to 0.040 inches in diameter were introduced separately 
% at the inner raceway, rolling element (i.e. ball) and outer raceway. 
%Faulted bearings were reinstalled into the test motor and vibration data
%was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).

% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
\cite{jamil_feature-based_2021}

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.48\textwidth}
	\includegraphics[width=\textwidth]{assets/cwru-test-stand-2.png}
	\caption{Schematic diagram \cite{song_bearing_2022}}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.48\textwidth}
	\includegraphics[width=\textwidth]{assets/cwru-test-stand.png}
	\caption{Mechanical construction \cite{yuhong_new_2021}}
\end{subfigure}
\caption{CWRU apparatus}
\label{fig:cwru-simulator}
\end{figure}

\subsection{Unbalance on rotating shaft}
Shaft -  unbalances of different sizes \footnote{\url{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}}

% Unbalances of different sizes was recorded. Sampling rate =  4096 Hz
% 4 different unbalance strengths were recorded as well as one dataset with the unbalance holder without additional weight (i.e. without unbalance). 
%The rotation speed was varied between approx. 630 and 2330 RPM in the development datasets 
% and between approx. 1060 and 1900 RPM

%Columns:
% V_in =  The input voltage to the motor controller V_in (in V)
% Measured_RPM  = The rotation speed of the motor (in RPM; computed from speed measurements using the DT9837)
% Vibration_[1 - 3]      : The signal from the 1.,2.,3. vibration sensor

% (“0” = no unbalance, “4” = strong unbalance), (“D” = development or training, “E” = evaluation)
% Radius in mm = 0, 14, 18.5, 23, 23
% Mass 3.3 g (0 ... 3), 6.6 g in 4

\begin{figure}[h]
\centering
\includegraphics[width=0.7\textwidth]{assets/rotating-shaft.jpg}
\caption{Rotating shaft dataset \cite{mey_machine_2020}}
\label{fig:rotating-shaft}
\end{figure}

% Machine Learning-Based Unbalance Detection of a Rotating Shaft Using Vibration Data
\cite{mey_machine_2020}

### 2023-04-28 thesis/chapters/03-design.tex
Reorganize chapter files and take notes about datasets

--- 2023-03-05 chapters/03-design.tex
@@
  \begin{itemize}
-\item \textbf{Input:} Samples from acceleration in 3-axis, RPM, Noise background
-\item \textbf{Output is either:} machine overall status, type of fault, remaining useful life
-\item \textbf{Output for domain expert}: Annotation interface, Control chart of trend features, Power frequency spectrum, Waterfall plot
+\item \textbf{Input:} Samples from three-axis MEMS accelerometers, RPM tachometer, Noise background
+\item \textbf{Output is either:} machine overall status, type of fault,
+\item \textbf{Output for domain expert}: Control chart of trend features
 \end{itemize}
@@
 \item Sensors are triggered in regular intervals (every 15 minutes) to collect sample recording from the band saw.
-Configurable parameters set based on experiments: sampling frequency, dynamic range, window type (Hamming) and size (based on resolution), PSD estimation method (Welch)
 \item \textbf{Features} are computed and compared to recent measurements. If there is an statistically significant change the whole summary is send, otherwise keepalive notification is send.
-\item Possible local communication between sensors to pre-compute clustering information
+\item Set of features - at the explatory stage all are computed and stored locally.
+Use features in conjunction with transformation techniques and diagnostics model to reduce the set of features to minimum with the k-fold cross-validation.
 \item Database stores history of measurements

### 2023-04-28 thesis/chapters/appendix/B-plan-of-work.tex
Reorganize chapter files and take notes about datasets

--- 2023-03-25 chapters/appendix/B-plan-of-work.tex
@@
 
-\section{Winter semester}
+\section{Summer semester - DP1}
 
@@
 \\ \hline
-\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering methodology in condition monitoring.
+\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering methodology in CbM.
  \\ \hline
@@
  \\ \hline
-\nth{6} week         & Find articles and take notes about unsupervised and semi-supervised techniques in streaming data for machinery diagnostics, in order to gather information about suitable features.
+\nth{6} week         & Find articles and take notes about unsupervised and semi-supervised techniques in streaming data for machinery diagnostics.
  \\ \hline
-\nth{7} week         & TBD (Narrow down wide variety applicable methods for signal decomposition)
+\nth{7} week         & Narrow down wide variety applicable methods for signal decomposition.
  \\ \hline
- \nth{8} week         & TBD (Write thesis section on condition monitoring and machinery fault types)
+ \nth{8} week         & Exploratory analysis on evaluation datasets. Progress report meeting with the supervisor to topic of related work.
  \\ \hline
-
+ \nth{9} week         & Organize detailed outline out of notes gathered during literature research. 
+ \\ \hline
+  \nth{10} week         & Write up the problem analysis about condition monitoring and evaluation datasets.
+ \\ \hline
+  \nth{11} week         & Write up the analysis section about feature engineering.
+ \\ \hline
+  \nth{12} week         & Write up the analysis section about machine learning diagnostics.
+ \\ \hline
 \end{tabular}
@@
 
-\section{Summer semester}
+\section{Winter semester - DP2}
+\begin{table}[h!]
+\def\arraystretch{1.25}
+\begin{tabular}{|l|p{12cm}|}
+\hline
+\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
+\nth{1}  - \nth{4} week         & Apply feature engineering and classifications methods to evalution datasets
+\\ \hline
+\nth{4}  - \nth{8} week         & Design the vibration measurement for woodworking factoring according to technical standards. 
+\\ \hline
+\nth{8} - \nth{12} week         & Take preliminary measurements in the factory and compare signals with evaluation datasets.
+ \\ \hline
+\end{tabular}
+\end{table}
 

### 2023-04-28 thesis/chapters/preliminaries/annotation.tex
Reorganize chapter files and take notes about datasets

\thispagestyle{empty}
\section*{Annotation}
\UniversityEN \\
\uppercase{\FacultyEN}
\vspace{-8pt}
{\setlength{\mathindent}{0cm}
\begin{align*}
&\text{Degree course:} && \text{\StudyProgrammeEN} \\
&\text{Author:} && \text{\Author} \\
&\text{\ThesisEN:} && \text{\TitleEN} \\
&\text{Supervisor:} && \text{\SupervisorEN} \\
&\text{\DateEN}
\end{align*}}

\emptypage

\thispagestyle{empty}
\section*{Anotácia}
\University \\
\uppercase{\Faculty}
\vspace{-8pt}
{\setlength{\mathindent}{0cm}
\begin{align*}
&\text{Študijný program:} && \text{\StudyProgramme} \\
&\text{Autor:} && \text{\Author} \\
&\text{\Thesis:} && \text{\Title} \\
&\text{Vedúci diplomovej práce:} && \text{\Supervisor} \\
&\text{\Date}
\end{align*}}

\emptypage

### 2023-05-01 thesis/chapters/02-analysis-A-CdM.tex
Describe MaFaulDa dataset

@@
 One of the methods vibration experts utilize in the identification of the damaged part from the frequency spectrum is \textbf{order analysis}.
-In essence, it is about noticing the excessive peaks at harmonic frequencies that are integer multiples of fundamental frequency (1x RPM)~(Tab.~\ref{tab:vibration-causes}):
+In essence, it is about noticing the excessive peaks at harmonic frequencies that are integer multiples of fundamental frequency (1x rpm)~(Tab.~\ref{tab:vibration-causes}):
 
@@
 \multicolumn{2}{|l|}{\textbf{Frequency content}}                            & \textbf{Likely reason}                                                                                                     & \textbf{Other causes}                                                                                                                          \\ \hline
-\multicolumn{1}{|l|}{\multirow{4}{*}{Synchronous}} & 1 x RPM                & Imbalance                                                                                                                & \begin{tabular}[c]{@{}l@{}}Eccentric journals\\ Bent shaft / Misalignment\\    (high axial vibration)\\ Bad belt (if RPM of belt)\end{tabular} \\ \cline{2-4}
-\multicolumn{1}{|l|}{}                             & 2 x RPM                & Looseness                                                                                                                & \begin{tabular}[c]{@{}l@{}}Misalignment \\    (high axial vibration)\\ Cracked rotor\\ Bad belt (if RPM of belt)\end{tabular}                  \\ \cline{2-4}
-\multicolumn{1}{|l|}{}                             & 3 x RPM                & Misalignment                                                                                                             & and axial looseness                                                                                                                             \\ \cline{2-4}
-\multicolumn{1}{|l|}{}                             & Many x RPM             & \begin{tabular}[c]{@{}l@{}}Bad gears\\ Severe looseness\end{tabular}                                                     & \begin{tabular}[c]{@{}l@{}}Gear teeth x RPM\\ Fan blade count x RPM\end{tabular}                                                               \\ \hline
-\multicolumn{1}{|l|}{Sub-synchronous}                 & \textless 1 x RPM      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
+\multicolumn{1}{|l|}{\multirow{4}{*}{Synchronous}} & 1 x rpm                & Imbalance                                                                                                                & \begin{tabular}[c]{@{}l@{}}Eccentric journals\\ Bent shaft / Misalignment\\    (high axial vibration)\\ Bad belt (if rpm of belt)\end{tabular} \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 2 x rpm                & Looseness                                                                                                                & \begin{tabular}[c]{@{}l@{}}Misalignment \\    (high axial vibration)\\ Cracked rotor\\ Bad belt (if rpm of belt)\end{tabular}                  \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 3 x rpm                & Misalignment                                                                                                             & and axial looseness                                                                                                                             \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & Many x rpm             & \begin{tabular}[c]{@{}l@{}}Bad gears\\ Severe looseness\end{tabular}                                                     & \begin{tabular}[c]{@{}l@{}}Gear teeth x rpm\\ Fan blade count x rpm\end{tabular}                                                               \\ \hline
+\multicolumn{1}{|l|}{Sub-synchronous}                 & \textless 1 x rpm      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
 \multicolumn{1}{|l|}{Non-synchronous}              & \multicolumn{1}{c|}{-} & \begin{tabular}[c]{@{}l@{}}Electrical problems (x 50 Hz)\\ Reciprocating forces\\ Aerodynamic forces \\ Bad antifriction bearings\end{tabular} & Rubbing \\ \hline

### 2023-05-01 thesis/chapters/02-analysis-D-datasets.tex
Describe MaFaulDa dataset

@@
 \section{Evaluation datasets}
+Before the experimental setting testing designed features relevancy is proven in comparison to comprehensive benchmark datasets.
+There are a few standardized datasets used in the related work \cite{ribeiro_rotating_2017} and are publically available in Comma-Separated Values files.
 
-To validate the industrial solution beforehand on comprehensive dataset we use following as a benchmark.
-Faults in the wild are rare so the preparation of balanced datasets is done create deficient configuartions on purpose.
-Datsets MaFaulDa and CWRU bearing dataset are being used in related work and are publically available in the Comma-Separated Values format.
-There is also less comprehensive dataset conserning unbalance, but demostrates behaviour during revolution speed up.
+\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearings abnormalities.\emph{CWRU dataset} focuses solely on faults in ball bearings.
+Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during revolution speed up.
 
 \subsection{Machinery Fault Database}
-(MaFaulDa)
-50 kHz, 5 sec. recordings, 
-Rotation speeds 10~Hz - 60~Hz (737 rpm - 3686 rpm with steps of approximately 60 rpm)
-
-% Sensors: 
-	% - Accelerometers IMI 601A01/604B31,  Range ±50 g (±490 m/s2)
-	% Magnetic tachometer MT-190
-	% Shure SM81 microphone with frequency range of 20-20.000 Hz
-	% National Instruments NI 9234 4 channel analog acquisition modules, with sample rate of 51.2 kHz
-
-% Normal
-% Imbalance  - load values within the range from 6 g to 35 g (step of 5g)
-% Misalignment (Horizontal/Vertical)
-% Bearings (Overhang / Underhang) - Inner, Outer, Cage
-
-% total of 1951 different fault scenarios for 4 different operational conditions. 
-% 49 of which from the normal class, 333 from unbalance class, 498 from misalignment class and 1071 from the bearing fault.
-
-% 2 sets of accelerometers each one associated to one bearing (inner and outer) and measuring in 3 directions
-
-% Column 1 - tachometer signal that allows to estimate rotation frequency
-% Columns 2 to 4 - underhang bearing accelerometer (axial, radiale tangential direction)
-% Columns 5 to 7 - overhang bearing accelerometer (axial, radiale tangential direction)
-% Column 8 - microphone
-
-RotorKit Alignment Balance Vibration Trainer (ABVT)
-\cite{pestana-viana_influence_2016}
-\cite{ribeiro_rotating_2017}
-
- \footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}}
+MaFaulDa\footnote{MaFaulDa: \url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
+Each series has 5~seconds in length and is captured at 50 kHz.
+Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to 490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
 
@@
 \end{subfigure}
-\caption{Machinery Fault Simulator for MaFaulDa}
+\caption{Machinery fault simulator for MaFaulDa}
 \label{fig:mafaulda-simulator}
@@
 
+Observations were conducted in three cardinal axes simultaneously with 2 sets of accelerometers each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}).
+Additionally, a magnetic tachometer produced a pulse on shaft turn.
+The cardioid condenser microphone recorded sound emissions with frequency range 20~Hz - 20~kHz.
+Sensors were fed into a four-channel dynamic signal acquisition module.
+
+Columns in dataset are organized as depicted in table~\ref{tab:mafaulda-columns}.
+Machine rotational speeds were kept constant during a particular measurement, but covered a range from 737 to 3686~rpm with steps of approximately 60 rpm (equiv.
+10~Hz - 60~Hz)~\cite{pestana-viana_influence_2016}.
+The maximal rotational frequency achieved with high unbalance load is 3300 rpm.
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                                                                                                                                               \\ \hline
+1.               & \begin{tabular}[c]{@{}l@{}}Pulse with modulation of tachometer signal \\ to estimate rotation frequency  (in TTL levels)\end{tabular}                              \\ \hline
+2., 3., 4.       & \begin{tabular}[c]{@{}l@{}}Underhang bearing accelerometer \\ (inner - between the rotor and motor)\\ - axial, radial, tangential direction\end{tabular}           \\ \hline
+5., 6., 7.       & \begin{tabular}[c]{@{}l@{}}Overhang  bearing accelerometer \\ (Outer - outside most position after the rotor)\\ - axial, radial, tangential direction\end{tabular} \\ \hline
+8.               & Microphone                                                                                                                                                         \\ \hline
+\end{tabular}
+\caption{MaFaulDa columns' descriptions}
+\label{tab:mafaulda-columns}
+\end{table}
+
+This database contains normal operating conditions, faults out of unbalance, horizontal and vertical shaft misalignment, and three types of faulty bearings in inner and outer positions: outer track, inner track, rolling elements~\cite{pestana-viana_influence_2016}.
+\begin{itemize}
+\itemsep0pt
+\item \textbf{Normal} conditions are baseline without the adverse effect of fault in 49 different rotation speeds. 
+\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight adding to 333 mass unbalance loads. 
+\item \textbf{Vertical misalignement} set is comprised of 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
+\item \textbf{Horizontal misalignement} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
+\item \textbf{Bearing faults} are unnoticable without unbalance.
+Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect.
+Each unbalance mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
+\end{itemize}
+
+%TODO
 \subsection{Case Western Reserve University bearing database}
@@
 \end{subfigure}
-\caption{CWRU apparatus}
+\caption{CWRU machine apparatus}
 \label{fig:cwru-simulator}
@@
 \includegraphics[width=0.7\textwidth]{assets/rotating-shaft.jpg}
-\caption{Rotating shaft dataset \cite{mey_machine_2020}}
+\caption{Motor driving shaft in unbalance measurement \cite{mey_machine_2020}}
 \label{fig:rotating-shaft}

### 2023-05-01 thesis/chapters/02-analysis-D-datasets.tex
Evaluation datasets before proofreading

@@
 \section{Evaluation datasets}
-Before the experimental setting testing designed features relevancy is proven in comparison to comprehensive benchmark datasets.
-There are a few standardized datasets used in the related work \cite{ribeiro_rotating_2017} and are publically available in Comma-Separated Values files.
+The experimentally designed features' relevancy is first proven in comparison to comprehensive benchmark datasets.
+There are a few standardized datasets used in the related work, e.g.
+\cite{ribeiro_rotating_2017}.
+The datasets listed below are also publically available in Comma-Separated Values files online.
 
@@
 \subsection{Machinery Fault Database}
-MaFaulDa\footnote{MaFaulDa: \url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
-Each series has 5~seconds in length and is captured at 50 kHz.
-Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to 490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
+MaFaulDa\footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
+Each series has 5~seconds in duration and is captured at 50 kHz.
+Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
 
@@
 Additionally, a magnetic tachometer produced a pulse on shaft turn.
-The cardioid condenser microphone recorded sound emissions with frequency range 20~Hz - 20~kHz.
+The cardioid condenser microphone recorded sound emissions with a frequency range 20~Hz - 20~kHz.
 Sensors were fed into a four-channel dynamic signal acquisition module.
 
-Columns in dataset are organized as depicted in table~\ref{tab:mafaulda-columns}.
+Columns in the dataset are organized as depicted in table~\ref{tab:mafaulda-columns}.
 Machine rotational speeds were kept constant during a particular measurement, but covered a range from 737 to 3686~rpm with steps of approximately 60 rpm (equiv.
 10~Hz - 60~Hz)~\cite{pestana-viana_influence_2016}.
-The maximal rotational frequency achieved with high unbalance load is 3300 rpm.
+The maximal rotational frequency achieved with a high unbalance load is 3300 rpm.
 
@@
 \end{tabular}
-\caption{MaFaulDa columns' descriptions}
+\caption{MaFaulDa description of columns}
 \label{tab:mafaulda-columns}
@@
 
-%TODO
-\subsection{Case Western Reserve University bearing database}
-(CWRU) 
-2 HP (1.492 kW) Reliance Electric motor \footnote{\url{https://engineering.case.edu/bearingdatacenter/download-data-file}}
-Bearings - Inner, Outer
-12 kHz, 48 kHz
-fan and drive end bearings
-Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway.
-
-% Faults ranging from 0.007 inches in diameter to 0.040 inches in diameter were introduced separately 
-% at the inner raceway, rolling element (i.e. ball) and outer raceway. 
-%Faulted bearings were reinstalled into the test motor and vibration data
-%was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).
-
-% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
-\cite{jamil_feature-based_2021}
+\subsection{CWRU bearings dataset}
+In Case Western Reserve University (CWRU) bearing dataset\footnote{\url{https://engineering.case.edu/bearingdatacenter/download-data-file}} recordings were made of a fan end and drive end bearings under motor loads of 0, 1, 2, and 3~Horsepower (equivalently 0, 0.75, 1.49, 2.24~kW).
+Shaft speed was unaltered in all experiments, but it fluctuated between 1720 and 1797~rpm (approx.
+29~Hz).
 
 \begin{figure}[h]
-\centering
 \begin{subfigure}[b]{0.48\textwidth}
@@
 
-\subsection{Unbalance on rotating shaft}
-Shaft -  unbalances of different sizes \footnote{\url{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}}
+Single point defects were created with diameters of 0.007, 0.014, 0.021, 0.028, and 0.040 inches (equivalently 0.18, 0.36, 0.72, 1.02 mm).
+Fault locations on bearings are in the inner raceway, in the outer raceway directly and orthogonally relative to the load zone, and on rolling ball elements~(Fig.~\ref{fig:cwru-simulator})~\cite{jamil_feature-based_2021}.
 
-% Unbalances of different sizes was recorded. Sampling rate =  4096 Hz
-% 4 different unbalance strengths were recorded as well as one dataset with the unbalance holder without additional weight (i.e. without unbalance). 
-%The rotation speed was varied between approx. 630 and 2330 RPM in the development datasets 
-% and between approx. 1060 and 1900 RPM
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                 \\ \hline
+1. DE        & Drive end accelerometer samples 		\\ \hline
+2. FE        & Fan end accelerometer samples   			\\ \hline
+3. BA        & Base accelerometer samples (optional)   \\ \hline
+4. RPM     & Rotation speed of the motor in rpm        \\ \hline
+\end{tabular}
+\caption{CWRU dataset description of columns}
+\label{tab:cwru-columns}
+\end{table}
 
-%Columns:
-% V_in =  The input voltage to the motor controller V_in (in V)
-% Measured_RPM  = The rotation speed of the motor (in RPM; computed from speed measurements using the DT9837)
-% Vibration_[1 - 3]      : The signal from the 1.,2.,3. vibration sensor
+The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz, exclusively for drive end bearings samples were taken at 48 kHz.
+The duration of the time series is varied from 5 to 40 seconds.
+Drive end and fan end bearings signals are measured in each experiment sometimes accelerometer was mounted on the supporting base plate.
 
-% (“0” = no unbalance, “4” = strong unbalance), (“D” = development or training, “E” = evaluation)
-% Radius in mm = 0, 14, 18.5, 23, 23
-% Mass 3.3 g (0 ... 3), 6.6 g in 4
-
+\subsection{Unbalance on the rotating shaft}
+Unbalance Detection of a Rotating Shaft\footnote{\url{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}} is a Kaggle dataset that simulates 4 different unbalance strengths.
 \begin{figure}[h]
@@
 
-% Machine Learning-Based Unbalance Detection of a Rotating Shaft Using Vibration Data
-\cite{mey_machine_2020}
+The setup is shown in Fig.~\ref{fig:rotating-shaft}.
+Mass of 3.28 grams (or 6.61 grams during severe unbalance test) is attached to unbalance holder successively in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm.
+The rotation speed of the motor is perpetually rising between 630 and 2330 rpm in development datasets (marked with suffix D) and speeds from 1060 to 1900 rpm in the evaluation datasets (suffix E).
+The vibrations were recorded at a sampling rate of 4 kHz~\cite{mey_machine_2020}.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                      \\ \hline
+1. V\_in         & Input voltage to the motor controller (V) \\ \hline
+2. Measured\_RPM & Rotation speed of the motor (rpm)  \\ \hline
+3. Vibration\_1  & 1. Vibration sensor (samples)             \\ \hline
+4. Vibration\_2  & 2. Vibration sensor (samples)             \\ \hline
+5. Vibration\_3  & 3. Vibration sensor (samples)             \\ \hline
+\end{tabular}
+\caption{`Unbalance on the rotating shaft' dataset description of columns}
+\end{table}
+
+The accelerometers used are piezoelectric and have a frequency range of up to 10 KHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
+These sensor parameters are the same as in the case of MaFaulDa.
+In total, three different uniaxial accelerometers are mounted on the motor housing.

### 2023-05-01 thesis/chapters/preliminaries/annotation.tex
Evaluation datasets before proofreading

@@
 &\text{Supervisor:} && \text{\SupervisorEN} \\
+&\text{Departmental advisor:} && \text{\DepartmentalAdvisorEN} \\
+&\text{Consultant:} && \text{\ConsultantEN} \\
 &\text{\DateEN}
@@
 &\text{Vedúci diplomovej práce:} && \text{\Supervisor} \\
+&\text{Pedagogický vedúci:} && \text{\DepartmentalAdvisor} \\
+&\text{Konzultant:} && \text{\Consultant} \\
 &\text{\Date}

### 2023-05-04 thesis/chapters/01-introduction.tex
Evaluation datasets before proofreading
Signal preprocessing to eliminate surrounding noise

@@
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
-The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear.
-The corrective action be it repair or replacement should be taken on time in response to the key indicators.
+The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipments' wear and tear.
+The corrective action be it repair or replacement should be done on time in response to the key indicators.
 
@@
 In critical circumstances such as is the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place.
-The monitoring solution has to be sufficiently independent, reliable, and as self-sufficient as per model performance to reach wider acceptance and spread.
+The monitoring solution has to be sufficiently independent, reliable, and accurate to reach wider acceptance and spread.
 
@@
 The majority of signals are viewed once at the maximum therefore to store or even transmit them from the edge device in its entirety would be wasteful.
-The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan on battery power.
-Preferably they should also remain physically small to reduce the additional clutter.
+The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan powered out of the battery pack.
+Preferably these devices should also remain physically small to reduce the additional clutter in the factory.
 
-Attempted machine and deep learning approaches have the crucial impediment that the construction of every single machine is unique to some extent because of tolerances and variable load.
+Attempted machine learning and deep learning approaches have the crucial impediment that the construction of every single machine is unique to some extent because of tolerances and variable load during regular operation.
 The model must be trained specifically for the target environment to achieve the ideal performance.
@@
 
-This interim report to master's thesis is organized in the following manner.
+This progress report to master's thesis is organized in the following manner.
 In the first chapter of problem analysis we explore the mechanical maintenance approaches and industry standards on common fault identification.
-Then section 2 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition.
-In section 3 we delve into modes of diagnosis based on reduced relevant indicators.
-Section 4 deals with evaluation datasets used to determine computational requirements on IIoT infrastructure.
+Then section 2 summarizes filters for signal preprocessing.
+The section 3 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition.
+In section 4 we delve into modes of diagnosis based of obtained relevant indicators.
+Section 5 deals with evaluation datasets for determining computational requirements on IIoT infrastructure.
 Chapter 2 defines data format and proposes processing steps to diagnose the imminent failure and different fault types.

### 2023-05-04 thesis/chapters/02-analysis-A-CdM.tex
Evaluation datasets before proofreading
Signal preprocessing to eliminate surrounding noise

@@
 \textbf{Reactive maintenance} allows machinery to run until a complete failure.
-This is the most inappropriate way to maintain the production line, but it is straightforward.
+This is the most inappropriate way to maintain the production line, but it is straightforward enough.
 It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
-On-demand repairs are justified if short downtime is acceptable full and swift replacement of a broken machine with a backup is possible or there is no threat of failure to the surrounding environment~\cite{ziaran_technicka_2013}.
+On-demand repairs are justified if short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is negligable threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
 \bigbreak
@@
 MTTF - Mean Time To Failure).
-The schedule is crucial but can result in components being replaced in good condition creating waste or occasionally too late after the machine breaks.
-In this case conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent intervention.
-\cite{mohanty_machinery_2015}.
+The schedule is crucial but can result in components being replaced in good condition creating waste.
+Occasionally parts can stay in operation too long and as a result the machine breaks.
+However, conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
 \bigbreak
@@
 	\includegraphics[width=\textwidth]{assets/P-F-Curve.png}
-	\caption{P-F curve represents the evolution of the asset's health \cite{jennions_integrated_2011}}
+	\caption{P-F curve represents the evolution of the asset's health~\cite{jennions_integrated_2011}}
 	\label{fig:p-f-curve}
@@
 \begin{table}[h]
+\centering
 \renewcommand{\arraystretch}{1.2}

### 2023-05-04 thesis/chapters/02-analysis-B-features.tex
Signal preprocessing to eliminate surrounding noise

@@
+\section{Signal preprocessing}
+The vibration signals in a factory environment are inherently full of disturbances from adjacent equipment or irregular movement during object manipulation in the surrondings.
+In addition, accelerometers suffer from systematic measurement errors in the form of zero-g offset and bias that originates from a constant force of gravity.
+These unavoidable distortions are suppressible to some extent with digital filters.
+In the preprocessing stage we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to supress interference among components.
+
+\subsection{Detrending}
+The oscillatory motion should be centered around the zero level for further manipulation.
+The constant offset is eliminated simply by subtracting the overall average from the signal.
+Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the mean value (Equation~\ref{equ:iir-dc-blocker}).
+The transition band depends upon the choice of corner frequency $f_{3dB}$ (Fig.~\ref{fig:dc-blocker}).
+
+\begin{equation} \label{equ:iir-dc-blocker}
+y_k = (1 - \frac{\omega}{2}) \cdot (x_k  -  x_{k - 1}) + (1 - \omega) \cdot y_{k - 1}; \quad \omega = 2\pi \cdot \frac{f_{3dB}}{f_s}
+\end{equation}
+
+A steeper 3~dB attenuation band can be achieved by increasing the order of the filter.
+Then the cutoff frequency should be such that filter coefficients are fractional numbers to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\textwidth]{assets/iir-1-dc-blocker-band.jpg}
+	\caption{Transfer function of 1st order DC blocker filters ~\cite{tittelbach-helmrich_digital_2021}}
+	\label{fig:dc-blocker}
+\end{figure}
+
+The finite impulse response (FIR) filter is not recommended for DC component removal because of the undesirable ripple effect with the small number of taps.
+Cascaded-integrator-comb (CIC) filters are proposed as an alternative instead~\cite{lyons_understanding_2011}.
+
+\subsection{Adaptive noise cancellation}
+Adaptive noise cancellation (ANC) involves an adaptive filter that self-adjusts coefficients through an update algorithm in response to the reference noise signal.
+The objective of this filter is to minimize the cost function of mean square error (MSE) in error signal $e_k$ between signal contaminated with additive Gaussian noise $d_k$ and filter output $y_k$.
+Additive noise $n_k$ is assumed to be correlated with noise signal $\mathbf{X_k}$~\cite{diniz_adaptive_2020}.
+
+Wiener-Hopf equations solve the optimal gradient of MSE function and FIR filter coefficient vector $\mathbf{W_k}$.
+The least mean squares (LMS) algorithm recursively approximates this analytical solution with the method of steepest descent (Equation~\ref{equ:lms-adaptive-filter})~\cite{diniz_adaptive_2020}.
+The multiple parameters are to be considered in the evaluation of filter performance: convergence rate, estimated error, and signal-to-noise ratio (SNR).
+
+\begin{ceqn}\begin{align} \label{equ:lms-adaptive-filter}
+\mathbf{W}_{k+1} = \mathbf{W}_{k} + 2 \mu \mathbf{X}_{k}  e_k
+\end{align}\end{ceqn}
+
+The convergence stability is affected by step size $\mu$ which is bounded from above with the inverse of the maximal eigenvalue of input covariance matrix $\lambda_{max}$.
+The normalized least mean squares (NLMS) can handle input of varying scales  (Equation~\ref{equ:nlms-adaptive-filter}).
+
+\begin{ceqn}\begin{align} \label{equ:nlms-adaptive-filter}
+\mathbf{W}_{k+1} = \mathbf{W}_{k} + \frac{\mu}{\lVert\mathbf{X}_{k}\rVert^2} \mathbf{X}_{k}  e_k
+\end{align}\end{ceqn}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.8\textwidth]{assets/adaptive-filter.png}
+	\caption{Adaptive noise cancellation filter diagram}
+	\label{fig:adaptive-filter}
+\end{figure}
+\bigbreak
+
+\subsection{Time synchronous averaging}
+Time synchronous averaging is dimished the impact of sources unrelated to the harmonics of the rotational frequency in the vibrations.
+Time-domain waveform is averaged over $N$ points and aligned to synchronization pulse with period $T$ (Equation~ref{equ:tsa-average}).
+This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}
+\begin{ceqn}\begin{align}
+x_{TSA} = \frac{1}{N} \sum_{n = 0}^{N - 1}{x(t + nT)}
+\label{equ:tsa-average}
+\end{align}\end{ceqn}
+
 \section{Feature engineering}
-Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
-\subsection{Preprocessing}
-\begin{itemize}
-\item Detrending - DC removal filter
-\item Adaptive noise canellation of the background noise
-\item Time synchronous averaging
-\end{itemize}
+Before the raw observations of the machine condition are input into a machine learning model, the descriptive and summarizing numerical attributes are calculated.
+The informative features are selected from the provided set to determine a diagnosis.
+
+Among the main advantages of add-in extraction effort, as opposed to processing samples unmodified, is to gain better classification precision and reduce computational burden downstream through dimensionality reduction techniques.
+Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal characteristics are pseudo-stationary, and the trend monitoring variables are established out of extensive domain expertise in mechanics.
+
+The steps to undertake in the transformation of source data streams to a knowledge of machine status begins with
+preprocessing that continues to feature extraction, then feature selection and the ultimate result is dependent on the model.
 
@@
 \cite{brito_fault_2021}
-% A large set of audio features for sound description
+% A large setof audio features for sound description
 \cite{peeters_large_2004}
@@
 
-\paragraph{Signal decompositions - sparse approximations}
-Matching pursuit algorithm optimalization problem
+\paragraph{Wavelet signal decomposition}
+%Matching pursuit algorithm optimalization problem
 \cite{song_mfbd_2021}
@@
 
-\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform) 
+\item CWT-SST - Synchrosqueezing Wavelet Transform
 	% The fast continuous wavelet transformation (fCWT) for real-time, high-quality, noise-resistant time–frequency analysis
@@
 \item EWT - Empirical Wavelet Transform - (Meyer wavelet)
+	% Empirical Wavelet Transform - Gilles
 	% On the computational complexity of the empirical mode decomposition algorithm
@@
 \begin{itemize}
+\item Normalization (min-max, standardize)
+\item Log transformation (Box-Cox Transform) to normal distribution
 \item Principal Component Analysis (PCA)
-\item Log transformation (Box-Cox Transform) to normal distribution
-\item Normalization (min-max, standardize) 
 \end{itemize}
@@
 \subsection{Feature selection}
-\cite{nandi_condition_2019}
+Subset generation p.193
+Subset evaluation
+Stopping criteria
+Validation
+
+\cite{nandi_condition_2019} p.192
 Filter method - SelectKBest  in evaluation phase

### 2023-05-07 thesis/chapters/02-analysis-A-CdM.tex
Summarize articles of high relevance for feature engineering section

@@
 Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz.
-Higher frequencies measured traditionally to a limit of 10 kHz help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.
+Higher frequencies, measured traditionally to a limit of 10 kHz, help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.
 
@@
 Because of inherent tolerances in machine manufacturing and assembly, the rotational frequency always manifests itself, even in baseline signature~\cite{davies_handbook_2012, noauthor_iso_2002}.
-In the most likely scenario, some faults appear as compared to rotational frequency solely in\textbf{synchronous, subsynchronous, or non-synchronous components}.
+In the most likely scenario, some faults appear as compared to rotational frequency solely in \textbf{synchronous, subsynchronous, or non-synchronous components}.
 The defects can occur also in a predictable combination of the ones mentioned.
@@
 The condition monitoring programme is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant.
-Those steps can be summarized as follows ~\cite{noauthor_iso_2002}:
+Those steps can be summarized as follows~\cite{noauthor_iso_2002}:
 \begin{enumerate}

### 2023-05-07 thesis/chapters/02-analysis-B-features.tex
Summarize articles of high relevance for feature engineering section

@@
 \cite{johnson_feature_2019}
+
+% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
+% - list of features
+\cite{mostafavi_novel_2021}
+
 % A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
+% - knn with manhalobis distance
+% - select features manually as oposed to CNN and RNN
 \cite{altaf_new_2022}
-% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
-\cite{mostafavi_novel_2021}
+$$X_{rms} = \sqrt{\frac{1}{N} \sum_{i=1}^{N}{x_i^2}}$$  % rms
+$$X_{cf} = \frac{\max(|x_i|)}{X_{rms}}$$  % crest factor
+
+$$ $$% standard deviation
+$$X_{kv} = \frac{1}{N}  \sum_{i=1}^{N}{\frac{x_i - \bar{x}}{\sigma}} $$ % kurtosis
+
 % Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
+% - Time domain: mean, standard deviation, rms (root mean square), peak value, peak-topeak value, shape indicator, skewness, kurtosis, crest factor, clearance indicator, etc.
+(ii) Frequency domain: mean frequency, central frequency, energy in frequency bands, etc.
+(iii) Time-frequency domain: entropy are usually extracted by Wavelet Transform, Wavelet Packet Transform, and empirical model decomposition.
 \cite{brito_fault_2021}
+
+FFT - Short Time Fourier Transform with Hamming window and Welch averaging
+	% \cite{oulmane_automatic_2015}
+
 % A large setof audio features for sound description
@@
 \item Harmonics (peaks)
-	% Comparative Study of Various CFAR Algorithms for Non-Homogenous Environments
-	\cite{hatem_comparative_2018}
 	% Multi-Scale Peak and Trough Detection Optimised for Periodic and Quasi-Periodic Neuroscience Data
@@
 	\cite{nunes_evaluation_2007}
-	% Statistical techniques to select detection thresholds for peak signals in ice-core data
-	\cite{karlof_statistical_2005}
 \item Spectral Envelope
@@
 
-\paragraph{Wavelet signal decomposition}
-%Matching pursuit algorithm optimalization problem
-\cite{song_mfbd_2021}
+\paragraph{Wavelet signal decompositions}
+
 \begin{itemize}
-\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
-	% \cite{oulmane_automatic_2015}
-
 \item CWT-SST - Synchrosqueezing Wavelet Transform
@@
 	\cite{wickmann_wavelet_2007}
+	% The MFBD: a novel weak features extraction method for rotating machinery
+	\cite{song_mfbd_2021}
 
@@
 \item Log transformation (Box-Cox Transform) to normal distribution
-\item Principal Component Analysis (PCA)
+\item Principal Component Analysis (PCA)  % \cite{brito_fault_2021}
 \end{itemize}
@@
 \subsection{Feature selection}
-Subset generation p.193
+Subset generation % p.193
 Subset evaluation
@@
 
-\cite{nandi_condition_2019} p.192
+\cite{nandi_condition_2019} % p.192
 Filter method - SelectKBest  in evaluation phase

### 2023-05-07 thesis/chapters/02-analysis-C-diagnostics.tex
Summarize articles of high relevance for feature engineering section

\section{Diagnostics techniques}
Idenification of faulty states in data streams in semi-supervised learning

% Analysis of different RNN autoencoder variants for time series classification and machine prognostics
\cite{yu_analysis_2021}

\subsection{Novelty detection}
\cite{gervasi_anomaly_2020}

\begin{itemize}
\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
	% One-Class Classification with LOF and LOCI: An Empirical Comparison
	\cite{janssens_one-class_2007}
	% Designing a Streaming Algorithm for Outlier Detection in Data Mining - An Incremental Approach
	\cite{yu_designing_2020}

\item DenStream (Density based clustering - DBSCAN)
	% Density-Based Clustering over an Evolving Data Stream with Noise
	\cite{cao_density-based_2006}
	% A Modified Approach of OPTICS Algorithm for Data Streams
	\cite{shukla_modified_2017}
	% Data Clustering - Algorithms and Applications
	\cite{aggarwal_data_2014}
	% State-of-the-art on clustering data streams
	\cite{ghesmoune_state---art_2016}
	% Cluster-Reduce: Compressing Sketches for Distributed Data Streams
	\cite{zhao_cluster-reduce_2021}

\item Half-space Trees (Isolation forest)
	% Fast Anomaly Detection for Streaming Data
	\cite{tan_fast_2011}
	% Anomaly Detection for Data Streams Based on Isolation Forest using Scikit-multiflow
	\cite{gervasi_anomaly_2020}

\end{itemize}

\subsection{Classification}
\begin{itemize}
\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Euclidian Mahalanobis distance /  RBF similarity

% Review of Artificial Intelligence-based Bearing Vibration Monitoring
\cite{sheng_review_2020}
% Semi-Supervised Learning on Data Streams via Temporal Label Propagation
\cite{wagner_semi-supervised_2018}
% Minimum covariance determinant and extensions
\cite{hubert_minimum_2018}
\end{itemize}

% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
\cite{jamil_feature-based_2021}
% Classification of washing machines vibration signals using discrete wavelet analysis for feature extraction
\cite{goumas_classification_2002}
% Semi-Supervised Learning
\cite{chapelle_semi-supervised_2006}

% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
\cite{maurya_condition-based_2021}

### 2023-05-14 thesis/chapters/02-analysis-B-features.tex
Features discovery in time and frequency domain in analysis

--- 2023-05-04 thesis/chapters/02-analysis-B-features.tex
@@
 \section{Signal preprocessing}
-The vibration signals in a factory environment are inherently full of disturbances from adjacent equipment or irregular movement during object manipulation in the surrondings.
-In addition, accelerometers suffer from systematic measurement errors in the form of zero-g offset and bias that originates from a constant force of gravity.
+The vibration signals in a factory environment are inherently full of disturbances.
+Nearby equipment operation and handling of heavy objects in the surroundings can all contribute to the unwanted chaotic movement in otherwise mostly pure oscillatory motion.
+In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset as a result of slight miscalibration, and bias originating from a constant force of gravity.
 These unavoidable distortions are suppressible to some extent with digital filters.
-In the preprocessing stage we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to supress interference among components.
+In the preprocessing stage, we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to eliminate interference among components.
 
@@
 The oscillatory motion should be centered around the zero level for further manipulation.
-The constant offset is eliminated simply by subtracting the overall average from the signal.
-Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the mean value (Equation~\ref{equ:iir-dc-blocker}).
+The constant offset is eliminated simply by subtracting the overall mean from the signal.
+Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time(Equation~\ref{equ:iir-dc-blocker}).
 The transition band depends upon the choice of corner frequency $f_{3dB}$ (Fig.~\ref{fig:dc-blocker}).
@@
 A steeper 3~dB attenuation band can be achieved by increasing the order of the filter.
-Then the cutoff frequency should be such that filter coefficients are fractional numbers to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
+Then the cutoff frequency should be such that filter coefficients are fractions to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
 
@@
 Adaptive noise cancellation (ANC) involves an adaptive filter that self-adjusts coefficients through an update algorithm in response to the reference noise signal.
-The objective of this filter is to minimize the cost function of mean square error (MSE) in error signal $e_k$ between signal contaminated with additive Gaussian noise $d_k$ and filter output $y_k$.
+The objective of this filter is to minimize the cost function of mean square error (MSE) in the error signal $e_k$ between signal contaminated with additive Gaussian noise $d_k$ and filter output $y_k$.
 Additive noise $n_k$ is assumed to be correlated with noise signal $\mathbf{X_k}$~\cite{diniz_adaptive_2020}.
 
-Wiener-Hopf equations solve the optimal gradient of MSE function and FIR filter coefficient vector $\mathbf{W_k}$.
+Wiener-Hopf equations solve the optimal gradient of MSE function and provide us with FIR filter coefficient vector $\mathbf{W_k}$.
 The least mean squares (LMS) algorithm recursively approximates this analytical solution with the method of steepest descent (Equation~\ref{equ:lms-adaptive-filter})~\cite{diniz_adaptive_2020}.
@@
 \subsection{Time synchronous averaging}
-Time synchronous averaging is dimished the impact of sources unrelated to the harmonics of the rotational frequency in the vibrations.
-Time-domain waveform is averaged over $N$ points and aligned to synchronization pulse with period $T$ (Equation~ref{equ:tsa-average}).
+Time synchronous averaging (TSA) diminishes the impact of vibration sources unrelated to the rotational frequency and its harmonics.
+TSA averages time-domain waveform over $N$ points and aligns it to a synchronization pulse with period $T$ (Equation~ref{equ:tsa-average}).
 This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}
@@
 \section{Feature engineering}
-Before the raw observations of the machine condition are input into a machine learning model, the descriptive and summarizing numerical attributes are calculated.
-The informative features are selected from the provided set to determine a diagnosis.
-
-Among the main advantages of add-in extraction effort, as opposed to processing samples unmodified, is to gain better classification precision and reduce computational burden downstream through dimensionality reduction techniques.
-Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal characteristics are pseudo-stationary, and the trend monitoring variables are established out of extensive domain expertise in mechanics.
-
-The steps to undertake in the transformation of source data streams to a knowledge of machine status begins with
-preprocessing that continues to feature extraction, then feature selection and the ultimate result is dependent on the model.
+Raw numerical vectors after preprocessing are merely low-level descriptors of the underlying physical phenomena.
+At first, these incomprehensible sequences of numbers are reduced to summary attributes called features in the process of feature discovery.
+Normalization and linear transformations are applied here to discriminate different categories in the feature space.
+The most informative set of features is obtained with feature selection methods for the diagnostic model.
+Features can be hand-crafted.
+Likewise, they can be learned implicitly within the model representation or explicitly as an optimization problem solution.
 
 \subsection{Feature extraction}
+Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
+The advantages of add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision and reduce computational burden and storage capacity downstream with dimensionality reduction techniques~\cite{johnson_feature_2019}.
+It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model.
+Signal features are computed in the time domain, frequency domain, and time-frequency domain~\cite{brito_fault_2021}.
+
+\subsubsection{Time domain features}
+The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
+Statistics can be calculated in any domain, but the mean value is not to be used in detrended data.
+The vibration severity metrics out of technical standards are also highly regarded.
+The characteristics of amplitude include root mean square, peak-to-peak, and maximum.
+\cite{mostafavi_novel_2021}.
+
+The other significant time-domain attributes are derived as ratios of previous simpler ones.
+These ratios are crest factor, margin factor, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
+Many articles have been successful in bearing fault detection out of transients in impulsive signals with kurtosis, crest factor, and margin indicators \cite{brito_fault_2021}.
+It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.5}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}            & \textbf{Equation}                                                                    & \textbf{Feature}        & \textbf{Equation}                                                                                                  \\ \hline
+\textit{Standard deviation} & $ \sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{x_i^2} \right)^\frac{1}{2}} $                       \\ \hline
+\textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$ & \textit{Margin factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $                          \\ \hline
+\textit{Kurtosis}           & $ X_{kv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^4}$ & \textit{Impulse factor} & $ X_{if} = \frac{max(|x_i|)}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}} $                                                  \\ \hline
+\textit{Root mean square}   & $ X_{rms} = \left(\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}\right)^\frac{1}{2}$             & \textit{Shape factor}   & $ X_{sf} = \frac{\left( \frac{1}{N} \sum_{i=1}^{N}{x_i^2} \right)^\frac{1}{2}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$ \\ \hline
+\textit{Peak-to-peak}       & $ X_{ppv} = \max(x_i) - \min(x_i) $                                                  & \textit{Maximum}        & $ X_{max} = \max(|x_i|) $                                                                                          \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Time domain features}
+\label{tab:td-features}
+\end{table}
+
+\subsubsection{Frequency domain features}
+The mechanical faults present themselves as oscillatory patterns which are combinations of frequencies with various amplitudes.
+The Fourier transform is one of the prominent strategies in power spectral density estimation.
+Experts on vibrodiagnostics utilize it as a primary signal processing technique for data analysis as it is recommended in ISO 13373 standard.
+
+The inherent symmetries in the Fourier matrix made it possible to invent an efficient implementation of the Fast Fourier transform (FFT) algorithm with time complexity $O(n \log n)$.
+The drawback of the plain spectral analysis is the lack of resolution in events that occurred at distant time instants, and so their spectral components might adversely blend in together.
+
+In the frequency domain, we can obtain spectral centroid, spectral kurtosis, spectral roll-off, spectral flux, energy in frequency bands, and energy ratio \cite{peeters_large_2004}.
+In geometry terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
+Spectral roll-off gives a notion about the spectral distribution because it finds the frequency $f_c$ below which 95\% of the signal energy is contained.
+The energy in the roll-off calculation is summed up to the Nyquist limit: $f_s / 2$.
+Spectral flux is according to the definition normalized cross-correlation between two successive amplitude spectra.
+The result of one means the spectra are the most dissimilar.
+
+The frequencies related by integer ratio known as harmonics may originate from higher order oscillation modes of the same shaft or other elastic rod supported on both ends.
+Several harmonics features have been proposed.
+Ones worth investigating are fundamental frequencies, noisiness, inharmonicity, and harmonic spectral deviation.
+Noisiness as a harmonic feature is a ratio of noise (non-harmonic components) energy to the total contained energy.
+Inharmonicity measures the divergence of spectral components from a purely harmonic signal with a value of 0.
+The inharmonic spectrum has an inharmonicity value of 1.
+Harmonic spectral deviation adds up differences of harmonic peaks from the spectral envelope \cite{peeters_large_2004}.
+
+If a single principal frequency exists, it can be determined with maximum likelihood estimation.
+Such frequency would explain the signal spectrum the best \cite{peeters_large_2004}.
+The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
+The essential peak-finding approaches are based either on magnitude or gradient.
+All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence.
+In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i−1} < x_i > x{i+1}$.
+The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is local maximum, local minimum, or inflection point \cite{adikaram_non-parametric_2016}.
+
+A substantial improvement is a robust non-parametric peak identification named \emph{MMS} based on the sum of terms in an arithmetic progression based on maximum, minimum, and sum.
+MMS max-min finder in the elementary form processes points in the window of length 3, it advances one point and deems its middle point as a local extremum if it satisfies equalities below.
+Equation~\ref{equ:mms-maxima} is for the peak and Equation~\ref{equ:mms-minima} is for the valley.
+The filtration techniques are incorporated in the adaptations of MMS algorithm: MMS-WBF, MMS-SG, MMS-LH~\cite{adikaram_non-parametric_2016}.
+
+\begin{ceqn}\begin{align}
+\mathrm{MMS}_{\mathrm{max}} = \mathrm{MMS}_{\mathrm{max|mid}} \\
+\frac{a_{max} - a_{min}}{S_3 - a_{min} \cdot 3} = \frac{a_{mid} - a_{min}}{S_3 - a_{min} \cdot 3}
+\label{equ:mms-maxima}
+ \end{align}\end{ceqn}
+
+\begin{ceqn}\begin{align}
+\mathrm{MMS}_{\mathrm{min}} = \mathrm{MMS}_{\mathrm{min|mid}} \\
+\frac{a_{max} - a_{min}}{a_{max} \cdot 3 - S_3} = \frac{a_{max} - a_{mid}}{a_{max} \cdot 3 - S_3}
+\label{equ:mms-minima}
+ \end{align}\end{ceqn}
+
+Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with central frequency, uncertainty, and amplitude $C_i(v_i, \delta v_i, A_i)$ by an exhaustive search algorithm.
+Harmonic family identification is a non-trivial problem because of the spectrum estimation errors.
+The criterium is proposed to select harmonic at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
+Two series with the same fundamental frequency are merged and thought of as a modulation series \cite{gerber_identification_2013}.
+
+\begin{ceqn}\begin{align}
+v_i^{(r)} = \frac{v_j}{\min{|v_j - r \cdot v_i|}}
+\label{equ:harmonic-search}
+\end{align}\end{ceqn}
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.5}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}           & \textbf{Equation}                                                                                                 & \textbf{Feature}                     & \textbf{Equation}                                                                               \\ \hline
+\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot s(f_i)}}{\sum_{i = 0}^{N - 1}{s(f_i)}}$                           & \textit{Noisiness}                   & $X_{noisi} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} $                             \\ \hline
+\textit{Spectral roll-off} & $ \sum_{0}^{f_c}a^2(f) = 0.95 \sum_{0}^{f_s / 2}a^2(f)$                                                           & \textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| * a^2(h)}{\sum_h a^2(h)}$ \\ \hline
+\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \frac{\sum_k a(t-1, k) \cdot a(t,k)}{\sqrt{\sum_k a(t-1, k)^2} \sqrt{\sum_k a(t, k)^2}}$ & \textit{Harmonic spectral deviation} & $ X_{\mathrm{HDEV}} = \frac{1}{H}\sum_h(a(h) - SE(h))$                                          \\ \hline
+\textit{Energy}            & $ E_s = \sum_{i = 0}^{N - 1}|x(t)|^2 $                                                                            & \textit{Energy ratio}                & $E_i = \frac{E_i}{\sum_{i = 1}^{N}E_i} $                                                        \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Frequency domain features}
+\label{tab:td-features}
+\end{table}
+
+%TODO
+\subsubsection{Time-Frequency domain features}
+% Time frequency + WPT (Energy, entropy) - gain resolution in time domain, CWT,WPT, discussed in detail later.
+The short-time Fourier transform (STFT) splits the time-domain signal at the equal length intervals and combines these chunks with window function to eliviate spectral leakage as a loss of resolution.
+\cite{zhuo_research_2022}
+\cite{mostafavi_novel_2021}
+
 % Feature Engineering for Machine Learning
@@
 \cite{johnson_feature_2019}
+
+% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
+% - list of features
+\cite{mostafavi_novel_2021}
+
 % A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
+% - knn with manhalobis distance
+% - select features manually as oposed to CNN and RNN
 \cite{altaf_new_2022}
-% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
-\cite{mostafavi_novel_2021}
+
 % Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
 \cite{brito_fault_2021}
+
+% FFT - Short Time Fourier Transform with Hamming window and Welch averaging
+
 % A large setof audio features for sound description
@@
 \cite{nandi_condition_2019}
-
 % Vibration Analysis for IoT Enabled Predictive Maintenance
@@
 \begin{itemize}
-\item Standard Deviation
-\item Max. amplitude
-\item RMS amplitude
-\item Skewness
-\item Kurtosis \\
----
-\item Spectral centroid
-\item RMS frequency
-\item Root variance frequency
-\item Spectral kurtosis / Fast kurtogram
-\item Harmonics (peaks)
-	% Comparative Study of Various CFAR Algorithms for Non-Homogenous Environments
-	\cite{hatem_comparative_2018}
-	% Multi-Scale Peak and Trough Detection Optimised for Periodic and Quasi-Periodic Neuroscience Data
-	\cite{bishop_multi-scale_2018}
-	% Non-Parametric Local Maxima and Minima Finder with Filtering Techniques for Bioprocess
-	\cite{adikaram_non-parametric_2016}
-	% Identification of harmonics and sidebands in a finite set of spectral components
-	\cite{gerber_identification_2013}
-	% Evaluation of Threshold-Based Algorithms for Detection of Spectral Peaks in Audio
-	\cite{nunes_evaluation_2007}
-	% Statistical techniques to select detection thresholds for peak signals in ice-core data
-	\cite{karlof_statistical_2005}
-\item Spectral Envelope
-\item Harmonic spectral deviation \\
----
 \item Energy
@@
 \cite{zheng_feature_2018}
-\begin{itemize}
-\item Normalization (min-max, standardize)
-\item Log transformation (Box-Cox Transform) to normal distribution
-\item Principal Component Analysis (PCA)
-\end{itemize}
+
+\subsubsection{Normalization}
+ (min-max, standardize)
+
+\subsubsection{Box-Cox transform}
+
+to normal distribution
+\begin{ceqn}\begin{align}
+\widetilde{x} =
+\begin{cases}
+\frac{x^\lambda - 1}{\lambda} \quad \mathrm{if} \;\lambda \neq 0, \\\\ 
+ln(x)\quad \mathrm{if}\;\lambda = 0
+\end{cases}
+\label{equ:box-cox-transform}
+\end{align}\end{ceqn}
+
+\subsubsection{Principal Component Analysis}
+%  (PCA)
+% \cite{brito_fault_2021}
 
 \subsection{Feature selection}
-Subset generation p.193
+% Add citations to usage of different features
+Subset generation % p.193
 Subset evaluation

### 2023-05-23 thesis/chapters/01-introduction.tex
The analysis and design before final consultation in DP1

@@
 \chapter{Introduction}
-Manufacturing is experiencing a shift in the traditional practices of asset operational status evaluation and utilization.
+Manufacturing is experiencing a shift in traditional asset operational status evaluation and utilization.
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
-The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipments' wear and tear.
+The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear.
 The corrective action be it repair or replacement should be done on time in response to the key indicators.
 
-The goal is to preserve required safety and production efficiency while extending the useful life of mechanical rotating parts.
+The goal is to preserve required safety and production efficiency while extending the useful life of rotating mechanical parts.
 In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to watch in real time the machine's health status.
@@
 The dashboard must aggregate these flows into trend variables with severity levels categorized based on industrial standards.
-The majority of signals are viewed once at the maximum therefore to store or even transmit them from the edge device in its entirety would be wasteful.
+The majority of signals are viewed once at the maximum.
+Therefore to store or even transmit them from the edge device in its entirety would be wasteful.
 The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan powered out of the battery pack.
@@
 Attempted machine learning and deep learning approaches have the crucial impediment that the construction of every single machine is unique to some extent because of tolerances and variable load during regular operation.
-The model must be trained specifically for the target environment to achieve the ideal performance.
+The model has to be trained for the target environment to achieve the ideal performance.
 In addition, the failures are relatively rare events that usually occur several months apart.
-In these circumstances, it is hard to obtain a large enough sample of fault events fast.
+In these circumstances, it is hard to quickly obtain a large enough sample of fault events.
 Novelty detection is a technique that can be applied in this case.
 
-This progress report to master's thesis is organized in the following manner.
-In the first chapter of problem analysis we explore the mechanical maintenance approaches and industry standards on common fault identification.
-Then section 2 summarizes filters for signal preprocessing.
-The section 3 is all about measuring vibrations and transforming them into features meaningful in automatic fault pattern recognition.
-In section 4 we delve into modes of diagnosis based of obtained relevant indicators.
-Section 5 deals with evaluation datasets for determining computational requirements on IIoT infrastructure.
-Chapter 2 defines data format and proposes processing steps to diagnose the imminent failure and different fault types.
+This progress report on the master's thesis is organized as follows.
+In the problem analysis, in section \ref{section:condition-monitoring} we explore the mechanical maintenance approaches and industry standards on common fault identification.
+Section \ref{section:signal-preprocessing} summarizes filters for signal preprocessing.
+The \ref{section:feature-engineering} is about measuring vibrations and their transformation into features meaningful in automatic fault pattern recognition.
+In \ref{section:diagnostics-techniques}, we delve into modes of machinery diagnostics based on obtained relevant indicators, and \ref{section:evaluation-datasets} describes the most common datasets for machinery faults.
+Chapter \ref{section:design} proposes the preliminary design of the model exploration and deployment phase of the project.

### 2023-05-23 thesis/chapters/02-analysis-A-CdM.tex
The analysis and design before final consultation in DP1

@@
-\section{Condition monitoring}
-All rotating machinery eventually fails because of the long-term strain on the individual parts, incorrect workmanship, installation, or operational procedures.
+\section{Condition monitoring} \label{section:condition-monitoring}
+All rotating machinery eventually fails because of the long-term strain on the individual parts, inadequate workmanship, installation, or operational procedures.
 In the end, these factors cause the equipment not to fulfill its intended functionality.
 Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, oil and particle analysis, ultrasonic testing, etc.
-However, vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
 
-The defect needs to be either repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or any endangerment of the responsible personnel.
+The defect needs to be repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or any endangerment of the responsible personnel.
 The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
-The guide to set appropriate maintenance procedures is outlined in the IEC~60706-2 standard and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
+The guide to set appropriate maintenance procedures as outlined in the IEC~60706-2 standard, and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
 
@@
 In general, the more sophisticated methods are beneficial in a high-stakes environment.
-The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands spare parts to be ready in the supply inventory at all times.
-In certain situations it suffice to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize assets' usage~\cite{cinar_machine_2020}.
+The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
+In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize assets' usage~\cite{cinar_machine_2020}.
 \bigbreak
@@
 It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
-On-demand repairs are justified if short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is negligable threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
+On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
 \bigbreak
@@
 \textbf{Preventive maintenance} is performed before any issue is detected.
-Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (e.g.
-MTTF - Mean Time To Failure).
+Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure).
 The schedule is crucial but can result in components being replaced in good condition creating waste.
-Occasionally parts can stay in operation too long and as a result the machine breaks.
-However, conservative planning is usually the norm to keep the machine always in a perfect state and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
+The parts can occasionally stay in operation too long, and the machine breaks as a result.
+Conservative planning is usually the norm to keep the machine always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
 \bigbreak
@@
 \textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
-The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and troublesome components are identified.
+The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and the identification of troublesome components.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
@@
 
-The P-F curve is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
+The \emph{P-F curve} is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
 Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval~\cite{bousdekis_enterprise_2021}.
@@
 
-The Remaining Useful Life (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, and based on the model of the `run-to-failure' histories and usage parameters~\cite{okoh_overview_2014}.
-Predictive condition monitoring aims to extend the machine lifespan to the maximum by predicting expected RUL.
+The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the `run-to-failure' histories, and usage parameters~\cite{okoh_overview_2014}.
+Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.
 
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
@@
 A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded but also in the early stages soon after assembly.
-Causes can be found in manufacturing or material defects, inadequate installation, or improper start-up procedures.
+Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes.
 During the stable middle phase, malfunction can occur after the machine's excessive overload.
-The time plot to failure rate is known as the bath tub curve~(Fig.~\ref{fig:bath-tub-curve}).
+The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}).
 
 \subsection{Vibration fault types}
-Mechanical problems during machinery operation bring about vibrations in the vast majority of cases.
-Therefore vibroacoustic diagnostics is considered one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
+Mechanical problems during machinery operation bring about vibrations in many instances.
+Therefore vibroacoustic diagnostics is considered as one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
 
 The cause of vibration comes out of the changing force in its magnitude or direction.
-The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure broadly categorized as \textbf{unbalance, misalignment, looseness, excentricity, deformation, crack and influence of the external force} (e.g.
-friction)~\cite{davies_handbook_2012}.
-It is important to stress that our concern are not the underlying deficiencies in mechanical parts, but the correct fault classification based on the signal waveform.
+The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure.
+These defects are broadly categorized as \textbf{unbalance, misalignment, looseness, eccentricity, deformation, crack, and influence of the external force} (friction)~\cite{davies_handbook_2012}.
+It is important to stress that our concern is not the underlying deformities in mechanical parts, but the correct fault classification based on the signal waveform.
 
-\begin{figure}[h]
+\begin{figure}[ht]
 	\centering
@@
 
-Rotating machine disorders do exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase.
+Rotating machine disorders exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase signal.
 Most of the occurring faults can be tied to the main rotational speed of the component under investigation (Fig.~\ref{fig:machinery-vibrations})~\cite{davies_handbook_2012}.
@@
 These low-frequency faults are associated with the movement of the shaft and primarily coincide with revolution speed and its harmonics.
-Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz to 1 kHz.
-Higher frequencies, measured traditionally to a limit of 10 kHz, help notice the deficiencies in bearings even sooner~\cite{torres_automatic_2022}.
+Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz and 1 kHz.
+Higher frequencies, measured traditionally to a limit of 10 kHz, help notice the faults in bearings even sooner~\cite{torres_automatic_2022}.
 
 One of the methods vibration experts utilize in the identification of the damaged part from the frequency spectrum is \textbf{order analysis}.
-In essence, it is about noticing the excessive peaks at harmonic frequencies that are integer multiples of fundamental frequency (1x rpm)~(Tab.~\ref{tab:vibration-causes}):
+The excessive peaks at harmonic frequencies are of interest.
+Harmonics are integer multiples of fundamental frequency (1x rpm)~(Tab.~\ref{tab:vibration-causes}):
 
@@
 In the most likely scenario, some faults appear as compared to rotational frequency solely in \textbf{synchronous, subsynchronous, or non-synchronous components}.
-The defects can occur also in a predictable combination of the ones mentioned.
+The defects can occur in a predictable combination of the ones mentioned.
 Other common patterns experts look for are modulation sidebands typical for bearings and gears extractable with cepstrum analysis~\cite{ziaran_technicka_2013}.
-Therefore procedure relying on elimination narrows down unrelated causes effectively.
+Procedures relying on elimination narrow down unrelated causes effectively.
 
@@
 Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards.
-The standards are concerned with each step in the process that originates with transducer placements and data acquisition.
+Standards are concerned with each step in the process that originates with transducer placements and data acquisition.
 They prescribe conventions for setting fault severity levels and provide empirically observed vibration characteristics of common defects.
-Two relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
+Relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
 \bigbreak
 
-\textbf{ISO 20816-1:2016} establishes the approach to vibration measurement and evaluation on non-rotating housing of machinery parts~\cite{noauthor_iso_2016}.
+\textbf{ISO 20816-1:2016} establishes the approaches of vibration measurement and evaluation on non-rotating housing of machinery parts~\cite{noauthor_iso_2016}.
 The measurement units are agreed upon for kinematic quantities of vibrations.
-Acceleration is to be measured in meters per second squared ($m/s^2$), velocity in millimeters per second ($mm/s$), and displacement in micrometers ($\mu m$).
-It is customary to evaluate broad-band vibration velocity in terms of root mean square value (RMS), as it has a relation to its signal energy.
-No simple direct relationship is expressible among these quantities, except in stationary signals.
+Acceleration is measured in meters per second squared ($m/s^2$), velocity in millimeters per second ($mm/s$), and displacement in micrometers ($\mu m$).
+It is customary to evaluate broad-band vibration velocity in terms of root mean square value (rms), as it is related to signal energy.
+No simple direct relationship is expressible among these physical quantities, except in stationary signals.
 
-The vibration severity is the maximum magnitude value measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft in the axial axis.
+The vibration severity is the maximum of magnitudes measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft in the axial axis.
 Multiple measurement locations, i.e.
-on several bearings or couplings, should be assessed independently.
+on different bearings or couplings, should be assessed independently.
 
-Criteria introduced to judge vibration severity are its absolute vibration magnitude, change in the magnitude vector, and rate of change.
-In terms of maximal magnitudes the machines of varied sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
-The table values serve as guidelines towards realistic requirements between machine manufacturers and customers.
+Criteria introduced to judge vibration severity are absolute vibration magnitude, change in the magnitude vector, and rate of change.
+In terms of maximal magnitudes, the machines of varied sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
+The values in this table serve as guidelines towards realistic requirements between machine manufacturers and their customers.
 
@@
 \emph{Zone B} signifies suitability for long-term operation.
-In \emph{zone C} is the machine deemed in unsatisfactory condition and corrective action should be taken soon.
+In \emph{zone C} the machine is deemed in unsatisfactory condition and corrective action should be taken soon.
 Finally, in zone D vibrations can cause damage to the machine.
-The span of acceptable values differs on machine class from I through to IV with an output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.
+The span of acceptable values differs with the machine class from I through to IV and their output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.
 
 The operational limits in the form of \emph{alarms} and \emph{trips} are usually established on the zone boundaries or close to them.
-Alarms are placed between zones B and C and provide a warning about reaching the threshold significant for noticeable change.
+Alarms are placed between zones B and C providing a warning about reaching the threshold significant for noticeable change.
 Trips in between zones C and D urge immediate action or machine shut down.
-Both limits should not exceed 1.25 times the upper boundary or lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
+Both limits should not exceed 1.25 times the upper boundary of lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
 
-\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in the vocabulary of ISO 20186.
-According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or intervals.
-Both designs can be permanently mounted, but in continuous, collection `multiplexing rate is sufficiently rapid so there is no significant data or trends lost'~\cite{noauthor_iso_2002}.
+\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in termos of the vocabulary in ISO 20186.
+According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval.
+Both designs can be permanently mounted.
+In continuous collection it is recommended to have `multiplexing rate sufficiently rapid so there is no significant data or trends lost'~\cite{noauthor_iso_2002}.
 When channels are scanned successively with gaps between data points the system is known as `scanning'.
 
-The condition monitoring programme is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant.
+The condition monitoring program is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant.
 Those steps can be summarized as follows~\cite{noauthor_iso_2002}:
@@
 \item Review machinery history and establish failure modes.
-\item When vibration monitoring is not applicable check for other condition monitoring techniques or resort to preventive maintenance.
+\item When vibration monitoring is not applicable check for other condition-monitoring techniques or resort to preventive maintenance.
 \item Select monitoring points and take preliminary vibration measurements.
@@
 \item If an alarm was exceeded, notify appropriate personnel to review data and trends, perform diagnostic evaluation, and repair as necessary.
-In case a new baseline is needed continue in the step of taking baseline measurements.
+In case a new baseline is needed, continue in the step of taking baseline measurements.
 \item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm trigger.
@@
 Measurement of vibrations should be accompanied by a description of the machine and its operating conditions.
-The machine description includes the machine identifier and its type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
-Measurement parameters such as timestamp, transducer type, sensor location and orientation in MIMOSA code, measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.) are to be recorded alongside the measurement value itself~\cite{noauthor_iso_2002}.
+The machine description includes its identifier and type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
+Measurement parameters are to be recorded alongside the measurement value itself such as timestamp, transducer type, sensor location and orientation in MIMOSA code, measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
 
 The transducer of choice for condition monitoring is the accelerometer which can provide the acceleration value of the body and velocity after signal integration.
-However, standard cautions against double integrating for displacement.
+However, standard advise against double integrating for displacement.
 The recommended frequency range for an accelerometer is 0.1~Hz to 30~kHz.
@@
 Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation.
-According to bath tub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period.
+According to the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period.
 The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.
 
-The vibration baseline is defined by broad-band magnitudes and phases of motion vectors, waveforms in time and frequency domain, the rotational speed of the machine as well as its frequency response to different speeds during start-up and coast-down captured in the Bode plot and waterfall plot.
+The vibration baseline is defined by broad-band magnitudes and phases of motion vectors, the waveform in the time and frequency domain, the rotational speed of the machine as well as its frequency response to different speeds during start-up and coast-down captured in the Bode plot and waterfall plot.
 Changes during the machine operation are then depicted in value trends.

### 2023-05-23 thesis/chapters/02-analysis-B-features.tex
The analysis and design before final consultation in DP1

@@
-\section{Signal preprocessing}
+\section{Signal preprocessing} \label{section:signal-preprocessing}
 The vibration signals in a factory environment are inherently full of disturbances.
@@
 These unavoidable distortions are suppressible to some extent with digital filters.
-In the preprocessing stage, we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to eliminate interference among components.
+In the preprocessing stage, we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to eliminate the external interference.
 
@@
 The constant offset is eliminated simply by subtracting the overall mean from the signal.
-Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time(Equation~\ref{equ:iir-dc-blocker}).
+Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time (Equation~\ref{equ:iir-dc-blocker}).
 The transition band depends upon the choice of corner frequency $f_{3dB}$ (Fig.~\ref{fig:dc-blocker}).
 
+\myequations{DC blocker IIR filter of 1st order}
 \begin{equation} \label{equ:iir-dc-blocker}
@@
 Adaptive noise cancellation (ANC) involves an adaptive filter that self-adjusts coefficients through an update algorithm in response to the reference noise signal.
-The objective of this filter is to minimize the cost function of mean square error (MSE) in the error signal $e_k$ between signal contaminated with additive Gaussian noise $d_k$ and filter output $y_k$.
+The objective of this filter is to minimize the mean square error (MSE) cost function in the error signal $e_k$ between signal contaminated with Gaussian noise $d_k$ and filter output $y_k$.
 Additive noise $n_k$ is assumed to be correlated with noise signal $\mathbf{X_k}$~\cite{diniz_adaptive_2020}.
 
-Wiener-Hopf equations solve the optimal gradient of MSE function and provide us with FIR filter coefficient vector $\mathbf{W_k}$.
+Wiener-Hopf equations solve the optimal gradient of the MSE function and provide us with FIR filter coefficient vector $\mathbf{W_k}$.
 The least mean squares (LMS) algorithm recursively approximates this analytical solution with the method of steepest descent (Equation~\ref{equ:lms-adaptive-filter})~\cite{diniz_adaptive_2020}.
@@
 
+\myequations{Adaptive noise filtering LMS update formula}
 \begin{ceqn}\begin{align} \label{equ:lms-adaptive-filter}
@@
 
+\myequations{Adaptive noise filtering NLMS update formula}
 \begin{ceqn}\begin{align} \label{equ:nlms-adaptive-filter}
@@
 Time synchronous averaging (TSA) diminishes the impact of vibration sources unrelated to the rotational frequency and its harmonics.
-TSA averages time-domain waveform over $N$ points and aligns it to a synchronization pulse with period $T$ (Equation~ref{equ:tsa-average}).
+TSA averages time-domain waveform over $N$ points and aligns it to a synchronization pulse with period $T$ (Equation~\ref{equ:tsa-average}).
 This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}
+
+\myequations{Time synchronous averaging}
 \begin{ceqn}\begin{align}
@@
 
-\section{Feature engineering}
+\section{Feature engineering} \label{section:feature-engineering}
 Raw numerical vectors after preprocessing are merely low-level descriptors of the underlying physical phenomena.
@@
 The most informative set of features is obtained with feature selection methods for the diagnostic model.
-Features can be hand-crafted.
-Likewise, they can be learned implicitly within the model representation or explicitly as an optimization problem solution.
+Features can be hand-crafted, learned implicitly within the model representation, or explicitly from an optimization problem solution.
 
@@
 Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
-The advantages of add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision and reduce computational burden and storage capacity downstream with dimensionality reduction techniques~\cite{johnson_feature_2019}.
+The advantages of add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
 It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model.
-Signal features are computed in the time domain, frequency domain, and time-frequency domain~\cite{brito_fault_2021}.
+Signal features are computed in the time, frequency, and time-frequency domain~\cite{brito_fault_2021}.
 
-\subsubsection{Time domain features}
+\subsection{Time domain features}
 The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
@@
 The vibration severity metrics out of technical standards are also highly regarded.
-The characteristics of amplitude include root mean square, peak-to-peak, and maximum.
-\cite{mostafavi_novel_2021}.
+The characteristics of amplitude include root mean square, peak-to-peak, and maximum~\cite{mostafavi_novel_2021}.
 
@@
 \begin{table}[h]
-\renewcommand{\arraystretch}{1.5}
+\centering
+\renewcommand{\arraystretch}{2}
 \begin{adjustbox}{width=\columnwidth,center}
@@
 
-\subsubsection{Frequency domain features}
+\subsection{Frequency domain features}
 The mechanical faults present themselves as oscillatory patterns which are combinations of frequencies with various amplitudes.
 The Fourier transform is one of the prominent strategies in power spectral density estimation.
-Experts on vibrodiagnostics utilize it as a primary signal processing technique for data analysis as it is recommended in ISO 13373 standard.
+Experts on vibrodiagnostics utilize it as a primary signal processing technique for data analysis as it is recommended in ISO 13373-2 standard~\cite{noauthor_iso_2016_2}.
 
 The inherent symmetries in the Fourier matrix made it possible to invent an efficient implementation of the Fast Fourier transform (FFT) algorithm with time complexity $O(n \log n)$.
-The drawback of the plain spectral analysis is the lack of resolution in events that occurred at distant time instants, and so their spectral components might adversely blend in together.
+The drawback of the plain spectral analysis is the lack of resolution for events that occurred at distant time instants, and so their spectral components might adversely blend in together.
 
-In the frequency domain, we can obtain spectral centroid, spectral kurtosis, spectral roll-off, spectral flux, energy in frequency bands, and energy ratio \cite{peeters_large_2004}.
+In the frequency domain, we can obtain spectral centroid, spectral kurtosis, spectral roll-off, spectral flux, energy in frequency bands, and energy ratio (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
 In geometry terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
-Spectral roll-off gives a notion about the spectral distribution because it finds the frequency $f_c$ below which 95\% of the signal energy is contained.
+Spectral roll-off gives a notion about the spectral distribution because it searches the frequency $f_c$ below which 95\% of the signal energy is contained.
 The energy in the roll-off calculation is summed up to the Nyquist limit: $f_s / 2$.
-Spectral flux is according to the definition normalized cross-correlation between two successive amplitude spectra.
-The result of one means the spectra are the most dissimilar.
+According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra, value of one means spectra are the most dissimilar.
 
-The frequencies related by integer ratio known as harmonics may originate from higher order oscillation modes of the same shaft or other elastic rod supported on both ends.
-Several harmonics features have been proposed.
-Ones worth investigating are fundamental frequencies, noisiness, inharmonicity, and harmonic spectral deviation.
+The harmonic frequencies may originate from higher order oscillation modes of the same shaft or other elastic rod supported on both ends.
+Several harmonics features worth investigating are fundamental frequencies, noisiness, inharmonicity, and harmonic spectral deviation~(Tab.~\ref{tab:fd-features}).
 Noisiness as a harmonic feature is a ratio of noise (non-harmonic components) energy to the total contained energy.
-Inharmonicity measures the divergence of spectral components from a purely harmonic signal with a value of 0.
-The inharmonic spectrum has an inharmonicity value of 1.
-Harmonic spectral deviation adds up differences of harmonic peaks from the spectral envelope \cite{peeters_large_2004}.
+Inharmonicity measures the divergence of spectral components from a purely harmonic to inharmonic signal on scale from 0 to 1.
+Harmonic spectral deviation adds up differences of amplitudes at harmonic peaks $a(h)$ from the spectral envelope $\mathrm{SE}(h)$~\cite{peeters_large_2004}.
 
 If a single principal frequency exists, it can be determined with maximum likelihood estimation.
-Such frequency would explain the signal spectrum the best \cite{peeters_large_2004}.
+Such frequency would explain the signal spectrum the best~\cite{peeters_large_2004}.
 The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
@@
 All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence.
-In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i−1} < x_i > x{i+1}$.
-The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is local maximum, local minimum, or inflection point \cite{adikaram_non-parametric_2016}.
+In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x{i+1}$.
+The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
 
@@
 MMS max-min finder in the elementary form processes points in the window of length 3, it advances one point and deems its middle point as a local extremum if it satisfies equalities below.
-Equation~\ref{equ:mms-maxima} is for the peak and Equation~\ref{equ:mms-minima} is for the valley.
-The filtration techniques are incorporated in the adaptations of MMS algorithm: MMS-WBF, MMS-SG, MMS-LH~\cite{adikaram_non-parametric_2016}.
+Equation~\ref{equ:mms-maxima} is for the hill and Equation~\ref{equ:mms-minima} is for the valley.
+The filtration techniques are incorporated in the adaptations of the MMS algorithm: MMS-WBF, MMS-SG, MMS-LH~\cite{adikaram_non-parametric_2016}.
 
+\myequations{MMS algorithm: Local maxima identification equality}
 \begin{ceqn}\begin{align}
@@
 
+\myequations{MMS algorithm: Local minima identification equality}
 \begin{ceqn}\begin{align}
@@
 
-Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with central frequency, uncertainty, and amplitude $C_i(v_i, \delta v_i, A_i)$ by an exhaustive search algorithm.
+Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with central frequency, uncertainty, and amplitude $C_i(v_i, \Delta v_i, A_i)$ by an exhaustive search algorithm.
 Harmonic family identification is a non-trivial problem because of the spectrum estimation errors.
-The criterium is proposed to select harmonic at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
-Two series with the same fundamental frequency are merged and thought of as a modulation series \cite{gerber_identification_2013}.
+The criterion is proposed to select harmonic at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
+Two series with the same fundamental frequency are merged and thought of as a modulation series~\cite{gerber_identification_2013}.
 
+\myequations{Harmonic series search criterion}
 \begin{ceqn}\begin{align}
@@
 
-\begin{table}[h]
-\renewcommand{\arraystretch}{1.5}
-\begin{adjustbox}{width=\columnwidth,center}
-\begin{tabular}{|l|l|l|l|}
+\begin{table}[ht]
+\renewcommand{\arraystretch}{2}
+\centering
+%\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|l|l|}
 \hline
-\textbf{Feature}           & \textbf{Equation}                                                                                                 & \textbf{Feature}                     & \textbf{Equation}                                                                               \\ \hline
-\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot s(f_i)}}{\sum_{i = 0}^{N - 1}{s(f_i)}}$                           & \textit{Noisiness}                   & $X_{noisi} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} $                             \\ \hline
-\textit{Spectral roll-off} & $ \sum_{0}^{f_c}a^2(f) = 0.95 \sum_{0}^{f_s / 2}a^2(f)$                                                           & \textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| * a^2(h)}{\sum_h a^2(h)}$ \\ \hline
-\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \frac{\sum_k a(t-1, k) \cdot a(t,k)}{\sqrt{\sum_k a(t-1, k)^2} \sqrt{\sum_k a(t, k)^2}}$ & \textit{Harmonic spectral deviation} & $ X_{\mathrm{HDEV}} = \frac{1}{H}\sum_h(a(h) - SE(h))$                                          \\ \hline
-\textit{Energy}            & $ E_s = \sum_{i = 0}^{N - 1}|x(t)|^2 $                                                                            & \textit{Energy ratio}                & $E_i = \frac{E_i}{\sum_{i = 1}^{N}E_i} $                                                        \\ \hline
+\textbf{Feature}           & \textbf{Equation}                                                                                                  \\ \hline
+\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot a(f_i)}}{\sum_{i = 0}^{N - 1}{a(f_i)}}$                   \\ \hline 
+\textit{Spectral roll-off} & $ \sum_{0}^{f_c}a^2(f) = 0.95 \sum_{0}^{f_s / 2}a^2(f)$                                                   \\ \hline
+\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \frac{\sum_k a(t-1, k) \cdot a(t,k)}{\sqrt{\sum_k a(t-1, k)^2} \sqrt{\sum_k a(t, k)^2}}$ \\ \hline 
+\textit{Harmonic spectral deviation} & $ X_{\mathrm{HDEV}} = \frac{1}{H}\sum_h(a(h) - \mathrm{SE}(h))$                                          \\ \hline
+\textit{Noisiness}                   & $X_{noise} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} $                             \\ \hline
+\textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| \cdot a^2(h)}{\sum_h a^2(h)}$ \\ \hline
+\textit{Energy}            & $ E = \sum_{i = 0}^{N - 1}|x(t)|^2 $                                                                    \\ \hline \textit{Energy ratio}                & $E_i = \frac{E_i}{\sum_{i = 1}^{N}E_i} $                                                        \\ \hline
+\textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
 \end{tabular}
-\end{adjustbox}
+%\end{adjustbox}
 \caption{Frequency domain features}
-\label{tab:td-features}
+\label{tab:fd-features}
 \end{table}
 
-%TODO
-\subsubsection{Time-Frequency domain features}
-% Time frequency + WPT (Energy, entropy) - gain resolution in time domain, CWT,WPT, discussed in detail later.
-The short-time Fourier transform (STFT) splits the time-domain signal at the equal length intervals and combines these chunks with window function to eliviate spectral leakage as a loss of resolution.
-\cite{zhuo_research_2022}
-\cite{mostafavi_novel_2021}
+\subsection{Time-frequency domain features}
+The \textbf{Short-time Fourier transform} (STFT) splits the time-domain signal to an equal-length intervals.
+Individual chunks have 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to Fourier transform periodicity assumption.
+Traditionally, the Hann window is commonly used instead of rectangular window~\cite{ziaran_technicka_2013,noauthor_iso_2016_2}.
 
-% Feature Engineering for Machine Learning
-\cite{zheng_feature_2018}
-% Feature Engineering and Selection: A Practical Approach for Predictive Models
-\cite{johnson_feature_2019}
+In the time-frequency domain, the same features can be derived as in the frequency domain, but in addition, the attributes are time-localized in this way.
+The STFT has a considerable flaw for implementation in a self-adaptable system and that is fixed resolution.
+The optimal window size has to be set beforehand or chosen after performing multiple transformations on chunks out of the range of lengths.
+Welch's methods averages multiple consecutive blocks to better estimate the spectrum.
+We have already researched the suitability of STFT for online detection of constant frequencies~\cite{hajek_iot_2022}.
 
-% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
-% - list of features
-\cite{mostafavi_novel_2021}
+The bands for lower frequencies should be longer in duration than for higher frequencies.
+The \textbf{Wavelet transform} (WT) possesses such multi-scale discrimination property effectively increasing resolution in time-frequency plain.
+Wavelet basis functions are constructed for that purpose (Equation~\ref{equ:mother-wavelet}).
+There are several wavelet families, for example, Haar, Daubechies, Coiflets, Symlets, Morlet, and Meyer~\cite{nandi_condition_2019}.
 
-% A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
-% - knn with manhalobis distance
-% - select features manually as oposed to CNN and RNN
-\cite{altaf_new_2022}
+\myequations{Mother wavelet function}
+\begin{ceqn}\begin{align}
+\psi_{s, \tau} = \frac{1}{\sqrt{s}}\psi\left(\frac{t - \tau}{s}\right)
+\label{equ:mother-wavelet}
+\end{align}\end{ceqn}
 
-% Fault Detection of Bearing: An Unsupervised Machine Learning Approach Exploiting Feature Extraction and Dimensionality Reduction
-\cite{brito_fault_2021}
+\textbf{Continuous Wavelet transform} (CWT)~(Equation~\ref{equ:cwt-transform}) is performed by scaling and translating the mother wavelet $\psi$ picked out of the appropriate family~\cite{nandi_condition_2019}.
+The scale factor is denoted with~$s$ and time position with~$\tau$.
+The choice of wavelet type is data-driven because distinct wavelet shapes have an impact on the response and ultimately contribute to filter length.
+The decision lies between recognition abilities for impulse-like signals or the inclusion of wider surrounding space.
 
-% FFT - Short Time Fourier Transform with Hamming window and Welch averaging
+\myequations{Continuous Wavelet transform}
+\begin{ceqn}\begin{align}
+W_{x(t)}(s, \tau) = \frac{1}{\sqrt{s}}\int x(t) \cdot \psi^*\left(\frac{t - \tau}{s}\right)\;\mathrm{dt}
+\label{equ:cwt-transform}
+\end{align}\end{ceqn}
 
-% A large setof audio features for sound description
-\cite{peeters_large_2004}
-% Research on online intelligent monitoring system of band saw blade wear status based on multi‑feature fusion of acoustic emission signals
-\cite{zhuo_research_2022}
-% Early Detection of Imbalance in Load and Machine In Front Load Washing Machines by Monitoring Drum Movement
-\cite{mohammadi_early_2020}
-% A Data Mining based Approach for Electric Motor Anomaly Detection Applied on Vibration Data
-\cite{egaji_data_2020}
-% Condition Monitoring with Vibration Signals
-\cite{nandi_condition_2019}
-% Vibration Analysis for IoT Enabled Predictive Maintenance
-\cite{jung_vibration_2017}
+The CWT is computationally intensive when a highly detailed scale resolution is required because each wavelet scale convolves with the entire signal.
+The fCWT algorithm allows 100 times higher spectral resolution then previous implementation at the same speed.
+It increases performance 122 times compared to Wavelib and 34 times in comparison with PyWavelets~\cite{arts_fast_2022}.
 
-\paragraph{Statistical measures}
+The fast CWT algorithm reaches compelling improvement by applying Parseval's theorem to the wavelet transform formula that removes the dependence on the time offset parameter~\cite{arts_fast_2022}.
+The convolution takes place with the mother wavelet in the Fourier base.
+Then, inverse FFT produces the coefficients for individual scales.
+
+\textbf{Synchrosqueezing Wavelet transform} (SST) is a modification of CWT attempting to sharpen the representation of frequency components by coefficient reassignments from around the central frequencies towards the middle of the bands.
+The justification for these reallocations is rooted in the signal approximation as amplitude-modulated oscillating modes with additive noise $\eta(t)$ (Equation~\ref{equ:sst-transform})~\cite{herrera_applications_2014}.
+
+\myequations{Representation of components for Synchrosqueezing Wavelet transform}
+\begin{ceqn}\begin{align}
+s(t) = \sum_{k=1}^{K} A_k(t)\cos(\theta_k(t)) + \eta(t)
+\label{equ:sst-transform}
+\end{align}\end{ceqn}
+
+The components are defined by their instantaneous amplitudes $A_k(t)$ and instantaneous phases $\theta_k(t)$.
+The energy spread to adjacent bins can be effectively squeezed only in regions with constant phase and large enough component separation.
+Despite the promising properties of this transform, white noise causes severe interference in the resulting time-frequency map.
+
+The alternative to isolating weak impacts with high time resolution is a \textbf{Teager-Kaiser energy operator} (TKEO) (Equation~ \ref{equ:tkeo-operator}).
+It is a tool for envelope analysis to demodulate characteristic AM-FM signal present during bearing faults.
+Energy operator output can be utilized as a standalone feature attribute.
+
+\myequations{Teager–Kaiser energy operator}
+\begin{ceqn}\begin{align}
+\psi[x(n)] = [x(n)]^2 - x(n - 1)x(n + 1)
+\label{equ:tkeo-operator}
+\end{align}\end{ceqn}
+
+Improved TKEO is necessary to prevent analysis from suffering from the noisy source.
+The key idea is to perform TKEO after signal decomposition into narrow-band components with different center frequencies.
+The extracted modes are reconstructed with weights assigned based on their correlations to the original signal~\cite{shi_application_2022}.
+
+Time-frequency spectrum modification preserving localization of abrupt wide-band spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
+Post-processing of STFT window $G(t,\omega)$ involves multiplication of the spectrum with the Transient extracting operator (TEO).
+This operator is expressed in the form of a Dirac delta function $\delta(t)$ (Equation~\ref{equ:tet-transform}).
+
+\myequations{Transient-extracting transform}
+\begin{ceqn}\begin{align}
+\mathrm{Te}(t,\omega) = G(t,\omega) \cdot  \delta(t - t_0)
+\label{equ:tet-transform}
+\end{align}\end{ceqn}
+
+TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
+These two transforms use distinct windows $g[n]$ and $n \cdot g[n]$.
+Decomposition of signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
+
+The spectrograms to illustrate the difference in the ability of Fourier transform, continuous Wavelet transform, and their modifications to pick up underlying patterns in bearing faults are shown in the Fig.~\ref{fig:transforms}.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/stft-spectrogram-sample.png}
+        \caption{STFT + Gaussian window}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/tet-spectrogram-sample.png}
+        \caption{TET}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/wt-spectrogram-sample.png}
+        \caption{CWT + Morlet wavelet}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/sst-spectrogram-sample.png}
+        \caption{SST}
+    \end{subfigure}
+    \caption{Comparison of time-frequency transform spectrograms~\cite{yu_concentrated_2020}}
+    \label{fig:transforms}
+\end{figure}
+
+The dyadic filter bank is another signal decomposition technique that generates subbands on multiple granularity levels.
+The practical realization of the multi-scale description is \textbf{Discrete Wavelet Transform} (DWT).
+The DWT behaves as a quadrature mirror filter and splits waveform using a wavelet filter to detail coefficients (D1) and approximation coefficients (A1) (Fig.~\ref{fig:dwt-filter-bank})~\cite{nandi_condition_2019}.
+Low-pass filter $h(k)$ creates approximation coefficients further decomposed in the successive levels.
+Detail coefficients represent the result of the high-pass filter $g(k) = (-1)^k h(1 - k)$ after decimation by the factor of 2.
+
+The maximum depth of the decomposition tree is $\log_2{n}$ where $n$ is the number of input samples.
+Energy, energy ratio, and entropy are prevalent features that succinctly encode the wavelet coefficients.
+Otherwise, the additional extracted levels raise the total number of data dimensions.
+
+In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provided features combined from approximation (cA5) and detail coefficients (cD1, \dots, cD5).
+Washing machines belonged to three categories: no fault, electric motor clamping screws problem, and a loose or broken counterweight.
+Extracted measures were sample mean and sample variances over autocorrelation functions of coefficients (AcD$n$) and smoothed coefficients cD1, cD2 by moving average filter~\cite{goumas_classification_2002}.
+
+\textbf{Wavelet Packet Decomposition} (WPD) applies filters to split detail coefficients identically as approximation ones (Fig.~\ref{fig:wpd-filter-bank}) thus increasing the resolution in the high-frequency bands and providing uniform spectrum partitioning.
+
+\myequations{Wavelet packet coefficient}
+\begin{ceqn}\begin{align}
+ w_{j,n,k} = \langle f, W_{j,k}^n\rangle = \langle f, 2^{j/2} W^n (2^jt-k) \rangle
+\label{equ:wavelet-packet-coefficient}
+\end{align}\end{ceqn}
+
+Each wavelet packet coefficient $w_{j,n,k}$ captures subband frequency content around time instant $2^j k$ (Equation~\ref{equ:wavelet-packet-coefficient})~\cite{yen_wavelet_2000}.
+This measure is an inner product of the source and scaled wavelet packet function.
+The aforementioned feature extraction established in DWT can be applied, for example calculation of the wavelet packet node energy.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/DWT.png}
+        \caption{Discrete wavelet transform}
+        \label{fig:dwt-filter-bank}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/WPD.png}
+        \caption{Wavelet packet decomposition}
+        \label{fig:wpd-filter-bank}
+    \end{subfigure}
+    \caption{Dyadic filter banks for discrete wavelet transform~\cite{nandi_condition_2019}}
+\end{figure}
+
+The wavelet packet energy ratio for weak feature extraction has been incorporated into the method of multiple frequency bands demodulation (MFBD).
+The highest $n$ energy coefficients are selected out of 8 narrow frequency bands to subsequently affect the principal components.
+Demodulation principle for the frequency bandwidth prescribes $n$ to satisfy condition: $1\;/\;2^n > f_{\mathrm{modulation}}\;/\;f_s$.
+The first few eigenvectors explaining together more than 80\% of energy are retained to reconstruct the signal with Fourier transform and retain the weak fault components~\cite{song_mfbd_2021}.
+
+Tool wear diagnosis based on acoustic emission (AE) signal considers \emph{wavelet packet energy} in bands $E_{8}$, $E_{10}$, $E_{12}$, \emph{energy ratios} $P_{8}$, $P_{13}$, and \emph{energy entropy} as having high correlation ($|r| > 0.8$) with the band saw flank face width.
+The acoustic signal is decomposed into three layers using Daubechies db3 wavelet.
+The bottom layer contains bands numbered 7 through 14, each with a bandwidth of 62.5 kHz, because of the 1 MHz sampling frequency.
+The feature vector constructed in the article includes other statistical metrics out of power spectral density that has reached a notable correlation with evolving wear.
+The statistics are \emph{skewness}, \emph{kurtosis}, \emph{shape factor}, and \emph{centroid frequency}~\cite{zhuo_research_2022}.
+
+Discrete wavelet transform and wavelet packets partition the spectrum into predefined frequency bands that do not always adequately capture individual elementary oscillations.
+Adaptive spectral segmentation is needed to extract separate intrinsic mode functions (IMF).
+
+\textbf{Empirical Wavelet Transform} (EWT) constructs adaptive bandpass filters with Meyer wavelet.
+The scaling function $\hat{\phi_n}$ and wavelet function are defined according to equations (\ref{equ:ewt-scaling}) and (\ref{equ:ewt-wavelet}) respectively.
+The inner product of the signal with the scaling function obtains the approximation coefficients and the inner product with the wavelet function results in detail coefficients.
+
+\myequations{Empirical scaling function}
+\begin{ceqn}\begin{align}
+\hat{\phi_n}(\omega) = 
+\begin{cases}
+1       & \text{if } |\omega| \leq \omega_n - \tau_n \\
+\cos\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_n}(|\omega| - \omega_n + \tau_n)\right)\right]  &  \text{if } \omega_n  - \tau_n \leq |\omega| \leq \omega_n + \tau_n \\
+0       & \text{otherwise }
+\end{cases}
+\label{equ:ewt-scaling}
+\end{align}\end{ceqn}
+
+\myequations{Empirical wavelet function}
+\begin{ceqn}\begin{align}
+\hat{\psi_n}(\omega) = 
+\begin{cases}
+1       & \text{if } \omega_n + \tau_n \leq |\omega| \leq \omega_{n+1} - \tau_{n+1} \\
+\cos\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_{n+1}}(|\omega| - \omega_{n+1} + \tau_{n+1})\right)\right] & \text{if } \omega_{n+1} - \tau_{n+1} \leq |\omega| \leq \omega_{n+1} + \tau_{n+1} \\
+\sin\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_n}(|\omega| - \omega_n + \tau_n)\right)\right] & \text{if }\omega_n - \tau_n \leq |\omega| \leq \omega_{n} + \tau_{n} \\
+0       & \text{otherwise }
+\end{cases}
+\label{equ:ewt-wavelet}
+\end{align}\end{ceqn}
+
+The normalized frequency axis in range $\omega \in [0, \pi]$ is divided by split points $\omega_0, \dots, \omega_N$ where $\omega_n = f_n \cdot 2 \pi\;/\;f_s$ (Fig.~\ref{fig:ewt-spectrum-segmentation}).
+Each segment is bounded between $[\omega_{n-1}, \omega_n]$ with transition phase of width $2\tau_n$ and polynomial transition function $\beta(x)$.
+A tight frame set of empirical wavelets is built by setting the transition phase proportional to the band boundary: $\tau_n = \lambda \omega_n$, and proportional constant must obey constrain: $\lambda = \min\left(\frac{\omega_{n+1} - \omega_n}{\omega_{n+1} + \omega_n}\right)$.
+The $N$ boundaries defining different portions of the Fourier spectrum are placed at the center between two consecutive local maxima~\cite{gilles_empirical_2013}.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.9\textwidth]{assets/EWT.png}
+    \caption{Empirical wavelet segmentation of Fourier spectrum~\cite{gilles_empirical_2013}}
+    \label{fig:ewt-spectrum-segmentation}
+\end{figure}
+
+The drawback of EWT is improper segmentation in noisy and non-stationary signals producing too many uninformative partitions of the spectrum.
+The solutions we discuss fall into two groups that apply improvements before or after the wavelet transformation step.
+
+Refinements acting in the onset as preparation before wavelet processing create an envelope curve in the frequency domain and attempts to eliminate supposed interference.
+
+A combination of \textbf{Maximum Correlated Kurtosis Deconvolution} and improved EWT (MKCD-EWT) favors periodic impacts by dynamically constructing an optimal FIR filter that maximizes the correlation kurtosis of the signal.
+The envelope curve smooths of the amplitude spectrum by linear interpolation (Fig.~\ref{fig:mkcd-ewt-segmentation}).
+The threshold accounting for desired SNR modifies the envelope when more than $n$ components are discovered ($A_h$ is maximal amplitude and $A_l$ is minimal amplitude): $\lambda = A_l + \frac{C}{\mathrm{SNR}}(A_h - A_l)$.
+\emph{Squared envelope spectrum} and \emph{Teager energy operator spectrum} are computed as fault features for the IMF with highest kurtosis~\cite{li_fault_2019}.
+
+The segmentation boundaries detection can be accomplished also on the spectral envelope consisting of \textbf{Piecewise Cubic Hermite Interpolating Polynomial} (PCHIP-EWT) instead of scanning the Fourier spectrum directly (Fig.~\ref{fig:pchip-ewt-segmentation}).
+Divisions of the upper cut-off frequency are kept if local power indicates a subband with useful information ($p_i(f) \geq \lambda$)  as in the case of abrupt level change.
+Local power is the ratio of $n$th local envelope maximum and difference of indexes of its adjacent local minima:  $p_i(f) = K_{max(i)(f)} \;/\;\left(f_{k_{min(i+1)}} - f_{k_{min(i)}}\right)$.
+The best $\lambda$ is set experimentally~\cite{zhuang_improved_2020}.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/MKCD-EWT.png}
+        \caption{MKCD-EWT~\cite{li_fault_2019}}
+        \label{fig:mkcd-ewt-segmentation}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/PCHIP-EWT.png}
+        \caption{PCHIP-EWT~\cite{zhuang_improved_2020}}
+        \label{fig:pchip-ewt-segmentation}
+    \end{subfigure}
+    \caption{Illustration of improved EWT spectral segmentations}
+\end{figure}
+
+Alternatively, the central frequencies of bands containing the most unevenness measured by negentropy are picked after the EWT processing passed.
+The filter bank is then reconstructed accordingly.
+`Negentropy measures the inclination of a system to increase its level of organization'~\cite{avoci_spectral_2020}.
+The larger \emph{spectral negentropy} (Equation~\ref{equ:spectral-negentropy}) suggests more fault-induced impulses.
+$E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
+
+\myequations{Spectral negentropy}
+\begin{ceqn}\begin{align}
+\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}} \cdot \ln\left(\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}\right)
+\label{equ:spectral-negentropy}
+\end{align}\end{ceqn}
+
+In \textbf{time-frequency domain scanning empirical spectral negentropy} method (T-FSESNE) the scanning EWT filter establishes the empirical mode components $X_i(t)$.
+The central frequencies $f_{cj}$ are retained in resonance bands where the frequency-domain spectrum negentropy (FSNE) is greater than mean $\overline{\Delta I_E}$.
+The optimal bandwidth for each component is searched among the set of incrementally expanding regions fixed at $f_{cj}$.
+The interval with the largest time-domain spectrum negentropy (TSNE) is selected to restrict the bounds of the mode $(f_{cj}, B_{wk})$~\cite{yonggang_time_2020}.
+
+The following scheme termed \textbf{adaptive and fast empirical wavelet transform} (AFEWT) calculates spectral negentropy of key functions $K'_i(f)$.
+The spectral section with the highest entropy is assumed to contribute the most to the rolling bearing fault.
+First, the Fourier transform of the spectrum establishes the key function $K(f)$.
+This function is analogous to the cepstrum.
+The leftmost ridge in the $K(f)$ plot is transformed using inverse FFT to attain trend spectrum $T(f)$.
+Finally, the array of local minima points in the trend spectrum bound frequency bands whose Fourier transform produces key functions $K'_i(f)$~\cite{xu_adaptive_2019}.
+
+The inspiration for filtering with adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
+This procedure locates local maxima and minima in the time waveform that are interpolated with cubic splines to form signal envelopes.
+The average of the upper and lower envelope is repeatedly subtracted from the residuals recovering the higher order and lower frequency IMFs~\cite{wang_computational_2014}.
+
+The EMD is not recommended for practical applications because it suffers from mode mixing problems and lacks rigid theoretical foundations.
+Many improvements based on the mode sifting process, such as Local Mean Decomposition (LMD), Ensemble Empirical Mode Decomposition (EEMD), Concealed Component Decomposition (CCD)~\cite{tiwari_novel_2021}, and Empirical Wavelet Transform, have been devised as being capable of estimating more reasonable modes.
+
+The time-frequency representation offers plenty of features depending on the choice of spectral transformation.
+We have reviewed Short-time Fourier transform, Continuous Wavelet transform, Synchrosqueezing transform, Discrete Wavelet transform, Wavelet packet decomposition, Empirical Wavelet transform, and operators of negentropy, TKEO, and TEO.
+
+\subsection{Feature transformation}
+Numeric features from the feature extraction phase have non-normal distributions and span the range of scales.
+Broad differences among features skew the spread in the particular axis.
+Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}.
+The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.
+
+\myequations{Min-max feature scaling}
+\begin{ceqn}\begin{align}
+\widetilde{x} = \frac{x - \min(x)}{\max(x) - \min(x)}
+\label{equ:min-max-scaler}
+\end{align}\end{ceqn}
+
+\myequations{Feature standardization}
+\begin{ceqn}\begin{align}
+\widetilde{x} = \frac{x - \bar{x}}{\sigma_x}
+\label{equ:standardization-scaler}
+\end{align}\end{ceqn}
+
+Feature normalization most often takes two forms.
+\textbf{Min-max scaling} changes original range of values into interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
+\textbf{Standardization} (Equation~\ref{equ:standardization-scaler}) constrains the mean of the variable to 0 with a variance of 1~\cite{zheng_feature_2018}.
+
+Highly correlated features generated from a relatively small original column space are redundant as they do not provide any additional information for diagnostics.
+\textbf{Principal Component Analysis} (PCA) solves this problem by projecting potentially linearly dependant features into a new feature space where the incoming information is preserved in a smaller number of features~\cite{zheng_feature_2018}.
+The threshold of how many principal components are picked depends on the amount of explained variance and desired quantity of data reduction.
+
+\myequations{Singular Value Decomposition}
+\begin{ceqn}\begin{align}
+\mathbf{C} = \mathbf{U \Sigma V^T}
+\label{equ:svd}
+\end{align}\end{ceqn}
+
+PCA consists of taking the Singular Value Decomposition (SVD) (Equation~\ref{equ:svd}) of the mean-centered input matrix.
+The disadvantage of this method is the loss of explainability in transformed space though it generally outperforms the model working with hand-crafted features~\cite{brito_fault_2021}.
+The signal samples can be processed directly by PCA without going through an intermediate step of calculating statistical measures.
+
+\subsection{Feature selection}
+Not all features contribute to the model's discriminatory power with an even share.
+A certain subset can reach better results than other substitute options.
+The \emph{filtering methods} of feature selection rank the predictors in order of their importance for the problem at hand, or they separate the group of predictors that achieve the top modeling accuracies in unison~\cite{johnson_feature_2019}.
+
+Still, the features can be chosen by \emph{embedded methods} intrinsically as a part of a model or else in \emph{wrapper methods} by machine learning search algorithm at a serious computational expense.
+However, we will focus next only on filtering methods.
+
+The general steps in selecting the adequate predictors is outlined next~\cite{nandi_condition_2019}:
+\begin{enumerate}
+    \itemsep0pt
+    \item \textbf{Subset generation} - sets of features are generated in different search directions and with various strategies.
+Attributes are either appended to an empty set or pruned away from a universal set, sequentially or randomly.
+    \item \textbf{Subset evaluation} - comparison of subset quality is assessed with relevance measure some of which are discussed below.
+    \item \textbf{Stopping criteria} - search is exhausted when the specified number of features has been found, subset metrics cannot be improved further, or satisfactory model performance is achieved.
+Subset generation and evaluation can be performed multiple times until the stopping criteria are met.
+    \item \textbf{Validation} - resulting subset is tested for the specific model on synthetic and real-world datasets against well-known results. 
+\end{enumerate}
+
+Filter-based feature selection is preprocessing step independent of model choice with small computational requirements.
+Measures of information, correlation, similarity, and interdependence output the relevancy rating.
+Predictors are rated individually or in interacting congregations.
+
+Most of the scores are based on supervised learning, so they expect true class labels to apportion the measurements respectively.
+After the scores are assigned to the first $n$ features, those below a threshold are removed.
+
+The frequently used scores upon which the feature relevance is ordered are~\cite{nandi_condition_2019}: 
 \begin{itemize}
-\item Energy
-\item Spectral negentropy
-	% Spectral negentropy and kurtogram performance comparison for bearing fault diagnosis
-	\cite{avoci_spectral_2020}
-\item TKEO - Teager-Kaiser energy operator
-	%Application of Teager–Kaiser Energy Operator in the Early Fault Diagnosis of Rolling Bearings
-	\cite{shi_application_2022}
+\item \textbf{Variance threshold} - removes low-variance features below set threshold.
+\item \textbf{Pearson correlation} - expresses linear relationship between class label $c$ and features $f_i$.
+Attributes are ranked in descending order according to the absolute value of their correlation coefficient from zero upwards, i.
+e.
+we seek the highest correlations to the class label.
+\myequations{Pearson correlation coefficient}
+\begin{ceqn}\begin{align}
+r(i) = \frac{\mathrm{cov}(f_i, c)}{\sqrt{\mathrm{var}(f_i) \cdot \mathrm{var}(c)}}
+\end{align}\end{ceqn}
+
+\item \textbf{Fisher score} - measures the difference among the means of the classes.
+It is interchangeable with ANOVA F-value, but it is evaluated for each feature $X^j$ separately.
+Ideally, the features in the subset have large distances between samples of various classes in $C$ and distances within a class are the smallest possible.
+In the formula (\ref{equ:fisher-score}), $n_j$ is the sample size of $j$th feature, $\mu^j$ is its sample mean, and $\mu$ is the overall mean.
+
+\myequations{Fisher score}
+\begin{ceqn}\begin{align}
+\mathrm{FS}(X^j) = \frac{\sum_{i=1}^{C} n_i(\mu_i^j - \mu^i)^2}{\sum_{i=1}^{C} n_i (\sigma_i^j)^2}
+\label{equ:fisher-score}
+\end{align}\end{ceqn}
+
+\item \textbf{Mutal information} - quantifies the dependence among features, or between features and class labels.
+It is almost identical to Information Gain.
+The probability distribution proximity of variables derives from relative entropy known as the Kullback-Leibler distance.
+Probabilities $P(x)$, $P(y)$, $P(x, y)$ are estimated in the contingency table from event occurrence count to all sample population $|x|\;/\;N$.
+Joint probability $P(x, y)$ represents samples of feature $x$ simultaneously in class $y$.
+
+\myequations{Mutal information}
+\begin{ceqn}\begin{align}
+\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
+\end{align}\end{ceqn}
 \end{itemize}
 
-\paragraph{Wavelet signal decompositions}
-
-\begin{itemize}
-\item CWT-SST - Synchrosqueezing Wavelet Transform
-	% The fast continuous wavelet transformation (fCWT) for real-time, high-quality, noise-resistant time–frequency analysis
-	\cite{arts_fast_2022}
-	% A Concentrated Time–Frequency Analysis Tool for Bearing Fault Diagnosis
-	\cite{yu_concentrated_2020}
-	% Applications of the synchrosqueezing transform in seismic time-frequency analysis
-	\cite{herrera_applications_2014}
-
-\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
-	% Wavelet Packet Feature Extraction for Vibration Monitoring
-	\cite{yen_wavelet_2000}
-	% A wavelet approach to dimension reduction and classiﬁcation of hyperspectral data
-	\cite{wickmann_wavelet_2007}
-	% The MFBD: a novel weak features extraction method for rotating machinery
-	\cite{song_mfbd_2021}
-
-\item EWT - Empirical Wavelet Transform - (Meyer wavelet)
-	% Empirical Wavelet Transform - Gilles
-	% On the computational complexity of the empirical mode decomposition algorithm
-	\cite{wang_computational_2014}
-	% Novel self-adaptive vibration signal analysis: Concealed component decomposition and its application in bearing fault diagnosis
-	\cite{tiwari_novel_2021}
-	% The MFBD: a novel weak features extraction method for rotating machinery
-	\cite{song_mfbd_2021}
-	% Fault Feature Extraction and Enhancement of Rolling Element Bearings Based on Maximum Correlated Kurtosis Deconvolution and Improved Empirical Wavelet Transform
-	\cite{li_fault_2019}
-	% An Improved Empirical Wavelet Transform for Noisy and Non-Stationary Signal Processing
-	\cite{zhuang_improved_2020}
-	% Time and frequency domain scanning fault diagnosis method based on spectral negentropy and its application
-	\cite{yonggang_time_2020}
-	% An Adaptive Spectrum Segmentation Method to Optimize Empirical Wavelet Transform for Rolling Bearings Fault Diagnosis
-	\cite{xu_adaptive_2019}
-	% Improved empirical wavelet transform (EWT) and its application in non‑stationary vibration signal of transformer
-	\cite{ni_improved_2022}
-\end{itemize}
-
-\subsection{Feature transformation}
-\cite{zheng_feature_2018}
-
-\subsubsection{Normalization}
- (min-max, standardize)
-
-\subsubsection{Box-Cox transform}
-
-to normal distribution
-\begin{ceqn}\begin{align}
-\widetilde{x} =
-\begin{cases}
-\frac{x^\lambda - 1}{\lambda} \quad \mathrm{if} \;\lambda \neq 0, \\\\ 
-ln(x)\quad \mathrm{if}\;\lambda = 0
-\end{cases}
-\label{equ:box-cox-transform}
-\end{align}\end{ceqn}
-
-\subsubsection{Principal Component Analysis}
-%  (PCA)
-% \cite{brito_fault_2021}
-
-\subsection{Feature selection}
-% Add citations to usage of different features
-Subset generation % p.193
-Subset evaluation
-Stopping criteria
-Validation
-
-\cite{nandi_condition_2019} % p.192
-Filter method - SelectKBest  in evaluation phase
-\begin{itemize}
-\item Variance Threshold
-\item Pearson correlation
-\item ANOVA F-value
-\item Mutal information
-\item Fisher score
-\item Spectral feature selection algorithm (SPEC)
-\end{itemize}
+Multiple subsets of predictors produced by each evaluation metric can train several variants of a classification model.
+Sets of attributes can be likewise combined into an ensemble by majority voting, taking the best features out of every group.

### 2023-05-23 thesis/chapters/02-analysis-C-diagnostics.tex
The analysis and design before final consultation in DP1

@@
-\section{Diagnostics techniques}
-Idenification of faulty states in data streams in semi-supervised learning
+\section{Diagnostics techniques} \label{section:diagnostics-techniques}
+Fault identification in the rotating machinery is one-class or multi-class classification problem acting in a semi-supervised manner because labels for degraded conditions are scarce in practice.
+The automation goals in monitoring can be broadly categorized as anomaly detection and recognizing the momentary fault type.
 
-% Analysis of different RNN autoencoder variants for time series classification and machine prognostics
-\cite{yu_analysis_2021}
+The guiding principles for algorithm selection are simplicity in terms of their straightforward visual explanation for the production managers, and the ability to progressively improve the model on the streaming data to address peculiarities in individual machine constructions.
 
 \subsection{Novelty detection}
-\cite{gervasi_anomaly_2020}
+Anomaly, novelty, or outlier detection determines whether a health status deviates considerably from the baseline profile.
+The expert can then step in and diagnose the machine after the notice.
+Anomaly is a rare observation different from the others raising suspicion that it was created with an unrelated behavior~\cite{aggarwal_outlier_2016}.
+The observations get assigned anomaly scores, and those over the threshold are novelties.
 
-\begin{itemize}
-\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
-	% One-Class Classification with LOF and LOCI: An Empirical Comparison
-	\cite{janssens_one-class_2007}
-	% Designing a Streaming Algorithm for Outlier Detection in Data Mining - An Incremental Approach
-	\cite{yu_designing_2020}
+The measurements coming in the steaming fashion have to be processed in a single pass.
+The detection model must deal with the minimal admissible assumptions about the nature of the input events.
+The outliers are based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
+\bigbreak
 
-\item DenStream (Density based clustering - DBSCAN)
-	% Density-Based Clustering over an Evolving Data Stream with Noise
-	\cite{cao_density-based_2006}
-	% A Modified Approach of OPTICS Algorithm for Data Streams
-	\cite{shukla_modified_2017}
-	% Data Clustering - Algorithms and Applications
-	\cite{aggarwal_data_2014}
-	% State-of-the-art on clustering data streams
-	\cite{ghesmoune_state---art_2016}
-	% Cluster-Reduce: Compressing Sketches for Distributed Data Streams
-	\cite{zhao_cluster-reduce_2021}
+\textbf{DenStream} is a density-based algorithm adapted from DBSCAN to cluster streaming data of arbitrarily shaped groups.
+Samples it includes in the first step into coherent clusters are core data points in each other's neighborhoods.
+Core points have at least \emph{MinPts} ($\mu$) points in their neighborhood of radius \emph{Eps} ($\varepsilon$) units.
+Then non-core points in the proximity area of the core point are attached to the cluster containing it~\cite{aggarwal_data_2014}.
 
-\item Half-space Trees (Isolation forest)
-	% Fast Anomaly Detection for Streaming Data
-	\cite{tan_fast_2011}
-	% Anomaly Detection for Data Streams Based on Isolation Forest using Scikit-multiflow
-	\cite{gervasi_anomaly_2020}
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/DenStream.png}
+    \caption{DenStream~\cite{amini_density_2012}}
+    \label{fig:denstream}
+\end{figure}
 
-\end{itemize}
+In the online maintenance phase, DenStream summarizes the nearby observations into core \emph{micro-clusters} that can be potential or outlier \emph{micro-clusters} (Fig.~\ref{fig:denstream})~\cite{ghesmoune_state---art_2016}.
+The (outlier) \emph{o-micro-clusters} can grow into (potential) \emph{p-micro-clusters} when they encompass $\beta \mu$ points.
+The outliers are discounted after some time in accordance to the decay function: $f(t) = 2^{-\lambda t}$ or below lower weight limit $\xi$.
+The on-demand offline stage runs DBSCAN over the approximate representation in micro-clusters to deliver final apportionment~\cite{cao_density-based_2006}.
+\bigbreak
+
+\textbf{Half-Space Tree} (HS-Tree) stands upon the concept of Isolation forest.
+It assumes that random splitting of each axis in the feature space will isolate outliers to their separate divisions sooner than non-deviant observations~\cite{gervasi_anomaly_2020,torres_automatic_2022}.
+This ensemble of trees is better suited for batch setting.
+HS-Tree stands out in adapting to changing streams because it is trained solely on normal data, requires constant memory, and is faster than density-based methods~\cite{tan_fast_2011}.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/HS-Tree.png}
+    \caption{Half-space tree~\cite{tan_fast_2011}}
+\end{figure}
+
+A full binary tree is built before the novelty detection begins by splitting tree nodes along the divisions in the randomly chosen perpendicular planes.
+The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and link to both child nodes~\cite{tan_fast_2011}.
+
+The anomaly profile in the latest window is always compared to the predecessor reference window.
+After the latest window is filled up it replaces the reference window.
+It suffices to use a window size of 250 and 25 tree ensemble~\cite{tan_fast_2011}.
 
 \subsection{Classification}
-\begin{itemize}
-\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Euclidian Mahalanobis distance /  RBF similarity
+Accurate multi-class classification of machine fault causes out of the characteristics of known ones is a much more difficult task than novelty detection.
+Universal enough fault baseline has to be recorded and transformed into feature space.
+Interactions among fault manifestations have to be accounted for.
+We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}.
+So far, solutions seem not production ready.
+Therefore, we opt to use a more rudimentary model.
+\bigbreak
 
-% Review of Artificial Intelligence-based Bearing Vibration Monitoring
-\cite{sheng_review_2020}
-% Semi-Supervised Learning on Data Streams via Temporal Label Propagation
-\cite{wagner_semi-supervised_2018}
-% Minimum covariance determinant and extensions
-\cite{hubert_minimum_2018}
-\end{itemize}
+\textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:knn}).
+This means it can work in the semi-supervised environment because it can infer labels just from knowing a few annotations.
 
-% Feature-based performance of SVM and KNN classifiers for diagnosis of rolling element bearing faults
-\cite{jamil_feature-based_2021}
-% Classification of washing machines vibration signals using discrete wavelet analysis for feature extraction
-\cite{goumas_classification_2002}
-% Semi-Supervised Learning
-\cite{chapelle_semi-supervised_2006}
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/kNN.png}
+        \caption{kNN with k = 5}
+        \label{fig:knn}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/M-tree.png}
+        \caption{M-tree data structure}
+        \label{fig:m-tree}
+    \end{subfigure}
+    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
+\end{figure}
 
-% A Novel Online Machine Learning Approach for Real-Time Condition Monitoring of Rotating Machines
-\cite{maurya_condition-based_2021}
+The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{RBF kernel} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}.
+The demanding neighborhood queries are sped up by a Metric search tree data structure such as \emph{M-Tree} (Fig.~\ref{fig:m-tree}).
+The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
+
+\begin{table}[ht]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
+Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
+Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
+Radial basis function & $ \exp\left(-\frac{\lVert \mathbf{x} - \mathbf{y} \rVert^2}{t}\right) $ \\ \hline
+\end{tabular}
+\caption{Distance metrics for kNN}
+\label{tab:knn-distance}
+\end{table}
+
+Nearest-neighbour classifier has been successfully applied in machinery fault diagnostics.
+On the CWRU bearing dataset, the kNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - kNN 91.2\%, SVM 88.8\%, and frequency domain features - kNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
+
+Comparison of kNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
+Best accuracies were reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric.
+The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
+Despite kNN lagging in accuracy, we have to keep in mind annotations for faults were complete and machine learning was not tested in a streaming context.

### 2023-05-23 thesis/chapters/02-analysis-D-datasets.tex
The analysis and design before final consultation in DP1

@@
-\section{Evaluation datasets}
+\section{Evaluation datasets} \label{section:evaluation-datasets}
 The experimentally designed features' relevancy is first proven in comparison to comprehensive benchmark datasets.
@@
 \cite{ribeiro_rotating_2017}.
-The datasets listed below are also publically available in Comma-Separated Values files online.
+The datasets listed below are also publically available online in Comma-Separated Values files.
 
-\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearings abnormalities.\emph{CWRU dataset} focuses solely on faults in ball bearings.
+\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearings abnormalities.
+\emph{CWRU dataset} focuses solely on faults in ball bearings.
 Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during revolution speed up.
@@
 \item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight adding to 333 mass unbalance loads. 
-\item \textbf{Vertical misalignement} set is comprised of 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
-\item \textbf{Horizontal misalignement} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
-\item \textbf{Bearing faults} are unnoticable without unbalance.
+\item \textbf{Vertical misalignment} set is comprised of 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
+\item \textbf{Horizontal misalignment} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
+\item \textbf{Bearing faults} are unnoticeable without unbalance.
 Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect.
@@
 The duration of the time series is varied from 5 to 40 seconds.
-Drive end and fan end bearings signals are measured in each experiment sometimes accelerometer was mounted on the supporting base plate.
+Drive end and fan end bearings signals are measured in each experiment.
+Accelerometer was sometimes mounted on the supporting base plate.
 
-\subsection{Unbalance on the rotating shaft}
+\subsection{Unbalance of the rotating shaft}
 Unbalance Detection of a Rotating Shaft\footnote{\url{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}} is a Kaggle dataset that simulates 4 different unbalance strengths.

### 2023-05-23 thesis/chapters/03-design.tex
The analysis and design before final consultation in DP1

@@
-\chapter{Design}
+\chapter{Design} \label{section:design}
+In the spirit of an extensive overview of standardized procedures of industrial vibration acquisition and monitoring, the methods in feature selection, feature selection, and machine diagnostics from vibration signals, we propose a preliminary design of elements in the sensor network capable of discriminating machinery faults.
 
-\section{Research questions}
+\section{Preparatory exploration}
+The wood processing factory we plan to collaborate with has to choose machines that are worthy of condition monitoring.
+In the meantime, the data processing pipeline will be put together in Python language and packages for scientific computing.
+The pipeline will consist of the following stages.
+
 \begin{enumerate}
-\item \emph{Which time-frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?}
-\item \emph{What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?}
-\item \emph{How can the machinery faults be continuously identified based on collected events?}
+    \itemsep0pt
+    \item Detrending
+    \item Adaptive noise cancellation of the background interference
+    \item Vector of all features
+    \begin{itemize}
+        \itemsep0pt
+        \item Time domain: statistical measures (Tab.~\ref{tab:td-features})
+        \item Frequency domain: PSD estimation with FFT and Welch averaging with the resolution of 1 Hz combined with Hann window (Tab.~\ref{tab:fd-features})
+        \item Time-frequency domain: energy and entropy in wavelet coefficients from WPD and EWT filter banks.
+    \end{itemize}
+    \item Feature selection on evaluation datasets and experimental measurements from the factory to prune away irrelevant features with pearson correlation, Fisher score, and mutal information.
+    \item Model evaluation and comparison of novelty detection methods and precision of classification with different sets of predictors.
+The range of optimal parameters will be found for the DenStream ($\mu$, $\epsilon$, $beta$, $\lambda$), Half-Space Trees (window size, ensemble size), and kNN (distance metric, $k$ neighbours).
+Evaluation metrics associated with confusion matrices will be used like accuracy, precision, true positive rate, and false positive rate.
 \end{enumerate}
 
-\section{Infrastructure}
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.9\textwidth]{assets/ml-lifecycle.png}
+\caption{Machine learning lifecycle of feature discovery}
+\end{figure}
+
+\section{Vibration processing}
  \begin{itemize}
+ \itemsep0pt
 \item \textbf{Input:} Samples from three-axis MEMS accelerometers, RPM tachometer, Noise background
-\item \textbf{Output is either:} machine overall status, type of fault,
-\item \textbf{Output for domain expert}: Control chart of trend features
+\item \textbf{Output:} machine health status / type of fault
+\item \textbf{Output on demand}: Control chart of trend features
 \end{itemize}
@@
 \begin{enumerate}
-\item MEMS accelerometers are placed on at least two distinict measurement points in two perpendicular axis and one sensor in base for denoising. Rotational speed is captured at the same time too.
-\item Sensors are triggered in regular intervals (every 15 minutes) to collect sample recording from the band saw.
-\item \textbf{Features} are computed and compared to recent measurements. If there is an statistically significant change the whole summary is send, otherwise keepalive notification is send.
-\item Set of features - at the explatory stage all are computed and stored locally.
-Use features in conjunction with transformation techniques and diagnostics model to reduce the set of features to minimum with the k-fold cross-validation.
-\item Database stores history of measurements
-\item \textbf{Diagnosis panel runs clustering} with introduction of annotations to notify the operator about observed fault and imminent failure of the machine.
+\itemsep0pt
+\item \textbf{Accelerometer} - MEMS accelerometers will be placed on at least two distinct measurement points in two perpendicular axes and one sensor in the machine base for denoising purposes.
+Rotational speed has to be captured at the same time too.
+The sampling frequency shall be around 2 kHz if unbalance and looseness is to be identified, and 10 kHz if bearing faults are also of interest.
+The range of overall rms vibrations is not expected to exceed 30 mm/s according to the vibration severity chart.
+\item \textbf{Acquisition interval} - sensor units will be triggered in regular intervals (every 15 - 60 minutes) to collect vibration recordings from the band saw (or another machine of choice).
+The machine has to be under the same load conditions every time is recording is active.
+\item \textbf{Features} - most relevant features are computed and compared to recent measurements.
+If there is a statistically significant change the whole summary is sent, otherwise keep-alive notification is sent.
+\item \textbf{Wireless network} - earlier design decision has been made to establish wireless connections.
+Therefore, the sensor unit will send data over Wifi (IEEE 802.11), or Thread with IEEE 802.15.4 over 2.4 GHz or 868 MHz frequency bands.
+The application protocol shall be Constrained Application Protocol (CoAP).
+The messages will be encoded by Concise Binary Object Representation (CBOR) or MessagePack which provides the best compression ratio and is widely supported.
+\item \textbf{Time series database} - stores history of trend values.
+Raw vibration measurements can be requested by the operator at any time but are available and delayed according to transfer speeds and other network constraints.
+The promissing database technologies is TimescaleDB.
+\item \textbf{Diagnosis panel} - continuously updates the anomaly detection and classification models with the introduction of annotations to notify the operator about observed faults and imminent failure of the machine.
+The dashboard is provided to display the current status of multiple machines.
 \end{enumerate}
+
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\textwidth]{assets/sensor-network.png}
+\caption{Sensor network components}
+\end{figure}

### 2023-08-02 thesis/chapters/preliminaries/acknowledgments.tex
Minor changes in template

% Poďakovanie
\thispagestyle{empty}
\vspace*{\fill}

\settowidth\longest{\itshape We must know. We will know.}
\centering
\parbox{\longest}{
  \hrulefill\hspace{0.2cm} \decofourleft\decofourright \hspace{0.2cm} \hrulefill\par
  \raggedright{
  \itshape
  	We must know. We will know.\par
  }   
  \raggedleft{--- David Hilbert}\par
  \hrulefill\hspace{0.2cm} \decofourleft\decofourright\hspace{0.2cm} \hrulefill\par
}

\vspace*{\fill}
\section*{Acknowledgement}

\vspace{3cm}

### 2023-09-29 thesis/chapters/02-analysis-B-features.tex
Minor changes in template
Refactor MAFAULDA EDA and add experimental sampler for beaglebone

@@
 \myequations{DC blocker IIR filter of 1st order}
-\begin{equation} \label{equ:iir-dc-blocker}
+\begin{ceqn}\begin{align} \label{equ:iir-dc-blocker}
 y_k = (1 - \frac{\omega}{2}) \cdot (x_k  -  x_{k - 1}) + (1 - \omega) \cdot y_{k - 1}; \quad \omega = 2\pi \cdot \frac{f_{3dB}}{f_s}
-\end{equation}
+\end{align}\end{ceqn}
 
@@
 All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence.
-In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x{i+1}$.
+In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
 The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.

### 2023-09-29 jupyter/beaglebone-adc-sampler.c

@@ -1,0 +1,124 @@
+/*
+ * ssh 192.168.7.2 -l debian
+ * gcc sampler.c -o sampler
+ * sudo nice -n -20 ./sampler out.tsv
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <signal.h>
+#include <pthread.h>
+#include <string.h>
+#include <unistd.h>
+#include <fcntl.h>
+#include <sys/time.h>
+#include <sys/timerfd.h>
+
+/*
+ * https://www.analog.com/en/products/adxl335.html
+low-pass filtering for antialiasing and noise reduction.
+Bandwidth (Hz) Capacitor (μF)
+    1 4.7
+    10 0.47
+    50 0.10
+    100 0.05
+    200 0.027
+    500 0.01
+*/
+// One second
+// #define PERIOD_NS   1000000
+
+// ODR = 500 Hz
+// Sampling frequency = 2000 Hz
+#define PERIOD_NS           500
+#define ANALOG_IN_PATH      "/sys/bus/iio/devices/iio:device0/"
+#define AIN_CH              3
+#define AIN0                ANALOG_IN_PATH "in_voltage0_raw"
+#define AIN1                ANALOG_IN_PATH "in_voltage1_raw"
+#define AIN2                ANALOG_IN_PATH "in_voltage2_raw"
+#define BUF_SIZE            8192
+
+
+int make_periodic(unsigned int period)
+{
+    int fd = timerfd_create(CLOCK_REALTIME, 0);
+    if (fd == -1)
+        return fd;
+
+    unsigned int sec = period / 1000000;
+    unsigned int ns = (period - (sec * 1000000)) * 1000;
+
+    struct itimerspec itval;
+    itval.it_interval.tv_sec = sec;
+    itval.it_interval.tv_nsec = ns;
+    itval.it_value.tv_sec = sec;
+    itval.it_value.tv_nsec = ns;
+
+    timerfd_settime(fd, 0, &itval, NULL);
+    return fd;
+}
+
+void wait_period(int timer)
+{
+    unsigned long long missed;
+
+    int ret =  read(timer, &missed, sizeof(missed));
+    if (ret == -1) {
+        perror("read timer");
+        return;
+    }
+}
+
+
+volatile sig_atomic_t done = 0;
+
+void term(int signum)
+{
+   done = 1;
+}
+
+int main(int argc, char* argv[])
+{
+    struct sigaction action;
[…]

### 2023-09-29 jupyter/mafaulda.py

@@ -1,0 +1,253 @@
+import numpy as np
+import pandas as pd
+import seaborn as sns
+import statsmodels.api as sm
+from scipy.stats import skew, kurtosis, kstest
+from scipy.signal import welch
+from scipy.fft import rfft
+from scipy.signal import butter, filtfilt, find_peaks
+from tqdm.notebook import tqdm
+import matplotlib.pyplot as plt
+
+from multiprocessing.pool import ThreadPool
+
+FS_HZ = 50000
+
+
+def import_files(zip_file, file_list, func):
+    pool = ThreadPool(processes=4)
+    
+    return pd.concat([
+        pool.apply_async(func, (zip_file, name, )).get()
+        for name in tqdm(file_list)
+    ])
+
+def normality_tests(ts, columns=None):
+    columns = columns or ['ax', 'ay', 'az', 'bx', 'by', 'bz']
+    figure, axes = plt.subplots(2, 3, figsize=(10, 5))
+
+    for i, col in enumerate(columns):
+        print('Normality test p-value: ', kstest(ts[col], 'norm').pvalue, '(<0.05 is not normal)')
+        sm.qqplot(ts[col], line='45', ax = axes[i // 3, i % 3])
+
+    plt.tight_layout()
+    plt.show()
+
+
+def resolution_calc(fs, window):
+    print('Window size:', window)
+    print('Heinsenberg rectangle')
+    print('Time step:', window / fs * 1000, 'ms')
+    print('Frequency step:', fs / window, 'Hz')
+
+
+def rms(x):
+    return np.sqrt((x ** 2).mean())
+
+
+def get_mafaulda_files(zip_file):
+    filenames = [
+        text_file.filename
+        for text_file in zip_file.infolist()
+        if text_file.filename.endswith('.csv')
+    ]
+    filenames.sort()
+    return filenames
+
+
+def preprocess(ts):
+    return (
+        ts
+        .assign(t = lambda x: x.index * (1 / FS_HZ))
+        .assign(mag_a = lambda x: np.hypot(x.ax, x.ay, x.ay))
+        .assign(mag_b = lambda x: np.hypot(x.bx, x.by, x.by))
+        .assign(rev = lambda x: (x.tachometer - x.shift(-1).tachometer) >= 3)
+        .assign(rpm = lambda x: 60 / (x[x.rev == True].t - x[x.rev == True].shift(1).t))
[…]

### 2023-09-29 jupyter/mat_convert.py

@@ -1,29 +1,0 @@
-import pandas as pd
-import numpy as np
-import scipy.io
-import os
-import re
-
-filenames = [name.split('.')[0] for name in os.listdir('.') if name.endswith('.mat')]
-
-for filename in sorted(filenames):
-    print(filename)
-    mat = scipy.io.loadmat(f'{filename}.mat')
-    columns = [column for column in mat.keys() if not column.startswith('__')]
-
-    records = {}
-    longest = max([len(mat[col].T[0]) for col in columns])
-
-    for col in columns:
-        dt = mat[col].T[0]
-        col_edit = re.sub(r'^X\d+_?', '', col)
-        print(col_edit, len(dt))
-        if len(dt) == 1:
-            records[col_edit] = dt[0]
-        elif len(dt) < longest:
-            records[col_edit] = np.pad(dt, (0, longest - len(dt)))
-        else:
-            records[col_edit] = dt
-
-    x = pd.DataFrame(records)
-    x.to_csv(f"{filename}.csv", index=False)

### 2023-09-29 jupyter/naive.py

@@ -1,29 +1,0 @@
-from skmultiflow.data import SEAGenerator
-from skmultiflow.bayes import NaiveBayes
-
-# Setup a data stream
-stream = SEAGenerator(random_state=1)
-
-# Setup Naive Bayes estimator
-naive_bayes = NaiveBayes()
-
-# Setup variables to control loop and track performance
-n_samples = 0
-correct_cnt = 0
-max_samples = 200
-
-# Train the estimator with the samples provided by the data stream
-
-while n_samples < max_samples and stream.has_more_samples():
-    X, y = stream.next_sample()
-    y_pred = naive_bayes.predict(X)
-
-    if y[0] == y_pred[0]:
-        correct_cnt += 1
-
-    naive_bayes.partial_fit(X, y)
-    n_samples += 1
-
-# Display results
-print('{} samples analyzed.'.format(n_samples))
-print('Naive Bayes accuracy: {}'.format(correct_cnt / n_samples))

### 2023-10-02 thesis/chapters/appendix/B-plan-of-work.tex
The analysis and design before final consultation in DP1
Journal actual work done in the plan of work

@@
  \\ \hline
-  \nth{12} week         & Write up the analysis section about machine learning diagnostics.
+  \nth{12} week         & Write up the analysis section about machine learning diagnostics and consult final choice of methods in the analysis section.
  \\ \hline
@@
 \section{Winter semester - DP2}
+
+\begin{table}[h!]
+\def\arraystretch{1.25}
+\begin{tabular}{|l|p{12cm}|}
+\hline
+\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
+\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
+\\ \hline
+\nth{2} week         &  Arrange collaboration with alternative industry partner.
+Prepare to do list for technical inspection of machinery.
+Put together device (BeagleBone Black + ADXL335) for exploratory measuruments.
+\\ \hline
+\nth{3} week         & Technical inspection of air condition and rotational UPS in data centre of the industry partner. Calculate features from Mafaulda dataset and their storage saving.
+ \\ \hline
+\nth{4} week         & 
+ \\ \hline
+\nth{5} week         & 
+ \\ \hline
+\nth{6} week         & 
+ \\ \hline
+\nth{7} week         &
+ \\ \hline
+ \nth{8} week         & 
+ \\ \hline
+ \nth{9} week         & 
+ \\ \hline
+  \nth{10} week         & 
+ \\ \hline
+  \nth{11} week         & 
+ \\ \hline
+  \nth{12} week         & 
+ \\ \hline
+\end{tabular}
+\end{table}
+
+\clearpage
+\newpage
+
 \begin{table}[h!]
@@
 
+\section{Summer semester - DP3}
+\begin{table}[h!]
+\def\arraystretch{1.25}
+\begin{tabular}{|l|p{12cm}|}
+\hline
+\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
+\nth{1}  - \nth{4} week         & 
+\\ \hline
+\nth{4}  - \nth{8} week         & 
+\\ \hline
+\nth{8} - \nth{12} week         & 
+ \\ \hline
+\end{tabular}
+\end{table}
+
 \clearpage

### 2023-10-12 thesis/chapters/appendix/B-plan-of-work.tex
Revise plan of work

@@
 \nth{2} week         &  Arrange collaboration with alternative industry partner.
-Prepare to do list for technical inspection of machinery.
-Put together device (BeagleBone Black + ADXL335) for exploratory measuruments.
+Prepare checklist for technical inspection of machinery.
+Construct device (BeagleBone Black + ADXL335) for exploratory measurements.
 \\ \hline
-\nth{3} week         & Technical inspection of air condition and rotational UPS in data centre of the industry partner. Calculate features from Mafaulda dataset and their storage saving.
+\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Calculate features from Mafaulda dataset and start feature selection
  \\ \hline
-\nth{4} week         & 
+\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering.
+Feature selection methods comparison on Mafaulda dataset.
  \\ \hline
-\nth{5} week         & 
+\nth{5} week         & Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling.
+Make a plan of measurement and negotiate it with industry partner.
+Feed exporatory dataset into anomaly detection models.
  \\ \hline
@@
 \\ \hline
-\nth{4}  - \nth{8} week         & Design the vibration measurement for woodworking factoring according to technical standards. 
+\nth{4}  - \nth{8} week         & Design the vibration measurement for factory according to technical standards. 
 \\ \hline

### 2023-10-12 recorder/recorder.c
Restructure folders

@@ -1,0 +1,175 @@
+/*
+ * debian:temppwd
+ *
+ * ssh debian@192.168.7.2
+ * gcc sampler.c -o sampler
+ *
+ * sudo nice -n -20 ./sampler out.tsv
+ * scp debian@192.168.7.2:/home/debian/out.tsv out.tsv
+ *
+ * FILE COLUMNS
+ * x[raw]  y[raw]  z[raw]  time_interval[us]
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <signal.h>
+#include <pthread.h>
+#include <string.h>
+#include <unistd.h>
+#include <fcntl.h>
+#include <sys/time.h>
+#include <sys/timerfd.h>
+#include <inttypes.h>
+
+
+#define US_PER_SECOND       1000000
+#define NS_PER_SECOND       1000000000
+
+#define FS_HZ               8000
+#define PERIOD_US           (US_PER_SECOND / (double)FS_HZ)
+
+#define ANALOG_IN_PATH      "/sys/bus/iio/devices/iio:device0"
+#define ANALOG_IN_DEV       "/dev/iio:device0"
+#define AIN_CH              3
+
+#define BUFFER_LENGTH_PATH  ANALOG_IN_PATH "/buffer/length"
+#define BUFFER_ENABLE_PATH  ANALOG_IN_PATH "/buffer/enable"
+#define AIN0                ANALOG_IN_PATH "/scan_elements/in_voltage0_en"
+#define AIN1                ANALOG_IN_PATH "/scan_elements/in_voltage1_en"
+#define AIN2                ANALOG_IN_PATH "/scan_elements/in_voltage2_en"
+#define AIN3                ANALOG_IN_PATH "/scan_elements/in_voltage3_en"
+#define AIN4                ANALOG_IN_PATH "/scan_elements/in_voltage4_en"
+#define AIN5                ANALOG_IN_PATH "/scan_elements/in_voltage5_en"
+#define AIN6                ANALOG_IN_PATH "/scan_elements/in_voltage6_en"
+#define CNT_SAMPLES         100
+#define BUF_SIZE            AIN_CH * CNT_SAMPLES
+
+
+volatile sig_atomic_t done = 0;
+
+void term(int signum)
+{
+   done = 1;
+}
+
+void adc_enable(void)
+{
+    FILE *ain;
+    const char *channels[AIN_CH] = {AIN0, AIN2, AIN6};
+
[…]

### 2023-10-23 thesis/chapters/03-design.tex
Refactor feature selection methods and finish correletion ranking

@@
 \end{figure}
+
+\section{Measurment strategy}
+Describe technical inspection in VNET, a.s. datacentres (DC Digitalis, SHC\rom{2}) from 12th October 2023
+and
+
+HVAC - Air conditioning, Refrigirator
+Devices:
+	- Adiabatic plunger pump: better candidates because of fraquent faults, datacentere is inspected daily and maintaned regulary so it is not that critical, turns off under 26°C to save electricity consumption in winter, we do not have faulty machines for comparision
+
+	- Scroll compressor: example Copeland ZR16M3E-TWD-561 (2900 RPM @ 50 Hz; 9,7 kW (13 HP); 380/420V; 25 A) 3500 RPM @ 60Hz
+
+	Faults (\url{https://www.mdpi.com/1099-4300/17/10/7076})
+	- unbalance of the rotor, fault of the scroll, mechanical assembly loose, bearing loose
+
+	- Fig: insert image of cut of compressor
+	- Fig: insert spectrograms, orbitals from exploratory measurements
+
+- How to obtain dataset (plan had to been aggreed to by datacentre technician)
+ 	- every 2 or 3 weeks (4 - 6 times)
+ 	- 60 - 90 s recordings in each place
+  	- good and bad compressor (4 x top, 4x side, 1x base)
+
+\section{Embedded system for dataset measurement}	
+Functional requirements
+\begin{itemize}
+	\item MCU has interface to accept commands and storage to save measurements
+	\item Driver for accelerometer is build in
+	\item Accelerometer has frequency response at least 500 Hz (FS = min. 3200 Hz)
+\end{itemize}
+Business (management) requirements: because of time constraints before first technical inspection: build from parts already on stock or inexpensive and quickly procurable, driver should be available, easily save massive recordings to persistant storage, extensible platform in case better option would not be avaiable in the future
+
+Hardware parts:
+Faster than target device to enable experimentation, ARM platform
+\begin{itemize}
+	\item Beaglebone Black 
+		(Texas Instruments Sitara AM3358: 1GHz ARM Cortex-A8, 
+		 SDRAM: 512MB DDR3L 800MHZ, 
+		 Onboard Flash: 4GB)
+	\item OS: Debian 10 Kernel 5.10.168-ti-r72
+	\item Accelerometer ADXL335, 3-Axis $\pm$3 g Accelerometer, 
+	      Bandwidths X, Y axes: (0.5 Hz - 1.6 kHz), Z axes: (0.5 Hz - 0.55 kHz)
+	  (via 8 channel 12-bit SAR ADC, 1.8V, 200 MSPS)
+	 \item Later: ADXL345 (SPI, ODR: 3.2 kHz) 
+\end{itemize}
 

### 2023-10-23 thesis/chapters/04-implementation.tex
Refactor feature selection methods and finish correletion ranking

\chapter{Implementation} \label{section:implementation} 
Mafaulda dataset
Jupyter notebook - Python

\section{Feature extraction}
- How looked dataframe for: time frequency, frequency domain, wavelet packet features

\section{Feature selection}
- What are the best features
- Feature normalization
- PCA and inverse transformations

\section{Fault detection models}
- Streaming algorithms: sklearn, river packages
kNN, Half-space tree (vs. Isolation forest),  DenStream (vs. DBSCAN)

### 2023-10-23 thesis/chapters/appendix/B-plan-of-work.tex
Refactor feature selection methods and finish correletion ranking

@@
 \\ \hline
-\nth{2} week         &  Arrange collaboration with alternative industry partner.
-Prepare checklist for technical inspection of machinery.
-Construct device (BeagleBone Black + ADXL335) for exploratory measurements.
+\nth{2} week         &  Arrange collaboration with alternative industry partner. Prepare checklist for technical inspection of machinery. Construct device for exploratory measurements.
 \\ \hline
-\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Calculate features from Mafaulda dataset and start feature selection
+\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction: calculate features from Mafaulda dataset.
  \\ \hline
 \nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering.
-Feature selection methods comparison on Mafaulda dataset.
+Fine tune measurement device.
  \\ \hline
-\nth{5} week         & Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling.
-Make a plan of measurement and negotiate it with industry partner.
-Feed exporatory dataset into anomaly detection models.
+\nth{5} week         &  Feature selection: create procedures to determine sets of best data features in Mafaulda dataset.
  \\ \hline
-\nth{6} week         & 
+\nth{6} week         & Generate comprehensive reports from jupyter notebooks. Mafaulda feature sampling for kNN multiclass classification.
  \\ \hline
-\nth{7} week         &
+\nth{7} week         & ?Consultation with the supervisor ... Feed exporatory dataset into anomaly detection models.
  \\ \hline
@@
  \\ \hline
- \nth{9} week         & 
+ \nth{9} week         & ??Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling. Make a plan of measurement and negotiate it with industry partner.
  \\ \hline
-  \nth{10} week         & 
+  \nth{10} week         & ?Begin writing implementation
  \\ \hline

### 2023-10-23 feature/discovery.py

@@ -13,7 +13,7 @@ from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
 import pywt
 
 import matplotlib.pylab as plt
-import mafaulda
+from feature import mafaulda
 
 
 def features_time_domain(zip_file: ZipFile, filename: str) -> pd.DataFrame:
@@ -251,7 +251,6 @@ def harmonic_series_detection(f: np.array, Pxx: np.array, fs: int, fft_window: i
                 break
 
         if len(series) > 1:
-            print(series, end='\n\n')
             result.append(series)
 
     return result
@@ -374,6 +373,6 @@ def plot_spectral_envelope(dataset, file, axis):
 
     fig, ax = plt.subplots(1, 1, figsize=(20, 5))
     ax.plot(f, Pxx)
-    ax.scatter(f[peaks], Pxx[peaks], color='red')
+    #ax.scatter(f[peaks], Pxx[peaks], color='red')
     ax.plot(f, y_env)
 

### 2023-10-23 feature/selection.py

@@ -1,0 +1,47 @@
+import pandas as pd
+
+
+# Dataset paths and attributes
+TIME_FEATURES_PATH = '../../../datasets/features_data/td_features_no_filter.csv'
+FREQ_FEATURES_PATH = '../../../datasets/features_data/fd_features_no_filter.csv'
+WPD_FEATURES_PATH = '../../../datasets/features_data/wpd_features_no_filter.csv'
+
+TD_COLUMNS = ['mean', 'std', 'skew', 'kurt', 'rms', 'pp', 'crest', 'margin', 'impulse', 'shape']
+FD_COLUMNS = [
+    'centroid', 'std', 'skew', 'kurt', 'roll-off', 'flux_mean', 'flux_std',
+    'noisiness', 'energy', 'entropy', 'negentropy'
+]
+WPD_COLUMNS_EXCLUDE = {
+    'fault', 'severity', 'seq', 'rpm', 'axis', 'feature'
+}
+
+
+def load_time_domain_features(axis):
+    features = pd.read_csv(TIME_FEATURES_PATH)
+    features = features[features['axis'].isin(axis)]
+    features['fault'] = features['fault'].astype('category')
+    return features
+
+
+def load_frequency_domain_features():
+    features = pd.read_csv(FREQ_FEATURES_PATH)
+    features['fault'] = features['fault'].astype('category')
+    features['fft_window_length'] = features['fft_window_length'].astype('category')
+    return features
+
+
+def load_wavelet_domain_features(axis):
+    features = pd.read_csv(WPD_FEATURES_PATH)
+    features['axis'] = features['axis'].astype('category')
+    features['feature'] = features['feature'].astype('category')
+    features['fault'] = features['fault'].astype('category')
+    features = features[features['axis'].isin(axis)]
+    return features
+
+def plot_bar_chart(ax, x, y, title):
+    ax.bar(x, y)
+    ax.grid(True)
+    ax.set_title(title)
+    # Rotate x labels by 45 deg
+    ax.set_xticks(ax.get_xticks())
+    ax.set_xticklabels(ax.get_xticklabels(), rotation=45, ha='right')

### 2023-10-31 thesis/chapters/appendix/B-plan-of-work.tex
Revise plan of work

@@
 \\ \hline
-\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction: calculate features from Mafaulda dataset.
+\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Feature extraction step to calculate features from Mafaulda dataset.
  \\ \hline
@@
  \\ \hline
-\nth{5} week         &  Feature selection: create procedures to determine sets of best data features in Mafaulda dataset.
+\nth{5} week         &  In feature selection use various metrics to determine sets of best data features in Mafaulda dataset.
  \\ \hline
-\nth{6} week         & Generate comprehensive reports from jupyter notebooks. Mafaulda feature sampling for kNN multiclass classification.
+\nth{6} week         & Generate reports from jupyter notebooks. Feature sampling used in kNN multiclass and binary classificator.
  \\ \hline
-\nth{7} week         & ?Consultation with the supervisor ... Feed exporatory dataset into anomaly detection models.
+\nth{7} week         & Explore streaming ML models with Mafaulda dataset. Consultation with the supervisor and status report.
  \\ \hline
- \nth{8} week         & 
+ \nth{8} week         & ?Anomaly detection models evaluation and conclude/gather all the findings.
  \\ \hline

### 2023-11-08 thesis/chapters/02-analysis-B-features.tex
Journal actual work done in the plan of work
Restructure folders
Refactor feature selection methods and finish correletion ranking
Revise analysis chapter and add placeholder sections to be filled

@@
 
+% TODO: add td and fd features from tsfel
 \begin{table}[h]
@@
 \textbf{Feature}            & \textbf{Equation}                                                                    & \textbf{Feature}        & \textbf{Equation}                                                                                                  \\ \hline
-\textit{Standard deviation} & $ \sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{x_i^2} \right)^\frac{1}{2}} $                       \\ \hline
+\textit{Standard deviation} & $ \sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                       \\ \hline
 \textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$ & \textit{Margin factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $                          \\ \hline
 \textit{Kurtosis}           & $ X_{kv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^4}$ & \textit{Impulse factor} & $ X_{if} = \frac{max(|x_i|)}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}} $                                                  \\ \hline
-\textit{Root mean square}   & $ X_{rms} = \left(\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}\right)^\frac{1}{2}$             & \textit{Shape factor}   & $ X_{sf} = \frac{\left( \frac{1}{N} \sum_{i=1}^{N}{x_i^2} \right)^\frac{1}{2}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$ \\ \hline
+\textit{Root mean square}   & $ X_{rms} = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}} $             & \textit{Shape factor}   & $ X_{sf} = \frac{X_{rms}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$ \\ \hline
 \textit{Peak-to-peak}       & $ X_{ppv} = \max(x_i) - \min(x_i) $                                                  & \textit{Maximum}        & $ X_{max} = \max(|x_i|) $                                                                                          \\ \hline
@@
 \begin{ceqn}\begin{align}
-\mathrm{MMS}_{\mathrm{max}} = \mathrm{MMS}_{\mathrm{max|mid}} \\
 \frac{a_{max} - a_{min}}{S_3 - a_{min} \cdot 3} = \frac{a_{mid} - a_{min}}{S_3 - a_{min} \cdot 3}
@@
 \begin{ceqn}\begin{align}
-\mathrm{MMS}_{\mathrm{min}} = \mathrm{MMS}_{\mathrm{min|mid}} \\
 \frac{a_{max} - a_{min}}{a_{max} \cdot 3 - S_3} = \frac{a_{max} - a_{mid}}{a_{max} \cdot 3 - S_3}
@@
 \textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot a(f_i)}}{\sum_{i = 0}^{N - 1}{a(f_i)}}$                   \\ \hline 
-\textit{Spectral roll-off} & $ \sum_{0}^{f_c}a^2(f) = 0.95 \sum_{0}^{f_s / 2}a^2(f)$                                                   \\ \hline
-\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \frac{\sum_k a(t-1, k) \cdot a(t,k)}{\sqrt{\sum_k a(t-1, k)^2} \sqrt{\sum_k a(t, k)^2}}$ \\ \hline 
+\textit{Spectral roll-off} & $ E(f_c) = 0.95 \cdot E(f_s / 2) $                                                   \\ \hline
+\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \mathrm{corr}(A_{t-1}, A_t)$ \\ \hline 
 \textit{Harmonic spectral deviation} & $ X_{\mathrm{HDEV}} = \frac{1}{H}\sum_h(a(h) - \mathrm{SE}(h))$                                          \\ \hline
-\textit{Noisiness}                   & $X_{noise} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} $                             \\ \hline
-\textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| \cdot a^2(h)}{\sum_h a^2(h)}$ \\ \hline
-\textit{Energy}            & $ E = \sum_{i = 0}^{N - 1}|x(t)|^2 $                                                                    \\ \hline \textit{Energy ratio}                & $E_i = \frac{E_i}{\sum_{i = 1}^{N}E_i} $                                                        \\ \hline
+\textit{Noisiness}                   & $X_{noise} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} = \mathrm{SNR}(X) = \mu \;/\; \sigma $                             \\ \hline
+\textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| \cdot a^2(h)}{\sum_h a^2(h)} $ \\ \hline
+\textit{Energy}            & $ E(N) = \sum_{i = 1}^{N} a^2(t) $                                                                    \\ \hline \textit{Energy ratio}                & $E_r = E_i \;/\; \sum_{i = 1}^{N}{E_i} $                                                        \\ \hline
 \textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
@@
 \textbf{Empirical Wavelet Transform} (EWT) constructs adaptive bandpass filters with Meyer wavelet.
-The scaling function $\hat{\phi_n}$ and wavelet function are defined according to equations (\ref{equ:ewt-scaling}) and (\ref{equ:ewt-wavelet}) respectively.
-The inner product of the signal with the scaling function obtains the approximation coefficients and the inner product with the wavelet function results in detail coefficients.
-
-\myequations{Empirical scaling function}
-\begin{ceqn}\begin{align}
-\hat{\phi_n}(\omega) = 
-\begin{cases}
-1       & \text{if } |\omega| \leq \omega_n - \tau_n \\
-\cos\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_n}(|\omega| - \omega_n + \tau_n)\right)\right]  &  \text{if } \omega_n  - \tau_n \leq |\omega| \leq \omega_n + \tau_n \\
-0       & \text{otherwise }
-\end{cases}
-\label{equ:ewt-scaling}
-\end{align}\end{ceqn}
-
-\myequations{Empirical wavelet function}
-\begin{ceqn}\begin{align}
-\hat{\psi_n}(\omega) = 
-\begin{cases}
-1       & \text{if } \omega_n + \tau_n \leq |\omega| \leq \omega_{n+1} - \tau_{n+1} \\
-\cos\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_{n+1}}(|\omega| - \omega_{n+1} + \tau_{n+1})\right)\right] & \text{if } \omega_{n+1} - \tau_{n+1} \leq |\omega| \leq \omega_{n+1} + \tau_{n+1} \\
-\sin\left[\frac{\pi}{2}\cdot \beta\left(\frac{1}{2\tau_n}(|\omega| - \omega_n + \tau_n)\right)\right] & \text{if }\omega_n - \tau_n \leq |\omega| \leq \omega_{n} + \tau_{n} \\
-0       & \text{otherwise }
-\end{cases}
-\label{equ:ewt-wavelet}
-\end{align}\end{ceqn}
+The inner product of the signal with the scaling function $\hat{\phi_n}$ obtains the approximation coefficients and the inner product with the wavelet function results in detail coefficients.
 
@@
 The solutions we discuss fall into two groups that apply improvements before or after the wavelet transformation step.
-
-Refinements acting in the onset as preparation before wavelet processing create an envelope curve in the frequency domain and attempts to eliminate supposed interference.
 
@@
 We have reviewed Short-time Fourier transform, Continuous Wavelet transform, Synchrosqueezing transform, Discrete Wavelet transform, Wavelet packet decomposition, Empirical Wavelet transform, and operators of negentropy, TKEO, and TEO.
+
+% TODO: we did not utilize wavelets as of yet
+% 
+% 
+%
 

### 2023-11-08 thesis/chapters/02-analysis-C-diagnostics.tex
Revise analysis chapter and add placeholder sections to be filled

@@
 The guiding principles for algorithm selection are simplicity in terms of their straightforward visual explanation for the production managers, and the ability to progressively improve the model on the streaming data to address peculiarities in individual machine constructions.
+
+\subsection{Concept drift}
+% TODO: ADWIN (ADaptive WINdowing)
+% Kolmogorov-Smirnov Windowing method for concept drift detection.
 
@@
 \subsection{Classification}
+% TODO: HoeffdingTreeClassifier
+% https://analyticsindiamag.com/a-beginners-guide-to-hoeffding-tree-with-python-implementation/
+% https://www.cms.waikato.ac.nz/~abifet/book/chapter_5.html
+
 Accurate multi-class classification of machine fault causes out of the characteristics of known ones is a much more difficult task than novelty detection.
@@
 
-The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{RBF kernel} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}.
+% TODO: Spatial database
+% TODO: Sliding WIndow-based Nearest Neighbor (SWINN)
+
+The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{Manhatann distance} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}.
 The demanding neighborhood queries are sped up by a Metric search tree data structure such as \emph{M-Tree} (Fig.~\ref{fig:m-tree}).
@@
 \textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
+Manhatann distance	 & $ |x_i - y_i| $													   \\ \hline
 Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
 Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
-Radial basis function & $ \exp\left(-\frac{\lVert \mathbf{x} - \mathbf{y} \rVert^2}{t}\right) $ \\ \hline
 \end{tabular}
@@
 Despite kNN lagging in accuracy, we have to keep in mind annotations for faults were complete and machine learning was not tested in a streaming context.
+
+\subsection{Online model evaluation}
+% TODO

### 2023-11-08 thesis/chapters/03-design.tex
Revise analysis chapter and add placeholder sections to be filled

@@
 \end{figure}
+
+\chapter{ML Pipeline Design}
+
+Mafaulda dataset
+Jupyter notebook - Python
+
+\section{Data labeling and cleaning}
+- Mafaulda labeling and creating subset (RPM range, 4 classes, Anomaly class)
+- Measurement of custom datasets (Schiratech iComox, Beaglebone) - air conditioning, compressor
+
+\section{Feature relevance}
+- supervised - correlation, fisher, mi
+- custom, tsfel, in sensor and in one axis
+- online learning features
+
+\section{Nearest neighbour classifier}
+- kNN (fault and anomaly)
+	- Offine (baseline)
+	- Online (evolution)
+- parameters: k-neigh, distance
+- metrics: accuracy, precision, recall
+
+\section{Clustering}
+- Density based clustering
+	- DBSCAN (all features, PCA, subset of best)
+	- DenStream (all features, subset of best)
+
+\section{Anomaly detection / Decision Trees}
+- Offline (DecisionTree)
+- Online (Hoefing Tree)
+
+\section{Comparision to real data}
+- Can be part of original chapters

### 2023-11-08 thesis/chapters/04-implementation.tex
Revise analysis chapter and add placeholder sections to be filled

@@
 \chapter{Implementation} \label{section:implementation}
-Mafaulda dataset
-Jupyter notebook - Python
-
-\section{Feature extraction}
-- How looked dataframe for: time frequency, frequency domain, wavelet packet features
-
-\section{Feature selection}
-- What are the best features
-- Feature normalization
-- PCA and inverse transformations
-
-\section{Fault detection models}
-- Streaming algorithms: sklearn, river packages
-kNN, Half-space tree (vs. Isolation forest),  DenStream (vs. DBSCAN)

### 2023-11-12 feature/discovery.py
Remove exports and feature selection rework

@@ -1,478 +1,0 @@
-from zipfile import ZipFile
-import numpy as np
-import pandas as pd
-from itertools import pairwise
-from typing import List
-
-from numpy.lib.stride_tricks import sliding_window_view
-from scipy.stats import skew, kurtosis, entropy
-from scipy.signal import welch, windows, find_peaks
-from scipy.interpolate import interp1d
-from scipy.fft import rfft
-
-from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
-import pywt
-import tsfel
-
-import matplotlib.pylab as plt
-from feature import mafaulda
-
-
-def split_dataframe(dataframe: pd.DataFrame, parts: int) -> List[pd.DataFrame]:
-    step = len(dataframe) // parts
-    return [
-        dataframe.iloc[i:i + step].reset_index(drop=True)
-        for i in range(0, len(dataframe), step)
-    ]
-
-
-def features_list():
-    config = tsfel.get_features_by_domain()
-    for domain in config.values():
-        for feature, options in domain.items():
-            if options['n_features'] != 1:
-                options['use'] = 'no'
-    return config
-
-
-def tsfel_features_generate(dataset: ZipFile, filename: str, parts=None) -> pd.DataFrame:
-    print(f'Processing: {filename}')
-
-    conf_extraction = features_list()
-    columns = mafaulda.COLUMNS
-
-    ts = mafaulda.csv_import(dataset, filename)
-    fault, severity, seq = mafaulda.parse_filename(filename)
-    dataframe = [ts] if parts is None else discovery.split_dataframe(ts, parts)
-
-    results = []
-    for i, df in enumerate(dataframe):
-        fv = pd.DataFrame({
-            'fault': [fault],
-            'severity': [severity],
-            'seq': [f'{seq}.part.{i}'],
-            'rpm': [df['rpm'].mean()]
-        })
-
-        for col in columns:
-            features = tsfel.time_series_features_extractor(
-                conf_extraction, df[col], fs=mafaulda.FS_HZ
-            )
-            features.columns = [
-                col + '_' + c.strip('0_').replace(' ', '_').lower()
-                for c in features.columns
-            ]
-            fv = fv.assign(**features)
-        results.append(fv)
-
-    return pd.concat(results).reset_index(drop=True)
-
-
[…]

### 2023-11-12 feature/mafaulda.py

@@ -1,312 +1,0 @@
-import numpy as np
-import pandas as pd
-import seaborn as sns
-import statsmodels.api as sm
-
-from scipy.stats import skew, kurtosis, kstest
-from scipy.signal import welch
-from scipy.fft import rfft
-from scipy.signal import butter, filtfilt, find_peaks
-
-from tqdm.notebook import tqdm
-import matplotlib.pyplot as plt
-from zipfile import ZipFile
-
-from multiprocessing.pool import ThreadPool
-
-FS_HZ = 50000
-DB_REF = 0.000001                                # 1 dB = 1 um/s^2
-COLUMNS = ['ax', 'ay', 'az', 'bx', 'by', 'bz']   # 'mic'
-
-################################# IMPORT ########################################
-
-def parse_filename(filename: str) -> (str, str, str):
-    path = filename.split('/')
-    if path[0].strip() in ('overhang', 'underhang'):
-        fault = f'{path[0]}-{path[1]}'
-        severity = path[2]
-        seq = path[3]
-    elif path[0].strip() == 'normal':
-        fault, severity, seq = path[0], '0', path[1]
-    else:
-        fault, severity, seq = path
-
-    return fault, severity, seq
-
-
-def import_files_split(zip_file, file_list, func, parts, cores=4):
-    pool = ThreadPool(processes=cores)
-    
-    return pd.concat([
-        pool.apply_async(func, (zip_file, name, parts )).get()
-        for name in tqdm(file_list)
-    ])
-
-
-def import_files(zip_file, file_list, func, cores=4):
-    pool = ThreadPool(processes=cores)
-    
-    return pd.concat([
-        pool.apply_async(func, (zip_file, name, )).get()
-        for name in tqdm(file_list)
-    ])
-
-
-def get_mafaulda_files(zip_file):
-    filenames = [
-        text_file.filename
-        for text_file in zip_file.infolist()
-        if text_file.filename.endswith('.csv')
-    ]
-    filenames.sort()
-    return filenames
-
-
-def rpm_calc(tachometer: pd.Series) -> float:
-    t = tachometer.index.to_numpy()
-    y = tachometer.to_numpy()
-    peaks, _ = find_peaks(y, prominence=3, width=50)
-    interval = np.diff(t[peaks]).mean()
-    return 60 / interval
-
-
[…]

### 2023-11-12 feature/selection.py

@@ -1,334 +1,0 @@
-import os.path
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-
-from scipy.stats import pearsonr
-from sklearn.feature_selection import mutual_info_classif, f_classif
-
-from sklearn.compose import ColumnTransformer
-from sklearn.pipeline import Pipeline
-from sklearn.preprocessing import StandardScaler, MinMaxScaler
-
-
-# Dataset paths and attributes
-TIME_FEATURES_PATH = 'td_features.csv'
-FREQ_FEATURES_PATH = 'fd_features.csv'
-TIME_AND_FREQ_FEATURES_PATH = 'time_freq_features.csv'
-WPD_FEATURES_PATH = 'wpd_features.csv'
-TSFEL_FEATURES_PATH = 'tsfel_features.csv'
-
-TIME_FEATURES_PATH_ALL = 'all_td_features.csv'
-FREQ_FEATURES_PATH_ALL = 'all_fd_features.csv'
-WPD_FEATURES_PATH_ALL = 'all_wpd_features.csv'
-TSFEL_FEATURES_PATH_ALL = 'all_tsfel_features.csv'
-
-TD_COLUMNS = ['mean', 'std', 'skew', 'kurt', 'rms', 'pp', 'crest', 'margin', 'impulse', 'shape']
-FD_COLUMNS = [
-    'centroid', 'std', 'skew', 'kurt', 'roll-off', 'flux_mean', 'flux_std',
-    'noisiness', 'energy', 'entropy', 'negentropy'
-]
-WPD_COLUMNS_EXCLUDE = {
-    'fault', 'severity', 'seq', 'rpm', 'axis', 'feature'
-}
-
-FAULT_CLASSES = {'normal': 'N', 'imbalance': 'I', 'horizontal-misalignment': 'HM', 'vertical-misalignment': 'VM'}
-METADATA_COLUMNS = ['fault', 'severity', 'seq', 'rpm']
-METADATA_COLUMNS_ALL = METADATA_COLUMNS + ['severity_class', 'severity_level', 'anomaly']
-
-#########################################################
-def filter_out_metadata_columns(df):
-    return df[df.columns[~df.columns.isin(METADATA_COLUMNS_ALL)]]
-
-
-def remove_column_prefix(df):
-    return df.columns.str.extract(r'\w+_(\w+)')[0]
-
-
-def fd_extract_feature_name(column):
-    return column.str.extract(r'[A-Za-z]+_(.*)_\d+$')[0]
-
-
[…]

### 2023-11-12 notebooks/vibrodiagnostics/discovery.py

@@ -1,0 +1,478 @@
+from zipfile import ZipFile
+import numpy as np
+import pandas as pd
+from itertools import pairwise
+from typing import List
+
+from numpy.lib.stride_tricks import sliding_window_view
+from scipy.stats import skew, kurtosis, entropy
+from scipy.signal import welch, windows, find_peaks
+from scipy.interpolate import interp1d
+from scipy.fft import rfft
+
+from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
+import pywt
+import tsfel
+
+import matplotlib.pylab as plt
+from vibrodiagnostics import mafaulda
+
+
+def split_dataframe(dataframe: pd.DataFrame, parts: int) -> List[pd.DataFrame]:
+    step = len(dataframe) // parts
+    return [
+        dataframe.iloc[i:i + step].reset_index(drop=True)
+        for i in range(0, len(dataframe), step)
+    ]
+
+
+def features_list():
+    config = tsfel.get_features_by_domain()
+    for domain in config.values():
+        for feature, options in domain.items():
+            if options['n_features'] != 1:
+                options['use'] = 'no'
+    return config
+
+
+def tsfel_features_generate(dataset: ZipFile, filename: str, parts=None) -> pd.DataFrame:
+    print(f'Processing: {filename}')
+
+    conf_extraction = features_list()
+    columns = mafaulda.COLUMNS
+
+    ts = mafaulda.csv_import(dataset, filename)
+    fault, severity, seq = mafaulda.parse_filename(filename)
+    dataframe = [ts] if parts is None else discovery.split_dataframe(ts, parts)
+
+    results = []
+    for i, df in enumerate(dataframe):
+        fv = pd.DataFrame({
+            'fault': [fault],
+            'severity': [severity],
+            'seq': [f'{seq}.part.{i}'],
+            'rpm': [df['rpm'].mean()]
+        })
+
+        for col in columns:
+            features = tsfel.time_series_features_extractor(
+                conf_extraction, df[col], fs=mafaulda.FS_HZ
+            )
+            features.columns = [
+                col + '_' + c.strip('0_').replace(' ', '_').lower()
+                for c in features.columns
+            ]
+            fv = fv.assign(**features)
+        results.append(fv)
+
+    return pd.concat(results).reset_index(drop=True)
+
+
[…]

### 2023-11-12 notebooks/vibrodiagnostics/mafaulda.py

@@ -1,0 +1,123 @@
+import numpy as np
+import pandas as pd
+import seaborn as sb
+
+from scipy.stats import skew, kurtosis, kstest
+from scipy.fft import rfft
+from scipy.signal import butter, filtfilt, find_peaks
+
+from tqdm.notebook import tqdm
+import matplotlib.pyplot as plt
+from zipfile import ZipFile
+
+from multiprocessing.pool import ThreadPool
+
+FS_HZ = 50000
+DB_REF = 0.000001                                # 1 dB = 1 um/s^2
+COLUMNS = ['ax', 'ay', 'az', 'bx', 'by', 'bz']   # 'mic'
+
+################################# IMPORT ########################################
+
+def parse_filename(filename: str) -> (str, str, str):
+    path = filename.split('/')
+    if path[0].strip() in ('overhang', 'underhang'):
+        fault = f'{path[0]}-{path[1]}'
+        severity = path[2]
+        seq = path[3]
+    elif path[0].strip() == 'normal':
+        fault, severity, seq = path[0], '0', path[1]
+    else:
+        fault, severity, seq = path
+
+    return fault, severity, seq
+
+
+def import_files_split(zip_file, file_list, func, parts, cores=4):
+    pool = ThreadPool(processes=cores)
+    
+    return pd.concat([
+        pool.apply_async(func, (zip_file, name, parts )).get()
+        for name in tqdm(file_list)
+    ])
+
+
+def import_files(zip_file, file_list, func, cores=4):
+    pool = ThreadPool(processes=cores)
+    
+    return pd.concat([
+        pool.apply_async(func, (zip_file, name, )).get()
+        for name in tqdm(file_list)
+    ])
+
+
+def get_mafaulda_files(zip_file):
+    filenames = [
+        text_file.filename
+        for text_file in zip_file.infolist()
+        if text_file.filename.endswith('.csv')
+    ]
+    filenames.sort()
+    return filenames
+
+
+def rpm_calc(tachometer: pd.Series) -> float:
+    t = tachometer.index.to_numpy()
+    y = tachometer.to_numpy()
+    peaks, _ = find_peaks(y, prominence=3, width=50)
+    interval = np.diff(t[peaks]).mean()
+    return 60 / interval
+
+
+def preprocess(ts: pd.DataFrame):
+    return (
+        ts
+        .assign(t = lambda x: x.index * (1 / FS_HZ))
[…]

### 2023-11-12 notebooks/vibrodiagnostics/models.py

@@ -1,0 +1,302 @@
+import numpy as np
+import pandas as pd
+from vibrodiagnostics.selection import  METADATA_COLUMNS_ALL
+import matplotlib.pyplot as plt
+import seaborn as sb
+
+from sklearn.decomposition import PCA
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.model_selection import train_test_split
+
+from scipy.stats import pearsonr
+from sklearn.feature_selection import mutual_info_classif, f_classif
+from sklearn.feature_selection import SelectPercentile, SelectKBest
+
+
+def features_subset(filename, classes, axis, label=None, severity_sort=False, anomaly_severity=0.5):
+    features = pd.read_csv(filename)
+    features = fault_labeling(features, classes, anomaly_severity=anomaly_severity, debug=False)
+
+    if severity_sort:
+        groups = [
+            df.sample(frac=1, random_state=10)
+            for i, df in (
+                features.sort_values(by='severity_level')
+                        .groupby('severity_level')
+            )
+        ]
+        features = pd.concat(groups).reset_index(drop=True)
+
+    else:
+        features = (         # Shuffle
+            features
+            .sample(frac=1, random_state=10)
+            .reset_index(drop=True)
+        )
+
+    columns = features.columns.str.startswith(tuple(axis))
+    features.columns[columns]
+    X = features[features.columns[columns]]
+    if label is None:
+        return X
+    else:
+        y = features[label].astype('category').cat.codes
+        return X, y
+
+
+def features_subset_offline(filename, classes, axis, label, train_size=0.7, anomaly_severity=0.5):
+    features = pd.read_csv(filename)
+    features = fault_labeling(features, classes, anomaly_severity=anomaly_severity, debug=False)
+
+    columns = features.columns.str.startswith(tuple(axis))
+    features.columns[columns]
+    X = features[features.columns[columns]]
+    y = features[label].astype('category')
+
+    if label == 'anomaly':
+        X, y = anomalies_undersample(X, y, 0.1)
+
+    return train_test_split(
+        X, y, train_size=train_size, stratify=y, random_state=10
+    )
+
+
+def fault_labeling(dataset, classes, anomaly_severity=0.7, debug=False):
[…]

### 2023-11-12 notebooks/vibrodiagnostics/selection.py

@@ -1,0 +1,427 @@
+import os.path
+import math
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+
+from river import stats, preprocessing
+from scipy.stats import pearsonr
+from sklearn.feature_selection import mutual_info_classif, f_classif
+
+from sklearn.compose import ColumnTransformer
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import StandardScaler, MinMaxScaler
+
+
+# Dataset paths and attributes
+TIME_FEATURES_PATH = 'td_features.csv'
+FREQ_FEATURES_PATH = 'fd_features.csv'
+TIME_AND_FREQ_FEATURES_PATH = 'time_freq_features.csv'
+
+TSFEL_FEATURES_PATH = 'tsfel_features.csv'
+TSFEL_TIME_FEATURES_PATH = 'tsfel_td_features.csv'
+TSFEL_FREQ_FEATURES_PATH = 'tsfel_fd_features.csv'
+TSFEL_STAT_FEATURES_PATH = 'tsfel_sd_features.csv'
+
+WPD_FEATURES_PATH = 'wpd_features.csv'
+
+TIME_FEATURES_PATH_ALL = 'all_td_features.csv'
+FREQ_FEATURES_PATH_ALL = 'all_fd_features.csv'
+WPD_FEATURES_PATH_ALL = 'all_wpd_features.csv'
+TSFEL_FEATURES_PATH_ALL = 'all_tsfel_features.csv'
+
+TD_COLUMNS = ['mean', 'std', 'skew', 'kurt', 'rms', 'pp', 'crest', 'margin', 'impulse', 'shape']
+FD_COLUMNS = [
+    'centroid', 'std', 'skew', 'kurt', 'roll-off', 'flux_mean', 'flux_std',
+    'noisiness', 'energy', 'entropy', 'negentropy'
+]
+WPD_COLUMNS_EXCLUDE = {
+    'fault', 'severity', 'seq', 'rpm', 'axis', 'feature'
+}
+
+FAULT_CLASSES = {'normal': 'N', 'imbalance': 'I', 'horizontal-misalignment': 'HM', 'vertical-misalignment': 'VM'}
+METADATA_COLUMNS = ['fault', 'severity', 'seq', 'rpm']
+METADATA_COLUMNS_ALL = METADATA_COLUMNS + ['severity_class', 'severity_level', 'anomaly']
+
+#########################################################
+def filter_out_metadata_columns(df):
[…]

### 2023-11-27 thesis/chapters/02-analysis-A-CdM.tex
Incremental learning in thesis

@@
 The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
-In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize assets' usage~\cite{cinar_machine_2020}.
-\bigbreak
+In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.
 
@@
 This is the most inappropriate way to maintain the production line, but it is straightforward enough.
-It requires a large stock of replacement parts on-site and breakage inflicts a `crisis management mode' upon the plant \cite{scheffer_practical_2004}.
+It requires a large stock of replacement parts on-site and breakage inflicts a ``crisis management mode'' upon the plant \cite{scheffer_practical_2004}.
 On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
-\bigbreak
 
@@
 Conservative planning is usually the norm to keep the machine always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
-\bigbreak
 
@@
 The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
-\bigbreak
 
@@
 
-The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the `run-to-failure' histories, and usage parameters~\cite{okoh_overview_2014}.
+The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the ``run-to-failure'' histories, and usage parameters~\cite{okoh_overview_2014}.
 Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{assets/bath-tub-curve.png}
-	\caption{Bath tub curve~\cite{mohanty_machinery_2015}}
-	\label{fig:bath-tub-curve}
+	\includegraphics[width=0.6\textwidth]{assets/bath-tub-curve.png}
+	\caption{Bathtub curve~\cite{mohanty_machinery_2015}}
+	\label{fig:bathtub-curve}
 \end{figure}
@@
 During the stable middle phase, malfunction can occur after the machine's excessive overload.
-The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}).
+The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bathtub-curve}).
 
@@
 Both designs can be permanently mounted.
-In continuous collection it is recommended to have `multiplexing rate sufficiently rapid so there is no significant data or trends lost'~\cite{noauthor_iso_2002}.
-When channels are scanned successively with gaps between data points the system is known as `scanning'.
+In continuous collection it is recommended to have ``multiplexing rate sufficiently rapid so there is no significant data or trends lost''~\cite{noauthor_iso_2002}.
+When channels are scanned successively with gaps between data points the system is known as ``scanning''.
 
@@
 
-Broadband measurement requires `frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest'~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s.
+Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s.
 Bearings and gears diagnosis may push the upper-frequency limit even higher.
@@
 
-Equipment's `health' can be mischaracterized when there are significant differences in the machine's normal operating conditions.
+Equipment's ``health'' can be mischaracterized when there are significant differences in the machine's normal operating conditions.
 Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation.

### 2023-11-27 thesis/chapters/02-analysis-B-features.tex
Remove exports and feature selection rework
Incremental learning in thesis

@@
 In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset as a result of slight miscalibration, and bias originating from a constant force of gravity.
-These unavoidable distortions are suppressible to some extent with digital filters.
+These unavoidable distortions are to some extent suppressible with digital filters.
 In the preprocessing stage, we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to eliminate the external interference.
@@
 
-\section{Feature engineering} \label{section:feature-engineering}
-Raw numerical vectors after preprocessing are merely low-level descriptors of the underlying physical phenomena.
-At first, these incomprehensible sequences of numbers are reduced to summary attributes called features in the process of feature discovery.
-Normalization and linear transformations are applied here to discriminate different categories in the feature space.
-The most informative set of features is obtained with feature selection methods for the diagnostic model.
-Features can be hand-crafted, learned implicitly within the model representation, or explicitly from an optimization problem solution.
+\section{Feature extraction} \label{section:feature-extraction}
+After preprocessing raw numerical vectors are merely low-level descriptors of the underlying physical phenomena.
+At first, these incomprehensible sequences of numbers are reduced to summary attributes called features in the process of feature extraction or feature discovery.
+Features can be hand-crafted (as is our case), learned implicitly within the model representation, or explicitly from an optimization problem solution.
 
-\subsection{Feature extraction}
 Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
 The advantages of add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
+
 It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model.
@@
 
-\subsection{Time domain features}
+\subsection{Temporal domain features}
 The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
-Statistics can be calculated in any domain, but the mean value is not to be used in detrended data.
+Statistics can be calculated in any domain, but the mean value should not to be used in detrended data.
 The vibration severity metrics out of technical standards are also highly regarded.
-The characteristics of amplitude include root mean square, peak-to-peak, and maximum~\cite{mostafavi_novel_2021}.
+The characteristics of amplitude include root mean square, peak-to-peak distance, and maximum~\cite{mostafavi_novel_2021}.
 
@@
 
-% TODO: add td and fd features from tsfel
 \begin{table}[h]
@@
 \textbf{Feature}            & \textbf{Equation}                                                                    & \textbf{Feature}        & \textbf{Equation}                                                                                                  \\ \hline
-\textit{Standard deviation} & $ \sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                       \\ \hline
+\textit{Standard deviation} & $ X_\sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                       \\ \hline
 \textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$ & \textit{Margin factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $                          \\ \hline
@@
 \end{adjustbox}
-\caption{Time domain features}
+\caption{Temporal domain features}
 \label{tab:td-features}
@@
 
-\subsection{Frequency domain features}
+\subsection{Spectral domain features}
 The mechanical faults present themselves as oscillatory patterns which are combinations of frequencies with various amplitudes.
-The Fourier transform is one of the prominent strategies in power spectral density estimation.
+The Fourier transform is one of the most prominent strategies in power spectral density estimation.
 Experts on vibrodiagnostics utilize it as a primary signal processing technique for data analysis as it is recommended in ISO 13373-2 standard~\cite{noauthor_iso_2016_2}.
 
-The inherent symmetries in the Fourier matrix made it possible to invent an efficient implementation of the Fast Fourier transform (FFT) algorithm with time complexity $O(n \log n)$.
+The inherent symmetries in the Fourier matrix made it possible to implement the Fast Fourier transform (FFT) algorithm with time complexity $O(n \log n)$.
 The drawback of the plain spectral analysis is the lack of resolution for events that occurred at distant time instants, and so their spectral components might adversely blend in together.
 
-In the frequency domain, we can obtain spectral centroid, spectral kurtosis, spectral roll-off, spectral flux, energy in frequency bands, and energy ratio (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
-In geometry terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
-Spectral roll-off gives a notion about the spectral distribution because it searches the frequency $f_c$ below which 95\% of the signal energy is contained.
-The energy in the roll-off calculation is summed up to the Nyquist limit: $f_s / 2$.
-According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra, value of one means spectra are the most dissimilar.
+\begin{table}[ht]
+\renewcommand{\arraystretch}{2}
+\centering
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Feature}           & \textbf{Equation}                                                                                                  \\ \hline
+\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot a(f_i)}}{\sum_{i = 0}^{N - 1}{a(f_i)}}$                   \\ \hline 
+\textit{Energy}            & $ E(N) = \sum_{i = 1}^{N} a^2(t) $                                                                    \\ \hline \textit{Energy ratio}                & $E_r = E_i \;/\; \sum_{i = 1}^{N}{E_i} $                                                        \\ \hline
+\textit{Spectral roll-on} & $ E(f_c) = 0.05 \cdot E(f_s / 2) $ \\ \hline                    
+\textit{Spectral roll-off} & $ E(f_c) = 0.95 \cdot E(f_s / 2) $                                                   \\ \hline
+\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \mathrm{corr}(A_{t-1}, A_t)$ \\ \hline 
+\textit{Noisiness}                   & $X_{noise} = \mathrm{SNR}(X) = \mu \;/\; \sigma $                             \\ \hline
+\textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
+\textit{Spectral negentropy}      & $\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}} \cdot \ln\left(\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}\right)$                                                \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Frequency domain features}
+\label{tab:fd-features}
+\end{table}
 
-The harmonic frequencies may originate from higher order oscillation modes of the same shaft or other elastic rod supported on both ends.
-Several harmonics features worth investigating are fundamental frequencies, noisiness, inharmonicity, and harmonic spectral deviation~(Tab.~\ref{tab:fd-features}).
-Noisiness as a harmonic feature is a ratio of noise (non-harmonic components) energy to the total contained energy.
-Inharmonicity measures the divergence of spectral components from a purely harmonic to inharmonic signal on scale from 0 to 1.
-Harmonic spectral deviation adds up differences of amplitudes at harmonic peaks $a(h)$ from the spectral envelope $\mathrm{SE}(h)$~\cite{peeters_large_2004}.
+In the spectral domain, we can obtain usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
+Additionaly spectral roll-on and roll-off, fundamental frequency, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
+
+In geometric terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
+Spectral roll-off gives a notion about the spectral distribution because it identifies the frequency $f_c$ below which 95\% of the signal energy is contained.
+Complementary, the roll-on frequency is chosen so that 5\% of the signal energy is below this value.
+According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra, a value of one means spectra are the most dissimilar.
+
+``Negentropy measures the inclination of a system to increase its level of organization''~\cite{avoci_spectral_2020}.
+The larger \emph{spectral negentropy} (Equation~\ref{equ:spectral-negentropy}) suggests more fault-induced impulses.
+$E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
 
@@
 The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
+
 The essential peak-finding approaches are based either on magnitude or gradient.
@@
 
-\begin{table}[ht]
-\renewcommand{\arraystretch}{2}
-\centering
-%\begin{adjustbox}{width=\columnwidth,center}
-\begin{tabular}{|l|l|}
-\hline
-\textbf{Feature}           & \textbf{Equation}                                                                                                  \\ \hline
-\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot a(f_i)}}{\sum_{i = 0}^{N - 1}{a(f_i)}}$                   \\ \hline 
-\textit{Spectral roll-off} & $ E(f_c) = 0.95 \cdot E(f_s / 2) $                                                   \\ \hline
-\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \mathrm{corr}(A_{t-1}, A_t)$ \\ \hline 
-\textit{Harmonic spectral deviation} & $ X_{\mathrm{HDEV}} = \frac{1}{H}\sum_h(a(h) - \mathrm{SE}(h))$                                          \\ \hline
-\textit{Noisiness}                   & $X_{noise} = \frac{\sum_{k \notin h}^{N}E_k}{\sum_{i = 1}^{N}E_i} = \mathrm{SNR}(X) = \mu \;/\; \sigma $                             \\ \hline
-\textit{Inharmonicity}               & $X_{inharmo} = \frac{2}{f_0} \cdot \frac{\sum_h | f(h) - h \cdot f_0| \cdot a^2(h)}{\sum_h a^2(h)} $ \\ \hline
-\textit{Energy}            & $ E(N) = \sum_{i = 1}^{N} a^2(t) $                                                                    \\ \hline \textit{Energy ratio}                & $E_r = E_i \;/\; \sum_{i = 1}^{N}{E_i} $                                                        \\ \hline
-\textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
-\end{tabular}
-%\end{adjustbox}
-\caption{Frequency domain features}
-\label{tab:fd-features}
-\end{table}
-
 \subsection{Time-frequency domain features}
@@
 
+The alternative to isolating weak impacts with high time resolution is a \textbf{Teager-Kaiser energy operator} (TKEO) (Equation~ \ref{equ:tkeo-operator}).
+It is a tool for envelope analysis to demodulate characteristic AM-FM signal present during bearing faults.
+Energy operator output can be utilized as a standalone feature attribute.
+
+\myequations{Teager–Kaiser energy operator}
+\begin{ceqn}\begin{align}
+\psi[x(n)] = [x(n)]^2 - x(n - 1)x(n + 1)
+\label{equ:tkeo-operator}
+\end{align}\end{ceqn}
+
+Improved TKEO is necessary to prevent analysis from suffering from the noisy source.
+The key idea is to perform TKEO after signal decomposition into narrow-band components with different center frequencies.
+The extracted modes are reconstructed with weights assigned based on their correlations to the original signal~\cite{shi_application_2022}.
+
+Time-frequency spectrum modification preserving localization of abrupt wide-band spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
+Post-processing of STFT window $G(t,\omega)$ involves multiplication of the spectrum with the Transient extracting operator (TEO).
+This operator is expressed in the form of a Dirac delta function $\delta(t)$ (Equation~\ref{equ:tet-transform}).
+
+\myequations{Transient-extracting transform}
+\begin{ceqn}\begin{align}
+\mathrm{Te}(t,\omega) = G(t,\omega) \cdot  \delta(t - t_0)
+\label{equ:tet-transform}
+\end{align}\end{ceqn}
+
+TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
+These two transforms use distinct windows $g[n]$ and $n \cdot g[n]$.
+Decomposition of signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
+
+\subsection{Wavelet domain features}
 The bands for lower frequencies should be longer in duration than for higher frequencies.
@@
 
-The alternative to isolating weak impacts with high time resolution is a \textbf{Teager-Kaiser energy operator} (TKEO) (Equation~ \ref{equ:tkeo-operator}).
-It is a tool for envelope analysis to demodulate characteristic AM-FM signal present during bearing faults.
-Energy operator output can be utilized as a standalone feature attribute.
-
-\myequations{Teager–Kaiser energy operator}
-\begin{ceqn}\begin{align}
-\psi[x(n)] = [x(n)]^2 - x(n - 1)x(n + 1)
-\label{equ:tkeo-operator}
-\end{align}\end{ceqn}
-
-Improved TKEO is necessary to prevent analysis from suffering from the noisy source.
-The key idea is to perform TKEO after signal decomposition into narrow-band components with different center frequencies.
-The extracted modes are reconstructed with weights assigned based on their correlations to the original signal~\cite{shi_application_2022}.
-
-Time-frequency spectrum modification preserving localization of abrupt wide-band spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
-Post-processing of STFT window $G(t,\omega)$ involves multiplication of the spectrum with the Transient extracting operator (TEO).
-This operator is expressed in the form of a Dirac delta function $\delta(t)$ (Equation~\ref{equ:tet-transform}).
-
-\myequations{Transient-extracting transform}
-\begin{ceqn}\begin{align}
-\mathrm{Te}(t,\omega) = G(t,\omega) \cdot  \delta(t - t_0)
-\label{equ:tet-transform}
-\end{align}\end{ceqn}
-
-TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
-These two transforms use distinct windows $g[n]$ and $n \cdot g[n]$.
-Decomposition of signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
-
 The spectrograms to illustrate the difference in the ability of Fourier transform, continuous Wavelet transform, and their modifications to pick up underlying patterns in bearing faults are shown in the Fig.~\ref{fig:transforms}.
@@
         \includegraphics[width=\textwidth]{assets/stft-spectrogram-sample.png}
-        \caption{STFT + Gaussian window}
+        \caption{STFT \& Gaussian window}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/wt-spectrogram-sample.png}
-        \caption{CWT + Morlet wavelet}
+        \caption{CWT \& Morlet wavelet}
     \end{subfigure}
@@
 
+\subsection{Empirical wavelet features}
 \textbf{Empirical Wavelet Transform} (EWT) constructs adaptive bandpass filters with Meyer wavelet.
@@
 
-Alternatively, the central frequencies of bands containing the most unevenness measured by negentropy are picked after the EWT processing passed.
-The filter bank is then reconstructed accordingly.
-`Negentropy measures the inclination of a system to increase its level of organization'~\cite{avoci_spectral_2020}.
-The larger \emph{spectral negentropy} (Equation~\ref{equ:spectral-negentropy}) suggests more fault-induced impulses.
-$E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
-
-\myequations{Spectral negentropy}
-\begin{ceqn}\begin{align}
-\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}} \cdot \ln\left(\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}\right)
-\label{equ:spectral-negentropy}
-\end{align}\end{ceqn}
-
-In \textbf{time-frequency domain scanning empirical spectral negentropy} method (T-FSESNE) the scanning EWT filter establishes the empirical mode components $X_i(t)$.
-The central frequencies $f_{cj}$ are retained in resonance bands where the frequency-domain spectrum negentropy (FSNE) is greater than mean $\overline{\Delta I_E}$.
-The optimal bandwidth for each component is searched among the set of incrementally expanding regions fixed at $f_{cj}$.
-The interval with the largest time-domain spectrum negentropy (TSNE) is selected to restrict the bounds of the mode $(f_{cj}, B_{wk})$~\cite{yonggang_time_2020}.
-
-The following scheme termed \textbf{adaptive and fast empirical wavelet transform} (AFEWT) calculates spectral negentropy of key functions $K'_i(f)$.
-The spectral section with the highest entropy is assumed to contribute the most to the rolling bearing fault.
-First, the Fourier transform of the spectrum establishes the key function $K(f)$.
-This function is analogous to the cepstrum.
-The leftmost ridge in the $K(f)$ plot is transformed using inverse FFT to attain trend spectrum $T(f)$.
-Finally, the array of local minima points in the trend spectrum bound frequency bands whose Fourier transform produces key functions $K'_i(f)$~\cite{xu_adaptive_2019}.
-
 The inspiration for filtering with adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
@@
 
-The time-frequency representation offers plenty of features depending on the choice of spectral transformation.
-We have reviewed Short-time Fourier transform, Continuous Wavelet transform, Synchrosqueezing transform, Discrete Wavelet transform, Wavelet packet decomposition, Empirical Wavelet transform, and operators of negentropy, TKEO, and TEO.
+Wavelet domain features and associated spectral segmenation appears to be a powerful tool in conserving data bandwidth.
+For the use in white-box machinery diagnosis these trend indicator turn out to be difficult to comunicate and comprehend.
+Therefore we use more standardized metrics in the further study.
 
-% TODO: we did not utilize wavelets as of yet
-% 
-% 
-%
-
-\subsection{Feature transformation}
-Numeric features from the feature extraction phase have non-normal distributions and span the range of scales.
+\section{Feature transformations}
+Numerical features from the feature extraction phase have non-normal distributions and span the range of scales.
 Broad differences among features skew the spread in the particular axis.
@@
 The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.
+
+\subsection{Feature normalization}
+Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its component.
+Models have to be resilient to any slight inclination or sensor orientation.
+To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and Euclidian norm is computed~\cite{kamminga_robust_2018}.
+
+\myequations{Feature euclidian norm}
+\begin{ceqn}\begin{align}
+\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
+\label{equ:min-max-scaler}
+\end{align}\end{ceqn}
+
+Feature normalization most often takes two forms.
+\textbf{Min-max scaling} changes original range of values into interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
+\textbf{Standardization} (Equation~\ref{equ:standardization-scaler}) constrains the mean of the variable to 0 with a variance of 1~\cite{zheng_feature_2018}.
 
@@
 
-Feature normalization most often takes two forms.
-\textbf{Min-max scaling} changes original range of values into interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
-\textbf{Standardization} (Equation~\ref{equ:standardization-scaler}) constrains the mean of the variable to 0 with a variance of 1~\cite{zheng_feature_2018}.
-
+\subsection{Principal components analysis}
 Highly correlated features generated from a relatively small original column space are redundant as they do not provide any additional information for diagnostics.
@@
 
-\subsection{Feature selection}
-Not all features contribute to the model's discriminatory power with an even share.
-A certain subset can reach better results than other substitute options.
-The \emph{filtering methods} of feature selection rank the predictors in order of their importance for the problem at hand, or they separate the group of predictors that achieve the top modeling accuracies in unison~\cite{johnson_feature_2019}.
+\section{Feature selection}
+Features do not contribute to predictive power of the model with an even share. A certain subset can reach better results than others. Choosing optimal feature subset is NP-hard combinatorial problem.
 
-Still, the features can be chosen by \emph{embedded methods} intrinsically as a part of a model or else in \emph{wrapper methods} by machine learning search algorithm at a serious computational expense.
-However, we will focus next only on filtering methods.
+\subsection{Filtering methods}
+The features can be chosen intrinsically as a part of a model by \emph{embedded methods} or by machine learning search algorithm at a serious computational expense in \emph{wrapper methods}.
+However, we will focus on \emph{filtering methods} which rank the predictors in order of their importance for the problem at hand and separate the best performing group~\cite{johnson_feature_2019}.
+The most common strategy is \emph{K-Best Selection}.
 
-The general steps in selecting the adequate predictors is outlined next~\cite{nandi_condition_2019}:
+The general steps in selecting the adequate predictors is as follows~\cite{nandi_condition_2019}:
 \begin{enumerate}
@@
 
+\subsection{Scores for ranking}
 Most of the scores are based on supervised learning, so they expect true class labels to apportion the measurements respectively.
@@
 \item \textbf{Variance threshold} - removes low-variance features below set threshold.
-\item \textbf{Pearson correlation} - expresses linear relationship between class label $c$ and features $f_i$.
-Attributes are ranked in descending order according to the absolute value of their correlation coefficient from zero upwards, i.
-e.
-we seek the highest correlations to the class label.
+\item \textbf{Correlation coefficient} - expresses the linear relationship between two variables.
+The codependent variables are of three sorts: quantitative, ordinal, and nominal.
+The choice of coefficient calculation is determined by the type of variables under consideration shown in Table \ref{tab:corr-coef}.
+
+\emph{Pearson correlation} coeficient expresses similarity between two quantitative features $f_i$ and $f_j$.
+In the classification setting the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}.
+Mathematically, this is equivalent to the Pearson coefficient.
+Rank correspondence is quantified with either Spearman rho or Kendall's Tau~\cite{calkins_more_2005}.
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.5}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|l|l|l|}
+\hline
+\textbf{Variable Y\textbackslash{}X} & \multicolumn{1}{c|}{\textbf{Quantitiative X}} & \multicolumn{1}{c|}{\textbf{Ordinal X}} & \multicolumn{1}{c|}{\textbf{Nominal X}} \\ \hline
+\textbf{Quantitative Y}              & Pearson $r$                                   & Biserial $r_b$                          & Point Biserial $r_{pb}$                 \\ \hline
+\textbf{Ordinal Y}                   & Biserial $r_b$                                & Spearman $\rho$    & Rank Biserial $r_{rb}$                  \\ \hline
+\textbf{Nominal Y}                   & Point Biserial $r_{pb}$                       & Rank Bisereal $r_{rb}$                  & Phi, L, C, Lambda                       \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Correlation coeficients}
+\label{tab:corr-coef}
+\end{table}
+
+Attributes are ranked in descending order according to the absolute value of their correlation coefficient. We seek the highest correlation to the class label.
 \myequations{Pearson correlation coefficient}
 \begin{ceqn}\begin{align}
-r(i) = \frac{\mathrm{cov}(f_i, c)}{\sqrt{\mathrm{var}(f_i) \cdot \mathrm{var}(c)}}
+r(i) = \frac{\mathrm{cov}(f, c)}{\sqrt{\mathrm{var}(f) \cdot \mathrm{var}(c)}}
 \end{align}\end{ceqn}
@@
 \begin{ceqn}\begin{align}
-\mathrm{FS}(X^j) = \frac{\sum_{i=1}^{C} n_i(\mu_i^j - \mu^i)^2}{\sum_{i=1}^{C} n_i (\sigma_i^j)^2}
+\mathrm{FS}(X^j) = \frac{\sum_{i=1}^{C} n_i(\mu_i^j - \mu^i)^2}{\sum_{i=1}^{C} (n_i - 1) \cdot (\sigma_i^j)^2}
 \label{equ:fisher-score}
@@
 The probability distribution proximity of variables derives from relative entropy known as the Kullback-Leibler distance.
+Mutual information presumes variables are discrete.
+In the case of quantitative variables, mutual information is estimated with binning or nearest neighbors methods~\cite{ross_mutual_2014}.
+
 Probabilities $P(x)$, $P(y)$, $P(x, y)$ are estimated in the contingency table from event occurrence count to all sample population $|x|\;/\;N$.
@@
 \begin{ceqn}\begin{align}
-\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
+\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \cdot \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
 \end{align}\end{ceqn}

### 2023-11-27 thesis/chapters/02-analysis-C-diagnostics.tex
Incremental learning in thesis

@@
 The guiding principles for algorithm selection are simplicity in terms of their straightforward visual explanation for the production managers, and the ability to progressively improve the model on the streaming data to address peculiarities in individual machine constructions.
-
-\subsection{Concept drift}
-% TODO: ADWIN (ADaptive WINdowing)
-% Kolmogorov-Smirnov Windowing method for concept drift detection.
 
@@
 Then non-core points in the proximity area of the core point are attached to the cluster containing it~\cite{aggarwal_data_2014}.
+
+Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1].
+It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters.
+The low score indicates a too little or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
 
@@
 \subsection{Classification}
-% TODO: HoeffdingTreeClassifier
-% https://analyticsindiamag.com/a-beginners-guide-to-hoeffding-tree-with-python-implementation/
-% https://www.cms.waikato.ac.nz/~abifet/book/chapter_5.html
-
 Accurate multi-class classification of machine fault causes out of the characteristics of known ones is a much more difficult task than novelty detection.
 Universal enough fault baseline has to be recorded and transformed into feature space.
-Interactions among fault manifestations have to be accounted for.
+Interactions among fault root causes have to be considered.
 We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}.
-So far, solutions seem not production ready.
-Therefore, we opt to use a more rudimentary model.
+So far, solutions seem not production-ready and hard to explain.
+Therefore, we opt to use a simpler model.
+
+Performance of classification is estimated by several metrics on the validation set obtained using hold-out or cross-validation techniques.
+Frequently used quantities for classifier model evaluation include accuracy, precision, recall, f1 score, area under ROC curve, and counts of hits and misses in confusion matrix.
 \bigbreak
@@
 \textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:knn}).
-This means it can work in the semi-supervised environment because it can infer labels just from knowing a few annotations.
+It means it can work in the semi-supervised environment because it can infer labels just from knowing a few annotations.
+The major drawback of kNN is a preference for the majority class in imbalanced class sizes datasets~\cite{shi_improving_2020}.
+The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
+kNN algorithm requires features to be normalized to assign the same importance to each predictor.
 
@@
 
-% TODO: Spatial database
-% TODO: Sliding WIndow-based Nearest Neighbor (SWINN)
-
 The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{Manhatann distance} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}.
-The demanding neighborhood queries are sped up by a Metric search tree data structure such as \emph{M-Tree} (Fig.~\ref{fig:m-tree}).
 The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
+The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.
 
@@
 
-\subsection{Online model evaluation}
-% TODO
+\subsection{Incremental learning}
+Online and incremental machine learning operates in the streaming setting updating the model parameters with each new incoming event or in mini-batches.
+This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.
+
+There are some additional obstacles to watch out for with incremental learning in comparison to batch learning~\cite{gepperth_incremental_2016}:
+\begin{enumerate}
+    \itemsep0pt
+    \item \textbf{Concept drift} is defined as the change in data distribution function over time.
+The two types of concept drift are virtual and real.
+In virtual drift, changes occur only in the input distribution.
+Real drift means that the alteration comes to underlying functionality.
+Concept shift occurs with the abrupt change.
+    \item \textbf{Stability-plasticity tradeoff} concerns the speed with which the model adapts to new information.
+The model can react quickly making it less stable, or retain patterns for longer but become irresponsive to sudden shifts.
+    \item \textbf{Model complexity} should be adjustable to ensure flexibility in unforeseen circumstances.
+Simpler models in the ensemble can also further increase prediction robustness.
+Resource limitation bound complexity from above.
+    \item \textbf{Memory model} can store aggregates from seen observations and its typical examples or finite window of latest samples with forgetting factor.
+\end{enumerate}
+
+\textbf{Model benchmarking} in incremental learning is achieved by comparing models to their batch counterparts or using progressive validation~\cite{blum_beating_1999, halford_correct_2020}.
+It has been shown that incremental clustering algorithms have overall worse accuracy than batch versions~\cite{gepperth_incremental_2016}.
+In the validation process, precautions should be taken to prevent data leakage from future events into the past.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{assets/incremental-learning.png}
+    \caption{Incremental learning deployment architecture~\cite{gaia_online_2022}}
+    \label{fig:online-learn-arch}
+\end{figure}
+
+Deployment of an online machine learning model alongside supporting services is different than in established MLOps processes.
+Model store and Inference service components are supplemented with Labelling and Learning service~\cite{gaia_online_2022}.
+Their goal is to tune model parameters gradually as additional ground truth labels are provided.
+Labels can be provided later in a scheme called ``log and wait'', but data features are stored until such time.

### 2023-11-27 thesis/chapters/03-design.tex
Incremental learning in thesis

--- 2023-05-23 thesis/chapters/03-design.tex
@@
 
-\section{Preparatory exploration}
-The wood processing factory we plan to collaborate with has to choose machines that are worthy of condition monitoring.
-In the meantime, the data processing pipeline will be put together in Python language and packages for scientific computing.
-The pipeline will consist of the following stages.
+\section{Machine learning pipeline}
 
+Mafaulda dataset
+Jupyter notebook - Python
 \begin{enumerate}
@@
     \item Detrending
-    \item Adaptive noise cancellation of the background interference
+    \item (Optional) Adaptive noise cancellation of the background interference
     \item Vector of all features
@@
         \item Frequency domain: PSD estimation with FFT and Welch averaging with the resolution of 1 Hz combined with Hann window (Tab.~\ref{tab:fd-features})
-        \item Time-frequency domain: energy and entropy in wavelet coefficients from WPD and EWT filter banks.
     \end{itemize}
@@
 
-\section{Vibration processing}
+\section{Research questions}
+Main goals:
+	- How does vibration data look like (spectral and time domain)?
+	- Create dataset of machinery vibrations
+	- Reduce number of features (samples) send from edge device - to minimal amount
+	- Adapt to features changing over time (RiverML can handle it, find proof)
+	- Evaluate model performance on all features and different feature sets
+	- Keep in mind: data ordering!
+
+\section{Data preparation}
+- Mafaulda dataset
+	- Choose 4 faults - normal (N), imbalance (I), vertical (VM) and horizonal misalignment (HM)
+	- Convert severity to 0 - 1 scale.
+		- Label samples above 0.5, 0.7, 0.9 as anomalous
+	- Choose rpm range 2900 $\pm$ 500 (around rotational speed of machinery with some spread, some features are correlated with rpm 
+	- Counts before split: 
+		- Split to 5 parts of 1 second intervals
+	- Two measurement points A, B
+	- Detrending by removing mean
+	- Calculate features: temporal, spectral (in 5 window sizes): welch averaging, hann window
+
+	- Batch: 
+		- Balancing dataset with oversampling minority classes	
+		- Hold-out validation - split to train and test set
+	- Online: Order by severity
+
+- Measurement of custom datasets 
+	- one 3-axis accelerometer on top of scroll compressor of air conditioning
+		- one in the base to capture noise
+	- water pump
+
+	- columns: t, x, y, z: rpm
+	- 20 s recordings - split to 5 parts - extract features
+	- do PCA to explore see differences
+	- label as worse, better (classes are hard to provide)
+
+\section{Feature relevance}
+- choose 3 features
+- supervised
+	- highly correlated features >= 0.9:
+		- Temporal domain (A)
+			- std, rms, 1.000000
+			- margin, impulse, 0.999079
+			- crest, impulse, 0.996807
+			- crest, margin,	0.992548
+			- pp, max, 0.970055
+			- max, (std, rms), 0.938198
+			- pp, (std, rms), 0.938180 / 0.928
+		- Spectral domain (A)
+			- same feature in different window sizes (0.99)
+			- kurtosis, skewness, 0.980618
+			- std, energy, 0.960110
+			- entropy, noisiness, 0.945514
+
+	- calcultate euclidian measure of feature 
+	- correlation point biserial, fisher, mutual information
+		- Sperman rank correlation: corr, f_stat, 1.000000
+	- calculate feature rank
+		- Temporal (A) - Remove corr: pp, skewness, margin
+			pp	1.442250
+			std	2.080084
+			max	2.714418
+			rms	3.174802
+			skewness	6.082202
+			margin	6.868285
+
+			(B)			
+			skewness	1.817121
+			rms	1.817121
+			std	2.289428
+			kurtosis	4.308869
+		- Spectral (A) - multiple window sizes 
+			- (energy, roll off, std)
+
+- online learning features
+	- evolution of feature importace
+
+\section{Nearest neighbour classifier}
+- kNN (fault and anomaly)
+	- Offine (baseline)
+	- Online (evolution)
+- parameters: k-neigh, distance
+- metrics: accuracy, precision, recall
+
+\section{Clustering}
+- Density based clustering
+	- DBSCAN (all features, PCA, subset of best)
+	- DenStream (all features, subset of best)
+
+\section{Novelty detection}
+- Offline (Isolation forest)
+- Online (Half-space Tree)
+
+\section{Infrastructure deployment}
+Future work: engineer new feature, deploy, tweek models, validate on real dataset
+
  \begin{itemize}

### 2023-11-27 notebooks/vibrodiagnostics/discovery.py

@@ -2,7 +2,7 @@ from zipfile import ZipFile
 import numpy as np
 import pandas as pd
 from itertools import pairwise
-from typing import List
+from typing import List, Tuple, Callable
 
 from numpy.lib.stride_tricks import sliding_window_view
 from scipy.stats import skew, kurtosis, entropy
@@ -12,12 +12,186 @@ from scipy.fft import rfft
 
 from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
 import pywt
-import tsfel
+from tsfel import feature_extraction as ft
 
 import matplotlib.pylab as plt
 from vibrodiagnostics import mafaulda
 
 
+
+def split_dataframe(dataframe: pd.DataFrame, parts: int = None) -> List[pd.DataFrame]:
+    if parts is None:
+        return [dataframe]
+
+    step = len(dataframe) // parts
+    return [
+        dataframe.iloc[i:i + step].reset_index(drop=True)
+        for i in range(0, len(dataframe), step)
+        if len(dataframe.iloc[i:i + step]) == step
+    ]
+
+
+def detrending_filter(dataframe: pd.DataFrame) -> pd.DataFrame:
+    for df in dataframe:
+        df[mafaulda.COLUMNS] = df[mafaulda.COLUMNS].apply(lambda x: x - x.mean())
+    return dataframe
+
+
+def time_features_calc(df: pd.DataFrame, col: str) -> List[Tuple[str, pd.DataFrame]]:
+    x = df[col]
+    features = [
+        ('std', [ft.calc_std(x)]),
+        ('skewness', [ft.skewness(x)]),
+        ('kurtosis', [ft.kurtosis(x)]),
+        ('rms', [ft.rms(x)]),
+        ('pp', [ft.pk_pk_distance(x)]),
+        ('crest', [np.max(np.absolute(x)) / ft.rms(x)]),
+        ('margin', [np.max(np.absolute(x)) / (np.mean(np.sqrt(np.absolute(x))) ** 2)]),
+        ('impulse', [np.max(np.absolute(x)) / np.mean(np.absolute(x))]),
+        ('shape', [ft.rms(x) / np.mean(np.absolute(x))]),
+        ('max', [ft.calc_max(x)])
+    ]
+    return [(f'{col}_{f[0]}', f[1]) for f in features]
+
+def frequency_features_calc(df: pd.DataFrame, col: str, window: int) -> List[Tuple[str, pd.DataFrame]]:
[…]

### 2023-11-27 notebooks/vibrodiagnostics/mafaulda.py

@@ -72,8 +72,8 @@ def preprocess(ts: pd.DataFrame):
     return (
         ts
         .assign(t = lambda x: x.index * (1 / FS_HZ))
-        .assign(mag_a = lambda x: np.hypot(x.ax, x.ay, x.ay))
-        .assign(mag_b = lambda x: np.hypot(x.bx, x.by, x.by))
+        # .assign(mag_a = lambda x: np.hypot(x.ax, x.ay, x.ay))
+        # .assign(mag_b = lambda x: np.hypot(x.bx, x.by, x.by))
         .reset_index()
         .assign(t = lambda x: x.index * (1 / FS_HZ))
         .set_index('t')

### 2023-11-27 notebooks/vibrodiagnostics/models.py

@@ -13,49 +13,6 @@ from sklearn.feature_selection import mutual_info_classif, f_classif
 from sklearn.feature_selection import SelectPercentile, SelectKBest
 
 
-def features_subset_online(filename, classes, axis, label, train_size=0.7, anomaly_severity=0.7):
-    features = pd.read_csv(filename).fillna(0)
-    features = fault_labeling(features, classes, anomaly_severity=anomaly_severity)
-
-    groups = [
-        df.sample(frac=1, random_state=10)
-        for i, df in (
-            features.sort_values(by='severity_level').groupby('severity_level')
-        )
-    ]
-    features = pd.concat(groups).reset_index(drop=True)
-
-    columns = features.columns.str.startswith(tuple(axis))
-    features.columns[columns]
-    X = features[features.columns[columns]]
-    y = features[label].astype('category').cat.codes
-
-    # X, y = anomalies_undersample(X, y, 0.1)
-    X_train, X_test, y_train, y_test = train_test_split(
-        X, y, train_size=train_size, random_state=10
-    )   
-    return (
-        X_train.sort_index(), y_train.sort_index(),
-        X_test.sort_index(), y_test.sort_index()
-    )
-
-
-def features_subset_offline(filename, classes, axis, label, train_size=0.7, anomaly_severity=0.7):
-    features = pd.read_csv(filename).fillna(0)
-    features = fault_labeling(features, classes, anomaly_severity=anomaly_severity)
-
-    columns = features.columns.str.startswith(tuple(axis))
-    X = features[features.columns[columns]]
-    y = features[label].astype('category')
-
-    # X, y = anomalies_undersample(X, y, 0.1)
-    X_train, X_test, y_train, y_test = train_test_split(
-        X, y, train_size=train_size, stratify=y, random_state=10
-    )
-    
-    return X_train, y_train, X_test, y_test
-
-
 def fault_labeling(dataset, classes, anomaly_severity=0.7, debug=False):
     # Faults
     df = dataset.copy()

### 2023-11-27 notebooks/vibrodiagnostics/selection.py

@@ -3,9 +3,10 @@ import math
 import pandas as pd
 import numpy as np
 import matplotlib.pyplot as plt
+import tsfel
 
 from river import stats, preprocessing
-from scipy.stats import pearsonr
+from scipy.stats import pearsonr, pointbiserialr
 from sklearn.feature_selection import mutual_info_classif, f_classif
 
 from sklearn.compose import ColumnTransformer
@@ -14,27 +15,22 @@ from sklearn.preprocessing import StandardScaler, MinMaxScaler
 
 
 # Dataset paths and attributes
-TIME_FEATURES_PATH = 'td_features.csv'
-FREQ_FEATURES_PATH = 'fd_features.csv'
+MAFAULDA_METADATA = 'mafaulda_metadata.csv'
+TIME_FEATURES_PATH = 'temporal_features.csv'
+FREQ_FEATURES_PATH = 'spectral_features.csv'
 TIME_AND_FREQ_FEATURES_PATH = 'time_freq_features.csv'
 
-TSFEL_FEATURES_PATH = 'tsfel_features.csv'
-TSFEL_TIME_FEATURES_PATH = 'tsfel_td_features.csv'
-TSFEL_FREQ_FEATURES_PATH = 'tsfel_fd_features.csv'
-TSFEL_STAT_FEATURES_PATH = 'tsfel_sd_features.csv'
-
-WPD_FEATURES_PATH = 'wpd_features.csv'
 
 TIME_FEATURES_PATH_ALL = 'all_td_features.csv'
 FREQ_FEATURES_PATH_ALL = 'all_fd_features.csv'
 WPD_FEATURES_PATH_ALL = 'all_wpd_features.csv'
 TSFEL_FEATURES_PATH_ALL = 'all_tsfel_features.csv'
 
-TD_COLUMNS = ['mean', 'std', 'skew', 'kurt', 'rms', 'pp', 'crest', 'margin', 'impulse', 'shape']
-FD_COLUMNS = [
-    'centroid', 'std', 'skew', 'kurt', 'roll-off', 'flux_mean', 'flux_std',
-    'noisiness', 'energy', 'entropy', 'negentropy'
-]
+# TD_COLUMNS = ['mean', 'std', 'skew', 'kurt', 'rms', 'pp', 'crest', 'margin', 'impulse', 'shape']
+# FD_COLUMNS = [
[…]

### 2023-12-03 thesis/chapters/02-analysis-B-features.tex
Come up with layout of summarization tables for best features

@@
 Multiple subsets of predictors produced by each evaluation metric can train several variants of a classification model.
-Sets of attributes can be likewise combined into an ensemble by majority voting, taking the best features out of every group.
+Sets of attributes can be combined into an ensemble by \emph{electoral system}.
+One such example is \textbf{majority voting} which chooses the best feature out of the group.
+\textbf{Rank product} unifies several feature orderings by computing the geometric mean of feature rank in every experiment realization~\cite{breitling_rank_2004}.

### 2023-12-03 thesis/chapters/03-design.tex
Come up with layout of summarization tables for best features

@@
 	- correlation point biserial, fisher, mutual information
-		- Sperman rank correlation: corr, f_stat, 1.000000
+		- Sperman rank correlation: corr, f\_stat, 0.98
 	- calculate feature rank
 		- Temporal (A) - Remove corr: pp, skewness, margin
-			pp	1.442250
-			std	2.080084
-			max	2.714418
-			rms	3.174802
-			skewness	6.082202
-			margin	6.868285
+			shape 	1.442250
+			std 	1.587401
+			rms 	2.620741
+			max 	4.308869
+			pp 	5.428835
+			skewness 	5.646216
+
+			std 	1.000000
+			rms 	2.000000
+			pp 	3.000000
+			max 	4.000000
+			skewness 	5.593445
 

### 2023-12-03 notebooks/vibrodiagnostics/models.py

@@ -140,10 +140,13 @@ def pipeline_v1(features, train, nfeat, func_select, multiclass=True, anomaly_ra
 
 def cross_cuts_3d(X_train, y_train):
     fig, ax = plt.subplots(1, 3, figsize=(15, 3))
+    labels = np.unique(y_train.to_numpy())
+    colors = sb.color_palette('tab10', len(labels))
+
     for i, axes in enumerate(((0, 1), (0, 2), (1, 2))):
         a, b = axes
 
-        for label, color in (('VM', 'purple'), ('N', 'green'), ('I', 'blue'), ('HM', 'orange')):
+        for label, color in zip(labels, colors):
             x = X_train.loc[
                 list(y_train[y_train == label].index), 
                 X_train.columns[a]

### 2023-12-07 thesis/chapters/03-design.tex
BVS inspection and data

--- 2023-11-27 thesis/chapters/03-design.tex
@@
 \section{Research questions}
+Open ended Research questions:
+	- Which time and frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?
+	- What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?
+	- How can the machinery faults be continuously identified based on collected events?
+
 Main goals:
@@
 \section{Data preparation}
+- Machinery:
+   - KALORIK BASIC Stand Fan TKGVT1037C  - height 125 cm, stable 60 cm cross base, 3 speed, 45 W, 45 cm fan diameter, 3 propelers
+   - AC unit VERTIV: Scroll Compressor: Copeland ZR16M3E-TWD-561 (2900 RPM @ 50 Hz; 9.7 kW (13 HP); 380/420V; 25 A) - 2 units
+   - Water pump: KSB Omega 300-560 B GB G F (2018, 1493 (1500) RPM @ 50 Hz; 500 kW elektromotor; power requirement: 380 kW) - 1 unit
+
+- Sensors:
+	- Accelerometer: ADXL335 ($\pm$3g, Bandwidth: 0.55 kHz)
+	- Noise density: 150 - 300 $\mu g / \sqrt{Hz}$ rms
+	- Resolution: 12 bits
+	- Axis: 3 axis
+	- Sensitvity: 300 mV/g
+	- Sample time: 400 ns (2.5 kHz)
+	- Voltage range: up to 1.8 V
+
+	- IIS3DWB (STEVAL-MKI208V1K) Digitálny (SPI), 1 / 3 axis, Resultution: 16 bits ADC, Range: 2 - 16g, Sensitvity: 0.061 mg/LSB pri 2g, Noise density:: 75 $\mu g / \sqrt{Hz}$, ODR: 26.7 kHz,Bandwidth: 5 - 6.3 kHz (-3 dB), FIFO: 3 kB (512 vzoriek)
+
+- EDA
+	- Time waveform
+	- Spectrogram
+	- Features: boxplot
+
+- Experiment subsets:
+	features = temporal, spectral
+	rpm_limit = False, True
+	hardware = shaft, bearings
+	target = fault, anomaly_60, anomaly_90
+	placement = A, B
+	online = False, True
+
 - Mafaulda dataset
@@
 	- Convert severity to 0 - 1 scale.
-		- Label samples above 0.5, 0.7, 0.9 as anomalous
+		- Label samples above 0., 0.9 as anomalous
 	- Choose rpm range 2900 $\pm$ 500 (around rotational speed of machinery with some spread, some features are correlated with rpm 
@@
 
+- \textbf{Measurements-SHC3.html}
+- \textbf{BVS-Measurements.html}
+
 \section{Feature relevance}
+- \textbf{FeatureSummary.html}
+
 - choose 3 features
@@
 	- correlation point biserial, fisher, mutual information
-		- Sperman rank correlation: corr, f_stat, 1.000000
+		- Sperman rank correlation: corr, f\_stat, 0.98
 	- calculate feature rank
 		- Temporal (A) - Remove corr: pp, skewness, margin
-			pp	1.442250
-			std	2.080084
-			max	2.714418
-			rms	3.174802
-			skewness	6.082202
-			margin	6.868285
-
-			(B)			
-			skewness	1.817121
-			rms	1.817121
-			std	2.289428
-			kurtosis	4.308869
 		- Spectral (A) - multiple window sizes 
@@
 \section{Nearest neighbour classifier}
+- \textbf{kNN.html}
 - kNN (fault and anomaly)

### 2023-12-16 thesis/chapters/02-analysis-A-CdM.tex
Come up with layout of summarization tables for best features
Write research questions in design section and place illustations

@@
 	\centering
-	\includegraphics[width=\textwidth]{assets/P-F-Curve.png}
+	\includegraphics[width=\textwidth]{assets/analysis/P-F-Curve.png}
 	\caption{P-F curve represents the evolution of the asset's health~\cite{jennions_integrated_2011}}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{assets/bath-tub-curve.png}
+	\includegraphics[width=0.6\textwidth]{assets/analysis/bath-tub-curve.png}
 	\caption{Bathtub curve~\cite{mohanty_machinery_2015}}
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{assets/complex-vibrations.png}
+	\includegraphics[width=0.6\textwidth]{assets/analysis/complex-vibrations.png}
 	\caption{Complex machinery vibrations~\cite{davies_handbook_2012}}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{assets/transducer-response.png}
+	\includegraphics[width=0.8\textwidth]{assets/analysis/transducer-response.png}
 	\caption{The transducer linear response and resonance in tolerance intervals~\cite{noauthor_iso_2002}}
@@
 Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation.
-According to the bathtub curve~(Fig.~\ref{fig:bath-tub-curve}) reference signatures should be obtained after the initial part wear-in period.
+According to the bathtub curve~(Fig.~\ref{fig:bathtub-curve}) reference signatures should be obtained after the initial part wear-in period.
 The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.

### 2023-12-16 thesis/chapters/02-analysis-B-features.tex
Write research questions in design section and place illustations

@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{assets/iir-1-dc-blocker-band.jpg}
+	\includegraphics[width=0.7\textwidth]{assets/analysis/iir-1-dc-blocker-band.jpg}
 	\caption{Transfer function of 1st order DC blocker filters ~\cite{tittelbach-helmrich_digital_2021}}
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{assets/adaptive-filter.png}
+	\includegraphics[width=0.8\textwidth]{assets/analysis/adaptive-filter.png}
 	\caption{Adaptive noise cancellation filter diagram}
@@
 TSA averages time-domain waveform over $N$ points and aligns it to a synchronization pulse with period $T$ (Equation~\ref{equ:tsa-average}).
-This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}
 
@@
 \end{align}\end{ceqn}
+
+This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/stft-spectrogram-sample.png}
+        \includegraphics[width=\textwidth]{assets/analysis/stft-spectrogram-sample.png}
         \caption{STFT \& Gaussian window}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/tet-spectrogram-sample.png}
+        \includegraphics[width=\textwidth]{assets/analysis/tet-spectrogram-sample.png}
         \caption{TET}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/wt-spectrogram-sample.png}
+        \includegraphics[width=\textwidth]{assets/analysis/wt-spectrogram-sample.png}
         \caption{CWT \& Morlet wavelet}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/sst-spectrogram-sample.png}
+        \includegraphics[width=\textwidth]{assets/analysis/sst-spectrogram-sample.png}
         \caption{SST}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/DWT.png}
+        \includegraphics[width=\textwidth]{assets/analysis/DWT.png}
         \caption{Discrete wavelet transform}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/WPD.png}
+        \includegraphics[width=\textwidth]{assets/analysis/WPD.png}
         \caption{Wavelet packet decomposition}
@@
     \centering
-    \includegraphics[width=0.9\textwidth]{assets/EWT.png}
+    \includegraphics[width=0.9\textwidth]{assets/analysis/EWT.png}
     \caption{Empirical wavelet segmentation of Fourier spectrum~\cite{gilles_empirical_2013}}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/MKCD-EWT.png}
+        \includegraphics[width=\textwidth]{assets/analysis/MKCD-EWT.png}
         \caption{MKCD-EWT~\cite{li_fault_2019}}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/PCHIP-EWT.png}
+        \includegraphics[width=\textwidth]{assets/analysis/PCHIP-EWT.png}
         \caption{PCHIP-EWT~\cite{zhuang_improved_2020}}

### 2023-12-16 thesis/chapters/02-analysis-D-datasets.tex
Restructure folders
Incremental learning in thesis
Write research questions in design section and place illustations

@@
 \cite{ribeiro_rotating_2017}.
-The datasets listed below are also publically available online in Comma-Separated Values files.
 
@@
 \begin{subfigure}[b]{0.48\textwidth}
-	\includegraphics[width=\textwidth]{assets/mafaulda-simulator.png}
+	\includegraphics[width=\textwidth]{assets/analysis/mafaulda-simulator.png}
 	\caption{Schematic diagram \cite{pestana-viana_influence_2016}}
@@
 \begin{subfigure}[b]{0.48\textwidth}
-	\includegraphics[width=\textwidth]{assets/machinery-fault-simulator.jpg}
+	\includegraphics[width=\textwidth]{assets/analysis/machinery-fault-simulator.jpg}
 	\caption{Mechanical construction \cite{noauthor_spectraquest_nodate}}
@@
 2., 3., 4.       & \begin{tabular}[c]{@{}l@{}}Underhang bearing accelerometer \\ (inner - between the rotor and motor)\\ - axial, radial, tangential direction\end{tabular}           \\ \hline
-5., 6., 7.       & \begin{tabular}[c]{@{}l@{}}Overhang  bearing accelerometer \\ (Outer - outside most position after the rotor)\\ - axial, radial, tangential direction\end{tabular} \\ \hline
+5., 6., 7.       & \begin{tabular}[c]{@{}l@{}}Overhang bearing accelerometer \\ (outer - outside most position after the rotor)\\ - axial, radial, tangential direction\end{tabular} \\ \hline
 8.               & Microphone                                                                                                                                                         \\ \hline
@@
 \begin{subfigure}[b]{0.48\textwidth}
-	\includegraphics[width=\textwidth]{assets/cwru-test-stand-2.png}
+	\includegraphics[width=\textwidth]{assets/analysis/cwru-test-stand-2.png}
 	\caption{Schematic diagram \cite{song_bearing_2022}}
@@
 \begin{subfigure}[b]{0.48\textwidth}
-	\includegraphics[width=\textwidth]{assets/cwru-test-stand.png}
+	\includegraphics[width=\textwidth]{assets/analysis/cwru-test-stand.png}
 	\caption{Mechanical construction \cite{yuhong_new_2021}}
@@
 \centering
-\includegraphics[width=0.7\textwidth]{assets/rotating-shaft.jpg}
+\includegraphics[width=0.7\textwidth]{assets/analysis/rotating-shaft.jpg}
 \caption{Motor driving shaft in unbalance measurement \cite{mey_machine_2020}}
@@
 \end{tabular}
-\caption{`Unbalance on the rotating shaft' dataset description of columns}
+\caption{``Unbalance on the rotating shaft'' dataset description of columns}
 \end{table}

### 2023-12-16 thesis/chapters/03-design.tex
Write research questions in design section and place illustations

@@
 \chapter{Design} \label{section:design}
-In the spirit of an extensive overview of standardized procedures of industrial vibration acquisition and monitoring, the methods in feature selection, feature selection, and machine diagnostics from vibration signals, we propose a preliminary design of elements in the sensor network capable of discriminating machinery faults.
+The design phase sets out to elaborate on the scenarios for experiments with IoT device.
+In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
+Noted observations are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
+Finally, the network infrastructure layout is provided where we propose optimizations in the functions of the components.
 
+\section{Research questions}
+This thesis aims to provide answers to four broader formulated research questions.
+The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
+The \textbf{research questions} are:
+\begin{enumerate}
+    \itemsep0pt
+	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
+	\item What is the reduction in transmission goodput when chosen signal features are used?
+	\item What accuracies of prediction models can be achieved with various feature subsets? 
+	\item How can machinery faults be continuously identified and predicted based upon collected events?
+\end{enumerate}
+
+\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
+\begin{itemize}
+    \itemsep0pt
+	\item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
+	\item Establish a list of conditions that should be later investigated in the experimental setting.
+	\item Prepare dataset to be used in conjunction with statistical learning models, namely by identifying labels and balancing classes.
+	\item Find the best subsets of features in temporal and spectral domain with previously analyzed feature extraction and selection methods.
+	\item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
+	\item Combine feature selection with online machine learning model.
+	\item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
+	\item Develop hardware and implement its firmware to obtain such measurement in the quality demanded by vibrodiagnostics standards.
+\end{itemize}
+
+However, we leave out from our efforts experiments on the data features from wavelets and on the peaks in the spectral domain.
+The reason is that we did not find a way to represent extracted features more succinctly as a one number.
+We also did not discover a strategy for choosing only the relevant frequency bins.
+The assembled description is kept to empower further research on that topic.
+
+The tasks are associated with \textbf{risks} impacting their successful completion.
+The possible risks are assessed and prioritized.
+The most notable risk encountered early on is that the machine in the real environment will not be available for vibration measurements.
+We successfully eliminated the risk by contacting and establishing collaboration with alternative partners.
+The additional risks are that the repeated measurements will not be consistent and fault modes could not be reliably differentiated and labeled in the dataset because each machine is unique in its structure.
+Related is the risk that not enough data is obtained from various classes.
+Also, suggestions can made by exploring the MaFaulDa dataset which will not be applicable in the practice.
+All these risks have to be regularly reevaluated to achieve our goals.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.44\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
+        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
+        \caption{Spectral domain in radial direction (y). FFT with Hann window of length $2^{14}$ ($\approx 328$ ms)}
+    \end{subfigure} 
+    \caption{Signals at 1 s timestamp from inner bearing in each fault category with the highest fault severity}
+\end{figure}
+
+\section{Dataset preparation}
+
+\section{Feature relevance}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-fault.png}
+        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-fault.png}
+        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-anomaly90.png}
+        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-anomaly90.png}
+        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
+    \end{subfigure}
+    \caption{Confusion matrix of batch kNN algorithm predictions in temporal and spectral domain for two predicted variables measured on inner bearing.}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-train.png}
+        \caption{Testing set}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-test.png}
+        \caption{Training set}
+    \end{subfigure}
+    \caption{Range of prediction accuracy in all kNN models with subset of 3 features. Subplots show three different predicted variables.}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-train}
+        \caption{Testing set}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-test}
+        \caption{Training set}
+    \end{subfigure} 
+    \caption{Batch kNN algorithm prediction accuracy with various feature sets.}
+\end{figure}
+
+% Number of neighbors (graphs)
+
+\section{Online kNN model}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
+        \caption{Training set and fault as predicted variable}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-test.png}
+        \caption{Testing set and fault as predicted variable}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-train.png}
+        \caption{Training set and medium anomaly severity as predicted variable}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-test.png}
+        \caption{Training set and medium anomaly severity as predicted variable}
+    \end{subfigure}
+    \caption{Label order in progressive valuation}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-temporal-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-spectral-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-temporal-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-spectral-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \caption{Gradual learning}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \caption{Gradual learning accuracy with delay}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \caption{Gradual learning with delay}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \caption{Gradual learning and skip labels}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-anomaly60.png}
+        \caption{}
+    \end{subfigure}
+    \caption{Gradual learning accuracy with delay}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-temporal.png}
+        \caption{}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-spectral.png}
+        \caption{}
+    \end{subfigure}
+    \caption{PCA 2 components to visualize results and mistakes of online learning on all features}
+\end{figure}
+)
+
+\section{Measuments on machinery}
+- Machinery
+% Enum list
+
+- Sensors
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
+\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
+\textbf{Bus}                                     & Analog           & SPI                \\ \hline
+\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
+\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
+\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
+\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
+\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
+\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
+\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
+\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
+\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
+\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
+\end{tabular}
+\caption{Accelerometers}
+\end{table}
+
+- Preliminary measurements
+% Waveforms
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{assets/design/hw-block-schematic.png}
+	\caption{Sensor unit hardware block diagram}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.44\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
+        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
+        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
+    \end{subfigure} 
+    \caption{Signals at 5 s timestamp}
+\end{figure}
+
+\newpage
 \section{Machine learning pipeline}
-
-Mafaulda dataset
-Jupyter notebook - Python
 \begin{enumerate}
@@
 \centering
-\includegraphics[width=0.9\textwidth]{assets/ml-lifecycle.png}
+\includegraphics[width=0.9\textwidth]{assets/analysis/ml-lifecycle.png}
 \caption{Machine learning lifecycle of feature discovery}
@@
 
-\section{Research questions}
-Open ended Research questions:
-	- Which time and frequency features can be extracted from vibrational signals to provide an accurate record of machinery faults?
-	- What are the savings in transmission bandwidth when chosen signal features are used in comparison to raw sampled measurement or lossless compression techniques?
-	- How can the machinery faults be continuously identified based on collected events?
-
-Main goals:
-	- How does vibration data look like (spectral and time domain)?
-	- Create dataset of machinery vibrations
-	- Reduce number of features (samples) send from edge device - to minimal amount
-	- Adapt to features changing over time (RiverML can handle it, find proof)
-	- Evaluate model performance on all features and different feature sets
-	- Keep in mind: data ordering!
-
 \section{Data preparation}
-- Machinery:
-   - KALORIK BASIC Stand Fan TKGVT1037C  - height 125 cm, stable 60 cm cross base, 3 speed, 45 W, 45 cm fan diameter, 3 propelers
-   - AC unit VERTIV: Scroll Compressor: Copeland ZR16M3E-TWD-561 (2900 RPM @ 50 Hz; 9.7 kW (13 HP); 380/420V; 25 A) - 2 units
-   - Water pump: KSB Omega 300-560 B GB G F (2018, 1493 (1500) RPM @ 50 Hz; 500 kW elektromotor; power requirement: 380 kW) - 1 unit
-
-- Sensors:
-	- Accelerometer: ADXL335 ($\pm$3g, Bandwidth: 0.55 kHz)
-	- Noise density: 150 - 300 $\mu g / \sqrt{Hz}$ rms
-	- Resolution: 12 bits
-	- Axis: 3 axis
-	- Sensitvity: 300 mV/g
-	- Sample time: 400 ns (2.5 kHz)
-	- Voltage range: up to 1.8 V
-
-	- IIS3DWB (STEVAL-MKI208V1K) Digitálny (SPI), 1 / 3 axis, Resultution: 16 bits ADC, Range: 2 - 16g, Sensitvity: 0.061 mg/LSB pri 2g, Noise density:: 75 $\mu g / \sqrt{Hz}$, ODR: 26.7 kHz,Bandwidth: 5 - 6.3 kHz (-3 dB), FIFO: 3 kB (512 vzoriek)
-
-- EDA
-	- Time waveform
-	- Spectrogram
-	- Features: boxplot
-
-- Experiment subsets:
-	features = temporal, spectral
-	rpm_limit = False, True
-	hardware = shaft, bearings
-	target = fault, anomaly_60, anomaly_90
-	placement = A, B
-	online = False, True
-
-- Mafaulda dataset
-	- Choose 4 faults - normal (N), imbalance (I), vertical (VM) and horizonal misalignment (HM)
-	- Convert severity to 0 - 1 scale.
-		- Label samples above 0., 0.9 as anomalous
-	- Choose rpm range 2900 $\pm$ 500 (around rotational speed of machinery with some spread, some features are correlated with rpm 
-	- Counts before split: 
-		- Split to 5 parts of 1 second intervals
-	- Two measurement points A, B
-	- Detrending by removing mean
-	- Calculate features: temporal, spectral (in 5 window sizes): welch averaging, hann window
-
-	- Batch: 
-		- Balancing dataset with oversampling minority classes	
-		- Hold-out validation - split to train and test set
-	- Online: Order by severity
-
-- Measurement of custom datasets 
-	- one 3-axis accelerometer on top of scroll compressor of air conditioning
-		- one in the base to capture noise
-	- water pump
-
-	- columns: t, x, y, z: rpm
-	- 20 s recordings - split to 5 parts - extract features
-	- do PCA to explore see differences
-	- label as worse, better (classes are hard to provide)
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{assets/sensor-network.png}
+\includegraphics[width=0.7\textwidth]{assets/design/sensor-network.png}
 \caption{Sensor network components}

### 2023-12-16 thesis/chapters/03-design.tex
Activity diagram of data preparation

@@
 \section{Research questions}
-This thesis aims to provide answers to four broader formulated research questions.
+This thesis aims to provide answers to four research questions formulated in broader sense.
 The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
 The \textbf{research questions} are:
-\begin{enumerate}
+\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
     \itemsep0pt
@@
 
+\section{Dataset exploration}
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\textwidth]{assets/design/activity-data-exploration.png}
+	\caption{Activity diagram of MaFaulDa dataset preprocessing}
+\end{figure}
+
 \begin{figure}[ht]
@@
         \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
-        \caption{Spectral domain in radial direction (y). FFT with Hann window of length $2^{14}$ ($\approx 328$ ms)}
+        \caption{Frequency spectrum in radial direction (y)}
     \end{subfigure} 
@@
 
-\section{Dataset preparation}
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{rrrrrllll}
+\cline{1-5}
+\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Fault}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} &                               &                               &                               &                               \\ \cline{2-5}
+\multicolumn{1}{|l|}{}                                & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                   & \multicolumn{1}{r|}{16 (3\%)}                              & \multicolumn{1}{r|}{16 (3\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                 & \multicolumn{1}{r|}{173 (34\%)}                            & \multicolumn{1}{r|}{173 (36\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                 & \multicolumn{1}{r|}{118 (23\%)}                            & \multicolumn{1}{r|}{118 (25\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{67 (13\%)}                             & \multicolumn{1}{r|}{69 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                 & \multicolumn{1}{r|}{61 (12\%)}                             & \multicolumn{1}{r|}{34 (7\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{69 (14\%)}                             & \multicolumn{1}{r|}{68 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{Total}}                  & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} \\ \cline{1-5}
+\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
+\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
+\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
+\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
+                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
+                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{rrrrrrrrr}
+\cline{1-5}
+\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 60\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
+\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &
+\end{tabular}
+\end{table}
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{rrrrrrrrr}
+\cline{1-5}
+\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 90\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
+\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
+\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
+                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &
+\end{tabular}
+\end{table}
 
@@
 \end{figure}
-)
 

### 2023-12-17 thesis/chapters/02-analysis-A-CdM.tex
Write data exploration in design

@@
 The machine description includes its identifier and type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
-Measurement parameters are to be recorded alongside the measurement value itself such as timestamp, transducer type, sensor location and orientation in MIMOSA code, measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
+Measurement parameters are to be recorded alongside the measurement value itself such as timestamp, transducer type, sensor location and orientation in \textbf{MIMOSA convention} (Machinery Information Mangement Open System Alliance), measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
 

### 2023-12-17 thesis/chapters/02-analysis-D-datasets.tex
Write data exploration in design

@@
 Observations were conducted in three cardinal axes simultaneously with 2 sets of accelerometers each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}).
-Additionally, a magnetic tachometer produced a pulse on shaft turn.
+Additionally, a magnetic speedometer produced a pulse on shaft turn.
 The cardioid condenser microphone recorded sound emissions with a frequency range 20~Hz - 20~kHz.
@@
 \textbf{Columns} & \textbf{Description}                                                                                                                                               \\ \hline
-1.               & \begin{tabular}[c]{@{}l@{}}Pulse with modulation of tachometer signal \\ to estimate rotation frequency  (in TTL levels)\end{tabular}                              \\ \hline
+1.               & \begin{tabular}[c]{@{}l@{}}Pulse with modulation of speedometer signal \\ to estimate rotation frequency  (in TTL levels)\end{tabular}                              \\ \hline
 2., 3., 4.       & \begin{tabular}[c]{@{}l@{}}Underhang bearing accelerometer \\ (inner - between the rotor and motor)\\ - axial, radial, tangential direction\end{tabular}           \\ \hline
@@
 
-The accelerometers used are piezoelectric and have a frequency range of up to 10 KHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
+The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
 These sensor parameters are the same as in the case of MaFaulDa.

### 2023-12-17 thesis/chapters/03-design.tex
Write data exploration in design

@@
 \noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
-\begin{itemize}
+\begin{todolist}
     \itemsep0pt
@@
 	\item Develop hardware and implement its firmware to obtain such measurement in the quality demanded by vibrodiagnostics standards.
-\end{itemize}
+\end{todolist}
 
-However, we leave out from our efforts experiments on the data features from wavelets and on the peaks in the spectral domain.
-The reason is that we did not find a way to represent extracted features more succinctly as a one number.
+However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain.
+The reason is that we did not find a way to represent extracted features more succinctly as a single number.
 We also did not discover a strategy for choosing only the relevant frequency bins.
-The assembled description is kept to empower further research on that topic.
+The assembled description is retained to lead further research on that topic.
+\\
 
-The tasks are associated with \textbf{risks} impacting their successful completion.
+The tasks are associated with certain \textbf{risks} impacting their successful completion.
 The possible risks are assessed and prioritized.
-The most notable risk encountered early on is that the machine in the real environment will not be available for vibration measurements.
+The most notable risk encountered is that the machine in the real environment will not be available for vibration measurements.
 We successfully eliminated the risk by contacting and establishing collaboration with alternative partners.
+
 The additional risks are that the repeated measurements will not be consistent and fault modes could not be reliably differentiated and labeled in the dataset because each machine is unique in its structure.
-Related is the risk that not enough data is obtained from various classes.
-Also, suggestions can made by exploring the MaFaulDa dataset which will not be applicable in the practice.
-All these risks have to be regularly reevaluated to achieve our goals.
+Related is the risk that not enough data is obtained from various classes and suggestions made by exploring the MaFaulDa dataset not be applicable in practice.
+All these risks have to be tracked and regularly reevaluated to achieve our goals.
 
 \section{Dataset exploration}
+In establishing the validity of methods to be deployed on the sensor node we explore the MaFaulDa dataset.
+It is the largest known machinery fault collection, so it is possible to create multiple subsets based on requested conditions.
+
+One representative recording is first selected in each available fault category.
+The sample is visualized and statistically described in both temporal and spectral domains.
+A whole step-by-step procedure is outlined in the activity diagram (Fig.~\ref{fig:design:mafaulda-preprocessing}).
 
@@
 	\caption{Activity diagram of MaFaulDa dataset preprocessing}
+	\label{fig:design:mafaulda-preprocessing}
 \end{figure}
+
+MaFaulda contains 1951 records labeled with inducted faults of increasing severity.
+The defects were set up on the machine simulator as is mentioned in the part about datasets.
+Time series of the triaxial piezoelectric accelerometers in separate files have a sampling frequency of 50 kHz.
+
+These vibration sensors are placed in two positions.
+The first placement is around the inner underhang bearing named \emph{A} which is closer to the motor.
+The second location is around the outer overhang bearing denoted as \emph{B} position.
+
+\subsection{Fault annotations}
+The dataset has annotations altogether for 10 classes of faults of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
+Some categories are redundant or irrelevant for a given sensor position.
+
+Therefore rotor shaft misalignements in vertical and horizontal directions are merged into one joint group. Depending on the chosen bearing position only records having relevant labels are considered.
+
+This means that fault classification solely concerns bearing in the direct contact and shaft mechanically passing through it.
+The bearings affect each other, but the effect on the opposite side should appear via a common interconnection shaft.
+
+In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
+In the step of choosing the accelerometer location records pointing to the other bearing as a source of the malfunction are discarded.
+Then the next action renames the labels to be better recognizable and unite the same phenomena.
+
+Groups of identified machine defects are additionally characterized by altered masses attached or motor shaft displacement shifts.
+The set amount is sorted in ascending order separating \textbf{multiple event severities}.
+However, the count of severity levels is not identical in every group.
+Levels are hence scaled into the range between zero and one using a min-max scaler.
+Scaling is applied to classes separately.
+
+The strength of the recorded response by the underlying defect is also dependent on the shaft \textbf{rotational speed}.
+Speed in rpm is calculated from pulsed speedometer output.
+It is the average distance between two successive rising edges:
+\begin{ceqn}\begin{align}
+\mathrm{rpm} = 60 \;/\; \overline{\Delta t}
+\end{align}\end{ceqn}
+
+\textbf{A specimen waveform} is picked from each fault class to illustrate their superficial differences.
+Recordings are filtered to get one of the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz)  to see the patterns most pronounced.
+The baseline class sample is chosen according to fixed rotor speed.
+
+\subsection{Signal filters}
+The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
+Immediately follows a digital IIR Butterworth \textbf{ low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
+
+Before the low pass filter usage, the peak at 20 kHz with sideband was present as an unwanted artifact.
+It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
+At the same time, such frequency is outside the range of any feasible MEMS accelerometer.
 
@@
         \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
-        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
+        \caption{Temporal domain waveforms}
+        \label{fig:design:fault-temporal-waveform}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
-        \caption{Frequency spectrum in radial direction (y)}
+        \caption{Spectra in radial direction}
+        \label{fig:design:fault-spectral-waveform}
     \end{subfigure} 
-    \caption{Signals at 1 s timestamp from inner bearing in each fault category with the highest fault severity}
+    \caption{Signals for each fault category with the highest fault severity at 2500 rpm}
 \end{figure}
 
+Temporal domain waveforms of the 300 ms signal slice are shown in the graphs in Figure \ref{fig:design:fault-temporal-waveform}.
+Subplots for radial, tangential, and axial directions are laid out in columns from left to right.
+Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
+
+The frequency spectrum in Figure \ref{fig:design:fault-spectral-waveform} is obtained by FFT and Hann window of length $2^{14}$.
+The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz.
+The graph has been cropped in both axes to make the most important peaks visible.
+
+\subsection{Statistical tests}
+%TODO boxplot in featue selection
+%TODO images of machines
+%TODO
+
+\subsection{Feature extraction}
+%TODO - activity diagram, implementation and value counts
 \begin{table}[ht]

### 2023-12-17 thesis/chapters/03-design.tex
Statistical tests and boxplots

@@
 
-\textbf{A specimen waveform} is picked from each fault class to illustrate their superficial differences.
-Recordings are filtered to get one of the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz)  to see the patterns most pronounced.
+\textbf{One specimen waveform} is picked from each fault class to illustrate their superficial differences.
+Recordings are filtered to get the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz)  to see the patterns most pronounced.
 The baseline class sample is chosen according to fixed rotor speed.
@@
 The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
-Immediately follows a digital IIR Butterworth \textbf{ low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
+Immediately follows a digital IIR Butterworth \textbf{low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
 
@@
     \end{subfigure} 
-    \caption{Signals for each fault category with the highest fault severity at 2500 rpm}
+    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
 \end{figure}
@@
 \subsection{Statistical tests}
-%TODO boxplot in featue selection
-%TODO images of machines
-%TODO
+The statistical tests and visual checks are conducted to assess \textbf{normality and stationary} of time series.
+Half a second of amplitude samples are used from every sensor channel.
+These 25 thousand observations are downsampled tenfold to $2500$ points.
+
+\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from normal distribution under most circumstances.
+The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms.
+\textbf{Quantile–quantile plots} confirm non-normal distribution because of the striking samples tilt to the diagonal line.
+
+\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root 
+(${p < 0.001}$). The same is confirmed with the \textbf{autocorrelation} function shape. It denotes that the stochastic process is stationary as oscillation is bounded.
+
+\section{Feature relevance}
 
 \subsection{Feature extraction}
+% tsfel, scipy
+
+%A) **Activity diagram** (Image)
+%1. Label recording using filename path in zip: fault, severity, seq
+%2. Split each recording to 5 parts (1 second - 50000 samples)
+%3. Calculate rpm (out of impulse tachometer = prominence=3, width=50, 60 / $\Delta t$)
+%4. Remove mean - DC component filter
+%5. Filter frequencies: cutoff = 10 kHz (Butterworth lowpass filter of 5 order) - peak 20 kHz (not possibe to capture)
+%6. Label with 6 classes of faults, and 2 anomaly classes (based on arbitrary severity 0.6 and 0.9)
+%7. X - extract temporal features in all axis for both bearings A, B: ax/ay/az_feature_name
+%8. X - window size: windows and welch averaging (2**14 = 16384 samples, 3 okná, 3.05 Hz resolution)
+
+%B) **Counts of classes** (to table and Sum) - **Unbalanced dataset**  (2 Tables - `RPM unlimited | RPM limited`)
+
+%C) **Correlation of features with rpm**:
+%    - Temporal: mostly **very low** (25% - 75% quantile: 0.07 - 0.20,
+%    - Spectral: mostly **very low** for all 5 window sizes: 25% (0.08)  - 75% (0.23)
+
+%C) **Correlation among features**:
+%- Feature correlations (> 0.95):
+%    - Temporal:
+%        - std, rms: 1.0
+%        - std, pp, rms, 0.96
+%        - pp, max, 0.98
+%        - crest, margin, implulse, 0.99
+%    - Spectral:
+%        - skewness, kurtosis, 0.98
+
 %TODO - activity diagram, implementation and value counts
+
 \begin{table}[ht]
+\centering
 \renewcommand{\arraystretch}{1.2}
 \begin{tabular}{rrrrrllll}
-\cline{1-5}
-\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Fault}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} &                               &                               &                               &                               \\ \cline{2-5}
-\multicolumn{1}{|l|}{}                                & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                   & \multicolumn{1}{r|}{16 (3\%)}                              & \multicolumn{1}{r|}{16 (3\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                 & \multicolumn{1}{r|}{173 (34\%)}                            & \multicolumn{1}{r|}{173 (36\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                 & \multicolumn{1}{r|}{118 (23\%)}                            & \multicolumn{1}{r|}{118 (25\%)}                           &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{67 (13\%)}                             & \multicolumn{1}{r|}{69 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                 & \multicolumn{1}{r|}{61 (12\%)}                             & \multicolumn{1}{r|}{34 (7\%)}                             &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{69 (14\%)}                             & \multicolumn{1}{r|}{68 (14\%)}                            &                               &                               &                               &                               \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{Total}}                  & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} & \multicolumn{1}{r}{\textbf{}} \\ \cline{1-5}
-\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
-\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
-\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
-\textbf{}                                             &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
-                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          \\
-                                                      &                                                 &                                                 &                                                            &                                                           & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}          & \multicolumn{1}{r}{}
+\cline{1-3}
+\multicolumn{1}{|l|}{\textbf{Fault}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                    \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                  \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                  \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                  \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}
+
+\multicolumn{1}{|l|}{\textbf{Anomaly 60\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}          \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}          \\ \cline{1-3}
+
+\multicolumn{1}{|l|}{\textbf{Anomaly 90\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{1227 (85\%)}                 & \multicolumn{1}{r|}{1197 (86\%)}         \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{211 (15\%)}                 & \multicolumn{1}{r|}{196 (14\%)}         \\ \cline{1-3}
+\multicolumn{1}{|r|}{\textbf{Total}}                                                                            & \multicolumn{1}{r|}{\textbf{1438} (100\%)}                       & \multicolumn{1}{r|}{\textbf{1393} (100\%)}               \\ \cline{1-3}
 \end{tabular}
+\caption{Class count in all rotational speeds}
 \end{table}
 
-\begin{table}[ht]
-\renewcommand{\arraystretch}{1.2}
-\begin{tabular}{rrrrrrrrr}
-\cline{1-5}
-\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 60\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
-\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &
-\end{tabular}
-\end{table}
+\subsection{Data volume savings}
+%TODO - reduction in data goodput (without metadata): data kept ratio = (nfeat * dim) / (ch * fs * t)
+% - (21 * 3) / (3 * 25000 * 1)  (realistic fs because of low pass, we could dowsample by the factor 2) (inverse ratio is data reduction factor =  11904 times less)
+% - 7 times less features: (3*3) / (25000*1*3) (83333 times less than original)
 
-\begin{table}[ht]
-\renewcommand{\arraystretch}{1.2}
-\begin{tabular}{rrrrrrrrr}
-\cline{1-5}
-\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Anomaly\\ 90\% severity\end{tabular}}}} & \multicolumn{2}{l|}{\textbf{All rotational speeds}}                                               & \multicolumn{2}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Selected rotational speeds \\ 2500 $\pm$ 500 rpm\end{tabular}}} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{2-5}
-\multicolumn{1}{|l|}{}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}}            & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}}           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}                 & \multicolumn{1}{r|}{375 (74\%)}                            & \multicolumn{1}{r|}{354 (74\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}                 & \multicolumn{1}{r|}{129 (26\%)}                            & \multicolumn{1}{r|}{124 (26\%)}                           & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} & \multicolumn{1}{l}{} \\ \cline{1-5}
-\multicolumn{1}{|r|}{\textbf{Total}}                                                                                 & \multicolumn{1}{r|}{1438}                       & \multicolumn{1}{r|}{1393}                       & \multicolumn{1}{r|}{504}                                   & \multicolumn{1}{r|}{478}                                  & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\ \cline{1-5}
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-\textbf{}                                                                                                       & \textbf{}                                       & \textbf{}                                       & \textbf{}                                                  & \textbf{}                                                 & \textbf{}            & \textbf{}            & \textbf{}            & \textbf{}            \\
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-\textbf{}                                                                                                       &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &                      \\
-                                                                                                                &                                                 &                                                 &                                                            &                                                           &                      &                      &                      &
-\end{tabular}
-\end{table}
+% parameters for measurements
+% 1. number of measurement places (bearings) -- number of machines * places
+% 2. sampling frequency (fs) = const
+% 3. interval between measuremnts (s) 
+% 4. duration of measuremnt (s)
 
-\section{Feature relevance}
+% Requiremnts classic per bearing (per year): 5s * 20khz * 3dim (365 * 24 = every hour) = (sample is 4/8B just multiplication factor) =  300 kS per measuremnts * 8760 measuremnts = 2.628 GSamples per year per placement
+% Frequncy spectra with 1 Hz res = 1*10kHz*3= 30kS = 262.8 MSamples
+% All features = 9S  => 78.84 KSamples / year (per year as much as per 3 spectra measurements)
+
+% According to standars is rms velocity enough => indicator of fault (but not of the type)
+
+\section{Nearest neighbour classifier}
+
+\subsection{Batch model}
 
@@
 
-\section{Online kNN model}
+\subsection{Online kNN model}
 
@@
 
-\section{Measuments on machinery}
-- Machinery
+\section{Vibration measurement plan}
+
+\subsection{Machinery}
 % Enum list
 
-- Sensors
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=0.5\textwidth]{assets/design/machine-fan.jpg}
+        \caption{Stand fan Kalorik}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=0.5\textwidth]{assets/design/machine-compressor.jpg}
+        \caption{Scroll compressor Copeland}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
+        \caption{Water pump KSB Omega}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
+        \caption{Water pump Sigma}
+    \end{subfigure}
+    \caption{Machine}
+\end{figure}
+
+\subsection{Sensors}
 
@@
 
-- Preliminary measurements
-% Waveforms
-
 \begin{figure}[h]
@@
 
+\subsection{Preliminary measurements}
 \begin{figure}[ht]
@@
 
-\section{Data preparation}
-
-- \textbf{Measurements-SHC3.html}
-- \textbf{BVS-Measurements.html}
-
-\section{Feature relevance}
-- \textbf{FeatureSummary.html}
-
-- choose 3 features
-- supervised
-	- highly correlated features >= 0.9:
-		- Temporal domain (A)
-			- std, rms, 1.000000
-			- margin, impulse, 0.999079
-			- crest, impulse, 0.996807
-			- crest, margin,	0.992548
-			- pp, max, 0.970055
-			- max, (std, rms), 0.938198
-			- pp, (std, rms), 0.938180 / 0.928
-		- Spectral domain (A)
-			- same feature in different window sizes (0.99)
-			- kurtosis, skewness, 0.980618
-			- std, energy, 0.960110
-			- entropy, noisiness, 0.945514
-
-	- calcultate euclidian measure of feature 
-	- correlation point biserial, fisher, mutual information
-		- Sperman rank correlation: corr, f\_stat, 0.98
-	- calculate feature rank
-		- Temporal (A) - Remove corr: pp, skewness, margin
-		- Spectral (A) - multiple window sizes 
-			- (energy, roll off, std)
-
-- online learning features
-	- evolution of feature importace
-
-\section{Nearest neighbour classifier}
-- \textbf{kNN.html}
-- kNN (fault and anomaly)
-	- Offine (baseline)
-	- Online (evolution)
-- parameters: k-neigh, distance
-- metrics: accuracy, precision, recall
-
-\section{Clustering}
-- Density based clustering
-	- DBSCAN (all features, PCA, subset of best)
-	- DenStream (all features, subset of best)
-
-\section{Novelty detection}
-- Offline (Isolation forest)
-- Online (Half-space Tree)
-
 \section{Infrastructure deployment}

### 2023-12-20 thesis/chapters/03-design.tex
Principal components analysis

@@
 \subsection{Fault annotations}
-The dataset has annotations altogether for 10 classes of faults of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
+The MaFaulDa has annotations altogether for 10 classes of faults of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
 Some categories are redundant or irrelevant for a given sensor position.
@@
 \section{Feature relevance}
+Attributes described in section \ref{section:feature-extraction} are independently summarized from each sensor position and direction.
+Then similarity score of features is ascertained in relation to a predicted variable.
+The subset of the strongest predictors is chosen based on the order of their perceived importance.
 
 \subsection{Feature extraction}
-% tsfel, scipy
+Each file in the MaFaulDa contains 6 accelerometer channels.
+In the feature extraction process sequence of samples is split into 5 parts or 1-second intervals and is passed through the same DC removal filter and low pass filter as in previous experiments.
+The rotational speed is determined from speedometer pulses belonging to the given chunk.
 
-%A) **Activity diagram** (Image)
-%1. Label recording using filename path in zip: fault, severity, seq
-%2. Split each recording to 5 parts (1 second - 50000 samples)
-%3. Calculate rpm (out of impulse tachometer = prominence=3, width=50, 60 / $\Delta t$)
-%4. Remove mean - DC component filter
-%5. Filter frequencies: cutoff = 10 kHz (Butterworth lowpass filter of 5 order) - peak 20 kHz (not possibe to capture)
-%6. Label with 6 classes of faults, and 2 anomaly classes (based on arbitrary severity 0.6 and 0.9)
-%7. X - extract temporal features in all axis for both bearings A, B: ax/ay/az_feature_name
-%8. X - window size: windows and welch averaging (2**14 = 16384 samples, 3 okná, 3.05 Hz resolution)
+Signal chunks are converted afterward into \textbf{10 temporal and 11 spectral features}.
+Welch's method for spectrum density estimation averaging over $2^{14}$ long FFT segments after Hann windowing is the source for spectral features.
+The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}
 
-%B) **Counts of classes** (to table and Sum) - **Unbalanced dataset**  (2 Tables - `RPM unlimited | RPM limited`)
+The Euclidian norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure \ref{fig:design:feature-range}.
 
-%C) **Correlation of features with rpm**:
-%    - Temporal: mostly **very low** (25% - 75% quantile: 0.07 - 0.20,
-%    - Spectral: mostly **very low** for all 5 window sizes: 25% (0.08)  - 75% (0.23)
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
+        \caption{Temporal features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
+        \caption{Spectral features}
+    \end{subfigure}
+    \caption{Feature value ranges in inner bearing position (A)}
+    \label{fig:design:feature-range}
+\end{figure}
 
-%C) **Correlation among features**:
-%- Feature correlations (> 0.95):
-%    - Temporal:
-%        - std, rms: 1.0
-%        - std, pp, rms, 0.96
-%        - pp, max, 0.98
-%        - crest, margin, implulse, 0.99
-%    - Spectral:
-%        - skewness, kurtosis, 0.98
-
-%TODO - activity diagram, implementation and value counts
+Fault labels and their severities come from the directory structure within the dataset.
+The binary target variable indicating whether to initiate a warning is named to be an anomaly.
+Anomalies are labeled according to relative fault severity level.
+We decided to investigate two fault severities having levels above 0.6 and 0.9.
+The quantity of observation by fault and anomaly severity is shown in Table \ref{tab:observation-counts}.
+The dataset is substantially unbalanced.
 
@@
 
-\multicolumn{1}{|l|}{\textbf{Anomaly 60\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
+\multicolumn{1}{|l|}{\textbf{Anomaly (> 0.6)}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
 \multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}          \\ \cline{1-3}
@@
 
-\multicolumn{1}{|l|}{\textbf{Anomaly 90\%}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
+\multicolumn{1}{|l|}{\textbf{Anomaly (> 0.9)}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
 \multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{1227 (85\%)}                 & \multicolumn{1}{r|}{1197 (86\%)}         \\ \cline{1-3}
@@
 \end{tabular}
-\caption{Class count in all rotational speeds}
+\caption{Label count for whole MaFaulDa dataset with recordings split to 5 chunks}
+\label{tab:observation-counts}
 \end{table}
 
+Pearson's correlation of features to rpm is very low in the whole dataset.
+In the temporal domain, the correlation coefficient is within an interval of -0.08 to 0.26.
+In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for centroid being around 0.35.
+
+The correlation among features can reduce prediction power if a pair is elected where $|\mathrm{corr}| > 0.95$.
+The feature is not added to the subset when the threshold is exceeded.
+High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{std, rms\}, \{pp, max\}, \{crest, margin\}, \{impulse, std\}, \{impulse, rms\}.
+In the spectral domain set \{skewness, kurtosis\} has a strong correlation.
+
+It is assumed that data points spread in each dimension of the feature space could distinguish groups well.
+The variables that the best explain after min-max scaling total dataset variance in the temporal domain are shape (29\%), RMS, std, max, and pp (each around 15\%).
+In the spectral domain, variance is the best explained by roll-off (28\%), entropy, skewness, centroid, and kurtosis (each around 12\%).
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
+    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
+    \label{fig:design:pca-explained-variance} 
+\end{figure}
+
+The variables are also more inter-correlated in the temporal domain shown by principal components analysis.
+For 95\% of the explained variance of PCA 3 components (98.69\%) are needed in the temporal domain whereas 4 in the spectral domain (95.26\%).
+Figure \ref{fig:design:pca-explained-variance} visualizes cumulative explained variance with an increasing number of principal components.
+
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
+        \caption{Temporal features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
+        \caption{Spectral features}
+    \end{subfigure}
+    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
+    \label{fig:design:pca-loading-plot} 
+\end{figure}
+
+PCA loading plots (Fig.
+\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
+The first PC in the temporal domain focuses on amplitude range (max, rms, pp, std).
+The second PC mainly describes the impulsiveness of the waveform (shape, impulse, crest, margin).
+
+However, the distinction between groups is not so apparent for spectral features.
+Overall chaos in spectra can be attributed to PC1 (flux, entropy, negentropy, noisiness) and the shape of frequency distribution to PC2 (roll-on, roll-off, centroid).
+
 \subsection{Data volume savings}
-%TODO - reduction in data goodput (without metadata): data kept ratio = (nfeat * dim) / (ch * fs * t)
+%TODO
+Apparent advantages of feature discovery is data saving.
+We could do it effetively with PCA but the linear combination is meaningless in reasoning abount which predictors - trend indicators - are decision makers.
+Data compression must occur on edge device to enable utilize wireless low-power wide area networks (LPWPANs).
+Protocol stack may differ therefore we focus on goodput without node configuration metadata and keepalive messages.
+
+Formula to express compression factor depends on several domain specific parameters:
+\begin{itemize}
+\itemsep0pt
+\item number of machines monitored
+\item number of measuremnt places and channels (bearings) - $p_{ch}$ is same in source as output features - devided by dim saved
+\item sampling frequency (in Hz) - const. minimum according to faults that warant detection
+\item interval between measurements (in s) - $T$
+\item duration of valid measurement (in s) - $d$ there can be listening periods which reduc baterry capacity.
+\item number of features extracted ($n_{ft}$)
+\end{itemize}
+
+Compression ratio ($\mathcal{C}$) for feature space is:
+\begin{ceqn}\begin{align}
+\mathcal{C} = \frac{n_{ft}}{f_s \cdot d}
+\end{align}\end{ceqn}
+
+Compression factor for mafaulda machine simulator
 % - (21 * 3) / (3 * 25000 * 1)  (realistic fs because of low pass, we could dowsample by the factor 2) (inverse ratio is data reduction factor =  11904 times less)
-% - 7 times less features: (3*3) / (25000*1*3) (83333 times less than original)
-
-% parameters for measurements
-% 1. number of measurement places (bearings) -- number of machines * places
-% 2. sampling frequency (fs) = const
-% 3. interval between measuremnts (s) 
-% 4. duration of measuremnt (s)
+% - 3 times less features: (6*3) / (25000*1*3) (83333 times less than original)
 
@@
 
+\subsection{Feature selection}
+%TODO
+% Methods to find best 3 features
+% How many is appropriate?
+
+% COnditions for experminetal setup
+
+%- MaFaulDa features subsets (12 = online, 12 = batch experiments, **Use decision tree ilustation with shorten leaves**
+%    - Placement: A, B   - filter only bearing fault for measured bearing, vm and hm to misalign,
+%    - Domain: temporal, spectral
+%    - Online: no, yes
+%    - RPM limit: no, yes (2500 $\pm$ 500)
+%    - Classification: fault (multiclass), anomaly (binary - 60%), anomaly( binary - 90%)
+%   
+%- Validation:
+%- **Batch**
+%    - Magnitude of 3D feature vector
+%    - Balancing dataset with oversampling minority classes
+%        - **TODO:Dataset sizes in all experiments (adj/non adjust)**
+%    - Hold-out validation - split to train and test set (80/20)
+%- **Online**: Order by increaing severity, shuffle samples within severity level
+%    - Severity:
+%        - Number fault severities by sequence
+%        - Keep only decimal numbers in severity
+%        - Number severity per group (0 - best, 1 - worst)
+%        - Transform severities to range (0, 1)
+%     
+%- Best features:
+%    - Compute metrics: Corr, F stat, MI
+%    - Compute Rank product and order descending
+
+% Approval voting
+
+% Ranking
+
 \section{Nearest neighbour classifier}
 
-\subsection{Batch model}
+\subsection{Batch models}
 
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-train}
+        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-train.png}
         \caption{Testing set}
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-test}
+        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-test.png}
         \caption{Training set}
@@
 
-\subsection{Online kNN model}
+\subsection{Online models}
 

### 2023-12-20 thesis/chapters/preliminaries/annotation.tex
Principal components analysis

@@
 &\text{Degree course:} && \text{\StudyProgrammeEN} \\
-&\text{Author:} && \text{\Author} \\
+&\text{Author:} && \text{\AuthorEN} \\
 &\text{\ThesisEN:} && \text{\TitleEN} \\

### 2023-12-20 thesis/chapters/03-design.tex
Plan of work for DP2&3 and finish feature relevance

@@
 In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
-Noted observations are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
-Finally, the network infrastructure layout is provided where we propose optimizations in the functions of the components.
+Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
 
@@
 The assembled description is retained to lead further research on that topic.
-\\
 
-The tasks are associated with certain \textbf{risks} impacting their successful completion.
-The possible risks are assessed and prioritized.
-The most notable risk encountered is that the machine in the real environment will not be available for vibration measurements.
-We successfully eliminated the risk by contacting and establishing collaboration with alternative partners.
-
-The additional risks are that the repeated measurements will not be consistent and fault modes could not be reliably differentiated and labeled in the dataset because each machine is unique in its structure.
-Related is the risk that not enough data is obtained from various classes and suggestions made by exploring the MaFaulDa dataset not be applicable in practice.
-All these risks have to be tracked and regularly reevaluated to achieve our goals.
+The goals are impacted by certain \textbf{risks} that are assessed and tracked:
+\begin{enumerate}[label=R-\arabic*., font=\bfseries]
+\itemsep0pt
+\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
+\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
+\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
+\item Fault modes could not be reliably differentiated and labeled in the dataset.
+\\ \emph{Mitigation}: Consult domain experts and machines' maintenance staff.
+\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
+\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
+\end{enumerate}
 
@@
 Half a second of amplitude samples are used from every sensor channel.
-These 25 thousand observations are downsampled tenfold to $2500$ points.
+These 25 thousand observations are downsampled tenfold to $2500$.
 
@@
 \subsection{Feature extraction}
-Each file in the MaFaulDa contains 6 accelerometer channels.
-In the feature extraction process sequence of samples is split into 5 parts or 1-second intervals and is passed through the same DC removal filter and low pass filter as in previous experiments.
-The rotational speed is determined from speedometer pulses belonging to the given chunk.
+Each file in the MaFaulDa contains six accelerometer channels.
+In the feature extraction process, the sequence of samples is split into five parts or 1-second intervals.
+The portions are passed through the same DC removal and low pass filters as previously.
+The rotational speed is derived from speedometer pulses within the chunk.
 
@@
 Welch's method for spectrum density estimation averaging over $2^{14}$ long FFT segments after Hann windowing is the source for spectral features.
-The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}
+The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}.
 
@@
 It is assumed that data points spread in each dimension of the feature space could distinguish groups well.
-The variables that the best explain after min-max scaling total dataset variance in the temporal domain are shape (29\%), RMS, std, max, and pp (each around 15\%).
+The variables that the best explain after min-max scaling total dataset variance in the temporal domain are shape (29\%), rms, std, max, and p-p (each around 15\%).
 In the spectral domain, variance is the best explained by roll-off (28\%), entropy, skewness, centroid, and kurtosis (each around 12\%).
@@
 
-PCA loading plots (Fig.
+PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
+Loading plots of PCA (Fig.
 \ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
-The first PC in the temporal domain focuses on amplitude range (max, rms, pp, std).
-The second PC mainly describes the impulsiveness of the waveform (shape, impulse, crest, margin).
+The first PC in the temporal domain focuses more on amplitude range: \emph{max, rms, pp, std}.
+The second PC mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, margin}.
 
-However, the distinction between groups is not so apparent for spectral features.
-Overall chaos in spectra can be attributed to PC1 (flux, entropy, negentropy, noisiness) and the shape of frequency distribution to PC2 (roll-on, roll-off, centroid).
+However, the groups are not as clear cut for spectral features.
+Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.
 
 \subsection{Data volume savings}
-%TODO
-Apparent advantages of feature discovery is data saving.
-We could do it effetively with PCA but the linear combination is meaningless in reasoning abount which predictors - trend indicators - are decision makers.
-Data compression must occur on edge device to enable utilize wireless low-power wide area networks (LPWPANs).
-Protocol stack may differ therefore we focus on goodput without node configuration metadata and keepalive messages.
+The apparent advantage of feature discovery is reducing the amount of data downstream.
+Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN).
+The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.
 
-Formula to express compression factor depends on several domain specific parameters:
+Machinery monitoring system relies on determining several parameters:
 \begin{itemize}
 \itemsep0pt
-\item number of machines monitored
-\item number of measuremnt places and channels (bearings) - $p_{ch}$ is same in source as output features - devided by dim saved
-\item sampling frequency (in Hz) - const. minimum according to faults that warant detection
-\item interval between measurements (in s) - $T$
-\item duration of valid measurement (in s) - $d$ there can be listening periods which reduc baterry capacity.
-\item number of features extracted ($n_{ft}$)
+\item \textbf{Number of source channels} ($S$): is comprised of the number of monitored machines, measurement locations for sensors, and active sensor axes.
+\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
+The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem.
+At a minimum, it should be 15 kHz to 20 kHz.
+\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
+The more critical the machine is, interval should be shorter.
+The bigger the machine parts, the slower the defect evolves.
+\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltering behavior associated with a timestamp.
+Duration should cover at least 3 windows for spectral estimation.
+The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
+\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfuctions. We aim for total of 6 features.
 \end{itemize}
 
-Compression ratio ($\mathcal{C}$) for feature space is:
-\begin{ceqn}\begin{align}
-\mathcal{C} = \frac{n_{ft}}{f_s \cdot d}
+Equation \ref{equ:compression-ratio-features} expresses the lossy compression ratio ($\mathcal{C}$) formula if trend indicators are stored instead of full recording.
+The number of raw channels ($S_{\mathrm{in}}$) can differ from those extracted in features ($S_{\mathrm{out}}$).
+Parameter $D = 0.5$ when we use frequency bins with 1 Hz resolution.
+
+\myequations{Lossy compression ratio with features}
+\begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
+\mathcal{C} = \frac{F \cdot S_{\mathrm{out}}}{D \cdot f_s \cdot S_{\mathrm{in}}}
 \end{align}\end{ceqn}
 
-Compression factor for mafaulda machine simulator
-% - (21 * 3) / (3 * 25000 * 1)  (realistic fs because of low pass, we could dowsample by the factor 2) (inverse ratio is data reduction factor =  11904 times less)
-% - 3 times less features: (6*3) / (25000*1*3) (83333 times less than original)
+\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is $4.2 \times 10^{-4}$.
+In case 6 features are kept, the compression is $4.2 \times 10^{-5}$, hundredth-thousandths of the original data.
 
-% Requiremnts classic per bearing (per year): 5s * 20khz * 3dim (365 * 24 = every hour) = (sample is 4/8B just multiplication factor) =  300 kS per measuremnts * 8760 measuremnts = 2.628 GSamples per year per placement
-% Frequncy spectra with 1 Hz res = 1*10kHz*3= 30kS = 262.8 MSamples
-% All features = 9S  => 78.84 KSamples / year (per year as much as per 3 spectra measurements)
+As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
+The station has 3 pumps and matching 3 electric induction motors.
 
-% According to standars is rms velocity enough => indicator of fault (but not of the type)
+A pump and motor pair have 4 bearings together for drive end and non-drive end positions.
+Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
+The sampling frequency on each position is set to \emph{20 kHz}.
+The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
+
+In a year the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with 16-bit ADC resolution.
+Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
+On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of $6 \times 10^{-5}$.
 
 \subsection{Feature selection}
-%TODO
-% Methods to find best 3 features
-% How many is appropriate?
+The objective of feature selection is to find a subset of the most relevant predictors in each domain.
+As a starting point, the set consists of 3 non-correlated attributes under diverse conditions.
+Ultimately a number of chosen features is to be tweaked to increase prediction accuracy.
+Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
+\begin{itemize}
+\itemsep0pt
+\item \textbf{online}: boolean selector that influences whether metrics are calculated in batch or incremental fashion,
+\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
+\item \textbf{target variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
+\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
+\end{itemize}
 
-% COnditions for experminetal setup
+In feature evaluation for fault prediction, we use hold-out validation in batch models and progressive valuation in online models.
+Classes in observations for batch models are rebalanced to the majority class with a random oversampling strategy.
+The training and testing set split ratio is 80 to 20.
+Classes for incremental learning are ordered by relative severity level and shuffled within levels.
 
-%- MaFaulDa features subsets (12 = online, 12 = batch experiments, **Use decision tree ilustation with shorten leaves**
-%    - Placement: A, B   - filter only bearing fault for measured bearing, vm and hm to misalign,
-%    - Domain: temporal, spectral
-%    - Online: no, yes
-%    - RPM limit: no, yes (2500 $\pm$ 500)
-%    - Classification: fault (multiclass), anomaly (binary - 60%), anomaly( binary - 90%)
-%   
-%- Validation:
-%- **Batch**
-%    - Magnitude of 3D feature vector
-%    - Balancing dataset with oversampling minority classes
-%        - **TODO:Dataset sizes in all experiments (adj/non adjust)**
-%    - Hold-out validation - split to train and test set (80/20)
-%- **Online**: Order by increaing severity, shuffle samples within severity level
-%    - Severity:
-%        - Number fault severities by sequence
-%        - Keep only decimal numbers in severity
-%        - Number severity per group (0 - best, 1 - worst)
-%        - Transform severities to range (0, 1)
-%     
-%- Best features:
-%    - Compute metrics: Corr, F stat, MI
-%    - Compute Rank product and order descending
+The best group of attributes is elected based on a training set with multiple methods.
+We compute the mean of absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable.
+The features are then ordered in descending order of the received score.
+These individual ranks are combined by rank product to create an ensemble out of the metrics.
+Reference implementation of feature selection metrics uses Python packages Scikit Learn\footnote{SciKit Learn: \url{https://scikit-learn.org/}} in batch learning and RiverML\footnote{RiverML: \url{https://riverml.xyz/}} for online learning.
 
-% Approval voting
+\begin{figure}[h!]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/approval-voting-temporal.png}
+        \caption{Temporal domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/approval-voting-spectral.png}
+        \caption{Spectral domain features}
+    \end{subfigure}
+    \caption{Approval rating of the best triplet of features to target variable ``fault'' scored by rank product of correlation, F statistic, and mutual information.}
+    \label{fig:design:approval-rating-features}
+\end{figure}
 
-% Ranking
+The choice of features is very sensitive to experimental conditions.
+Tendencies are demonstrated by counting how many triplets the indicator appears in across all possible situations.
+The results of approval voting are shown in Figure~\ref{fig:design:approval-rating-features}.
+The most occurring attributes in the temporal domain are peak-to-peak, shape, and crest, and in the spectral domain, those are centroid, roll-off, and roll-on.
 
 \section{Nearest neighbour classifier}
+%TODO
 
 \subsection{Batch models}
-
 \begin{figure}[ht]
@@
 
+\newpage
 \section{Vibration measurement plan}
@@
 \renewcommand{\arraystretch}{1.2}
+\centering
 \begin{tabular}{|l|l|l|}
@@
 \end{figure}
-
-\newpage
-\section{Machine learning pipeline}
-\begin{enumerate}
-    \itemsep0pt
-    \item Detrending
-    \item (Optional) Adaptive noise cancellation of the background interference
-    \item Vector of all features
-    \begin{itemize}
-        \itemsep0pt
-        \item Time domain: statistical measures (Tab.~\ref{tab:td-features})
-        \item Frequency domain: PSD estimation with FFT and Welch averaging with the resolution of 1 Hz combined with Hann window (Tab.~\ref{tab:fd-features})
-    \end{itemize}
-    \item Feature selection on evaluation datasets and experimental measurements from the factory to prune away irrelevant features with pearson correlation, Fisher score, and mutal information.
-    \item Model evaluation and comparison of novelty detection methods and precision of classification with different sets of predictors.
-The range of optimal parameters will be found for the DenStream ($\mu$, $\epsilon$, $beta$, $\lambda$), Half-Space Trees (window size, ensemble size), and kNN (distance metric, $k$ neighbours).
-Evaluation metrics associated with confusion matrices will be used like accuracy, precision, true positive rate, and false positive rate.
-\end{enumerate}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.9\textwidth]{assets/analysis/ml-lifecycle.png}
-\caption{Machine learning lifecycle of feature discovery}
-\end{figure}
-
-\section{Infrastructure deployment}
-Future work: engineer new feature, deploy, tweek models, validate on real dataset
-
- \begin{itemize}
- \itemsep0pt
-\item \textbf{Input:} Samples from three-axis MEMS accelerometers, RPM tachometer, Noise background
-\item \textbf{Output:} machine health status / type of fault
-\item \textbf{Output on demand}: Control chart of trend features
-\end{itemize}
-
-\begin{enumerate}
-\itemsep0pt
-\item \textbf{Accelerometer} - MEMS accelerometers will be placed on at least two distinct measurement points in two perpendicular axes and one sensor in the machine base for denoising purposes.
-Rotational speed has to be captured at the same time too.
-The sampling frequency shall be around 2 kHz if unbalance and looseness is to be identified, and 10 kHz if bearing faults are also of interest.
-The range of overall rms vibrations is not expected to exceed 30 mm/s according to the vibration severity chart.
-\item \textbf{Acquisition interval} - sensor units will be triggered in regular intervals (every 15 - 60 minutes) to collect vibration recordings from the band saw (or another machine of choice).
-The machine has to be under the same load conditions every time is recording is active.
-\item \textbf{Features} - most relevant features are computed and compared to recent measurements.
-If there is a statistically significant change the whole summary is sent, otherwise keep-alive notification is sent.
-\item \textbf{Wireless network} - earlier design decision has been made to establish wireless connections.
-Therefore, the sensor unit will send data over Wifi (IEEE 802.11), or Thread with IEEE 802.15.4 over 2.4 GHz or 868 MHz frequency bands.
-The application protocol shall be Constrained Application Protocol (CoAP).
-The messages will be encoded by Concise Binary Object Representation (CBOR) or MessagePack which provides the best compression ratio and is widely supported.
-\item \textbf{Time series database} - stores history of trend values.
-Raw vibration measurements can be requested by the operator at any time but are available and delayed according to transfer speeds and other network constraints.
-The promissing database technologies is TimescaleDB.
-\item \textbf{Diagnosis panel} - continuously updates the anomaly detection and classification models with the introduction of annotations to notify the operator about observed faults and imminent failure of the machine.
-The dashboard is provided to display the current status of multiple machines.
-\end{enumerate}
-
-\begin{figure}[h]
-\centering
-\includegraphics[width=0.7\textwidth]{assets/design/sensor-network.png}
-\caption{Sensor network components}
-\end{figure}

### 2023-12-20 thesis/chapters/appendix/B-plan-of-work.tex
Plan of work for DP2&3 and finish feature relevance

--- 2023-10-12 thesis/chapters/appendix/B-plan-of-work.tex
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week         & Consultation with the supervisor on directions of the future work based on literature review during previous semester.
+\nth{1} week         & Consultation with the supervisor on directions of the future work based on literature review during the previous semester.
 \\ \hline
@@
 \\ \hline
-\nth{3} week         & Match supporting literature with analysis sections. Further invesigation on the feature engineering methodology in CbM.
+\nth{3} week         & Match supporting literature with analysis sections. Further investigation on the feature engineering methodology in CbM.
  \\ \hline
-\nth{4} week         & Summarize notes from condition monitoring articles and videorecordings of tutorials and conferences.
+\nth{4} week         & Summarize notes from condition monitoring articles and video recordings of tutorials and conferences.
  \\ \hline
-\nth{5} week         & Research transformation of vibration signal to feature space using time-frequency, harmonic and energy statistical metrics. Progress report meeting with the supervisor.
+\nth{5} week         & Research transformation of a vibration signal to feature space using time-frequency, harmonic, and energy statistical metrics. Progress report meeting with the supervisor.
  \\ \hline
@@
  \\ \hline
-\nth{7} week         & Narrow down wide variety applicable methods for signal decomposition.
+\nth{7} week         & Narrow down a wide variety of applicable methods for signal decomposition.
  \\ \hline
- \nth{8} week         & Exploratory analysis on evaluation datasets. Progress report meeting with the supervisor to topic of related work.
+ \nth{8} week         & Exploratory analysis on evaluation datasets. Progress report meeting with the supervisor on the topic of related work.
  \\ \hline
@@
  \\ \hline
-  \nth{12} week         & Write up the analysis section about machine learning diagnostics and consult final choice of methods in the analysis section.
+  \nth{12} week         & Write up the analysis section about machine learning diagnostics and consult the final choice of methods in the analysis section.
  \\ \hline
@@
 \newpage
-
 \section{Winter semester - DP2}
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week         & Semester kickoff meeting with the supervisor and consultant to set goals, experiments and discuss status of collaborations with the industry.
+\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
 \\ \hline
-\nth{2} week         &  Arrange collaboration with alternative industry partner.
-Prepare checklist for technical inspection of machinery.
-Construct device (BeagleBone Black + ADXL335) for exploratory measurements.
+\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
 \\ \hline
-\nth{3} week         & Technical inspection of air conditioning units in data centre of the industry partner. Calculate features from Mafaulda dataset and start feature selection
+\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
  \\ \hline
-\nth{4} week         & Consultation with the supervisor about choice of machine to measure (scroll compressor), device for measurement, and requirements for dataset gathering.
-Feature selection methods comparison on Mafaulda dataset.
+\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
  \\ \hline
-\nth{5} week         & Make further exploratory measurements with rewritten code ensuring more precise accelerometer sampling.
-Make a plan of measurement and negotiate it with industry partner.
-Feed exporatory dataset into anomaly detection models.
+\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
  \\ \hline
-\nth{6} week         & 
+\nth{6} week         & Feature selection used in kNN multiclass and binary classificator.
  \\ \hline
-\nth{7} week         &
+\nth{7} week         & Explore incremental learning kNN algorithm with MaFaulDa dataset. Consultation and status report.
  \\ \hline
- \nth{8} week         & 
+ \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
  \\ \hline
- \nth{9} week         & 
+ \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for kNN validation. Consultation to discuss progress.
  \\ \hline
-  \nth{10} week         & 
+  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
  \\ \hline
-  \nth{11} week         & 
+  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
  \\ \hline
-  \nth{12} week         & 
+  \nth{12} - \nth{13} week         &  Write up design chapter: research questions, visualization export. Finish writing design chapter.
  \\ \hline
@@
 
+The semester for DP2 was split into 3 periods.
+Feature engineering and ML model evaluation was planned from \nth{1} to \nth{4} week, and technical inspections and plan of measurement in weeks \nth{4} to \nth{8}.
+
+In reality, these tasks switched order because, between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study.
+Only then from \nth{4} to \nth{11} week, main focus was on experiments with the MaFaulDa.
+
+Lastly, preliminary measurements were conducted, as was the plan. Requirements were presented for the new sensor device, and a chapter about design was written.
 \clearpage
 \newpage
-
-\begin{table}[h!]
-\def\arraystretch{1.25}
-\begin{tabular}{|l|p{12cm}|}
-\hline
-\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1}  - \nth{4} week         & Apply feature engineering and classifications methods to evalution datasets
-\\ \hline
-\nth{4}  - \nth{8} week         & Design the vibration measurement for factory according to technical standards. 
-\\ \hline
-\nth{8} - \nth{12} week         & Take preliminary measurements in the factory and compare signals with evaluation datasets.
- \\ \hline
-\end{tabular}
-\end{table}
 
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1}  - \nth{4} week         & 
+\nth{1}  - \nth{2} week         & 
+\begin{enumerate}
+\itemsep0pt
+\item Incorporate suggestions from DP2 defense. 
+\item Develop and test firmware for designed sensor unit.
+\end{enumerate}
 \\ \hline
-\nth{4}  - \nth{8} week         & 
+\nth{2}  - \nth{10} week         & 
+\begin{enumerate}
+\itemsep0pt
+\item Long-term manual regular gathering of vibration data from compressors and pumps. 
+\item Find optimal number of features. 
+\item Try to increase kNN prediction metrics.
+\item Put together incremental learning with feature selection. 
+\item Explore incremental clustering in search of method that can help with labeling.
+\end{enumerate}
 \\ \hline
-\nth{8} - \nth{12} week         & 
+\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
  \\ \hline

### 2023-12-23 thesis/chapters/03-design.tex
kNN batch models: all features & comb. subset

@@
 	\item Establish a list of conditions that should be later investigated in the experimental setting.
-	\item Prepare dataset to be used in conjunction with statistical learning models, namely by identifying labels and balancing classes.
+	\item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
 	\item Find the best subsets of features in temporal and spectral domain with previously analyzed feature extraction and selection methods.
@@
 On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of $6 \times 10^{-5}$.
+Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
+The entire machine's history can be kept in a small flash memory module.
 
@@
 
-\section{Nearest neighbour classifier}
-%TODO
+\section{K-nearest neighbor classifier}
+We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets.
+kNN classifier being a lazy learner means it can be adapted easily from offline to online context.
+Training labels establish nearest-neighbor decision boundaries for attribute values.
+Voronoi diagrams can display these regions and explain the model in that way.
+Batch learning in kNN serves here as a target performance whose attainment is desirable with online learning.
 
 \subsection{Batch models}
+Three types of kNN model experiments run with hold-out validation. 
+First, the model learns all extracted features, so no feature selection occurs.
+Then, the brute-force method searches for a combination of three features with the highest training accuracy.
+In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.
+
 \begin{figure}[ht]
@@
     \end{subfigure}
-    \caption{Confusion matrix of batch kNN algorithm predictions in temporal and spectral domain for two predicted variables measured on inner bearing.}
+    \caption{Confusion matrix of kNN predictions on bearing position A}
+    \label{fig:design:knn-confusion-matrix}
 \end{figure}
+
+Two models are created for the target variable in classification with all 10 temporal and 11 spectral features.
+The subset of records includes all rotational speeds on bearing position A.
+Either six fault labels or anomaly above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
+The number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
+
+Confusion matrices for fault predicion and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}.
+The most inaccuracies in the temporal domain are between misalignment and bearing race faults.
+In the spectral domain, the model confuses imbalance and bearing faults.
+It is to be expected since mass to unbalance the shaft is hanged to simulate bearing defects.
+
+In anomaly prediction, the error of the first degree is 7 times more prevalent than the error of the second degree.
+False positives are preferable since we do not want the machine to fail prematurely and not know about it.
+In all cases, spectral features maintain better prediction metrics than all temporal features because of less interdependency among features.
+Bearing B exhibits overall worse classification performance because of more noise in the original signal.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|l|l|l|rrr|rrr|}
+\hline
+\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Bearing\\ position\end{tabular}}} & \multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Target\\ variable\end{tabular}}} & \multirow{2}{*}{\textbf{Observations}}                                             & \multicolumn{3}{l|}{\textbf{Temporal domain}}                                                                                                                                                                                                                                    & \multicolumn{3}{l|}{\textbf{Spectral domain}}                                                                                                                                                                                                                                    \\ \cline{4-9}
+                                                                                     &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
+\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 pre class\end{tabular}  & \multicolumn{1}{r|}{0.9413}                                                               & \multicolumn{1}{r|}{0.9093}                                                              & 0.91                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
+                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9668}                                                               & \multicolumn{1}{r|}{0.9535}                                                              & 0.96                                                                                      & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
+\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.8634}                                                               & \multicolumn{1}{r|}{0.7935}                                                              & 0.79                                                                                      & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9}
+                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9148}                                                               & \multicolumn{1}{r|}{0.8668}                                                              & 0.87                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{kNN model performance trained on all extracted features}
+\label{tab:design:all-extracted-features}
+\end{table}
+
+Accuracies and F1 scores in both bearing positions with all extracted features are shown in Table \ref{tab:design:all-extracted-features}.
+Models are overtrained, especially for temporal features, because of the substantial difference between accuracy on training and validation sets.
+Binary classification of anomaly is unsurprisingly more precise in general than multiclass case.
+Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 87\% for bearing B.
+
+Next, we exhaustively list all combinations of three features and look at the range of model performances generated.
+There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate kNN models for temporal domain features and 165 for the spectral domain.
+The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
+Accuracies of kNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-knn}.
 
@@
     \caption{Range of prediction accuracy in all kNN models with subset of 3 features. Subplots show three different predicted variables.}
+    \label{fig:design:feature-combinations-knn}
 \end{figure}
+
+Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-knn}.
+Worst accuracies occur for temporal features in multiclass classification 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
+An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.
+
+\begin{table}[ht!]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|r|r|r|l|r|r|}
+\hline
+\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
+\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, skewness, shape\}         & 0.9559                & 0.9328               \\ \cline{3-6}
+                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
+                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, shape\}         & 0.9106                & 0.8591 \\ \cline{3-6} 
+                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
+\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{std, kurtosis, pp\}            & 0.9085                & 0.8551               \\ \cline{3-6}
+                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
+                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, kurtosis\}      & 0.8369                & 0.7654 \\ \cline{3-6} 
+                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Features with the highest accuracies on the training set found combinatorically}
+\label{tab:design:feature-combinations-knn}
+\end{table}
+
+The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-knn}.
+Their prediction accuracies in kNN models are subpar to optimal sets.
+However, the advantage is that the feature election process is not so computationally taxing.
+On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains.
+Because of the low k hyperparameter value, models are overtrained either way.
+
+\begin{table}[ht!]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|r|r|r|l|r|r|}
+\hline
+\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
+\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{shape, std, rms\}               & 0.9333                                       & 0.8916                                      \\ \cline{3-6}
+                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6}
+                   & \multirow{2}{*}{fault}                        & temporal        & \{std, shape, max\}               & 0.9048                                       & 0.8544                                      \\ \cline{3-6}
+                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
+\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, shape, crest\}             & 0.8961                                       & 0.8505                                      \\ \cline{3-6}
+                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6}
+                   & \multirow{2}{*}{fault}                        & temporal        & \{pp, crest, skewness\}           & 0.8194                                       & 0.7380                                      \\ \cline{3-6}
+                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated kNN accuracies.}
+\label{tab:design:best-3-features-knn}
+\end{table}
+
+Lowering the number of attributes allows for visualization of labels in planar scatter plots.
+The data points in 3-dimensional cross sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
+We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
+
+Overlapping clusters are evidenced by relatively low silhouette scores around zero.
+Therefore, we cannot increase the k hyperparameter as much because otherwise, categories merge.
+Relabeling according to severity should be undertaken.
+Low severity faults should be reassigned to a class with no fault.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
+        \caption{Temporal domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
+        \caption{Spectral domain features}
+    \end{subfigure} 
+    \caption{Cross sections of 3-dimensional feature spaces for best attributes chosen by rank product method}
+    \label{fig:design:feature-space-scatter}
+\end{figure}
+
+\clearpage
+\newpage
+
+%TODO
+% Model performance on feature selection techniques is compared on 3 features to set of all features and best ever combinations of triplets.
+Three principal components computed out of all features in each domain are also used in comparison.
+(significant overlap) We suspect the PCA property of maximizing variances in each dimention support separating groups in classification.
+
+% Results of experiments in the scenarios is aggregated in Figure X.
+Best combinations of 3 features is always better than all 10 features because of overfitting.
+PCA is always better than any other method of feature selection.
+Rank product is not universally  better but balances other methods to achieve more stable results.
+
+% In majority of situations it it better than all three individually.
+Subset of spectral features have better performance than temporal features, presumbly because of many correlated pairs of features.
+In would be interesting to investigate how many features is optimal by giving yet better performance and altering feature election process.
 
@@
 
-% Number of neighbors (graphs)
+\clearpage
+\newpage
 
 \subsection{Online models}
+%- Temporal and Spectral (2 exports)
+%    - config = {'rpm_limit': False, 'placement': 'A', 'domain': DOMAIN, 'target': 'fault'}
+%    - config = {'rpm_limit': False, 'placement': 'A', 'domain': DOMAIN, 'target': 'anomaly'}
+%    - When examples for all classes in labels exists - accuracies of model stabilizes quickly
+%    - When new label is introduced accuracy drops momentarily
+%    - Delay, Skiping labels -  degrades model performance
+%- Online (Progressive valuation):
+%    - Plot: label ordering in train (in future create strategy for balancing of classes)
+%        - Faults (Plot)
+%        - Anomaly (Plot)
+%    - Gradual learning
+%        - Fault (shaft) / anomaly (2 plots) - comment on convergence
+%    - Window learning
+%        - Fault (shaft) / anomaly
+%        - Compare classification accuracies for window sizes in one graph: (1, 10, 50, 100, 250)
+%        - Scenarios: fault, anomaly
+%    - Missing labels
+%        - Faults
+%        - Anomaly
+%    - Scatter plot - True labels vs. Predicted labels (it is not the case that areas with one fault are homogenous and compact in PC dimensions)
+%        - Faults 
+%        - Anomaly
+%    - **One physical defect can have multiple manifestations - outer race fault and misalignment overlap**
 
@@
 
+\clearpage
 \newpage
+
 \section{Vibration measurement plan}
@@
 \end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{assets/design/compressor-orbitals-1x.png}
+	\caption{Orbital analysis of compressor's 1x harmonic}
+\end{figure}

### 2023-12-23 notebooks/vibrodiagnostics/models.py

@@ -141,10 +141,10 @@ def pipeline_v1(features, train, nfeat, func_select, multiclass=True, anomaly_ra
     )
 
 
-def cross_cuts_3d(X_train, y_train):
-    fig, ax = plt.subplots(1, 3, figsize=(15, 3))
+def cross_cuts_3d(X_train, y_train, ylim=None):
+    fig, ax = plt.subplots(1, 3, figsize=(20, 5))
     labels = np.unique(y_train.to_numpy())
-    colors = sb.color_palette('tab10', len(labels))
+    colors = sb.color_palette('hls', len(labels))
 
     for i, axes in enumerate(((0, 1), (0, 2), (1, 2))):
         a, b = axes
@@ -159,7 +159,9 @@ def cross_cuts_3d(X_train, y_train):
                 X_train.columns[b]
             ]
             ax[i].scatter(x, y, s=1, color=color, label=label)
-        
+            if ylim is not None:
+                ax[i].set_ylim(ylim)
+            
         ax[i].set_xlabel(X_train.columns[a])
         ax[i].set_ylabel(X_train.columns[b])
         ax[i].grid()

### 2023-12-23 thesis/chapters/03-design.tex
kNN batch models

@@
 \begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
-\mathcal{C} = \frac{F \cdot S_{\mathrm{out}}}{D \cdot f_s \cdot S_{\mathrm{in}}}
+\mathcal{C} = \frac{D \cdot f_s \cdot S_{\mathrm{in}}}{F \cdot S_{\mathrm{out}}}
 \end{align}\end{ceqn}
 
-\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is $4.2 \times 10^{-4}$.
-In case 6 features are kept, the compression is $4.2 \times 10^{-5}$, hundredth-thousandths of the original data.
+\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
+In case 6 features are kept, the compression is 25000:1, which is a saving of the original data amount of 99.996\%.
 
@@
 Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
-On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of $6 \times 10^{-5}$.
+On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
 Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
@@
 Either six fault labels or anomaly above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
-The number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
 
 Confusion matrices for fault predicion and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}.
+In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
 The most inaccuracies in the temporal domain are between misalignment and bearing race faults.
@@
 
-Lowering the number of attributes allows for visualization of labels in planar scatter plots.
+Lowering the number of attributes allows visualization of labels in planar scatter plots.
 The data points in 3-dimensional cross sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
@@
 
-Overlapping clusters are evidenced by relatively low silhouette scores around zero.
-Therefore, we cannot increase the k hyperparameter as much because otherwise, categories merge.
-Relabeling according to severity should be undertaken.
-Low severity faults should be reassigned to a class with no fault.
+Cluster overlaps of various defect types are also confirmed by silhouette scores around zero.
+Therefore, the k hyperparameter cannot be increased much, as it would cause the merge of mutually confused categories.
+Low-severity faults should be relabeled as a class without fault to watch out just for alert conditions.
 
@@
     \end{subfigure} 
-    \caption{Cross sections of 3-dimensional feature spaces for best attributes chosen by rank product method}
+    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
     \label{fig:design:feature-space-scatter}
@@
 
-\clearpage
-\newpage
-
-%TODO
-% Model performance on feature selection techniques is compared on 3 features to set of all features and best ever combinations of triplets.
-Three principal components computed out of all features in each domain are also used in comparison.
-(significant overlap) We suspect the PCA property of maximizing variances in each dimention support separating groups in classification.
-
-% Results of experiments in the scenarios is aggregated in Figure X.
-Best combinations of 3 features is always better than all 10 features because of overfitting.
-PCA is always better than any other method of feature selection.
-Rank product is not universally  better but balances other methods to achieve more stable results.
-
-% In majority of situations it it better than all three individually.
-Subset of spectral features have better performance than temporal features, presumbly because of many correlated pairs of features.
-In would be interesting to investigate how many features is optimal by giving yet better performance and altering feature election process.
+Model performance of kNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:knn-accuracy-batch}.
+Best combination of three features achieves always better than when the model is trained on all features.
+This has to do with curse of dimensionality phenomenon.
 
@@
     \caption{Batch kNN algorithm prediction accuracy with various feature sets.}
+    \label{fig:design:knn-accuracy-batch}
 \end{figure}
 
-\clearpage
-\newpage
+We suspected that the PCA property of maximizing variances in each of the few dimensions would support more separation of clustered groups and would be beneficial in classification.
+The bar chart supports this assumption.
+PCA always produces greater model accuracies than any other method of feature selection.
+The rank product of the three scoring techniques is not better every time, but it balances out aggregated methods to achieve more stable results across testing sets.
+
+In every instance, a subset of spectral features is responsible for better accuracy than a subset of temporal features.
+Presumably, it is so because of many correlated pairs of attributes in the temporal domain.
+Further tests should be made to determine optimal feature subsets and the impact of altering the feature election process.
 
 \subsection{Online models}
-%- Temporal and Spectral (2 exports)
-%    - config = {'rpm_limit': False, 'placement': 'A', 'domain': DOMAIN, 'target': 'fault'}
-%    - config = {'rpm_limit': False, 'placement': 'A', 'domain': DOMAIN, 'target': 'anomaly'}
-%    - When examples for all classes in labels exists - accuracies of model stabilizes quickly
-%    - When new label is introduced accuracy drops momentarily
-%    - Delay, Skiping labels -  degrades model performance
-%- Online (Progressive valuation):
-%    - Plot: label ordering in train (in future create strategy for balancing of classes)
-%        - Faults (Plot)
-%        - Anomaly (Plot)
-%    - Gradual learning
-%        - Fault (shaft) / anomaly (2 plots) - comment on convergence
-%    - Window learning
-%        - Fault (shaft) / anomaly
-%        - Compare classification accuracies for window sizes in one graph: (1, 10, 50, 100, 250)
-%        - Scenarios: fault, anomaly
-%    - Missing labels
-%        - Faults
-%        - Anomaly
-%    - Scatter plot - True labels vs. Predicted labels (it is not the case that areas with one fault are homogenous and compact in PC dimensions)
-%        - Faults 
-%        - Anomaly
-%    - **One physical defect can have multiple manifestations - outer race fault and misalignment overlap**
+%TODO
+
+% Order of classes, whole feature set, all rpm, placement on bearing A
+	% Severity is rising sequentially, each group is shuffled randomly, validation set is kept away for hold-valiadtion.
+	% (Progressive valuation with 20\% of dataset kept away for additional hold-out validation):
 
@@
         \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
-        \caption{Training set and fault as predicted variable}
+        \caption{Training set and defect types ``fault'' as predicted variable}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-test.png}
-        \caption{Testing set and fault as predicted variable}
+        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-train.png}
+        \caption{Training set and anomaly with severity above 0.6 ``anomaly60'' as predicted variable}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-train.png}
-        \caption{Training set and medium anomaly severity as predicted variable}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-test.png}
-        \caption{Training set and medium anomaly severity as predicted variable}
-    \end{subfigure}
-    \caption{Label order in progressive valuation}
+    \caption{Label sequencing for progressive evaluation}
 \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-temporal-domain-fault.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-spectral-domain-fault.png}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-temporal-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-spectral-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \caption{Gradual learning}
-\end{figure}
+% Gradual learning with delay - label provided after it has been predicted by the model
+	% The amount to wait before revealing the target associated with each observation to the model.
 
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-        \caption{}
+        \caption{Temporal domain features, predicted variable is fault}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-        \caption{}
+        \caption{Spectral domain features, predicted variable is fault}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-anomaly60.png}
-        \caption{}
+        \caption{Temporal domain features, predicted variable is anomaly above severity 0.6}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-anomaly60.png}
-        \caption{}
+        \caption{Spectral domain features, predicted variable is anomaly above severity 0.6}
     \end{subfigure}
-    \caption{Gradual learning accuracy with delay}
+    \caption{Incremental learning on all extracted features with delayed reveal of labels in rolling window}
 \end{figure}
+
+% Window learning- all labels for fixed previous period are provided at once.
 
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
-        \caption{}
+        \caption{Temporal domain features}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
-        \caption{}
+        \caption{Spectral domain features}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \caption{Gradual learning with delay}
+    \caption{Incremental learning for variable ``fault'' with delayed reveal of labels at regular intervals.}
 \end{figure}
+
+% Missing labels - some labels are skipped before another one is anotated
 
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
-        \caption{}
+        \caption{Temporal domain features}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
-        \caption{}
+        \caption{Spectral domain features}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \caption{Gradual learning and skip labels}
+    \caption{Incremental learning with skipping of labels and delay of 10 observations}
 \end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-anomaly60.png}
-        \caption{}
-    \end{subfigure}
-    \caption{Gradual learning accuracy with delay}
-\end{figure}
+% Scatter plot of fault classification - min-max scale shifts. From left true labels, predicted labels, mistakes made by model in red
 
@@
         \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-temporal.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-anomaly60-spectral.png}
         \caption{}

### 2023-12-25 thesis/chapters/03-design.tex
Increamental learing results with kNN

@@
 kNN classifier being a lazy learner means it can be adapted easily from offline to online context.
-Training labels establish nearest-neighbor decision boundaries for attribute values.
+Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values.
 Voronoi diagrams can display these regions and explain the model in that way.
@@
 \subsection{Batch models}
-Three types of kNN model experiments run with hold-out validation. 
+Three types of kNN model experiments run with hold-out validation in batch setting. 
 First, the model learns all extracted features, so no feature selection occurs.
@@
                                                                                      &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
-\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 pre class\end{tabular}  & \multicolumn{1}{r|}{0.9413}                                                               & \multicolumn{1}{r|}{0.9093}                                                              & 0.91                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
+\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9413}                                                               & \multicolumn{1}{r|}{0.9093}                                                              & 0.91                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
                                                                                      & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9668}                                                               & \multicolumn{1}{r|}{0.9535}                                                              & 0.96                                                                                      & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
@@
 \subsection{Online models}
-%TODO
+Online learning imitates hardened conditions for machinery diagnostics that appear in deployment.
+Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
+The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.
 
-% Order of classes, whole feature set, all rpm, placement on bearing A
-	% Severity is rising sequentially, each group is shuffled randomly, validation set is kept away for hold-valiadtion.
-	% (Progressive valuation with 20\% of dataset kept away for additional hold-out validation):
+The kNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context.
+In this manner, we can compare the training accuracies in the last sample for both models.
+kNN is set to 5 nearest neighbors and proximity metric of Euclidian distance.
+Online learning metrics are evaluated in progressive valuation on a dataset that is left unbalanced.
+
+The \textbf{stream of events is sorted} by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}) which ensures steady increments in label counts throughout the whole duration of the simulation (Fig.~\ref{fig:design:online-event-order}).
+This constructed event sequence is a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
+It is meant to approximate the gradual overall degradation of the machine.
 
@@
         \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
-        \caption{Training set and defect types ``fault'' as predicted variable}
+        \caption{Event ordering of faults}
+        \label{fig:design:online-event-order}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-anomaly60-train.png}
-        \caption{Training set and anomaly with severity above 0.6 ``anomaly60'' as predicted variable}
+        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
+        \caption{Fault severity levels ordering}
+        \label{fig:design:online-count-severity-level}
     \end{subfigure}
@@
 
-% Gradual learning with delay - label provided after it has been predicted by the model
-	% The amount to wait before revealing the target associated with each observation to the model.
+Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
+Counters of other faults show that model prediction are skewed towards more represented classes of imbalance and misalignement.
+The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
+The training accuracies of comparable batch models are 94.13\% \emph{(temporal features)} and 99.17\% \emph{(spectral features)}.
+
+During gradual learning, the correct label is supplied after a fixed period passes after its prediction.
+This \textbf{sliding window} simulation examines accuracy every 100 iterations.
+Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{ffig:design:online-fault-delay-sliding}).
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
+        \caption{Principal components from temporal domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
+        \caption{Principal components from spectral domain features}
+    \end{subfigure}
+    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
+    \label{fig:design:scatter-plot-online}
+\end{figure}
+
+Accuracies after sequentially seeing all samples are 82.92\% \emph{(temporal)} and 89.11\% \emph{(spectral)} when labels are shown instantly.
+Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
+Labeling delay of 250 observations causes accuracies to drop to 70.51\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
+Accuracy better than 50\% is achieved 200 steps sooner in the spectral domain than in the temporal domain.
 
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-        \caption{Temporal domain features, predicted variable is fault}
+        \caption{Temporal domain features}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-        \caption{Spectral domain features, predicted variable is fault}
+        \caption{Spectral domain features}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-anomaly60.png}
-        \caption{Temporal domain features, predicted variable is anomaly above severity 0.6}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-anomaly60.png}
-        \caption{Spectral domain features, predicted variable is anomaly above severity 0.6}
-    \end{subfigure}
-    \caption{Incremental learning on all extracted features with delayed reveal of labels in rolling window}
+    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows.}
+    \label{fig:design:online-fault-delay-sliding}
 \end{figure}
 
-% Window learning- all labels for fixed previous period are provided at once.
+The \textbf{tumbling window} simulates regular expert visits annotating observations recorded until that moment.
+Labels for the whole previous window are supplied at once.
+At the final sample, the accuracies are 83.41\% \emph{(temporal)} and 90.14\% \emph{(spectral)} with immediate feedback, and 77.95\% \emph{(temporal)} and 85.90\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
 
@@
     \end{subfigure}
-    \caption{Incremental learning for variable ``fault'' with delayed reveal of labels at regular intervals.}
+    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows.}
+    \label{fig:design:online-fault-delay-tumbling}
 \end{figure}
 
-% Missing labels - some labels are skipped before another one is anotated
+A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
+Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows true labels are unknown.
+After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observation.
+
+Another common problem in online learning is \textbf{missing annotations} due to the size of the dataset.
+In the simulation of missing labels, the equal-length gaps are skipped before another observation is annotated.
+This approach of choosing samples to annotate without considering their representativeness results in severe harm to predictions.
 
@@
     \end{subfigure}
-    \caption{Incremental learning with skipping of labels and delay of 10 observations}
+    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
+    \label{fig:design:online-label-skip}
 \end{figure}
 
-% Scatter plot of fault classification - min-max scale shifts. From left true labels, predicted labels, mistakes made by model in red
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
-        \caption{}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
-        \caption{}
-    \end{subfigure}
-    \caption{PCA 2 components to visualize results and mistakes of online learning on all features}
-\end{figure}
-
-\clearpage
-\newpage
+Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.77\% to 74.07\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
+Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\%.
+The same cannot be said about the model from temporal features with very poor accuracy of 53.68\%.
+More missing labels require recording more observations before the equivalent accuracy is reached.
 

### 2023-12-25 thesis/chapters/03-design.tex
Rough draft of vibration measurement plan

@@
 \section{Vibration measurement plan}
+%TODO
+Identify machines, measurement positions, vibration sensor requirements and parameters with schedule for long-term measurement. It has to take into account with machinery operations.
 
 \subsection{Machinery}
-% Enum list
+We have three kinds of rotating machines at disposal for measurements which are standing fan, scroll compressor, and water pump:
+\begin{itemize}
+\itemsep0pt
+\item \textbf{Standing fan}: model \emph{Kalorik TKG VT 1037 C} (Fig.~\ref{fig:machine:fan}) 1 piece with 1 measurement axial position on the plastic casing back of the electromotor  as testing environment for firmware.
+It has 45W of power (ISO 20186 class \rom{1}) and 45 cm fan diameter consiting of 3 propelers.
+3 speeds are approximated with tolerance of $\pm$ 0.61 Hz (37 rpm) by measuring fundamental frequency to speed 1 is 18.5 Hz (1100 rpm), speed 2 is 20.4 Hz (1200 rpm), speed 3 is 22 Hz (1300 rpm).
+Acceleration observed is $\pm$ 5 $\mathrm{m/s}^2$ in radial and tangential directions, and $\pm$ 1 $\mathrm{m/s}^2$ in axial direction.
+
+\item \textbf{Scroll compressor}: model \emph{Copeland ZR16M3E-TWD-561} (Fig.~\ref{fig:machine:compressor}) 2 pieces in two independent air condition units Vertiv for data center.
+Compressor has 9.7 kW of power (ISO20186 class \rom{1}).
+It rotates with 2900 rpm (48.3 Hz).
+Faulty parts can result in unbalance of the rotor, fault of the scroll, mechanical assembly loose, or losse bearing.
+It has two possible measuremnt locations from sides on bearing just above the base and above the scroll.
+Accelerations picked up by sensor are $\pm$ 3 $\mathrm{m/s}^2$ tops.
+
+\item \textbf{Water pump}: 3 municipal single-stage axially split volute casing pump and attached electric induction motor with squirrel cage rotor.
+Newer primary pump with vendor cloud monitoring solution is \emph{KSB Omega 300-560 B GB G F} (Fig.~\ref{fig:machine:pump-ksb}) commisioned in 2019, with rotational speed around 1500 rpm (precisly 1493 rpm or 24.9 Hz).
+Motor has 400 kW of power (ISO20186 class \rom{2}).
+Outer bearing on pump experiences acceleration of  Secondary pumps are  two pieces produced by Sigma (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of $\pm$ 5 $\mathrm{m/s}^2$ ,  .
+Each pump and motor has 2 bearing therefore 4 measuement positions in total.
+\end{itemize}
 
@@
     		\centering
-        \includegraphics[width=0.5\textwidth]{assets/design/machine-fan.jpg}
+        \includegraphics[width=0.4\textwidth]{assets/design/machine-fan.jpg}
         \caption{Stand fan Kalorik}
+        \label{fig:machine:fan}
     \end{subfigure}
@@
     		\centering
-        \includegraphics[width=0.5\textwidth]{assets/design/machine-compressor.jpg}
+        \includegraphics[width=0.4\textwidth]{assets/design/machine-compressor.jpg}
         \caption{Scroll compressor Copeland}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
-        \caption{Water pump KSB Omega}
+        \label{fig:machine:compressor}
     \end{subfigure}
@@
     		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
+        \includegraphics[width=0.8\textwidth]{assets/design/machine-ksb-pump.jpg}
+        \caption{Water pump KSB Omega}
+        \label{fig:machine:pump-ksb}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=0.8\textwidth]{assets/design/machine-sigma-pump.jpg}
         \caption{Water pump Sigma}
+        \label{fig:machine:pump-sigma}
     \end{subfigure}
-    \caption{Machine}
+    \caption{Machines dedicated for vibration measurements}
+\end{figure}
+
+%TODO bi-weekly measurements. Describe preliminary measurements and orbital
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.44\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
+        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.55\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
+        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
+    \end{subfigure} 
+    \caption{Signals at 5 s timestamp}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{assets/design/compressor-orbitals-1x.png}
+	\caption{Orbital analysis of compressor's 1x harmonic}
 \end{figure}
@@
 \subsection{Sensors}
+In prelimary exploratory vibration measurements of machines we used ADXL335 accelerometer connected to BeagleBone Black microcontroller.
+Hardware characteristics are depicted in Table~\ref{tab:design:hw-sensors}.
+The bandwidth, sensitivity and  sampling frequency in the first attempt solution we find to be not adequate (satisfactory).
 
@@
 \caption{Accelerometers}
+\label{tab:design:hw-sensors}
 \end{table}
+
+The ST IIS3DWB is appropriately low priced accelerometer approching industrial standards for vibration monitoring.
+We need high speed interface to store all recorded samples to be used in later analysis and optimization.
+Therefore as a microcontroller development kit we choose ESP32-PoE-ISO that has SD card slot connected via SD/MMC bus.
+SPI bus can be connected to any GPIO pin and is routed via GPIO matrix at lower but enough speed, sensor can handle SPI speed of 10 MHz at maximum.
+The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{assets/design/hw-block-schematic.png}
+	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
 	\caption{Sensor unit hardware block diagram}
+	\label{fig:design:block-diagram-hw}
 \end{figure}
 
-\subsection{Preliminary measurements}
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.44\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
-    \end{subfigure} 
-    \caption{Signals at 5 s timestamp}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.6\textwidth]{assets/design/compressor-orbitals-1x.png}
-	\caption{Orbital analysis of compressor's 1x harmonic}
-\end{figure}
+The drivers for neccessary low level interfaces and FatFS filesystem are already implemented in ESP-IDF software development kit\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
+The acceleromter driver is also made available by vendor and can be integrated with just two function calls to bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.

### 2023-12-26 thesis/chapters/02-analysis-A-CdM.tex
Rough draft of vibration measurement plan
Vibration measurement plan

@@
 
-\subsection{Technical standards}
+\subsection{Technical standards} \label{section:technical-standards}
 Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards.
@@
 In \emph{zone C} the machine is deemed in unsatisfactory condition and corrective action should be taken soon.
-Finally, in zone D vibrations can cause damage to the machine.
+Finally, in \emph{zone D} vibrations can cause damage to the machine.
 The span of acceptable values differs with the machine class from I through to IV and their output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.

### 2023-12-26 thesis/chapters/03-design.tex
Vibration measurement plan

--- 2023-12-25 thesis/chapters/03-design.tex
@@
 
-Confusion matrices for fault predicion and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}.
+Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}.
 In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
 The most inaccuracies in the temporal domain are between misalignment and bearing race faults.
-In the spectral domain, the model confuses imbalance and bearing faults.
-It is to be expected since mass to unbalance the shaft is hanged to simulate bearing defects.
+In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.
 
@@
 This \textbf{sliding window} simulation examines accuracy every 100 iterations.
-Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{ffig:design:online-fault-delay-sliding}).
+Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).
 
@@
 
-\section{Vibration measurement plan}
+\section{Dataset collection in industrial environment}
+The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment.
+Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}).
+We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes.
+The collection of the novel dataset is accompanied by an agreed upon schedule.
 
 \subsection{Machinery}
-% Enum list
+Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
 
@@
     \centering
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{0.17\textwidth}
     		\centering
-        \includegraphics[width=0.5\textwidth]{assets/design/machine-fan.jpg}
-        \caption{Stand fan Kalorik}
+        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
+        \caption{\footnotesize Fan}
+        \label{fig:machine:fan}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{0.17\textwidth}
     		\centering
-        \includegraphics[width=0.5\textwidth]{assets/design/machine-compressor.jpg}
-        \caption{Scroll compressor Copeland}
+        \includegraphics[width=\textwidth]{assets/design/machine-compressor.jpg}
+        \caption{\footnotesize Compressor}
+        \label{fig:machine:compressor}
     \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
     		\centering
         \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
-        \caption{Water pump KSB Omega}
+        \caption{\footnotesize Water pump KSB}
+        \label{fig:machine:pump-ksb}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
     		\centering
         \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
-        \caption{Water pump Sigma}
+        \caption{\footnotesize Water pump Sigma}
+        \label{fig:machine:pump-sigma}
     \end{subfigure}
-    \caption{Machine}
+    \caption{Machines dedicated for vibration measurements}
 \end{figure}
 
+\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
+It serves as a test bed during the sensor unit development.
+The sensor is placed on the plastic casing at the back of the drive motor.
+The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
+It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
+Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.
+
+\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}) and altogether two units are available in two independent air conditioning units for the data center.
+The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
+Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
+Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.
+
+\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
+The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor with a squirrel cage rotor.
+
+The newer primary pump with cloud monitoring solution is one unit of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The pump was commissioned in 2019 and it rotates at a speed of circa 1500 rpm (precisely 1493 rpm or 24.9 Hz).
+The electric motor in the vicinity has 400~kW of power (class~\rom{2}).
+Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.
+
+Secondary pumps are two units produced by \emph{Sigma} (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of 250~kW and 100~kW.
+Each pump and motor has 2 bearings therefore there are 4 measurement positions in total.
+
+\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix \ref{appendix:data-collection}.
+
 \subsection{Sensors}
+In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
+The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate.
+Hardware parameters of previous and proposed sensor units are in Table~\ref{tab:design:hw-sensors}.
 
@@
 \caption{Accelerometers}
+\label{tab:design:hw-sensors}
 \end{table}
+
+The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
+An interface capable of higher speeds is needed to store all acceleration samples.
+Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
+The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pins.
+The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{assets/design/hw-block-schematic.png}
+	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
 	\caption{Sensor unit hardware block diagram}
+	\label{fig:design:block-diagram-hw}
 \end{figure}
 
+The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF software development kit\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
+The accelerometer driver is also made available by the vendor and can be integrated with just two function calls for bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
+
 \subsection{Preliminary measurements}
+% Describe preliminary measurements, waveform (1) orbital (2), velocity (3)
+
 \begin{figure}[ht]
     \centering
-    \begin{subfigure}[b]{0.44\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
         \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
+        \caption{Acceleration in $\mathrm{m/s}^2$}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
+        \caption{Approximate velocity in $\mathrm{mm/s}$}
     \end{subfigure} 
-    \caption{Signals at 5 s timestamp}
+    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
 \end{figure}
 
-\begin{figure}[h]
+% Velocity: integrated with composite trapezoidal rule and subtracted mean of envelope found by cubic interpolation of peaks.
+
+% bandpass Butterworth filter of \nth{5} order with cuttoff frequencies f_{max} \pm 5 Hz.
+
+\begin{figure}[ht]
     \centering
-	\includegraphics[width=0.6\textwidth]{assets/design/compressor-orbitals-1x.png}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
 	\caption{Orbital analysis of compressor's 1x harmonic}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.54\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
+        \caption{Spectral domain in x axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
+    \end{subfigure} 
+    \caption{Orbital and spectral methods of vibration signal analysis}
 \end{figure}
+
+% Historical logs of pump from KSB cloud
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
+     \caption{KSB cloud pump monitoring after ramp up with displayed warning and alert levels}
+\end{figure}

### 2023-12-26 thesis/chapters/appendix/C-measurement-plan.tex
Vibration measurement plan

\thispagestyle{empty}
\chapter{Data collection plan} \label{appendix:data-collection}
\pagenumbering{arabic}
\renewcommand*{\thepage}{C-\arabic{page}}

The vibration measurements will occur biweekly and will contain three trials for each position as designed in the checklist spreadsheet below. The sensor is mounted to the machine with adhesive on double-sided carpet tape. After every trial, the sensor is detached and attached again.

Each triaxial recording has a 60-second duration at a sampling frequency of 26.6 kHz and a sample resolution of 16 bits. Measurement places are described according to the MIMOSA convention (ISO~13373-1). The total space requirement for a complete dataset composed out of 192 recordings is 1.71 GiB.

\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|l|l|lll|lll|lll|lll|}
\hline
\textbf{Machine}                                                                       & \textbf{Placement / Inspection} & \multicolumn{3}{l|}{\textbf{\nth{1}}}                & \multicolumn{3}{l|}{\textbf{\nth{2}}}                & \multicolumn{3}{l|}{\textbf{\nth{3}}}                & \multicolumn{3}{l|}{\textbf{\nth{4}}}                \\ \hline
\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC no.3\end{tabular}}} & SFTA001AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & SFTA002AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \hline
\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC no.5\end{tabular}}} & SFTA001AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & SFTA002AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \hline
\multirow{4}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump\\ KSB (new)\end{tabular}}}     & MTRA001AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & MTRA002AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA003AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA004AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \hline
\multirow{4}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump\\ Sigma (big)\end{tabular}}}   & MTRA001AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & MTRA002AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA003AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA004AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \hline
\multirow{4}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump\\ Sigma (small)\end{tabular}}} & MTRA001AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & MTRA002AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA003AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \cline{2-14} 
                                                                                       & PMPA004AT000TN                               & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} &  \\ \hline
\end{tabular}
\end{table}

\clearpage

### 2023-12-26 thesis/chapters/03-design.tex
Describe preliminary measurements in industry environment

@@
     \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows.}
+    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
     \label{fig:design:online-fault-delay-sliding}
@@
     \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows.}
+    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
     \label{fig:design:online-fault-delay-tumbling}
@@
 \textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix \ref{appendix:data-collection}.
+In addition, we might be able to export the entire historical logs of the water pump from \textbf{KSB cloud} to enlarge the dataset.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
+     \caption{KSB cloud pump monitoring after ramp-up with displayed warning and alert levels}
+\end{figure}
 
@@
 In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
-The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate.
-Hardware parameters of previous and proposed sensor units are in Table~\ref{tab:design:hw-sensors}.
+The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
 
@@
 \end{tabular}
-\caption{Accelerometers}
+\caption{Hardware parameters of previous and proposed sensor units}
 \label{tab:design:hw-sensors}
@@
 The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF software development kit\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
-The accelerometer driver is also made available by the vendor and can be integrated with just two function calls for bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
+The accelerometer driver is also made available by the vendor and demands customization of bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
 
 \subsection{Preliminary measurements}
-% Describe preliminary measurements, waveform (1) orbital (2), velocity (3)
+During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
+Raw waveforms of acceleration for the fan, two different compressors, and outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
+The acceleration rarely exceeds 1~g.
+
+In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned, below the resonance frequency of the accelerometer (550 Hz).
+The compressor suspected to be faulty has stronger \nth{4} harmonic and above than the other one.
 
@@
         \caption{Acceleration in $\mathrm{m/s}^2$}
+        \label{fig:design:preliminary-acceleration}
     \end{subfigure}
@@
         \caption{Approximate velocity in $\mathrm{mm/s}$}
+        \label{fig:design:preliminary-velocity}
     \end{subfigure} 
@@
 
-% Velocity: integrated with composite trapezoidal rule and subtracted mean of envelope found by cubic interpolation of peaks.
+Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
+The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks.
+Envelopes must be tweaked further to achieve more accurate values.
 
-% bandpass Butterworth filter of \nth{5} order with cuttoff frequencies f_{max} \pm 5 Hz.
+The orbital plot of the first harmonic frequency $f_{max}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
+The Butterworth filter of \nth{5} order with cutoff frequencies $f_{max} \pm 5\;\mathrm{Hz}$ is applied in its filtering.
 
@@
         \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
-	\caption{Orbital analysis of compressor's 1x harmonic}
+		\caption{Orbital analysis of compressor's \nth{1} harmonic frequency}
+		\label{fig:design:orbital-analysis}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{Spectral domain in x axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
+        \caption{FFT with Hann window of length $2^{10}$ ($\approx 409\;\mathrm{ms}$)}
+        \label{fig:design:preliminary-spectrum}
     \end{subfigure} 
@@
 \end{figure}
-
-% Historical logs of pump from KSB cloud
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
-     \caption{KSB cloud pump monitoring after ramp up with displayed warning and alert levels}
-\end{figure}

### 2023-12-26 thesis/chapters/appendix/C-measurement-plan.tex
Describe preliminary measurements in industry environment

@@
 
-Each triaxial recording has a 60-second duration at a sampling frequency of 26.6 kHz and a sample resolution of 16 bits.
+Each triaxial recording has a 60-second duration at a sampling frequency of 26.7 kHz and a sample resolution of 16 bits.
 Measurement places are described according to the MIMOSA convention (ISO~13373-1).
-The total space requirement for a complete dataset composed out of 192 recordings is 1.71 GiB.
+The total space requirement for a complete dataset composed out of 192 recordings is 1.72 GiB.
 

### 2023-12-27 thesis/chapters/05-conclusion.tex
Conclusion for DP2

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute 10 features summarizing waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.

In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable. Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning. The features are squished from multiple dimensions using the Euclidian norm. Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset. We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.

Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power. Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%. The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.

The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations. No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively. Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotation can be assigned belatedly or even never. Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions. Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.

The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations. We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards. The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.

Feature selection methods shall be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2023-12-27 thesis/chapters/01-introduction.tex
Introduction

@@
 \chapter{Introduction}
-Manufacturing is experiencing a shift in traditional asset operational status evaluation and utilization.
+Manufacturing experiences a shift in traditional asset operational status evaluation and utilization.
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
@@
 
-This progress report on the master's thesis is organized as follows.
-In the problem analysis, in section \ref{section:condition-monitoring} we explore the mechanical maintenance approaches and industry standards on common fault identification.
-Section \ref{section:signal-preprocessing} summarizes filters for signal preprocessing.
-The \ref{section:feature-engineering} is about measuring vibrations and their transformation into features meaningful in automatic fault pattern recognition.
-In \ref{section:diagnostics-techniques}, we delve into modes of machinery diagnostics based on obtained relevant indicators, and \ref{section:evaluation-datasets} describes the most common datasets for machinery faults.
-Chapter \ref{section:design} proposes the preliminary design of the model exploration and deployment phase of the project.
+This progress report on the master's thesis \rom{2} is organized followingly.
+The problem analysis chapter \ref{chapter:problem-analysis} begins by exploring the mechanical maintenance approaches and industry standards on common fault identification.
+Vibration monitoring starts with a section on preprocessing that summarizes basic filters.
+The process of transforming raw samples into features and their meaningful selection is covered in automatic fault pattern recognition with machine learning models trained in offline and online contexts.
+An overview follows of the most common machinery fault databases.
+
+Chapter \ref{chapter:design} on solution design starts by posing research questions and establishing goals.
+Then, the MaFaulDa dataset statistical properties and labeling procedure are described on the original samples as well as on extracted attributes.
+Data rates with feature selection are derived based on the MaFaulDa.
+In the section about classification models, we compare the performance for various feature sets in the k-nearest neighbors algorithm.
+Finally, in preparation for the evaluation part, designated machines in the industrial environment are presented alongside the sensor device suitable for their measurement.

### 2023-12-27 thesis/chapters/02-analysis-B-features.tex
Principal components analysis
Increamental learing results with kNN
Introduction

@@
 ``Negentropy measures the inclination of a system to increase its level of organization''~\cite{avoci_spectral_2020}.
-The larger \emph{spectral negentropy} (Equation~\ref{equ:spectral-negentropy}) suggests more fault-induced impulses.
+The larger \emph{spectral negentropy} suggests more fault-induced impulses.
 $E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
@@
 
-\section{Feature transformations}
+\section{Feature transformations} \label{section:feature-selection}
 Numerical features from the feature extraction phase have non-normal distributions and span the range of scales.
@@
 \widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
-\label{equ:min-max-scaler}
 \end{align}\end{ceqn}

### 2023-12-27 thesis/chapters/preliminaries/annotation.tex
Conclusion for DP2
Annotation in SK/EN for DP2

--- 2023-05-01 thesis/chapters/preliminaries/annotation.tex
@@
 &\text{Degree course:} && \text{\StudyProgrammeEN} \\
-&\text{Author:} && \text{\Author} \\
+&\text{Author:} && \text{\AuthorEN} \\
 &\text{\ThesisEN:} && \text{\TitleEN} \\
-&\text{Supervisor:} && \text{\SupervisorEN} \\
+&\text{Thesis supervisor:} && \text{\SupervisorEN} \\
 &\text{Departmental advisor:} && \text{\DepartmentalAdvisorEN} \\
@@
 
+The progress report in Master's thesis project \rom{2} deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.
+
+Trend indicators are derived from vibration signals to form summarizing numerical attributes.
+The similarity of features to a dependent variable describing fault types is assessed with supervised feature selection metrics individually and in the ensemble.
+The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve data rates of the monitoring solution.
+The incremental learning model is compared to its batch counterpart when truthful labels are delayed or missing.
+
+Based on the MaFaulDa dataset, classification metrics are evaluated in several scenarios, and lossy compression ratios are expressed.
+The measurement plan and sensor device are designed to enable collection of novel datasets of machinery behavior for compressors and pumps.
+The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.
 \emptypage
@@
 
+Priebežná správa o riešení DP2 sa zaoberá monitorovaním stavu rotačných strojov a ich prediktívnou údržbou prostredníctvom techník výberu atribútov a štatistickej klasifikácie.
+
+Z vibračných signálov sú odvodené trendové indikátory a tak vytvárajú sumarizujúce číselné atribúty.
+Podobnosť atribútov so závislou premennou popisujúcou typy porúch sa posudzuje metrikami výberu atribútov v učení s učiteľom.
+Metriky sú hodnotené individuálne a súborovo.
+Presnosť detekcie porúch s algoritmom k-najbližších susedov sa vyhodnocuje na podskupinách najlepších atribútov, aby sa znížili požiadavky na objem prenosu dát v monitorovacom riešení.
+Model prírastkového učenia sa porovnáva s jeho dávkovým náprotivkom, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
+
+Na základe súboru údajov MaFaulDa sú klasifikačné metriky vyhodnocované podľa viacerých scenárov a tiež sú vyjdrené stratové kompresné pomery.
+Plán merania a senzorové zariadenie sú navrhnuté na zber nového súboru údajov o správaní sa strojov ako sú kompresory a čerpadlá.
+Prínos tejto práce spočíva v identifikácii možnosti použitia iba pár veličín na opis nielen prítomnosti poruchy, ale aj jej príčiny.
 \emptypage

### 2023-12-27 thesis/chapters/01-introduction.tex
Move machinery and sensors to implementation and resume background

@@
 \chapter{Introduction}
-Manufacturing experiences a shift in traditional asset operational status evaluation and utilization.
+The industry experiences a shift in traditional asset operational status evaluation and utilization.
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
@@
 
-Vibrations are the most non-intrusive way to sense and record eventually fatal deficiencies right at the onset.
+Vibrations are non-intrusive way to sense and record eventually fatal deficiencies right at the onset.
 The experts use it to distinguish faulty states and to identify the malfunction's root causes.
@@
 In the section about classification models, we compare the performance for various feature sets in the k-nearest neighbors algorithm.
-Finally, in preparation for the evaluation part, designated machines in the industrial environment are presented alongside the sensor device suitable for their measurement.
+Finally, in preparation for the evaluation part, the sensor device is propresed which is suitable for measurements of designated machines in the industrial environment.

### 2023-12-27 thesis/chapters/03-design.tex
Introduction
Move machinery and sensors to implementation and resume background

--- 2023-12-25 thesis/chapters/03-design.tex
@@
-\chapter{Design} \label{section:design}
+\chapter{Design} \label{chapter:design}
 The design phase sets out to elaborate on the scenarios for experiments with IoT device.
@@
 More missing labels require recording more observations before the equivalent accuracy is reached.
-
-\section{Vibration measurement plan}
-%TODO
-Identify machines, measurement positions, vibration sensor requirements and parameters with schedule for long-term measurement. It has to take into account with machinery operations.
-
-\subsection{Machinery}
-We have three kinds of rotating machines at disposal for measurements which are standing fan, scroll compressor, and water pump:
-\begin{itemize}
-\itemsep0pt
-\item \textbf{Standing fan}: model \emph{Kalorik TKG VT 1037 C} (Fig.~\ref{fig:machine:fan}) 1 piece with 1 measurement axial position on the plastic casing back of the electromotor  as testing environment for firmware.
-It has 45W of power (ISO 20186 class \rom{1}) and 45 cm fan diameter consiting of 3 propelers.
-3 speeds are approximated with tolerance of $\pm$ 0.61 Hz (37 rpm) by measuring fundamental frequency to speed 1 is 18.5 Hz (1100 rpm), speed 2 is 20.4 Hz (1200 rpm), speed 3 is 22 Hz (1300 rpm).
-Acceleration observed is $\pm$ 5 $\mathrm{m/s}^2$ in radial and tangential directions, and $\pm$ 1 $\mathrm{m/s}^2$ in axial direction.
-
-\item \textbf{Scroll compressor}: model \emph{Copeland ZR16M3E-TWD-561} (Fig.~\ref{fig:machine:compressor}) 2 pieces in two independent air condition units Vertiv for data center.
-Compressor has 9.7 kW of power (ISO20186 class \rom{1}).
-It rotates with 2900 rpm (48.3 Hz).
-Faulty parts can result in unbalance of the rotor, fault of the scroll, mechanical assembly loose, or losse bearing.
-It has two possible measuremnt locations from sides on bearing just above the base and above the scroll.
-Accelerations picked up by sensor are $\pm$ 3 $\mathrm{m/s}^2$ tops.
-
-\item \textbf{Water pump}: 3 municipal single-stage axially split volute casing pump and attached electric induction motor with squirrel cage rotor.
-Newer primary pump with vendor cloud monitoring solution is \emph{KSB Omega 300-560 B GB G F} (Fig.~\ref{fig:machine:pump-ksb}) commisioned in 2019, with rotational speed around 1500 rpm (precisly 1493 rpm or 24.9 Hz).
-Motor has 400 kW of power (ISO20186 class \rom{2}).
-Outer bearing on pump experiences acceleration of  Secondary pumps are  two pieces produced by Sigma (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of $\pm$ 5 $\mathrm{m/s}^2$ ,  .
-Each pump and motor has 2 bearing therefore 4 measuement positions in total.
-\end{itemize}
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=0.4\textwidth]{assets/design/machine-fan.jpg}
-        \caption{Stand fan Kalorik}
-        \label{fig:machine:fan}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=0.4\textwidth]{assets/design/machine-compressor.jpg}
-        \caption{Scroll compressor Copeland}
-        \label{fig:machine:compressor}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=0.8\textwidth]{assets/design/machine-ksb-pump.jpg}
-        \caption{Water pump KSB Omega}
-        \label{fig:machine:pump-ksb}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=0.8\textwidth]{assets/design/machine-sigma-pump.jpg}
-        \caption{Water pump Sigma}
-        \label{fig:machine:pump-sigma}
-    \end{subfigure}
-    \caption{Machines dedicated for vibration measurements}
-\end{figure}
-
-%TODO bi-weekly measurements. Describe preliminary measurements and orbital
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.44\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
-    \end{subfigure} 
-    \caption{Signals at 5 s timestamp}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.5\textwidth]{assets/design/compressor-orbitals-1x.png}
-	\caption{Orbital analysis of compressor's 1x harmonic}
-\end{figure}
-
-\subsection{Sensors}
-In prelimary exploratory vibration measurements of machines we used ADXL335 accelerometer connected to BeagleBone Black microcontroller.
-Hardware characteristics are depicted in Table~\ref{tab:design:hw-sensors}.
-The bandwidth, sensitivity and  sampling frequency in the first attempt solution we find to be not adequate (satisfactory).
-
-\begin{table}[ht]
-\renewcommand{\arraystretch}{1.2}
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
-\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
-\textbf{Bus}                                     & Analog           & SPI                \\ \hline
-\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
-\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
-\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
-\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
-\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
-\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
-\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
-\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
-\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
-\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
-\end{tabular}
-\caption{Accelerometers}
-\label{tab:design:hw-sensors}
-\end{table}
-
-The ST IIS3DWB is appropriately low priced accelerometer approching industrial standards for vibration monitoring.
-We need high speed interface to store all recorded samples to be used in later analysis and optimization.
-Therefore as a microcontroller development kit we choose ESP32-PoE-ISO that has SD card slot connected via SD/MMC bus.
-SPI bus can be connected to any GPIO pin and is routed via GPIO matrix at lower but enough speed, sensor can handle SPI speed of 10 MHz at maximum.
-The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
-	\caption{Sensor unit hardware block diagram}
-	\label{fig:design:block-diagram-hw}
-\end{figure}
-
-The drivers for neccessary low level interfaces and FatFS filesystem are already implemented in ESP-IDF software development kit\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
-The acceleromter driver is also made available by vendor and can be integrated with just two function calls to bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.

### 2023-12-27 thesis/chapters/04-implementation.tex
Move machinery and sensors to implementation and resume background

@@
 \chapter{Implementation} \label{section:implementation} 
+The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment.
+Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}).
+
+We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes.
+The collection of the novel dataset is accompanied by an agreed upon schedule.
+
+\section{Monitored machinery}
+Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.17\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
+        \caption{\footnotesize Fan}
+        \label{fig:machine:fan}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.17\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-compressor.jpg}
+        \caption{\footnotesize Compressor}
+        \label{fig:machine:compressor}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
+        \caption{\footnotesize Water pump KSB}
+        \label{fig:machine:pump-ksb}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
+        \caption{\footnotesize Water pump Sigma}
+        \label{fig:machine:pump-sigma}
+    \end{subfigure}
+    \caption{Machines dedicated for vibration measurements}
+\end{figure}
+
+\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
+It serves as a test bed during the sensor unit development.
+The sensor is placed on the plastic casing at the back of the drive motor.
+The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
+It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
+Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.
+
+\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}) and altogether two units are available in two independent air conditioning units for the data center.
+The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
+Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
+Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.
+
+\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
+The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor with a squirrel cage rotor.
+
+The newer primary pump with cloud monitoring solution is one unit of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The pump was commissioned in 2019 and it rotates at a speed of circa 1500 rpm (precisely 1493 rpm or 24.9 Hz).
+The electric motor in the vicinity has 400~kW of power (class~\rom{2}).
+Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.
+
+Secondary pumps are two units produced by \emph{Sigma} (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of 250~kW and 100~kW.
+Each pump and motor has 2 bearings therefore there are 4 measurement positions in total.
+
+\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix \ref{appendix:data-collection}.
+In addition, we might be able to export the entire historical logs of the water pump from \textbf{KSB cloud} to enlarge the dataset.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
+     \caption{KSB cloud pump monitoring after ramp-up with displayed warning and alert levels}
+\end{figure}
+
+\section{Sensor hardware and drivers}
+In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
+The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
+\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
+\textbf{Bus}                                     & Analog           & SPI                \\ \hline
+\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
+\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
+\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
+\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
+\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
+\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
+\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
+\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
+\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
+\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
+\end{tabular}
+\caption{Hardware parameters of previous and proposed sensor units}
+\label{tab:design:hw-sensors}
+\end{table}
+
+The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
+An interface capable of higher speeds is needed to store all acceleration samples.
+Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
+The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pins.
+The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
+	\caption{Sensor unit hardware block diagram}
+	\label{fig:design:block-diagram-hw}
+\end{figure}
+
+The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF SDK\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
+The accelerometer driver is also made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
+
+\section{Preliminary measurements}
+During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
+Raw waveforms of acceleration for the fan, two different compressors, and outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
+The acceleration rarely exceeds 1~g.
+
+In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned, below the resonance frequency of the accelerometer (550 Hz).
+The compressor suspected to be faulty has stronger \nth{4} harmonic and above than the other one.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
+        \caption{Acceleration in $\mathrm{m/s}^2$}
+        \label{fig:design:preliminary-acceleration}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
+        \caption{Approximate velocity in $\mathrm{mm/s}$}
+        \label{fig:design:preliminary-velocity}
+    \end{subfigure} 
+    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
+\end{figure}
+
+Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
+The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks.
+Envelopes must be tweaked further to achieve more accurate values.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
+		\caption{Orbital analysis of compressor's \nth{1} harmonic frequency}
+		\label{fig:design:orbital-analysis}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.54\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
+        \caption{FFT with Hann window of length $2^{10}$ ($\approx 409\;\mathrm{ms}$)}
+        \label{fig:design:preliminary-spectrum}
+    \end{subfigure} 
+    \caption{Orbital and spectral methods of vibration signal analysis}
+\end{figure}
+
+The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.

### 2023-12-27 thesis/chapters/appendix/A-resume.tex
Move machinery and sensors to implementation and resume background

\thispagestyle{empty}
\chapter{Resumé}
\pagenumbering{arabic}
\renewcommand*{\thepage}{A-\arabic{page}}

\section{Úvod}
Vzostup priemyslu 4.0 prináša so sebou väčšiu mieru automatizácie s cieľom dosiahnuť optimálne využitie dostupných zdrojov. Na základe nepretržitého sledovania opotrebenia zariadení v reálnom čase sa majú zabezpečiť nápravné opatrenia na opravu alebo výmenu súčiastok včas, v reakcii na trendové ukazovatele.

Cieľom je zachovať požadovanú bezpečnosť a efektivitu výroby a zároveň predĺžiť životnosť rotujúcich komponentov. Proaktívna diagnostika porúch je nevyhnutná na začatie opráv bez nadbytočných nákladov. Vibrácie predstavujú nerušivý spôsob, ako zistiť a zaznamenať prípadne fatálne zlyhania hneď v zárodku. Hlavným problémom pri monitorovaní veľa strojov s vibráciami, je to, že vzniká množstvo záznamov, ktoré nie sú priamo užitočné pre operátora výrobnej linky. Väčšina signálov sa zobrazí maximálne raz, preto je zbytočné ich ukladať alebo prenášať vcelku.

Zároveň na dosiahnutie maximálnej presnosti detekcie musí byť model strojového učenia trénovaný pre cieľové prostredie. Poruchy sú navyše pomerne zriedkavé udalosti, ktoré sa zvyčajne vyskytujú s odstupom niekoľkých mesiacov. Za týchto okolností je ťažké rýchlo získať dostatočne veľkú vzorku poruchových udalostí.

\section{Sledovanie prevádzkového stavu}
Existujú tri rôzne prístupy k údržbe strojov: reaktívny, preventívny a prediktívny.
Pri reaktívnej údržbe beží stroj až do úplného zlyhania a je prijateľná vtedy, keď sú dovolené krátke prestoje, je možná úplná a rýchla výmena pokazeného stroja za záložný, alebo ohrozenie zapríčinené poruchou je zanedbateľné. Preventívna údržba prebieha v pravidelných intervaloch odvodených od vopred určeného rozvrhu v alebo strednej doby medzi poruchami. Prediktívna údržba zlepšuje predvídateľnosť oproti reaktívnej údržbe a eliminuje plytvanie voči prílš obozretnej prevencii. Odstávka stroja je naplánovaná po zistení kritických hodnôt a po odhalení problematických komponentov.

Mechanické problémy počas prevádzky strojov spôsobujú v mnohých prípadoch vibrácie. Vibroakustická diagnostika sa preto považuje za jednu z najdôležitejších metód pri včasnej identifikácii porúch komponentov. Najbežnejšie sa vyskytujúcimi poruchami sú nevyváženosť, nesúososť, vôla, excentricita, deformácia, trhlina a nadmerné trenie.

Symptómy porúch rotačných strojov sa prejavujú rôznymi frekvenčnými pásmami, ale väčšina je závislá od rotačnej rýchlosti súčiastky. Nevyváženosť, nevyváženosť a vôla sa bežne objavujú v frekvenciách do 300 Hz. Poruchy ložísk a prevodovky v neskorých štádiách vývoja sa prejavujú v rozsahu medzi 300 Hz a 1 kHz. Vyššie frekvencie do 10 kHz pomáhajú odhaliť poruchy ložísk v skorších štádiach rozvoja.

Postupy monitorovania stavu založené na vibráciách musia byť v súlade s normatívnymi smernicami ISO 20816 a ISO 13373. Normy sa týkajú umiestnenia meracích zariadení, zberu údajov, konvencií nastavenia úrovní závažnosti porúch.

\section{Extrakcia a výber atribútov}
%TODO Page 14

\section{Diagnostické prístupy}

\section{Výskumné otázky}

\section{Návrh metód s MaFaulDa}

\section{Zber vibrácií v priemysle}

\section{Záver}

\clearpage

### 2023-12-27 thesis/chapters/preliminaries/annotation.tex
Move machinery and sensors to implementation and resume background

@@
 Metriky sú hodnotené individuálne a súborovo.
-Presnosť detekcie porúch s algoritmom k-najbližších susedov sa vyhodnocuje na podskupinách najlepších atribútov, aby sa znížili požiadavky na objem prenosu dát v monitorovacom riešení.
-Model prírastkového učenia sa porovnáva s jeho dávkovým náprotivkom, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
+Presnosť detekcie porúch algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
+Tým sa znížia požiadavky na objem prenosu dát v monitorovacom riešení.
+Model prírastkového učenia sa porovnáva s učením v dávkach, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
 
-Na základe súboru údajov MaFaulDa sú klasifikačné metriky vyhodnocované podľa viacerých scenárov a tiež sú vyjdrené stratové kompresné pomery.
+Na základe súboru údajov MaFaulDa sú klasifikačné metriky vyhodnotené podľa viacerých scenárov a tiež sú vyjdrené stratové kompresné pomery.
 Plán merania a senzorové zariadenie sú navrhnuté na zber nového súboru údajov o správaní sa strojov ako sú kompresory a čerpadlá.

### 2023-12-28 thesis/chapters/02-analysis-B-features.tex
Fix machinery information and finish Resume

@@
 It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model.
-Signal features are computed in the time, frequency, and time-frequency domain~\cite{brito_fault_2021}.
+Signal features are computed in the temporal and spectral domain~\cite{brito_fault_2021}.
 
@@
 In the spectral domain, we can obtain usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
-Additionaly spectral roll-on and roll-off, fundamental frequency, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
+Additionaly spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
 
@@
 \section{Feature transformations} \label{section:feature-selection}
-Numerical features from the feature extraction phase have non-normal distributions and span the range of scales.
+Numerical features from the feature extraction phase have non-normal distributions and span wide ranges.
 Broad differences among features skew the spread in the particular axis.

### 2023-12-28 thesis/chapters/02-analysis-C-diagnostics.tex
Write research questions in design section and place illustations
Fix machinery information and finish Resume

@@
 The detection model must deal with the minimal admissible assumptions about the nature of the input events.
-The outliers are based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
+The outliers are derived based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
 \bigbreak
@@
 Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1].
-It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters.
+It demands for points within clusters to have high cohesion and at the same time to have large separation from other clusters.
 The low score indicates a too little or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{assets/DenStream.png}
+    \includegraphics[width=0.8\textwidth]{assets/analysis/DenStream.png}
     \caption{DenStream~\cite{amini_density_2012}}
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{assets/HS-Tree.png}
+    \includegraphics[width=0.8\textwidth]{assets/analysis/HS-Tree.png}
     \caption{Half-space tree~\cite{tan_fast_2011}}
@@
 \subsection{Classification}
-Accurate multi-class classification of machine fault causes out of the characteristics of known ones is a much more difficult task than novelty detection.
-Universal enough fault baseline has to be recorded and transformed into feature space.
+Accurate multi-class classification of machine fault causes according to the characteristics of known ones is a much more difficult task than novelty detection.
+Fault combinations have to be recorded and transformed into feature space.
 Interactions among fault root causes have to be considered.
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/kNN.png}
+        \includegraphics[width=\textwidth]{assets/analysis/kNN.png}
         \caption{kNN with k = 5}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/M-tree.png}
+        \includegraphics[width=\textwidth]{assets/analysis/M-tree.png}
         \caption{M-tree data structure}
@@
 
-The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, or \emph{Manhatann distance} (Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020}.
+The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
+(Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
 The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
@@
 \subsection{Incremental learning}
-Online and incremental machine learning operates in the streaming setting updating the model parameters with each new incoming event or in mini-batches.
+Online or incremental machine learning operates on the streaming data updating the model parameters with each new incoming event or in mini-batches.
 This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.
@@
     \centering
-    \includegraphics[width=\textwidth]{assets/incremental-learning.png}
+    \includegraphics[width=\textwidth]{assets/analysis/incremental-learning.png}
     \caption{Incremental learning deployment architecture~\cite{gaia_online_2022}}

### 2023-12-28 thesis/chapters/03-design.tex
Fix machinery information and finish Resume

@@
 \section{Research questions}
-This thesis aims to provide answers to four research questions formulated in broader sense.
+This thesis aims to provide answers to four research questions.
 The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
@@
 \section{Dataset exploration}
-In establishing the validity of methods to be deployed on the sensor node we explore the MaFaulDa dataset.
+In establishing the viability of methods to be deployed in the sensor node, we explore the MaFaulDa dataset.
 It is the largest known machinery fault collection, so it is possible to create multiple subsets based on requested conditions.
@@
 
-The Euclidian norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure \ref{fig:design:feature-range}.
+The Euclidean norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure~\ref{fig:design:feature-range}.
 
@@
 \item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
-\item \textbf{target variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
+\item \textbf{predicted variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
 \item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
@@
 Voronoi diagrams can display these regions and explain the model in that way.
-Batch learning in kNN serves here as a target performance whose attainment is desirable with online learning.
+Batch learning in KNN serves here as a target performance whose attainment is desirable with online learning.
 
 \subsection{Batch models}
-Three types of kNN model experiments run with hold-out validation in batch setting. 
+Three types of KNN model experiments run with hold-out validation in batch setting. 
 First, the model learns all extracted features, so no feature selection occurs.
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-fault.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-fault.png}
         \caption{Prediction for 6 fault classes in testing set with temporal domain features}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-fault.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-fault.png}
         \caption{Prediction for 6 fault classes in testing set with spectral domain features}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-temporal-confusion-matrix-anomaly90.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-anomaly90.png}
         \caption{Prediction of high severity anomalies in testing set with temporal domain features}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-spectral-confusion-matrix-anomaly90.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-anomaly90.png}
         \caption{Prediction of high severity anomalies in testing set with spectral domain features}
     \end{subfigure}
-    \caption{Confusion matrix of kNN predictions on bearing position A}
-    \label{fig:design:knn-confusion-matrix}
+    \caption{Confusion matrix of KNN predictions on bearing position A}
+    \label{fig:design:KNN-confusion-matrix}
 \end{figure}
@@
 
-Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}.
+Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:KNN-confusion-matrix}.
 In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
@@
 \end{adjustbox}
-\caption{kNN model performance trained on all extracted features}
+\caption{KNN model performance trained on all extracted features}
 \label{tab:design:all-extracted-features}
@@
 Next, we exhaustively list all combinations of three features and look at the range of model performances generated.
-There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate kNN models for temporal domain features and 165 for the spectral domain.
+There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate KNN models for temporal domain features and 165 for the spectral domain.
 The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
-Accuracies of kNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-knn}.
+Accuracies of KNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-KNN}.
 
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-train.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
         \caption{Testing set}
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-3-features-combinations-test.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
         \caption{Training set}
     \end{subfigure}
-    \caption{Range of prediction accuracy in all kNN models with subset of 3 features. Subplots show three different predicted variables.}
-    \label{fig:design:feature-combinations-knn}
+    \caption{Range of prediction accuracy in all KNN models with subset of 3 features. Subplots show three different predicted variables.}
+    \label{fig:design:feature-combinations-KNN}
 \end{figure}
 
-Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-knn}.
+Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}.
 Worst accuracies occur for temporal features in multiclass classification 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
@@
 \caption{Features with the highest accuracies on the training set found combinatorically}
-\label{tab:design:feature-combinations-knn}
+\label{tab:design:feature-combinations-KNN}
 \end{table}
 
-The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-knn}.
-Their prediction accuracies in kNN models are subpar to optimal sets.
+The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}.
+Their prediction accuracies in KNN models are subpar to optimal sets.
 However, the advantage is that the feature election process is not so computationally taxing.
@@
 \centering
-\renewcommand{\arraystretch}{1.2}
 \begin{adjustbox}{width=\textwidth}
@@
 \end{adjustbox}
-\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated kNN accuracies.}
-\label{tab:design:best-3-features-knn}
+\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated KNN accuracies.}
+\label{tab:design:best-3-features-KNN}
 \end{table}
@@
 
-Model performance of kNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:knn-accuracy-batch}.
+Model performance of KNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
 Best combination of three features achieves always better than when the model is trained on all features.
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-train.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
         \caption{Testing set}
@@
     \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/kNN-feature-selection-predictions-test.png}
+        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
         \caption{Training set}
     \end{subfigure} 
-    \caption{Batch kNN algorithm prediction accuracy with various feature sets.}
-    \label{fig:design:knn-accuracy-batch}
+    \caption{Batch KNN algorithm prediction accuracy with various feature sets.}
+    \label{fig:design:KNN-accuracy-batch}
 \end{figure}
@@
 
-The kNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context.
+The KNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context.
 In this manner, we can compare the training accuracies in the last sample for both models.
-kNN is set to 5 nearest neighbors and proximity metric of Euclidian distance.
+KNN is set to 5 nearest neighbors and proximity metric of Euclidian distance.
 Online learning metrics are evaluated in progressive valuation on a dataset that is left unbalanced.

### 2023-12-28 thesis/chapters/04-implementation.tex
Fix machinery information and finish Resume

@@
 
-\section{Monitored machinery}
+\section{Machinery for monitoring}
 Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
@@
 
-\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}) and altogether two units are available in two independent air conditioning units for the data center.
+\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
+Altogether two units are available in two independent air conditioning units for the data center.
 The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
@@
 \textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
-The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor with a squirrel cage rotor.
+The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
 
-The newer primary pump with cloud monitoring solution is one unit of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
-The pump was commissioned in 2019 and it rotates at a speed of circa 1500 rpm (precisely 1493 rpm or 24.9 Hz).
-The electric motor in the vicinity has 400~kW of power (class~\rom{2}).
+The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
+The electric motor provides 400~kW of power (class~\rom{3}).
 Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.
 
-Secondary pumps are two units produced by \emph{Sigma} (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of 250~kW and 100~kW.
-Each pump and motor has 2 bearings therefore there are 4 measurement positions in total.
+The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
+It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW.
+Each pump and motor have 2 bearings.
+Therefore, there are 4 measurement positions in total.
 
-\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix \ref{appendix:data-collection}.
-In addition, we might be able to export the entire historical logs of the water pump from \textbf{KSB cloud} to enlarge the dataset.
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
+        \caption{Vibration rms velocity dashboard}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
+        \caption{Vibration spectral analysis dashboard}
+    \end{subfigure}
+     \caption{KSB Guard cloud monitoring for pumps}
+     \label{fig:design:ksb-guard}
+\end{figure}
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
-     \caption{KSB cloud pump monitoring after ramp-up with displayed warning and alert levels}
-\end{figure}
+\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
+In addition, we are able to export the entire historical record in hourly intervals.
+Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps  (Figure~\ref{fig:design:ksb-guard}).
 
@@
 The accelerometer driver is also made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
+Activity diagrams of required firmware functionality are in Appendix~\ref{appendix:technical-docs}.
 
@@
         \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
-		\caption{Orbital analysis of compressor's \nth{1} harmonic frequency}
+		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
 		\label{fig:design:orbital-analysis}
@@
         \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{FFT with Hann window of length $2^{10}$ ($\approx 409\;\mathrm{ms}$)}
+        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
         \label{fig:design:preliminary-spectrum}

### 2023-12-28 thesis/chapters/appendix/A-resume.tex
Fix machinery information and finish Resume

@@
 Existujú tri rôzne prístupy k údržbe strojov: reaktívny, preventívny a prediktívny.
-Pri reaktívnej údržbe beží stroj až do úplného zlyhania a je prijateľná vtedy, keď sú dovolené krátke prestoje, je možná úplná a rýchla výmena pokazeného stroja za záložný, alebo ohrozenie zapríčinené poruchou je zanedbateľné.
+Pri reaktívnej údržbe beží stroj až do úplného zlyhania a je prijateľná vtedy, keď je možná úplná a rýchla výmena pokazeného stroja za záložný.
 Preventívna údržba prebieha v pravidelných intervaloch odvodených od vopred určeného rozvrhu v alebo strednej doby medzi poruchami.
@@
 \section{Extrakcia a výber atribútov}
-%TODO Page 14
+Prediktívna údržba má ideálne predpoklady na využitie extrakcie atribútov, pretože signál je zvyčajne pseudostacionárny a trendové premenné v časovej a frekevnčnej oblasti vychádzajú z expertných znalostí v oblasti mechaniky.
+Výhody dodatočného úsilia v porovnaní so spracovaním pôvodných vzoriek spočívajú v dosahovaní lepšej presnosti klasifikácie, znížení výpočtovej záťaže a znížení potreby úložnej kapacity.
+Výber atribútov nie je samostatným krokom v procese strojového učenia, ale mal by sa vykonávať iteratívne na zlepšenie výsledného modelu.
+
+Najrozšírenejšími používanými atribútmi sú štatistické miery centrálneho momentu: priemer, rozptyl, štandardná odchýlka, šikmosť a špičatosť.
+Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička a maximum.
+Ostatné významné atribúty časovej oblasti sú odvodené ako pomery a sú nim: faktor výkyvu, faktor rozpätia, faktor impulzu a faktor tvaru.
+
+V spektrálnej oblasti môžeme získať obvyklé štatistické vlastnosti distribúcie, ktorými sú spektrálne ťažisko, šikmosť a špičatosť.
+Okrem toho sa extrahujú roll-on a roll-off, fundamentálna frekvencia, entropia, negentropia, vzájomná korelácia spektier, pomer signálu k šum, energia vo frekvenčných pásmach.
+
+Atribúty neprispievajú k prediktívnej sile modelu s rovnakým podielom.
+Výber ich optimálnej podmnožiny je NP-ťažký kombinatorický problém.
+Kroky všeobecného postup pri výbere atribútov metódou filtrovania sú generovanie podmnožín, vyhodnotenie podmnožín, ukončovacie kritérium hľadania, a validácia.
+
+Hodnotenie relevancie atribútov sú založené na skórovaní podobnosti s predikovanou premennou.
+Často používané spôsoby zoraďovania dôležitosti atribútov sú prah rozptylu, koeficienty korelácie, ANOVA F štatistika, a vzájomná informácia.
+Viaceré podmnožiny prediktorov produkovaných každou z výberových metrík môžu slúžiť na trénovanie viacerých variantov klasifikačného modelu.
+Množiny atribútov je možné kombinovať do súboru volebným systémom ako sú väčšinové hlasovanie alebo súčin poradí.
 
 \section{Diagnostické prístupy}
+Identifikácia porúch v rotujúcich strojoch je binárny alebo viactriedny klasifikačný problém, ktorý pracuje na princípe učenia čiastočne s učiteľom, pretože označenia pre degradované stavy stroja sú v praxi zriedkavé.
+Ciele automatizácie monitorovania možno rozdeliť na detekciu anomálií a rozpoznanie typu poruchy.
+
+Detekcia anomálií, novostí alebo odľahlých hodnôt určuje, či sa prevádzkový stav stroja výrazne odchyľuje od normálu.
+Po upozornení môže zasiahnuť odborník a stroj diagnostikovať.
+Odľahlé hodnoty sú odvodzované na základe neparametrických štatistických modelov, zhlukovania podľa najbližších susedov a prístupov založených na izolácii anomálnych vzoriek.
+DenStream je algoritmus zhlukovania založený na hustote prispôsobený z DBSCAN na zhlukovanie prúdových dát do ľubovoľne tvarovaných skupín.
+Half-space strom predpokladá, že náhodné delenie v každej osi v priestore atribútov izoluje odľahlé hodnoty do samostatných oddielov skôr ako nedeviantné pozorovania.
+
+Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
+ALgoritmus k-najbližších susedov (KNN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
+Nachádza uplatnenie aj v učení čiastočne s učiteľom, pretože dokáže odvodiť označenia len zo znalosti niekoľkých anotácií.
+
+Ďalším prístupom je online alebo postupné učenie, ktoré aktualizuje parametre modelu s každou novou prichádzajúcou udalosťou.
+Tento prístup je užitočný pri spracovaní veľkých dát, kedy celý súbor údajov nie je k dispozícii vopred alebo ho nemožno spracovať naraz z dôvodu pamäťových obmedzení.
 
 \section{Výskumné otázky}
+Cieľom tejto práce je poskytnúť odpovede na štyri výskumné otázky:
+\begin{enumerate}
+\itemsep0pt
+\item Aké atribúty dokážeme extrahovať z vibračných signálov?
+\item Akú úsporu dát dosiahneme výberom atribútov?
+\item Aké budú presnosti diagnostiky porúch s rôznymi sadami atribútov?
+\item Ako môžeme priebežne označovať poruchové stavy?
+\end{enumerate}
 
 \section{Návrh metód s MaFaulDa}
+Súbor údajov MaFaulDa používame ako smerodajný pri určovaní metód schopných nasadenia na senzorovú jednotku.
+MaFaulda obsahuje 1951 záznamov so vzorkovaciu frekvenciu 50 kHz a označenými simulovanými poruchami rôznej závažnosti.
+Nahrávky obsahujú časové rady z dvoch trojosích piezoelektrických akcelerometrov.
+Po úprave ponechávame 6 typov značiek: referenčný bezporuchový stav, dve poruchy hriadeľa (nevyváženosť, nesúososť) a tri poruchy ložísk (poruhy klietky, guľôčok, vonkajšieho krúžku).
+
+Zo signálov rozdeleních na pät jednosekundových častí sa odstraňuje jednosmerná zložka odčítaním priemernej akcelerácie, po ktorej nasleduje dolnopriepustný 10 kHz filter.
+Z častí signálu je potom vytvorených 10 časových a 11 spektrálnych premenných.
+Euklidovská norma trojrozmerných atribútov eliminuje závislosť na smere merania.
+Pri výbere atribútov nie je do množiny pridaná taká dvojica, ak ich absolútna hodnota korelácie presahuje 0.95.
+
+Predpokladáme, že dátové body rozprestrené v každej dimenzii priestoru môžu dobre rozlíšiť skupiny.
+Ukazuje sa, že premenné sú navzájom vica korelované v časovej doméne ako ilustuje analýza hlavných komponentov.
+Pre 95\% vysvetleného rozptylu PCA sú v časovej doméne potrebné 3 zložky, zatiaľ čo vo frekvenčnej doméne 4 zložky.
+PCA efektívne vyjadruje atribúty v menej rozmernom priestore, ale ich výslednou lineárnou kombináciou sa ťažko odvôvodňujú rozhodnutia modelu.
+
+Pri posudzovaní všeobecne najdôležitejších atribútov vychádzame z trojíc nekorelovaných atribútov vytvorených v 24 scenároch.
+Podmienky scenárov vznikli kombináciou štyroch kritérií: dávkové alebo inkrementálne učenie, pozícia ložiska, predikovaná premenná, limit na rotačnú rýchlosť.
+Na základe schvalovacieho hlasovania sú najčastejšie sa vyskytujúcimi atribútmi v časovej doméne: špička-špička, faktor tvaru, faktor výkyvu.
+Vo frekvenčnej doméne sú to spektrálne ťažisko, roll-on a roll-off.
+
+Tri typy experimentov s modelom KNN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
+Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovacou presnosťou.
+Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov.
+Dávkový model KNN slúži ako referenčný, podľa ktorého sa posudzuje KNN v postupnom učení.
+
+Online učenie napodobňuje sťažené podmienky diagnostiky strojov, ktoré sa objavujú v praxi.
+Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie.
+Modely KNN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A a nad všetkými extrahovanými atribútami.
+Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie.
+KNN sma nastavili na 5 susedov a euklidovskú vzdialenosť.
+Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocanie na ešte nevyváženom súbore údajov.
 
 \section{Zber vibrácií v priemysle}
+Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia.
+Pri monitorovaní zúžitkujeme mierne prispôsobený postup z noriem.
+Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.
+Zber nového súboru údajov sprevádza vopred dohodnutý harmonogram.
+
+Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čepadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
+Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
+Ako senzor vibrácii použijeme MEMS akcelerometer IIS3DWB.
+Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
 
 \section{Záver}
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhalovanie porúch z vibračných signálov.
+Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.
+
+Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
+Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť KNN modelu oproti metrikám samostatne.
+Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%.
+Trénovanie KNN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
+
+Model postupného učenia kNN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% oanotovaného súboru údajov.
+Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.
+Doteraz boli urobené závery podľa súboru údajov MaFaulDa, ktoré plánujeme overiť na súbore údajov získaných v priemysle počas DP3.
 

### 2023-12-28 thesis/chapters/appendix/C-technical-documentation.tex
Fix machinery information and finish Resume

\thispagestyle{empty}
\chapter{Technical documentation} \label{appendix:technical-docs}
\pagenumbering{arabic}
\renewcommand*{\thepage}{C-\arabic{page}}

\section{Data collection plan}

The vibration measurements will occur monthly for pumps and biweekly for compressors from February 2024 until May 2024.
\begin{table}[ht]
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{|l|l|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|}
\hline
\textbf{Machine}                                                                      & \textbf{Placement \textbackslash Month} & \multicolumn{2}{p{1.2cm}|}{\textbf{02/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{03/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{04/2024}} \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#3\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &        \\ \cline{2-8} 
                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#5\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\multirow{6}{*}{\textbf{Pump Sigma}}                                                  & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 
                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
\end{tabular}
\end{table}
Each measurement will involve 3 trials for each position. The sensor is mounted to the machine with adhesive on double-sided carpet tape (placement notation follows MIMOSA convention from ISO~13373-1). After every trial, the sensor will be detached and attached again.

The plan was consulted and approved by the machinery owners: VNET~a.s. and Bratislavská vodárenská spoločnosť,~a.s. Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution. Total space requirements for 108 recordings are 990 MiB.

\section{Firmware activities}

Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

\begin{itemize}
\itemsep0pt
\item begin new recording, 
\item log block of samples into CSV file,
\item finish recording.
\end{itemize}

\begin{figure}[h]
    \centering
	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
\end{figure}

### 2023-12-28 thesis/chapters/appendix/E-digital-medium.tex
Fix machinery information and finish Resume

\thispagestyle{empty}
\setcounter{figure}{0}
\chapter{Contents of the digital medium}
\pagenumbering{arabic}
\renewcommand*{\thepage}{E-\arabic{page}}
\par Evidenčné číslo práce v informačnom systéme: \RegNo
\par Obsah digitálnej časti práce (archív ZIP):
\par Názov odovzdaného archívu:

### 2023-12-28 thesis/chapters/appendix/A-resume.tex
Fix spelling in resume

@@
 \section{Úvod}
-Vzostup priemyslu 4.0 prináša so sebou väčšiu mieru automatizácie s cieľom dosiahnuť optimálne využitie dostupných zdrojov.
+Vzostup priemyslu 4.0 so sebou prináša väčšiu mieru automatizácie s cieľom dosiahnuť optimálne využitie dostupných zdrojov.
 Na základe nepretržitého sledovania opotrebenia zariadení v reálnom čase sa majú zabezpečiť nápravné opatrenia na opravu alebo výmenu súčiastok včas, v reakcii na trendové ukazovatele.
@@
 Preventívna údržba prebieha v pravidelných intervaloch odvodených od vopred určeného rozvrhu v alebo strednej doby medzi poruchami.
-Prediktívna údržba zlepšuje predvídateľnosť oproti reaktívnej údržbe a eliminuje plytvanie voči prílš obozretnej prevencii.
+Prediktívna údržba zlepšuje predvídateľnosť oproti reaktívnej údržbe a eliminuje plytvanie voči príliš obozretnej prevencii.
 Odstávka stroja je naplánovaná po zistení kritických hodnôt a po odhalení problematických komponentov.
@@
 Vibroakustická diagnostika sa preto považuje za jednu z najdôležitejších metód pri včasnej identifikácii porúch komponentov.
-Najbežnejšie sa vyskytujúcimi poruchami sú nevyváženosť, nesúososť, vôla, excentricita, deformácia, trhlina a nadmerné trenie.
+Najbežnejšie sa vyskytujúcimi poruchami sú nevyváženosť, nesúososť, vôľa, excentricita, deformácia, trhlina a nadmerné trenie.
 
 Symptómy porúch rotačných strojov sa prejavujú rôznymi frekvenčnými pásmami, ale väčšina je závislá od rotačnej rýchlosti súčiastky.
-Nevyváženosť, nevyváženosť a vôla sa bežne objavujú v frekvenciách do 300 Hz.
+Nevyváženosť, nevyváženosť a vôľa sa bežne objavujú v frekvenciách do 300 Hz.
 Poruchy ložísk a prevodovky v neskorých štádiách vývoja sa prejavujú v rozsahu medzi 300 Hz a 1 kHz.
-Vyššie frekvencie do 10 kHz pomáhajú odhaliť poruchy ložísk v skorších štádiach rozvoja.
+Vyššie frekvencie do 10 kHz pomáhajú odhaliť poruchy ložísk v skorších štádiách rozvoja.
 
@@
 \section{Extrakcia a výber atribútov}
-Prediktívna údržba má ideálne predpoklady na využitie extrakcie atribútov, pretože signál je zvyčajne pseudostacionárny a trendové premenné v časovej a frekevnčnej oblasti vychádzajú z expertných znalostí v oblasti mechaniky.
+Prediktívna údržba má ideálne predpoklady na využitie extrakcie atribútov, pretože signál je zvyčajne stacionárny a trendové premenné v časovej a frekvenčnej oblasti vychádzajú z expertných znalostí v oblasti mechaniky.
 Výhody dodatočného úsilia v porovnaní so spracovaním pôvodných vzoriek spočívajú v dosahovaní lepšej presnosti klasifikácie, znížení výpočtovej záťaže a znížení potreby úložnej kapacity.
@@
 
-Najrozšírenejšími používanými atribútmi sú štatistické miery centrálneho momentu: priemer, rozptyl, štandardná odchýlka, šikmosť a špičatosť.
+Najrozšírenejšími používanými atribútmi sú štatistické miery centrálneho momentu: priemer, rozptyl, štandardná odchýlka, šikmosť a špicatosť.
 Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička a maximum.
@@
 
-V spektrálnej oblasti môžeme získať obvyklé štatistické vlastnosti distribúcie, ktorými sú spektrálne ťažisko, šikmosť a špičatosť.
+V spektrálnej oblasti môžeme získať obvyklé štatistické vlastnosti distribúcie, ktorými sú spektrálne ťažisko, šikmosť a špicatosť.
 Okrem toho sa extrahujú roll-on a roll-off, fundamentálna frekvencia, entropia, negentropia, vzájomná korelácia spektier, pomer signálu k šum, energia vo frekvenčných pásmach.
@@
 Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
-ALgoritmus k-najbližších susedov (KNN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
+Algoritmus k-najbližších susedov (KNN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
 Nachádza uplatnenie aj v učení čiastočne s učiteľom, pretože dokáže odvodiť označenia len zo znalosti niekoľkých anotácií.
@@
 Nahrávky obsahujú časové rady z dvoch trojosích piezoelektrických akcelerometrov.
-Po úprave ponechávame 6 typov značiek: referenčný bezporuchový stav, dve poruchy hriadeľa (nevyváženosť, nesúososť) a tri poruchy ložísk (poruhy klietky, guľôčok, vonkajšieho krúžku).
+Po úprave ponechávame 6 typov značiek: referenčný bezporuchový stav, dve poruchy hriadeľa (nevyváženosť, nesúososť) a tri poruchy ložísk (poruchy klietky, guľôčok, vonkajšieho krúžku).
 
-Zo signálov rozdeleních na pät jednosekundových častí sa odstraňuje jednosmerná zložka odčítaním priemernej akcelerácie, po ktorej nasleduje dolnopriepustný 10 kHz filter.
+Zo signálov rozdeleních na päť jednosekundových častí sa odstraňuje jednosmerná zložka odčítaním priemernej akcelerácie, po ktorej nasleduje dolnopriepustný 10 kHz filter.
 Z častí signálu je potom vytvorených 10 časových a 11 spektrálnych premenných.
@@
 
-Predpokladáme, že dátové body rozprestrené v každej dimenzii priestoru môžu dobre rozlíšiť skupiny.
-Ukazuje sa, že premenné sú navzájom vica korelované v časovej doméne ako ilustuje analýza hlavných komponentov.
+Predpokladáme, že dátové body rozprestreté v každej dimenzii priestoru môžu dobre rozlíšiť skupiny.
+Ukazuje sa, že premenné sú navzájom viac korelované v časovej doméne ako ilustruje analýza hlavných komponentov.
 Pre 95\% vysvetleného rozptylu PCA sú v časovej doméne potrebné 3 zložky, zatiaľ čo vo frekvenčnej doméne 4 zložky.
-PCA efektívne vyjadruje atribúty v menej rozmernom priestore, ale ich výslednou lineárnou kombináciou sa ťažko odvôvodňujú rozhodnutia modelu.
+PCA efektívne vyjadruje atribúty v menej rozmernom priestore, ale ich výslednou lineárnou kombináciou sa ťažko odôvodňujú rozhodnutia modelu.
 
@@
 Podmienky scenárov vznikli kombináciou štyroch kritérií: dávkové alebo inkrementálne učenie, pozícia ložiska, predikovaná premenná, limit na rotačnú rýchlosť.
-Na základe schvalovacieho hlasovania sú najčastejšie sa vyskytujúcimi atribútmi v časovej doméne: špička-špička, faktor tvaru, faktor výkyvu.
+Na základe schvaľovacieho hlasovania sú najčastejšie sa vyskytujúcimi atribútmi v časovej doméne: špička-špička, faktor tvaru, faktor výkyvu.
 Vo frekvenčnej doméne sú to spektrálne ťažisko, roll-on a roll-off.
@@
 Tri typy experimentov s modelom KNN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
-Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovacou presnosťou.
+Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou.
 Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov.
@@
 Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie.
-Modely KNN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A a nad všetkými extrahovanými atribútami.
+Modely KNN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi.
 Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie.
-KNN sma nastavili na 5 susedov a euklidovskú vzdialenosť.
-Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocanie na ešte nevyváženom súbore údajov.
+KNN sme nastavili na 5 susedov a euklidovskú vzdialenosť.
+Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.
 
@@
 Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia.
-Pri monitorovaní zúžitkujeme mierne prispôsobený postup z noriem.
+Pri monitorovaní zužitkujeme mierne prispôsobený postup z noriem.
 Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.
@@
 
-Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čepadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
+Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
 Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
@@
 \section{Záver}
-V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhalovanie porúch z vibračných signálov.
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
 Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.
@@
 
-Model postupného učenia kNN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% oanotovaného súboru údajov.
+Model postupného učenia kNN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
 Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.

### 2023-12-28 thesis/chapters/appendix/B-plan-of-work.tex
Move machinery and sensors to implementation and resume background
Fix spelling in resume

@@
 \thispagestyle{empty}
-\chapter{Plan of work}
+\chapter{Work plan}
 \pagenumbering{arabic}
@@
  \\ \hline
-  \nth{12} - \nth{13} week         &  Write up design chapter: research questions, visualization export. Finish writing design chapter.
+  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
  \\ \hline
@@
 
-In reality, these tasks switched order because, between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study.
-Only then from \nth{4} to \nth{11} week, main focus was on experiments with the MaFaulDa.
+In reality, these tasks switched order because between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study.
+Only then from \nth{4} to \nth{11} week the main focus was on experiments with the MaFaulDa.
 
-Lastly, preliminary measurements were conducted, as was the plan. Requirements were presented for the new sensor device, and a chapter about design was written.
+Lastly, preliminary measurements were conducted, as was the plan. Requirements were presented for the new sensor device and its firmware.
 \clearpage

### 2023-12-31 thesis/chapters/02-analysis-C-diagnostics.tex
Setup firware project and gather pre-made examples

@@
 
-\textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:knn}).
+\textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
 It means it can work in the semi-supervised environment because it can infer labels just from knowing a few annotations.
-The major drawback of kNN is a preference for the majority class in imbalanced class sizes datasets~\cite{shi_improving_2020}.
+The major drawback of KNN is a preference for the majority class in imbalanced class sizes datasets~\cite{shi_improving_2020}.
 The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
-kNN algorithm requires features to be normalized to assign the same importance to each predictor.
+KNN algorithm requires features to be normalized to assign the same importance to each predictor.
 
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/analysis/kNN.png}
-        \caption{kNN with k = 5}
-        \label{fig:knn}
+        \includegraphics[width=\textwidth]{assets/analysis/KNN.png}
+        \caption{KNN with k = 5}
+        \label{fig:KNN}
     \end{subfigure}
@@
 The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
-(Tab.~\ref{tab:knn-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
+(Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
 The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
@@
 \end{tabular}
-\caption{Distance metrics for kNN}
-\label{tab:knn-distance}
+\caption{Distance metrics for KNN}
+\label{tab:KNN-distance}
 \end{table}
@@
 Nearest-neighbour classifier has been successfully applied in machinery fault diagnostics.
-On the CWRU bearing dataset, the kNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - kNN 91.2\%, SVM 88.8\%, and frequency domain features - kNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
+On the CWRU bearing dataset, the KNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - KNN 91.2\%, SVM 88.8\%, and frequency domain features - KNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
 
-Comparison of kNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
+Comparison of KNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
 Best accuracies were reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric.
 The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
-Despite kNN lagging in accuracy, we have to keep in mind annotations for faults were complete and machine learning was not tested in a streaming context.
+Despite KNN lagging in accuracy, we have to keep in mind annotations for faults were complete and machine learning was not tested in a streaming context.
 

### 2023-12-31 recorder/examples/iis3dwb-pid/examples/iis3dwb_fifo.c

@@ -1,0 +1,319 @@
+/*
+ ******************************************************************************
+ * @file    fifo.c
+ * @author  Sensors Software Solution Team
+ * @brief   This file how to configure compressed FIFO and to retrieve acc
+ *          data. This sample use a fifo utility library tool
+ *          for FIFO decompression.
+ *
+ ******************************************************************************
+ * @attention
+ *
+ * <h2><center>&copy; Copyright (c) 2020 STMicroelectronics.
+ * All rights reserved.</center></h2>
+ *
+ * This software component is licensed by ST under BSD 3-Clause license,
+ * the "License"; You may not use this file except in compliance with the
+ * License. You may obtain a copy of the License at:
+ *                        opensource.org/licenses/BSD-3-Clause
+ *
+ ******************************************************************************
+ */
+
+/*
+ * This example was developed using the following STMicroelectronics
+ * evaluation boards:
+ *
+ * - STEVAL_MKI109V3 + STEVAL-MKI208V1K
+ *
+ * Used interfaces:
+ *
+ * STEVAL_MKI109V3    - Host side:   USB (Virtual COM)
+ *                    - Sensor side: SPI(Default) / I2C(supported)
+ *
+ * If you need to run this example on a different hardware platform a
+ * modification of the functions: `platform_write`, `platform_read`,
+ * `tx_com` and 'platform_init' is required.
+ *
+ */
+
+/* STMicroelectronics evaluation boards definition
+ *
+ * Please uncomment ONLY the evaluation boards in use.
+ * If a different hardware is used please comment all
+ * following target board and redefine yours.
+ */
+
+//#define STEVAL_MKI109V3  /* little endian */
+
+/* ATTENTION: By default the driver is little endian. If you need switch
+ *            to big endian please see "Endianness definitions" in the
+ *            header file of the driver (_reg.h).
+ */
+
+#if defined(STEVAL_MKI109V3)
[…]

### 2023-12-31 recorder/examples/iis3dwb-pid/examples/iis3dwb_read_data_polling.c

@@ -1,0 +1,296 @@
+/*
+ ******************************************************************************
+ * @file    read_data_polling.c
+ * @author  Sensors Software Solution Team
+ * @brief   This file show the simplest way to get data from sensor.
+ *
+ ******************************************************************************
+ * @attention
+ *
+ * <h2><center>&copy; Copyright (c) 2020 STMicroelectronics.
+ * All rights reserved.</center></h2>
+ *
+ * This software component is licensed by ST under BSD 3-Clause license,
+ * the "License"; You may not use this file except in compliance with the
+ * License. You may obtain a copy of the License at:
+ *                        opensource.org/licenses/BSD-3-Clause
+ *
+ ******************************************************************************
+ */
+
+/*
+ * This example was developed using the following STMicroelectronics
+ * evaluation boards:
+ *
+ * - STEVAL_MKI109V3 + STEVAL-MKI208V1K
+ * - DISCOVERY_SPC584B + STEVAL-MKI208V1K
+ *
+ * and STM32CubeMX tool with STM32CubeF4 MCU Package
+ *
+ * Used interfaces:
+ *
+ * STEVAL_MKI109V3    - Host side:   USB (Virtual COM)
+ *                    - Sensor side: SPI(Default) / I2C(supported)
+ *
+ * DISCOVERY_SPC584B  - Host side: UART(COM) to USB bridge
+ *                    - Sensor side: I2C(Default) / SPI(supported)
+ *
+ *
+ * If you need to run this example on a different hardware platform a
+ * modification of the functions: `platform_write`, `platform_read`,
+ * `tx_com` and 'platform_init' is required.
+ *
+ */
+
+/* STMicroelectronics evaluation boards definition
+ *
+ * Please uncomment ONLY the evaluation boards in use.
+ * If a different hardware is used please comment all
+ * following target board and redefine yours.
+ */
+
+//#define STEVAL_MKI109V3  /* little endian */
+//#define SPC584B_DIS      /* big endian */
+
+/* ATTENTION: By default the driver is little endian. If you need switch
[…]

### 2023-12-31 recorder/firmware/main/main.c

@@ -1,0 +1,297 @@
+#include <stdio.h>
+#include <string.h>
+#include <sys/unistd.h>
+#include <sys/stat.h>
+#include <dirent.h>
+#include "esp_vfs_fat.h"
+#include "sdmmc_cmd.h"
+#include "driver/sdmmc_host.h"
+
+#include "hal/gpio_types.h"
+#include "driver/spi_master.h"
+#include "driver/gpio.h"
+#include "iis3dwb_reg.h"
+
+
+#define MAX_FILENAME            256
+#define MOUNT_POINT             "/sd"
+#define LOG_FOLDER              MOUNT_POINT"/acc"
+
+#define CARD_CLK_PIN    14
+#define CARD_CMD_PIN    15
+#define CARD_D0_PIN     2
+
+
+// Max fifo watermark is 511
+#define SENSOR_MISO         16
+#define SENSOR_MOSI         32
+#define SENSOR_CLK          33
+#define SENSOR_CS           13
+#define SENSOR_INT1         35
+#define SPI_BUS_FREQUENCY   SPI_MASTER_FREQ_8M
+#define FIFO_WATERMARK      256
+static spi_host_device_t    SPI_BUS = SPI2_HOST;
+static iis3dwb_fifo_out_raw_t fifo_data[FIFO_WATERMARK];
+
+
+sdmmc_card_t *storage_enable(const char *mount_point)
+{
+    esp_vfs_fat_sdmmc_mount_config_t mount_config = {
+        .format_if_mount_failed = true,     // Set to false
+        .max_files = 5,                     // Maximum number of opened files
+        .allocation_unit_size = 16 * 1024   // Useful only for format
+    };
+
+    sdmmc_slot_config_t slot_config = SDMMC_SLOT_CONFIG_DEFAULT();
+    slot_config.width = 1;
+    slot_config.clk = CARD_CLK_PIN;
+    slot_config.cmd = CARD_CMD_PIN;
+    slot_config.d0 = CARD_D0_PIN;
+
+    sdmmc_card_t *card;
+    sdmmc_host_t host = SDMMC_HOST_DEFAULT();
+    esp_err_t ret = esp_vfs_fat_sdmmc_mount(mount_point, &host, &slot_config, &mount_config, &card);
+
+    if (ret != ESP_OK) {
+        if (ret == ESP_FAIL) {
+            // Failed to mount filesystem
+        } else {
+            // Failed to initialize the card
+        }
+        return NULL;
[…]

### 2024-01-01 thesis/chapters/01-introduction.tex
Fix grammar

@@
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
-The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear.
-The corrective action be it repair or replacement should be done on time in response to the key indicators.
+The secondary aspect in the enterprises' endeavor, but not less important, is to keep track of the equipment's wear and tear.
+The corrective action, be it repair or replacement, should be done on time in response to the key indicators.
 
@@
 
-Vibrations are non-intrusive way to sense and record eventually fatal deficiencies right at the onset.
+Vibrations are a non-intrusive way to sense and record eventually fatal deficiencies right at the onset.
 The experts use it to distinguish faulty states and to identify the malfunction's root causes.
-In critical circumstances such as is the case of the large turbines in the power plants, the precautions leading to regular machinery check-ups are already in place.
-The monitoring solution has to be sufficiently independent, reliable, and accurate to reach wider acceptance and spread.
+In critical circumstances such as is the case of the large turbines in power plants, the precautions leading to regular machinery check-ups are already in place.
+The monitoring solution has to be sufficiently independent, reliable, and accurate to achieve wider acceptance and spread.
 
@@
 The majority of signals are viewed once at the maximum.
-Therefore to store or even transmit them from the edge device in its entirety would be wasteful.
+Therefore, to store or even transmit them from the edge device in its entirety would be wasteful.
 The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan powered out of the battery pack.
@@
 The model has to be trained for the target environment to achieve the ideal performance.
-In addition, the failures are relatively rare events that usually occur several months apart.
+In addition, failures are relatively rare events that usually occur several months apart.
 In these circumstances, it is hard to quickly obtain a large enough sample of fault events.
@@
 In the section about classification models, we compare the performance for various feature sets in the k-nearest neighbors algorithm.
-Finally, in preparation for the evaluation part, the sensor device is propresed which is suitable for measurements of designated machines in the industrial environment.
+Finally, in preparation for the evaluation part, the sensor device is proprosed which is suitable for measurement of designated machines in the industrial environment.

### 2024-01-01 thesis/chapters/02-analysis-A-CdM.tex
Fix grammar

@@
 The defect needs to be repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or any endangerment of the responsible personnel.
-The maintenance strategies are chosen according to the machine's importance as a result of its failure effect evaluation on the system.
+The maintenance strategies are chosen according to the machine's importance as a result of potential failure's impact on the system.
 The guide to set appropriate maintenance procedures as outlined in the IEC~60706-2 standard, and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
@@
 The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
-In certain situations, it suffices to utilize a simpler maintenance program, but the predictive maintenance gains attraction in the Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.
+In certain situations, it suffices to utilize a simpler maintenance program, but predictive maintenance gains attraction in Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.
 
@@
 It requires a large stock of replacement parts on-site and breakage inflicts a ``crisis management mode'' upon the plant \cite{scheffer_practical_2004}.
-On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment on failure~\cite{ziaran_technicka_2013}.
+On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment from failure~\cite{ziaran_technicka_2013}.
 
@@
 Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure).
-The schedule is crucial but can result in components being replaced in good condition creating waste.
+The schedule is crucial but can result in components being replaced in good condition, creating waste.
 The parts can occasionally stay in operation too long, and the machine breaks as a result.
-Conservative planning is usually the norm to keep the machine always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
+Conservative planning is usually the norm to keep the machines always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
 
-\textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates the waste in overall resource utilization of cautious prevention.
+\textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates waste in overall resource utilization of cautious prevention.
 The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and the identification of troublesome components.
 
-A measurable decrease in effectivity allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
-The misdetection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
+A measurable decrease in effectiveness allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
+The missed detection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
 
@@
 Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval~\cite{bousdekis_enterprise_2021}.
-These division points are not exactly set but have statistical distribution to them.
+These division points are not exactly set but have a statistical distribution to them.
 
@@
 
-A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded but also in the early stages soon after assembly.
+A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded, but also in the early stages soon after assembly.
 Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes.
@@
 Mechanical problems during machinery operation bring about vibrations in many instances.
-Therefore vibroacoustic diagnostics is considered as one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
+Therefore, vibroacoustic diagnostics is considered as one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
 
@@
 
-One of the methods vibration experts utilize in the identification of the damaged part from the frequency spectrum is \textbf{order analysis}.
+One of the methods vibration experts utilize in the identification of the damaged part, according to the frequency spectrum, is \textbf{order analysis}.
 The excessive peaks at harmonic frequencies are of interest.
@@
 
-The vibration severity is the maximum of magnitudes measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft in the axial axis.
+The vibration severity is the maximum magnitude measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft on the axial axis.
 Multiple measurement locations, i.e.
@@
 Criteria introduced to judge vibration severity are absolute vibration magnitude, change in the magnitude vector, and rate of change.
-In terms of maximal magnitudes, the machines of varied sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
+In terms of maximal magnitudes, the machines of varying sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
 The values in this table serve as guidelines towards realistic requirements between machine manufacturers and their customers.
@@
 
-\emph{Zone A} is reserved for newly commissioned machines.
-\emph{Zone B} signifies suitability for long-term operation.
-In \emph{zone C} the machine is deemed in unsatisfactory condition and corrective action should be taken soon.
-Finally, in \emph{zone D} vibrations can cause damage to the machine.
-The span of acceptable values differs with the machine class from I through to IV and their output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.
+Zone A is reserved for newly commissioned machines.
+Zone B signifies suitability for long-term operation.
+In zone C the machine is deemed in unsatisfactory condition and corrective action should be taken soon.
+Finally, in zone D vibrations can cause damage to the machine.
+The span of acceptable values differs with the machine class from \rom{1} through to \rom{4} and their output power of 15~kW (class~\rom{1}), 75~kW (class~\rom{2}), 10~MW (class~\rom{3}), or greater.
 
@@
 Trips in between zones C and D urge immediate action or machine shut down.
-Both limits should not exceed 1.25 times the upper boundary of lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
+Both limits should not exceed 1.25 times the upper boundary of the lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
 
-\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in termos of the vocabulary in ISO 20186.
+\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in terms of the vocabulary in ISO 20186.
 According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval.
 Both designs can be permanently mounted.
-In continuous collection it is recommended to have ``multiplexing rate sufficiently rapid so there is no significant data or trends lost''~\cite{noauthor_iso_2002}.
-When channels are scanned successively with gaps between data points the system is known as ``scanning''.
+In continuous collection, it is recommended to have a ``multiplexing rate sufficiently rapid, so there is no significant data or trends lost''~\cite{noauthor_iso_2002}.
+When channels are scanned in succession with gaps between data points, the system is known as ``scanning''.
 
-The condition monitoring program is run according to a flowchart adapted from one designed in the standard specifically to best benefit the plant.
+The condition monitoring program is run according to a flowchart adapted from one designed by the standard specifically to best benefit the plant.
 Those steps can be summarized as follows~\cite{noauthor_iso_2002}:
+
 \begin{enumerate}
@@
 \item Review machinery history and establish failure modes.
-\item When vibration monitoring is not applicable check for other condition-monitoring techniques or resort to preventive maintenance.
+\item When vibration monitoring is not applicable, check for other condition-monitoring techniques or resort to preventive maintenance.
 \item Select monitoring points and take preliminary vibration measurements.
@@
 In case a new baseline is needed, continue in the step of taking baseline measurements.
-\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm trigger.
+\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm is triggered.
 \end{enumerate}
@@
 The machine description includes its identifier and type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
-Measurement parameters are to be recorded alongside the measurement value itself such as timestamp, transducer type, sensor location and orientation in \textbf{MIMOSA convention} (Machinery Information Mangement Open System Alliance), measurement units and units qualifier (p-p, RMS), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
+Measurement parameters are to be recorded alongside the measurement value itself, such as timestamp, transducer type, sensor location and orientation in \textbf{MIMOSA convention} (Machinery Information Management Open System Alliance), measurement units and units qualifier (p-p, rms), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
 
-The transducer of choice for condition monitoring is the accelerometer which can provide the acceleration value of the body and velocity after signal integration.
+The transducer of choice for condition monitoring is the accelerometer, which can provide the acceleration value of the body and velocity after signal integration.
 However, standard advise against double integrating for displacement.
 The recommended frequency range for an accelerometer is 0.1~Hz to 30~kHz.
-The choice of transducer mount significantly lowers its resonance frequency which is least influenced by stud mount and stiff cement mount.
+The choice of transducer mount significantly lowers its resonance frequency, which is least influenced by the stud mount and stiff cement mount.
 The resonance is reduced to around 8~kHz with the use of soft epoxy or permanent magnet.
@@
 Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s.
-Bearings and gears diagnosis may push the upper-frequency limit even higher.
+Bearings and gear diagnosis may push the upper-frequency limit even higher.
 The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$~(Fig.~\ref{fig:tranducer-response}).
@@
 The vibration baseline is defined by broad-band magnitudes and phases of motion vectors, the waveform in the time and frequency domain, the rotational speed of the machine as well as its frequency response to different speeds during start-up and coast-down captured in the Bode plot and waterfall plot.
-Changes during the machine operation are then depicted in value trends.
-Trends can be shown of overall amplitudes or limited to frequency bands.
+Changes during the machine's operation are then depicted in value trends.
+Trends can be shown by overall amplitudes or limited to frequency bands.

### 2024-01-01 thesis/chapters/02-analysis-B-features.tex
Fix grammar

@@
 In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset as a result of slight miscalibration, and bias originating from a constant force of gravity.
-These unavoidable distortions are to some extent suppressible with digital filters.
-In the preprocessing stage, we consider detrending, noise reduction with adaptive filters, and time synchronous averaging to eliminate the external interference.
+These unavoidable distortions are to some extent suppressable by digital filters.
+In the preprocessing stage, we consider trend removal, noise reduction with adaptive filters, and time synchronous averaging to eliminate external interference.
 
@@
 The constant offset is eliminated simply by subtracting the overall mean from the signal.
-Moreover high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time (Equation~\ref{equ:iir-dc-blocker}).
+Moreover, the high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time (Equation~\ref{equ:iir-dc-blocker}).
 The transition band depends upon the choice of corner frequency $f_{3dB}$ (Fig.~\ref{fig:dc-blocker}).
@@
 \section{Feature extraction} \label{section:feature-extraction}
-After preprocessing raw numerical vectors are merely low-level descriptors of the underlying physical phenomena.
+After preprocessing, raw numerical vectors are merely low-level descriptors of the underlying physical phenomena.
 At first, these incomprehensible sequences of numbers are reduced to summary attributes called features in the process of feature extraction or feature discovery.
@@
 Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
-The advantages of add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
+The advantages of the add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
 
-It is important to note that the design of features is not a standalone step in the machine learning pipeline but it should be performed iteratively to improve the target model.
+It is important to note that the design of features is not a standalone step in the machine learning pipeline, but it should be done iteratively to improve the target model.
 Signal features are computed in the temporal and spectral domain~\cite{brito_fault_2021}.
@@
 The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
-Statistics can be calculated in any domain, but the mean value should not to be used in detrended data.
+Statistics can be calculated in any domain, but the mean value should not be used in detrended data.
 The vibration severity metrics out of technical standards are also highly regarded.
-The characteristics of amplitude include root mean square, peak-to-peak distance, and maximum~\cite{mostafavi_novel_2021}.
+The characteristics of amplitude include root-mean-square, peak-to-peak distance, and maximum~\cite{mostafavi_novel_2021}.
 
@@
 These ratios are crest factor, margin factor, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
-Many articles have been successful in bearing fault detection out of transients in impulsive signals with kurtosis, crest factor, and margin indicators \cite{brito_fault_2021}.
+Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest factor, and margin indicators \cite{brito_fault_2021}.
 It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.
@@
 
-In the spectral domain, we can obtain usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
-Additionaly spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal to noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
+In the spectral domain, we can obtain the usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
+Additionally, spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal-to-noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
 
@@
 Complementary, the roll-on frequency is chosen so that 5\% of the signal energy is below this value.
-According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra, a value of one means spectra are the most dissimilar.
+According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra a value of one means the spectra are the most dissimilar.
 
@@
 
-If a single principal frequency exists, it can be determined with maximum likelihood estimation.
+If a single principal frequency exists, it can be determined by maximum likelihood estimation.
 Such frequency would explain the signal spectrum the best~\cite{peeters_large_2004}.
@@
 The essential peak-finding approaches are based either on magnitude or gradient.
-All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence.
-In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
-The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
+All found extrema are commonly filtered with the magnitude of prominences and the width at half prominence.
+In the magnitude-based method, the middle point $x_i$ is compared to two neighboring points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
+The gradient-based method evaluates the first derivative at the point which is equal to zero if the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
 
@@
 
-Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with central frequency, uncertainty, and amplitude $C_i(v_i, \Delta v_i, A_i)$ by an exhaustive search algorithm.
-Harmonic family identification is a non-trivial problem because of the spectrum estimation errors.
-The criterion is proposed to select harmonic at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
+Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with a central frequency, uncertainty, and amplitude $C_i(v_i, \Delta v_i, A_i)$ by an exhaustive search algorithm.
+Harmonic family identification is a non-trivial problem because of spectrum estimation errors.
+The criterion is proposed to select harmonics at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
 Two series with the same fundamental frequency are merged and thought of as a modulation series~\cite{gerber_identification_2013}.
@@
 \subsection{Time-frequency domain features}
-The \textbf{Short-time Fourier transform} (STFT) splits the time-domain signal to an equal-length intervals.
-Individual chunks have 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to Fourier transform periodicity assumption.
-Traditionally, the Hann window is commonly used instead of rectangular window~\cite{ziaran_technicka_2013,noauthor_iso_2016_2}.
+The \textbf{Short-time Fourier transform} (STFT) splits the time-domain signal into equal-length intervals.
+Individual chunks have a 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to Fourier transform periodicity assumption.
+Traditionally, the Hann window is commonly used instead of the rectangular window~\cite{ziaran_technicka_2013,noauthor_iso_2016_2}.
 
@@
 The optimal window size has to be set beforehand or chosen after performing multiple transformations on chunks out of the range of lengths.
-Welch's methods averages multiple consecutive blocks to better estimate the spectrum.
+Welch's method averages multiple consecutive blocks to better estimate the spectrum.
 We have already researched the suitability of STFT for online detection of constant frequencies~\cite{hajek_iot_2022}.
@@
 The alternative to isolating weak impacts with high time resolution is a \textbf{Teager-Kaiser energy operator} (TKEO) (Equation~ \ref{equ:tkeo-operator}).
-It is a tool for envelope analysis to demodulate characteristic AM-FM signal present during bearing faults.
+It is a tool for envelope analysis to demodulate characteristic AM-FM signals present during bearing faults.
 Energy operator output can be utilized as a standalone feature attribute.
@@
 Improved TKEO is necessary to prevent analysis from suffering from the noisy source.
-The key idea is to perform TKEO after signal decomposition into narrow-band components with different center frequencies.
+The key idea is to perform TKEO after signal decomposition into narrowband components with different center frequencies.
 The extracted modes are reconstructed with weights assigned based on their correlations to the original signal~\cite{shi_application_2022}.
 
-Time-frequency spectrum modification preserving localization of abrupt wide-band spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
+Time-frequency spectrum modification preserving localization of abrupt wideband spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
 Post-processing of STFT window $G(t,\omega)$ involves multiplication of the spectrum with the Transient extracting operator (TEO).
@@
 
-TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
+TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs, $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
 These two transforms use distinct windows $g[n]$ and $n \cdot g[n]$.
-Decomposition of signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
+Decomposition of a signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
 
 \subsection{Wavelet domain features}
-The bands for lower frequencies should be longer in duration than for higher frequencies.
-The \textbf{Wavelet transform} (WT) possesses such multi-scale discrimination property effectively increasing resolution in time-frequency plain.
+The bands for lower frequencies should be longer in time than for higher frequencies.
+The \textbf{Wavelet transform} (WT) possesses such a multiscale discrimination property, effectively increasing resolution in time-frequency plain.
 Wavelet basis functions are constructed for that purpose (Equation~\ref{equ:mother-wavelet}).
-There are several wavelet families, for example, Haar, Daubechies, Coiflets, Symlets, Morlet, and Meyer~\cite{nandi_condition_2019}.
+There are several wavelet families.
+For example, Haar, Daubechies, Coiflets, Symlets, Morlet, and Meyer~\cite{nandi_condition_2019}.
 
@@
 
-\textbf{Continuous Wavelet transform} (CWT)~(Equation~\ref{equ:cwt-transform}) is performed by scaling and translating the mother wavelet $\psi$ picked out of the appropriate family~\cite{nandi_condition_2019}.
+\textbf{Continuous Wavelet transform} (CWT)~(Equation~\ref{equ:cwt-transform}) is done by scaling and translating the mother wavelet $\psi$ picked out of the appropriate family~\cite{nandi_condition_2019}.
 The scale factor is denoted with~$s$ and time position with~$\tau$.
@@
 The CWT is computationally intensive when a highly detailed scale resolution is required because each wavelet scale convolves with the entire signal.
-The fCWT algorithm allows 100 times higher spectral resolution then previous implementation at the same speed.
+The fCWT algorithm allows 100 times higher spectral resolution than previous implementations at the same speed.
 It increases performance 122 times compared to Wavelib and 34 times in comparison with PyWavelets~\cite{arts_fast_2022}.
@@
 The convolution takes place with the mother wavelet in the Fourier base.
-Then, inverse FFT produces the coefficients for individual scales.
+Then, the inverse FFT produces the coefficients for individual scales.
 
@@
 
-The spectrograms to illustrate the difference in the ability of Fourier transform, continuous Wavelet transform, and their modifications to pick up underlying patterns in bearing faults are shown in the Fig.~\ref{fig:transforms}.
+The spectrograms to illustrate the difference in the ability of the Fourier transform, the continuous Wavelet transform, and their modifications to pick up underlying patterns in bearing faults are shown in Fig.~\ref{fig:transforms}.
 
@@
 
-The dyadic filter bank is another signal decomposition technique that generates subbands on multiple granularity levels.
-The practical realization of the multi-scale description is \textbf{Discrete Wavelet Transform} (DWT).
-The DWT behaves as a quadrature mirror filter and splits waveform using a wavelet filter to detail coefficients (D1) and approximation coefficients (A1) (Fig.~\ref{fig:dwt-filter-bank})~\cite{nandi_condition_2019}.
-Low-pass filter $h(k)$ creates approximation coefficients further decomposed in the successive levels.
-Detail coefficients represent the result of the high-pass filter $g(k) = (-1)^k h(1 - k)$ after decimation by the factor of 2.
+The dyadic filter bank is another signal decomposition technique that generates subbands at multiple granularity levels.
+The practical realization of the multiscale description is \textbf{Discrete Wavelet Transform} (DWT).
+The DWT behaves as a quadrature mirror filter and splits waveforms using a wavelet filter to detail coefficients (D1) and approximation coefficients (A1) (Fig.~\ref{fig:dwt-filter-bank})~\cite{nandi_condition_2019}.
+The low-pass filter $h(k)$ creates approximation coefficients further decomposed at the successive levels.
+Detail coefficients represent the result of the high-pass filter $g(k) = (-1)^k h(1 - k)$ after decimation by a factor of 2.
 
@@
 
-In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provided features combined from approximation (cA5) and detail coefficients (cD1, \dots, cD5).
-Washing machines belonged to three categories: no fault, electric motor clamping screws problem, and a loose or broken counterweight.
+In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provide features with a combination of approximation (cA5) and detail coefficients (cD1, \dots, cD5).
+Washing machines belong to three categories: no fault, electric motor clamping screws problem, and a loose or broken counterweight.
 Extracted measures were sample mean and sample variances over autocorrelation functions of coefficients (AcD$n$) and smoothed coefficients cD1, cD2 by moving average filter~\cite{goumas_classification_2002}.
@@
 This measure is an inner product of the source and scaled wavelet packet function.
-The aforementioned feature extraction established in DWT can be applied, for example calculation of the wavelet packet node energy.
+The aforementioned feature extraction established in DWT can be applied.
+For example calculation of the wavelet packet node energy.
 
@@
 
-The wavelet packet energy ratio for weak feature extraction has been incorporated into the method of multiple frequency bands demodulation (MFBD).
+The wavelet packet energy ratio for weak feature extraction has been incorporated into the method of multiple frequency band demodulation (MFBD).
 The highest $n$ energy coefficients are selected out of 8 narrow frequency bands to subsequently affect the principal components.
 Demodulation principle for the frequency bandwidth prescribes $n$ to satisfy condition: $1\;/\;2^n > f_{\mathrm{modulation}}\;/\;f_s$.
-The first few eigenvectors explaining together more than 80\% of energy are retained to reconstruct the signal with Fourier transform and retain the weak fault components~\cite{song_mfbd_2021}.
+The first few eigenvectors that explain together more than 80\% of energy are retained to reconstruct the signal with a Fourier transform and retain the weak fault components~\cite{song_mfbd_2021}.
 
@@
 The normalized frequency axis in range $\omega \in [0, \pi]$ is divided by split points $\omega_0, \dots, \omega_N$ where $\omega_n = f_n \cdot 2 \pi\;/\;f_s$ (Fig.~\ref{fig:ewt-spectrum-segmentation}).
-Each segment is bounded between $[\omega_{n-1}, \omega_n]$ with transition phase of width $2\tau_n$ and polynomial transition function $\beta(x)$.
+Each segment is bounded between $[\omega_{n-1}, \omega_n]$ with a transition phase of width $2\tau_n$ and polynomial transition function $\beta(x)$.
 A tight frame set of empirical wavelets is built by setting the transition phase proportional to the band boundary: $\tau_n = \lambda \omega_n$, and proportional constant must obey constrain: $\lambda = \min\left(\frac{\omega_{n+1} - \omega_n}{\omega_{n+1} + \omega_n}\right)$.
@@
 
-The drawback of EWT is improper segmentation in noisy and non-stationary signals producing too many uninformative partitions of the spectrum.
+The drawback of EWT is improper segmentation in noisy and non-stationary signals, producing too many uninformative partitions of the spectrum.
 The solutions we discuss fall into two groups that apply improvements before or after the wavelet transformation step.
@@
 A combination of \textbf{Maximum Correlated Kurtosis Deconvolution} and improved EWT (MKCD-EWT) favors periodic impacts by dynamically constructing an optimal FIR filter that maximizes the correlation kurtosis of the signal.
-The envelope curve smooths of the amplitude spectrum by linear interpolation (Fig.~\ref{fig:mkcd-ewt-segmentation}).
+The envelope curve smooths the amplitude spectrum by linear interpolation (Fig.~\ref{fig:mkcd-ewt-segmentation}).
 The threshold accounting for desired SNR modifies the envelope when more than $n$ components are discovered ($A_h$ is maximal amplitude and $A_l$ is minimal amplitude): $\lambda = A_l + \frac{C}{\mathrm{SNR}}(A_h - A_l)$.
-\emph{Squared envelope spectrum} and \emph{Teager energy operator spectrum} are computed as fault features for the IMF with highest kurtosis~\cite{li_fault_2019}.
+\emph{Squared envelope spectrum} and \emph{Teager energy operator spectrum} are computed as fault features for the IMF with the highest kurtosis~\cite{li_fault_2019}.
 
-The segmentation boundaries detection can be accomplished also on the spectral envelope consisting of \textbf{Piecewise Cubic Hermite Interpolating Polynomial} (PCHIP-EWT) instead of scanning the Fourier spectrum directly (Fig.~\ref{fig:pchip-ewt-segmentation}).
-Divisions of the upper cut-off frequency are kept if local power indicates a subband with useful information ($p_i(f) \geq \lambda$)  as in the case of abrupt level change.
-Local power is the ratio of $n$th local envelope maximum and difference of indexes of its adjacent local minima:  $p_i(f) = K_{max(i)(f)} \;/\;\left(f_{k_{min(i+1)}} - f_{k_{min(i)}}\right)$.
+The segmentation boundary detection can also be accomplished on the spectral envelope consisting of \textbf{Piecewise Cubic Hermite Interpolating Polynomial} (PCHIP-EWT) instead of scanning the Fourier spectrum directly (Fig.~\ref{fig:pchip-ewt-segmentation}).
+Divisions of the upper cut-off frequency are kept if local power indicates a subband with useful information ($p_i(f) \geq \lambda$)  as in the case of an abrupt level change.
+Local power is the ratio of $n$th local envelope maximum and the difference between indexes of its adjacent local minima:  $p_i(f) = K_{max(i)(f)} \;/\;\left(f_{k_{min(i+1)}} - f_{k_{min(i)}}\right)$.
 The best $\lambda$ is set experimentally~\cite{zhuang_improved_2020}.
@@
 
-The inspiration for filtering with adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
+The inspiration for filtering on an adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
 This procedure locates local maxima and minima in the time waveform that are interpolated with cubic splines to form signal envelopes.
@@
 
-Wavelet domain features and associated spectral segmenation appears to be a powerful tool in conserving data bandwidth.
-For the use in white-box machinery diagnosis these trend indicator turn out to be difficult to comunicate and comprehend.
-Therefore we use more standardized metrics in the further study.
+Wavelet domain features and associated spectral segmentation appear to be a powerful tool in conserving data bandwidth.
+These variables turn out to be difficult to communicate and comprehend.
+Therefore, we will use more standardized metrics in further studies.
 
@@
 Numerical features from the feature extraction phase have non-normal distributions and span wide ranges.
-Broad differences among features skew the spread in the particular axis.
-Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}.
+Broad differences among features skew the spread on a particular axis.
+Inevitably, it can degrade the discernment of fault diagnostics models that map input onto a smooth function as regression does~\cite{zheng_feature_2018}.
 The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.
@@
 \subsection{Feature normalization}
-Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its component.
+Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its own component.
 Models have to be resilient to any slight inclination or sensor orientation.
-To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and Euclidian norm is computed~\cite{kamminga_robust_2018}.
+To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidian norm is computed~\cite{kamminga_robust_2018}.
 
@@
 Feature normalization most often takes two forms.
-\textbf{Min-max scaling} changes original range of values into interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
+\textbf{Min-max scaling} changes the original range of values into an interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
 \textbf{Standardization} (Equation~\ref{equ:standardization-scaler}) constrains the mean of the variable to 0 with a variance of 1~\cite{zheng_feature_2018}.
@@
 Highly correlated features generated from a relatively small original column space are redundant as they do not provide any additional information for diagnostics.
-\textbf{Principal Component Analysis} (PCA) solves this problem by projecting potentially linearly dependant features into a new feature space where the incoming information is preserved in a smaller number of features~\cite{zheng_feature_2018}.
+\textbf{Principal Component Analysis} (PCA) solves this problem by projecting potentially linearly dependent features into a new feature space where the incoming information is preserved in a smaller number of features~\cite{zheng_feature_2018}.
 The threshold of how many principal components are picked depends on the amount of explained variance and desired quantity of data reduction.
@@
 \section{Feature selection}
-Features do not contribute to predictive power of the model with an even share. A certain subset can reach better results than others. Choosing optimal feature subset is NP-hard combinatorial problem.
+Features do not contribute to the predictive power of the model with an even share.
+A certain subset can achieve better results than others.
+Choosing the optimal feature subset is the NP-hard combinatorial problem.
 
@@
 
-The general steps in selecting the adequate predictors is as follows~\cite{nandi_condition_2019}:
+The general steps in selecting the appropriate predictors are as follows~\cite{nandi_condition_2019}:
+
 \begin{enumerate}
@@
 Attributes are either appended to an empty set or pruned away from a universal set, sequentially or randomly.
-    \item \textbf{Subset evaluation} - comparison of subset quality is assessed with relevance measure some of which are discussed below.
+
+    \item \textbf{Subset evaluation} - comparison of subset quality is assessed with relevance measures, some of which are discussed below.
+
     \item \textbf{Stopping criteria} - search is exhausted when the specified number of features has been found, subset metrics cannot be improved further, or satisfactory model performance is achieved.
 Subset generation and evaluation can be performed multiple times until the stopping criteria are met.
-    \item \textbf{Validation} - resulting subset is tested for the specific model on synthetic and real-world datasets against well-known results. 
+
+    \item \textbf{Validation} - the resulting subset is tested for the specific model on synthetic and real-world datasets against well-known results. 
 \end{enumerate}
@@
 The frequently used scores upon which the feature relevance is ordered are~\cite{nandi_condition_2019}:
+
 \begin{itemize}
-\item \textbf{Variance threshold} - removes low-variance features below set threshold.
+\item \textbf{Variance threshold} - removes low-variance features below the set threshold.
+
 \item \textbf{Correlation coefficient} - expresses the linear relationship between two variables.
@@
 
-\emph{Pearson correlation} coeficient expresses similarity between two quantitative features $f_i$ and $f_j$.
-In the classification setting the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}.
+\emph{Pearson correlation} coeficient expresses similarity between two quantitative features: $f_i$ and $f_j$.
+In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}.
 Mathematically, this is equivalent to the Pearson coefficient.
@@
 Attributes are ranked in descending order according to the absolute value of their correlation coefficient. We seek the highest correlation to the class label.
+
 \myequations{Pearson correlation coefficient}
@@
 
-\item \textbf{Fisher score} - measures the difference among the means of the classes.
+\item \textbf{Fisher score} - measures the difference between the means of the classes.
 It is interchangeable with ANOVA F-value, but it is evaluated for each feature $X^j$ separately.
@@
 
-\item \textbf{Mutal information} - quantifies the dependence among features, or between features and class labels.
+\item \textbf{Mutal information} - quantifies the dependence between features, or between features and class labels.
 It is almost identical to Information Gain.
-The probability distribution proximity of variables derives from relative entropy known as the Kullback-Leibler distance.
+The probability distribution of proximity of variables derives from the relative entropy known as the Kullback-Leibler distance.
 Mutual information presumes variables are discrete.
-In the case of quantitative variables, mutual information is estimated with binning or nearest neighbors methods~\cite{ross_mutual_2014}.
+In the case of quantitative variables, mutual information is estimated by binning or nearest neighbors methods~\cite{ross_mutual_2014}.
 

### 2024-01-01 thesis/chapters/02-analysis-C-diagnostics.tex
Fix grammar

@@
 \section{Diagnostics techniques} \label{section:diagnostics-techniques}
-Fault identification in the rotating machinery is one-class or multi-class classification problem acting in a semi-supervised manner because labels for degraded conditions are scarce in practice.
+Fault identification in the rotating machinery is a one-class or multi-class classification problem acting in a semi-supervised manner because labels for degraded conditions are scarce in practice.
 The automation goals in monitoring can be broadly categorized as anomaly detection and recognizing the momentary fault type.
@@
 The expert can then step in and diagnose the machine after the notice.
-Anomaly is a rare observation different from the others raising suspicion that it was created with an unrelated behavior~\cite{aggarwal_outlier_2016}.
+Anomaly is a rare observation different from the others, raising suspicion that it was created by unrelated behavior~\cite{aggarwal_outlier_2016}.
 The observations get assigned anomaly scores, and those over the threshold are novelties.
@@
 Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1].
-It demands for points within clusters to have high cohesion and at the same time to have large separation from other clusters.
-The low score indicates a too little or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
+It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters.
+The low score indicates a too small or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
 
@@
 
-In the online maintenance phase, DenStream summarizes the nearby observations into core \emph{micro-clusters} that can be potential or outlier \emph{micro-clusters} (Fig.~\ref{fig:denstream})~\cite{ghesmoune_state---art_2016}.
+In the online maintenance phase, DenStream summarizes the nearby observations into core \emph{micro-clusters} that can be potential micro-clusters or outlier \emph{micro-clusters} (Fig.~\ref{fig:denstream})~\cite{ghesmoune_state---art_2016}.
 The (outlier) \emph{o-micro-clusters} can grow into (potential) \emph{p-micro-clusters} when they encompass $\beta \mu$ points.
-The outliers are discounted after some time in accordance to the decay function: $f(t) = 2^{-\lambda t}$ or below lower weight limit $\xi$.
+The outliers are discounted after some time in accordance to the decay function: $f(t) = 2^{-\lambda t}$ or below the lower weight limit $\xi$.
 The on-demand offline stage runs DBSCAN over the approximate representation in micro-clusters to deliver final apportionment~\cite{cao_density-based_2006}.
@@
 A full binary tree is built before the novelty detection begins by splitting tree nodes along the divisions in the randomly chosen perpendicular planes.
-The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and link to both child nodes~\cite{tan_fast_2011}.
+The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and links to both child nodes~\cite{tan_fast_2011}.
 
 The anomaly profile in the latest window is always compared to the predecessor reference window.
-After the latest window is filled up it replaces the reference window.
-It suffices to use a window size of 250 and 25 tree ensemble~\cite{tan_fast_2011}.
+After the latest window is filled up, it replaces the reference window.
+It suffices to use a window size of 250 and an ensemble of 25 trees~\cite{tan_fast_2011}.
 
@@
 Performance of classification is estimated by several metrics on the validation set obtained using hold-out or cross-validation techniques.
-Frequently used quantities for classifier model evaluation include accuracy, precision, recall, f1 score, area under ROC curve, and counts of hits and misses in confusion matrix.
+Frequently used quantities for classifier model evaluation include accuracy, precision, recall, f1 score, area under the ROC curve, and counts of hits and misses in a confusion matrix.
 \bigbreak
@@
 \textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
-It means it can work in the semi-supervised environment because it can infer labels just from knowing a few annotations.
-The major drawback of KNN is a preference for the majority class in imbalanced class sizes datasets~\cite{shi_improving_2020}.
+It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations.
+The major drawback of KNN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}.
 The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
-KNN algorithm requires features to be normalized to assign the same importance to each predictor.
+The KNN algorithm requires features to be normalized to assign the same importance to each predictor.
 
@@
 (Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
-The optimal $k$ parameter is set in supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
+The optimal $k$ parameter is set by supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
 The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.
@@
 
-Nearest-neighbour classifier has been successfully applied in machinery fault diagnostics.
+The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics.
 On the CWRU bearing dataset, the KNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - KNN 91.2\%, SVM 88.8\%, and frequency domain features - KNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
@@
 Comparison of KNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
-Best accuracies were reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric.
+Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric.
 The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
-Despite KNN lagging in accuracy, we have to keep in mind annotations for faults were complete and machine learning was not tested in a streaming context.
+Despite KNN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.
 
 \subsection{Incremental learning}
-Online or incremental machine learning operates on the streaming data updating the model parameters with each new incoming event or in mini-batches.
+Online or incremental machine learning operates on the streaming data, updating the model parameters with each new incoming event or in mini-batches.
 This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.
@@
 There are some additional obstacles to watch out for with incremental learning in comparison to batch learning~\cite{gepperth_incremental_2016}:
+
 \begin{enumerate}
     \itemsep0pt
+
     \item \textbf{Concept drift} is defined as the change in data distribution function over time.
@@
 Real drift means that the alteration comes to underlying functionality.
-Concept shift occurs with the abrupt change.
+Concept shift occurs with an abrupt change.
+
     \item \textbf{Stability-plasticity tradeoff} concerns the speed with which the model adapts to new information.
-The model can react quickly making it less stable, or retain patterns for longer but become irresponsive to sudden shifts.
+The model can react quickly, making it less stable, or retain patterns for longer but become irresponsive to sudden shifts.
+
     \item \textbf{Model complexity} should be adjustable to ensure flexibility in unforeseen circumstances.
@@
 Resource limitation bound complexity from above.
+
     \item \textbf{Memory model} can store aggregates from seen observations and its typical examples or finite window of latest samples with forgetting factor.
@@
 
-Deployment of an online machine learning model alongside supporting services is different than in established MLOps processes.
+Deployment of an online machine learning model alongside supporting services is different from in established MLOps processes.
 Model store and Inference service components are supplemented with Labelling and Learning service~\cite{gaia_online_2022}.

### 2024-01-01 thesis/chapters/03-design.tex
Setup firware project and gather pre-made examples
Fix grammar

@@
 	\item What is the reduction in transmission goodput when chosen signal features are used?
-	\item What accuracies of prediction models can be achieved with various feature subsets?
+	\item What accuracy of prediction models can be achieved with various feature subsets?
 	\item How can machinery faults be continuously identified and predicted based upon collected events?
@@
     \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
-	\item Find the best subsets of features in temporal and spectral domain with previously analyzed feature extraction and selection methods.
+    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
     \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
-	\item Combine feature selection with online machine learning model.
+    \item Combine feature selection with an online machine learning model.
     \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
-	\item Develop hardware and implement its firmware to obtain such measurement in the quality demanded by vibrodiagnostics standards.
+    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
 \end{todolist}
@@
 The goals are impacted by certain \textbf{risks} that are assessed and tracked:
+
 \begin{enumerate}[label=R-\arabic*., font=\bfseries]
@@
 \\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
-\item Fault modes could not be reliably differentiated and labeled in the dataset.
-\\ \emph{Mitigation}: Consult domain experts and machines' maintenance staff.
+\item Fault modes can not be reliably differentiated and labeled in the dataset.
+\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
 \item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
@@
 \section{Dataset exploration}
-In establishing the viability of methods to be deployed in the sensor node, we explore the MaFaulDa dataset.
-It is the largest known machinery fault collection, so it is possible to create multiple subsets based on requested conditions.
+In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset.
+It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.
 
@@
 \subsection{Fault annotations}
-The MaFaulDa has annotations altogether for 10 classes of faults of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
+The MaFaulDa has annotations altogether for 10 classes of faults, of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
 Some categories are redundant or irrelevant for a given sensor position.
 
-Therefore rotor shaft misalignements in vertical and horizontal directions are merged into one joint group. Depending on the chosen bearing position only records having relevant labels are considered.
+Therefore, rotor shaft misalignement in vertical and horizontal directions are merged into one joint group.
+Depending on the chosen bearing position, only records having relevant labels are considered.
 
-This means that fault classification solely concerns bearing in the direct contact and shaft mechanically passing through it.
+This means that fault classification solely concerns bearing in direct contact and shaft mechanically passing through it.
 The bearings affect each other, but the effect on the opposite side should appear via a common interconnection shaft.
@@
 In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
-In the step of choosing the accelerometer location records pointing to the other bearing as a source of the malfunction are discarded.
+In the step of choosing the accelerometer location, records pointing to the other bearing as a source of the malfunction are discarded.
 Then the next action renames the labels to be better recognizable and unite the same phenomena.
@@
 Groups of identified machine defects are additionally characterized by altered masses attached or motor shaft displacement shifts.
-The set amount is sorted in ascending order separating \textbf{multiple event severities}.
+The set amount is sorted in ascending order, separating \textbf{multiple event severities}.
 However, the count of severity levels is not identical in every group.
@@
 
-The strength of the recorded response by the underlying defect is also dependent on the shaft \textbf{rotational speed}.
-Speed in rpm is calculated from pulsed speedometer output.
+The strength of the recorded response to the underlying defect is also dependent on the shaft \textbf{rotational speed}.
+Speed in rpm units is calculated from pulsed speedometer output.
 It is the average distance between two successive rising edges:
@@
 
-Before the low pass filter usage, the peak at 20 kHz with sideband was present as an unwanted artifact.
+Before the low pass filter usage, the peak at 20 kHz with a sideband was present as an unwanted artifact.
 It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
-At the same time, such frequency is outside the range of any feasible MEMS accelerometer.
+At the same time, such a frequency is outside the range of any feasible MEMS accelerometer.
 
@@
 
-\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from normal distribution under most circumstances.
+\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from a normal distribution under most circumstances.
 The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms.
@@
 
-\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root 
-(${p < 0.001}$). The same is confirmed with the \textbf{autocorrelation} function shape. It denotes that the stochastic process is stationary as oscillation is bounded.
+\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root (${p < 0.001}$).
+The same is confirmed with the \textbf{autocorrelation} function shape.
+It denotes that the stochastic process is stationary as the oscillation is bounded.
 
@@
 Fault labels and their severities come from the directory structure within the dataset.
-The binary target variable indicating whether to initiate a warning is named to be an anomaly.
+The binary target variable indicating whether to initiate a warning is called an anomaly.
 Anomalies are labeled according to relative fault severity level.
@@
 In the temporal domain, the correlation coefficient is within an interval of -0.08 to 0.26.
-In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for centroid being around 0.35.
+In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for the centroid being around 0.35.
 
@@
 
-It is assumed that data points spread in each dimension of the feature space could distinguish groups well.
-The variables that the best explain after min-max scaling total dataset variance in the temporal domain are shape (29\%), rms, std, max, and p-p (each around 15\%).
-In the spectral domain, variance is the best explained by roll-off (28\%), entropy, skewness, centroid, and kurtosis (each around 12\%).
+It is assumed that data points spread throughout each dimension of the feature space could distinguish groups well.
+The variables that are the best explained after min-max scaling total dataset variance in the temporal domain are shape (29\%), rms, std, max, and p-p (each around 15\%).
+In the spectral domain, variance is best explained by roll-off (28\%), entropy, skewness, centroid, and kurtosis (each around 12\%).
+
 \begin{figure}[h!]
@@
 
-The variables are also more inter-correlated in the temporal domain shown by principal components analysis.
+The variables are also more inter-correlated in the temporal domain shown by principal component analysis.
 For 95\% of the explained variance of PCA 3 components (98.69\%) are needed in the temporal domain whereas 4 in the spectral domain (95.26\%).
@@
 \ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
-The first PC in the temporal domain focuses more on amplitude range: \emph{max, rms, pp, std}.
+The first PC in the temporal domain focuses more on the amplitude range: \emph{max, rms, pp, std}.
 The second PC mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, margin}.
 
-However, the groups are not as clear cut for spectral features.
+However, the groups are not as clear-cut for spectral features.
 Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.
@@
 
-Machinery monitoring system relies on determining several parameters:
+The machinery monitoring system relies on determining several parameters:
 \begin{itemize}
 \itemsep0pt
-\item \textbf{Number of source channels} ($S$): is comprised of the number of monitored machines, measurement locations for sensors, and active sensor axes.
+\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
 \item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
@@
 \item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
-The more critical the machine is, interval should be shorter.
+The more critical the machine is, the interval should be shorter.
 The bigger the machine parts, the slower the defect evolves.
-\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltering behavior associated with a timestamp.
+\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp.
 Duration should cover at least 3 windows for spectral estimation.
 The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
-\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfuctions. We aim for total of 6 features.
+\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
 \end{itemize}
@@
 \textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
-In case 6 features are kept, the compression is 25000:1, which is a saving of the original data amount of 99.996\%.
+If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.
 
 As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
-The station has 3 pumps and matching 3 electric induction motors.
+The station has 3 pumps and 3 electric motors.
 
@@
 Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
-The sampling frequency on each position is set to \emph{20 kHz}.
+The sampling frequency at each position is set to \emph{20 kHz}.
 The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
 
-In a year the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with 16-bit ADC resolution.
+In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution.
 Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
@@
 As a starting point, the set consists of 3 non-correlated attributes under diverse conditions.
-Ultimately a number of chosen features is to be tweaked to increase prediction accuracy.
+Ultimately, a number of chosen features are to be tweaked to increase prediction accuracy.
 Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
+
 \begin{itemize}
 \itemsep0pt
-\item \textbf{online}: boolean selector that influences whether metrics are calculated in batch or incremental fashion,
+\item \textbf{online}: a boolean selector that influences whether metrics are calculated in batch or incremental fashion,
 \item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
-\item \textbf{predicted variable}: selects column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
+\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
 \item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
@@
 The best group of attributes is elected based on a training set with multiple methods.
-We compute the mean of absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable.
-The features are then ordered in descending order of the received score.
+We compute the mean of the absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable.
+The features are then ordered in descending order by the received score.
 These individual ranks are combined by rank product to create an ensemble out of the metrics.
@@
 We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets.
-kNN classifier being a lazy learner means it can be adapted easily from offline to online context.
+The KNN classifier being a lazy learner means it can be adapted easily from offline to online context.
 Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values.
@@
 \subsection{Batch models}
-Three types of KNN model experiments run with hold-out validation in batch setting. 
+Three types of KNN model experiments run with hold-out validation in a batch setting.
 First, the model learns all extracted features, so no feature selection occurs.
@@
 The subset of records includes all rotational speeds on bearing position A.
-Either six fault labels or anomaly above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
+Either six fault labels or anomalies above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
 
@@
 In anomaly prediction, the error of the first degree is 7 times more prevalent than the error of the second degree.
-False positives are preferable since we do not want the machine to fail prematurely and not know about it.
+False positives are preferable, since we do not want the machine to fail prematurely and not know about it.
 In all cases, spectral features maintain better prediction metrics than all temporal features because of less interdependency among features.
@@
 Models are overtrained, especially for temporal features, because of the substantial difference between accuracy on training and validation sets.
-Binary classification of anomaly is unsurprisingly more precise in general than multiclass case.
+Binary classification of anomalies is unsurprisingly more precise in general than the multi-class case.
 Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 87\% for bearing B.
@@
 The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
-Accuracies of KNN algorithm for different target variables are in Figure \ref{fig:design:feature-combinations-KNN}.
+The accuracy of the KNN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
 
@@
 Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}.
-Worst accuracies occur for temporal features in multiclass classification 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
+The worst accuracy occurs for temporal features in multi-class classification, 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
 An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.
@@
 \centering
+\renewcommand{\arraystretch}{1.2}
 \begin{adjustbox}{width=\textwidth}
@@
 Lowering the number of attributes allows visualization of labels in planar scatter plots.
-The data points in 3-dimensional cross sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
+The data points in 3-dimensional cross-sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
 We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
@@
 
-Model performance of KNN algorithm preceeded by variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
-Best combination of three features achieves always better than when the model is trained on all features.
+Model performance of the KNN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
+The best combination of 3 features always achieves better than when the model is trained on all features.
 This has to do with curse of dimensionality phenomenon.
@@
 The bar chart supports this assumption.
-PCA always produces greater model accuracies than any other method of feature selection.
+PCA always produces greater model accuracy than any other method of feature selection.
 The rank product of the three scoring techniques is not better every time, but it balances out aggregated methods to achieve more stable results across testing sets.
@@
 
-The KNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in batch context.
+The KNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context.
 In this manner, we can compare the training accuracies in the last sample for both models.
-KNN is set to 5 nearest neighbors and proximity metric of Euclidian distance.
-Online learning metrics are evaluated in progressive valuation on a dataset that is left unbalanced.
+KNN is set to 5 nearest neighbors and a proximity metric of Euclidian distance.
+Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
 
@@
 Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
-Counters of other faults show that model prediction are skewed towards more represented classes of imbalance and misalignement.
+Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement.
 The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
@@
 Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
-Labeling delay of 250 observations causes accuracies to drop to 70.51\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
+Labeling delay of 250 observations causes accuracy to drop to 70.51\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
 Accuracy better than 50\% is achieved 200 steps sooner in the spectral domain than in the temporal domain.
@@
 Labels for the whole previous window are supplied at once.
-At the final sample, the accuracies are 83.41\% \emph{(temporal)} and 90.14\% \emph{(spectral)} with immediate feedback, and 77.95\% \emph{(temporal)} and 85.90\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
+In the final sample, the accuracies are 83.41\% \emph{(temporal)} and 90.14\% \emph{(spectral)} with immediate feedback, and 77.95\% \emph{(temporal)} and 85.90\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
 
@@
 A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
-Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows true labels are unknown.
-After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observation.
+Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows.
+The true labels are unknown.
+After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
 
-Another common problem in online learning is \textbf{missing annotations} due to the size of the dataset.
+Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset.
 In the simulation of missing labels, the equal-length gaps are skipped before another observation is annotated.

### 2024-01-01 thesis/chapters/04-implementation.tex
Fix grammar

@@
 \textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
-Altogether two units are available in two independent air conditioning units for the data center.
+Altogether, two units are available in two independent air conditioning units for the data center.
 The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
@@
 The electric motor provides 400~kW of power (class~\rom{3}).
-Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.
+The outer bearing on the pump vibrates with an acceleration of $\pm 5 \;\mathrm{m/s}^2$.
 
@@
 \textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
-In addition, we are able to export the entire historical record in hourly intervals.
+In addition, we are able to export the entire historical record at hourly intervals.
 Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
@@
 In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
-The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
+The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
 
@@
 Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
-The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pins.
+The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
 The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
@@
 During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
-Raw waveforms of acceleration for the fan, two different compressors, and outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
+Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
 The acceleration rarely exceeds 1~g.
 
-In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned, below the resonance frequency of the accelerometer (550 Hz).
-The compressor suspected to be faulty has stronger \nth{4} harmonic and above than the other one.
+In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz).
+The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
 

### 2024-01-01 thesis/chapters/05-conclusion.tex
Fix grammar

@@
 \chapter{Conclusion} \label{section:conclusion}  
-In the thesis we focused on trend indicator selection for inexpensive industrial condition monitoring solution from vibration signals.
+In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals.
 The goal is to enable timely fault detection of machinery parts with as little input data as possible.
@@
 Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343).
-These formulas compute 10 features summarizing waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.
+These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.
 
@@
 The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables.
-Annotation can be assigned belatedly or even never.
+Annotations can be assigned belatedly or even never.
 Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
@@
 
-Feature selection methods shall be incorporated into incremental learning.
+Feature selection methods should be incorporated into incremental learning.
 Hyperparameters shall be adjusted, and the balancing method used to increase model performance.

### 2024-01-01 thesis/chapters/appendix/C-technical-documentation.tex
Fix grammar

@@
                                                                                       & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
+\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
                                                                                       & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
@@
                                                                                       & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
+\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
                                                                                       & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
@@
 Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution.
-Total space requirements for 108 recordings are 990 MiB.
+The total space requirements for 108 recordings are 990 MiB.
 
 \section{Firmware activities}
-
 Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

### 2024-01-01 thesis/chapters/preliminaries/annotation.tex
Fix grammar

@@
 Trend indicators are derived from vibration signals to form summarizing numerical attributes.
-The similarity of features to a dependent variable describing fault types is assessed with supervised feature selection metrics individually and in the ensemble.
+The similarity of features to a dependent variable describing fault types is assessed by supervised feature selection metrics individually and in the ensemble.
 The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve data rates of the monitoring solution.
@@
 Based on the MaFaulDa dataset, classification metrics are evaluated in several scenarios, and lossy compression ratios are expressed.
-The measurement plan and sensor device are designed to enable collection of novel datasets of machinery behavior for compressors and pumps.
+The measurement plan and sensor device are designed to enable collection of novel dataset of machinery behavior for compressors and pumps.
 The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.

### 2024-01-03 thesis/chapters/04-implementation.tex
Test SD card and DP2 export

@@
 The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
-It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW.
+It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}).
 Each pump and motor have 2 bearings.
@@
 \textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
-\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
-\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
+\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
+\textbf{Sensitivity} (mg/LSB)                    & 2.930            & 0.061       \\ \hline
 \textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
@@
 The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
-An interface capable of higher speeds is needed to store all acceleration samples.
-Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
+ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
+It enables us to store all samples from FIFO.
 The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
@@
 During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
-Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
+Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
 The acceleration rarely exceeds 1~g.
@@
 Envelopes must be tweaked further to achieve more accurate values.
+The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
 
@@
 \end{figure}
-
-The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.

### 2024-01-03 thesis/chapters/appendix/B-plan-of-work.tex
Test SD card and DP2 export

@@
  \\ \hline
-\nth{6} week         & Feature selection used in kNN multiclass and binary classificator.
+\nth{6} week         & Feature selection used in KNN multiclass and binary classificator.
  \\ \hline
-\nth{7} week         & Explore incremental learning kNN algorithm with MaFaulDa dataset. Consultation and status report.
+\nth{7} week         & Explore incremental learning KNN algorithm with MaFaulDa dataset. Consultation and status report.
  \\ \hline
@@
 \item Find optimal number of features. 
-\item Try to increase kNN prediction metrics.
+\item Try to increase KNN prediction metrics.
 \item Put together incremental learning with feature selection. 

### 2024-01-03 recorder/firmware/main/include/pinout.h

@@ -6,11 +6,13 @@
 #include "hal/gpio_types.h"
 #include "driver/sdmmc_host.h"
 #include "esp_err.h"
+#include "esp_log.h"
 
 
 #define MAX_FILENAME            256
 #define MOUNT_POINT             "/sd"
-#define LOG_FOLDER              MOUNT_POINT"/acc"
+#define LOG_FOLDER              MOUNT_POINT"/"
+//MOUNT_POINT"/accelerometer"
 
 #define CARD_CLK_PIN            14
 #define CARD_CMD_PIN            15
@@ -23,8 +25,8 @@
 #define SENSOR_MISO             13
 #define SENSOR_MOSI             16
 #define SENSOR_CLK              4
-#define SENSOR_CS               36
-#define SENSOR_INT1             5
+#define SENSOR_CS               5
+#define SENSOR_INT1             36
 #define SPI_BUS_FREQUENCY       SPI_MASTER_FREQ_8M
 #define FIFO_WATERMARK          256
 #define SPI_BUS                 SPI3_HOST
@@ -32,7 +34,7 @@
 
 sdmmc_card_t *storage_enable(const char *mount_point);
 void storage_disable(sdmmc_card_t *card, const char *mount_point);
-FILE *create_recording(const char *path);
+void get_recording_filename(char *filename, const char *path);
 
 void switch_enable(bool on, gpio_isr_t isr_handler);
 void switch_disable(void);

### 2024-01-03 recorder/firmware/main/src/hid.c

@@ -4,11 +4,11 @@
 void switch_enable(bool on, gpio_isr_t isr_handler)
 {
     gpio_config_t pin = {
-        .intr_type = on ? GPIO_INTR_NEGEDGE: GPIO_INTR_POSEDGE,
+        .pin_bit_mask = (1ULL << RECORD_SWITCH_PIN),
         .mode = GPIO_MODE_INPUT,
-        .pin_bit_mask = (1 << RECORD_SWITCH_PIN),
         .pull_down_en = GPIO_PULLDOWN_DISABLE,
-        .pull_up_en = GPIO_PULLUP_DISABLE
+        .pull_up_en = GPIO_PULLUP_DISABLE,
+        .intr_type = on ? GPIO_INTR_NEGEDGE: GPIO_INTR_POSEDGE
     };
     gpio_config(&pin);
     gpio_isr_handler_add(RECORD_SWITCH_PIN, isr_handler, NULL);
@@ -24,7 +24,7 @@ void led_enable(void)
 {
     gpio_config_t pin = {
         .mode = GPIO_MODE_OUTPUT,
-        .pin_bit_mask = (1 << RECORD_LED_PIN)
+        .pin_bit_mask = (1ULL << RECORD_LED_PIN)
     };
     gpio_config(&pin);
 }

### 2024-01-03 recorder/firmware/main/src/sensor.c

@@ -98,7 +98,7 @@ void sensor_int_threshold_enable(stmdev_ctx_t *dev, gpio_isr_t isr_handler)
     gpio_config_t interrupt_pin = {
         .intr_type = GPIO_INTR_POSEDGE,
         .mode = GPIO_MODE_INPUT,
-        .pin_bit_mask = (1 << SENSOR_INT1),
+        .pin_bit_mask = (1ULL << SENSOR_INT1),
         .pull_down_en = GPIO_PULLDOWN_DISABLE,
         .pull_up_en = GPIO_PULLUP_DISABLE
     };
@@ -114,7 +114,6 @@ void sensor_int_threshold_disable(void)
 
 void sensor_read(stmdev_ctx_t *dev, FILE *output)
 {
-    static char row[MAX_FILENAME];
     static iis3dwb_fifo_out_raw_t fifo_data[FIFO_WATERMARK];
 
     iis3dwb_fifo_status_t fifo_status;
@@ -132,20 +131,17 @@ void sensor_read(stmdev_ctx_t *dev, FILE *output)
                 int16_t *y = (int16_t *)&sample->data[2];
                 int16_t *z = (int16_t *)&sample->data[4];
             
-                snprintf(row, MAX_FILENAME, "%d\t%4.2f\t%4.2f\t%4.2f\r\n",
+                fprintf(output, "%d\t%4.2f\t%4.2f\t%4.2f\r\n",
                         k,
                         iis3dwb_from_fs2g_to_mg(*x),
                         iis3dwb_from_fs2g_to_mg(*y),
                         iis3dwb_from_fs2g_to_mg(*z));
-
                 // [mg] units
-                fputs(row, output);
                 break;
             case IIS3DWB_TIMESTAMP_TAG:
                 int32_t *ts = (int32_t *)&sample->data[0];
-                snprintf(row, MAX_FILENAME, "%d\t%ld\r\n", k, *ts);
+                fprintf(output, "%d\t%ld\r\n", k, *ts);
                 // [ms] units
-                fputs(row, output);
                 break;
             default:
                 break;

### 2024-01-03 recorder/firmware/main/src/storage.c

@@ -8,16 +8,18 @@
 #include "driver/sdmmc_host.h"
 #include "pinout.h"
 
+static const char *TAG = "sd";
+
 
 sdmmc_card_t *storage_enable(const char *mount_point)
 {
     esp_vfs_fat_sdmmc_mount_config_t mount = {
-        .format_if_mount_failed = true,     // Set to false
+        .format_if_mount_failed = true,    // Set to false
         .max_files = 5,                     // Maximum number of opened files
         .allocation_unit_size = 16 * 1024   // Useful only for format
     };
 
-    sdmmc_slot_config_t slot = SDMMC_SLOT_CONFIG_DEFAULT();  // TODO: SDMMC_HOST_SLOT_1
+    sdmmc_slot_config_t slot = SDMMC_SLOT_CONFIG_DEFAULT();
     slot.width = 1;
 
     sdmmc_card_t *card;
@@ -26,17 +28,15 @@ sdmmc_card_t *storage_enable(const char *mount_point)
 
     if (ret != ESP_OK) {
         if (ret == ESP_FAIL) {
-            // Failed to mount filesystem
+            ESP_LOGE(TAG, "Failed to mount filesystem");
         } else {
-            // Failed to initialize the card
+            ESP_LOGE(TAG, "Failed to initialize the card");
         }
         return NULL;
     }
 
-    // Card has been initialized, print its properties
-    // sdmmc_card_print_info(stdout, card);
-    // Format FATFS
-    // ret = esp_vfs_fat_sdcard_format(mount_point, card);
+    // DEBUG: Card has been initialized, print its properties
+    sdmmc_card_print_info(stdout, card);
 
     return card;
 }
@@ -48,11 +48,11 @@ void storage_disable(sdmmc_card_t *card, const char *mount_point)
 
 static unsigned long get_new_recording_name(const char *path) 
 {
-    uint32_t seq = 1;
+    uint32_t seq = 0;
     char filename[MAX_FILENAME];
 
-    DIR *folder = opendir(path);
-    if (folder == NULL)
+    DIR *folder = opendir(path);        // Needs trailing slash
+    if (folder == NULL) 
         return seq;
     
     struct dirent *entry;
@@ -71,19 +71,11 @@ static unsigned long get_new_recording_name(const char *path)
     }
         
     closedir(folder);
-    return seq;
+    return seq + 1;
 }
 
-FILE *create_recording(const char *path)
[…]

### 2024-03-11 iit-src/paper.tex
Change two time domain features and reevaluate

\documentclass{llncs}

\usepackage{graphicx}
\usepackage{caption}
%\usepackage[caption=false]{subfig}
\usepackage[english]{babel}

\begin{document}

\title{Feature selection in fault detection for predictive maintenance of rotating machinery}
%
\titlerunning{NeurAI}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
	Miroslav Hájek\thanks{Master study programme in field: Informatics Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava }
}

\institute{Faculty of Informatics and Information Technologies STU in Bratislava\\
\email{xhajekm@stuba.sk}}

\maketitle

\begin{abstract}

what is reasearch about
what was shown in previous studies
new methods
findings

\keywords{keyword  \and keyword \and keyword \and keyword}
\end{abstract}

\section{Introduction}

\section{Innovative approachs}

%\begin{figure}[t]
%\centering
%\subfloat{
%	\includegraphics[width=0.45\textwidth]{app.png}
%}
%\subfloat{
%	\includegraphics[width=0.45\textwidth]{mri.png}
%}
%\caption{Patients list and MRI viewer}
%\end{figure}

\section{Summary}

\begin{thebibliography}{1}

\bibitem{example}
Author, F., Author, S.: Title of a proceedings paper. In: Editor,
F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
Springer, Heidelberg (2016). \doi{10.10007/1234567890}

\end{thebibliography}
\end{document}

### 2024-03-11 thesis/chapters/02-analysis-A-CdM.tex
Change two time domain features and reevaluate

@@
 \hline
-\textbf{\begin{tabular}[c]{@{}c@{}}Vibration velocity\\ RMS {[}mm/s{]}\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class I\\ Small machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class II\\ Medium machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class III\\ Large machines\\ Rigid supports\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class IV\\ Large machines\\ Flexible support\end{tabular}} \\ \hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Vibration velocity\\ rms {[}mm/s{]}\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class I\\ Small machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class II\\ Medium machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class III\\ Large machines\\ Rigid supports\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class IV\\ Large machines\\ Flexible support\end{tabular}} \\ \hline
 0.28                                                                                 & \cellcolor[HTML]{9AFF99}                                                  & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1}
@@
 
-Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with RMS velocity 0.1 - 100~mm/s.
+Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with rms velocity 0.1 - 100~mm/s.
 Bearings and gear diagnosis may push the upper-frequency limit even higher.

### 2024-03-11 thesis/chapters/02-analysis-B-features.tex
Change two time domain features and reevaluate

@@
 The vibration severity metrics out of technical standards are also highly regarded.
-The characteristics of amplitude include root-mean-square, peak-to-peak distance, and maximum~\cite{mostafavi_novel_2021}.
+The amplitude characteristics include root-mean-square and peak-to-peak distance~\cite{mostafavi_novel_2021}.
+The waveform shape is captured by zero-crossing rate and average amplitude change~\cite{moctar_time-domain_2023}.
 
-The other significant time-domain attributes are derived as ratios of previous simpler ones.
-These ratios are crest factor, margin factor, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
-Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest factor, and margin indicators \cite{brito_fault_2021}.
+The other significant time domain attributes are derived as ratios of previous simpler ones.
+These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
+Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor \cite{brito_fault_2021}.
 It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.
@@
 \renewcommand{\arraystretch}{2}
-\begin{adjustbox}{width=\columnwidth,center}
 \begin{tabular}{|l|l|l|l|}
 \hline
-\textbf{Feature}            & \textbf{Equation}                                                                    & \textbf{Feature}        & \textbf{Equation}                                                                                                  \\ \hline
-\textit{Standard deviation} & $ X_\sigma = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{\left(x_i - \bar{x}\right)^2}} $        & \textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                       \\ \hline
-\textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$ & \textit{Margin factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $                          \\ \hline
-\textit{Kurtosis}           & $ X_{kv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^4}$ & \textit{Impulse factor} & $ X_{if} = \frac{max(|x_i|)}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}} $                                                  \\ \hline
-\textit{Root mean square}   & $ X_{rms} = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}} $             & \textit{Shape factor}   & $ X_{sf} = \frac{X_{rms}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$ \\ \hline
-\textit{Peak-to-peak}       & $ X_{ppv} = \max(x_i) - \min(x_i) $                                                  & \textit{Maximum}        & $ X_{max} = \max(|x_i|) $                                                                                          \\ \hline
+\textbf{Feature}            & \textbf{Equation}                                                                    \\ \hline
+\textit{Peak-to-peak}       & $ X_{ppv} = \max(x_i) - \min(x_i) $               
+\\ \hline
+\textit{Zero-crossing rate} & $X_{zc} = \frac{1}{N}\sum_{i = 1}^{N}{\mathrm{sgn}(x_i \cdot x_{i-1})} $
+\\ \hline
+\textit{Root mean square}   & $ X_{rms} = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}} $ 
+\\ \hline
+\textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$      
+\\ \hline
+\textit{Kurtosis}           & $ X_{kv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^4}$                                           
+\\ \hline
+\textit{Shape factor}   & $ X_{sf} = \frac{X_{rms}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$  
+\\ \hline
+\textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                           \\ \hline
+\textit{Impulse factor} & $ X_{if} = \frac{max(|x_i|)}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}} $                                                 
+\\ \hline       
+\textit{Clearance factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $ 
+\\ \hline
+\textit{Average Amplitude Change (AAC)}        & $ X_{AAC} = \frac{1}{N}\sum_{i = 1}^{N - 1}{|x_{i + 1} - x_i|} $                             \\ \hline
 \end{tabular}
-\end{adjustbox}
 \caption{Temporal domain features}
@@
 \centering
-\begin{adjustbox}{width=\columnwidth,center}
 \begin{tabular}{|l|l|}
@@
 \textit{Spectral roll-on} & $ E(f_c) = 0.05 \cdot E(f_s / 2) $ \\ \hline                    
-\textit{Spectral roll-off} & $ E(f_c) = 0.95 \cdot E(f_s / 2) $                                                   \\ \hline
+\textit{Spectral roll-off} & $ E(f_c) = 0.85 \cdot E(f_s / 2) $                                                   \\ \hline
 \textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \mathrm{corr}(A_{t-1}, A_t)$ \\ \hline 
@@
 \end{tabular}
-\end{adjustbox}
 \caption{Frequency domain features}

### 2024-03-11 thesis/chapters/03-design.tex
Change two time domain features and reevaluate

@@
 The feature is not added to the subset when the threshold is exceeded.
-High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{std, rms\}, \{pp, max\}, \{crest, margin\}, \{impulse, std\}, \{impulse, rms\}.
+High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}.
 In the spectral domain set \{skewness, kurtosis\} has a strong correlation.
-
-It is assumed that data points spread throughout each dimension of the feature space could distinguish groups well.
-The variables that are the best explained after min-max scaling total dataset variance in the temporal domain are shape (29\%), rms, std, max, and p-p (each around 15\%).
-In the spectral domain, variance is best explained by roll-off (28\%), entropy, skewness, centroid, and kurtosis (each around 12\%).
 
@@
 \ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
-The first PC in the temporal domain focuses more on the amplitude range: \emph{max, rms, pp, std}.
-The second PC mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, margin}.
+The first PC in the temporal domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing}.
+The second PC focuses more on the amplitude range: \emph{rms, p-p, aac}.
 
@@
 \item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
-\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly60'', ``anomaly90'' against which similarity is judged,
+\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly90'' against which similarity is judged,
 \item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
@@
 The results of approval voting are shown in Figure~\ref{fig:design:approval-rating-features}.
-The most occurring attributes in the temporal domain are peak-to-peak, shape, and crest, and in the spectral domain, those are centroid, roll-off, and roll-on.
+The most occurring attributes in the temporal domain are zero-crossing rate, peak-to-peak distance, and average amplitude change.
+the features dominating in the spectral domain are centroid, roll-off, and roll-on.
 
@@
 We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets.
-The KNN classifier being a lazy learner means it can be adapted easily from offline to online context.
+The k-NN classifier being a lazy learner means it can be adapted easily from offline to online context.
 Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values.
 Voronoi diagrams can display these regions and explain the model in that way.
-Batch learning in KNN serves here as a target performance whose attainment is desirable with online learning.
+Batch learning in k-NN serves here as a target performance whose attainment is desirable with online learning.
 
 \subsection{Batch models}
-Three types of KNN model experiments run with hold-out validation in a batch setting.
+Three types of k-NN model experiments run with hold-out validation in a batch setting.
 First, the model learns all extracted features, so no feature selection occurs.
@@
     \end{subfigure}
-    \caption{Confusion matrix of KNN predictions on bearing position A}
+    \caption{Confusion matrix of k-NN predictions on bearing position A}
     \label{fig:design:KNN-confusion-matrix}
@@
                                                                                      &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
-\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9413}                                                               & \multicolumn{1}{r|}{0.9093}                                                              & 0.91                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9668}                                                               & \multicolumn{1}{r|}{0.9535}                                                              & 0.96                                                                                      & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
-\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.8634}                                                               & \multicolumn{1}{r|}{0.7935}                                                              & 0.79                                                                                      & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9148}                                                               & \multicolumn{1}{r|}{0.8668}                                                              & 0.87                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
+\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9859}                                                               & \multicolumn{1}{r|}{0.9736}                                                              & 0.97                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
+                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9869}                                                               & \multicolumn{1}{r|}{0.9800}                                                              & 0.98                                                                                     & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
+\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9316}                                                               & \multicolumn{1}{r|}{0.8969}                                                              & 0.90                                                                                     & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9}
+                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9568}                                                               & \multicolumn{1}{r|}{0.9273}                                                              & 0.93                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
 \end{tabular}
 \end{adjustbox}
-\caption{KNN model performance trained on all extracted features}
+\caption{k-NN model performance trained on all extracted features}
 \label{tab:design:all-extracted-features}
@@
 Binary classification of anomalies is unsurprisingly more precise in general than the multi-class case.
-Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 87\% for bearing B.
+Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 90\% for bearing B.
 
 Next, we exhaustively list all combinations of three features and look at the range of model performances generated.
-There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate KNN models for temporal domain features and 165 for the spectral domain.
+There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate k-NN models for temporal domain features and 165 for the spectral domain.
 The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
-The accuracy of the KNN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
+The accuracy of the k-NN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
 
@@
     \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.8\textwidth}
         \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
@@
     \hfill
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.8\textwidth}
         \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
@@
     \end{subfigure}
-    \caption{Range of prediction accuracy in all KNN models with subset of 3 features. Subplots show three different predicted variables.}
+    \caption{Range of prediction accuracy in all k-NN models with subset of 3 features. Subplots show three different predicted variables.}
     \label{fig:design:feature-combinations-KNN}
@@
 \multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, skewness, shape\}         & 0.9559                & 0.9328               \\ \cline{3-6}
+\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{zero-crossing, aac, rms\}         & 0.9843                & 0.9792 \\ \cline{3-6}
                    &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, shape\}         & 0.9106                & 0.8591 \\ \cline{3-6} 
+                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}         & 0.9701  & 0.9475 \\ \cline{3-6} 
                    &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{std, kurtosis, pp\}            & 0.9085                & 0.8551               \\ \cline{3-6}
+\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{zero-crossing, aac, rms\}            & 0.9570                & 0.9227 \\ \cline{3-6}
                    &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{std, skewness, kurtosis\}      & 0.8369                & 0.7654 \\ \cline{3-6} 
+                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}     & 0.9173 & 0.8738 \\ \cline{3-6} 
                    &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
@@
 The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}.
-Their prediction accuracies in KNN models are subpar to optimal sets.
+Their prediction accuracies in k-NN models are subpar to optimal sets.
 However, the advantage is that the feature election process is not so computationally taxing.
@@
 \multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{shape, std, rms\}               & 0.9333                                       & 0.8916                                      \\ \cline{3-6}
+\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{zero-crossing, rms, shape\}              & 0.9743 &	0.9633 \\ \cline{3-6}
                    &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{std, shape, max\}               & 0.9048                                       & 0.8544                                      \\ \cline{3-6}
+                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, rms, shape\}               & 0.9592 & 0.9274                                     \\ \cline{3-6} 
                    &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{std, shape, crest\}             & 0.8961                                       & 0.8505                                      \\ \cline{3-6}
+\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        &             \{zero-crossing, rms, shape\} & 0.9265	 & 0.8835                \\ \cline{3-6}
                    &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{pp, crest, skewness\}           & 0.8194                                       & 0.7380                                      \\ \cline{3-6}
+                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, p-p, aac\}           & 0.9113 &	0.8614                                      \\ \cline{3-6} 
                    &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
@@
 \end{adjustbox}
-\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated KNN accuracies.}
+\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated k-NN accuracies.}
 \label{tab:design:best-3-features-KNN}
@@
 
-Model performance of the KNN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
+Model performance of the k-NN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
 The best combination of 3 features always achieves better than when the model is trained on all features.
@@
     \end{subfigure} 
-    \caption{Batch KNN algorithm prediction accuracy with various feature sets.}
+    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
     \label{fig:design:KNN-accuracy-batch}
@@
 
-The KNN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context.
+The k-NN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context.
 In this manner, we can compare the training accuracies in the last sample for both models.
-KNN is set to 5 nearest neighbors and a proximity metric of Euclidian distance.
+k-NN is set to 5 nearest neighbors and a proximity metric of Euclidian distance.
 Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
@@
 The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
-The training accuracies of comparable batch models are 94.13\% \emph{(temporal features)} and 99.17\% \emph{(spectral features)}.
+The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.
 
@@
 
-Accuracies after sequentially seeing all samples are 82.92\% \emph{(temporal)} and 89.11\% \emph{(spectral)} when labels are shown instantly.
+Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly.
 Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
-Labeling delay of 250 observations causes accuracy to drop to 70.51\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
-Accuracy better than 50\% is achieved 200 steps sooner in the spectral domain than in the temporal domain.
+Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
 
@@
 Labels for the whole previous window are supplied at once.
-In the final sample, the accuracies are 83.41\% \emph{(temporal)} and 90.14\% \emph{(spectral)} with immediate feedback, and 77.95\% \emph{(temporal)} and 85.90\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
+In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
 
@@
 
-Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.77\% to 74.07\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
-Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\%.
-The same cannot be said about the model from temporal features with very poor accuracy of 53.68\%.
+Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
+Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.
 More missing labels require recording more observations before the equivalent accuracy is reached.

### 2024-03-11 thesis/chapters/04-implementation.tex
Change two time domain features and reevaluate

@@
 It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
-Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.
 
@@
 Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
-Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.
 
@@
 The electric motor provides 400~kW of power (class~\rom{3}).
-The outer bearing on the pump vibrates with an acceleration of $\pm 5 \;\mathrm{m/s}^2$.
 
@@
 \textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
-\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
+\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 - 16      \\ \hline
 \textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
-\textbf{Sensitivity} (mg/LSB)                    & 2.930            & 0.061       \\ \hline
+\textbf{Sensitivity} (mg/LSB)                    & 2.93            & 0.06 - 0.49       \\ \hline
 \textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
@@
 
-\section{Preliminary measurements}
-During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
-Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
-The acceleration rarely exceeds 1~g.
+\section{Firmware}
+% Timing is crutial 19ms.
+Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
 
-In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz).
-The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
+\begin{itemize}
+\itemsep0pt
+\item begin new recording, 
+\item log block of samples into CSV file,
+\item finish recording.
+\end{itemize}
 
@@
     \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-        \caption{Acceleration in $\mathrm{m/s}^2$}
-        \label{fig:design:preliminary-acceleration}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
-        \caption{Approximate velocity in $\mathrm{mm/s}$}
-        \label{fig:design:preliminary-velocity}
-    \end{subfigure} 
-    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
+	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
 \end{figure}
 
-Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
+\section{Dataset description}
+
+\section{BVS cloud}
+
+\section{Compressors}
+
+\section{Water pumps}
+
+%\section{Preliminary measurements}
+%During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
+Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
+The acceleration rarely exceeds 1~g.
+%
+%In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz).
+The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
+%
+%
+%\begin{figure}[h]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
+%        \caption{Acceleration in $\mathrm{m/s}^2$}
+%        \label{fig:design:preliminary-acceleration}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
+%        \caption{Approximate velocity in $\mathrm{mm/s}$}
+%        \label{fig:design:preliminary-velocity}
+%    \end{subfigure} 
+%    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
+%\end{figure} 
+%
+%Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
 The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks.
@@
 The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
-		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
-		\label{fig:design:orbital-analysis}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.54\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
-        \label{fig:design:preliminary-spectrum}
-    \end{subfigure} 
-    \caption{Orbital and spectral methods of vibration signal analysis}
-\end{figure}
+%
+%\begin{figure}[h]
+%    \centering
+%    \begin{subfigure}[b]{0.45\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
+%		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
+%		\label{fig:design:orbital-analysis}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.54\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
+%        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
+%        \label{fig:design:preliminary-spectrum}
+%    \end{subfigure} 
+%    \caption{Orbital and spectral methods of vibration signal analysis}
+%\end{figure}

### 2024-03-11 thesis/chapters/appendix/A-resume.tex
BVS cloud analysis for last year
Change two time domain features and reevaluate

@@
 Symptómy porúch rotačných strojov sa prejavujú rôznymi frekvenčnými pásmami, ale väčšina je závislá od rotačnej rýchlosti súčiastky.
-Nevyváženosť, nevyváženosť a vôľa sa bežne objavujú v frekvenciách do 300 Hz.
+Nevyváženosť, nesúosovosť a vôľa sa bežne objavujú v frekvenciách do 300 Hz.
 Poruchy ložísk a prevodovky v neskorých štádiách vývoja sa prejavujú v rozsahu medzi 300 Hz a 1 kHz.
@@
 Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
-Algoritmus k-najbližších susedov (KNN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
+Algoritmus k-najbližších susedov (k-NN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
 Nachádza uplatnenie aj v učení čiastočne s učiteľom, pretože dokáže odvodiť označenia len zo znalosti niekoľkých anotácií.
@@
 
-Tri typy experimentov s modelom KNN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
+Tri typy experimentov s modelom k-NN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
 Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou.
 Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov.
-Dávkový model KNN slúži ako referenčný, podľa ktorého sa posudzuje KNN v postupnom učení.
+Dávkový model k-NN slúži ako referenčný, podľa ktorého sa posudzuje k-NN v postupnom učení.
 
@@
 Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie.
-Modely KNN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi.
+Modely k-NN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi.
 Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie.
-KNN sme nastavili na 5 susedov a euklidovskú vzdialenosť.
+k-NN sme nastavili na 5 susedov a euklidovskú vzdialenosť.
 Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.
@@
 Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
-Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť KNN modelu oproti metrikám samostatne.
+Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne.
 Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%.
-Trénovanie KNN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
+Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
 
-Model postupného učenia kNN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
+Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
 Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.

### 2024-03-11 thesis/chapters/appendix/B-plan-of-work.tex
Change two time domain features and reevaluate

@@
  \\ \hline
-\nth{6} week         & Feature selection used in KNN multiclass and binary classificator.
+\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
  \\ \hline
-\nth{7} week         & Explore incremental learning KNN algorithm with MaFaulDa dataset. Consultation and status report.
+\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
  \\ \hline
@@
  \\ \hline
- \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for kNN validation. Consultation to discuss progress.
+ \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
  \\ \hline
@@
 \item Find optimal number of features. 
-\item Try to increase KNN prediction metrics.
+\item Try to increase k-NN prediction metrics.
 \item Put together incremental learning with feature selection. 

### 2024-03-11 thesis/chapters/preliminaries/annotation.tex
Change two time domain features and reevaluate

@@
 
-The progress report in Master's thesis project \rom{2} deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.
+Master's thesis deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.
 
@@
 
-Priebežná správa o riešení DP2 sa zaoberá monitorovaním stavu rotačných strojov a ich prediktívnou údržbou prostredníctvom techník výberu atribútov a štatistickej klasifikácie.
+Diplomová práca sa zaoberá monitorovaním stavu rotačných strojov a ich prediktívnou údržbou prostredníctvom techník výberu atribútov a štatistickej klasifikácie.
 

### 2024-03-11 firmware/main/src/sensor.c

@@ -81,8 +81,9 @@ int sensor_enable(spi_device_handle_t *spi_dev, stmdev_ctx_t *dev)
 
     iis3dwb_block_data_update_set(dev, PROPERTY_ENABLE);
 
-    // Resolution: 2g
-    iis3dwb_xl_full_scale_set(dev, IIS3DWB_2g);
+    // Resolution: 4g
+    iis3dwb_xl_full_scale_set(dev, IIS3DWB_4g);
+    // iis3dwb_xl_full_scale_set(dev,  IIS3DWB_16g);
 
     iis3dwb_fifo_watermark_set(dev, FIFO_WATERMARK);
     iis3dwb_fifo_xl_batch_set(dev, IIS3DWB_XL_BATCHED_AT_26k7Hz);

### 2024-03-11 notebooks/vibrodiagnostics/datasets.py

@@ -6,6 +6,43 @@ from tqdm.notebook import tqdm
 from multiprocessing.pool import ThreadPool
 
 
+def steval_files(path: str):
+    dataset = []
+    for root, subdirs, files in os.walk(path):
+        for filename in files:
+            if filename.lower().endswith('.tsv'):
+                dataset.append(os.path.join(root, filename))
+    return dataset
+
+
+def steval_measurement(filename: str, fs: int=26866) -> Tuple[str, pd.DataFrame]:
+    g = 9.81
+    columns = ['x', 'y', 'z']
+    ts = pd.read_csv(
+        filename,
+        delimiter='\t',
+        index_col=False,
+        header=0,
+        names=['t'] + columns
+    )
+
+    for dim in columns:
+        ts[dim] -= ts[dim].mean()
+        ts[dim] = g * (ts[dim] / 1000)
+
+    ts['t'] = ts.index * (1 / fs)
+    ts.set_index('t', inplace=True)
+    return (os.path.basename(filename), ts, fs, ts.columns)
+
+
+def steval_dataset(filenames: List[str], fs: int) -> List[Tuple[str, pd.DataFrame]]:
+    dataset = []
+    for filename in sorted(filenames, key=lambda x: int(os.path.basename(x).split('.')[0])):
+        name, ts, fs, cols = steval_measurement(filename, fs)
+        dataset.append((filename, ts))
+    return dataset
+
+
 def beaglebone_measurement(filename: str, fs: int=2500) -> Tuple[str, pd.DataFrame]:
     g = 9.81
     milivolts = 1800
@@ -28,30 +65,6 @@ def beaglebone_dataset(filenames: List[str]) -> List[Tuple[str, pd.DataFrame]]:
     dataset = []
     for filename in filenames:
         name, ts, fs, cols = beaglebone_measurement(filename)
-        dataset.append((name, ts))
-    return dataset
-
-
-def icomox_measurement(filename: str, fs: int) -> Tuple[str, pd.DataFrame]:
-    g = 9.81
-    ts = pd.read_csv(filename, delimiter=',', index_col=False)
-    ts = ts.rename(columns={'aX': 'x', 'aY': 'y', 'aZ': 'z'})
-    ts['t'] /= 1000
-    # print('FS:', 1 / (ts['t'] - ts['t'].shift(1)).mean())
-    ts.set_index('t', inplace=True)
-
-    # Convert amplitude from g to m/s^2
[…]

### 2024-03-11 notebooks/vibrodiagnostics/discovery.py

@@ -51,21 +51,21 @@ def lowpass_filter_extract(dataframe: pd.DataFrame, columns) -> pd.DataFrame:
 def time_features_calc(df: pd.DataFrame, col: str) -> List[Tuple[str, pd.DataFrame]]:
     x = df[col]
     features = [
-        ('std', [ft.calc_std(x)]),
+        ('zerocross', ft.zero_cross(x) / len(x)),
+        ('pp', [ft.pk_pk_distance(x)]),
+        ('aac', np.mean(np.absolute(np.diff(x)))),
+        ('rms', [ft.rms(x)]),
         ('skewness', [ft.skewness(x)]),
         ('kurtosis', [ft.kurtosis(x)]),
-        ('rms', [ft.rms(x)]),
-        ('pp', [ft.pk_pk_distance(x)]),
-        ('crest', [np.max(np.absolute(x)) / ft.rms(x)]),
-        ('margin', [np.max(nplot_label_occurencesp.absolute(x)) / (np.mean(np.sqrt(np.absolute(x))) ** 2)]),
-        ('impulse', [np.max(np.absolute(x)) / np.mean(np.absolute(x))]),
         ('shape', [ft.rms(x) / np.mean(np.absolute(x))]),
-        ('max', [ft.calc_max(x)])
+        ('crest', [np.max(np.absolute(x)) / ft.rms(x)]),
+        ('impulse', [np.max(np.absolute(x)) / np.mean(np.absolute(x))]),
+        ('clearance', [np.max(np.absolute(x)) / (np.mean(np.sqrt(np.absolute(x))) ** 2)]),
     ]
     return [(f'{col}_{f[0]}', f[1]) for f in features]
 
-def frequency_features_calc(df: pd.DataFrame, col: str, window: int) -> List[Tuple[str, pd.DataFrame]]:
-    f, pxx = spectral_transform(df, col, window)
+def frequency_features_calc(df: pd.DataFrame, col: str, window: int, fs: int) -> List[Tuple[str, pd.DataFrame]]:
+    f, pxx = spectral_transform(df, col, window, fs)
     
     fluxes = temporal_variation(df, col, window)
     envelope_spectrum = envelope_signal(f, pxx)
@@ -361,12 +361,12 @@ def envelope_signal(f: np.array, Pxx: np.array) -> np.array:
     return y_env
 
 
-def spectral_transform(dataset: pd.DataFrame, axis: str, window: int) -> (np.array, np.array):
[…]

### 2024-03-16 iit-src/paper.tex
Feature extraction for both mafaulda and fluid pumps

@@
 
-\title{Feature selection in fault detection for predictive maintenance of rotating machinery}
-%
-\titlerunning{NeurAI}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
+% 4 pages (5 pages with sources)
+\title{Feature selection in fault classification of rotating machinery}
+
+\titlerunning{Features for machinery faults}
+
 \author{
-	Miroslav Hájek\thanks{Master study programme in field: Informatics Supervisor: Dr.
-Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava }
+	Miroslav Hájek\thanks{Master study programme in field: Informatics
+	Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava }
 }
@@
 \section{Introduction}
+- predictive maintance, research question
 
-\section{Innovative approachs}
+Related work (citations)
+
+existence of standards
+domain - time, frequency, time-frequency
+feature extraction techniques
+feature selection techniques
+classification of faults
+datasets: mafaulda, cwru, rotating shaft
+Raw - KSB Cloud - BVS pumps
+!!! CITE do not describe !!!
+
+\section{Methodology}
+
+Mafaulda
+1. Signal processing (choose bearing A)
+2. Labeling - 6 classes (Class balancing by oversampling)
+3. Feature extraction - Time domain, Frequency domain - Min-max scaling before PCA
+4. Feature selection - 
+	PCA 2,3,4 - accuracy + loading plot (PC2)
+	KNN all features- 5-fold cross validation - rôzne domény, rôzne k, rôzne počty features
+	KNN exhaustive models - 
+		2,3,4 features (check corr, f-stat, mi, rank product scores)
+	 -> KNN classification(online and offiline)
+
+Custom dataset
+1. Choice of machines (pic measurement places - two images and dots)
+2. HW sensor + ESP32 + FW 60 s. recor
+3. How measure (plan)
+4. Signal processing
+4. Labeling  / Labeling (use machine - split by type) 
+5. Same as Mafaulda
+
+acc = prec micro = recall micro
+
+\section{Results}
+
+Figures:
+
+Signal analysis
+- 1ks obr. Mafaulda ABVT simulator
+- 1ks plot (histogram of td signal)?
+- 1ks plot (6x subplots) Mafaulda welch from each fault (1s, 2**14 window, hann window)  - largest severity - 2500 rpm
+- 1ks plot (6x subplots) Custom dataset - each place in one day spectrum (5s segment)
+
+Feature analysis:
+Mafaulda (3) a Custom (4) 
+- 1 ks table (how many faults have how many recordings)
+- 1 ks plot (2 lines TD, FD) - numer of PC vs. explained variance
+- 1 ks plot (2x subplots TD, FD) - loading plot (PC2)
+- 1 ks (4 subplots) custom: all machines, pumps, compressors, motors
+
+Classification accuracy (choices of k. and feat. count, 5-fold cross validation)
+
+For mafaulda and custom (which classes - all or just one machine)
+- 1 ks All features (2x subplots TD, FD)
+	- Each subplot boxplot (k = 3,5,7)
+
+All models (exhausive) - draw rank, corr, f-stat, mi as horizontal line
+	- 3 ks plots (2, 3, 4 features)
+		- Each plot 2 boxplot subplots (TD, FD) - k-neigh. vs. accuracy of all models
+
+Compare accuracies of best models in each categories for given number of features and k:
+- 1 ks plot - bar chart - color rainbow - one x (td), second x (fd)
+
+\section{Summary}
+
+\section{References}
 
@@
 
-\section{Summary}
-
 \begin{thebibliography}{1}

### 2024-03-16 bin2csv.py

@@ -1,42 +1,0 @@
-import struct
-import os
-import argparse
-
-
-parser = argparse.ArgumentParser()
-parser.add_argument('path', type=str, help='Folder with .bin files')
-parser.add_argument('res', type=int, help='Resolution in g') # default is 4g, sigma is 16g 
-args = parser.parse_args()
-print(f'Path: "{args.path}"')
-
-fmt = 'iiii'
-struct_len = struct.calcsize(fmt)
-struct_unpack = struct.Struct(fmt).unpack_from
-
-
-for root, subdirs, files in os.walk(args.path):
-    for filename in files:
-        if not filename.lower().endswith('.bin'):
-            continue
-
-        name, ext = os.path.splitext(filename)
-        csvfilename = os.path.join(root, f'{name}.tsv')
-        filename = os.path.join(root, filename)
-        print(filename)
-
-        if args.res == 4:
-            resolution = 0.122  # 4g
-        elif args.res == 16:
-            resolution = 0.488
-
-        with (open(filename, 'rb') as fr,
-            open(csvfilename, 'w') as fw):
-            while True:
-                data = fr.read(struct_len)
-                if not data:
-                    break
-                t, x, y, z = struct_unpack(data)
-                x *= resolution
-                y *= resolution
-                z *= resolution
-                print(f'{t}\t{x:.2f}\t{y:.2f}\t{z:.2f}', file=fw)

### 2024-03-16 consultations/recorder_beaglebone.c

@@ -1,0 +1,259 @@
+/*
+ * debian:temppwd
+ *
+ * scp recorder.c debian@192.168.7.2:/home/debian/recorder.c
+ * ssh debian@192.168.7.2
+ *
+ * FS = 2551 Hz (7.653 kHz / channels)
+ * gcc -Wall -Wextra -O2 recorder.c -o recorder
+ * timeout --signal=SIGINT 10s ./recorder out
+ *
+ * scp debian@192.168.7.2:/home/debian/out.tsv out.tsv
+ *
+ * FILE COLUMNS
+ * x[raw]  y[raw]  z[raw]
+ *
+ * Manuals:
+ * https://elinux.org/EBC_Exercise_10a_Analog_In
+ * https://www.kernel.org/doc/Documentation/ABI/testing/sysfs-bus-iio
+ * https://www.kernel.org/doc/Documentation/devicetree/bindings/input/touchscreen/ti-tsc-adc.txt
+ *
+ * ADC DRIVER: TI-am335x-adc.0.auto
+ * https://github.com/torvalds/linux/blob/master/drivers/iio/adc/ti_am335x_adc.c
+ * https://software-dl.ti.com/processor-sdk-linux/esd/docs/latest/linux/Foundational_Components/Kernel/Kernel_Drivers/ADC.html
+ *
+ * ADC config (Reconfigure driver): set SAMPLING_FREQUENCY accordingly 10 = 4000Hz, 80=3125Hz, 160=2500Hz
+ * cd /opt/source/bb.org-overlays/
+ * vim src/arm/BB-ADC-00A0.dts
+ * make
+ * sudo make install
+ * reboot
+ *
+ * &tscadc {
+        status = "okay";
+        adc {
+            ti,adc-channels = <0 1 2 3 4 5 6 7>;
+            ti,chan-step-opendelay = <160 160 160 160 160 160 160 160>;
+            ti,chan-step-avg = <16 16 16 16 16 16 16 16>;
+            ti,chan-step-sampledelay = <0 0 0 0 0 0 0 0>;
+        }
+    }
+ *
+ */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <signal.h>
+#include <string.h>
+#include <unistd.h>
+#include <fcntl.h>
+#include <sys/time.h>
+#include <sys/timerfd.h>
+#include <inttypes.h>
+
+
+
+#define NS_PER_SECOND       1000000000.0
[…]

### 2024-03-16 notebooks/legacy/experimental.c

@@ -1,170 +1,0 @@
-/*
- * WARNING: very unreliable - not precise sampling frequency - uses sw timer
- * debian:temppwd
- *
- * ssh debian@192.168.7.2
- * gcc sampler.c -o sampler
- *
- * sudo nice -n -20 ./sampler out.tsv
- * scp debian@192.168.7.2:/home/debian/out.tsv out.tsv
- *
- * FILE COLUMNS
- * x[raw]  y[raw]  z[raw]  time_interval[us]
- */
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <signal.h>
-#include <pthread.h>
-#include <string.h>
-#include <unistd.h>
-#include <fcntl.h>
-#include <sys/time.h>
-#include <sys/timerfd.h>
-#include <inttypes.h>
-
-
-#define US_PER_SECOND       1000000
-#define NS_PER_SECOND       1000000000
-// ODR = 500 Hz
-#define FS_HZ               4000
-#define PERIOD_US           (US_PER_SECOND / (double)FS_HZ)
-
-#define ANALOG_IN_PATH      "/sys/bus/iio/devices/iio:device0/"
-#define AIN_CH              3
-
-#define AIN0                ANALOG_IN_PATH "in_voltage0_raw"
-#define AIN1                ANALOG_IN_PATH "in_voltage1_raw"
-#define AIN2                ANALOG_IN_PATH "in_voltage2_raw"
-#define AIN3                ANALOG_IN_PATH "in_voltage3_raw"
-#define AIN4                ANALOG_IN_PATH "in_voltage4_raw"
-#define AIN5                ANALOG_IN_PATH "in_voltage5_raw"
-#define AIN6                ANALOG_IN_PATH "in_voltage6_raw"
-#define BUF_SIZE            8192
-
-    //TickType_t initial_time = 0, end_time = 0;
-    //initial_time = xTaskGetTickCount();
-    //end_time = xTaskGetTickCount();
-    //ESP_LOGW("m", "%lu", end_time - initial_time);
-
-
-// Time events
-int make_periodic(unsigned int period)
-{
-    int fd = timerfd_create(CLOCK_MONOTONIC, 0);
-    if (fd == -1)
-        return fd;
-
-    unsigned int sec = period / 1000000;
-    unsigned int ns = (period - (sec * 1000000)) * 1000;
-
-    struct itimerspec itval;
-    itval.it_interval.tv_sec = sec;
[…]

### 2024-03-16 notebooks/legacy/icomox_parser.py

@@ -1,90 +1,0 @@
-from enum import Enum
-import re
-import os
-import pandas as pd
-import numpy as np
-
-class Parser(Enum):
-    START = 0
-    HEADER = 1
-    DATA = 2
-
-
-class Device(Enum):
-    NO = 0
-    SMALL_ACCEL = 1
-    BIG_ACCEL = 2
-
-
-def csv_process(filename):
-    state = Parser.START
-    device = Device.NO
-    columns = []
-    axis = None
-    records = []
-
-    df_small_accel = pd.DataFrame()
-    df_big_accel = []
-
-
-    with open(filename, 'r') as measurement:
-        for line in measurement:
-            if state == Parser.START:
-                axis = None
-                columns = []
-                records = []
-
-                if line.startswith('ADXL362'):
-                    device = Device.SMALL_ACCEL
-                    state = Parser.HEADER
-
-                elif line.startswith('ADXL356'):
-                    axis = re.findall(r'ADXL356\.(\w):', line)
-                    device = Device.BIG_ACCEL
-                    state = Parser.HEADER
-
-            elif state == Parser.HEADER:
-                columns = re.findall(r'(\w+)\[[^\]]+\]', line)
-                if axis and len(columns) == 2:
-                    columns[-1] += axis[0]
-                print(columns)
-                state = Parser.DATA
-
-
-            elif state == Parser.DATA:
-                if not line.strip():
-                    state = Parser.START
-                    df = pd.DataFrame(records, columns=columns)
-                    if device == Device.SMALL_ACCEL:
-                        df['t'] = df['t'].astype(float) - df['t'].astype(float).shift(1)
-                        df['t'] = df['t'].fillna(0)
-                        df_small_accel = pd.concat([df_small_accel, df])
-
-                    elif device == Device.BIG_ACCEL:
-                        df_big_accel.append(df)
-
-                else:
-                    records.append(re.findall(r'(-?\d+\.\d+)', line))
-
-    X = []
-    for i in range(0, len(df_big_accel), 3):
-        x = df_big_accel[i]
-        x = x.merge(df_big_accel[i+1], on='t')
-        x = x.merge(df_big_accel[i+2], on='t')
-        x['t'] = x['t'].astype(float) - x['t'].astype(float).shift(1)
-        x['t'] = x['t'].fillna(0)
-        X.append(x)
-
-    df_big_accel = pd.concat(X)
[…]

### 2024-03-16 notebooks/vibrodiagnostics/datasets.py

@@ -1,78 +1,0 @@
-import os
-from typing import List, Tuple
-import pandas as pd
-
-from tqdm.notebook import tqdm
-from multiprocessing.pool import ThreadPool
-
-
-def steval_files(path: str):
-    dataset = []
-    for root, subdirs, files in os.walk(path):
-        for filename in files:
-            if filename.lower().endswith('.tsv'):
-                dataset.append(os.path.join(root, filename))
-    return dataset
-
-
-def steval_measurement(filename: str, fs: int=26866) -> Tuple[str, pd.DataFrame]:
-    g = 9.81
-    columns = ['x', 'y', 'z']
-    ts = pd.read_csv(
-        filename,
-        delimiter='\t',
-        index_col=False,
-        header=0,
-        names=['t'] + columns
-    )
-
-    for dim in columns:
-        ts[dim] -= ts[dim].mean()
-        ts[dim] = g * (ts[dim] / 1000)
-
-    ts['t'] = ts.index * (1 / fs)
-    ts.set_index('t', inplace=True)
-    return (os.path.basename(filename), ts, fs, ts.columns)
-
-
-def steval_dataset(filenames: List[str], fs: int) -> List[Tuple[str, pd.DataFrame]]:
-    dataset = []
-    for filename in sorted(filenames, key=lambda x: int(os.path.basename(x).split('.')[0])):
-        name, ts, fs, cols = steval_measurement(filename, fs)
-        dataset.append((filename, ts))
-    return dataset
-
-
-def beaglebone_measurement(filename: str, fs: int=2500) -> Tuple[str, pd.DataFrame]:
-    g = 9.81
-    milivolts = 1800
-    resolution = 2 ** 12
-    columns = ['x', 'y', 'z']
-    ts = pd.read_csv(filename, delimiter='\t', index_col=False, header=None, names=columns)
-        
-    # Calculate amplitude in m/s^2 Beaglebone Black ADC and ADXL335 resolution (VIN 1.8V, 12bits)
-    for dim in columns:
-        ts[dim] = ts[dim] * (milivolts / resolution)  # ADC to mV
-        ts[dim] = (ts[dim] / 180) * g                 # mV to m/s^2 (180 mV/g)
-        ts[dim] -= ts[dim].mean()
-
-    ts['t'] = ts.index * (1 / fs)
-    ts.set_index('t', inplace=True)
-    return (os.path.basename(filename), ts, fs, ts.columns)  # last is feature columns
-
-
[…]

### 2024-03-16 notebooks/vibrodiagnostics/discovery.py

@@ -13,9 +13,7 @@ from scipy.fft import rfft
 from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
 import pywt
 from tsfel import feature_extraction as ft
-
 import matplotlib.pylab as plt
-from vibrodiagnostics import mafaulda
 
 
 
@@ -30,91 +28,13 @@ def split_dataframe(dataframe: pd.DataFrame, parts: int = None) -> List[pd.DataF
         if len(dataframe.iloc[i:i + step]) == step
     ]
 
-def detrending_filter(dataframe: pd.DataFrame, columns: List[str]) -> pd.DataFrame:
-    for df in dataframe:
-        df[columns] = df[columns].apply(lambda x: x - x.mean())
-    return dataframe
 
-
-def butter_bandpass_filter(data, cutoff=10000, fs=mafaulda.FS_HZ, order=5):
+def butter_bandpass_filter(data, cutoff=10000, fs=50000, order=5):
     b, a = butter(order, cutoff, fs=fs, btype='lowpass')
     y = lfilter(b, a, data.to_numpy())
     return pd.Series(data=y, index=data.index)
 
 
-def lowpass_filter_extract(dataframe: pd.DataFrame, columns) -> pd.DataFrame:
-    for df in dataframe:
-        df[columns] = df[columns].apply(butter_bandpass_filter)
-    return dataframe
-
-
-def time_features_calc(df: pd.DataFrame, col: str) -> List[Tuple[str, pd.DataFrame]]:
-    x = df[col]
-    features = [
-        ('zerocross', ft.zero_cross(x) / len(x)),
-        ('pp', [ft.pk_pk_distance(x)]),
-        ('aac', np.mean(np.absolute(np.diff(x)))),
-        ('rms', [ft.rms(x)]),
-        ('skewness', [ft.skewness(x)]),
-        ('kurtosis', [ft.kurtosis(x)]),
-        ('shape', [ft.rms(x) / np.mean(np.absolute(x))]),
-        ('crest', [np.max(np.absolute(x)) / ft.rms(x)]),
-        ('impulse', [np.max(np.absolute(x)) / np.mean(np.absolute(x))]),
-        ('clearance', [np.max(np.absolute(x)) / (np.mean(np.sqrt(np.absolute(x))) ** 2)]),
-    ]
-    return [(f'{col}_{f[0]}', f[1]) for f in features]
-
[…]

### 2024-03-16 notebooks/vibrodiagnostics/mafaulda.py

@@ -1,123 +1,0 @@
-import numpy as np
-import pandas as pd
-import seaborn as sb
-
-from scipy.stats import skew, kurtosis, kstest
-from scipy.fft import rfft
-from scipy.signal import butter, filtfilt, find_peaks
-
-from tqdm.notebook import tqdm
-import matplotlib.pyplot as plt
-from zipfile import ZipFile
-
-from multiprocessing.pool import ThreadPool
-
-FS_HZ = 50000
-DB_REF = 0.000001                                # 1 dB = 1 um/s^2
-COLUMNS = ['ax', 'ay', 'az', 'bx', 'by', 'bz']   # 'mic'
-
-################################# IMPORT ########################################
-
-def parse_filename(filename: str) -> (str, str, str):
-    path = filename.split('/')
-    if path[0].strip() in ('overhang', 'underhang'):
-        fault = f'{path[0]}-{path[1]}'
-        severity = path[2]
-        seq = path[3]
-    elif path[0].strip() == 'normal':
-        fault, severity, seq = path[0], '0', path[1]
-    else:
-        fault, severity, seq = path
-
-    return fault, severity, seq
-
-
-def import_files_split(zip_file, file_list, func, parts, cores=4):
-    pool = ThreadPool(processes=cores)
-    
-    return pd.concat([
-        pool.apply_async(func, (zip_file, name, parts )).get()
-        for name in tqdm(file_list)
-    ])
-
-
-def import_files(zip_file, file_list, func, cores=4):
-    pool = ThreadPool(processes=cores)
-    
-    return pd.concat([
-        pool.apply_async(func, (zip_file, name, )).get()
-        for name in tqdm(file_list)
-    ])
-
-
-def get_mafaulda_files(zip_file):
-    filenames = [
-        text_file.filename
-        for text_file in zip_file.infolist()
-        if text_file.filename.endswith('.csv')
-    ]
-    filenames.sort()
-    return filenames
-
-
-def rpm_calc(tachometer: pd.Series) -> float:
-    t = tachometer.index.to_numpy()
-    y = tachometer.to_numpy()
-    peaks, _ = find_peaks(y, prominence=3, width=50)
-    interval = np.diff(t[peaks]).mean()
-    return 60 / interval
-
-
-def preprocess(ts: pd.DataFrame):
-    return (
-        ts
-        .assign(t = lambda x: x.index * (1 / FS_HZ))
[…]

### 2024-03-17 iit-src/paper.tex
Start creating figures for iit-src article
PCA analysis and load whole feature set

@@
 Figures:
+- 1ks obr. Mafaulda ABVT simulator
+- 1ks obr. (2ks subplots) machine and compressor measurement places with red squares
+- 1 ks obr. device
 
 Signal analysis
-- 1ks obr. Mafaulda ABVT simulator
+
 - 1ks plot (histogram of td signal)?
@@
 Feature analysis:
-Mafaulda (3) a Custom (4) 
+Mafaulda (4) a Custom (4) 
 - 1 ks table (how many faults have how many recordings)
@@
 - 1 ks plot (2x subplots TD, FD) - loading plot (PC2)
-- 1 ks (4 subplots) custom: all machines, pumps, compressors, motors
+
+% TODO
+- 1 ks (5 subplots) scatter: mafaulda, all machines, pumps, compressors, motors
 

### 2024-03-23 iit-src/paper.tex
Remove ANC from thesis and compare accuracies in box plots

@@
 Raw - KSB Cloud - BVS pumps
+
+# analytical - known bearing
+Ball Pass Frequency Outer Race (BPFO)
+Ball Pass Frequency Inner Race (BPFI)
+Ball Spin Frequency (BSF)
+Fundamental Train Frequency (FTF)
 !!! CITE do not describe !!!
@@
 \section{Methodology}
+
+1. Choose frequency precision (1 Hz at maximum)
+2. 12 windows at minimum (n+1 half windows with overlap), Hann window with 50\% overlap, 2^14 - 2^15 windows, 5s recodings
 
@@
 Custom dataset
-1. Choice of machines (pic measurement places - two images and dots)
+1. Choice of machines (pic measurement places - two images and dots) - pumps according to standards + callibrated sensors
+	- compressor is on housing
 2. HW sensor + ESP32 + FW 60 s. recor
@@
 
-For mafaulda and custom (which classes - all or just one machine)
+Whole serach space = For mafaulda and custom (which classes - all or just one machine)
 - 1 ks All features (2x subplots TD, FD)
 	- Each subplot boxplot (k = 3,5,7)
+
+2 features - best models under 55\% accuracy in test set
 
@@
 - 1 ks plot - bar chart - color rainbow - one x (td), second x (fd)
+
+- In training set growing number of neighbors decreases accuracy - in testing set there is no effect (more neighbors more overtraining)
+	- we choose k = 5
+- Number of features increases accuracy
 

### 2024-03-23 thesis/chapters/02-analysis-B-features.tex
Remove ANC from thesis and compare accuracies in box plots

@@
 Cascaded-integrator-comb (CIC) filters are proposed as an alternative instead~\cite{lyons_understanding_2011}.
-
-\subsection{Adaptive noise cancellation}
-Adaptive noise cancellation (ANC) involves an adaptive filter that self-adjusts coefficients through an update algorithm in response to the reference noise signal.
-The objective of this filter is to minimize the mean square error (MSE) cost function in the error signal $e_k$ between signal contaminated with Gaussian noise $d_k$ and filter output $y_k$.
-Additive noise $n_k$ is assumed to be correlated with noise signal $\mathbf{X_k}$~\cite{diniz_adaptive_2020}.
-
-Wiener-Hopf equations solve the optimal gradient of the MSE function and provide us with FIR filter coefficient vector $\mathbf{W_k}$.
-The least mean squares (LMS) algorithm recursively approximates this analytical solution with the method of steepest descent (Equation~\ref{equ:lms-adaptive-filter})~\cite{diniz_adaptive_2020}.
-The multiple parameters are to be considered in the evaluation of filter performance: convergence rate, estimated error, and signal-to-noise ratio (SNR).
-
-\myequations{Adaptive noise filtering LMS update formula}
-\begin{ceqn}\begin{align} \label{equ:lms-adaptive-filter}
-\mathbf{W}_{k+1} = \mathbf{W}_{k} + 2 \mu \mathbf{X}_{k}  e_k
-\end{align}\end{ceqn}
-
-The convergence stability is affected by step size $\mu$ which is bounded from above with the inverse of the maximal eigenvalue of input covariance matrix $\lambda_{max}$.
-The normalized least mean squares (NLMS) can handle input of varying scales  (Equation~\ref{equ:nlms-adaptive-filter}).
-
-\myequations{Adaptive noise filtering NLMS update formula}
-\begin{ceqn}\begin{align} \label{equ:nlms-adaptive-filter}
-\mathbf{W}_{k+1} = \mathbf{W}_{k} + \frac{\mu}{\lVert\mathbf{X}_{k}\rVert^2} \mathbf{X}_{k}  e_k
-\end{align}\end{ceqn}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.8\textwidth]{assets/analysis/adaptive-filter.png}
-	\caption{Adaptive noise cancellation filter diagram}
-	\label{fig:adaptive-filter}
-\end{figure}
-\bigbreak
 

### 2024-03-28 iit-src/paper.tex
Article introduction and part of related work

@@
 \usepackage{graphicx}
+\usepackage{biblatex}
 \usepackage{caption}
@@
 
+\addbibresource{literature.bib}
+
 \begin{document}
 
-% 4 pages (5 pages with sources)
-\title{Feature selection in fault classification of rotating machinery}
-
-\titlerunning{Features for machinery faults}
+\title{Fault classification of rotating machinery using limited set of features}
 
 \author{
-	Miroslav Hájek\thanks{Master study programme in field: Informatics
-	Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava }
+	Miroslav Hájek\thanks{Master study programme in field: Informatics,
+	Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava}
 }
@@
 \begin{abstract}
-
+% https://guides.lib.uci.edu/c.php?g=334338&p=2249908
 what is reasearch about
@@
 \section{Introduction}
-- predictive maintance, research question
+Rotary motion machinery is utilized throughout the industry as motors, pumps, and gearboxes.
+All equipment have bounded productive lifespan because of wear and tear or improper operating conditions.
+Sonner or later, moving elements start to exhibit faults that can lead to failure if left untreated.
 
-Related work (citations)
+Early real-time fault detection can be achieved by monitoring machine vibration levels and signal frequency content~\cite{ziaran_technicka_2013}.
+Sensors for vibrations are piezoelectric or MEMS wideband accelerometers.
+Data acquisition procedures and best evaluation practices are standardized in ISO~20816~\cite{noauthor_iso_2016} and ISO~13373~\cite{noauthor_iso_2002}.
 
-existence of standards
-domain - time, frequency, time-frequency
-feature extraction techniques
-feature selection techniques
-classification of faults
-datasets: mafaulda, cwru, rotating shaft
-Raw - KSB Cloud - BVS pumps
+Such a monitoring solution with internet of things devices allows us to introduce predictive (PdM) or condition-based maintanance (CbM).
+This strategy prolongs the life of the equipment and reduces cost for replacement parts and in preventive maintanance~\cite{ziaran_technicka_2013}.
 
-# analytical - known bearing
-Ball Pass Frequency Outer Race (BPFO)
-Ball Pass Frequency Inner Race (BPFI)
-Ball Spin Frequency (BSF)
-Fundamental Train Frequency (FTF)
-!!! CITE do not describe !!!
+Large number of machines in the plant and frequent sampling intervals poses a challange with shear amount of samples gathered.
+Data reduction should happen close to source to save on storage requirements, bandwidth and promote retainment of important observations only.
+Additional difficulty is to tailor the fault classification model to individual machinery because each piece has natural imperfections and differences in its construction.
+
+Technical diagnosis is tasked with identifying faulty machinery part which can be bearing, shaft, coupling, belt, or gear.
+The commonly found defects are unbalance, misalignment, looseness, eccentricity, deformation, crack, and rub~\cite{mohanty_machinery_2015, scheffer_practical_2004}.
+Majority of symptoms in vibrations appear synchronous to the rotational speed of the component under investigation as rotation fundamental frequency or its harmonics~\cite{davies_handbook_2012}.
+Imbalance, misalignment, or looseness of the shaft occurs under 300 Hz.
+Bearing and gearbox defects in the late stages of development show up between 300 Hz and 1 kHz.
+Higher frequencies contain the bearing faults even sooner~\cite{torres_automatic_2022}.
+
+\section{Related work}
+Approches taken in literature to reduce vibration samples and classify faults result in similiar framework of machine learning pipeline.
+The general sequence of steps consist of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015, brito_fault_2021}.
+
+Data retrieval from acceleration sensors is combined with factory database of machinery mechanical parameters and operating conditions~\cite{jung_vibration_2017}.
+The signal processing methods are traditionally used to extract low-level numerical features in time domain, frequency domain, and time-frequency domain~\cite{nandi_condition_2019}.
+Time-frequency features depend on transform method of which Morlet wavelet transform, discrete wavelet trasform or wavelet packet transform are ones used besides short-time Fourier transform~\cite{maurya_condition-based_2021}.
+Then statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress waveform composed of bins in each of the domains~\cite{zhuo_research_2022}.
+
+%TODO
+Na redukciu dát zo signálov z nahrávok získame numerické features.
+Spravidla in time and frequency domain.
+Najčastejšie štatické vlastnosti of waveform.
+Niekoľko článkov ich uvádza: .
+Pri vibráciach môžeme uplatniť podobné črty ako pri zvuku: (peeters) ale aj analytické odovodené z rýchlosti rotácie časti ložísk (mohanti).
+
+% Time domain features
+\cite{mostafavi_novel_2021}
+\cite{moctar_time-domain_2023}
+% Spectral
+\cite{noauthor_iso_2016_2}
+\cite{peeters_large_2004}
+
+% Dimentionality reduction
+Features sa transformujú či cez scaling (ak chceme ponechať pôvodné) alebo metódami ako PCA (na získanie kombinácie).
+Viac osí môžeme použiť ako samostné črty ale lepšie je použiť len os v smere vibrácii alebo vypočítať euklidovskú normu z 3d vektora.
+% Feature transformation
+\cite{brito_fault_2021}
+\cite{zheng_feature_2018}
+\cite{kamminga_robust_2018} % euclidean norm
+
+Na zredukovanie sady features použijeme techniky feature selection, ktoré môžu byť samostatné (filtering) alebo ako súčasť modelu klasifikátora (embedded).
+Na výber features dopredu porovnáme ich realtion ku categorical predicted variable cez point-biserial correlation, ANOVA F-value or Mutual information.
+Účinnejšie je použiť ensamble ako rôzne voting systems alebo rank product.
+% Feture ranking
+\cite{nandi_condition_2019}
+% Rank product
+\cite{breitling_rank_2004}
+
+Existujú rôzne štandardné datasety ako Machinery fault database (Mafaulda) (50 kHz)). Aké sú tam poruchy a rýchlosti a CWRU bearing dataset (Deep Groove Ball Bearing Data Set) (12 kHz) - aké poruchy.
+% Datasets
+\cite{ribeiro_rotating_2017}
+
+Najčastejšie na zmienených datasetoch sa overovali metódy. Na klasifikáciu porúch boli aplikované prístupy machine learning ale aj deep learning and transfer learning.
+
+% Classification
+
+% Effects of Distance Measure Choice on K-Nearest Neighbor Classifier Performance: A Review
+% recently proposed nonconvex distance performed the best when applied on most data sets comparing with the other tested distances. 
+% In addition, the performance of the KNN with this top performing distance degraded only *20% while the noise level reaches 90%, this is true for most of the distances used as well. 
+% This means that the KNN classifier using any of the top 10 distances tolerates noise to a certain degree
+% KNN is one of the laziest learning methods. This implies storing all training data and waits until having the test data produced, without having to create a learning model
+% Slowness is not the only problem associated with the KNN classifier, in addition to choosing the best K-neighbors problem choosing the best distance/similarity measure is an important problem,
+% he average accuracy of all distances over the first 14 data sets, using K = 1 with and without noise: 4% with , 7% without noise less on euclidean distance than on Hassanat distance, MD is slighly better
+\cite{abu_alfeilat_effects_2019} %metrics
+
+% Improving k-Nearest Neighbors Algorithm for Imbalanced Data Classification
+% k-NN classifiers will be significantly impacted by the imbalanced class distributions of data
+% we look into the data pre-processing techniques that can be used to rebalance the training data and enhance the performance of k-NN
+%14 real-world data sets collected from different application domains
+% precision metric (overall accuracy is not a good indicator)
+% smallest of 253 (i.e., mw1) to the largest of 17186 (i.e., pc5). The number of attributes is between 9 and 74
+% The most imbalanced data set is mv1 that has the highest imbalance rate of 4556%,
+% data sampling schemes, random oversampling (ROS), random undersampling (RUS) and ensemble oversampling (ENOS) are able to improve the precision of k-NN classifiers in most data sets (15% and 39%) - lower unbalance, over 40% - higher unbalance
+% The imbalance rate is defined as the number of instances in the majority class divided by the number of instances in the minority class
+\cite{shi_improving_2020} %k-NN balancing
+
+%  article proposes a novel low-level knowledge transfer framework using a deep neural network (DNN) model for condition monitoring of machines in variable running conditions.
+% air compressor acoustic data set - 100%; 2) the Case Western Reserve University bearing data set - 93%; and 3) the intelligent maintenance system bearing data set - 100%
+% The signal processing methods are used to extract low-level features in the TD, FD, and TF domains. The process of extracting these low-level features is described as follows
+% The TD, FD, M (Morlet)WT, DWT, and WPT features have been directly given to all the classifiers for comparing the effectiveness - low-level features
+% Furthermore, features have been selected using four different feature selection techniques, i.e., mutual information feature selection (MIFS), minimal redundancy maximal relevance (mRMR) , principal component analysis (PCA), and Bhattacharyya distance (BD)
+% To compare the performance of the proposed approach, a DNN without KT is implemented. SVM, RF, and softmax classifiers have been used for fault classification.
+% CWRU - 61% SVM on 8 time domain features, 88% on 20 spectral SVM (RF and soft max worse)
+\cite{maurya_condition-based_2021}
+
+% review the development of machine learning and deep learning methods for bearing vibration monitoring
+% Machine learning has been widely used in bearing health monitoring, which are generally divided into two steps: feature extraction and condition classification.
+% three main machine learning methods used in health monitoring are introduced, including KNN, ANN (Artificial neural network) and SVM.
+% briefly introduces three main deep learning methods used in health monitoring: AE  (Auto-encoder), RBM (Restricted Boltzmann Machines), CNN (Convolution Neural Networks) and their corresponding variants
+% This method can accurately detect and classify bearing stator and rotor faults.
+In order to detect early faults of motor rolling bearings under masked noises, PCA and KNN are used to accurately measure the distance and different fault features are extracted as health indicators
+% In [87], a transfer learning approach based on a 1D CNN and frequency domain analysis of the vibration signals is presented.
+Using bearing data with different failure severity for testing, the classification accuracy is about 99.67%
+\cite{sheng_review_2020}
+
+% In [50], a combined power spectral density (PSD), KNN) and SVM are proposed to perform journal bearing fault diagnosis.
+For KNN and SVM, the best classification accuracy is 85.7% and 100%, respectively.
+The results show that SVM is a more powerful fault diagnosis technology for rotating machinery
+\cite{moosavian_appropriate_2012}
+
+% ew way of diagnosing the fault of rolling element bearings.
+In the current work, ML models, namely, Support Vector Machine (SVM) and K-Nearest Neighbor (KNN), are used to classify the faults associated with different ball bearing elements.
+% Using open-source Case Western Reserve University (CWRU) bearing data
+% extracted time-domain and frequency-domain features. The results show that frequency-domain features are more convincing for the training of ML models, 
+% Set 1: Combination of time and frequency-domain features = SVM 95.0 % KNN 96.2 %
+% Set 2: Non-linear time-domain features SVM 88.8 % KNN 91.2 %
+% Set 3: Frequency-domain features SVM 96.2 % KNN 98.8 %
+% the KNN classifier has a high level of accuracy compared to SVM
+\cite{jamil_feature-based_2021} %knn,svm
+
+% A New Statistical Features Based Approach for Bearing Fault Diagnosis Using Vibration Signals
+% The vibration signal is also converted to the frequency domain and the same features are extracted.
+All three feature sets are concatenated, creating the time, frequency and spectral power domain feature vectors.
+%These feature vectors are finally fed into the K- nearest neighbour, support vector machine and kernel linear discriminant analysis for the detection and classification of bearing faults. 
+% With the proposed method, the reduction percentage of more than 95% percent is achieved, which not only reduces the computational burden but also the classification time. 
+% Simulation results show that the signals are classified to achieve an average accuracy of 99.13% using KLDA and 95.64% using KNN classifiers.
+% 95.64% (KNN on PSD), 99.13% (KLDA)
+% Statistical_P Fourier_P PSD_P, EMD, Fourier, PSD
+\cite{altaf_new_2022}
+
+% T4PDM: A DEEP NEURAL NETWORK BASED ON THE TRANSFORMER ARCHITECTURE FOR FAULT DIAGNOSIS OF ROTATING MACHINERY
+% Experimental results are developed and presented for the MaFaulDa and CWRU databases. T4PdM was able to achieve an overall accuracy of 99.98% and 98% for both datasets, respectively.
+\cite{nascimento_t4pdm_2022}
+
+% Bearing Fault Diagnosis Based on Statistical Locally Linear Embedding
+% Fault diagnosis is essentially a kind of pattern recognition. The measured signal samples usually distribute on nonlinear low-dimensional manifolds embedded in the high-dimensional signal space,
+% Signal acquisition, Feature extraction: time-domain, frequency-domain and time–frequency domain, Dimensionality reduction, Pattern recognition
+% A large set of statistical feature parameters has been defined in the process of roller bearing fault diagnosis
+% FEatures::::
+% .
+The experimental result show that S-LLE outperforms the other traditional dimensionality reduction methods such as PCA, LDA and LLE.
+Finally fault classification is carried out in the embedded space.
+Some experiments show the RBF-SVM classifier
+% The average classification accuracy (%) the original and reduction of statistical features extracted from multi-domain by various classifiers using supervised LLE.
+\cite{wang_bearing_2015}
+
+% PSD features from acceleration readings from the sensors. (1024)
+% 20 major peaks
+% The Peak Harmonic Distance Classification algorithm constructs a classifier using training data to determine equipment’s health condition category given the observed measurement’s Da
+% Remaining Usefulness Lifetime (RUL) estimation,
+% Peak Harmonic Feature Distance
+% random sample consensus (RANSAC) approach[6]. The Recursive RANSAC regression algorithm
+% enables to prolong the average lifetime of the tubes by 1.2x and reduce the replacement cost by 20%.
+\cite{jung_vibration_2017}  % RUL (remaining useful life)  models
+
+    Reviews the pertinent literature to orient the reader
+    States the method of the experiment
+    State the principle results of the experiment
 
@@
 1. Choose frequency precision (1 Hz at maximum)
-2. 12 windows at minimum (n+1 half windows with overlap), Hann window with 50\% overlap, 2^14 - 2^15 windows, 5s recodings
+2. 12 windows at minimum (n+1 half windows with overlap), Hann window with 50\% overlap, $2^14 - 2^15$ windows, 5s recodings
 
-Mafaulda
+Mafaulda (Maximum imbalance ratio (MaxIR): The ratio of the most common label against the rarest one. = max. 1016\% to 852\%)
 1. Signal processing (choose bearing A)
@@
 
-\section{Results}
-
 Figures:
@@
 
+\section{Results}
 Signal analysis
@@
 
-\section{Summary}
-
-\section{References}
-
 %\begin{figure}[t]
@@
 
-\begin{thebibliography}{1}
+\section{Discussion}
 
-\bibitem{example}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
+\section{Conclusions}
 
-\end{thebibliography}
+\section*{Acknowledgements}
+We thank Lukáš Doubravský (R-DAS,~s.r.o.) for consultations on the methodology and assisting in sensor unit development.
+We appreciate domain experts in vibrodiagnostics prof.~Stanislav Žiaran and Dr.~Ondrej Chlebo (SjF~STU) for checking our approches.
+We also thank Peter Csóka and Peter Kmeťko (Bratislavská vodárenská spoločnosť,~a.s.) for allowing us access to their water pumps.
+
+\printbibliography
+
 \end{document}

### 2024-03-28 firmware/main/src/sensor.c

@@ -83,7 +83,7 @@ int sensor_enable(spi_device_handle_t *spi_dev, stmdev_ctx_t *dev)
 
     // Resolution: 4g
     iis3dwb_xl_full_scale_set(dev, IIS3DWB_4g);
-    // TBD: iis3dwb_xl_full_scale_set(dev,  IIS3DWB_16g);
+    //iis3dwb_xl_full_scale_set(dev,  IIS3DWB_16g);
 
     iis3dwb_fifo_watermark_set(dev, FIFO_WATERMARK);
     iis3dwb_fifo_xl_batch_set(dev, IIS3DWB_XL_BATCHED_AT_26k7Hz);

### 2024-03-28 notebooks/bin2csv.py

@@ -13,9 +13,9 @@ fmt = 'iiii'
 struct_len = struct.calcsize(fmt)
 struct_unpack = struct.Struct(fmt).unpack_from
 
-
 for root, subdirs, files in os.walk(args.path):
     for filename in files:
+        print(filename)
         if not filename.lower().endswith('.bin'):
             continue
 

### 2024-03-28 iit-src/paper.tex
Feature selection in related work

@@
 
-\title{Fault classification of rotating machinery using limited set of features}
+\title{Fault Classification of Rotating Machinery Using Limited Set of Features and k-Nearest Neighbors}
 
@@
 Time-frequency features depend on transform method of which Morlet wavelet transform, discrete wavelet trasform or wavelet packet transform are ones used besides short-time Fourier transform~\cite{maurya_condition-based_2021}.
-Then statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress waveform composed of bins in each of the domains~\cite{zhuo_research_2022}.
+Then statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress
+waveform in each of the domains.
+
+Feature extraction of time and frequency attributes is utilized in online monitoring of band saw blade wear status from acoustic emission signal using SVM model ~\cite{zhuo_research_2022} and in novelty detection of health status of centrifugal pump using autoencoder~\cite{mostafavi_novel_2021}.
+Wavelength length, average amplitude change, and zero crossing taken out of overview of time domain features for surface electromyography (sEMG)~\cite{moctar_time-domain_2023} are generic enough to be tried for machine diagnostic.
+Harmonic features originaly designed for sound description~\cite{peeters_large_2004} could be reused similarily.
+Many features found in the literature are already implemented in Time Series Feature Extraction Library (TSFEL) which is package for Python language~\cite{tsfel}.
+
+Knowledge of rolling bearings geometry and rotational speed provides a way to calculate bearing defect frequencies for outer race (BPFO), inner race (BPFI), ball (BSF), and cage (FTF)~\cite{mohanty_machinery_2015, ziaran_technicka_2013}.
+There are situation when bearing fault is not evidenced by defect frequency, therefore kurtosis is recommended as it is asociated with impacts~\cite{brito_fault_2021}.
+
+Normalization assigns same weights to unbounded variables ~\cite{zheng_feature_2018}.
+In three-dimensional motion, either axis aligned only with principal direction of vibrations is retained, or euclidian norm is computed for each feature.
+The magnitude of feature vector was found useful in animal activity recognition from collar tags independent of sensor orientation~\cite{kamminga_robust_2018}.
+
+Extracted features lower the number of dimensions from original signal.
+Further dimensionality reduction is caried out with various methods, namely: PCA, t-SNE, ISOMAP, ICA, and AE~\cite{brito_fault_2021}.
+Keeping smaller number of attributes can result in better classification performance.
+However major disadvantage is the removal of the meaning from obtained features.
+
+Filtering feature selection methods decrease the feature set size so that the chosen predictors have the strongest relation to categorical predicted variable.
+The relationship is quantified with correlation, fisher score or mutual information and among others~\cite{nandi_condition_2019}.
+The metrics are combined to ensembles by means of electorial methods or rank product~\cite{breitling_rank_2004}.
 
 %TODO
-Na redukciu dát zo signálov z nahrávok získame numerické features.
-Spravidla in time and frequency domain.
-Najčastejšie štatické vlastnosti of waveform.
-Niekoľko článkov ich uvádza: .
-Pri vibráciach môžeme uplatniť podobné črty ako pri zvuku: (peeters) ale aj analytické odovodené z rýchlosti rotácie časti ložísk (mohanti).
-
-% Time domain features
-\cite{mostafavi_novel_2021}
-\cite{moctar_time-domain_2023}
-% Spectral
-\cite{noauthor_iso_2016_2}
-\cite{peeters_large_2004}
-
-% Dimentionality reduction
-Features sa transformujú či cez scaling (ak chceme ponechať pôvodné) alebo metódami ako PCA (na získanie kombinácie).
-Viac osí môžeme použiť ako samostné črty ale lepšie je použiť len os v smere vibrácii alebo vypočítať euklidovskú normu z 3d vektora.
-% Feature transformation
-\cite{brito_fault_2021}
-\cite{zheng_feature_2018}
-\cite{kamminga_robust_2018} % euclidean norm
-
-Na zredukovanie sady features použijeme techniky feature selection, ktoré môžu byť samostatné (filtering) alebo ako súčasť modelu klasifikátora (embedded).
-Na výber features dopredu porovnáme ich realtion ku categorical predicted variable cez point-biserial correlation, ANOVA F-value or Mutual information.
-Účinnejšie je použiť ensamble ako rôzne voting systems alebo rank product.
-% Feture ranking
-\cite{nandi_condition_2019}
-% Rank product
-\cite{breitling_rank_2004}
-
 Existujú rôzne štandardné datasety ako Machinery fault database (Mafaulda) (50 kHz)). Aké sú tam poruchy a rýchlosti a CWRU bearing dataset (Deep Groove Ball Bearing Data Set) (12 kHz) - aké poruchy.

### 2024-03-29 iit-src/paper.tex
Complete methodology of the article

--- 2024-03-23 iit-src/paper.tex
@@
 \usepackage{graphicx}
+\usepackage{biblatex}
 \usepackage{caption}
-%\usepackage[caption=false]{subfig}
 \usepackage[english]{babel}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{csquotes}
+
+\makeatletter
+\newcommand*{\rom}[1]{\expandafter\@slowromancap\romannumeral #1@}
+\makeatother
+
+\addbibresource{literature.bib}
 
@@
 
-% 4 pages (5 pages with sources)
-\title{Feature selection in fault classification of rotating machinery}
-
-\titlerunning{Features for machinery faults}
+\title{Fault Classification of Rotating Machinery using Limited Set of Features and k-Nearest Neighbors}
 
 \author{
-	Miroslav Hájek\thanks{Master study programme in field: Informatics
-	Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava }
+	Miroslav Hájek\thanks{Master study programme in field: Informatics,
+	Supervisor: Dr. Marcel Baláž, Institute of Computer Engineering and Applied Informatics, Faculty of Informatics and Information Technologies STU in Bratislava}
 }
@@
 \section{Introduction}
-- predictive maintance, research question
+Rotary motion machinery is utilized throughout the industry as motors, pumps, and gearboxes.
+All equipment have bounded productive lifespan because of wear and tear or improper operating conditions.
+Sonner or later, moving elements start to exhibit faults that can lead to failure if left untreated.
 
-Related work (citations)
+Early real-time fault detection can be achieved by monitoring machine vibration levels and signal frequency content~\cite{ziaran_technicka_2013}.
+Sensors for vibrations are piezoelectric or MEMS wideband accelerometers.
+Data acquisition procedures and best evaluation practices are standardized in ISO~20816~\cite{noauthor_iso_2016} and ISO~13373~\cite{noauthor_iso_2002}.
 
-existence of standards
-domain - time, frequency, time-frequency
-feature extraction techniques
-feature selection techniques
-classification of faults
-datasets: mafaulda, cwru, rotating shaft
-Raw - KSB Cloud - BVS pumps
+Such a monitoring solution with internet of things devices allows us to introduce predictive (PdM) or condition-based maintanance (CbM).
+This strategy prolongs the life of the equipment and reduces cost for replacement parts and in preventive maintanance~\cite{ziaran_technicka_2013}.
 
-# analytical - known bearing
-Ball Pass Frequency Outer Race (BPFO)
-Ball Pass Frequency Inner Race (BPFI)
-Ball Spin Frequency (BSF)
-Fundamental Train Frequency (FTF)
-!!! CITE do not describe !!!
+Large number of machines in the plant and frequent sampling intervals poses a challange with shear amount of samples gathered.
+Data reduction should happen close to source to save on storage requirements, bandwidth and promote retainment of important observations only.
+Additional difficulty is to tailor the fault classification model to individual machinery because each piece has natural imperfections and differences in its construction.
+
+Technical diagnosis is tasked with identifying faulty machinery part which can be bearing, shaft, coupling, belt, or gear.
+The commonly found defects are unbalance, misalignment, looseness, eccentricity, deformation, crack, and rub~\cite{mohanty_machinery_2015, scheffer_practical_2004}.
+Majority of symptoms in vibrations appear synchronous to the rotational speed of the component under investigation as rotation fundamental frequency or its harmonics~\cite{davies_handbook_2012}.
+Imbalance, misalignment, or looseness of the shaft occurs under 300 Hz.
+Bearing and gearbox defects in the late stages of development show up between 300 Hz and 1 kHz.
+Higher frequencies contain the bearing faults even sooner~\cite{torres_automatic_2022}.
+
+\section{Related work}
+Approches taken in literature to reduce vibration samples and classify faults result in similiar framework of machine learning pipeline.
+The general sequence of steps consist of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015, brito_fault_2021}.
+
+Data retrieval from acceleration sensors is combined with factory database of machinery mechanical parameters and operating conditions~\cite{jung_vibration_2017}.
+The signal processing methods are traditionally used to extract low-level numerical features in time domain, frequency domain, and time-frequency domain~\cite{nandi_condition_2019}.
+Time-frequency features depend on transform method of which Morlet wavelet transform, discrete wavelet trasform or wavelet packet transform are ones used besides short-time Fourier transform~\cite{maurya_condition-based_2021}.
+Then statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress
+waveform in each of the domains.
+
+Feature extraction of time and frequency attributes is utilized in online monitoring of band saw blade wear status from acoustic emission signal using SVM model ~\cite{zhuo_research_2022} and in novelty detection of health status of centrifugal pump using autoencoder~\cite{mostafavi_novel_2021}.
+Wavelength length, average amplitude change, and zero crossing taken out of overview of time domain features for surface electromyography (sEMG)~\cite{moctar_time-domain_2023} are generic enough to be tried for machine diagnostic.
+Harmonic features originaly designed for sound description~\cite{peeters_large_2004} could be reused similarily.
+Many features found in the literature are already implemented in Time Series Feature Extraction Library (TSFEL) which is package for Python language~\cite{tsfel}.
+
+Knowledge of rolling bearings geometry and rotational speed provides a way to calculate bearing defect frequencies for outer race (BPFO), inner race (BPFI), ball (BSF), and cage (FTF)~\cite{mohanty_machinery_2015, ziaran_technicka_2013}.
+There are situation when bearing fault is not evidenced by defect frequency, therefore kurtosis is recommended as it is asociated with impacts~\cite{brito_fault_2021}.
+
+Normalization assigns same weights to unbounded variables~\cite{zheng_feature_2018}.
+In three-dimensional motion, either axis aligned only with principal direction of vibrations is retained, or euclidian norm is computed for each feature.
+The magnitude of feature vector was found useful in animal activity recognition from collar tags independent of sensor orientation~\cite{kamminga_robust_2018}.
+
+Extracted features lower the number of dimensions from original signal.
+Further dimensionality reduction is caried out with various methods, namely: PCA, t-SNE, ISOMAP, ICA, and AE~\cite{brito_fault_2021}.
+Keeping smaller number of attributes can result in better classification performance.
+However major disadvantage is the removal of the meaning from obtained features.
+
+Filtering feature selection methods decrease the feature set size so that the chosen predictors have the strongest relation to categorical predicted variable.
+The relationship is quantified with correlation, fisher score or mutual information and among others~\cite{nandi_condition_2019}.
+The metrics are combined to ensembles by means of electorial methods or rank product~\cite{breitling_rank_2004}.
+
+Machinery Fault Database (MaFaulDa)~\cite{mafaulda_dataset} or Case Western Reserve University (CWRU) bearings dataset~\cite{cwru_dataset} are routinely used for evaluation of machinery fault models.
+MaFaulDa contains 1951 time series measured on two bearings
+simutanously with three uniaxial accelerometers at sampling rate of 50 kHz.
+Each recording lasts 5 seconds and it represents one of 5 defects but at different loads, shaft shifts, and rotation speeds between 737 to 3686 RPM.
+CWRU dataset has 161 scenarios at sample rates of 12 kHz or 48 kHz.
+Time series captures four different states of bearings on drive end and fan end of the motor.
+
+Classification of faults in machinery diagnostics focuses primarily on bearings health monitoring.
+Review article~\cite{sheng_review_2020} compares strengths and weaknesesses machine and deep learning models.
+Power spectral density (PSD) features from vibration signals of journal bearings in combination with k-NN and SVM reached classification accuracy 85.7\% and 100\%, respectively~\cite{moosavian_appropriate_2012}.
+Ball bearing fault diagnostic of CWRU dataset indicate better accuracy of k-NN (98.8\%) than SVM (96.2\%) on frequency-domain features~\cite{jamil_feature-based_2021}.
+Approach based on statistical features utilizing custom test rig compared three models for ball bearing faults: k-NN, SVM, and kernel linear discriminant analysis (KLDA).
+Results showed KLDA achieves best average accuracy on PSD features (99.13\%) followed by k-NN with PSD (95.64\%) and SVM with EMD (80.49\%)~\cite{altaf_new_2022}.
+
+On CWRU dataset SVM performs better in comparison of state-of-the-art methods to random forest (RF) and softmax classifiers.
+The best accuracy of SVM is 61.05\% on 5 time domain features (RF 59.07\%, Softmax 48.92\%) and 91.17\% on 64 frequency domain (RF 86.14\%, Softmax 86.05\%) features~\cite{maurya_condition-based_2021}.
+Random forest applied after similarity-based model has a accuracy of 96.43\% on the MaFaulDa and 98.7\% on the CWRU database~\cite{ribeiro_rotating_2017}.
+
+In k-NN algorithm the number of neigbors and similarity measure has to be chosen carefully.
+Hassanat distance performes the best on average for k = 1 but is only by 4\% better in situation without noise and 7\% in scenarios with noise when compared to Euclidian distance~\cite{abu_alfeilat_effects_2019}.
+Categories in dataset fed into k-NN classifier should be balanced in size otherwise precision drops 15\% to over 40\% depending on imbalance ratio~\cite{shi_improving_2020}.
 
 \section{Methodology}
+The two principal questions regarding automated machinery fault diagnostics from vibrations are investigated in this study.
+How does reducing number of features and different feature selection methods impact k-nearest neighbors multiclass classifier accuracy with varying k parameter?
+This first exploration takes place in supervised manner with 5-fold cross validation on preprocessed MaFaulDa dataset.
+Then the challanges are presented of how to apply same procedures to the monitoring solution of municipal water pumping station?
+Calibrated data from existing pump monitoring provided by the vendor on the site is taken as a reference.
 
-1. Choose frequency precision (1 Hz at maximum)
-2. 12 windows at minimum (n+1 half windows with overlap), Hann window with 50\% overlap, 2^14 - 2^15 windows, 5s recodings
+Classification of MaFaulDa dataset are caried out for extracted features in time domain (TD) and frequency domain (FD) separately.
+The accuracy is determined for features in radial axis $y$ and euclidian norm of all directions (Fig.~\ref{fig:mafaulda-simulator})  Experiments include different combination of selected attributes according to predefined conditions:
+\begin{enumerate}
+\item whole feature set with k value as odd number in range from 1 to 37,
+\item dimensionality reduction using pricipal components analysis (PCA) of whole feature set to 3 principal components ($k = 5$),
+\item every combination of 3, 4, 5 member feature subsets with k value being sequentially: 3, 5, 11, 15 (results in $\sum_{j = 3}^{5}{n\choose j}$ models for individual k value),
+\item best feature subset picked using feature selection methods: mean of point-biserial correlation to every class as a dichotomous variable, ANOVA F-value and mutual infomation ($k = 5$).
+\end{enumerate}
 
-Mafaulda
-1. Signal processing (choose bearing A)
-2. Labeling - 6 classes (Class balancing by oversampling)
-3. Feature extraction - Time domain, Frequency domain - Min-max scaling before PCA
-4. Feature selection - 
-	PCA 2,3,4 - accuracy + loading plot (PC2)
-	KNN all features- 5-fold cross validation - rôzne domény, rôzne k, rôzne počty features
-	KNN exhaustive models - 
-		2,3,4 features (check corr, f-stat, mi, rank product scores)
-	 -> KNN classification(online and offiline)
+\begin{figure}
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/sensor/mafaulda-simulator.jpg}
+         \caption{MaFaulDa}
+         \label{fig:mafaulda-simulator}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/sensor/ksb-pump.jpg}
+         \caption{Water pump}
+         \label{fig:water-pump}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/sensor/sensor.jpg}
+         \caption{Accelerometer}
+         \label{fig:steval-sensor}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/sensor/ksb-cloud.jpg}
+         \caption{KSB sensor}
+         \label{fig:ksb-cloud-sensor}
+     \end{subfigure}
+     \caption{Measurement positions and accelerometer orientations}
+\end{figure}
 
-Custom dataset
-1. Choice of machines (pic measurement places - two images and dots) - pumps according to standards + callibrated sensors
-	- compressor is on housing
-2. HW sensor + ESP32 + FW 60 s. recor
-3. How measure (plan)
-4. Signal processing
-4. Labeling  / Labeling (use machine - split by type) 
-5. Same as Mafaulda
+Data preprocessing of MaFaulDa is necessary to create feature sets in TD and FD. This process of several phases.
+\begin{enumerate}
+\item \textbf{Signal filtering}: Subtraction of overall mean removes DC component. IIR Butterworth low pass filter of 5th order attenuates frequencies above above 10 kHz.
+\item \textbf{Feature extraction}: Machine behavior in one time series is time-invariant therefore each feature is calculated out of whole duration.
+Frequency domain features are produced using Welch's method for power spectrums from FFT with $2^{15}$ long Hann windows and 50\% overlap  (bin resolution of 1.53~Hz).
+The resulting features belong to domains making up respective feature sets:
+\begin{enumerate}
+\item \textbf{10 time domain features} (TD): peak-to-peak amplitude, zero-crossing rate, root mean square, skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change,
+\item \textbf{11 frequency domain features} (FD): spectral centroid, standard deviation, skewness, kurtosis, roll on frequency of 5\% total energy, roll off frequency of 85\% total energy, spectral flux as a average correlation of separate windows, noisiness as a signal to noise ratio, spectral negentropy~\cite{avoci_spectral_2020}, energy, entropy.
+\end{enumerate}
+\item \textbf{Labeling}: Three target variables are constructed out of inner bearing, both bearings, and high severity defects on both bearings.
+Predicted variable has 6 classes: normal, misalignment, imbalance, outer race fault, inner race fault, cage fault.
+In high severity scenario, the normal class is assigned to observations where weight or shaft shift applied is in half below 60\% of all configuations for that fault.
+\item \textbf{Class balancing}: Random oversampling strategy is used on all classes except the majority one.
+\end{enumerate}
 
-acc = prec micro = recall micro
+Vibrations from pumps in municipal pumping station for drinking water in Podunajské Biskupice reveal practical challenges for deployment of machine learning models in the industry.
+Two pumps (P1, P2) of the same type KSB Omega 300-560 and two electric motors WEG W50 (M1, M2) were designated for measurements.
+Both machines have power 400~kW (ISO 20186 class~\rom{3}) and main shaft rotates at 1493~RPM.
+For purposes of expert labeling, the bearing designations at numbered places are: 6319-C3 (1), 6324-C3 (2), 6317-2Z (3 \& 4).
+
+Sensor were placed above bearings in numbered positions according to ISO 13373 (Fig.~\ref{fig:water-pump}) with axis orientation depicted in Fig.~\ref{fig:steval-sensor}.
+Each pump is equipped with KSB cloud monitoring at place (3) (Fig.~\ref{fig:ksb-cloud-sensor}) from which rms velocity in mm/s is available for year in hourly intervals.
+
+Our accelerometer ST IIS3DWB mounted to machine unig thin double sided tape has wideband 5 kHz linear response is sampled at 26.87~kHz.
+Microcontroller ESP32-POE-ISO stored triaxial 60 second long recordings onto SD card.
+In total 48 time series were gathered, 6 in each place.
+These are furter split to 5 second interval for 576 data points overall.
+
+The signal preprocessing is similiar which exceptions that low-pass filter is left out and FFT window size is set to $2^{14}$ (bin resolution of 1.64~Hz).
+Fault labels are missing therefore we analyse rotational speeds and defect bearing frequencies in the frequency spectrum.
+As an alternative, the observations are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.
+Another classfier is made solely with P1-3 and P2-3 placements.
+Classification is done for features in main axis of motion (z) and euclidian norm of same features in all directions.
 
 \section{Results}
-
-Figures:
-- 1ks obr. Mafaulda ABVT simulator
-- 1ks obr. (2ks subplots) machine and compressor measurement places with red squares
-- 1 ks obr. device
+Mafaulda tabulky - počtov - all axis, one bearing, one axis, severity all axis, severity all axis
 
 Signal analysis
+
+Figures KSB rms vibarion severity KSB-1 (P1), KSB-7 (P2)
 
@@
 
-\section{Summary}
+\section{Discussion}
 
-\section{References}
+\section{Conclusions}
 
-%\begin{figure}[t]
-%\centering
-%\subfloat{
-%	\includegraphics[width=0.45\textwidth]{app.png}
-%}
-%\subfloat{
-%	\includegraphics[width=0.45\textwidth]{mri.png}
-%}
-%\caption{Patients list and MRI viewer}
-%\end{figure}
+\section*{Acknowledgements}
+We thank Lukáš Doubravský (R-DAS,~s.r.o.) for consultations on the methodology and assisting in sensor unit development.
+We appreciate domain experts in vibrodiagnostics prof.~Stanislav Žiaran and Dr.~Ondrej Chlebo (SjF~STU) for checking our approches.
+We also thank Peter Csóka and Peter Kmeťko (Bratislavská vodárenská spoločnosť,~a.s.) for allowing us access to their water pumps.
 
-\begin{thebibliography}{1}
+\printbibliography
 
-\bibitem{example}
-Author, F., Author, S.: Title of a proceedings paper. In: Editor,
-F., Editor, S. (eds.) CONFERENCE 2016, LNCS, vol. 9999, pp. 1--13.
-Springer, Heidelberg (2016). \doi{10.10007/1234567890}
-
-\end{thebibliography}
 \end{document}

### 2024-03-31 iit-src/paper.tex
Graphs for results

@@
 \item \textbf{Labeling}: Three target variables are constructed out of inner bearing, both bearings, and high severity defects on both bearings.
-Predicted variable has 6 classes: normal, misalignment, imbalance, outer race fault, inner race fault, cage fault.
+Predicted variable has 6 classes: normal, misalignment (merged vertical and horizontal), imbalance, outer race fault, ball fault, cage fault.
 In high severity scenario, the normal class is assigned to observations where weight or shaft shift applied is in half below 60\% of all configuations for that fault.
@@
 \section{Results}
-Mafaulda tabulky - počtov - all axis, one bearing, one axis, severity all axis, severity all axis
+\begin{figure}
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/mafaulda-wideband.png}
+         \caption{MaFaulda}
+         \label{fig:mafaulda-wideband}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/motor-wideband.png}
+         \caption{Motors}
+         \label{fig:motor-wideband}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/pump-wideband.png}
+         \caption{Pumps}
+         \label{fig:motor-wideband}
+     \end{subfigure}
+     \caption{Wideband power spectrum}
+\end{figure}
 
-Signal analysis
+\begin{figure}
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/mafaulda-fault.png}
+         \caption{MaFaulda}
+         \label{fig:mafaulda-fault}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/motor-fault.png}
+         \caption{Motors}
+         \label{fig:motor-fault}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.3\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/spectrum/pump-fault.png}
+         \caption{Pumps}
+         \label{fig:pump-fault}
+     \end{subfigure}
+     \caption{Shaft and bearing defect frequencies}
+\end{figure}
 
-Figures KSB rms vibarion severity KSB-1 (P1), KSB-7 (P2)
+\begin{table}
+\centering
+\caption{Numbers of observations by label in MaFaulDa}\label{tab:mafaulda-observation-counts}
+\begin{tabular}{|l|r|r|r|}
+\hline
+\textbf{Label} &  \textbf{Bearing A} & \textbf{Both bearings} & \textbf{High severity} \\
+\hline
+normal            &  49  &  49  &  1125 \\
+misalignment      & 498  &  498 & 198 \\
+imbalance         & 333  &  333 & 139 \\
+cage fault        & 188  &  376 & 181 \\
+ball fault        & 186  &  323 & 132 \\
+outer race fault  & 184  &  372 & 176 \\
+\hline
+$\Sigma$ & 1438  & 1951 & 1951 \\
+\hline
+\end{tabular}
+\end{table}
 
-- 1ks plot (histogram of td signal)?
-- 1ks plot (6x subplots) Mafaulda welch from each fault (1s, 2**14 window, hann window)  - largest severity - 2500 rpm
-- 1ks plot (6x subplots) Custom dataset - each place in one day spectrum (5s segment)
+\begin{figure}
+     \begin{subfigure}[b]{0.48\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/ksb-cloud/P1-rms-vibration.png}
+         \caption{P1-3}
+         \label{fig:P1-ksb-rms}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.48\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/ksb-cloud/P2-rms-vibration.png}
+         \caption{P2-3}
+         \label{fig:P2-ksb-rms}
+     \end{subfigure}
+     \caption{RMS vibrations of pumps and ISO severity levels}
+\end{figure}
 
-Feature analysis:
-Mafaulda (4) a Custom (4) 
-- 1 ks table (how many faults have how many recordings)
-- 1 ks plot (2 lines TD, FD) - numer of PC vs. explained variance
-- 1 ks plot (2x subplots TD, FD) - loading plot (PC2)
+% Identical plots for one axis and multiple axis
+\begin{figure}
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-a-bearing.png}
+         \caption{Bearing A}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-all-bearings.png}
+         \caption{Both bearings}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-severity.png}
+         \caption{High severity}
+     \end{subfigure}
+     \caption{Whole feature sets in TD and FD from MaFaulDa}
+\end{figure}
 
-% TODO
-- 1 ks (5 subplots) scatter: mafaulda, all machines, pumps, compressors, motors
+\begin{figure}
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-pumps/machine.png}
+         \caption{Machines}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-pumps/position.png}
+         \caption{Positions}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-pumps/binary.png}
+         \caption{Pumps on position 3}
+     \end{subfigure}
+     \caption{Whole feature sets in TD and FD from water pumps}
+\end{figure}
 
-Classification accuracy (choices of k. and feat. count, 5-fold cross validation)
+% All bearings
+\begin{figure}
+	\centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-all-bearings.png}
+         \caption{Both bearings in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-severity.png}
+         \caption{High severity in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-all-bearings.png}
+         \caption{Both bearings in FD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-severity.png}
+         \caption{High severity in TD}
+     \end{subfigure}
+     \caption{PCA scatter plots of MaFaulDa with k-NN decision boundaries (k = 5)}
+\end{figure}
 
-Whole serach space = For mafaulda and custom (which classes - all or just one machine)
-- 1 ks All features (2x subplots TD, FD)
-	- Each subplot boxplot (k = 3,5,7)
+\begin{figure}
+	\centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-td.png}
+         \caption{Positions in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-fd.png}
+         \caption{Positions in FD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-td.png}
+         \caption{P1-3 and P2-3 in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-fd.png}
+         \caption{P1-3 and P2-3 in FD}
+     \end{subfigure}
+     \caption{PCA scatter plots of water pumps with k-NN decision boundaries (k = 5)}
+\end{figure}
 
-2 features - best models under 55\% accuracy in test set
+% All axis
+% by words relation to one axis, and one bearings
+% Pumps - spectral is better
+\begin{figure}
+	\centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-all-bearings-f3.png}
+         \caption{Both bearings f=3}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-all-bearings-f3.png}
+         \caption{Both bearings f=3}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-severity-f3.png}
+         \caption{High severity k = 5}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-severity-k5.png}
+         \caption{High severity k = 5}
+     \end{subfigure}
+     \caption{Test accuracies of all combinations of feature subsets}
+\end{figure}
 
-All models (exhausive) - draw rank, corr, f-stat, mi as horizontal line
-	- 3 ks plots (2, 3, 4 features)
-		- Each plot 2 boxplot subplots (TD, FD) - k-neigh. vs. accuracy of all models
+%TODO
+% Table of accuracies for Maufaulda for rainbow bar plot (test set)
 
-Compare accuracies of best models in each categories for given number of features and k:
-- 1 ks plot - bar chart - color rainbow - one x (td), second x (fd)
-
-- In training set growing number of neighbors decreases accuracy - in testing set there is no effect (more neighbors more overtraining)
-	- we choose k = 5
-- Number of features increases accuracy
-
-\section{Discussion}
+% Table for pumps
 
@@
 We appreciate domain experts in vibrodiagnostics prof.~Stanislav Žiaran and Dr.~Ondrej Chlebo (SjF~STU) for checking our approches.
-We also thank Peter Csóka and Peter Kmeťko (Bratislavská vodárenská spoločnosť,~a.s.) for allowing us access to their water pumps.
+We also thank Peter Csóka and Peter Kmeťko (Bratislavská vodárenská spoločnosť,~a.s.) for enabling us access to water pumps.
 

### 2024-04-01 iit-src/paper.tex
Finish IIT.SRC paper and poster

@@
 \usepackage{csquotes}
+\usepackage{multirow}
+\usepackage{nth}
 
@@
 \makeatother
+
+\setlength{\textfloatsep}{7pt}
+\setlength{\floatsep}{5pt}
+\setlength{\intextsep}{7pt}
+\newcommand{\squeezeup}{\vspace{-2.5mm}}
 
@@
 \begin{abstract}
-% https://guides.lib.uci.edu/c.php?g=334338&p=2249908
-what is reasearch about
-what was shown in previous studies
-new methods
-findings
+The ability to detect and diagnose faulty parts of the machine is important for the industry at scale.
+Continuous monitoring of vibrations  with accelerometers used as a diagnostic tool demands significant requrements for bandwidth and storage of samples.
+Standards already establish reliable attributes for the fault presence.
+The same cannot be said for purposes of root cause analysis.
+The goal is to examine the effect of reducing the number of features for fault prediction accuracy in the k-nearest neighbor model.
+We extract ten features in the time domain and eleven in frequency domain in the MaFaulDa dataset.
+We compare the accuracy of the whole feature set with three member subsets chosen by brute force, PCA, and feature selection methods: correlation, f-statistic, mutual information, and their rank product.
+We also qualitatively analyze features from the vibrations of water pumps.
+The rank product reaches accuracy 83.90\% and 79.08\%, for the time and frequency domain, respectively, which is by 1.82\% and 5.13\% less than the best three-member subset found by brute force.
 
-\keywords{keyword  \and keyword \and keyword \and keyword}
+\keywords{feature selection \and machine fault diagnosis \and vibrations \and MaFaulDa \and k-NN}
 \end{abstract}
@@
 Rotary motion machinery is utilized throughout the industry as motors, pumps, and gearboxes.
-All equipment have bounded productive lifespan because of wear and tear or improper operating conditions.
-Sonner or later, moving elements start to exhibit faults that can lead to failure if left untreated.
+All equipment has a bounded productive lifespan because of wear and tear or improper operating conditions.
+Sooner or later, moving elements start to exhibit faults that can lead to failure if left untreated.
 
@@
 
-Such a monitoring solution with internet of things devices allows us to introduce predictive (PdM) or condition-based maintanance (CbM).
-This strategy prolongs the life of the equipment and reduces cost for replacement parts and in preventive maintanance~\cite{ziaran_technicka_2013}.
+Such a monitoring solution with the Internet of Things devices allows us to introduce predictive (PdM) or condition-based maintenance (CbM).
+This strategy prolongs the life of the equipment and reduces the cost of replacement parts and preventive maintenance~\cite {ziaran_technicka_2013}.
 
-Large number of machines in the plant and frequent sampling intervals poses a challange with shear amount of samples gathered.
-Data reduction should happen close to source to save on storage requirements, bandwidth and promote retainment of important observations only.
-Additional difficulty is to tailor the fault classification model to individual machinery because each piece has natural imperfections and differences in its construction.
+A large number of machines in the plant and frequent sampling intervals pose a challenge with the sheer amount of samples gathered.
+Data reduction should happen close to the source to save on storage requirements, and bandwidth and promote retainment of important observations only.
+An additional difficulty is to tailor the fault classification model to individual machinery because each piece has natural imperfections and differences in its construction.
 
-Technical diagnosis is tasked with identifying faulty machinery part which can be bearing, shaft, coupling, belt, or gear.
-The commonly found defects are unbalance, misalignment, looseness, eccentricity, deformation, crack, and rub~\cite{mohanty_machinery_2015, scheffer_practical_2004}.
-Majority of symptoms in vibrations appear synchronous to the rotational speed of the component under investigation as rotation fundamental frequency or its harmonics~\cite{davies_handbook_2012}.
-Imbalance, misalignment, or looseness of the shaft occurs under 300 Hz.
-Bearing and gearbox defects in the late stages of development show up between 300 Hz and 1 kHz.
-Higher frequencies contain the bearing faults even sooner~\cite{torres_automatic_2022}.
+Technical diagnosis identifies faulty machinery parts that can be bearings, shafts, coupling, belts, or gear.
+The commonly found defects are imbalance, misalignment, looseness, eccentricity, deformation, crack, and rub~\cite{mohanty_machinery_2015, scheffer_practical_2004}.
+Most symptoms in vibrations appear synchronous to the rotational speed of the component under investigation as fundamental frequency of rotation or its harmonics~\cite{davies_handbook_2012}.
+Multiple faults can arise simultaneously or induce one another.
+For example, a severely damaged bearing introduces shaft imbalance.
 
 \section{Related work}
-Approches taken in literature to reduce vibration samples and classify faults result in similiar framework of machine learning pipeline.
-The general sequence of steps consist of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015, brito_fault_2021}.
+Approaches taken in literature to reduce vibration samples and classify faults result in a similar framework of machine learning pipeline.
+The general sequence of steps consists of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015, brito_fault_2021}.
 
-Data retrieval from acceleration sensors is combined with factory database of machinery mechanical parameters and operating conditions~\cite{jung_vibration_2017}.
-The signal processing methods are traditionally used to extract low-level numerical features in time domain, frequency domain, and time-frequency domain~\cite{nandi_condition_2019}.
-Time-frequency features depend on transform method of which Morlet wavelet transform, discrete wavelet trasform or wavelet packet transform are ones used besides short-time Fourier transform~\cite{maurya_condition-based_2021}.
-Then statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress
-waveform in each of the domains.
+Data retrieval from acceleration sensors is supplemented by a factory database of machinery mechanical parameters and operating conditions~\cite{jung_vibration_2017}.
+The signal processing methods extract low-level numerical features in the time domain, frequency domain, and time-frequency domain~\cite{nandi_condition_2019}.
+Time-frequency features depend on the transform method of which Morlet wavelet transform, discrete wavelet transform, or wavelet packet transform are the ones used besides short-time Fourier transform~\cite{maurya_condition-based_2021}.
+Then, statistical functions such as root mean square, centroid, kurtosis, energy, and entropy are applied to further compress the waveform.
 
-Feature extraction of time and frequency attributes is utilized in online monitoring of band saw blade wear status from acoustic emission signal using SVM model ~\cite{zhuo_research_2022} and in novelty detection of health status of centrifugal pump using autoencoder~\cite{mostafavi_novel_2021}.
+Feature extraction of time and frequency domain attributes is utilized in online monitoring of band saw blade wear status from acoustic emission signal using SVM model ~\cite{zhuo_research_2022} and in novelty detection of health status of centrifugal pump using autoencoder~\cite{mostafavi_novel_2021}.
 Wavelength length, average amplitude change, and zero crossing taken out of overview of time domain features for surface electromyography (sEMG)~\cite{moctar_time-domain_2023} are generic enough to be tried for machine diagnostic.
-Harmonic features originaly designed for sound description~\cite{peeters_large_2004} could be reused similarily.
-Many features found in the literature are already implemented in Time Series Feature Extraction Library (TSFEL) which is package for Python language~\cite{tsfel}.
+Harmonic features originally designed for sound description~\cite{peeters_large_2004} could be reused similarly.
+Many features found in the literature are already implemented in the Time Series Feature Extraction Library (TSFEL) which is a package for Python language~\cite{tsfel}.
 
 Knowledge of rolling bearings geometry and rotational speed provides a way to calculate bearing defect frequencies for outer race (BPFO), inner race (BPFI), ball (BSF), and cage (FTF)~\cite{mohanty_machinery_2015, ziaran_technicka_2013}.
-There are situation when bearing fault is not evidenced by defect frequency, therefore kurtosis is recommended as it is asociated with impacts~\cite{brito_fault_2021}.
+There are situations when bearing fault is not evidenced by defect frequency.
+Therefore, kurtosis is recommended as it is associated with impacts~\cite{brito_fault_2021}.
 
-Normalization assigns same weights to unbounded variables~\cite{zheng_feature_2018}.
-In three-dimensional motion, either axis aligned only with principal direction of vibrations is retained, or euclidian norm is computed for each feature.
-The magnitude of feature vector was found useful in animal activity recognition from collar tags independent of sensor orientation~\cite{kamminga_robust_2018}.
+Normalization assigns the same weights to unbounded variables~\cite{zheng_feature_2018}.
+In three-dimensional motion, either axis aligned only with the principal direction of vibrations is retained, or the Euclidian norm is computed for each feature.
+The idea of feature vector magnitude comes from animal activity recognition based on collar tags independent of sensor orientation~\cite{kamminga_robust_2018}.
 
-Extracted features lower the number of dimensions from original signal.
-Further dimensionality reduction is caried out with various methods, namely: PCA, t-SNE, ISOMAP, ICA, and AE~\cite{brito_fault_2021}.
-Keeping smaller number of attributes can result in better classification performance.
-However major disadvantage is the removal of the meaning from obtained features.
+Extracted features lower the number of dimensions from the original signal.
+Further dimensionality reduction is carried out with various methods: PCA, t-SNE, ISOMAP, ICA, and AE~\cite{brito_fault_2021}.
+Keeping a smaller number of attributes can result in better classification performance.
+However, the major disadvantage is the lack of meaning in acquired features.
 
-Filtering feature selection methods decrease the feature set size so that the chosen predictors have the strongest relation to categorical predicted variable.
-The relationship is quantified with correlation, fisher score or mutual information and among others~\cite{nandi_condition_2019}.
-The metrics are combined to ensembles by means of electorial methods or rank product~\cite{breitling_rank_2004}.
+Filtering feature selection methods decrease the feature set size so that the chosen predictors are related the strongest to a categorical predicted variable.
+The relationship is quantified with correlation, fisher score, or mutual information and among others~\cite{nandi_condition_2019}.
+The metrics are combined into ensembles using electoral methods or rank product~\cite{breitling_rank_2004}.
 
-Machinery Fault Database (MaFaulDa)~\cite{mafaulda_dataset} or Case Western Reserve University (CWRU) bearings dataset~\cite{cwru_dataset} are routinely used for evaluation of machinery fault models.
-MaFaulDa contains 1951 time series measured on two bearings
-simutanously with three uniaxial accelerometers at sampling rate of 50 kHz.
-Each recording lasts 5 seconds and it represents one of 5 defects but at different loads, shaft shifts, and rotation speeds between 737 to 3686 RPM.
-CWRU dataset has 161 scenarios at sample rates of 12 kHz or 48 kHz.
-Time series captures four different states of bearings on drive end and fan end of the motor.
+Machinery Fault Database (MaFaulDa)~\cite{mafaulda_dataset} or Case Western Reserve University (CWRU) bearings dataset~\cite{cwru_dataset} are commonplace in the evaluation of machinery fault models.
+MaFaulDa contains a 1951 time series measured on two bearings
+simultaneously with three uniaxial accelerometers at a sampling rate of 50 kHz.
+Each recording lasts 5 seconds and represents one of 5 defects but at different loads, shaft shifts, and rotation speeds between 737 to 3686 RPM.
+The CWRU dataset has 161 scenarios at sample rates of 12 kHz or 48 kHz.
+The time series captures four different states of bearings on both sides of the motor.
 
 Classification of faults in machinery diagnostics focuses primarily on bearings health monitoring.
-Review article~\cite{sheng_review_2020} compares strengths and weaknesesses machine and deep learning models.
+Review article~\cite{sheng_review_2020} compares the strengths and weaknesses of the machine learning and deep learning models.
 Power spectral density (PSD) features from vibration signals of journal bearings in combination with k-NN and SVM reached classification accuracy 85.7\% and 100\%, respectively~\cite{moosavian_appropriate_2012}.
-Ball bearing fault diagnostic of CWRU dataset indicate better accuracy of k-NN (98.8\%) than SVM (96.2\%) on frequency-domain features~\cite{jamil_feature-based_2021}.
-Approach based on statistical features utilizing custom test rig compared three models for ball bearing faults: k-NN, SVM, and kernel linear discriminant analysis (KLDA).
-Results showed KLDA achieves best average accuracy on PSD features (99.13\%) followed by k-NN with PSD (95.64\%) and SVM with EMD (80.49\%)~\cite{altaf_new_2022}.
+Ball bearing fault diagnostic of CWRU dataset indicates better accuracy of k-NN (98.8\%) than SVM (96.2\%) on frequency-domain features~\cite{jamil_feature-based_2021}.
+An approach based on statistical features utilizing a custom test rig compared three models for ball bearing faults: k-NN, SVM, and kernel linear discriminant analysis (KLDA).
+Results showed KLDA achieves the best average accuracy on PSD features (99.13\%) followed by k-NN with PSD (95.64\%) and SVM with EMD (80.49\%)~\cite{altaf_new_2022}.
 
-On CWRU dataset SVM performs better in comparison of state-of-the-art methods to random forest (RF) and softmax classifiers.
+On the CWRU dataset, SVM performs better compared to state-of-the-art methods for random forest (RF) and softmax classifiers.
 The best accuracy of SVM is 61.05\% on 5 time domain features (RF 59.07\%, Softmax 48.92\%) and 91.17\% on 64 frequency domain (RF 86.14\%, Softmax 86.05\%) features~\cite{maurya_condition-based_2021}.
-Random forest applied after similarity-based model has a accuracy of 96.43\% on the MaFaulDa and 98.7\% on the CWRU database~\cite{ribeiro_rotating_2017}.
+Random forest applied after the similarity-based model has an accuracy of 96.43\% on the MaFaulDa and 98.7\% on the CWRU database~\cite{ribeiro_rotating_2017}.
 
-In k-NN algorithm the number of neigbors and similarity measure has to be chosen carefully.
-Hassanat distance performes the best on average for k = 1 but is only by 4\% better in situation without noise and 7\% in scenarios with noise when compared to Euclidian distance~\cite{abu_alfeilat_effects_2019}.
-Categories in dataset fed into k-NN classifier should be balanced in size otherwise precision drops 15\% to over 40\% depending on imbalance ratio~\cite{shi_improving_2020}.
+In the k-NN algorithm, the number of neighbors and similarity measure has to be chosen carefully.
+Labels in the dataset should be balanced in size when they are intended for the k-NN classifier.
+Otherwise, precision of the model drops 15\% to over 40\% depending on the imbalance ratio~\cite{shi_improving_2020}.
 
@@
 The two principal questions regarding automated machinery fault diagnostics from vibrations are investigated in this study.
-How does reducing number of features and different feature selection methods impact k-nearest neighbors multiclass classifier accuracy with varying k parameter?
-This first exploration takes place in supervised manner with 5-fold cross validation on preprocessed MaFaulDa dataset.
-Then the challanges are presented of how to apply same procedures to the monitoring solution of municipal water pumping station?
+How does reducing the number of features and different feature selection methods impact k-nearest neighbors multiclass classifier accuracy with varying k parameters?
+This first exploration is done by supervised learning with 5-fold cross-validation on a preprocessed MaFaulDa dataset.
+Then the challenges are presented of applying the same procedures to the monitoring solution of municipal water pumping station.
 Calibrated data from existing pump monitoring provided by the vendor on the site is taken as a reference.
 
-Classification of MaFaulDa dataset are caried out for extracted features in time domain (TD) and frequency domain (FD) separately.
-The accuracy is determined for features in radial axis $y$ and euclidian norm of all directions (Fig.~\ref{fig:mafaulda-simulator})  Experiments include different combination of selected attributes according to predefined conditions:
+Classification of the MaFaulDa dataset is carried out for extracted features in the time domain (TD) and frequency domain (FD) separately.
+The accuracy is determined for features in radial axis $y$ and Euclidian norm of all directions (Fig.~\ref{fig:mafaulda-simulator})  Experiments include different combinations of selected attributes according to predefined conditions:
 \begin{enumerate}
-\item whole feature set with k value as odd number in range from 1 to 37,
-\item dimensionality reduction using pricipal components analysis (PCA) of whole feature set to 3 principal components ($k = 5$),
-\item every combination of 3, 4, 5 member feature subsets with k value being sequentially: 3, 5, 11, 15 (results in $\sum_{j = 3}^{5}{n\choose j}$ models for individual k value),
-\item best feature subset picked using feature selection methods: mean of point-biserial correlation to every class as a dichotomous variable, ANOVA F-value and mutual infomation ($k = 5$).
+\item whole feature set with k value as an odd number in the range from 1 to 37,
+\item dimensionality reduction using principal components analysis (PCA) of the whole feature set to 3 principal components ($k = 5$),
+\item every combination of 2, 3, 4, 5 member feature subsets with k value being sequentially: 3, 5, 11, 15 (results in $\sum_{j = 2}^{5}{n\choose j}$ models for individual k value),
+\item best feature subset picked using feature selection methods: mean of point-biserial correlation to every class as a dichotomous variable, ANOVA F-value, and mutual information ($k = 5$).
 \end{enumerate}
@@
 
-Data preprocessing of MaFaulDa is necessary to create feature sets in TD and FD. This process of several phases.
+Data preprocessing of MaFaulDa is necessary to create feature sets in TD and FD. This process has several phases.
 \begin{enumerate}
-\item \textbf{Signal filtering}: Subtraction of overall mean removes DC component. IIR Butterworth low pass filter of 5th order attenuates frequencies above above 10 kHz.
-\item \textbf{Feature extraction}: Machine behavior in one time series is time-invariant therefore each feature is calculated out of whole duration.
+\item \textbf{Signal filtering}: Subtraction of overall mean removes DC component. IIR Butterworth low pass filter of 5th order attenuates frequencies above 10 kHz.
+\item \textbf{Feature extraction}: Machine behavior in one time series is time-invariant.
+Therefore, features are calculated out of the whole duration.
 Frequency domain features are produced using Welch's method for power spectrums from FFT with $2^{15}$ long Hann windows and 50\% overlap  (bin resolution of 1.53~Hz).
@@
 \begin{enumerate}
-\item \textbf{10 time domain features} (TD): peak-to-peak amplitude, zero-crossing rate, root mean square, skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change,
-\item \textbf{11 frequency domain features} (FD): spectral centroid, standard deviation, skewness, kurtosis, roll on frequency of 5\% total energy, roll off frequency of 85\% total energy, spectral flux as a average correlation of separate windows, noisiness as a signal to noise ratio, spectral negentropy~\cite{avoci_spectral_2020}, energy, entropy.
+\item \textbf{10 features in time domain} (TD): peak-to-peak amplitude, zero-crossing rate, root mean square, skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change,
+\item \textbf{11 features in frequency domain} (FD): spectral centroid, standard deviation, skewness, kurtosis, roll-on frequency of 5\% total energy, roll-off frequency of 85\% total energy, spectral flux as an average correlation of separate windows, noisiness as a signal to noise ratio, spectral negentropy~\cite{avoci_spectral_2020}, energy, entropy.
 \end{enumerate}
-\item \textbf{Labeling}: Three target variables are constructed out of inner bearing, both bearings, and high severity defects on both bearings.
-Predicted variable has 6 classes: normal, misalignment (merged vertical and horizontal), imbalance, outer race fault, ball fault, cage fault.
-In high severity scenario, the normal class is assigned to observations where weight or shaft shift applied is in half below 60\% of all configuations for that fault.
+In summary 627 time domain and 1012 frequency domain feature subsets are evaluated by the same number of 5-fold cross-validated k-NN models for each value of k. 
+\item \textbf{Labeling}: Three target variables are constructed out of the inner bearing, both bearings and high severity defects on both bearings.
+The predicted variable has 6 classes: normal, misalignment (merged vertical and horizontal), imbalance, outer race fault, ball fault, and cage fault.
+In the "high severity" scenario, the normal class is assigned to observations where the weight or shaft shift applied is in lower half of all of the configurations for that fault numbered from least to most severe.
 \item \textbf{Class balancing}: Random oversampling strategy is used on all classes except the majority one.
@@
 
-Vibrations from pumps in municipal pumping station for drinking water in Podunajské Biskupice reveal practical challenges for deployment of machine learning models in the industry.
-Two pumps (P1, P2) of the same type KSB Omega 300-560 and two electric motors WEG W50 (M1, M2) were designated for measurements.
-Both machines have power 400~kW (ISO 20186 class~\rom{3}) and main shaft rotates at 1493~RPM.
-For purposes of expert labeling, the bearing designations at numbered places are: 6319-C3 (1), 6324-C3 (2), 6317-2Z (3 \& 4).
+Vibrations from pumps in municipal pumping station for drinking water in Podunajské Biskupice reveal practical challenges for the deployment of machine learning models in the industry.
+Two pumps (P1, P2) of the same type KSB Omega 300-560, and two electric motors WEG W50 (M1, M2) were designated for measurements.
+Both machines have power 400~kW (ISO 20186 class~\rom{3}) and the main shaft rotates at 1493~RPM.
+For purposes of expert labeling, the bearing designations at numbered places are 6319-C3 (1), 6324-C3 (2), and 6317-2Z (3\&4).
+Sensors were placed above bearings in numbered positions according to ISO 13373 (Fig.~\ref{fig:water-pump}) with axis orientation depicted in Fig.~\ref{fig:steval-sensor}.
+Each pump is equipped with KSB cloud monitoring at the place (3) (Fig.~\ref{fig:ksb-cloud-sensor}) from which RMS velocity in mm/s is available for a year in hourly intervals.
 
-Sensor were placed above bearings in numbered positions according to ISO 13373 (Fig.~\ref{fig:water-pump}) with axis orientation depicted in Fig.~\ref{fig:steval-sensor}.
-Each pump is equipped with KSB cloud monitoring at place (3) (Fig.~\ref{fig:ksb-cloud-sensor}) from which rms velocity in mm/s is available for year in hourly intervals.
-
-Our accelerometer ST IIS3DWB mounted to machine unig thin double sided tape has wideband 5 kHz linear response is sampled at 26.87~kHz.
-Microcontroller ESP32-POE-ISO stored triaxial 60 second long recordings onto SD card.
+Our accelerometer ST IIS3DWB mounted to the machine using thin double-sided tape has a wideband 5 kHz linear response sampled at 26.87~kHz.
+Microcontroller ESP32-POE-ISO stored triaxial 60-second long recordings onto an SD card.
 In total 48 time series were gathered, 6 in each place.
-These are furter split to 5 second interval for 576 data points overall.
-
-The signal preprocessing is similiar which exceptions that low-pass filter is left out and FFT window size is set to $2^{14}$ (bin resolution of 1.64~Hz).
-Fault labels are missing therefore we analyse rotational speeds and defect bearing frequencies in the frequency spectrum.
-As an alternative, the observations are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.
-Another classfier is made solely with P1-3 and P2-3 placements.
-Classification is done for features in main axis of motion (z) and euclidian norm of same features in all directions.
+These are split into 5-second intervals for 576 data points overall.
+Fault labels are missing, therefore we analyze rotational speeds and defective bearing frequencies in the frequency spectrum.
+The observations form machines are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.
 
 \section{Results}
+In qualitative exploratory data analysis, representative observations from both datasets are examined through their frequency spectra in the radial direction.
+Patterns for categories of faults in MaFaulDa with shaft speed around 2500 RPM and in conditions of the worst severity are depicted in the wideband spectrum with a range up to 2.5 kHz (Fig.~\ref{fig:mafaulda-wideband}).
+Clear distinctions in spectra are apparent for different labels.
+The rotational frequency shows up as a spike in each case and is the only one in a normal state.
+Misalignment gives rise in amplitude to \nth{6} RPM harmonic, whereas imbalance excites even more harmonic frequencies.
+
 \begin{figure}
@@
          \includegraphics[width=\textwidth]{fig/spectrum/mafaulda-wideband.png}
-         \caption{MaFaulda}
+         \caption{MaFaulDa}
          \label{fig:mafaulda-wideband}
@@
          \centering
-         \includegraphics[width=\textwidth]{fig/spectrum/motor-wideband.png}
+         \includegraphics[width=\textwidth]{fig/spectrum/motor-wideband-60s.png}
          \caption{Motors}
@@
          \centering
-         \includegraphics[width=\textwidth]{fig/spectrum/pump-wideband.png}
+         \includegraphics[width=\textwidth]{fig/spectrum/pump-wideband-60s.png}
          \caption{Pumps}
-         \label{fig:motor-wideband}
+         \label{fig:pump-wideband}
      \end{subfigure}
@@
 
-\begin{figure}
-     \begin{subfigure}[b]{0.3\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/spectrum/mafaulda-fault.png}
-         \caption{MaFaulda}
-         \label{fig:mafaulda-fault}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.3\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/spectrum/motor-fault.png}
-         \caption{Motors}
-         \label{fig:motor-fault}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.3\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/spectrum/pump-fault.png}
-         \caption{Pumps}
-         \label{fig:pump-fault}
-     \end{subfigure}
-     \caption{Shaft and bearing defect frequencies}
-\end{figure}
+The wideband spectrum of the electric motor is polluted by the wind coming out of the back fan blades (Fig~\ref{fig:motor-wideband}).
+Pump spectra are lookalike in the same respective positions (Fig~\ref{fig:pump-wideband}).
+P1 has significantly more energy than P2 in frequency bands around 2.5 kHz, 3.6 kHz, and 5 kHz and in low frequencies.
+This energy can indicate a fault in the early stages because amplitudes are not tall enough.
+The range of amplitudes measured is at most $\pm 50$ m/$s^2$.
 
-\begin{table}
-\centering
-\caption{Numbers of observations by label in MaFaulDa}\label{tab:mafaulda-observation-counts}
-\begin{tabular}{|l|r|r|r|}
-\hline
-\textbf{Label} &  \textbf{Bearing A} & \textbf{Both bearings} & \textbf{High severity} \\
-\hline
-normal            &  49  &  49  &  1125 \\
-misalignment      & 498  &  498 & 198 \\
-imbalance         & 333  &  333 & 139 \\
-cage fault        & 188  &  376 & 181 \\
-ball fault        & 186  &  323 & 132 \\
-outer race fault  & 184  &  372 & 176 \\
-\hline
-$\Sigma$ & 1438  & 1951 & 1951 \\
-\hline
-\end{tabular}
-\end{table}
+The long-term vendor's pump monitoring system confirms that the velocity of vibrations is still in normal conditions.
+Levels in radial axis (z) are almost identical for both pumps circa 1.6 mm/s (Fig.~\ref{fig:ksb-rms}).
 
@@
      \end{subfigure}
-     \caption{RMS vibrations of pumps and ISO severity levels}
+     \caption{Vibrations of water pumps and ISO severity levels}
+     \label{fig:ksb-rms}
 \end{figure}
 
-% Identical plots for one axis and multiple axis
+\begin{table}
+\centering
+\caption{Numbers of observations by label in MaFaulDa}
+\label{tab:mafaulda-observation-counts}
+\begin{tabular}{|l|r|r|r|}
+\hline
+\textbf{Label} &  \textbf{Bearing A} & \textbf{Both bearings} & \textbf{Severity} \\
+\hline
+normal            &  49  &  49  &  1125 \\
+misalignment      & 498  &  498 & 198 \\
+imbalance         & 333  &  333 & 139 \\
+cage fault        & 188  &  376 & 181 \\
+ball fault        & 186  &  323 & 132 \\
+outer race fault  & 184  &  372 & 176 \\
+\hline
+$\Sigma$ & 1438  & 1951 & 1951 \\
+\hline
+\end{tabular}
+\end{table}
+
+Scatter plots (Fig.~\ref{fig:mafaulda-scatter}, \ref{fig:pump-scatter}) visualize the spatial distribution of labels for entire feature sets after min-max scaler and PCA.
+Explained variance percentages are next to the component's name.
+Labels are assigned in three different ways producing observation counts according to Table~\ref{tab:mafaulda-observation-counts}.
+The imbalance ratio in the MaFaulDa dataset is 1016\% for original classes and 852\% for high-severity modification.
+Colored regions are decision boundaries of the k-NN classifier trained on 80\% of the PCA transformed dataset.
+
+Misalignment and ball fault groups are separated the best from the rest but the imbalance group is intertwined with bearing faults.
+Silhouette scores of the feature sets of the MaFaulDa after min-max scaling are 0.05 (TD) and 0.14 (FD).
+Sensor placements on pumps have silhouette scores of 0.20 (TD) and 0.21 (FD).
+
 \begin{figure}
+	\centering
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-a-bearing.png}
+         \caption{Bearing A in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-a-bearing.png}
+         \caption{Bearing A in FD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-severity.png}
+         \caption{Severity in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-severity.png}
+         \caption{Severity in FD}
+     \end{subfigure}
+     \caption{PCA scatter plots of MaFaulDa with 5-NN decision boundaries}
+     \label{fig:mafaulda-scatter}
+\end{figure}
+
+\begin{figure}[h]
+	\centering
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-td.png}
+         \caption{Positions in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-fd.png}
+         \caption{Positions in FD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-td.png}
+         \caption{P1-3/P2-3 in TD}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.24\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-fd.png}
+         \caption{P1-3/P2-3 in FD}
+     \end{subfigure}
+     \caption{PCA scatter plots of pumps with 5-NN decision boundaries}
+     \label{fig:pump-scatter}
+\end{figure}
+
+The increase in hyperparameter of k for whole feature sets results in less accuracy of k-NN (Fig.~\ref{fig:accuracy-all-features}).
+The sharp decline of more than 10\% in some cases is noticeable for k between 1 and 9.
+The features extracted in the time domain have overall better accuracy than those in the frequency domain.
+The attributes combined from all sensor directions also reach better accuracies than just from a single axis.
+
+\begin{figure}
+	% One axis
+	\centering
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/one-axis-a-bearing.png}
+         \caption{One axis, Bearing A}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/one-axis-all-bearings.png}
+         \caption{One axis, Both bearings}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.32\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/all-features-mafaulda/one-axis-severity.png}
+         \caption{One axis, High severity}
+     \end{subfigure}
+     \hfill
+     % All axis
      \begin{subfigure}[b]{0.32\textwidth}
@@
          \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-a-bearing.png}
-         \caption{Bearing A}
+         \caption{All axis, Bearing A}
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-all-bearings.png}
-         \caption{Both bearings}
+         \caption{All axis, Both bearings}
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{fig/all-features-mafaulda/all-axis-severity.png}
-         \caption{High severity}
+         \caption{All axis, High severity}
      \end{subfigure}
-     \caption{Whole feature sets in TD and FD from MaFaulDa}
+     \caption{Accuracy on MaFaulDa feature sets TD and FD depending on k value}
+     \label{fig:accuracy-all-features}
 \end{figure}
 
-\begin{figure}
-     \begin{subfigure}[b]{0.32\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/all-features-pumps/machine.png}
-         \caption{Machines}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.32\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/all-features-pumps/position.png}
-         \caption{Positions}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.32\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/all-features-pumps/binary.png}
-         \caption{Pumps on position 3}
-     \end{subfigure}
-     \caption{Whole feature sets in TD and FD from water pumps}
-\end{figure}
-
-% All bearings
-\begin{figure}
-	\centering
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-all-bearings.png}
-         \caption{Both bearings in TD}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-severity.png}
-         \caption{High severity in TD}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-all-bearings.png}
-         \caption{Both bearings in FD}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-severity.png}
-         \caption{High severity in TD}
-     \end{subfigure}
-     \caption{PCA scatter plots of MaFaulDa with k-NN decision boundaries (k = 5)}
-\end{figure}
+The tendency of decrease in accuracy with an increase in number of neighbors holds even in feature subsets (Fig.~\ref{fig:all-models-bearings-f-3}, \ref{fig:all-models-severity-f-3}).
+The k-NN trained with any 3 features from FD have accuracy distribution shifted higher than TD, contrary to whole feature sets.
+Picking a model with $k < 15$ at random always guarantees better than chance accuracy.
+Increasing the number of features increases the k-NN accuracies for both domains and scenarios at any k value (Fig.~\ref{fig:all-models-bearings-k-5}, \ref{fig:all-models-severity-k-5}).
 
@@
          \centering
-         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-td.png}
-         \caption{Positions in TD}
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-a-bearing-f3.png}
+         \caption{Bearing A}
+         \label{fig:all-models-bearings-f-3}
      \end{subfigure}
@@
          \centering
-         \includegraphics[width=\textwidth]{fig/scatter-pumps/position-fd.png}
-         \caption{Positions in FD}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-td.png}
-         \caption{P1-3 and P2-3 in TD}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/scatter-pumps/binary-fd.png}
-         \caption{P1-3 and P2-3 in FD}
-     \end{subfigure}
-     \caption{PCA scatter plots of water pumps with k-NN decision boundaries (k = 5)}
-\end{figure}
-
-% All axis
-% by words relation to one axis, and one bearings
-% Pumps - spectral is better
-\begin{figure}
-	\centering
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-all-bearings-f3.png}
-         \caption{Both bearings f=3}
-     \end{subfigure}
-     \hfill
-     \begin{subfigure}[b]{0.45\textwidth}
-         \centering
-         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-all-bearings-f3.png}
-         \caption{Both bearings f=3}
+         \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-a-bearing-k5.png}
+         \caption{Bearing A}
+         \label{fig:all-models-bearings-k-5}
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-severity-f3.png}
-         \caption{High severity k = 5}
+         \caption{High severity}
+         \label{fig:all-models-severity-f-3}
      \end{subfigure}
@@
          \includegraphics[width=\textwidth]{fig/combinations-mafaulda/all-axis-severity-k5.png}
-         \caption{High severity k = 5}
+         \caption{High severity}
+         \label{fig:all-models-severity-k-5}
      \end{subfigure}
@@
 
-%TODO
-% Table of accuracies for Maufaulda for rainbow bar plot (test set)
+Tables~\ref{tab:fsel-methods-td} and \ref{tab:fsel-methods-fd} compare the average 5-fold test accuracy of different feature selection methods for the k-NN model with k = 5.
+Three-axis features have better accuracy for original classes but perform worse than single axes after relabeling for high-severity faults.
 
-% Table for pumps
+\begin{table}
+\centering
+\caption{Accuracy of k-NN in TD feature set and subsets of 3}
+\label{tab:fsel-methods-td}
+\begin{tabular}{|r|l|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|}
+\hline
+\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Axis}}} & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Method}}} & \multicolumn{2}{l|}{\textbf{Bearing A}}                                  & \multicolumn{2}{l|}{\textbf{Both Bearings}}                              & \multicolumn{2}{l|}{\textbf{High severity}}                              \\ \cline{3-8}
+\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                                 & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} \\ \hline
+\multirow{7}{*}{1}                                   & All features                                          & \textit{94.56}                      & 89.99                              & \textit{89.45}                      & 83.53                              & \textit{94.93}                      & 91.60                              \\
+                                                     & PCA 3 PC                                              & \textit{88.63}                      & 80.09                              & \textit{82.87}                      & 73.66                              & \textit{92.17}                      & 87.22                              \\
+                                                     & Best 3 features                                       & \textit{91.98}                      & 85.37                              & \textit{85.56}                      & 78.48                              & \textit{93.90}                      & 89.64                              \\
+                                                     & Rank product                                          & \textit{87.96}                      & 79.99                              & \textit{80.71}                      & 71.42                              & \textit{93.07}                      & 88.50                              \\
+                                                     & Correlation                                           & \textit{88.83}                      & 80.99                              & \textit{81.40}                      & 72.83                              & \textit{93.07}                      & 88.50                              \\
+                                                     & F-statistic                                           & \textit{87.53}                      & 79.08                              & \textit{80.71}                      & 71.42                              & \textit{93.07}                      & 88.50                              \\
+                                                     & Mutual information                                    & \textit{87.06}                      & 78.75                              & \textit{80.71}                      & 71.42                              & \textit{93.07}                      & 88.50                              \\ \hline
+\multirow{7}{*}{3}                                   & All features                                          & \textit{95.98}                      & 92.54                              & \textit{91.52}                      & 85.64                              & \textit{95.37}                      & 92.82                              \\
+                                                     & PCA 3 PC                                              & \textit{91.17}                      & 84.74                              & \textit{85.41}                      & 77.64                              & \textit{93.53}                      & 89.15                              \\
+                                                     & Best 3 features                                       & \textit{91.91}                      & 85.57                              & \textit{86.04}                      & 78.01                              & \textit{93.75}                      & 90.14                              \\
+                                                     & Rank product                                          & \textit{90.09}                      & 83.90                              & \textit{83.90}                      & 76.11                              & \textit{93.62}                      & 89.96                              \\
+                                                     & Correlation                                           & \textit{91.44}                      & 84.87                              & \textit{83.90}                      & 76.11                              & \textit{93.66}                      & 90.12                              \\
+                                                     & F-statistic                                           & \textit{90.09}                      & 83.90                              & \textit{83.90}                      & 76.11                              & \textit{93.62}                      & 89.96                              \\
+                                                     & Mutual information                                    & \textit{91.44}                      & 84.87                              & \textit{83.90}                      & 76.11                              & \textit{93.62}                      & 89.96                          \\
+
+                                                     \hline                     
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Accuracy of k-NN in FD feature set and subsets of 3}
+\label{tab:fsel-methods-fd}
+\begin{tabular}{|r|l|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|p{1.2cm}|}
+\hline
+\multicolumn{1}{|l|}{\multirow{2}{*}{\textbf{Axis}}} & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Method}}} & \multicolumn{2}{l|}{\textbf{Bearing A}}                                  & \multicolumn{2}{l|}{\textbf{Both Bearings}}                              & \multicolumn{2}{l|}{\textbf{High severity}}                              \\ \cline{3-8}
+\multicolumn{1}{|l|}{}                               & \multicolumn{1}{l|}{}                                 & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} \\ \hline
+\multirow{7}{*}{1}                                   & All features                                          & \textit{88.14}                      & 80.02                              & \textit{83.12}                      & 73.86                              & \textit{94.63}                      & 90.53                              \\
+                                                     & PCA 3 PC                                              & \textit{83.85}                      & 74.26                              & \textit{77.94}                      & 67.57                              & \textit{92.02}                      & 87.33                              \\
+                                                     & Best 3 features                                       & \textit{88.64}                      & 81.53                              & \textit{82.43}                      & 74.67                              & \textit{93.70}                      & 89.44                              \\
+                                                     & Rank product                                          & \textit{86.85}                      & 78.28                              & \textit{82.24}                      & 72.92                              & \textit{92.93}                      & 89.23                              \\
+                                                     & Correlation                                           & \textit{80.53}                      & 68.01                              & \textit{73.47}                      & 61.04                              & \textit{92.93}                      & 89.23                              \\
+                                                     & F-statistic                                           & \textit{86.85}                      & 78.28                              & \textit{82.24}                      & 72.92                              & \textit{92.93}                      & 89.23                              \\
+                                                     & Mutual information                                    & \textit{87.88}                      & 80.49                              & \textit{78.55}                      & 68.21                              & \textit{92.93}                      & 89.23                              \\ \hline
+\multirow{7}{*}{3}                                   & All features                                          & \textit{93.64}                      & 88.49                              & \textit{89.51}                      & 82.83                              & \textit{94.90}                      & 91.49                              \\
+                                                     & PCA 3 PC                                              & \textit{87.12}                      & 79.18                              & \textit{82.09}                      & 74.33                              & \textit{91.84}                      & 86.96                              \\
+                                                     & Best 3 features                                       & \textit{92.71}                      & 87.48                              & \textit{88.30}                      & 81.96                              & \textit{93.80}                      & 90.72                              \\
+                                                     & Rank product                                          & \textit{87.58}                      & 79.08                              & \textit{82.63}                      & 73.90                              & \textit{93.48}                      & 89.99                              \\
+                                                     & Correlation                                           & \textit{84.45}                      & 74.87                              & \textit{82.63}                      & 73.90                              & \textit{93.48}                      & 89.99                              \\
+                                                     & F-statistic                                           & \textit{90.51}                      & 84.30                              & \textit{82.43}                      & 74.40                              & \textit{93.48}                      & 89.99                              \\
+                                                     & Mutual information                                    & \textit{90.27}                      & 83.03                              & \textit{85.35}                      & 78.88                              & \textit{92.76}                      & 88.74                     \\
+                                      \hline                    
+\end{tabular}
+\end{table}
+
+Vibrations from just bearing A cannot reliably detect bearing faults in position B, located on the opposite end of the shaft.
+Average drops in accuracy to diagnose both bearings from the same position are 7.81\% (TD) and 5.18\% (FD) for 3-axis features.
+Rank product of feature selection methods does not always perform better than the individual ones but provides an acceptable middle-ground.
+
+All extracted features for bearing A reach accuracies of 92.54\% (TD) and 88.49\% (FD).
+The best subset of the three features is worse by 6.97\% (TD) and 2.92\% (FD).
+Rank product regularly picks model with accuracy on upper quartile Q3 of k-NN accuracy distribution, but there is still room for improvement to the best subset.
+In high-severity situations, the classifier performance is better for TD with three-dimensional features: 92.82\% (TD), 91.49\% (FD).
+Features selected by rank product have accuracy larger than principal components with differences 1.28\% (TD), 2.66\% (FD).
+
+\begin{figure}
+	\centering
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/td-rank-features.png}
+         \caption{TD features (Accuracy = 83.90\%)}
+     \end{subfigure}
+     \hfill
+     \begin{subfigure}[b]{0.45\textwidth}
+         \centering
+         \includegraphics[width=\textwidth]{fig/scatter-mafaulda/fd-rank-features.png}
+         \caption{FD features (Accuracy = 79.08\%)}
+     \end{subfigure}
+     \hfill
+     \caption{Best 3 features for bearing A chosen by rank product}
+     \label{tab:scatter-rank-product}
+\end{figure}
+
+The most commonly chosen subset of features by rank product are in order of decreasing popularity in the time domain: zero-crossing rate, root mean square, peak-to-peak, and in the frequency domain: roll-off frequency, centroid, flux, or entropy.
+Figure~\ref{tab:scatter-rank-product} shows clustering abilities of selected feature space for bearing A.
+Scale of attributes values are inverse of mix-max scaler function.
+
+Features expressing machinery vibration amplitude, chaos, or richer frequency content look to be better predictors of fault types.
+The potential design of new features should follow these observations.
 
 \section{Conclusions}
+We reviewed processes and standards for vibration monitoring of rotating machinery using accelerometers.
+The aim is to diagnose faults of the machinery parts with a machine learning model and fewer features to make results more comprehensible.
+The related work includes low-level feature extraction as an important preprocessing step to reduce information from vibration signals.
+
+We built an embedded system with ESP32 MCU capable of recording vibrations from water pumps.
+Based on the data analysis of collected data, we discussed the problems with the implementation of a diagnostic model for machinery in the industry.
+
+We developed the data pipeline with signal preprocessing and the k-nearest neighbors model for the MaFaulDa dataset.
+The bigger k values cause less accuracy for all feature spaces.
+Increasing the number of features taken out of the same feature set improves classification accuracy.
+The rank product balances the performance of other feature selection methods in the ensemble and reaches accuracies close to the upper quartile of the model distribution.
+
+The best validation accuracies found for one bearing when using just three features picked by rank product are 83.90\% (TD) and 79.08\% (FD).
+It is less than the accuracy for the best subset of three features by 1.82\% (TD), 5.13\% (FD), and is less than for the whole feature set.
+Relabeling faults to be only those with high severity gives an accuracy of three features for both bearings 89.96\% (TD) and 89.99\% (FD).
+Testing out different base feature sets could bring improvements for so few features.
 

### 2024-04-09 iit-src/paper.tex
EDA of stnding fan to calibrate

@@
 Fault labels are missing, therefore we analyze rotational speeds and defective bearing frequencies in the frequency spectrum.
-The observations form machines are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.
+The observations from machines are labeled based on source machinery to 4 classes: M1, M2, P1, P2; based on sensor position to 8 classes: M1-1, M1-2, P1-3, P1-4, etc.
 
@@
 Tables~\ref{tab:fsel-methods-td} and \ref{tab:fsel-methods-fd} compare the average 5-fold test accuracy of different feature selection methods for the k-NN model with k = 5.
-Three-axis features have better accuracy for original classes but perform worse than single axes after relabeling for high-severity faults.
+Three-axis features reach better accuracy the one-axis ones.
 

### 2024-04-13 thesis/chapters/02-analysis.tex
Refactor jupyter

\chapter{Problem analysis} \label{chapter:problem-analysis}
In the problem analysis chapter we explore the feature engineering methods and machine learning algorithms for fault diagnostics. The basis we build upon is the domain knowledge of mechanical engineers in vibration signal measurement and its evaluation.

\input{chapters/analysis/1-condition-monitoring}
\input{chapters/analysis/2-features}
\input{chapters/analysis/3-diagnostics}
\input{chapters/analysis/4-datasets}

### 2024-04-13 thesis/chapters/05-evaluation.tex
Refactor jupyter

\chapter{Evaluation} \label{section:evaluation} 
% Notebooky:
% MAFAULDA preprocessing - feature extraction and helper

% Vyhodnotenie experimentov - výsledky

% Remove anomaly and replace with 2 severity levels - MAFAULDA

% Fan firmware validation
% Speed estimation - spectroid app, audio
% Acc from three diffent places

% Offline - KNN
% MafaulDa labeling:
% Bez aj stĺpce pre B nielen A a zdvojnásob dataset pri A+B
% A, B, A+B, A-severity-0.5, B-severity-0.5, A+B-severity-0.5
% main axis / 3 axis

% Explanatory analysis
	% Korelácia s RPM
	% Rozsah hodnôt features
% All features - MaFaulDa: (FD, TD, FD+TD), CWRU: (FD, TD, FD+TD)
% All combinations - k-values, feature values
% Feature selection methods - choose best features for all feature values and k-values (in which quantile of distribution of all cominations)
% 	- Evolution of rank product based on k
% Scatter plots in 3D and decision boundaries of best features

% DBSCAN - determine parameters (eps, ...), Silhoutte score

% Online - KNN
% Progressive valuation - severity of how is data sorted
	% Sorting - postupne rastúca severita u všetkých chýb rovnako
	% - Náhodne začne vybiehať každá
% Different kinds of windows
	% Same experiments as in offline
	% - All features
	% - All cominations
	% - Feature selection methods

% Uchovať všetky features po neajkú hranicu n generácii
% Skórovať priebežne cez rank product podľa stability faktora a n-generáciach - koľko generácii si držia poradie a s akým náskokom

% Analýza vibrácii z čerpadiel
% kompresory
% pumpy - ksb
% pumpy - ksb cloud
% pumpa - sigma

% Mafaulda

% CWRU

### 2024-04-13 thesis/chapters/06-conclusion.tex
Refactor jupyter

--- 2024-01-01 thesis/chapters/05-conclusion.tex
@@
 Annotations can be assigned belatedly or even never.
-Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
+Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
 The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

### 2024-04-13 thesis/chapters/analysis/1-condition-monitoring.tex
Refactor jupyter

--- 2024-03-11 thesis/chapters/02-analysis-A-CdM.tex
@@
 
+%TODO bearing image / equations
+
 \subsection{Technical standards} \label{section:technical-standards}
@@
 According to the bathtub curve~(Fig.~\ref{fig:bathtub-curve}) reference signatures should be obtained after the initial part wear-in period.
-The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band ~\cite{ziaran_technicka_2013}.
+The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band~\cite{ziaran_technicka_2013}.
 

### 2024-04-13 thesis/chapters/analysis/2-features.tex
Refactor jupyter

--- 2024-03-23 thesis/chapters/02-analysis-B-features.tex
@@
 These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
-Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor \cite{brito_fault_2021}.
+Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor~\cite{brito_fault_2021}.
 It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.

### 2024-04-13 thesis/chapters/analysis/3-diagnostics.tex
Refactor jupyter

--- 2024-01-01 thesis/chapters/02-analysis-C-diagnostics.tex
@@
 
-\textbf{K-nearest neighbors} (kNN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
+\textbf{K-nearest neighbors} (k-NN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
 It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations.
-The major drawback of KNN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}.
+The major drawback of k-NN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}.
 The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
-The KNN algorithm requires features to be normalized to assign the same importance to each predictor.
+The k-NN algorithm requires features to be normalized to assign the same importance to each predictor.
 
@@
         \includegraphics[width=\textwidth]{assets/analysis/KNN.png}
-        \caption{KNN with k = 5}
+        \caption{k-NN with k = 5}
         \label{fig:KNN}
@@
 \end{tabular}
-\caption{Distance metrics for KNN}
+\caption{Distance metrics for k-NN}
 \label{tab:KNN-distance}
@@
 The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics.
-On the CWRU bearing dataset, the KNN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - KNN 91.2\%, SVM 88.8\%, and frequency domain features - KNN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
+On the CWRU bearing dataset, the k-NN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - k-NN 91.2\%, SVM 88.8\%, and frequency domain features - k-NN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
 
-Comparison of KNN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
-Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with KNN classifiers and Mahalanobis metric.
+Comparison of k-NN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
+Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with k-NN classifiers and Mahalanobis metric.
 The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
-Despite KNN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.
+Despite k-NN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.
 

### 2024-04-13 thesis/chapters/analysis/4-datasets.tex
Refactor jupyter

--- 2023-12-17 thesis/chapters/02-analysis-D-datasets.tex
@@
 
-\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearings abnormalities.
+\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearing abnormalities.
 \emph{CWRU dataset} focuses solely on faults in ball bearings.
-Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during revolution speed up.
+Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during speed up.
 
@@
 Each series has 5~seconds in duration and is captured at 50 kHz.
-Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
+Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $\mathrm{m/s}^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$.
 
@@
 
-Observations were conducted in three cardinal axes simultaneously with 2 sets of accelerometers each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}).
+Observations were conducted on three cardinal axes simultaneously with 2 sets of accelerometers, each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}).
 Additionally, a magnetic speedometer produced a pulse on shaft turn.
-The cardioid condenser microphone recorded sound emissions with a frequency range 20~Hz - 20~kHz.
+The cardioid condenser microphone recorded sound emissions at a frequency range 20~Hz - 20~kHz.
 Sensors were fed into a four-channel dynamic signal acquisition module.
@@
 This database contains normal operating conditions, faults out of unbalance, horizontal and vertical shaft misalignment, and three types of faulty bearings in inner and outer positions: outer track, inner track, rolling elements~\cite{pestana-viana_influence_2016}.
+
 \begin{itemize}
 \itemsep0pt
-\item \textbf{Normal} conditions are baseline without the adverse effect of fault in 49 different rotation speeds. 
-\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight adding to 333 mass unbalance loads. 
-\item \textbf{Vertical misalignment} set is comprised of 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
+
+\item \textbf{Normal} conditions are baseline without the adverse effect of fault at 49 different rotation speeds.
+
+\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight, adding to 333 mass unbalance loads.
+
+\item \textbf{Vertical misalignment} set comprises 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
+
 \item \textbf{Horizontal misalignment} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
+
 \item \textbf{Bearing faults} are unnoticeable without unbalance.
 Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect.
-Each unbalance mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
+Each mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
 \end{itemize}
@@
 
-The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz, exclusively for drive end bearings samples were taken at 48 kHz.
-The duration of the time series is varied from 5 to 40 seconds.
-Drive end and fan end bearings signals are measured in each experiment.
-Accelerometer was sometimes mounted on the supporting base plate.
+The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz.
+For drive end bearings, samples were taken at 48 kHz.
+The duration of the time series varies from 5 to 40 seconds.
+Drive end and fan end bearing signals are measured in each experiment.
+Accelerometer was sometimes mounted on the supporting baseplate.
 
@@
 The setup is shown in Fig.~\ref{fig:rotating-shaft}.
-Mass of 3.28 grams (or 6.61 grams during severe unbalance test) is attached to unbalance holder successively in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm.
+A mass of 3.28 grams (or 6.61 grams during the severe unbalance test) is attached to the unbalance holder in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm.
 The rotation speed of the motor is perpetually rising between 630 and 2330 rpm in development datasets (marked with suffix D) and speeds from 1060 to 1900 rpm in the evaluation datasets (suffix E).
-The vibrations were recorded at a sampling rate of 4 kHz~\cite{mey_machine_2020}.
+The vibrations were recorded at a sampling rate of 4~kHz~\cite{mey_machine_2020}.
 
@@
 
-The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $m/s^2$.
+The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$.
 These sensor parameters are the same as in the case of MaFaulDa.

### 2024-04-13 thesis/chapters/appendix/C-user-guide.tex
Refactor jupyter

--- 2023-12-28 thesis/chapters/appendix/C-technical-documentation.tex
@@
 \thispagestyle{empty}
-\chapter{Technical documentation} \label{appendix:technical-docs}
+\chapter{User Guide} \label{appendix:user-guide}
 \pagenumbering{arabic}
 \renewcommand*{\thepage}{C-\arabic{page}}
-
-\section{Data collection plan}
-
-The vibration measurements will occur monthly for pumps and biweekly for compressors from February 2024 until May 2024.
-\begin{table}[ht]
-\centering
-\renewcommand{\arraystretch}{1.1}
-\begin{tabular}{|l|l|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|}
-\hline
-\textbf{Machine}                                                                      & \textbf{Placement \textbackslash Month} & \multicolumn{2}{p{1.2cm}|}{\textbf{02/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{03/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{04/2024}} \\ \hline
-\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#3\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &        \\ \cline{2-8} 
-                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
-\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#5\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\multirow{6}{*}{\textbf{Pump Sigma}}                                                  & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\end{tabular}
-\end{table}
-Each measurement will involve 3 trials for each position.
-The sensor is mounted to the machine with adhesive on double-sided carpet tape (placement notation follows MIMOSA convention from ISO~13373-1).
-After every trial, the sensor will be detached and attached again.
-
-The plan was consulted and approved by the machinery owners: VNET~a.s.
-and Bratislavská vodárenská spoločnosť,~a.s.
-Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution.
-Total space requirements for 108 recordings are 990 MiB.
-
-\section{Firmware activities}
-
-Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
-
-\begin{itemize}
-\itemsep0pt
-\item begin new recording, 
-\item log block of samples into CSV file,
-\item finish recording.
-\end{itemize}
-
-\begin{figure}[h]
-    \centering
-	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
-\end{figure}

### 2024-04-13 thesis/chapters/appendix/E-work-plan.tex
Refactor jupyter

--- 2024-03-11 thesis/chapters/appendix/B-plan-of-work.tex
@@
 \pagenumbering{arabic}
-\renewcommand*{\thepage}{B-\arabic{page}}
+\renewcommand*{\thepage}{E-\arabic{page}}
 
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
+\nth{1} week         & Semester kickoff meeting to set goals, experiments and discuss the status of collaborations with partners.
 \\ \hline
@@
  \\ \hline
-  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
+  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning.
  \\ \hline
-  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
+  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Desihn the firmware for new datalogger.
  \\ \hline
-  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
+  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing chapter on design and implementation.
  \\ \hline
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1}  - \nth{2} week         & 
-\begin{enumerate}
-\itemsep0pt
-\item Incorporate suggestions from DP2 defense. 
-\item Develop and test firmware for designed sensor unit.
-\end{enumerate}
+\nth{1} week  & Build and debug hardware of vibration logger with the consultant. 
 \\ \hline
-\nth{2}  - \nth{10} week         & 
-\begin{enumerate}
-\itemsep0pt
-\item Long-term manual regular gathering of vibration data from compressors and pumps. 
-\item Find optimal number of features. 
-\item Try to increase k-NN prediction metrics.
-\item Put together incremental learning with feature selection. 
-\item Explore incremental clustering in search of method that can help with labeling.
-\end{enumerate}
+\nth{2} week & Implement and test firmware on standing fan for logging signal to SD card.
 \\ \hline
-\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
+\nth{3} week & First compressor (\nth{20} February) and water pump (\nth{27} and \nth{28} February) vibration measurements and their fault and frequency analysis. 
+ \\ \hline
+\nth{4} week & Replace two time domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
+ \\ \hline
+\nth{5} week & Perform PCA analysis of whole feature sets. Consultation about methods for own dataset evaluation.
+ \\ \hline
+\nth{6} week  & Consultation with experts in SjF STU.
+Formulate research goals for scientific paper and create graphs of the model results.
+Experiment with k-value and number of features to reach better accuracy.
+Repeated measurement of compressors (\nth{19} March).
+ \\ \hline
+\nth{7} week & Repeated measurement of water pumps (\nth{26} and \nth{27} March). Request and download data about pumps from KSB Cloud.
+ \\ \hline
+ \nth{8} week & Write up complete paper and submit to IIT.SRC student conference after feedback from supervisor.
+ \\ \hline
+ \nth{9} week & Refactor jupyter notebooks nad apply different labeling strategy applied in paper to incremental learning.
+ \\ \hline
+  \nth{10} week & Write up implementation chapter of the thesis.
+ \\ \hline
+  \nth{11} week & 
+ \\ \hline
+  \nth{12} - \nth{15} week &  
  \\ \hline
@@
 
+The aim of final semestre was to gather own dataset from compressors and water pumps with custom data logger. The k-NN model was validated with diffrent hyperparameters.
+
 \clearpage

### 2024-04-13 notebooks/bin2csv.py

@@ -1,42 +1,0 @@
-import struct
-import os
-import argparse
-
-
-parser = argparse.ArgumentParser()
-parser.add_argument('path', type=str, help='Folder with .bin files')
-parser.add_argument('res', type=int, help='Resolution in g') # default is 4g, sigma is 16g 
-args = parser.parse_args()
-print(f'Path: "{args.path}"')
-
-fmt = 'iiii'
-struct_len = struct.calcsize(fmt)
-struct_unpack = struct.Struct(fmt).unpack_from
-
-for root, subdirs, files in os.walk(args.path):
-    for filename in files:
-        print(filename)
-        if not filename.lower().endswith('.bin'):
-            continue
-
-        name, ext = os.path.splitext(filename)
-        csvfilename = os.path.join(root, f'{name}.tsv')
-        filename = os.path.join(root, filename)
-        print(filename)
-
-        if args.res == 4:
-            resolution = 0.122  # 4g
-        elif args.res == 16:
-            resolution = 0.488
-
-        with (open(filename, 'rb') as fr,
-            open(csvfilename, 'w') as fw):
-            while True:
-                data = fr.read(struct_len)
-                if not data:
-                    break
-                t, x, y, z = struct_unpack(data)
-                x *= resolution
-                y *= resolution
-                z *= resolution
-                print(f'{t}\t{x:.2f}\t{y:.2f}\t{z:.2f}', file=fw)

### 2024-04-13 notebooks/convertor.py

@@ -1,0 +1,48 @@
+""" Convert .bin from SD card to .tsv for further processing
+"""
+import struct
+import os
+import argparse
+
+
+parser = argparse.ArgumentParser()
+parser.add_argument('path', type=str, help='Folder with .bin files')
+# Default resolution in firmware is 4g
+parser.add_argument('res', type=int, help='Resolution in g') 
+args = parser.parse_args()
+print(f'Path: "{args.path}"')
+
+fmt = 'iiii'
+struct_len = struct.calcsize(fmt)
+struct_unpack = struct.Struct(fmt).unpack_from
+if args.res == 2:
+    resolution = 0.061
+elif args.res == 4:
+    resolution = 0.122
+elif args.res == 8:
+    resolution = 0.244
+elif args.res == 16:
+    resolution = 0.488
+
+for root, subdirs, files in os.walk(args.path):
+    for filename in files:
+        print(filename)
+        if not filename.lower().endswith('.bin'):
+            continue
+
+        name, ext = os.path.splitext(filename)
+        csvfilename = os.path.join(root, f'{name}.tsv')
+        filename = os.path.join(root, filename)
+        print(filename)
+
+        with (open(filename, 'rb') as fr,
+            open(csvfilename, 'w') as fw):
+            while True:
+                data = fr.read(struct_len)
+                if not data:
+                    break
+                t, x, y, z = struct_unpack(data)
+                x *= resolution
+                y *= resolution
+                z *= resolution
+                print(f'{t}\t{x:.2f}\t{y:.2f}\t{z:.2f}', file=fw)

### 2024-04-13 notebooks/mafaulda.py

@@ -1,0 +1,206 @@
+import re
+from typing import (
+    Callable,
+    Tuple,
+    List,
+    Dict
+)
+from zipfile import ZipFile
+
+import numpy as np
+import pandas as pd
+from scipy.signal import (
+    find_peaks,
+    butter,
+    lfilter,
+    welch
+)
+from sklearn.preprocessing import MinMaxScaler
+import extraction
+
+
+SAMPLING_RATE = 50000
+BEARING_A_COLUMNS = ['ax', 'ay', 'az']
+BEARING_B_COLUMNS = ['bx', 'by', 'bz']
+BEARINGS_COLUMNS = BEARING_A_COLUMNS + BEARING_B_COLUMNS
+COLUMNS = ['tachometer'] + BEARINGS_COLUMNS + ['mic']
+LABEL_COLUMNS = ['fault', 'severity', 'rpm']
+
+BEARINGS = {
+    'balls': 8,
+    'ball_diameter': 0.7145,
+    'pitch_diameter': 2.8519,
+    'bpfo_factor': 2.9980,
+    'bpfi_factor': 5.0020,
+    'bsf_factor': 1.8710,
+    'ftf_factor': 0.3750
+}
+
+FAULTS = {
+    'A': {
+        'normal': 'normal',
+        'imbalance': 'imbalance',
+        'horizontal-misalignment': 'misalignment',
+        'vertical-misalignment': 'misalignment',
+        'underhang-outer_race': 'outer race fault',
+        'underhang-cage_fault': 'cage fault',
+        'underhang-ball_fault': 'ball fault'
+    },
+    'B': {
+        'normal': 'normal',
+        'imbalance': 'imbalance',
+        'horizontal-misalignment': 'misalignment',
+        'vertical-misalignment': 'misalignment',
+        'overhang-outer_race': 'outer race fault',
+        'overhang-cage_fault': 'cage fault',
+        'overhang-ball_fault': 'ball fault',
+    }
+}
+
+
+def bearing_frequencies(rpm: int) -> Dict[str, float]: 
+    machine = {}
+    rpm /= 60
+    machine['RPM'] = rpm
+    machine['BPFO'] = BEARINGS['bpfo_factor'] * rpm
+    machine['BPFI'] = BEARINGS['bpfi_factor'] * rpm
+    machine['BSF'] = BEARINGS['bsf_factor'] * rpm
+    machine['FTF'] = BEARINGS['ftf_factor'] * rpm
+    return machine
+
+
[…]

### 2024-04-13 notebooks/models.py

@@ -1,0 +1,225 @@
+from typing import (
+    Dict,
+    Tuple,
+    List
+)
+import itertools
+import numpy as np
+import pandas as pd
+from imblearn.over_sampling import RandomOverSampler
+
+from sklearn.neighbors import KNeighborsClassifier
+from sklearn.model_selection import KFold
+from sklearn import metrics
+from sklearn.metrics import silhouette_score
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.decomposition import PCA
+
+from sklearn.discriminant_analysis import LinearDiscriminantAnalysis
+from sklearn.svm import LinearSVC
+from sklearn.naive_bayes import GaussianNB
+
+from tqdm.notebook import tqdm
+import ranking
+
+
+def transform_to_pca(X, n):
+    scaler = MinMaxScaler()
+    X[X.columns] = scaler.fit_transform(X)
+
+    pca = PCA(n_components=n)
+    X_pca = pca.fit_transform(X)
+    X_pca = pd.DataFrame(X_pca)
+    return X_pca
+
+
+def find_best_subset(
+        X: pd.DataFrame,
+        Y: pd.DataFrame,
+        metric: str,
+        members: int = 3,
+        kfolds: int = 5
+    ):
+    Y = Y.dropna().astype('category')
+    X = X[X.index.isin(Y.index)].copy()
+    Y = Y[Y.index.isin(X.index)].astype('category')
+    X = X.reset_index(drop=True)
+    Y = Y.reset_index(drop=True)
+
+    kf = KFold(n_splits=kfolds, shuffle=True, random_state=10)
+    elements = []
+
+    for train_idx, test_idx in kf.split(X, Y):
+        x_train, x_test, y_train, y_test = (
+            X.loc[train_idx].copy(), X.loc[test_idx].copy(),
+            Y.loc[train_idx].copy(), Y.loc[test_idx].copy()
+        )
+        ranks = ranking.batch_feature_ranking(x_train, y_train, metric)
+        if metric != 'rank':
+            synonyms = ranking.compute_correlations(x_train, corr_above=0.95)
+            subset = ranking.best_subset(ranks, synonyms, n=members)
+            output = subset
+        else:
+            output = ranks
+
+        output = list(output.reset_index().head(3)['feature'])
+
+    return output
+
+
+def kfold_accuracy(
+        X: pd.DataFrame,
+        Y: pd.DataFrame,
+        k_neighbors: int,
+        kfolds: int,
+        model_name: str, 
[…]

### 2024-04-13 notebooks/old/discovery.py

@@ -1,0 +1,225 @@
+from zipfile import ZipFile
+import numpy as np
+import pandas as pd
+from itertools import pairwise
+from typing import List, Tuple, Callable
+
+from numpy.lib.stride_tricks import sliding_window_view
+from scipy.stats import skew, kurtosis, entropy
+from scipy.signal import welch, windows, find_peaks
+from scipy.interpolate import interp1d
+from scipy.fft import rfft
+
+from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
+import pywt
+from tsfel import feature_extraction as ft
+import matplotlib.pylab as plt
+
+
+
+def plot_label_occurences(y):
+    observations = []
+    columns = list(y.astype('category').cat.categories)
+    empty = dict(zip(columns, len(columns) * [0]))
+
+    for row in y.astype('category'):
+        sample = empty.copy()
+        sample[row] = 1
+        observations.append(sample)
+
+    class_occurences = pd.DataFrame.from_records(observations).cumsum()
+    ax = class_occurences.plot(grid=True, figsize=(10, 5), xlabel='Observations', ylabel='Label occurences')
+    return ax, class_occurences
+
+
+def features_list():
+    config = tsfel.get_features_by_domain()
+    for domain in config.values():
+        for feature, options in domain.items():
+            if options['n_features'] != 1:
+                options['use'] = 'no'
+    return config
+
+
+def features_wavelet_domain(zip_file: ZipFile, filename: str) -> pd.DataFrame:
+    print(f'Processing: {filename}')
+
+    max_level = 6
+    wavelet = 'dmey'
+    ordering = 'freq'
+
+    columns = mafaulda.COLUMNS
+    ts = mafaulda.csv_import(zip_file, filename)
+    fault, severity, seq = mafaulda.parse_filename(filename)
+
+    rpm = ts['rpm'].mean()
+    result = []
+
+    for col in columns:
+        wp = pywt.WaveletPacket(data=ts[col], wavelet=wavelet, mode='symmetric')
+
+        for feature in ('energy', 'energy_ratio', 'kurtosis', 'negentropy'):
+            wpd_header = []
+            row = {
+                'fault': fault,
+                'severity': severity,
+                'seq': seq,
+                'rpm': rpm,
+                'axis': col,
+                'feature': feature
+            }
+
+            feature_vector = []
+            for level in range(1, max_level + 1):
[…]

### 2024-04-13 notebooks/old/selection.py

@@ -1,0 +1,270 @@
+import os.path
+import math
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import tsfel
+
+from river import stats, preprocessing
+from scipy.stats import pearsonr, pointbiserialr
+from sklearn.feature_selection import mutual_info_classif, f_classif
+
+from sklearn.compose import ColumnTransformer
+from sklearn.pipeline import Pipeline
+from sklearn.preprocessing import StandardScaler, MinMaxScaler
+
+
+# Dataset paths and attributes
+MAFAULDA_METADATA = 'mafaulda_metadata.csv'
+TIME_FEATURES_PATH = 'temporal_features.csv'
+FREQ_FEATURES_PATH = 'spectral_features.csv'
+TIME_AND_FREQ_FEATURES_PATH = 'time_freq_features.csv'
+
+
+TIME_FEATURES_PATH_ALL = 'all_td_features.csv'
+FREQ_FEATURES_PATH_ALL = 'all_fd_features.csv'
+WPD_FEATURES_PATH_ALL = 'all_wpd_features.csv'
+TSFEL_FEATURES_PATH_ALL = 'all_tsfel_features.csv'
+
+
+WPD_COLUMNS_EXCLUDE = {
+    'fault', 'severity', 'seq', 'rpm', 'axis', 'feature'
+}
+
+FAULT_CLASSES = {'normal': 'N', 'imbalance': 'I', 'horizontal-misalignment': 'HM', 'vertical-misalignment': 'VM'}
+METADATA_COLUMNS = ['fault', 'severity', 'seq', 'rpm']
+METADATA_COLUMNS_ALL = METADATA_COLUMNS + ['severity_class', 'severity_level', 'anomaly']
+
+#########################################################
+def filter_out_metadata_columns(df):
+    return df[df.columns[~df.columns.isin(METADATA_COLUMNS_ALL)]]
+
+
+def remove_column_prefix(df):
+    return df.columns.str.extract(r'\w+_(\w+)')[0]
+
+
+def fd_extract_feature_name(column):
+    return column.str.extract(r'[A-Za-z]+_(.*)_\d+$')[0]
+
+
+def plot_bar_chart(ax, x, y, title):
+    ax.bar(x, y)
+    ax.grid(True)
+    ax.set_title(title)
+    # Rotate x labels by 45 deg
+    ax.set_xticks(ax.get_xticks())
+    ax.set_xticklabels(ax.get_xticklabels(), rotation=45, ha='right')
+
[…]

### 2024-04-13 notebooks/pumps.py

@@ -1,0 +1,147 @@
+import os
+from typing import (
+    Callable,
+    Tuple,
+    List,
+    Dict
+)
+from datetime import datetime
+from zipfile import ZipFile
+
+import numpy as np
+import pandas as pd
+import extraction
+
+
+SAMPLING_RATE = 26866
+BEARINGS_COLUMNS = ['x', 'y', 'z']
+COLUMNS = ['t'] +  BEARINGS_COLUMNS
+LABEL_COLUMNS = ['date', 'device', 'position']
+G_CONSTANT = 9.80665
+
+
+def csv_import(dataset: ZipFile, filename: str) -> pd.DataFrame:
+    if dataset is not None:
+        name = dataset.open(filename)
+    else:
+        name = filename
+
+    ts = pd.read_csv(
+        name,
+        delimiter='\t',
+        index_col=False,
+        header=0,
+        names=COLUMNS
+    ) 
+
+    columns = BEARINGS_COLUMNS
+    ts[columns] = ts[columns].apply(lambda x: G_CONSTANT * (x / 1000))
+
+    T = 1 / SAMPLING_RATE
+    ts = (
+        ts
+        .assign(t = lambda x: x.index * T)
+        .assign(key=filename)
+    )
+    return ts
+
+
+def features_by_domain(
+        features_calc: Callable,
+        dataset: ZipFile,
+        filename: str, 
+        window: int = None,
+        parts: int = None
+    ):
+
+    # print(f'Processing: {filename}')
+    fs = SAMPLING_RATE
+    columns = BEARINGS_COLUMNS
+
+    ts = csv_import(dataset, filename)
+    dataframe = extraction.split_dataframe(ts, parts)
+    dataframe = extraction.detrending_filter(dataframe, columns)
+    
+    header = filename.split(os.path.sep)
+    metadata = [
+        ('date', [datetime.fromisoformat(header[-4]).date()]),
+        ('device', [header[-3]]),
+        ('position', [header[-2]]),
+        ('seq', [int(header[-1].split('.')[0])])
+    ]
+
+    result = []
+    for i, df in enumerate(dataframe):
+        fvector = metadata.copy()
+        for col in columns:
+            fvector.extend(features_calc(df, col, fs, window))
+        result.append(pd.DataFrame(dict(fvector))) 
+
+    return pd.concat(result).reset_index(drop=True)
+
+
+def features_by_domain_no_metadata(
+        features_calc: Callable,
[…]

### 2024-04-13 notebooks/ranking.py

@@ -1,0 +1,196 @@
+from enum import (
+    Enum,
+    auto
+)
+from typing import (
+    List,
+    Set,
+    Tuple,
+    Dict
+)
+
+import pandas as pd
+from scipy.stats import gmean
+from sklearn.feature_selection import (
+    mutual_info_classif,
+    f_classif
+)
+from sklearn.preprocessing import MinMaxScaler
+from sklearn.decomposition import PCA
+from sklearn.metrics import silhouette_score
+
+from river import (
+    feature_selection,
+    stream,
+    preprocessing
+)
+import selection
+
+
+class ExperimentOutput(Enum):
+    COUNTS = auto()
+    BEST_SET = auto()
+    RANKS = auto()
+    SCORES_RANGE = auto()
+    PCA = auto()
+    SILHOUETTE = auto()
+    BEST_CORR = auto()
+    BEST_F_STAT = auto()
+    BEST_MI = auto()
+
+
+def silhouette_scores(
+        X_train: pd.DataFrame,
+        X_test: pd.DataFrame,
+        Y_train: pd.DataFrame,
+        Y_test: pd.DataFrame,
+        best_features: list,
+        pc: int) -> Dict[str, float]:
+    Y_train = Y_train.reset_index(drop=True).astype('category')
+    Y_test = Y_test.reset_index(drop=True).astype('category')
+
+    scaler = MinMaxScaler()
+    X_train[X_train.columns] = scaler.fit_transform(X_train)
+    X_test[X_test.columns] = scaler.transform(X_test)    
+
+    model = PCA(n_components=pc).fit(X_train)
+    X_train_pca = pd.DataFrame(model.transform(X_train))
+    X_test_pca = pd.DataFrame(model.transform(X_test))
+
+    return {
+        'train': silhouette_score(X_train[best_features], Y_train),
+        'test': silhouette_score(X_test[best_features], Y_test),
+        'train_pca': silhouette_score(X_train_pca, Y_train),
+        'test_pca': silhouette_score(X_test_pca, Y_test)
+    }
+
+
+def pca_explained_variances(X_train: pd.DataFrame, pc: int) -> Dict[str, float]:
+    scaler = MinMaxScaler()
+    X_train[X_train.columns] = scaler.fit_transform(X_train)
+    model = PCA(n_components=pc).fit(X_train)    
[…]

### 2024-04-13 notebooks/selection.py

@@ -1,0 +1,140 @@
+import numpy as np
+import pandas as pd
+from river import (
+    stats,
+    preprocessing
+)
+from scipy.stats import pointbiserialr
+
+############### ONLINE FEATURE SELECTION SCORE ###############################
+class Correlation(stats.base.Bivariate):
+
+    def __init__(self):
+        self.labels = {}
+
+    def update(self, x, y):
+        if y not in self.labels:
+            self.labels[y] = stats.PearsonCorr()
+
+        for label, corr in self.labels.items():
+            if label == y:
+                corr.update(x, 1)
+            else:
+                corr.update(x, 0)  
+        return self
+
+    def get(self):
+        return np.mean([
+            abs(corr.get())
+            for corr in self.labels.values()
+        ])
+
+
+class FisherScore(stats.base.Bivariate):
+
+    def __init__(self):
+        self.mean_x = stats.Mean()
+        self.labels = {}
+
+    def update(self, x, y):
+        self.mean_x.update(x)
+
+        if y not in self.labels:
+            self.labels[y] = {
+                'n': stats.Sum(), 
+                'mean': stats.Mean(), 
+                'var': stats.Var()
+            }
+
+        for s in self.labels[y].values():
+            s.update(x)
+        
+        return self
+
+    def get(self):
+        mean_x = self.mean_x.get()
+
+        inter_class = sum([
+            s['n'].get() * ((s['mean'].get() - mean_x) ** 2)
+            for s in self.labels.values()
+        ])
+        intra_class = sum([
+            (s['n'].get() - 1) * s['var'].get()
+            for s in self.labels.values()
+        ])
+        if intra_class == 0:
+            return 0
+
+        score = inter_class / intra_class
+        return score
+
+
+class MutualInformation(stats.base.Bivariate):
+
+    def __init__(self):
+        self.n = stats.Count()
+        self.scaler = preprocessing.MinMaxScaler()
+        self.label_bins = 3
+        self.labels = {}
+
+        self.matrix = []
+        self.row_margins = []
+        self.col_margins = [
+            stats.Count() for i in range(self.label_bins)
+        ]
+
+    def update(self, x, y):
+        self.n.update()
+        if y not in self.labels:
+            self.labels[y] = len(self.matrix)
+            self.row_margins.append(stats.Count())
+            self.matrix.append([
+                stats.Count() for i in range(self.label_bins)
+            ])
+        
+        row = self.labels[y]
[…]

### 2024-04-13 notebooks/vibrodiagnostics/discovery.py

@@ -1,246 +1,0 @@
-from zipfile import ZipFile
-import numpy as np
-import pandas as pd
-from itertools import pairwise
-from typing import List, Tuple, Callable
-
-from numpy.lib.stride_tricks import sliding_window_view
-from scipy.stats import skew, kurtosis, entropy
-from scipy.signal import welch, windows, find_peaks
-from scipy.interpolate import interp1d
-from scipy.fft import rfft
-
-from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
-import pywt
-from tsfel import feature_extraction as ft
-import matplotlib.pylab as plt
-
-
-
-def split_dataframe(dataframe: pd.DataFrame, parts: int = None) -> List[pd.DataFrame]:
-    if parts is None:
-        return [dataframe]
-
-    step = len(dataframe) // parts
-    return [
-        dataframe.iloc[i:i+step].reset_index(drop=True)
-        for i in range(0, len(dataframe), step)
-        if len(dataframe.iloc[i:i + step]) == step
-    ]
-
-
-def butter_bandpass_filter(data, cutoff=10000, fs=50000, order=5):
-    b, a = butter(order, cutoff, fs=fs, btype='lowpass')
-    y = lfilter(b, a, data.to_numpy())
-    return pd.Series(data=y, index=data.index)
-
-
-
-def plot_label_occurences(y):
-    observations = []
-    columns = list(y.astype('category').cat.categories)
-    empty = dict(zip(columns, len(columns) * [0]))
-
-    for row in y.astype('category'):
-        sample = empty.copy()
-        sample[row] = 1
-        observations.append(sample)
-
-    class_occurences = pd.DataFrame.from_records(observations).cumsum()
-    ax = class_occurences.plot(grid=True, figsize=(10, 5), xlabel='Observations', ylabel='Label occurences')
-    return ax, class_occurences
-
-
-def features_list():
-    config = tsfel.get_features_by_domain()
-    for domain in config.values():
-        for feature, options in domain.items():
-            if options['n_features'] != 1:
-                options['use'] = 'no'
-    return config
-
-
-def features_wavelet_domain(zip_file: ZipFile, filename: str) -> pd.DataFrame:
-    print(f'Processing: {filename}')
-
-    max_level = 6
-    wavelet = 'dmey'
-    ordering = 'freq'
-
-    columns = mafaulda.COLUMNS
-    ts = mafaulda.csv_import(zip_file, filename)
[…]

### 2024-04-13 notebooks/vibrodiagnostics/ranking.py

@@ -1,175 +1,0 @@
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.stats import gmean
-from sklearn.feature_selection import mutual_info_classif, f_classif
-from sklearn.preprocessing import MinMaxScaler
-from sklearn.decomposition import PCA
-from typing import List, Set, Tuple, Dict
-from river import feature_selection, stream, preprocessing
-from sklearn.metrics import silhouette_score
-from vibrodiagnostics import selection
-from enum import Enum, auto
-
-
-class ExperimentOutput(Enum):
-    COUNTS = auto()
-    BEST_SET = auto()
-    RANKS = auto()
-    SCORES_RANGE = auto()
-    PCA = auto()
-    SILHOUETTE = auto()
-    BEST_CORR = auto()
-    BEST_F_STAT = auto()
-    BEST_MI = auto()
-
-
-def silhouette_scores(X_train, X_test, Y_train, Y_test, best_features, pc):
-    Y_train = Y_train.reset_index(drop=True).astype('category')
-    Y_test = Y_test.reset_index(drop=True).astype('category')
-
-    scaler = MinMaxScaler()
-    X_train[X_train.columns] = scaler.fit_transform(X_train)
-    X_test[X_test.columns] = scaler.transform(X_test)    
-
-    model = PCA(n_components=pc).fit(X_train)
-    X_train_pca = pd.DataFrame(model.transform(X_train))
-    X_test_pca = pd.DataFrame(model.transform(X_test))
-
-    return {
-        'train': silhouette_score(X_train[best_features], Y_train),
-        'test': silhouette_score(X_test[best_features], Y_test),
-        'train_pca': silhouette_score(X_train_pca, Y_train),
-        'test_pca': silhouette_score(X_test_pca, Y_test)
-    }
-
-
-def pca_explained_variances(X_train: pd.DataFrame, pc: int) -> Dict[str, float]:
-    scaler = MinMaxScaler()
-    X_train[X_train.columns] = scaler.fit_transform(X_train)
-    model = PCA(n_components=pc).fit(X_train)    
-    return {f'PC{pc}': var for pc, var in enumerate(model.explained_variance_ratio_, start=1)}
-
-
-def batch_feature_ranking(X: pd.DataFrame, Y: pd.DataFrame, mode: str = 'rank') -> pd.DataFrame:
-    metric_ranks = pd.DataFrame()
[…]

### 2024-04-13 notebooks/vibrodiagnostics/selection.py

@@ -1,403 +1,0 @@
-import os.path
-import math
-import pandas as pd
-import numpy as np
-import matplotlib.pyplot as plt
-import tsfel
-
-from river import stats, preprocessing
-from scipy.stats import pearsonr, pointbiserialr
-from sklearn.feature_selection import mutual_info_classif, f_classif
-
-from sklearn.compose import ColumnTransformer
-from sklearn.pipeline import Pipeline
-from sklearn.preprocessing import StandardScaler, MinMaxScaler
-
-
-# Dataset paths and attributes
-MAFAULDA_METADATA = 'mafaulda_metadata.csv'
-TIME_FEATURES_PATH = 'temporal_features.csv'
-FREQ_FEATURES_PATH = 'spectral_features.csv'
-TIME_AND_FREQ_FEATURES_PATH = 'time_freq_features.csv'
-
-
-TIME_FEATURES_PATH_ALL = 'all_td_features.csv'
-FREQ_FEATURES_PATH_ALL = 'all_fd_features.csv'
-WPD_FEATURES_PATH_ALL = 'all_wpd_features.csv'
-TSFEL_FEATURES_PATH_ALL = 'all_tsfel_features.csv'
-
-
-WPD_COLUMNS_EXCLUDE = {
-    'fault', 'severity', 'seq', 'rpm', 'axis', 'feature'
-}
-
-FAULT_CLASSES = {'normal': 'N', 'imbalance': 'I', 'horizontal-misalignment': 'HM', 'vertical-misalignment': 'VM'}
-METADATA_COLUMNS = ['fault', 'severity', 'seq', 'rpm']
-METADATA_COLUMNS_ALL = METADATA_COLUMNS + ['severity_class', 'severity_level', 'anomaly']
-
-#########################################################
-def filter_out_metadata_columns(df):
-    return df[df.columns[~df.columns.isin(METADATA_COLUMNS_ALL)]]
-
-
-def remove_column_prefix(df):
-    return df.columns.str.extract(r'\w+_(\w+)')[0]
-
-
-def fd_extract_feature_name(column):
-    return column.str.extract(r'[A-Za-z]+_(.*)_\d+$')[0]
-
-
-def plot_bar_chart(ax, x, y, title):
-    ax.bar(x, y)
-    ax.grid(True)
-    ax.set_title(title)
-    # Rotate x labels by 45 deg
-    ax.set_xticks(ax.get_xticks())
-    ax.set_xticklabels(ax.get_xticklabels(), rotation=45, ha='right')
-
-
[…]

### 2024-04-14 notebooks/extraction.py
Online knn on all features refactor

@@ -204,3 +204,71 @@ def load_features(
     
     df[label_columns] = Y
     return df
+
+
+def mms_peak_finder(x: np.array, win_len=3) -> np.array:
+    a = sliding_window_view(x, window_shape=win_len)
+
+    mms_max = (
+        (np.max(a, axis=1) - np.min(a, axis=1)) /
+        (np.sum(a, axis=1) - np.min(a, axis=1) * win_len)
+    )
+    mms_mid = (
+        (a[:,win_len//2] - np.min(a, axis=1)) /
+        (np.sum(a, axis=1) - np.min(a, axis=1) * win_len)
+    )
+    peaks_in_windows, *other = np.where(mms_max == mms_mid)
+    return peaks_in_windows + 1
+
+
+def have_intersection(interval1, interval2):
+    new_min = max(interval1[0], interval2[0])
+    new_max = min(interval1[1], interval2[1])
+    return new_min <= new_max
+
+
+def harmonic_series_detection(f: np.array, Pxx: np.array, fs: int, fft_window: int) -> np.array:
+    peaks = mms_peak_finder(Pxx)
+    f_central = f[peaks]
+    delta_f = fs / fft_window
+    amplitudes = Pxx[peaks]
+
+    largest_frequency = int(fs / 2 + delta_f)
+    components = np.vstack((f_central, amplitudes)).T
+    k = 8     # Limit harmonics not detected in series (skips)
+
+    result = []
+    # Each component can be fundamental frequency
+    for v, a in components:
+        series = [(v, a)]
+
+        # Harmonic components from given fundamental frequency
+        order_distance = 0
+        delta_v = delta_f
+        for r, vi in enumerate(range(2*int(v), largest_frequency, int(v)), start=2):
+            # Search interval for harmonic component candidates
+            search_interval = (vi - ((r * delta_v) / 2), vi + ((r * delta_v) / 2))
+
+            # If tolerances are in search interval find minimal distance
+            # between true harmonic and candidate
+            candidates = []
+            for vj, aj in components:
+                tolerance_interval = (vj - delta_v / 2, vj + delta_v / 2)
+                if have_intersection(search_interval, tolerance_interval):
+                    candidates.append((vj, aj, abs(vj - vi)))
+
+            if len(candidates) > 0:
+                vh, ah, dh = min(candidates, key=lambda x: x[2])
+                series.append((vh, ah))
+                xh, yh = (vh - delta_v), (vh + delta_v)
[…]

### 2024-04-14 notebooks/mafaulda.py

@@ -161,17 +161,27 @@ def features_by_domain(
     return pd.concat(result).reset_index(drop=True)
 
 
-def assign_labels(df: pd.DataFrame, bearing: str) -> pd.DataFrame:
-    df['label'] = df.apply(lambda row: FAULTS[bearing].get(row['fault']), axis=1)
+def get_classes(df: pd.DataFrame, bearing: str) -> pd.DataFrame:
+    if not bearing:
+        faults = [f for f in FAULTS.values()]
+        faults = {k: v for d in faults for k, v in d.items()}
+        df['label'] = df.apply(lambda row: faults.get(row['fault']), axis=1)
+    else:
+        df['label'] = df.apply(lambda row: FAULTS[bearing].get(row['fault']), axis=1)
     df['label'] = df['label'].astype('category')
+    return df
+
+
+def assign_labels(df: pd.DataFrame, bearing: str) -> pd.DataFrame:
+    df = get_classes(df, bearing)
     df = df.dropna()
     df = df.drop(columns=LABEL_COLUMNS)
     df = df.reset_index(drop=True)
     return df
 
 
-def label_severity(df: pd.DataFrame, bearing: str, level: float, debug: bool = False) -> pd.DataFrame:
-    df['label'] = df.apply(lambda row: FAULTS[bearing].get(row['fault']), axis=1)
+def label_severity(df: pd.DataFrame, bearing: str, level: float, debug: bool = False, keep: bool = False) -> pd.DataFrame:
+    df = get_classes(df, bearing)
     df = df.dropna()
     df = df.reset_index(drop=True)
     df['label'] = df['label'].astype('category')
@@ -201,6 +211,7 @@ def label_severity(df: pd.DataFrame, bearing: str, level: float, debug: bool = F
             )
             
     df.loc[df['severity_level'] < level, 'label'] = 'normal'
-    df = df.drop(columns=LABEL_COLUMNS)
-    df = df.drop(columns=['severity_class', 'severity_level', 'severity_no'])
+    if not keep:
+        df = df.drop(columns=LABEL_COLUMNS)
+        df = df.drop(columns=['severity_class', 'severity_level', 'severity_no'])
     return df

### 2024-04-14 notebooks/models.py

@@ -40,11 +40,6 @@ def find_best_subset(
         members: int = 3,
         kfolds: int = 5
     ):
-    Y = Y.dropna().astype('category')
-    X = X[X.index.isin(Y.index)].copy()
-    Y = Y[Y.index.isin(X.index)].astype('category')
-    X = X.reset_index(drop=True)
-    Y = Y.reset_index(drop=True)
 
     kf = KFold(n_splits=kfolds, shuffle=True, random_state=10)
     elements = []
@@ -74,11 +69,6 @@ def kfold_accuracy(
         kfolds: int,
         model_name: str, 
         knn_metric='euclidean') -> Dict[str, float]:
-
-    # Remove missing data
-    Y = Y.dropna()
-    X = X[X.index.isin(Y.index)]
-    Y = Y[Y.index.isin(X.index)].astype('category')
 
     # Class balancing
     oversample = RandomOverSampler(sampling_strategy='not majority', random_state=10)
@@ -130,10 +120,6 @@ def all_features(
         model: str,
         k_neighbors: list = list(range(1, 40, 4)),
         kfold_param: int = 5) -> dict:
-    # Remove missing data
-    Y = Y.dropna()
-    X = X[X.index.isin(Y.index)]
-    Y = Y[Y.index.isin(X.index)].astype('category')
 
     # Class balancing
     oversample = RandomOverSampler(sampling_strategy='not majority', random_state=10)
@@ -183,7 +169,10 @@ def enumerate_models(
         model='knn') -> pd.DataFrame:
 
     models = []
-    domains = {'temporal': X_temporal, 'spectral': X_spectral}
+    domains = {
+        'TD': X_temporal,
+        'FD': X_spectral
+    }
 
     for fnum in num_of_features:
         for domain, X in domains.items():

### 2024-04-14 notebooks/old/discovery.py

@@ -1,225 +1,0 @@
-from zipfile import ZipFile
-import numpy as np
-import pandas as pd
-from itertools import pairwise
-from typing import List, Tuple, Callable
-
-from numpy.lib.stride_tricks import sliding_window_view
-from scipy.stats import skew, kurtosis, entropy
-from scipy.signal import welch, windows, find_peaks
-from scipy.interpolate import interp1d
-from scipy.fft import rfft
-
-from scipy.signal import butter, iirfilter, freqz, lfilter, decimate
-import pywt
-from tsfel import feature_extraction as ft
-import matplotlib.pylab as plt
-
-
-
-def plot_label_occurences(y):
-    observations = []
-    columns = list(y.astype('category').cat.categories)
-    empty = dict(zip(columns, len(columns) * [0]))
-
-    for row in y.astype('category'):
-        sample = empty.copy()
-        sample[row] = 1
-        observations.append(sample)
-
-    class_occurences = pd.DataFrame.from_records(observations).cumsum()
-    ax = class_occurences.plot(grid=True, figsize=(10, 5), xlabel='Observations', ylabel='Label occurences')
-    return ax, class_occurences
-
-
-def features_list():
-    config = tsfel.get_features_by_domain()
-    for domain in config.values():
-        for feature, options in domain.items():
-            if options['n_features'] != 1:
-                options['use'] = 'no'
-    return config
-
-
-def features_wavelet_domain(zip_file: ZipFile, filename: str) -> pd.DataFrame:
-    print(f'Processing: {filename}')
-
-    max_level = 6
-    wavelet = 'dmey'
-    ordering = 'freq'
-
-    columns = mafaulda.COLUMNS
-    ts = mafaulda.csv_import(zip_file, filename)
-    fault, severity, seq = mafaulda.parse_filename(filename)
-
-    rpm = ts['rpm'].mean()
-    result = []
-
-    for col in columns:
-        wp = pywt.WaveletPacket(data=ts[col], wavelet=wavelet, mode='symmetric')
-
-        for feature in ('energy', 'energy_ratio', 'kurtosis', 'negentropy'):
-            wpd_header = []
-            row = {
-                'fault': fault,
-                'severity': severity,
-                'seq': seq,
-                'rpm': rpm,
-                'axis': col,
-                'feature': feature
-            }
-
-            feature_vector = []
-            for level in range(1, max_level + 1):
[…]

### 2024-04-14 notebooks/old/nn.py

@@ -1,66 +1,0 @@
-import numpy as np
-from sklearn.neighbors import KNeighborsClassifier
-from sklearn import metrics
-import pandas as pd
-import seaborn as sb
-import matplotlib.pyplot as plt
-from tqdm.notebook import tqdm
-import itertools
-
-
-def knn_evaluation(x_train, y_train, x_test, y_test, n=5):
-    knn = KNeighborsClassifier(n_neighbors=n, metric='euclidean', algorithm='kd_tree')
-    knn.fit(x_train, y_train)
-    y_predict_train = knn.predict(x_train)
-    y_predict_test = knn.predict(x_test)
-
-    print(f'Train accuracy: {metrics.accuracy_score(y_train, y_predict_train) * 100:.2f} %')
-    print(f'Test accuracy: {metrics.accuracy_score(y_test, y_predict_test) * 100:.2f} %')
-    print(metrics.classification_report(y_test, y_predict_test))
-
-    labels = np.unique(y_test)
-    cm = metrics.confusion_matrix(y_test, y_predict_test)
-    cm = pd.DataFrame(cm, index=labels, columns=labels)
-
-    ax = sb.heatmap(cm, cbar=True, cmap='BuGn', annot=True, fmt='d')
-    ax.set_xlabel('Predicted label')    # size=15)
-    ax.set_ylabel('True label')         # size=15)
-    plt.show()
-
-
-def knn_one_case_eval(neighbours, features, x_train, y_train, x_test, y_test):
-    x_train_selected = x_train[features]
-    x_test_selected = x_test[features]
-
-    knn = KNeighborsClassifier(n_neighbors=neighbours, metric='euclidean', algorithm='kd_tree')
-    knn.fit(x_train_selected, y_train)
-    y_predict_train = knn.predict(x_train_selected)
-    y_predict_test = knn.predict(x_test_selected)
-
-    y_proba_train = knn.predict_proba(x_train_selected)
-    y_proba_test = knn.predict_proba(x_test_selected)
-
-    return {
-        'features': features,
-        'train_accuracy': metrics.accuracy_score(y_train, y_predict_train),
-        'train_precision': metrics.precision_score(y_train, y_predict_train, average='micro'),
-        'train_recall': metrics.recall_score(y_train, y_predict_train, average='micro'),
-        'train_error_rate': np.mean(y_train != y_predict_train),
-        # 'train_auc': metrics.roc_auc_score(y_train, y_proba_train, multi_class='ovo', average='macro'),
[…]

### 2024-04-14 notebooks/pumps.py

@@ -122,6 +122,17 @@ def assign_labels(df: pd.DataFrame) -> pd.DataFrame:
     return df
 
 
+def get_classes(df: pd.DataFrame, labels: Dict[str, dict]) -> pd.DataFrame:
+    df['label'] = df.apply(
+        lambda row: labels.get(row['device'], {}).get(row['position']), axis=1
+    )
+    df['label'] = df['label'].astype('category')
+    df = df.dropna()
+    df = df.drop(columns=LABEL_COLUMNS)
+    df = df.reset_index(drop=True)
+    return df
+
+
 def beaglebone_measurement(filename: str, fs: int) -> Tuple[str, pd.DataFrame]:
     milivolts = 1800
     resolution = 2**12

### 2024-04-14 notebooks/visualize.py

@@ -1,16 +1,18 @@
-import extraction
+from typing import List
 import numpy as np
 import pandas as pd
 
 import matplotlib.pyplot as plt
 from matplotlib.colors import ListedColormap
 import matplotlib.patches as mpatches
+from adjustText import adjust_text
 
 import seaborn as sb
 from sklearn.metrics import silhouette_score
 from sklearn.preprocessing import MinMaxScaler
 from sklearn.decomposition import PCA
 
+import extraction
 import models
 
 
@@ -20,7 +22,7 @@ def plot_models_performance_bar(
         Y: pd.DataFrame,
         models_summary: pd.DataFrame,
         k_neighbors: int = 5,
-        number_of_features: int = 3):
+        number_of_features: int = 3) -> pd.DataFrame:
 
     MODEL_TYPE = 'knn'
     Y = Y.dropna().astype('category')
@@ -37,72 +39,80 @@ def plot_models_performance_bar(
     columns = ['train', 'test']
     kfolds = 5
     x = np.arange(len(columns))
-    domains = {'temporal': X_temporal, 'spectral': X_spectral}
+    domains = {'TD': X_temporal, 'FD': X_spectral}
+    results = []
 
-    for i, d in enumerate(domains.items()):
-        domain, X = d 
+    for i, (domain, X) in enumerate(domains.items()):
         width = 0.13
 
         y_best = models.all_features(X, Y, MODEL_TYPE, [k_neighbors])
         y_best = [y_best['train'][0], y_best['test'][0]]
         rect = ax[i].bar(x - 3*width, y_best, width, label='All features')
         ax[i].bar_label(rect, padding=3, fmt=lambda x: f'{x * 100:.0f}')
-        print('All features', y_best)
+        results.append({
+            'domain': domain, 'set': 'All features', 
+            'train': y_best[0], 'test': y_best[1]
+        })
 
-        y_best = kfold_accuracy(extraction.transform_to_pca(X, n=number_of_features), Y, k_neighbors, kfolds, MODEL_TYPE)
+        y_best = models.kfold_accuracy(
+            models.transform_to_pca(X, n=number_of_features), 
+            Y, k_neighbors, kfolds, MODEL_TYPE
+        )
         y_best = [y_best['train'], y_best['test']]
-        rect = ax[i].bar(x - 2*width, y_best, width, label='PCA 3 PC')
+        rect = ax[i].bar(
[…]

### 2024-04-22 machine-learning/vibrodiagnostics/extraction.py
Batch MaFaulDa all experimental situations

@@ -21,6 +21,10 @@ from scipy.signal import (
 from scipy.fft import rfft
 from scipy.interpolate import interp1d
 from tsfel import feature_extraction as ft
+import pywt
+from scipy.signal import iirfilter, lfilter, decimate
+
+from vibrodiagnostics import mafaulda
 
 
 def energy(pxx: np.array) -> float:
@@ -116,7 +120,7 @@ def time_features_calc(df: pd.DataFrame, col: str, fs: int, window: int) -> List
 
 def frequency_features_calc(df: pd.DataFrame, col: str, fs: int, window: int) -> List[Tuple[str, pd.DataFrame]]:
     f, pxx = spectral_transform(df[col], window, fs)
-    
+
     fluxes = temporal_variation(df[col], window)
     envelope_spectrum = envelope_signal(f, pxx)
 
@@ -136,6 +140,53 @@ def frequency_features_calc(df: pd.DataFrame, col: str, fs: int, window: int) ->
     return [(f'{col}_{f[0]}', f[1]) for f in features]
 
 
+def wavelet_features_calc(df: pd.DataFrame, col: str, fs: int, window: int) -> List[Tuple[str, pd.DataFrame]]:
+    max_level = 6
+    wavelet = 'dmey'
+    ordering = 'freq'
+    x = df[col]
+    result = []
+    columns = mafaulda.BEARINGS_COLUMNS
+
+    for col in columns:
+        wp = pywt.WaveletPacket(data=x, wavelet=wavelet, mode='symmetric')
+
+        for feature in ('energy', 'energy_ratio', 'kurtosis', 'negentropy'):
+            wpd_header = []
+            row = {
+                'axis': col,
+                'feature': feature
+            }
+
+            feature_vector = []
+            for level in range(1, max_level + 1):
+                nodes = wp.get_level(level, ordering)
+
+                if feature == 'energy':
+                    e = [energy(node.data) for node in nodes]
+                    feature_vector.extend(e)
+
+                elif feature == 'energy_ratio':
+                    e = [energy(node.data) for node in nodes]
+                    total_energy = np.sum(e)
+                    energy_ratios = [energy(node.data) / total_energy for node in nodes]
+                    feature_vector.extend(energy_ratios)
+
+                elif feature == 'kurtosis':
+                    kurts = [ft.kurtosis(node.data) for node in nodes]
+                    feature_vector.extend(kurts)
+
[…]

### 2024-04-22 machine-learning/vibrodiagnostics/mafaulda.py

@@ -135,7 +135,8 @@ def features_by_domain(
         dataset: ZipFile,
         filename: str,
         window: int = None,
-        parts: int = 1) -> pd.DataFrame:
+        parts: int = 1,
+        multirow: bool = False) -> pd.DataFrame:
 
     # print(f'Processing: {filename}')
     fs = SAMPLING_RATE
@@ -150,15 +151,21 @@ def features_by_domain(
 
     result = []
     for i, df in enumerate(dataframe):
-        fvector = [
+        header = [
             ('fault', [fault]),
             ('severity', [severity]),
             ('seq', [f'{seq}.part.{i}']),
             ('rpm', [df['rpm'].mean()])
         ]
         for col in columns:
-            fvector.extend(features_calc(df, col, fs, window))
-        result.append(pd.DataFrame(dict(fvector))) 
+            if multirow is True:
+                for data in features_calc(df, col, fs, window):
+                    row = dict(header.copy())
+                    row.update(data)
+                    result.append(pd.DataFrame(row))
+            else:
+                header.extend(features_calc(df, col, fs, window))
+                result.append(pd.DataFrame(dict(header))) 
 
     return pd.concat(result).reset_index(drop=True)
 

### 2024-04-22 machine-learning/vibrodiagnostics/models.py

@@ -7,12 +7,13 @@ import itertools
 import numpy as np
 import pandas as pd
 from imblearn.over_sampling import RandomOverSampler
+from scipy.stats import percentileofscore
 
 from sklearn.neighbors import KNeighborsClassifier
 from sklearn.model_selection import KFold
 from sklearn import metrics
 from sklearn.metrics import silhouette_score
-from sklearn.preprocessing import MinMaxScaler
+from sklearn.preprocessing import MinMaxScaler, PowerTransformer
 from sklearn.decomposition import PCA
 
 from sklearn.discriminant_analysis import LinearDiscriminantAnalysis
@@ -68,12 +69,13 @@ def kfold_accuracy(
         k_neighbors: int,
         kfolds: int,
         model_name: str, 
+        power_transform: bool = True,
         knn_metric='euclidean') -> Dict[str, float]:
 
     # Class balancing
     oversample = RandomOverSampler(sampling_strategy='not majority', random_state=10)
     X, Y = oversample.fit_resample(X, Y.to_numpy())
-    X.reset_index(drop=True, inplace=True)
+    X = X.reset_index(drop=True)
     Y = pd.Series(Y)
 
     kf = KFold(n_splits=kfolds, shuffle=True, random_state=10)
@@ -86,10 +88,14 @@ def kfold_accuracy(
             X.loc[train_idx].copy(), X.loc[test_idx].copy(),
             Y.loc[train_idx].copy(), Y.loc[test_idx].copy()
         )
-        # Scale
-        scaler = MinMaxScaler()
-        x_train[x_train.columns] = scaler.fit_transform(x_train)
-        x_test[x_test.columns] = scaler.transform(x_test)
+
+        if power_transform is True:
+            transform = PowerTransformer(method='yeo-johnson', standardize=True)
+        else:
+            transform = MinMaxScaler()
+
+        x_train[x_train.columns] = transform.fit_transform(x_train)
+        x_test[x_test.columns] = transform.transform(x_test)
     
         # Train k-NN model on all features
         if model_name == 'knn':
@@ -117,21 +123,19 @@ def kfold_accuracy(
 def all_features(
         X: pd.DataFrame,
         Y: pd.DataFrame,
-        model: str,
+        model: str = 'knn',
+        power_transform: bool = False,
         k_neighbors: list = list(range(1, 40, 4)),
         kfold_param: int = 5) -> dict:
-
-    # Class balancing
-    oversample = RandomOverSampler(sampling_strategy='not majority', random_state=10)
[…]

### 2024-04-22 machine-learning/vibrodiagnostics/visualize.py

@@ -11,107 +11,45 @@ import seaborn as sb
 from sklearn.metrics import silhouette_score
 from sklearn.preprocessing import MinMaxScaler
 from sklearn.decomposition import PCA
+from scipy.signal import freqz
 
 from vibrodiagnostics import extraction, models
 
 
-def plot_models_performance_bar(
-        X_temporal: pd.DataFrame,
-        X_spectral: pd.DataFrame, 
-        Y: pd.DataFrame,
-        models_summary: pd.DataFrame,
-        k_neighbors: int = 5,
-        number_of_features: int = 3) -> pd.DataFrame:
+DOMAIN_TITLES = {
+    'TD': 'Time domain',
+    'FD': 'Frequency domain',
+    'TD+FD': 'Time and Frequency domain'
+}
 
-    MODEL_TYPE = 'knn'
-    Y = Y.dropna().astype('category')
-    X_temporal = X_temporal[X_temporal.index.isin(Y.index)].copy()
-    X_spectral = X_spectral[X_spectral.index.isin(Y.index)].copy()
-    Y = Y[Y.index.isin(X_temporal.index)].astype('category')
 
-    X_temporal = X_temporal.reset_index(drop=True)
-    X_spectral = X_spectral.reset_index(drop=True)
-    Y = Y.reset_index(drop=True)
-    Y = Y.cat.codes
 
-    fig, ax = plt.subplots(1, 2, figsize=(10, 5)) 
+def plot_models_performance_bar(results: pd.DataFrame) -> pd.DataFrame:
+    if len(results['domain'].unique()) == 1:
+        fig, ax = plt.subplots(1, 1, figsize=(8, 6))
+        ax = [ax]
+    else:
+        fig, ax = plt.subplots(1, 2, figsize=(10, 5), sharey=True)
+
+    width = 0.13
     columns = ['train', 'test']
-    kfolds = 5
     x = np.arange(len(columns))
-    domains = {'TD': X_temporal, 'FD': X_spectral}
-    results = []
 
-    for i, (domain, X) in enumerate(domains.items()):
-        width = 0.13
+    for i, (domain_name, domain) in enumerate(results.groupby(by=['domain'])):
+        for pos, (name, scenario) in enumerate(domain.iterrows(), start=-3):
+            title = scenario['set']
+            y = scenario['train_accuracy'], scenario['test_accuracy']
+            rect = ax[i].bar(x + pos*width, y, width, label=title)
 
[…]

### 2024-04-27 thesis/chapters/03-design.tex
Export graphs from experiments and prepare outline of thesis

@@
     \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
-    \item Combine feature selection with an online machine learning model.
     \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
@@
 
+% -------------------------------------------------------------------------------
+\clearpage
+
+% All features --------------------------------------------------------
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD-confusion-matrix.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD-confusion-matrix.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{All features confusion matrix}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{All features accuracy based on k-value}
+\end{figure}
+
+% Standing fan (EDA) --------------------------------------------------------
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
+        \caption{Speed 1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
+        \caption{Speed 2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
+        \caption{Speed 3}
+    \end{subfigure}
+    \caption{Frequency spectrum from sound of standing fan}
+\end{figure}
+
+% Frequency from vibrations
+% Plot
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
+    \caption{Estimation of rotation speed from vibrations}
+\end{figure}
+
+% Clusters with true labels --------------------------------------------------------------
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{PCA of all features to 2 components}
+\end{figure}
+
+%TODO fix inverse transform
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{3 Best features and their ranges}
+\end{figure}
+
+% Incremental learning ------------------------------------------------------
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
+        \caption{Order by raising severity}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
+        \caption{Order after relabeing normal class}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
+        \caption{Order of severities}
+    \end{subfigure}
+    \caption{Ordering of faults}
+\end{figure}
+
+% Gradual
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Gradual learning (window = 1, skip = 0)}
+\end{figure}
+
+% Tumbling windows
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Tumbling window in incremental learning}
+\end{figure}
+
+% % Label skips and parts of dataset
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure} 
+    \caption{Skip labels in incremental learning}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Skip labels in incremental learning with different sizes}
+\end{figure}
+
+% Histograms of machinery measurements
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
+        \caption{C1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
+        \caption{C2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
+        \caption{M1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
+        \caption{M2}
+    \end{subfigure} 
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
+        \caption{M3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
+        \caption{P1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
+        \caption{P2}
+    \end{subfigure} 
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
+        \caption{P3}
+    \end{subfigure} 
+    \caption{Histograms}
+\end{figure}
+
+% Correlations to RPM
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
+    \caption{Correlation of features to RPM over all experiments}
+\end{figure}
+
+% Features range (3D)
+% Standing Fan
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-TD-features.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-FD-features.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature range in standing fan}
+\end{figure}
+
+% Pumps and compressors
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature range in pumps}
+\end{figure}
+
+% Mafaulda
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/features-TD-dim3-A+B.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/features-FD-dim3-A+B.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature range in MaFaulDa}
+\end{figure}
+
+% Feature combinations accuracy
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-accuracy.png}
+        \caption{Accuracy}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
+        \caption{Percentile}
+    \end{subfigure}
+    \caption{Feature selection method choices}
+\end{figure}
+
+% In fsel percentile - mention median from notebook for each method - table
+\begin{table}[h]
+\begin{tabular}{|l|r|r|}
+\hline
+\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
+Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
+Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
+F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
+Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-features-A-dim3.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-5-neighbors-A-dim3.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-features-A-dim3.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-5-neighbors-A-dim3.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \caption{Model accuracy distribution}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
+    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
+\end{figure}
+
+% Counts table
+
+% Best feature selection methods table (order by best count)
+
+% Bearing frequencies table
+
+\clearpage
+
+%TODO ---------------------------------------------------------------------------
 \section{Dataset exploration}
@@
         \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
-        \caption{Temporal domain waveforms}
+        \caption{Time domain waveforms}
         \label{fig:design:fault-temporal-waveform}
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
-        \caption{Temporal features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
-        \caption{Spectral features}
-    \end{subfigure}
-    \caption{Feature value ranges in inner bearing position (A)}
-    \label{fig:design:feature-range}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
+%        \caption{Time-domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
+%        \caption{Frequency-domain features}
+%    \end{subfigure}
+%    \caption{Feature value ranges in inner bearing position (A)}
+%    \label{fig:design:feature-range}
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
-    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
-    \label{fig:design:pca-explained-variance} 
-\end{figure}
+%\begin{figure}[h!]
+%    \centering
+%    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
+%    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
+%    \label{fig:design:pca-explained-variance} 
+%\end{figure}
 
@@
 
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
-        \caption{Temporal features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
-        \caption{Spectral features}
-    \end{subfigure}
-    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
-    \label{fig:design:pca-loading-plot} 
-\end{figure}
+%\begin{figure}[h!]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
+%        \caption{Temporal features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
+%        \caption{Spectral features}
+%    \end{subfigure}
+%    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
+%    \label{fig:design:pca-loading-plot} 
+%\end{figure}
 
@@
 
-\begin{itemize}
-\itemsep0pt
-\item \textbf{online}: a boolean selector that influences whether metrics are calculated in batch or incremental fashion,
-\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
-\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly90'' against which similarity is judged,
-\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
-\end{itemize}
-
 In feature evaluation for fault prediction, we use hold-out validation in batch models and progressive valuation in online models.
@@
 Reference implementation of feature selection metrics uses Python packages Scikit Learn\footnote{SciKit Learn: \url{https://scikit-learn.org/}} in batch learning and RiverML\footnote{RiverML: \url{https://riverml.xyz/}} for online learning.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/approval-voting-temporal.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/approval-voting-spectral.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Approval rating of the best triplet of features to target variable ``fault'' scored by rank product of correlation, F statistic, and mutual information.}
-    \label{fig:design:approval-rating-features}
-\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-fault.png}
-        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-fault.png}
-        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-anomaly90.png}
-        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-anomaly90.png}
-        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
-    \end{subfigure}
-    \caption{Confusion matrix of k-NN predictions on bearing position A}
-    \label{fig:design:KNN-confusion-matrix}
-\end{figure}
-
 Two models are created for the target variable in classification with all 10 temporal and 11 spectral features.
@@
 
-\begin{table}[h]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|l|l|rrr|rrr|}
-\hline
-\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Bearing\\ position\end{tabular}}} & \multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Target\\ variable\end{tabular}}} & \multirow{2}{*}{\textbf{Observations}}                                             & \multicolumn{3}{l|}{\textbf{Temporal domain}}                                                                                                                                                                                                                                    & \multicolumn{3}{l|}{\textbf{Spectral domain}}                                                                                                                                                                                                                                    \\ \cline{4-9}
-                                                                                     &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
-\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9859}                                                               & \multicolumn{1}{r|}{0.9736}                                                              & 0.97                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9869}                                                               & \multicolumn{1}{r|}{0.9800}                                                              & 0.98                                                                                     & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
-\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9316}                                                               & \multicolumn{1}{r|}{0.8969}                                                              & 0.90                                                                                     & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9568}                                                               & \multicolumn{1}{r|}{0.9273}                                                              & 0.93                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{k-NN model performance trained on all extracted features}
-\label{tab:design:all-extracted-features}
-\end{table}
+%\begin{table}[h]
+%\centering
+%\renewcommand{\arraystretch}{1.2}
+%\begin{adjustbox}{width=\textwidth}
+%
+%\end{tabular}
+%\end{adjustbox}
+%\caption{k-NN model performance trained on all extracted features}
+%\label{tab:design:all-extracted-features}
+%\end{table}
 
@@
 The accuracy of the k-NN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
-        \caption{Testing set}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
-        \caption{Training set}
-    \end{subfigure}
-    \caption{Range of prediction accuracy in all k-NN models with subset of 3 features. Subplots show three different predicted variables.}
-    \label{fig:design:feature-combinations-KNN}
-\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
-        \caption{Spectral domain features}
-    \end{subfigure} 
-    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
-    \label{fig:design:feature-space-scatter}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
+%        \caption{Temporal domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
+%        \caption{Spectral domain features}
+%    \end{subfigure} 
+%    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
+%    \label{fig:design:feature-space-scatter}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
-        \caption{Testing set}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
-        \caption{Training set}
-    \end{subfigure} 
-    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
-    \label{fig:design:KNN-accuracy-batch}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
+%        \caption{Testing set}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
+%        \caption{Training set}
+%    \end{subfigure} 
+%    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
+%    \label{fig:design:KNN-accuracy-batch}
+%\end{figure}
 
@@
 
+\clearpage
 \subsection{Online models}
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
-        \caption{Event ordering of faults}
-        \label{fig:design:online-event-order}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
-        \caption{Fault severity levels ordering}
-        \label{fig:design:online-count-severity-level}
-    \end{subfigure}
-    \caption{Label sequencing for progressive evaluation}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
+%        \caption{Event ordering of faults}
+%        \label{fig:design:online-event-order}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
+%        \caption{Fault severity levels ordering}
+%        \label{fig:design:online-count-severity-level}
+%    \end{subfigure}
+%    \caption{Label sequencing for progressive evaluation}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
-        \caption{Principal components from temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
-        \caption{Principal components from spectral domain features}
-    \end{subfigure}
-    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
-    \label{fig:design:scatter-plot-online}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
+%        \caption{Principal components from temporal domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
+%        \caption{Principal components from spectral domain features}
+%    \end{subfigure}
+%    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
+%    \label{fig:design:scatter-plot-online}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
-    \label{fig:design:online-fault-delay-sliding}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
+%        \caption{Temporal domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
+%        \caption{Spectral domain features}
+%    \end{subfigure}
+%    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
+%    \label{fig:design:online-fault-delay-sliding}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
-    \label{fig:design:online-fault-delay-tumbling}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
+%        \caption{Temporal domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
+%        \caption{Spectral domain features}
+%    \end{subfigure}
+%    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
+%    \label{fig:design:online-fault-delay-tumbling}
+%\end{figure}
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
-    \label{fig:design:online-label-skip}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
+%        \caption{Temporal domain features}
+%    \end{subfigure}
+%    \hfill
+%    \begin{subfigure}[b]{0.49\textwidth}
+%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
+%        \caption{Spectral domain features}
+%    \end{subfigure}
+%    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
+%    \label{fig:design:online-label-skip}
+%\end{figure}
 

### 2024-04-27 thesis/chapters/analysis/2-features.tex
Export graphs from experiments and prepare outline of thesis

@@
 It is important to note that the design of features is not a standalone step in the machine learning pipeline, but it should be done iteratively to improve the target model.
-Signal features are computed in the temporal and spectral domain~\cite{brito_fault_2021}.
+Signal features are computed in the time and frequency domain~\cite{brito_fault_2021}.
 
-\subsection{Temporal domain features}
+\subsection{Time-domain features}
 The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
@@
 \end{tabular}
-\caption{Temporal domain features}
+\caption{Time-domain features}
 \label{tab:td-features}
@@
 
-\subsection{Spectral domain features}
+\subsection{Frequency-domain features}
 The mechanical faults present themselves as oscillatory patterns which are combinations of frequencies with various amplitudes.
@@
 \end{tabular}
-\caption{Frequency domain features}
+\caption{Frequency-domain features}
 \label{tab:fd-features}
@@
 
-In the spectral domain, we can obtain the usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
+In the frequency domain, we can obtain the usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
 Additionally, spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal-to-noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
@@
 \end{align}\end{ceqn}
+
+\subsection{Bearing defect frequencies}
+%TODO n = number of balls, d - average of outer ring diameter and outer ring, f_s - rotation speed, beta - contact angle - ball bearings close to 0
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{assets/analysis/bearing-parts.jpg}
+    \caption{Bearing parts~\cite{lu_what_is_ball_bearing_2023}}
+    \label{fig:bearing-parts}
+\end{figure}
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}            & \textbf{Equation}                                                                   
+ \\ \hline
+\textit{Outer race fault frequency} & $ BPFO = f_s \cdot \frac{n}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right)$               
+\\ \hline
+\textit{Inner race fault frequency} & $ BPFI = f_s \cdot \frac{n}{2} \cdot \left(1 + \frac{d}{D}\cos \beta \right)$
+\\ \hline
+\textit{Cage rotation frequency}    & $ FTF = f_s \cdot \frac{1}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right) $      
+\\ \hline
+\textit{Ball defect frequencies} & $ BSF = f_s \cdot \frac{D}{d} \cdot \left(1 + \left(\frac{D}{d}\cos \beta\right)^2 \right) $
+\\ \hline
+\end{tabular}
+\caption{Bearing defect frequencies}
+\label{tab:bearing-defect-features}
+\end{table}
 
@@
 
-\subsection{Scores for ranking}
+\subsection{Feature importanance ranking}
 Most of the scores are based on supervised learning, so they expect true class labels to apportion the measurements respectively.

### 2024-04-27 thesis/chapters/analysis/3-diagnostics.tex
Export graphs from experiments and prepare outline of thesis

@@
 \textbf{Half-Space Tree} (HS-Tree) stands upon the concept of Isolation forest.
-It assumes that random splitting of each axis in the feature space will isolate outliers to their separate divisions sooner than non-deviant observations~\cite{gervasi_anomaly_2020,torres_automatic_2022}.
+It assumes that random splitting of each axis in the feature space will isolate outliers to their separate divisions sooner than non-deviant observations~\cite{gervasi_anomaly_2020, torres_automatic_2022}.
 This ensemble of trees is better suited for batch setting.
@@
 The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and links to both child nodes~\cite{tan_fast_2011}.
-
-The anomaly profile in the latest window is always compared to the predecessor reference window.
-After the latest window is filled up, it replaces the reference window.
-It suffices to use a window size of 250 and an ensemble of 25 trees~\cite{tan_fast_2011}.
 

### 2024-04-27 thesis/chapters/analysis/4-datasets.tex
Export graphs from experiments and prepare outline of thesis

@@
 \subsection{Machinery Fault Database}
-MaFaulDa\footnote{\url{https://www02.smt.ufrj.br/~offshore/mfs/page_01.html}} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
+MaFaulDa~\cite{mafaulda_dataset} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
 Each series has 5~seconds in duration and is captured at 50 kHz.
@@
 \subsection{CWRU bearings dataset}
-In Case Western Reserve University (CWRU) bearing dataset\footnote{\url{https://engineering.case.edu/bearingdatacenter/download-data-file}} recordings were made of a fan end and drive end bearings under motor loads of 0, 1, 2, and 3~Horsepower (equivalently 0, 0.75, 1.49, 2.24~kW).
+In Case Western Reserve University (CWRU) bearing dataset~\cite{cwru_dataset} recordings were made of a fan end and drive end bearings under motor loads of 0, 1, 2, and 3~Horsepower (equivalently 0, 0.75, 1.49, 2.24~kW).
 Shaft speed was unaltered in all experiments, but it fluctuated between 1720 and 1797~rpm (approx.
@@
 \subsection{Unbalance of the rotating shaft}
-Unbalance Detection of a Rotating Shaft\footnote{\url{https://www.kaggle.com/datasets/jishnukoliyadan/vibration-analysis-on-rotating-shaft}} is a Kaggle dataset that simulates 4 different unbalance strengths.
+Unbalance Detection of a Rotating Shaft~\cite{unbalance_shaft} is a Kaggle dataset that simulates 4 different unbalance strengths. 
 \begin{figure}[h]

### 2024-04-27 machine-learning/vibrodiagnostics/models.py

@@ -163,7 +163,7 @@ def feature_combinations(
         power_transform: bool = False) -> List[dict]:
     
     results = []
-    for features in tqdm(itertools.combinations(X.columns, r=num_of_features)):
+    for features in tqdm(list(itertools.combinations(X.columns, r=num_of_features))):
         r = kfold_accuracy(
             X[list(features)], Y, k_neighbors, kfolds, model,
             power_transform=power_transform

### 2024-04-27 machine-learning/vibrodiagnostics/visualize.py

@@ -24,6 +24,15 @@ DOMAIN_TITLES = {
 
 
 
+def evolution_of_severity_levels(df: pd.DataFrame):
+    fig, ax = plt.subplots(1, 1, figsize=(10, 5))
+    ax.plot(np.arange(0, len(df)), df['severity_level'], color='red')
+    ax.set_xlabel('Observations')
+    ax.set_ylabel('Severity level')
+    ax.grid()
+    plt.show()
+
+
 def plot_models_performance_bar(results: pd.DataFrame) -> pd.DataFrame:
     if len(results['domain'].unique()) == 1:
         fig, ax = plt.subplots(1, 1, figsize=(8, 6))

### 2024-04-28 thesis/chapters/02-analysis.tex
Turn outline into section headings

@@
 
-\input{chapters/analysis/1-condition-monitoring}
-\input{chapters/analysis/2-features}
-\input{chapters/analysis/3-diagnostics}
-\input{chapters/analysis/4-datasets}
+\section{Condition monitoring} \label{section:condition-monitoring}
+All rotating machinery eventually fails because of the long-term strain on the individual parts, inadequate workmanship, installation, or operational procedures.
+In the end, these factors cause the equipment not to fulfill its intended functionality.
+Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, oil and particle analysis, ultrasonic testing, etc.
+Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+
+The defect needs to be repaired or replaced, preferably without significant production downtime, further damage to the other attached elements, or any endangerment of the responsible personnel.
+The maintenance strategies are chosen according to the machine's importance as a result of potential failure's impact on the system.
+The guide to set appropriate maintenance procedures as outlined in the IEC~60706-2 standard, and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
+
+\subsection{Maintenance strategies}
+There are three different approaches to maintenance across the industry: \textbf{reactive, preventive, and predictive}~\cite{scheffer_practical_2004}.
+In general, the more sophisticated methods are beneficial in a high-stakes environment.
+The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
+In certain situations, it suffices to utilize a simpler maintenance program, but predictive maintenance gains attraction in Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.
+
+\textbf{Reactive maintenance} allows machinery to run until a complete failure.
+This is the most inappropriate way to maintain the production line, but it is straightforward enough.
+It requires a large stock of replacement parts on-site and breakage inflicts a ``crisis management mode'' upon the plant \cite{scheffer_practical_2004}.
+On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment from failure~\cite{ziaran_technicka_2013}.
+
+\textbf{Preventive maintenance} is performed before any issue is detected.
+Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure).
+The schedule is crucial but can result in components being replaced in good condition, creating waste.
+The parts can occasionally stay in operation too long, and the machine breaks as a result.
+Conservative planning is usually the norm to keep the machines always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
+
+\textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates waste in overall resource utilization of cautious prevention.
+The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and the identification of troublesome components.
+
+A measurable decrease in effectiveness allows us to order necessary parts in advance and organize repairs of several machines at a convenient time.
+The missed detection leads to increased costs compared to previous methods and raises the expectation that faults are distinguishable among themselves~\cite{davies_handbook_2012}.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\textwidth]{assets/analysis/P-F-Curve.png}
+	\caption{P-F curve represents the evolution of the asset's health~\cite{jennions_integrated_2011}}
+	\label{fig:p-f-curve}
+\end{figure}
+
+The \emph{P-F curve} is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
+Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval~\cite{bousdekis_enterprise_2021}.
+These division points are not exactly set but have a statistical distribution to them.
+
+The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the ``run-to-failure'' histories, and usage parameters~\cite{okoh_overview_2014}.
+Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.6\textwidth]{assets/analysis/bath-tub-curve.png}
+	\caption{Bathtub curve~\cite{mohanty_machinery_2015}}
+	\label{fig:bathtub-curve}
+\end{figure}
+
+A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded, but also in the early stages soon after assembly.
+Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes.
+During the stable middle phase, malfunction can occur after the machine's excessive overload.
+The time plot to failure rate is known as the bathtub curve~(Fig.~\ref{fig:bathtub-curve}).
+
+\subsection{Vibration fault types}
+Mechanical problems during machinery operation bring about vibrations in many instances.
+Therefore, vibroacoustic diagnostics is considered as one of the most important methods in early component fault identification~\cite{ziaran_technicka_2013}.
+
+The cause of vibration comes out of the changing force in its magnitude or direction.
+The most emerging defects can be encompassed by explaining the deficiencies of the mechanical structure.
+These defects are broadly categorized as \textbf{unbalance, misalignment, looseness, eccentricity, deformation, crack, and influence of the external force} (friction)~\cite{davies_handbook_2012}.
+It is important to stress that our concern is not the underlying deformities in mechanical parts, but the correct fault classification based on the signal waveform.
+
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.6\textwidth]{assets/analysis/complex-vibrations.png}
+	\caption{Complex machinery vibrations~\cite{davies_handbook_2012}}
+	\label{fig:machinery-vibrations}
+\end{figure}
+
+Rotating machine disorders exhibit frequency signatures at various ranges in the frequency spectrum with supplementary symptoms carried in phase signal.
+Most of the occurring faults can be tied to the main rotational speed of the component under investigation (Fig.~\ref{fig:machinery-vibrations})~\cite{davies_handbook_2012}.
+Imbalance, misalignment, and looseness normally appear at frequencies up to 300 Hz.
+These low-frequency faults are associated with the movement of the shaft and primarily coincide with revolution speed and its harmonics.
+Bearing and gearbox defects in the late stages of development, show up in the range between 300 Hz and 1 kHz.
+Higher frequencies, measured traditionally to a limit of 10 kHz, help notice the faults in bearings even sooner~\cite{torres_automatic_2022}.
+
+One of the methods vibration experts utilize in the identification of the damaged part, according to the frequency spectrum, is \textbf{order analysis}.
+The excessive peaks at harmonic frequencies are of interest.
+Harmonics are integer multiples of fundamental frequency (1x rpm)~(Tab.~\ref{tab:vibration-causes}):
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|ll|l|l|}
+\hline
+\multicolumn{2}{|l|}{\textbf{Frequency content}}                            & \textbf{Likely reason}                                                                                                     & \textbf{Other causes}                                                                                                                          \\ \hline
+\multicolumn{1}{|l|}{\multirow{4}{*}{Synchronous}} & 1 x rpm                & Imbalance                                                                                                                & \begin{tabular}[c]{@{}l@{}}Eccentric journals\\ Bent shaft / Misalignment\\    (high axial vibration)\\ Bad belt (if rpm of belt)\end{tabular} \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 2 x rpm                & Looseness                                                                                                                & \begin{tabular}[c]{@{}l@{}}Misalignment \\    (high axial vibration)\\ Cracked rotor\\ Bad belt (if rpm of belt)\end{tabular}                  \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & 3 x rpm                & Misalignment                                                                                                             & and axial looseness                                                                                                                             \\ \cline{2-4}
+\multicolumn{1}{|l|}{}                             & Many x rpm             & \begin{tabular}[c]{@{}l@{}}Bad gears\\ Severe looseness\end{tabular}                                                     & \begin{tabular}[c]{@{}l@{}}Gear teeth x rpm\\ Fan blade count x rpm\end{tabular}                                                               \\ \hline
+\multicolumn{1}{|l|}{Sub-synchronous}                 & \textless 1 x rpm      & Oil whirl                                                                                                                & \begin{tabular}[c]{@{}l@{}}Bad drive belt\\ Background\\ Resonance\end{tabular}                                                                \\ \hline
+\multicolumn{1}{|l|}{Non-synchronous}              & \multicolumn{1}{c|}{-} & \begin{tabular}[c]{@{}l@{}}Electrical problems (x 50 Hz)\\ Reciprocating forces\\ Aerodynamic forces \\ Bad antifriction bearings\end{tabular} & Rubbing \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Expert observed likely vibration causes (based on~\cite{davies_handbook_2012,ziaran_technicka_2013,noauthor_iso_2002})}
+\label{tab:vibration-causes}
+\end{table}
+
+Because of inherent tolerances in machine manufacturing and assembly, the rotational frequency always manifests itself, even in baseline signature~\cite{davies_handbook_2012, noauthor_iso_2002}.
+In the most likely scenario, some faults appear as compared to rotational frequency solely in \textbf{synchronous, subsynchronous, or non-synchronous components}.
+The defects can occur in a predictable combination of the ones mentioned.
+Other common patterns experts look for are modulation sidebands typical for bearings and gears extractable with cepstrum analysis~\cite{ziaran_technicka_2013}.
+Procedures relying on elimination narrow down unrelated causes effectively.
+
+%TODO bearing image / equations
+
+\subsection{Technical standards} \label{section:technical-standards}
+Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards.
+Standards are concerned with each step in the process that originates with transducer placements and data acquisition.
+They prescribe conventions for setting fault severity levels and provide empirically observed vibration characteristics of common defects.
+Relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
+\bigbreak
+
+\textbf{ISO 20816-1:2016} establishes the approaches of vibration measurement and evaluation on non-rotating housing of machinery parts~\cite{noauthor_iso_2016}.
+The measurement units are agreed upon for kinematic quantities of vibrations.
+Acceleration is measured in meters per second squared ($m/s^2$), velocity in millimeters per second ($mm/s$), and displacement in micrometers ($\mu m$).
+It is customary to evaluate broad-band vibration velocity in terms of root mean square value (rms), as it is related to signal energy.
+No simple direct relationship is expressible among these physical quantities, except in stationary signals.
+
+The vibration severity is the maximum magnitude measured in two radial directions (horizontal, and vertical) or supplemented with a third direction along the shaft on the axial axis.
+Multiple measurement locations, i.e.
+on different bearings or couplings, should be assessed independently.
+
+Criteria introduced to judge vibration severity are absolute vibration magnitude, change in the magnitude vector, and rate of change.
+In terms of maximal magnitudes, the machines of varying sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
+The values in this table serve as guidelines towards realistic requirements between machine manufacturers and their customers.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\textbf{\begin{tabular}[c]{@{}c@{}}Vibration velocity\\ rms {[}mm/s{]}\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class I\\ Small machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class II\\ Medium machines\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class III\\ Large machines\\ Rigid supports\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Class IV\\ Large machines\\ Flexible support\end{tabular}} \\ \hline
+0.28                                                                                 & \cellcolor[HTML]{9AFF99}                                                  & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1}
+0.45                                                                                 & \cellcolor[HTML]{9AFF99}                                                  & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1}
+0.71                                                                                 & \multirow{-3}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}               & \cellcolor[HTML]{9AFF99}                                                    & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-2}
+1.12                                                                                 & \cellcolor[HTML]{FFFC9E}                                                  & \multirow{-4}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                 & \cellcolor[HTML]{9AFF99}                                                                     & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-1} \cline{3-3}
+1.8                                                                                  & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}       & \cellcolor[HTML]{FFFC9E}                                                    & \multirow{-5}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                                  & \cellcolor[HTML]{9AFF99}                                                                      \\ \cline{1-2} \cline{4-4}
+2.8                                                                                  & \cellcolor[HTML]{F8A102}                                                  & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}         & \cellcolor[HTML]{FFFC9E}                                                                     & \multirow{-6}{*}{\cellcolor[HTML]{9AFF99}\textbf{Good (A)}}                                   \\ \cline{1-1} \cline{3-3} \cline{5-5}
+4.5                                                                                  & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}     & \cellcolor[HTML]{F8A102}                                                    & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}                          & \cellcolor[HTML]{FFFC9E}                                                                      \\ \cline{1-2} \cline{4-4}
+7.1                                                                                  & \cellcolor[HTML]{FD6864}                                                  & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}       & \cellcolor[HTML]{F8A102}                                                                     & \multirow{-2}{*}{\cellcolor[HTML]{FFFC9E}\textbf{Satisfactory (B)}}                           \\ \cline{1-1} \cline{3-3} \cline{5-5}
+11.2                                                                                 & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}                        & \cellcolor[HTML]{F8A102}                                                                      \\ \cline{1-1} \cline{4-4}
+18                                                                                   & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \cellcolor[HTML]{FD6864}                                                                     & \multirow{-2}{*}{\cellcolor[HTML]{F8A102}\textbf{Unsatisfactory (C)}}                         \\ \cline{1-1} \cline{5-5}
+28                                                                                   & \cellcolor[HTML]{FD6864}                                                  & \cellcolor[HTML]{FD6864}                                                    & \cellcolor[HTML]{FD6864}                                                                     & \cellcolor[HTML]{FD6864}                                                                      \\ \cline{1-1}
+45                                                                                   & \multirow{-5}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}       & \multirow{-4}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}         & \multirow{-3}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}                          & \multirow{-2}{*}{\cellcolor[HTML]{FD6864}\textbf{Unacceptable (D)}}                           \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{ISO 20816 vibration severity chart with typical magnitudes \cite{noauthor_iso_2016}}
+\label{tab:iso20816-vibration-severity}
+\end{table}
+
+Zone A is reserved for newly commissioned machines.
+Zone B signifies suitability for long-term operation.
+In zone C the machine is deemed in unsatisfactory condition and corrective action should be taken soon.
+Finally, in zone D vibrations can cause damage to the machine.
+The span of acceptable values differs with the machine class from \rom{1} through to \rom{4} and their output power of 15~kW (class~\rom{1}), 75~kW (class~\rom{2}), 10~MW (class~\rom{3}), or greater.
+
+The operational limits in the form of \emph{alarms} and \emph{trips} are usually established on the zone boundaries or close to them.
+Alarms are placed between zones B and C providing a warning about reaching the threshold significant for noticeable change.
+Trips in between zones C and D urge immediate action or machine shut down.
+Both limits should not exceed 1.25 times the upper boundary of the lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
+
+\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in terms of the vocabulary in ISO 20186.
+According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval.
+Both designs can be permanently mounted.
+In continuous collection, it is recommended to have a ``multiplexing rate sufficiently rapid, so there is no significant data or trends lost''~\cite{noauthor_iso_2002}.
+When channels are scanned in succession with gaps between data points, the system is known as ``scanning''.
+
+The condition monitoring program is run according to a flowchart adapted from one designed by the standard specifically to best benefit the plant.
+Those steps can be summarized as follows~\cite{noauthor_iso_2002}:
+
+\begin{enumerate}
+\itemsep0pt
+\item Review machinery history and establish failure modes.
+\item When vibration monitoring is not applicable, check for other condition-monitoring techniques or resort to preventive maintenance.
+\item Select monitoring points and take preliminary vibration measurements.
+\item Select vibration monitoring techniques: broadband, frequency analysis, or special techniques, and set parameters of measurement units.
+\item Take baseline measurements.
+\item Change levels that would warrant investigation.
+\item Carry out routine condition monitoring.
+\item If an alarm was exceeded, notify appropriate personnel to review data and trends, perform diagnostic evaluation, and repair as necessary.
+In case a new baseline is needed, continue in the step of taking baseline measurements.
+\item Shut down the machine when the trip level is exceeded. Then proceed the same as after the alarm is triggered.
+\end{enumerate}
+
+Measurement of vibrations should be accompanied by a description of the machine and its operating conditions.
+The machine description includes its identifier and type, power source, rated rotation speed and power, configuration (shaft or belt driven), and machine support.
+Measurement parameters are to be recorded alongside the measurement value itself, such as timestamp, transducer type, sensor location and orientation in \textbf{MIMOSA convention} (Machinery Information Management Open System Alliance), measurement units and units qualifier (p-p, rms), and other processing options (filters, number of averages, etc.)~\cite{noauthor_iso_2002}.
+
+The transducer of choice for condition monitoring is the accelerometer, which can provide the acceleration value of the body and velocity after signal integration.
+However, standard advise against double integrating for displacement.
+The recommended frequency range for an accelerometer is 0.1~Hz to 30~kHz.
+The choice of transducer mount significantly lowers its resonance frequency, which is least influenced by the stud mount and stiff cement mount.
+The resonance is reduced to around 8~kHz with the use of soft epoxy or permanent magnet.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.8\textwidth]{assets/analysis/transducer-response.png}
+	\caption{The transducer linear response and resonance in tolerance intervals~\cite{noauthor_iso_2002}}
+	\label{fig:tranducer-response}
+\end{figure}
+
+Broadband measurement requires ``frequency ranges of 0.2 times the lowest rotational frequency to the highest frequency of interest''~\cite{noauthor_iso_2002}, not exceeding 10 kHz, with rms velocity 0.1 - 100~mm/s.
+Bearings and gear diagnosis may push the upper-frequency limit even higher.
+The tolerances of amplitude and frequency calibrations fall into two types with allowable tolerances of $\pm 5 \%$ or $\pm 10 \%$~(Fig.~\ref{fig:tranducer-response}).
+
+Equipment's ``health'' can be mischaracterized when there are significant differences in the machine's normal operating conditions.
+Baseline measurements in all acceptable conditions are to be acquired to reduce the error in vibration evaluation.
+According to the bathtub curve~(Fig.~\ref{fig:bathtub-curve}) reference signatures should be obtained after the initial part wear-in period.
+The reference spectral mask of the baseline condition is designed if maximal acceptance amplitudes are different for each significant frequency band~\cite{ziaran_technicka_2013}.
+
+The vibration baseline is defined by broad-band magnitudes and phases of motion vectors, the waveform in the time and frequency domain, the rotational speed of the machine as well as its frequency response to different speeds during start-up and coast-down captured in the Bode plot and waterfall plot.
+Changes during the machine's operation are then depicted in value trends.
+Trends can be shown by overall amplitudes or limited to frequency bands.
+
+\section{Signal preprocessing} \label{section:signal-preprocessing}
+The vibration signals in a factory environment are inherently full of disturbances.
+Nearby equipment operation and handling of heavy objects in the surroundings can all contribute to the unwanted chaotic movement in otherwise mostly pure oscillatory motion.
+In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset as a result of slight miscalibration, and bias originating from a constant force of gravity.
+These unavoidable distortions are to some extent suppressable by digital filters.
+In the preprocessing stage, we consider trend removal, noise reduction with adaptive filters, and time synchronous averaging to eliminate external interference.
+
+\subsection{Detrending}
+The oscillatory motion should be centered around the zero level for further manipulation.
+The constant offset is eliminated simply by subtracting the overall mean from the signal.
+Moreover, the high pass DC blocker infinite impulse response (IIR) filter of 1st order can adjust to shifts of the average value over time (Equation~\ref{equ:iir-dc-blocker}).
+The transition band depends upon the choice of corner frequency $f_{3dB}$ (Fig.~\ref{fig:dc-blocker}).
+
+\myequations{DC blocker IIR filter of 1st order}
+\begin{ceqn}\begin{align} \label{equ:iir-dc-blocker}
+y_k = (1 - \frac{\omega}{2}) \cdot (x_k  -  x_{k - 1}) + (1 - \omega) \cdot y_{k - 1}; \quad \omega = 2\pi \cdot \frac{f_{3dB}}{f_s}
+\end{align}\end{ceqn}
+
+A steeper 3~dB attenuation band can be achieved by increasing the order of the filter.
+Then the cutoff frequency should be such that filter coefficients are fractions to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\textwidth]{assets/analysis/iir-1-dc-blocker-band.jpg}
+	\caption{Transfer function of 1st order DC blocker filters ~\cite{tittelbach-helmrich_digital_2021}}
+	\label{fig:dc-blocker}
+\end{figure}
+
+The finite impulse response (FIR) filter is not recommended for DC component removal because of the undesirable ripple effect with the small number of taps.
+Cascaded-integrator-comb (CIC) filters are proposed as an alternative instead~\cite{lyons_understanding_2011}.
+
+\subsection{Time synchronous averaging}
+Time synchronous averaging (TSA) diminishes the impact of vibration sources unrelated to the rotational frequency and its harmonics.
+TSA averages time-domain waveform over $N$ points and aligns it to a synchronization pulse with period $T$ (Equation~\ref{equ:tsa-average}).
+
+\myequations{Time synchronous averaging}
+\begin{ceqn}\begin{align}
+x_{TSA} = \frac{1}{N} \sum_{n = 0}^{N - 1}{x(t + nT)}
+\label{equ:tsa-average}
+\end{align}\end{ceqn}
+
+This technique has been successfully applied to the gearbox and bearing fault diagnosis~\cite{davies_handbook_2012,nandi_condition_2019}.
+
+\section{Feature extraction} \label{section:feature-extraction}
+After preprocessing, raw numerical vectors are merely low-level descriptors of the underlying physical phenomena.
+At first, these incomprehensible sequences of numbers are reduced to summary attributes called features in the process of feature extraction or feature discovery.
+Features can be hand-crafted (as is our case), learned implicitly within the model representation, or explicitly from an optimization problem solution.
+
+Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
+The advantages of the add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
+
+It is important to note that the design of features is not a standalone step in the machine learning pipeline, but it should be done iteratively to improve the target model.
+Signal features are computed in the time and frequency domain~\cite{brito_fault_2021}.
+
+\subsection{Time-domain features}
+The most widely found features in the literature are rudimentary statistical measures of the central moment: mean, variance, standard deviation, skewness, and kurtosis~(Tab.~\ref{tab:td-features}).
+Statistics can be calculated in any domain, but the mean value should not be used in detrended data.
+The vibration severity metrics out of technical standards are also highly regarded.
+The amplitude characteristics include root-mean-square and peak-to-peak distance~\cite{mostafavi_novel_2021}.
+The waveform shape is captured by zero-crossing rate and average amplitude change~\cite{moctar_time-domain_2023}.
+
+The other significant time domain attributes are derived as ratios of previous simpler ones.
+These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
+Many articles have been successful in fault detection of bearings out of transients in impulsive signals with kurtosis, crest, and clearance factor~\cite{brito_fault_2021}.
+It is also suggested that the shape factor can signify unbalance and misalignment faults~\cite{nandi_condition_2019}.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}            & \textbf{Equation}                                                                    \\ \hline
+\textit{Peak-to-peak}       & $ X_{ppv} = \max(x_i) - \min(x_i) $               
+\\ \hline
+\textit{Zero-crossing rate} & $X_{zc} = \frac{1}{N}\sum_{i = 1}^{N}{\mathrm{sgn}(x_i \cdot x_{i-1})} $
+\\ \hline
+\textit{Root mean square}   & $ X_{rms} = \sqrt{\frac{1}{N}\sum_{i = 1}^{N}{x_i^2}} $ 
+\\ \hline
+\textit{Skewness}           & $ X_{sv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^3}$      
+\\ \hline
+\textit{Kurtosis}           & $ X_{kv} = \frac{1}{N}\sum_{i = 1}^{N}{\left(\frac{x_i - \bar{x}}{\sigma}\right)^4}$                                           
+\\ \hline
+\textit{Shape factor}   & $ X_{sf} = \frac{X_{rms}}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}}$  
+\\ \hline
+\textit{Crest factor}   & $ X_{cf} = \frac{max(|x_i|)}{X_{rms}} $                           \\ \hline
+\textit{Impulse factor} & $ X_{if} = \frac{max(|x_i|)}{\frac{1}{N} \sum_{i=1}^{N}{|x_i|}} $                                                 
+\\ \hline       
+\textit{Clearance factor}  & $ X_{mf} = \frac{max(|x_i|)}{\left( \frac{1}{N} \sum_{i=1}^{N}{\sqrt{|x_i|}} \right)^2} $ 
+\\ \hline
+\textit{Average Amplitude Change (AAC)}        & $ X_{AAC} = \frac{1}{N}\sum_{i = 1}^{N - 1}{|x_{i + 1} - x_i|} $                             \\ \hline
+\end{tabular}
+\caption{Time-domain features}
+\label{tab:td-features}
+\end{table}
+
+\subsection{Frequency-domain features}
+The mechanical faults present themselves as oscillatory patterns which are combinations of frequencies with various amplitudes.
+The Fourier transform is one of the most prominent strategies in power spectral density estimation.
+Experts on vibrodiagnostics utilize it as a primary signal processing technique for data analysis as it is recommended in ISO 13373-2 standard~\cite{noauthor_iso_2016_2}.
+
+The inherent symmetries in the Fourier matrix made it possible to implement the Fast Fourier transform (FFT) algorithm with time complexity $O(n \log n)$.
+The drawback of the plain spectral analysis is the lack of resolution for events that occurred at distant time instants, and so their spectral components might adversely blend in together.
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{2}
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Feature}           & \textbf{Equation}                                                                                                  \\ \hline
+\textit{Spectral centroid} & $ X_{fc} = \frac{\sum_{i = 0}^{N - 1}{f_i \cdot a(f_i)}}{\sum_{i = 0}^{N - 1}{a(f_i)}}$                   \\ \hline 
+\textit{Energy}            & $ E(N) = \sum_{i = 1}^{N} a^2(t) $                                                                    \\ \hline \textit{Energy ratio}                & $E_r = E_i \;/\; \sum_{i = 1}^{N}{E_i} $                                                        \\ \hline
+\textit{Spectral roll-on} & $ E(f_c) = 0.05 \cdot E(f_s / 2) $ \\ \hline                    
+\textit{Spectral roll-off} & $ E(f_c) = 0.85 \cdot E(f_s / 2) $                                                   \\ \hline
+\textit{Spectral flux}     & $X_{\mathrm{flux}} = 1 - \mathrm{corr}(A_{t-1}, A_t)$ \\ \hline 
+\textit{Noisiness}                   & $X_{noise} = \mathrm{SNR}(X) = \mu \;/\; \sigma $                             \\ \hline
+\textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
+\textit{Spectral negentropy}      & $\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}} \cdot \ln\left(\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}\right)$                                                \\ \hline
+\end{tabular}
+\caption{Frequency-domain features}
+\label{tab:fd-features}
+\end{table}
+
+In the frequency domain, we can obtain the usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
+Additionally, spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal-to-noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
+
+In geometric terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
+Spectral roll-off gives a notion about the spectral distribution because it identifies the frequency $f_c$ below which 95\% of the signal energy is contained.
+Complementary, the roll-on frequency is chosen so that 5\% of the signal energy is below this value.
+According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra a value of one means the spectra are the most dissimilar.
+
+``Negentropy measures the inclination of a system to increase its level of organization''~\cite{avoci_spectral_2020}.
+The larger \emph{spectral negentropy} suggests more fault-induced impulses.
+$E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
+
+If a single principal frequency exists, it can be determined by maximum likelihood estimation.
+Such frequency would explain the signal spectrum the best~\cite{peeters_large_2004}.
+The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
+
+The essential peak-finding approaches are based either on magnitude or gradient.
+All found extrema are commonly filtered with the magnitude of prominences and the width at half prominence.
+In the magnitude-based method, the middle point $x_i$ is compared to two neighboring points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
+The gradient-based method evaluates the first derivative at the point which is equal to zero if the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
+
+A substantial improvement is a robust non-parametric peak identification named \emph{MMS} based on the sum of terms in an arithmetic progression based on maximum, minimum, and sum.
+MMS max-min finder in the elementary form processes points in the window of length 3, it advances one point and deems its middle point as a local extremum if it satisfies equalities below.
+Equation~\ref{equ:mms-maxima} is for the hill and Equation~\ref{equ:mms-minima} is for the valley.
+The filtration techniques are incorporated in the adaptations of the MMS algorithm: MMS-WBF, MMS-SG, MMS-LH~\cite{adikaram_non-parametric_2016}.
+
+\myequations{MMS algorithm: Local maxima identification equality}
+\begin{ceqn}\begin{align}
+\frac{a_{max} - a_{min}}{S_3 - a_{min} \cdot 3} = \frac{a_{mid} - a_{min}}{S_3 - a_{min} \cdot 3}
+\label{equ:mms-maxima}
+\end{align}\end{ceqn}
+
+\myequations{MMS algorithm: Local minima identification equality}
+\begin{ceqn}\begin{align}
+\frac{a_{max} - a_{min}}{a_{max} \cdot 3 - S_3} = \frac{a_{max} - a_{mid}}{a_{max} \cdot 3 - S_3}
+\label{equ:mms-minima}
+ \end{align}\end{ceqn}
+
+Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with a central frequency, uncertainty, and amplitude $C_i(v_i, \Delta v_i, A_i)$ by an exhaustive search algorithm.
+Harmonic family identification is a non-trivial problem because of spectrum estimation errors.
+The criterion is proposed to select harmonics at the minimal distance from the true fundamental frequency multiple~(Equation~\ref{equ:harmonic-search}).
+Two series with the same fundamental frequency are merged and thought of as a modulation series~\cite{gerber_identification_2013}.
+
+\myequations{Harmonic series search criterion}
+\begin{ceqn}\begin{align}
+v_i^{(r)} = \frac{v_j}{\min{|v_j - r \cdot v_i|}}
+\label{equ:harmonic-search}
+\end{align}\end{ceqn}
+
+\subsection{Bearing defect frequencies}
+%TODO n = number of balls, d - average of outer ring diameter and outer ring, f_s - rotation speed, beta - contact angle - ball bearings close to 0
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{assets/analysis/bearing-parts.jpg}
+    \caption{Bearing parts~\cite{lu_what_is_ball_bearing_2023}}
+    \label{fig:bearing-parts}
+\end{figure}
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}            & \textbf{Equation}                                                                   
+ \\ \hline
+\textit{Outer race fault frequency} & $ BPFO = f_s \cdot \frac{n}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right)$               
+\\ \hline
+\textit{Inner race fault frequency} & $ BPFI = f_s \cdot \frac{n}{2} \cdot \left(1 + \frac{d}{D}\cos \beta \right)$
+\\ \hline
+\textit{Cage rotation frequency}    & $ FTF = f_s \cdot \frac{1}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right) $      
+\\ \hline
+\textit{Ball defect frequencies} & $ BSF = f_s \cdot \frac{D}{d} \cdot \left(1 + \left(\frac{D}{d}\cos \beta\right)^2 \right) $
+\\ \hline
+\end{tabular}
+\caption{Bearing defect frequencies}
+\label{tab:bearing-defect-features}
+\end{table}
+
+\subsection{Time-frequency domain features}
+The \textbf{Short-time Fourier transform} (STFT) splits the time-domain signal into equal-length intervals.
+Individual chunks have a 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to Fourier transform periodicity assumption.
+Traditionally, the Hann window is commonly used instead of the rectangular window~\cite{ziaran_technicka_2013,noauthor_iso_2016_2}.
+
+In the time-frequency domain, the same features can be derived as in the frequency domain, but in addition, the attributes are time-localized in this way.
+The STFT has a considerable flaw for implementation in a self-adaptable system and that is fixed resolution.
+The optimal window size has to be set beforehand or chosen after performing multiple transformations on chunks out of the range of lengths.
+Welch's method averages multiple consecutive blocks to better estimate the spectrum.
+We have already researched the suitability of STFT for online detection of constant frequencies~\cite{hajek_iot_2022}.
+
+The alternative to isolating weak impacts with high time resolution is a \textbf{Teager-Kaiser energy operator} (TKEO) (Equation~ \ref{equ:tkeo-operator}).
+It is a tool for envelope analysis to demodulate characteristic AM-FM signals present during bearing faults.
+Energy operator output can be utilized as a standalone feature attribute.
+
+\myequations{Teager–Kaiser energy operator}
+\begin{ceqn}\begin{align}
+\psi[x(n)] = [x(n)]^2 - x(n - 1)x(n + 1)
+\label{equ:tkeo-operator}
+\end{align}\end{ceqn}
+
+Improved TKEO is necessary to prevent analysis from suffering from the noisy source.
+The key idea is to perform TKEO after signal decomposition into narrowband components with different center frequencies.
+The extracted modes are reconstructed with weights assigned based on their correlations to the original signal~\cite{shi_application_2022}.
+
+Time-frequency spectrum modification preserving localization of abrupt wideband spikes at time $t_0$ and simultaneously reducing energy smear over the larger region is a goal of \textbf{Transient-extracting transform} (TET).
+Post-processing of STFT window $G(t,\omega)$ involves multiplication of the spectrum with the Transient extracting operator (TEO).
+This operator is expressed in the form of a Dirac delta function $\delta(t)$ (Equation~\ref{equ:tet-transform}).
+
+\myequations{Transient-extracting transform}
+\begin{ceqn}\begin{align}
+\mathrm{Te}(t,\omega) = G(t,\omega) \cdot  \delta(t - t_0)
+\label{equ:tet-transform}
+\end{align}\end{ceqn}
+
+TET representation retains non-zero coefficients where the absolute value of the ratio between two STFTs, $G^{tg}[n, k]\;/\;G[n, k]$ is less than half the sampling interval $T$.
+These two transforms use distinct windows $g[n]$ and $n \cdot g[n]$.
+Decomposition of a signal with TET is proved to produce significantly larger kurtosis (around 38 in TET, 4 in other methods) and hence better discriminate the transient fault~\cite{yu_concentrated_2020}.
+
+\subsection{Wavelet domain features}
+The bands for lower frequencies should be longer in time than for higher frequencies.
+The \textbf{Wavelet transform} (WT) possesses such a multiscale discrimination property, effectively increasing resolution in time-frequency plain.
+Wavelet basis functions are constructed for that purpose (Equation~\ref{equ:mother-wavelet}).
+There are several wavelet families.
+For example, Haar, Daubechies, Coiflets, Symlets, Morlet, and Meyer~\cite{nandi_condition_2019}.
+
+\myequations{Mother wavelet function}
+\begin{ceqn}\begin{align}
+\psi_{s, \tau} = \frac{1}{\sqrt{s}}\psi\left(\frac{t - \tau}{s}\right)
+\label{equ:mother-wavelet}
+\end{align}\end{ceqn}
+
+\textbf{Continuous Wavelet transform} (CWT)~(Equation~\ref{equ:cwt-transform}) is done by scaling and translating the mother wavelet $\psi$ picked out of the appropriate family~\cite{nandi_condition_2019}.
+The scale factor is denoted with~$s$ and time position with~$\tau$.
+The choice of wavelet type is data-driven because distinct wavelet shapes have an impact on the response and ultimately contribute to filter length.
+The decision lies between recognition abilities for impulse-like signals or the inclusion of wider surrounding space.
+
+\myequations{Continuous Wavelet transform}
+\begin{ceqn}\begin{align}
+W_{x(t)}(s, \tau) = \frac{1}{\sqrt{s}}\int x(t) \cdot \psi^*\left(\frac{t - \tau}{s}\right)\;\mathrm{dt}
+\label{equ:cwt-transform}
+\end{align}\end{ceqn}
+
+The CWT is computationally intensive when a highly detailed scale resolution is required because each wavelet scale convolves with the entire signal.
+The fCWT algorithm allows 100 times higher spectral resolution than previous implementations at the same speed.
+It increases performance 122 times compared to Wavelib and 34 times in comparison with PyWavelets~\cite{arts_fast_2022}.
+
+The fast CWT algorithm reaches compelling improvement by applying Parseval's theorem to the wavelet transform formula that removes the dependence on the time offset parameter~\cite{arts_fast_2022}.
+The convolution takes place with the mother wavelet in the Fourier base.
+Then, the inverse FFT produces the coefficients for individual scales.
+
+\textbf{Synchrosqueezing Wavelet transform} (SST) is a modification of CWT attempting to sharpen the representation of frequency components by coefficient reassignments from around the central frequencies towards the middle of the bands.
+The justification for these reallocations is rooted in the signal approximation as amplitude-modulated oscillating modes with additive noise $\eta(t)$ (Equation~\ref{equ:sst-transform})~\cite{herrera_applications_2014}.
+
+\myequations{Representation of components for Synchrosqueezing Wavelet transform}
+\begin{ceqn}\begin{align}
+s(t) = \sum_{k=1}^{K} A_k(t)\cos(\theta_k(t)) + \eta(t)
+\label{equ:sst-transform}
+\end{align}\end{ceqn}
+
+The components are defined by their instantaneous amplitudes $A_k(t)$ and instantaneous phases $\theta_k(t)$.
+The energy spread to adjacent bins can be effectively squeezed only in regions with constant phase and large enough component separation.
+Despite the promising properties of this transform, white noise causes severe interference in the resulting time-frequency map.
+
+The spectrograms to illustrate the difference in the ability of the Fourier transform, the continuous Wavelet transform, and their modifications to pick up underlying patterns in bearing faults are shown in Fig.~\ref{fig:transforms}.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/stft-spectrogram-sample.png}
+        \caption{STFT \& Gaussian window}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/tet-spectrogram-sample.png}
+        \caption{TET}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/wt-spectrogram-sample.png}
+        \caption{CWT \& Morlet wavelet}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/sst-spectrogram-sample.png}
+        \caption{SST}
+    \end{subfigure}
+    \caption{Comparison of time-frequency transform spectrograms~\cite{yu_concentrated_2020}}
+    \label{fig:transforms}
+\end{figure}
+
+The dyadic filter bank is another signal decomposition technique that generates subbands at multiple granularity levels.
+The practical realization of the multiscale description is \textbf{Discrete Wavelet Transform} (DWT).
+The DWT behaves as a quadrature mirror filter and splits waveforms using a wavelet filter to detail coefficients (D1) and approximation coefficients (A1) (Fig.~\ref{fig:dwt-filter-bank})~\cite{nandi_condition_2019}.
+The low-pass filter $h(k)$ creates approximation coefficients further decomposed at the successive levels.
+Detail coefficients represent the result of the high-pass filter $g(k) = (-1)^k h(1 - k)$ after decimation by a factor of 2.
+
+The maximum depth of the decomposition tree is $\log_2{n}$ where $n$ is the number of input samples.
+Energy, energy ratio, and entropy are prevalent features that succinctly encode the wavelet coefficients.
+Otherwise, the additional extracted levels raise the total number of data dimensions.
+
+In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provide features with a combination of approximation (cA5) and detail coefficients (cD1, \dots, cD5).
+Washing machines belong to three categories: no fault, electric motor clamping screws problem, and a loose or broken counterweight.
+Extracted measures were sample mean and sample variances over autocorrelation functions of coefficients (AcD$n$) and smoothed coefficients cD1, cD2 by moving average filter~\cite{goumas_classification_2002}.
+
+\textbf{Wavelet Packet Decomposition} (WPD) applies filters to split detail coefficients identically as approximation ones (Fig.~\ref{fig:wpd-filter-bank}) thus increasing the resolution in the high-frequency bands and providing uniform spectrum partitioning.
+
+\myequations{Wavelet packet coefficient}
+\begin{ceqn}\begin{align}
+ w_{j,n,k} = \langle f, W_{j,k}^n\rangle = \langle f, 2^{j/2} W^n (2^jt-k) \rangle
+\label{equ:wavelet-packet-coefficient}
+\end{align}\end{ceqn}
+
+Each wavelet packet coefficient $w_{j,n,k}$ captures subband frequency content around time instant $2^j k$ (Equation~\ref{equ:wavelet-packet-coefficient})~\cite{yen_wavelet_2000}.
+This measure is an inner product of the source and scaled wavelet packet function.
+The aforementioned feature extraction established in DWT can be applied.
+For example calculation of the wavelet packet node energy.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/DWT.png}
+        \caption{Discrete wavelet transform}
+        \label{fig:dwt-filter-bank}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/WPD.png}
+        \caption{Wavelet packet decomposition}
+        \label{fig:wpd-filter-bank}
+    \end{subfigure}
+    \caption{Dyadic filter banks for discrete wavelet transform~\cite{nandi_condition_2019}}
+\end{figure}
+
+The wavelet packet energy ratio for weak feature extraction has been incorporated into the method of multiple frequency band demodulation (MFBD).
+The highest $n$ energy coefficients are selected out of 8 narrow frequency bands to subsequently affect the principal components.
+Demodulation principle for the frequency bandwidth prescribes $n$ to satisfy condition: $1\;/\;2^n > f_{\mathrm{modulation}}\;/\;f_s$.
+The first few eigenvectors that explain together more than 80\% of energy are retained to reconstruct the signal with a Fourier transform and retain the weak fault components~\cite{song_mfbd_2021}.
+
+Tool wear diagnosis based on acoustic emission (AE) signal considers \emph{wavelet packet energy} in bands $E_{8}$, $E_{10}$, $E_{12}$, \emph{energy ratios} $P_{8}$, $P_{13}$, and \emph{energy entropy} as having high correlation ($|r| > 0.8$) with the band saw flank face width.
+The acoustic signal is decomposed into three layers using Daubechies db3 wavelet.
+The bottom layer contains bands numbered 7 through 14, each with a bandwidth of 62.5 kHz, because of the 1 MHz sampling frequency.
+The feature vector constructed in the article includes other statistical metrics out of power spectral density that has reached a notable correlation with evolving wear.
+The statistics are \emph{skewness}, \emph{kurtosis}, \emph{shape factor}, and \emph{centroid frequency}~\cite{zhuo_research_2022}.
+
+Discrete wavelet transform and wavelet packets partition the spectrum into predefined frequency bands that do not always adequately capture individual elementary oscillations.
+Adaptive spectral segmentation is needed to extract separate intrinsic mode functions (IMF).
+
+\subsection{Empirical wavelet features}
+\textbf{Empirical Wavelet Transform} (EWT) constructs adaptive bandpass filters with Meyer wavelet.
+The inner product of the signal with the scaling function $\hat{\phi_n}$ obtains the approximation coefficients and the inner product with the wavelet function results in detail coefficients.
+
+The normalized frequency axis in range $\omega \in [0, \pi]$ is divided by split points $\omega_0, \dots, \omega_N$ where $\omega_n = f_n \cdot 2 \pi\;/\;f_s$ (Fig.~\ref{fig:ewt-spectrum-segmentation}).
+Each segment is bounded between $[\omega_{n-1}, \omega_n]$ with a transition phase of width $2\tau_n$ and polynomial transition function $\beta(x)$.
+A tight frame set of empirical wavelets is built by setting the transition phase proportional to the band boundary: $\tau_n = \lambda \omega_n$, and proportional constant must obey constrain: $\lambda = \min\left(\frac{\omega_{n+1} - \omega_n}{\omega_{n+1} + \omega_n}\right)$.
+The $N$ boundaries defining different portions of the Fourier spectrum are placed at the center between two consecutive local maxima~\cite{gilles_empirical_2013}.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.9\textwidth]{assets/analysis/EWT.png}
+    \caption{Empirical wavelet segmentation of Fourier spectrum~\cite{gilles_empirical_2013}}
+    \label{fig:ewt-spectrum-segmentation}
+\end{figure}
+
+The drawback of EWT is improper segmentation in noisy and non-stationary signals, producing too many uninformative partitions of the spectrum.
+The solutions we discuss fall into two groups that apply improvements before or after the wavelet transformation step.
+
+A combination of \textbf{Maximum Correlated Kurtosis Deconvolution} and improved EWT (MKCD-EWT) favors periodic impacts by dynamically constructing an optimal FIR filter that maximizes the correlation kurtosis of the signal.
+The envelope curve smooths the amplitude spectrum by linear interpolation (Fig.~\ref{fig:mkcd-ewt-segmentation}).
+The threshold accounting for desired SNR modifies the envelope when more than $n$ components are discovered ($A_h$ is maximal amplitude and $A_l$ is minimal amplitude): $\lambda = A_l + \frac{C}{\mathrm{SNR}}(A_h - A_l)$.
+\emph{Squared envelope spectrum} and \emph{Teager energy operator spectrum} are computed as fault features for the IMF with the highest kurtosis~\cite{li_fault_2019}.
+
+The segmentation boundary detection can also be accomplished on the spectral envelope consisting of \textbf{Piecewise Cubic Hermite Interpolating Polynomial} (PCHIP-EWT) instead of scanning the Fourier spectrum directly (Fig.~\ref{fig:pchip-ewt-segmentation}).
+Divisions of the upper cut-off frequency are kept if local power indicates a subband with useful information ($p_i(f) \geq \lambda$)  as in the case of an abrupt level change.
+Local power is the ratio of $n$th local envelope maximum and the difference between indexes of its adjacent local minima:  $p_i(f) = K_{max(i)(f)} \;/\;\left(f_{k_{min(i+1)}} - f_{k_{min(i)}}\right)$.
+The best $\lambda$ is set experimentally~\cite{zhuang_improved_2020}.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/MKCD-EWT.png}
+        \caption{MKCD-EWT~\cite{li_fault_2019}}
+        \label{fig:mkcd-ewt-segmentation}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/PCHIP-EWT.png}
+        \caption{PCHIP-EWT~\cite{zhuang_improved_2020}}
+        \label{fig:pchip-ewt-segmentation}
+    \end{subfigure}
+    \caption{Illustration of improved EWT spectral segmentations}
+\end{figure}
+
+The inspiration for filtering on an adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
+This procedure locates local maxima and minima in the time waveform that are interpolated with cubic splines to form signal envelopes.
+The average of the upper and lower envelope is repeatedly subtracted from the residuals recovering the higher order and lower frequency IMFs~\cite{wang_computational_2014}.
+
+The EMD is not recommended for practical applications because it suffers from mode mixing problems and lacks rigid theoretical foundations.
+Many improvements based on the mode sifting process, such as Local Mean Decomposition (LMD), Ensemble Empirical Mode Decomposition (EEMD), Concealed Component Decomposition (CCD)~\cite{tiwari_novel_2021}, and Empirical Wavelet Transform, have been devised as being capable of estimating more reasonable modes.
+
+Wavelet domain features and associated spectral segmentation appear to be a powerful tool in conserving data bandwidth.
+These variables turn out to be difficult to communicate and comprehend.
+Therefore, we will use more standardized metrics in further studies.
+
+\section{Feature transformations} \label{section:feature-selection}
+Numerical features from the feature extraction phase have non-normal distributions and span wide ranges.
+Broad differences among features skew the spread on a particular axis.
+Inevitably, it can degrade the discernment of fault diagnostics models that map input onto a smooth function as regression does~\cite{zheng_feature_2018}.
+The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.
+
+\subsection{Feature normalization}
+Vibrations are measured with an accelerometer in the form of 3D vectors where each axis has its own component.
+Models have to be resilient to any slight inclination or sensor orientation.
+To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidian norm is computed~\cite{kamminga_robust_2018}.
+
+\myequations{Feature euclidian norm}
+\begin{ceqn}\begin{align}
+\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
+\end{align}\end{ceqn}
+
+Feature normalization most often takes two forms.
+\textbf{Min-max scaling} changes the original range of values into an interval $[0, 1]$ (Equation~\ref{equ:min-max-scaler}).
+\textbf{Standardization} (Equation~\ref{equ:standardization-scaler}) constrains the mean of the variable to 0 with a variance of 1~\cite{zheng_feature_2018}.
+
+\myequations{Min-max feature scaling}
+\begin{ceqn}\begin{align}
+\widetilde{x} = \frac{x - \min(x)}{\max(x) - \min(x)}
+\label{equ:min-max-scaler}
+\end{align}\end{ceqn}
+
+\myequations{Feature standardization}
+\begin{ceqn}\begin{align}
+\widetilde{x} = \frac{x - \bar{x}}{\sigma_x}
+\label{equ:standardization-scaler}
+\end{align}\end{ceqn}
+
+\subsection{Principal components analysis}
+Highly correlated features generated from a relatively small original column space are redundant as they do not provide any additional information for diagnostics.
+\textbf{Principal Component Analysis} (PCA) solves this problem by projecting potentially linearly dependent features into a new feature space where the incoming information is preserved in a smaller number of features~\cite{zheng_feature_2018}.
+The threshold of how many principal components are picked depends on the amount of explained variance and desired quantity of data reduction.
+
+\myequations{Singular Value Decomposition}
+\begin{ceqn}\begin{align}
+\mathbf{C} = \mathbf{U \Sigma V^T}
+\label{equ:svd}
+\end{align}\end{ceqn}
+
+PCA consists of taking the Singular Value Decomposition (SVD) (Equation~\ref{equ:svd}) of the mean-centered input matrix.
+The disadvantage of this method is the loss of explainability in transformed space though it generally outperforms the model working with hand-crafted features~\cite{brito_fault_2021}.
+The signal samples can be processed directly by PCA without going through an intermediate step of calculating statistical measures.
+
+\section{Feature selection}
+Features do not contribute to the predictive power of the model with an even share.
+A certain subset can achieve better results than others.
+Choosing the optimal feature subset is the NP-hard combinatorial problem.
+
+\subsection{Filtering methods}
+The features can be chosen intrinsically as a part of a model by \emph{embedded methods} or by machine learning search algorithm at a serious computational expense in \emph{wrapper methods}.
+However, we will focus on \emph{filtering methods} which rank the predictors in order of their importance for the problem at hand and separate the best performing group~\cite{johnson_feature_2019}.
+The most common strategy is \emph{K-Best Selection}.
+
+The general steps in selecting the appropriate predictors are as follows~\cite{nandi_condition_2019}:
+
+\begin{enumerate}
+    \itemsep0pt
+    \item \textbf{Subset generation} - sets of features are generated in different search directions and with various strategies.
+Attributes are either appended to an empty set or pruned away from a universal set, sequentially or randomly.
+
+    \item \textbf{Subset evaluation} - comparison of subset quality is assessed with relevance measures, some of which are discussed below.
+
+    \item \textbf{Stopping criteria} - search is exhausted when the specified number of features has been found, subset metrics cannot be improved further, or satisfactory model performance is achieved.
+Subset generation and evaluation can be performed multiple times until the stopping criteria are met.
+
+    \item \textbf{Validation} - the resulting subset is tested for the specific model on synthetic and real-world datasets against well-known results. 
+\end{enumerate}
+
+Filter-based feature selection is preprocessing step independent of model choice with small computational requirements.
+Measures of information, correlation, similarity, and interdependence output the relevancy rating.
+Predictors are rated individually or in interacting congregations.
+
+\subsection{Feature importance ranking}
+Most of the scores are based on supervised learning, so they expect true class labels to apportion the measurements respectively.
+After the scores are assigned to the first $n$ features, those below a threshold are removed.
+
+The frequently used scores upon which the feature relevance is ordered are~\cite{nandi_condition_2019}:
+
+\begin{itemize}
+\item \textbf{Variance threshold} - removes low-variance features below the set threshold.
+
+\item \textbf{Correlation coefficient} - expresses the linear relationship between two variables.
+The codependent variables are of three sorts: quantitative, ordinal, and nominal.
+The choice of coefficient calculation is determined by the type of variables under consideration shown in Table \ref{tab:corr-coef}.
+
+\emph{Pearson correlation} coeficient expresses similarity between two quantitative features: $f_i$ and $f_j$.
+In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}.
+Mathematically, this is equivalent to the Pearson coefficient.
+Rank correspondence is quantified with either Spearman rho or Kendall's Tau~\cite{calkins_more_2005}.
+
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.5}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|c|l|l|l|}
+\hline
+\textbf{Variable Y\textbackslash{}X} & \multicolumn{1}{c|}{\textbf{Quantitiative X}} & \multicolumn{1}{c|}{\textbf{Ordinal X}} & \multicolumn{1}{c|}{\textbf{Nominal X}} \\ \hline
+\textbf{Quantitative Y}              & Pearson $r$                                   & Biserial $r_b$                          & Point Biserial $r_{pb}$                 \\ \hline
+\textbf{Ordinal Y}                   & Biserial $r_b$                                & Spearman $\rho$    & Rank Biserial $r_{rb}$                  \\ \hline
+\textbf{Nominal Y}                   & Point Biserial $r_{pb}$                       & Rank Bisereal $r_{rb}$                  & Phi, L, C, Lambda                       \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Correlation coeficients}
+\label{tab:corr-coef}
+\end{table}
+
+Attributes are ranked in descending order according to the absolute value of their correlation coefficient. We seek the highest correlation to the class label.
+
+\myequations{Pearson correlation coefficient}
+\begin{ceqn}\begin{align}
+r(i) = \frac{\mathrm{cov}(f, c)}{\sqrt{\mathrm{var}(f) \cdot \mathrm{var}(c)}}
+\end{align}\end{ceqn}
+
+\item \textbf{Fisher score} - measures the difference between the means of the classes.
+It is interchangeable with ANOVA F-value, but it is evaluated for each feature $X^j$ separately.
+Ideally, the features in the subset have large distances between samples of various classes in $C$ and distances within a class are the smallest possible.
+In the formula (\ref{equ:fisher-score}), $n_j$ is the sample size of $j$th feature, $\mu^j$ is its sample mean, and $\mu$ is the overall mean.
+
+\myequations{Fisher score}
+\begin{ceqn}\begin{align}
+\mathrm{FS}(X^j) = \frac{\sum_{i=1}^{C} n_i(\mu_i^j - \mu^i)^2}{\sum_{i=1}^{C} (n_i - 1) \cdot (\sigma_i^j)^2}
+\label{equ:fisher-score}
+\end{align}\end{ceqn}
+
+\item \textbf{Mutal information} - quantifies the dependence between features, or between features and class labels.
+It is almost identical to Information Gain.
+The probability distribution of proximity of variables derives from the relative entropy known as the Kullback-Leibler distance.
+Mutual information presumes variables are discrete.
+In the case of quantitative variables, mutual information is estimated by binning or nearest neighbors methods~\cite{ross_mutual_2014}.
+
+Probabilities $P(x)$, $P(y)$, $P(x, y)$ are estimated in the contingency table from event occurrence count to all sample population $|x|\;/\;N$.
+Joint probability $P(x, y)$ represents samples of feature $x$ simultaneously in class $y$.
+
+\myequations{Mutal information}
+\begin{ceqn}\begin{align}
+\mathrm{MI}(X, Y) = \sum_{y \in Y} \sum_{x \in X} P(x, y) \cdot \log\left(\frac{P(x, y)}{P(x)P(y)}\right)
+\end{align}\end{ceqn}
+\end{itemize}
+
+Multiple subsets of predictors produced by each evaluation metric can train several variants of a classification model.
+Sets of attributes can be combined into an ensemble by \emph{electoral system}.
+One such example is \textbf{majority voting} which chooses the best feature out of the group.
+\textbf{Rank product} unifies several feature orderings by computing the geometric mean of feature rank in every experiment realization~\cite{breitling_rank_2004}.
+
+\section{Diagnostics techniques} \label{section:diagnostics-techniques}
+Fault identification in the rotating machinery is a one-class or multi-class classification problem acting in a semi-supervised manner because labels for degraded conditions are scarce in practice.
+The automation goals in monitoring can be broadly categorized as anomaly detection and recognizing the momentary fault type.
+
+The guiding principles for algorithm selection are simplicity in terms of their straightforward visual explanation for the production managers, and the ability to progressively improve the model on the streaming data to address peculiarities in individual machine constructions.
+
+\subsection{Novelty detection}
+Anomaly, novelty, or outlier detection determines whether a health status deviates considerably from the baseline profile.
+The expert can then step in and diagnose the machine after the notice.
+Anomaly is a rare observation different from the others, raising suspicion that it was created by unrelated behavior~\cite{aggarwal_outlier_2016}.
+The observations get assigned anomaly scores, and those over the threshold are novelties.
+
+The measurements coming in the steaming fashion have to be processed in a single pass.
+The detection model must deal with the minimal admissible assumptions about the nature of the input events.
+The outliers are derived based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
+\bigbreak
+
+\textbf{DenStream} is a density-based algorithm adapted from DBSCAN to cluster streaming data of arbitrarily shaped groups.
+Samples it includes in the first step into coherent clusters are core data points in each other's neighborhoods.
+Core points have at least \emph{MinPts} ($\mu$) points in their neighborhood of radius \emph{Eps} ($\varepsilon$) units.
+Then non-core points in the proximity area of the core point are attached to the cluster containing it~\cite{aggarwal_data_2014}.
+
+Quality of clustering results is evaluated by \emph{Silhouette score} in the range [-1; 1].
+It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters.
+The low score indicates a too small or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/analysis/DenStream.png}
+    \caption{DenStream~\cite{amini_density_2012}}
+    \label{fig:denstream}
+\end{figure}
+
+In the online maintenance phase, DenStream summarizes the nearby observations into core \emph{micro-clusters} that can be potential micro-clusters or outlier \emph{micro-clusters} (Fig.~\ref{fig:denstream})~\cite{ghesmoune_state---art_2016}.
+The (outlier) \emph{o-micro-clusters} can grow into (potential) \emph{p-micro-clusters} when they encompass $\beta \mu$ points.
+The outliers are discounted after some time in accordance to the decay function: $f(t) = 2^{-\lambda t}$ or below the lower weight limit $\xi$.
+The on-demand offline stage runs DBSCAN over the approximate representation in micro-clusters to deliver final apportionment~\cite{cao_density-based_2006}.
+\bigbreak
+
+\textbf{Half-Space Tree} (HS-Tree) stands upon the concept of Isolation forest.
+It assumes that random splitting of each axis in the feature space will isolate outliers to their separate divisions sooner than non-deviant observations~\cite{gervasi_anomaly_2020, torres_automatic_2022}.
+This ensemble of trees is better suited for batch setting.
+HS-Tree stands out in adapting to changing streams because it is trained solely on normal data, requires constant memory, and is faster than density-based methods~\cite{tan_fast_2011}.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/analysis/HS-Tree.png}
+    \caption{Half-space tree~\cite{tan_fast_2011}}
+\end{figure}
+
+A full binary tree is built before the novelty detection begins by splitting tree nodes along the divisions in the randomly chosen perpendicular planes.
+The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and links to both child nodes~\cite{tan_fast_2011}.
+
+\subsection{Classification}
+Accurate multi-class classification of machine fault causes according to the characteristics of known ones is a much more difficult task than novelty detection.
+Fault combinations have to be recorded and transformed into feature space.
+Interactions among fault root causes have to be considered.
+We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}.
+So far, solutions seem not production-ready and hard to explain.
+Therefore, we opt to use a simpler model.
+
+Performance of classification is estimated by several metrics on the validation set obtained using hold-out or cross-validation techniques.
+Frequently used quantities for classifier model evaluation include accuracy, precision, recall, f1 score, area under the ROC curve, and counts of hits and misses in a confusion matrix.
+\bigbreak
+
+\textbf{K-nearest neighbors} (k-NN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
+It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations.
+The major drawback of k-NN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}.
+The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
+The k-NN algorithm requires features to be normalized to assign the same importance to each predictor.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/KNN.png}
+        \caption{k-NN with k = 5}
+        \label{fig:KNN}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/analysis/M-tree.png}
+        \caption{M-tree data structure}
+        \label{fig:m-tree}
+    \end{subfigure}
+    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
+\end{figure}
+
+The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
+(Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
+The optimal $k$ parameter is set by supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
+The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.
+
+\begin{table}[ht]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
+Manhatann distance	 & $ |x_i - y_i| $													   \\ \hline
+Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
+Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline
+\end{tabular}
+\caption{Distance metrics for k-NN}
+\label{tab:KNN-distance}
+\end{table}
+
+The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics.
+On the CWRU bearing dataset, the k-NN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - k-NN 91.2\%, SVM 88.8\%, and frequency domain features - k-NN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
+
+Comparison of k-NN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
+Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with k-NN classifiers and Mahalanobis metric.
+The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
+Despite k-NN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.
+
+\subsection{Incremental learning}
+Online or incremental machine learning operates on the streaming data, updating the model parameters with each new incoming event or in mini-batches.
+This approach finds its use in big data processing when the whole dataset is not available in advance or cannot be processed at once because of memory limitations.
+
+There are some additional obstacles to watch out for with incremental learning in comparison to batch learning~\cite{gepperth_incremental_2016}:
+
+\begin{enumerate}
+    \itemsep0pt
+
+    \item \textbf{Concept drift} is defined as the change in data distribution function over time.
+The two types of concept drift are virtual and real.
+In virtual drift, changes occur only in the input distribution.
+Real drift means that the alteration comes to underlying functionality.
+Concept shift occurs with an abrupt change.
+
+    \item \textbf{Stability-plasticity tradeoff} concerns the speed with which the model adapts to new information.
+The model can react quickly, making it less stable, or retain patterns for longer but become irresponsive to sudden shifts.
+
+    \item \textbf{Model complexity} should be adjustable to ensure flexibility in unforeseen circumstances.
+Simpler models in the ensemble can also further increase prediction robustness.
+Resource limitation bound complexity from above.
+
+    \item \textbf{Memory model} can store aggregates from seen observations and its typical examples or finite window of latest samples with forgetting factor.
+\end{enumerate}
+
+\textbf{Model benchmarking} in incremental learning is achieved by comparing models to their batch counterparts or using progressive validation~\cite{blum_beating_1999, halford_correct_2020}.
+It has been shown that incremental clustering algorithms have overall worse accuracy than batch versions~\cite{gepperth_incremental_2016}.
+In the validation process, precautions should be taken to prevent data leakage from future events into the past.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=\textwidth]{assets/analysis/incremental-learning.png}
+    \caption{Incremental learning deployment architecture~\cite{gaia_online_2022}}
+    \label{fig:online-learn-arch}
+\end{figure}
+
+Deployment of an online machine learning model alongside supporting services is different from in established MLOps processes.
+Model store and Inference service components are supplemented with Labelling and Learning service~\cite{gaia_online_2022}.
+Their goal is to tune model parameters gradually as additional ground truth labels are provided.
+Labels can be provided later in a scheme called ``log and wait'', but data features are stored until such time.
+
+\section{Evaluation datasets} \label{section:evaluation-datasets}
+The experimentally designed features' relevancy is first proven in comparison to comprehensive benchmark datasets.
+There are a few standardized datasets used in the related work, e.g.
+\cite{ribeiro_rotating_2017}.
+
+\emph{MaFaulDa} dataset combines vibration and acoustic measurements of the shaft in deviating positions and bearing abnormalities.
+\emph{CWRU dataset} focuses solely on faults in ball bearings.
+Another less known dataset concerns shaft unbalance, but compared to the previous two, it demonstrates behavior during speed up.
+
+\subsection{Machinery Fault Database}
+MaFaulDa~\cite{mafaulda_dataset} is a collection of 1951 multivariate time series for 4 different operational conditions on rotor kit Alignment Balance Vibration Trainer (ABVT)~(Fig.~\ref{fig:mafaulda-simulator}).
+Each series has 5~seconds in duration and is captured at 50 kHz.
+Vibration signals were obtained with piezoelectric accelerometers with a linear response up to 10~kHz, amplitude range to $\pm$490 $\mathrm{m/s}^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$.
+
+\begin{figure}[h]
+\centering
+\begin{subfigure}[b]{0.48\textwidth}
+	\includegraphics[width=\textwidth]{assets/analysis/mafaulda-simulator.png}
+	\caption{Schematic diagram \cite{pestana-viana_influence_2016}}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.48\textwidth}
+	\includegraphics[width=\textwidth]{assets/design/sensor/mafaulda-simulator.jpg}
+	\caption{Mechanical construction \cite{noauthor_spectraquest_nodate}}
+\end{subfigure}
+\caption{Machinery fault simulator for MaFaulDa}
+\label{fig:mafaulda-simulator}
+\end{figure}
+
+Observations were conducted on three cardinal axes simultaneously with 2 sets of accelerometers, each one associated with one bearing (inner and outer bearings)~(Fig.~\ref{fig:mafaulda-simulator}).
+Additionally, a magnetic speedometer produced a pulse on shaft turn.
+The cardioid condenser microphone recorded sound emissions at a frequency range 20~Hz - 20~kHz.
+Sensors were fed into a four-channel dynamic signal acquisition module.
+
+Columns in the dataset are organized as depicted in table~\ref{tab:mafaulda-columns}.
+Machine rotational speeds were kept constant during a particular measurement, but covered a range from 737 to 3686~rpm with steps of approximately 60 rpm (equiv.
+10~Hz - 60~Hz)~\cite{pestana-viana_influence_2016}.
+The maximal rotational frequency achieved with a high unbalance load is 3300 rpm.
+
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\centering
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                                                                                                                                               \\ \hline
+1.               & \begin{tabular}[c]{@{}l@{}}Pulse with modulation of speedometer signal \\ to estimate rotation frequency  (in TTL levels)\end{tabular}                              \\ \hline
+2., 3., 4.       & \begin{tabular}[c]{@{}l@{}}Underhang bearing accelerometer \\ (inner - between the rotor and motor)\\ - axial, radial, tangential direction\end{tabular}           \\ \hline
+5., 6., 7.       & \begin{tabular}[c]{@{}l@{}}Overhang bearing accelerometer \\ (outer - outside most position after the rotor)\\ - axial, radial, tangential direction\end{tabular} \\ \hline
+8.               & Microphone                                                                                                                                                         \\ \hline
+\end{tabular}
+\caption{MaFaulDa description of columns}
+\label{tab:mafaulda-columns}
+\end{table}
+
+This database contains normal operating conditions, faults out of unbalance, horizontal and vertical shaft misalignment, and three types of faulty bearings in inner and outer positions: outer track, inner track, rolling elements~\cite{pestana-viana_influence_2016}.
+
+\begin{itemize}
+\itemsep0pt
+
+\item \textbf{Normal} conditions are baseline without the adverse effect of fault at 49 different rotation speeds.
+
+\item \textbf{Unbalance} shaft time series uses 8 unbalancing weights from 6 to 35 grams and varying 45 - 49 speeds for each weight, adding to 333 mass unbalance loads.
+
+\item \textbf{Vertical misalignment} set comprises 50 signals each (or 51 in one instance) obtained under displacements: 0.51, 0.63, 1.40, 1.90, 1.27, 1.78 mm.
+
+\item \textbf{Horizontal misalignment} signals were recorded under displacements: 0.50, 1.00, 1.50, 2.00 mm, each with 49 different speeds (or 50 in one instance)~\cite{pestana-viana_influence_2016}.
+
+\item \textbf{Bearing faults} are unnoticeable without unbalance.
+Therefore, weights of 6, 20, and 35 grams were attached to induce a detectable effect.
+Each mass was combined with cage, outer race, and ball faults at multiple rotation speeds, usually at 50 different speeds.
+\end{itemize}
+
+\subsection{CWRU bearings dataset}
+In Case Western Reserve University (CWRU) bearing dataset~\cite{cwru_dataset} recordings were made of a fan end and drive end bearings under motor loads of 0, 1, 2, and 3~Horsepower (equivalently 0, 0.75, 1.49, 2.24~kW).
+Shaft speed was unaltered in all experiments, but it fluctuated between 1720 and 1797~rpm (approx.
+29~Hz).
+
+\begin{figure}[h]
+\begin{subfigure}[b]{0.48\textwidth}
+	\includegraphics[width=\textwidth]{assets/analysis/cwru-test-stand-2.png}
+	\caption{Schematic diagram \cite{song_bearing_2022}}
+\end{subfigure}
+\hfill
+\begin{subfigure}[b]{0.48\textwidth}
+	\includegraphics[width=\textwidth]{assets/analysis/cwru-test-stand.png}
+	\caption{Mechanical construction \cite{yuhong_new_2021}}
+\end{subfigure}
+\caption{CWRU machine apparatus}
+\label{fig:cwru-simulator}
+\end{figure}
+
+Single point defects were created with diameters of 0.007, 0.014, 0.021, 0.028, and 0.040 inches (equivalently 0.18, 0.36, 0.72, 1.02 mm).
+Fault locations on bearings are in the inner raceway, in the outer raceway directly and orthogonally relative to the load zone, and on rolling ball elements~(Fig.~\ref{fig:cwru-simulator})~\cite{jamil_feature-based_2021}.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                 \\ \hline
+1. DE        & Drive end accelerometer samples 		\\ \hline
+2. FE        & Fan end accelerometer samples   			\\ \hline
+3. BA        & Base accelerometer samples (optional)   \\ \hline
+4. RPM     & Rotation speed of the motor in rpm        \\ \hline
+\end{tabular}
+\caption{CWRU dataset description of columns}
+\label{tab:cwru-columns}
+\end{table}
+
+The sampling frequency during baseline set, drive end, and fan end bearing capture is 12 kHz.
+For drive end bearings, samples were taken at 48 kHz.
+The duration of the time series varies from 5 to 40 seconds.
+Drive end and fan end bearing signals are measured in each experiment.
+Accelerometer was sometimes mounted on the supporting baseplate.
+
+\subsection{Unbalance of the rotating shaft}
+Unbalance Detection of a Rotating Shaft~\cite{unbalance_shaft} is a Kaggle dataset that simulates 4 different unbalance strengths. 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.7\textwidth]{assets/analysis/rotating-shaft.jpg}
+\caption{Motor driving shaft in unbalance measurement \cite{mey_machine_2020}}
+\label{fig:rotating-shaft}
+\end{figure}
+
+The setup is shown in Fig.~\ref{fig:rotating-shaft}.
+A mass of 3.28 grams (or 6.61 grams during the severe unbalance test) is attached to the unbalance holder in 5 sets (numbered 0 - 4) on the radii 0, 14, 18.5, 23, 23 mm.
+The rotation speed of the motor is perpetually rising between 630 and 2330 rpm in development datasets (marked with suffix D) and speeds from 1060 to 1900 rpm in the evaluation datasets (suffix E).
+The vibrations were recorded at a sampling rate of 4~kHz~\cite{mey_machine_2020}.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{1.2}
+\begin{tabular}{|l|l|}
+\hline
+\textbf{Columns} & \textbf{Description}                      \\ \hline
+1. V\_in         & Input voltage to the motor controller (V) \\ \hline
+2. Measured\_RPM & Rotation speed of the motor (rpm)  \\ \hline
+3. Vibration\_1  & 1. Vibration sensor (samples)             \\ \hline
+4. Vibration\_2  & 2. Vibration sensor (samples)             \\ \hline
+5. Vibration\_3  & 3. Vibration sensor (samples)             \\ \hline
+\end{tabular}
+\caption{``Unbalance on the rotating shaft'' dataset description of columns}
+\end{table}
+
+The accelerometers used are piezoelectric and have a frequency range of up to 10 kHz, dynamic range of $\pm$490 $m/s^2$, and resolution step of 10.2~mV per $\mathrm{m/s}^2$.
+These sensor parameters are the same as in the case of MaFaulDa.
+In total, three different uniaxial accelerometers are mounted on the motor housing.

### 2024-04-28 thesis/chapters/03-design.tex
Turn outline into section headings

--- 2024-03-11 thesis/chapters/03-design.tex
@@
 \chapter{Design} \label{chapter:design}
-The design phase sets out to elaborate on the scenarios for experiments with IoT device.
-In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
-Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
 
 \section{Research questions}
-This thesis aims to provide answers to four research questions.
-The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
-The \textbf{research questions} are:
-\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
-    \itemsep0pt
-	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
-	\item What is the reduction in transmission goodput when chosen signal features are used?
-	\item What accuracy of prediction models can be achieved with various feature subsets?
-	\item How can machinery faults be continuously identified and predicted based upon collected events?
-\end{enumerate}
+% Questions
 
-\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
-\begin{todolist}
-    \itemsep0pt
-    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
-    \item Establish a list of conditions that should be later investigated in the experimental setting.
-    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
-    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
-    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
-    \item Combine feature selection with an online machine learning model.
-    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
-    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
-\end{todolist}
+% Goals
 
-However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain.
-The reason is that we did not find a way to represent extracted features more succinctly as a single number.
-We also did not discover a strategy for choosing only the relevant frequency bins.
-The assembled description is retained to lead further research on that topic.
+% Risks in the table (probability vs. impact)
+% Project risk management
 
-The goals are impacted by certain \textbf{risks} that are assessed and tracked:
+\section{Machine learning pipeline}
+% UML pipeline (fig.) and parameters
 
-\begin{enumerate}[label=R-\arabic*., font=\bfseries]
-\itemsep0pt
-\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
-\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
-\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
-\item Fault modes can not be reliably differentiated and labeled in the dataset.
-\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
-\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
-\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
-\end{enumerate}
+% Experimental scenarios - domain, dim, bearings, severity
 
-\section{Dataset exploration}
-In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset.
-It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.
+% Experiments and metrics:
+% - All features
+% - Feature combinations
+% - Feature selection methods
+% - Incremental learning
+% - Clustering
 
-One representative recording is first selected in each available fault category.
-The sample is visualized and statistically described in both temporal and spectral domains.
-A whole step-by-step procedure is outlined in the activity diagram (Fig.~\ref{fig:design:mafaulda-preprocessing}).
+\section{Exploratory data analysis of MaFaulDa}
+% Fault counts
+% Correlation to RPM
+% Features Range
+% Time domain waveforms of different faults
+% Bearing defect frequencies
+% PCA loading plots
 
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=\textwidth]{assets/design/activity-data-exploration.png}
-	\caption{Activity diagram of MaFaulDa dataset preprocessing}
-	\label{fig:design:mafaulda-preprocessing}
-\end{figure}
+\section{Accelerometer data logger}
+% Block diagram of device
 
-MaFaulda contains 1951 records labeled with inducted faults of increasing severity.
-The defects were set up on the machine simulator as is mentioned in the part about datasets.
-Time series of the triaxial piezoelectric accelerometers in separate files have a sampling frequency of 50 kHz.
+% HW parameters and mention temporary device
 
-These vibration sensors are placed in two positions.
-The first placement is around the inner underhang bearing named \emph{A} which is closer to the motor.
-The second location is around the outer overhang bearing denoted as \emph{B} position.
+% Task communication sequence diagram
 
-\subsection{Fault annotations}
-The MaFaulDa has annotations altogether for 10 classes of faults, of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
-Some categories are redundant or irrelevant for a given sensor position.
+% Firmware
 
-Therefore, rotor shaft misalignement in vertical and horizontal directions are merged into one joint group.
-Depending on the chosen bearing position, only records having relevant labels are considered.
+\section{Industrial equipment}
+% Description of machines
 
-This means that fault classification solely concerns bearing in direct contact and shaft mechanically passing through it.
-The bearings affect each other, but the effect on the opposite side should appear via a common interconnection shaft.
+\section{Data collection methodology}
+% UML of experiment
 
-In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
-In the step of choosing the accelerometer location, records pointing to the other bearing as a source of the malfunction are discarded.
-Then the next action renames the labels to be better recognizable and unite the same phenomena.
-
-Groups of identified machine defects are additionally characterized by altered masses attached or motor shaft displacement shifts.
-The set amount is sorted in ascending order, separating \textbf{multiple event severities}.
-However, the count of severity levels is not identical in every group.
-Levels are hence scaled into the range between zero and one using a min-max scaler.
-Scaling is applied to classes separately.
-
-The strength of the recorded response to the underlying defect is also dependent on the shaft \textbf{rotational speed}.
-Speed in rpm units is calculated from pulsed speedometer output.
-It is the average distance between two successive rising edges:
-\begin{ceqn}\begin{align}
-\mathrm{rpm} = 60 \;/\; \overline{\Delta t}
-\end{align}\end{ceqn}
-
-\textbf{One specimen waveform} is picked from each fault class to illustrate their superficial differences.
-Recordings are filtered to get the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz) to see the patterns most pronounced.
-The baseline class sample is chosen according to fixed rotor speed.
-
-\subsection{Signal filters}
-The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
-Immediately follows a digital IIR Butterworth \textbf{low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
-
-Before the low pass filter usage, the peak at 20 kHz with a sideband was present as an unwanted artifact.
-It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
-At the same time, such a frequency is outside the range of any feasible MEMS accelerometer.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.44\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
-        \caption{Temporal domain waveforms}
-        \label{fig:design:fault-temporal-waveform}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
-        \caption{Spectra in radial direction}
-        \label{fig:design:fault-spectral-waveform}
-    \end{subfigure} 
-    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
-\end{figure}
-
-Temporal domain waveforms of the 300 ms signal slice are shown in the graphs in Figure \ref{fig:design:fault-temporal-waveform}.
-Subplots for radial, tangential, and axial directions are laid out in columns from left to right.
-Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
-
-The frequency spectrum in Figure \ref{fig:design:fault-spectral-waveform} is obtained by FFT and Hann window of length $2^{14}$.
-The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz.
-The graph has been cropped in both axes to make the most important peaks visible.
-
-\subsection{Statistical tests}
-The statistical tests and visual checks are conducted to assess \textbf{normality and stationary} of time series.
-Half a second of amplitude samples are used from every sensor channel.
-These 25 thousand observations are downsampled tenfold to $2500$.
-
-\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from a normal distribution under most circumstances.
-The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms.
-\textbf{Quantile–quantile plots} confirm non-normal distribution because of the striking samples tilt to the diagonal line.
-
-\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root (${p < 0.001}$).
-The same is confirmed with the \textbf{autocorrelation} function shape.
-It denotes that the stochastic process is stationary as the oscillation is bounded.
-
-\section{Feature relevance}
-Attributes described in section \ref{section:feature-extraction} are independently summarized from each sensor position and direction.
-Then similarity score of features is ascertained in relation to a predicted variable.
-The subset of the strongest predictors is chosen based on the order of their perceived importance.
-
-\subsection{Feature extraction}
-Each file in the MaFaulDa contains six accelerometer channels.
-In the feature extraction process, the sequence of samples is split into five parts or 1-second intervals.
-The portions are passed through the same DC removal and low pass filters as previously.
-The rotational speed is derived from speedometer pulses within the chunk.
-
-Signal chunks are converted afterward into \textbf{10 temporal and 11 spectral features}.
-Welch's method for spectrum density estimation averaging over $2^{14}$ long FFT segments after Hann windowing is the source for spectral features.
-The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}.
-
-The Euclidean norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure~\ref{fig:design:feature-range}.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
-        \caption{Temporal features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
-        \caption{Spectral features}
-    \end{subfigure}
-    \caption{Feature value ranges in inner bearing position (A)}
-    \label{fig:design:feature-range}
-\end{figure}
-
-Fault labels and their severities come from the directory structure within the dataset.
-The binary target variable indicating whether to initiate a warning is called an anomaly.
-Anomalies are labeled according to relative fault severity level.
-We decided to investigate two fault severities having levels above 0.6 and 0.9.
-The quantity of observation by fault and anomaly severity is shown in Table \ref{tab:observation-counts}.
-The dataset is substantially unbalanced.
-
-\begin{table}[ht]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{tabular}{rrrrrllll}
-\cline{1-3}
-\multicolumn{1}{|l|}{\textbf{Fault}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{normal}}                 & \multicolumn{1}{r|}{49 (3\%)}                   & \multicolumn{1}{r|}{49 (4\%)}                    \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{misalignment}}           & \multicolumn{1}{r|}{498 (35\%)}                 & \multicolumn{1}{r|}{498 (36\%)}                  \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{imbalance}}              & \multicolumn{1}{r|}{333 (23\%)}                 & \multicolumn{1}{r|}{333 (24\%)}                  \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{cage fault}}             & \multicolumn{1}{r|}{188 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{ball fault}}             & \multicolumn{1}{r|}{186 (13\%)}                 & \multicolumn{1}{r|}{137 (10\%)}                  \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{outer race fault}}       & \multicolumn{1}{r|}{184 (13\%)}                 & \multicolumn{1}{r|}{188 (13\%)}                  \\ \cline{1-3}
-
-\multicolumn{1}{|l|}{\textbf{Anomaly (> 0.6)}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{837 (58\%)}                 & \multicolumn{1}{r|}{831 (60\%)}          \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{601 (42\%)}                 & \multicolumn{1}{r|}{562 (40\%)}          \\ \cline{1-3}
-
-\multicolumn{1}{|l|}{\textbf{Anomaly (> 0.9)}}                                                                                          & \multicolumn{1}{l|}{\textbf{Inner bearing (A)}} & \multicolumn{1}{l|}{\textbf{Outer bearing (B)}} \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{False}}                                                                            & \multicolumn{1}{r|}{1227 (85\%)}                 & \multicolumn{1}{r|}{1197 (86\%)}         \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{True}}                                                                             & \multicolumn{1}{r|}{211 (15\%)}                 & \multicolumn{1}{r|}{196 (14\%)}         \\ \cline{1-3}
-\multicolumn{1}{|r|}{\textbf{Total}}                                                                            & \multicolumn{1}{r|}{\textbf{1438} (100\%)}                       & \multicolumn{1}{r|}{\textbf{1393} (100\%)}               \\ \cline{1-3}
-\end{tabular}
-\caption{Label count for whole MaFaulDa dataset with recordings split to 5 chunks}
-\label{tab:observation-counts}
-\end{table}
-
-Pearson's correlation of features to rpm is very low in the whole dataset.
-In the temporal domain, the correlation coefficient is within an interval of -0.08 to 0.26.
-In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for the centroid being around 0.35.
-
-The correlation among features can reduce prediction power if a pair is elected where $|\mathrm{corr}| > 0.95$.
-The feature is not added to the subset when the threshold is exceeded.
-High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}.
-In the spectral domain set \{skewness, kurtosis\} has a strong correlation.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
-    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
-    \label{fig:design:pca-explained-variance} 
-\end{figure}
-
-The variables are also more inter-correlated in the temporal domain shown by principal component analysis.
-For 95\% of the explained variance of PCA 3 components (98.69\%) are needed in the temporal domain whereas 4 in the spectral domain (95.26\%).
-Figure \ref{fig:design:pca-explained-variance} visualizes cumulative explained variance with an increasing number of principal components.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
-        \caption{Temporal features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
-        \caption{Spectral features}
-    \end{subfigure}
-    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
-    \label{fig:design:pca-loading-plot} 
-\end{figure}
-
-PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
-Loading plots of PCA (Fig.
-\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
-The first PC in the temporal domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing}.
-The second PC focuses more on the amplitude range: \emph{rms, p-p, aac}.
-
-However, the groups are not as clear-cut for spectral features.
-Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.
-
-\subsection{Data volume savings}
-The apparent advantage of feature discovery is reducing the amount of data downstream.
-Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN).
-The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.
-
-The machinery monitoring system relies on determining several parameters:
-\begin{itemize}
-\itemsep0pt
-\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
-\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
-The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem.
-At a minimum, it should be 15 kHz to 20 kHz.
-\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
-The more critical the machine is, the interval should be shorter.
-The bigger the machine parts, the slower the defect evolves.
-\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp.
-Duration should cover at least 3 windows for spectral estimation.
-The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
-\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
-\end{itemize}
-
-Equation \ref{equ:compression-ratio-features} expresses the lossy compression ratio ($\mathcal{C}$) formula if trend indicators are stored instead of full recording.
-The number of raw channels ($S_{\mathrm{in}}$) can differ from those extracted in features ($S_{\mathrm{out}}$).
-Parameter $D = 0.5$ when we use frequency bins with 1 Hz resolution.
-
-\myequations{Lossy compression ratio with features}
-\begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
-\mathcal{C} = \frac{D \cdot f_s \cdot S_{\mathrm{in}}}{F \cdot S_{\mathrm{out}}}
-\end{align}\end{ceqn}
-
-\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
-If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.
-
-As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
-The station has 3 pumps and 3 electric motors.
-
-A pump and motor pair have 4 bearings together for drive end and non-drive end positions.
-Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
-The sampling frequency at each position is set to \emph{20 kHz}.
-The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
-
-In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution.
-Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
-On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
-Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
-The entire machine's history can be kept in a small flash memory module.
-
-\subsection{Feature selection}
-The objective of feature selection is to find a subset of the most relevant predictors in each domain.
-As a starting point, the set consists of 3 non-correlated attributes under diverse conditions.
-Ultimately, a number of chosen features are to be tweaked to increase prediction accuracy.
-Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
-
-\begin{itemize}
-\itemsep0pt
-\item \textbf{online}: a boolean selector that influences whether metrics are calculated in batch or incremental fashion,
-\item \textbf{placement}: chooses between bearing ``A'' and bearing ``B'',
-\item \textbf{predicted variable}: select a column out of ``fault'', ``anomaly90'' against which similarity is judged,
-\item \textbf{rotational speed limit}: chosses whether only observations occuring within predermined range $2500 \pm 500$ rpm are filtered.
-\end{itemize}
-
-In feature evaluation for fault prediction, we use hold-out validation in batch models and progressive valuation in online models.
-Classes in observations for batch models are rebalanced to the majority class with a random oversampling strategy.
-The training and testing set split ratio is 80 to 20.
-Classes for incremental learning are ordered by relative severity level and shuffled within levels.
-
-The best group of attributes is elected based on a training set with multiple methods.
-We compute the mean of the absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable.
-The features are then ordered in descending order by the received score.
-These individual ranks are combined by rank product to create an ensemble out of the metrics.
-Reference implementation of feature selection metrics uses Python packages Scikit Learn\footnote{SciKit Learn: \url{https://scikit-learn.org/}} in batch learning and RiverML\footnote{RiverML: \url{https://riverml.xyz/}} for online learning.
-
-\begin{figure}[h!]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/approval-voting-temporal.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/approval-voting-spectral.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Approval rating of the best triplet of features to target variable ``fault'' scored by rank product of correlation, F statistic, and mutual information.}
-    \label{fig:design:approval-rating-features}
-\end{figure}
-
-The choice of features is very sensitive to experimental conditions.
-Tendencies are demonstrated by counting how many triplets the indicator appears in across all possible situations.
-The results of approval voting are shown in Figure~\ref{fig:design:approval-rating-features}.
-The most occurring attributes in the temporal domain are zero-crossing rate, peak-to-peak distance, and average amplitude change.
-the features dominating in the spectral domain are centroid, roll-off, and roll-on.
-
-\section{K-nearest neighbor classifier}
-We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets.
-The k-NN classifier being a lazy learner means it can be adapted easily from offline to online context.
-Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values.
-Voronoi diagrams can display these regions and explain the model in that way.
-Batch learning in k-NN serves here as a target performance whose attainment is desirable with online learning.
-
-\subsection{Batch models}
-Three types of k-NN model experiments run with hold-out validation in a batch setting.
-First, the model learns all extracted features, so no feature selection occurs.
-Then, the brute-force method searches for a combination of three features with the highest training accuracy.
-In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-fault.png}
-        \caption{Prediction for 6 fault classes in testing set with temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-fault.png}
-        \caption{Prediction for 6 fault classes in testing set with spectral domain features}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-temporal-confusion-matrix-anomaly90.png}
-        \caption{Prediction of high severity anomalies in testing set with temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-spectral-confusion-matrix-anomaly90.png}
-        \caption{Prediction of high severity anomalies in testing set with spectral domain features}
-    \end{subfigure}
-    \caption{Confusion matrix of k-NN predictions on bearing position A}
-    \label{fig:design:KNN-confusion-matrix}
-\end{figure}
-
-Two models are created for the target variable in classification with all 10 temporal and 11 spectral features.
-The subset of records includes all rotational speeds on bearing position A.
-Either six fault labels or anomalies above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
-
-Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:KNN-confusion-matrix}.
-In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
-The most inaccuracies in the temporal domain are between misalignment and bearing race faults.
-In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.
-
-In anomaly prediction, the error of the first degree is 7 times more prevalent than the error of the second degree.
-False positives are preferable, since we do not want the machine to fail prematurely and not know about it.
-In all cases, spectral features maintain better prediction metrics than all temporal features because of less interdependency among features.
-Bearing B exhibits overall worse classification performance because of more noise in the original signal.
-
-\begin{table}[h]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|l|l|rrr|rrr|}
-\hline
-\multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Bearing\\ position\end{tabular}}} & \multirow{2}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Target\\ variable\end{tabular}}} & \multirow{2}{*}{\textbf{Observations}}                                             & \multicolumn{3}{l|}{\textbf{Temporal domain}}                                                                                                                                                                                                                                    & \multicolumn{3}{l|}{\textbf{Spectral domain}}                                                                                                                                                                                                                                    \\ \cline{4-9}
-                                                                                     &                                                                                     &                                                                                   & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Testing\\ accuracy\end{tabular}}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Training\\ F1 score\end{tabular}}} \\ \hline
-\multirow{2}{*}{A}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9859}                                                               & \multicolumn{1}{r|}{0.9736}                                                              & 0.97                                                                                      & \multicolumn{1}{r|}{0.9917}                                                               & \multicolumn{1}{r|}{0.9836}                                                              & 0.98                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly\\ (0.9)\end{tabular}                               & \begin{tabular}[c]{@{}l@{}}$\sum 2454$\\ 1227 per class\end{tabular} & \multicolumn{1}{r|}{0.9869}                                                               & \multicolumn{1}{r|}{0.9800}                                                              & 0.98                                                                                     & \multicolumn{1}{r|}{0.9921}                                                               & \multicolumn{1}{r|}{0.9874}                                                              & 0.99                                                                                      \\ \hline
-\multirow{2}{*}{B}                                                                   & Fault                                                                               & \begin{tabular}[c]{@{}l@{}}$\sum 2998$\\ 498 per class\end{tabular}  & \multicolumn{1}{r|}{0.9316}                                                               & \multicolumn{1}{r|}{0.8969}                                                              & 0.90                                                                                     & \multicolumn{1}{r|}{0.9207}                                                               & \multicolumn{1}{r|}{0.8765}                                                              & 0.87                                                                                      \\ \cline{2-9}
-                                                                                     & \begin{tabular}[c]{@{}l@{}}Anomaly \\ (0.9)\end{tabular}                              & \begin{tabular}[c]{@{}l@{}}$\sum 2394$\\ 1197 pre class\end{tabular} & \multicolumn{1}{r|}{0.9568}                                                               & \multicolumn{1}{r|}{0.9273}                                                              & 0.93                                                                                      & \multicolumn{1}{r|}{0.9428}                                                               & \multicolumn{1}{r|}{0.9156}                                                              & 0.92                                                                                      \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{k-NN model performance trained on all extracted features}
-\label{tab:design:all-extracted-features}
-\end{table}
-
-Accuracies and F1 scores in both bearing positions with all extracted features are shown in Table \ref{tab:design:all-extracted-features}.
-Models are overtrained, especially for temporal features, because of the substantial difference between accuracy on training and validation sets.
-Binary classification of anomalies is unsurprisingly more precise in general than the multi-class case.
-Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 90\% for bearing B.
-
-Next, we exhaustively list all combinations of three features and look at the range of model performances generated.
-There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate k-NN models for temporal domain features and 165 for the spectral domain.
-The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
-The accuracy of the k-NN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-train.png}
-        \caption{Testing set}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.8\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-3-features-combinations-test.png}
-        \caption{Training set}
-    \end{subfigure}
-    \caption{Range of prediction accuracy in all k-NN models with subset of 3 features. Subplots show three different predicted variables.}
-    \label{fig:design:feature-combinations-KNN}
-\end{figure}
-
-Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}.
-The worst accuracy occurs for temporal features in multi-class classification, 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
-An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.
-
-\begin{table}[ht!]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|r|r|r|l|r|r|}
-\hline
-\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{zero-crossing, aac, rms\}         & 0.9843                & 0.9792 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}         & 0.9701  & 0.9475 \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{zero-crossing, aac, rms\}            & 0.9570                & 0.9227 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}     & 0.9173 & 0.8738 \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{Features with the highest accuracies on the training set found combinatorically}
-\label{tab:design:feature-combinations-KNN}
-\end{table}
-
-The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}.
-Their prediction accuracies in k-NN models are subpar to optimal sets.
-However, the advantage is that the feature election process is not so computationally taxing.
-On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains.
-Because of the low k hyperparameter value, models are overtrained either way.
-
-\begin{table}[ht!]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|r|r|r|l|r|r|}
-\hline
-\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{zero-crossing, rms, shape\}              & 0.9743 &	0.9633 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, rms, shape\}               & 0.9592 & 0.9274                                     \\ \cline{3-6} 
-                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        &             \{zero-crossing, rms, shape\} & 0.9265	 & 0.8835                \\ \cline{3-6}
-                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, p-p, aac\}           & 0.9113 &	0.8614                                      \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated k-NN accuracies.}
-\label{tab:design:best-3-features-KNN}
-\end{table}
-
-Lowering the number of attributes allows visualization of labels in planar scatter plots.
-The data points in 3-dimensional cross-sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
-We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
-
-Cluster overlaps of various defect types are also confirmed by silhouette scores around zero.
-Therefore, the k hyperparameter cannot be increased much, as it would cause the merge of mutually confused categories.
-Low-severity faults should be relabeled as a class without fault to watch out just for alert conditions.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
-        \caption{Spectral domain features}
-    \end{subfigure} 
-    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
-    \label{fig:design:feature-space-scatter}
-\end{figure}
-
-Model performance of the k-NN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
-The best combination of 3 features always achieves better than when the model is trained on all features.
-This has to do with curse of dimensionality phenomenon.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
-        \caption{Testing set}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
-        \caption{Training set}
-    \end{subfigure} 
-    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
-    \label{fig:design:KNN-accuracy-batch}
-\end{figure}
-
-We suspected that the PCA property of maximizing variances in each of the few dimensions would support more separation of clustered groups and would be beneficial in classification.
-The bar chart supports this assumption.
-PCA always produces greater model accuracy than any other method of feature selection.
-The rank product of the three scoring techniques is not better every time, but it balances out aggregated methods to achieve more stable results across testing sets.
-
-In every instance, a subset of spectral features is responsible for better accuracy than a subset of temporal features.
-Presumably, it is so because of many correlated pairs of attributes in the temporal domain.
-Further tests should be made to determine optimal feature subsets and the impact of altering the feature election process.
-
-\subsection{Online models}
-Online learning imitates hardened conditions for machinery diagnostics that appear in deployment.
-Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
-The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.
-
-The k-NN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context.
-In this manner, we can compare the training accuracies in the last sample for both models.
-k-NN is set to 5 nearest neighbors and a proximity metric of Euclidian distance.
-Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
-
-The \textbf{stream of events is sorted} by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}) which ensures steady increments in label counts throughout the whole duration of the simulation (Fig.~\ref{fig:design:online-event-order}).
-This constructed event sequence is a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
-It is meant to approximate the gradual overall degradation of the machine.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
-        \caption{Event ordering of faults}
-        \label{fig:design:online-event-order}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
-        \caption{Fault severity levels ordering}
-        \label{fig:design:online-count-severity-level}
-    \end{subfigure}
-    \caption{Label sequencing for progressive evaluation}
-\end{figure}
-
-Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
-Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement.
-The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
-The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.
-
-During gradual learning, the correct label is supplied after a fixed period passes after its prediction.
-This \textbf{sliding window} simulation examines accuracy every 100 iterations.
-Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
-        \caption{Principal components from temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
-        \caption{Principal components from spectral domain features}
-    \end{subfigure}
-    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
-    \label{fig:design:scatter-plot-online}
-\end{figure}
-
-Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly.
-Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
-Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
-    \label{fig:design:online-fault-delay-sliding}
-\end{figure}
-
-The \textbf{tumbling window} simulates regular expert visits annotating observations recorded until that moment.
-Labels for the whole previous window are supplied at once.
-In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
-    \label{fig:design:online-fault-delay-tumbling}
-\end{figure}
-
-A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
-Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows.
-The true labels are unknown.
-After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
-
-Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset.
-In the simulation of missing labels, the equal-length gaps are skipped before another observation is annotated.
-This approach of choosing samples to annotate without considering their representativeness results in severe harm to predictions.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
-        \caption{Temporal domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
-        \caption{Spectral domain features}
-    \end{subfigure}
-    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
-    \label{fig:design:online-label-skip}
-\end{figure}
-
-Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
-Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.
-More missing labels require recording more observations before the equivalent accuracy is reached.
+% Measurement plan (calendar and folders) - dataset schema

### 2024-04-28 thesis/chapters/04-implementation.tex
Turn outline into section headings

--- 2024-01-03 thesis/chapters/04-implementation.tex
@@
 \chapter{Implementation} \label{section:implementation}
-The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment.
-Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}).
 
-We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes.
-The collection of the novel dataset is accompanied by an agreed upon schedule.
+\section{Data analysis}
+% Jupyter notebook - TSFEL, numpy, pandas (data handling),  scipy (signal processing and stats),   | sklearn, imblearn | matplotlib
 
-\section{Machinery for monitoring}
-Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.17\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
-        \caption{\footnotesize Fan}
-        \label{fig:machine:fan}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.17\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-compressor.jpg}
-        \caption{\footnotesize Compressor}
-        \label{fig:machine:compressor}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
-        \caption{\footnotesize Water pump KSB}
-        \label{fig:machine:pump-ksb}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
-        \caption{\footnotesize Water pump Sigma}
-        \label{fig:machine:pump-sigma}
-    \end{subfigure}
-    \caption{Machines dedicated for vibration measurements}
-\end{figure}
-
-\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
-It serves as a test bed during the sensor unit development.
-The sensor is placed on the plastic casing at the back of the drive motor.
-The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
-It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
-Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.
-
-\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
-Altogether, two units are available in two independent air conditioning units for the data center.
-The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
-Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
-Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.
-
-\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
-The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
-
-The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
-The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
-The electric motor provides 400~kW of power (class~\rom{3}).
-The outer bearing on the pump vibrates with an acceleration of $\pm 5 \;\mathrm{m/s}^2$.
-
-The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
-It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}).
-Each pump and motor have 2 bearings.
-Therefore, there are 4 measurement positions in total.
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
-        \caption{Vibration rms velocity dashboard}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
-        \caption{Vibration spectral analysis dashboard}
-    \end{subfigure}
-     \caption{KSB Guard cloud monitoring for pumps}
-     \label{fig:design:ksb-guard}
-\end{figure}
-
-\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
-In addition, we are able to export the entire historical record at hourly intervals.
-Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
-
-\section{Sensor hardware and drivers}
-In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
-The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
-
-\begin{table}[ht]
-\renewcommand{\arraystretch}{1.2}
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
-\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
-\textbf{Bus}                                     & Analog           & SPI                \\ \hline
-\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
-\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
-\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
-\textbf{Sensitivity} (mg/LSB)                    & 2.930            & 0.061       \\ \hline
-\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
-\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
-\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
-\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
-\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
-\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
-\end{tabular}
-\caption{Hardware parameters of previous and proposed sensor units}
-\label{tab:design:hw-sensors}
-\end{table}
-
-The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
-ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
-It enables us to store all samples from FIFO.
-The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
-The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
-	\caption{Sensor unit hardware block diagram}
-	\label{fig:design:block-diagram-hw}
-\end{figure}
-
-The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF SDK\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
-The accelerometer driver is also made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
-Activity diagrams of required firmware functionality are in Appendix~\ref{appendix:technical-docs}.
-
-\section{Preliminary measurements}
-During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
-Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
-The acceleration rarely exceeds 1~g.
-
-In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz).
-The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-        \caption{Acceleration in $\mathrm{m/s}^2$}
-        \label{fig:design:preliminary-acceleration}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
-        \caption{Approximate velocity in $\mathrm{mm/s}$}
-        \label{fig:design:preliminary-velocity}
-    \end{subfigure} 
-    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
-\end{figure}
-
-Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
-The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks.
-Envelopes must be tweaked further to achieve more accurate values.
-The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
-		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
-		\label{fig:design:orbital-analysis}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.54\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
-        \label{fig:design:preliminary-spectrum}
-    \end{subfigure} 
-    \caption{Orbital and spectral methods of vibration signal analysis}
-\end{figure}
+\section{Firmware}
+% In C, ESP-IDF SDK and FreeRTOS tasks
+% Found driver online
+% Problems with timing - binary write (osciloscope pictures)
+% tool for convert bin2csv

### 2024-04-28 thesis/chapters/06-conclusion.tex
Turn outline into section headings

--- 2023-12-27 thesis/chapters/05-conclusion.tex
@@
 \chapter{Conclusion} \label{section:conclusion}
-In the thesis we focused on trend indicator selection for inexpensive industrial condition monitoring solution from vibration signals.
-The goal is to enable timely fault detection of machinery parts with as little input data as possible.
-For that purpose, we answer four research questions.
-
-Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343).
-These formulas compute 10 features summarizing waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.
-
-In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable.
-Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning.
-The features are squished from multiple dimensions using the Euclidian norm.
-Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset.
-We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.
-
-Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power.
-Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%.
-The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.
-
-The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations.
-No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively.
-Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.
-
-The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables.
-Annotation can be assigned belatedly or even never.
-Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
-The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.
-
-Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions.
-Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.
-
-The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations.
-We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards.
-The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.
-
-Feature selection methods shall be incorporated into incremental learning.
-Hyperparameters shall be adjusted, and the balancing method used to increase model performance.
-The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2024-04-28 thesis/chapters/TEXT.tex
Turn outline into section headings

\chapter{Design} \label{chapter:design}
The design phase sets out to elaborate on the scenarios for experiments with IoT device. In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section. Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.

\section{Research questions}
This thesis aims to provide answers to four research questions. The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines. The \textbf{research questions} are:
\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
    \itemsep0pt
	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
	\item What is the reduction in transmission goodput when chosen signal features are used?
	\item What accuracy of prediction models can be achieved with various feature subsets?
	\item How can machinery faults be continuously identified and predicted based upon collected events?
\end{enumerate}

\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
\begin{todolist}
    \itemsep0pt
    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
    \item Establish a list of conditions that should be later investigated in the experimental setting.
    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
\end{todolist}

However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain. The reason is that we did not find a way to represent extracted features more succinctly as a single number. We also did not discover a strategy for choosing only the relevant frequency bins. The assembled description is retained to lead further research on that topic.

The goals are impacted by certain \textbf{risks} that are assessed and tracked:

\begin{enumerate}[label=R-\arabic*., font=\bfseries]
\itemsep0pt
\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
\item Fault modes can not be reliably differentiated and labeled in the dataset.
\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
\end{enumerate}

% All features --------------------------------------------------------
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD-confusion-matrix.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD-confusion-matrix.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{All features confusion matrix}
\end{figure}

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/all-features/FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{All features accuracy based on k-value}
\end{figure}

% Standing fan (EDA) --------------------------------------------------------

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
        \caption{Speed 1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
        \caption{Speed 2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
        \caption{Speed 3}
    \end{subfigure}
    \caption{Frequency spectrum from sound of standing fan}
\end{figure}

% Frequency from vibrations
% Plot
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
    \caption{Estimation of rotation speed from vibrations}
\end{figure}

% Clusters with true labels --------------------------------------------------------------
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{PCA of all features to 2 components}
\end{figure}

%TODO fix inverse transform
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{3 Best features and their ranges}
\end{figure}

% Incremental learning ------------------------------------------------------

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
        \caption{Order by raising severity}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
        \caption{Order after relabeing normal class}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
        \caption{Order of severities}
    \end{subfigure}
    \caption{Ordering of faults}
\end{figure}

% Gradual
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Gradual learning (window = 1, skip = 0)}
\end{figure}

% Tumbling windows
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Tumbling window in incremental learning}
\end{figure}

% % Label skips and parts of dataset
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure} 
    \caption{Skip labels in incremental learning}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD-severity.png}
        \caption{Time-domain features (severity)}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD-severity.png}
        \caption{Frequency-domain features (severity)}
    \end{subfigure} 
    \caption{Skip labels in incremental learning with different sizes}
\end{figure}

% Histograms of machinery measurements
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
        \caption{C1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
        \caption{C2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
        \caption{M1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
        \caption{M2}
    \end{subfigure} 
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
        \caption{M3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
        \caption{P1}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
        \caption{P2}
    \end{subfigure} 
    \hfill
    \begin{subfigure}[b]{0.33\textwidth}
        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
        \caption{P3}
    \end{subfigure} 
    \caption{Histograms}
\end{figure}

% Correlations to RPM
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
    \caption{Correlation of features to RPM over all experiments}
\end{figure}

% Features range (3D)
% Standing Fan
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-TD-features.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/fan-FD-features.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in standing fan}
\end{figure}

% Pumps and compressors
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in pumps}
\end{figure}

% Mafaulda
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A+B.png}
        \caption{Time-domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A+B.png}
        \caption{Frequency-domain features}
    \end{subfigure}
    \caption{Feature range in MaFaulDa}
\end{figure}

% Feature combinations accuracy
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-accuracy.png}
        \caption{Accuracy}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
        \caption{Percentile}
    \end{subfigure}
    \caption{Feature selection method choices}
\end{figure}

% In fsel percentile - mention median from notebook for each method - table
\begin{table}[h]
\begin{tabular}{|l|r|r|}
\hline
\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
\end{tabular}
\end{table}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-features-A-dim3.png}
        \caption{Time domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-5-neighbors-A-dim3.png}
        \caption{Time domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-features-A-dim3.png}
        \caption{Frequency domain features}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-5-neighbors-A-dim3.png}
        \caption{Frequency domain features}
    \end{subfigure}
    \caption{Model accuracy distribution}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
\end{figure}

% Counts table

\begin{table}[h]
\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
\hline
\textbf{Bearings} & \textbf{Severity} & \textbf{Misalignment} & \textbf{Imbalance} & \textbf{Cage fault} & \textbf{Ball fault} & \textbf{Outer race fault} & \textbf{Normal} & \textbf{$\Sigma$} \\ \hline
A                 & No                & 498                   & 333                & 188                 & 186                 & 184                       & 49              & 1438              \\ \hline
B                 & No                & 498                   & 333                & 188                 & 137                 & 188                       & 49              & 1393              \\ \hline
A+B               & No                & 996                   & 666                & 376                 & 323                 & 372                       & 98              & 2831              \\ \hline
A                 & Yes               & 248                   & 188                & 91                  & 87                  & 86                        & 738             & 1438              \\ \hline
B                 & Yes               & 248                   & 188                & 90                  & 45                  & 90                        & 732             & 1393              \\ \hline
A+B               & Yes               & 496                   & 376                & 181                 & 132                 & 176                       & 1470            & 2831              \\ \hline
\end{tabular}
\end{table}

% Best feature selection methods table (order by best count)
\begin{table}[]
\begin{tabular}{|l|r|r|r|}
\hline
                            & \multicolumn{1}{l|}{\textbf{Best method for scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
\textbf{Rank product}       & 151                                                     & 69.91                                            & 90.85                                                  \\ \hline
\textbf{Mutual information} & 46                                                      & 21.30                                            & 90.35                                                  \\ \hline
\textbf{Correlation}        & 13                                                      & 6.02                                             & 88.88                                                  \\ \hline
\textbf{F statistic}        & 6                                                       & 2.78                                             & 78.70                                                  \\ \hline
\textbf{$\Sigma$}           & 216                                                     & 100.000000                                       & -                                                      \\ \hline
\end{tabular}
\end{table}

% Bearing frequencies table
\begin{table}[h]
\begin{tabular}{|l|r|r|r|}
\hline
\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{Motor \#1}} & \multicolumn{1}{l|}{\textbf{Motor \#2}} & \multicolumn{1}{l|}{\textbf{Pump \#3 \& \#4}} \\ \hline
\textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
\textbf{$n$}           & 8                                       & 8                                       & 8                                             \\ \hline
\textbf{$f_s$}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
\textbf{$d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
\textbf{$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
\textbf{$\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
\textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
\textbf{BPFO {[}Hz{]}} & 77.18                                   & 77.91                                   & 77.00                                         \\ \hline
\textbf{BPFI {[}Hz{]}} & 121.88                                  & 121.16                                  & 122.07                                        \\ \hline
\textbf{BSF {[}Hz{]}}  & 58.20                                   & 59.97                                   & 57.77                                         \\ \hline
\textbf{FTF {[}Hz{]}}  & 9.65                                    & 9.74                                    & 9.63                                          \\ \hline
\end{tabular}
\end{table}

% Time-frequency spectrum
% Compare with other pump - same places
\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT.png}
        \caption{K3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT.png}
        \caption{M1-2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT.png}
        \caption{P1-3}
    \end{subfigure}
    \caption{Time frequency spectrum}
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/X-P2-Turn-on-Sigma.png}
        \caption{P2-3 turn off with intererence (X-axis)}
    \end{subfigure}
    \caption{Time frequency spectrum}
\end{figure}

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
        \caption{Pump P1 turns off}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
        \caption{Pump P2 turn on}
    \end{subfigure}
\end{figure}

% Dataset scenarios - 24 scenarios
\begin{itemize}
\item domain - TD, FD
\item dim - 1, 3
\item bearing - A, B, A+B
\item severity - No, Yes
\end{itemize}

\clearpage

%TODO ---------------------------------------------------------------------------
\section{Dataset exploration}
In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset. It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.

One representative recording is first selected in each available fault category. The sample is visualized and statistically described in both temporal and spectral domains. A whole step-by-step procedure is outlined in the activity diagram (Fig.~\ref{fig:design:mafaulda-preprocessing}).

%\begin{figure}[ht]
%	\centering
%	\includegraphics[width=\textwidth]{assets/design/activity-data-exploration.png}
%	\caption{Activity diagram of MaFaulDa dataset preprocessing}
%	\label{fig:design:mafaulda-preprocessing}
%\end{figure}

MaFaulda contains 1951 records labeled with inducted faults of increasing severity. The defects were set up on the machine simulator as is mentioned in the part about datasets. Time series of the triaxial piezoelectric accelerometers in separate files have a sampling frequency of 50 kHz.

These vibration sensors are placed in two positions. The first placement is around the inner underhang bearing named \emph{A} which is closer to the motor. The second location is around the outer overhang bearing denoted as \emph{B} position.

\subsection{Fault annotations}
The MaFaulDa has annotations altogether for 10 classes of faults, of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects. Some categories are redundant or irrelevant for a given sensor position.

Therefore, rotor shaft misalignement in vertical and horizontal directions are merged into one joint group. Depending on the chosen bearing position, only records having relevant labels are considered.

This means that fault classification solely concerns bearing in direct contact and shaft mechanically passing through it. The bearings affect each other, but the effect on the opposite side should appear via a common interconnection shaft.

In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault. In the step of choosing the accelerometer location, records pointing to the other bearing as a source of the malfunction are discarded. Then the next action renames the labels to be better recognizable and unite the same phenomena.

Groups of identified machine defects are additionally characterized by altered masses attached or motor shaft displacement shifts. The set amount is sorted in ascending order, separating \textbf{multiple event severities}. However, the count of severity levels is not identical in every group. Levels are hence scaled into the range between zero and one using a min-max scaler. Scaling is applied to classes separately.

The strength of the recorded response to the underlying defect is also dependent on the shaft \textbf{rotational speed}. Speed in rpm units is calculated from pulsed speedometer output. It is the average distance between two successive rising edges: 
\begin{ceqn}\begin{align}
\mathrm{rpm} = 60 \;/\; \overline{\Delta t}
\end{align}\end{ceqn}

\textbf{One specimen waveform} is picked from each fault class to illustrate their superficial differences. Recordings are filtered to get the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz) to see the patterns most pronounced. The baseline class sample is chosen according to fixed rotor speed.

\subsection{Signal filters}
The DC component in the three-dimensional vibration signal is removed by subtracting the global mean. Immediately follows a digital IIR Butterworth \textbf{low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.

Before the low pass filter usage, the peak at 20 kHz with a sideband was present as an unwanted artifact. It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz. At the same time, such a frequency is outside the range of any feasible MEMS accelerometer.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
        \caption{Time domain waveforms}
        \label{fig:design:fault-temporal-waveform}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
        \caption{Spectra in radial direction}
        \label{fig:design:fault-spectral-waveform}
    \end{subfigure} 
    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
\end{figure}

Temporal domain waveforms of the 300 ms signal slice are shown in the graphs in Figure \ref{fig:design:fault-temporal-waveform}. Subplots for radial, tangential, and axial directions are laid out in columns from left to right. Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.

The frequency spectrum in Figure \ref{fig:design:fault-spectral-waveform} is obtained by FFT and Hann window of length $2^{14}$. The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz. The graph has been cropped in both axes to make the most important peaks visible.

\subsection{Statistical tests}
The statistical tests and visual checks are conducted to assess \textbf{normality and stationary} of time series. Half a second of amplitude samples are used from every sensor channel. These 25 thousand observations are downsampled tenfold to $2500$.

\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from a normal distribution under most circumstances. The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms. \textbf{Quantile–quantile plots} confirm non-normal distribution because of the striking samples tilt to the diagonal line.

\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root (${p < 0.001}$). The same is confirmed with the \textbf{autocorrelation} function shape. It denotes that the stochastic process is stationary as the oscillation is bounded.

\section{Feature relevance}
Attributes described in section \ref{section:feature-extraction} are independently summarized from each sensor position and direction. Then similarity score of features is ascertained in relation to a predicted variable. The subset of the strongest predictors is chosen based on the order of their perceived importance.

\subsection{Feature extraction}
Each file in the MaFaulDa contains six accelerometer channels. In the feature extraction process, the sequence of samples is split into five parts or 1-second intervals. The portions are passed through the same DC removal and low pass filters as previously. The rotational speed is derived from speedometer pulses within the chunk.

Signal chunks are converted afterward into \textbf{10 temporal and 11 spectral features}. Welch's method for spectrum density estimation averaging over $2^{14}$ long FFT segments after Hann windowing is the source for spectral features. The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}.

The Euclidean norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure~\ref{fig:design:feature-range}.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
%        \caption{Time-domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
%        \caption{Frequency-domain features}
%    \end{subfigure}
%    \caption{Feature value ranges in inner bearing position (A)}
%    \label{fig:design:feature-range}
%\end{figure}

Fault labels and their severities come from the directory structure within the dataset. The binary target variable indicating whether to initiate a warning is called an anomaly. Anomalies are labeled according to relative fault severity level. We decided to investigate two fault severities having levels above 0.6 and 0.9. The quantity of observation by fault and anomaly severity is shown in Table \ref{tab:observation-counts}. The dataset is substantially unbalanced.

Pearson's correlation of features to rpm is very low in the whole dataset. In the temporal domain, the correlation coefficient is within an interval of -0.08 to 0.26. In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for the centroid being around 0.35.

The correlation among features can reduce prediction power if a pair is elected where $|\mathrm{corr}| > 0.95$. The feature is not added to the subset when the threshold is exceeded. High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}. In the spectral domain set \{skewness, kurtosis\} has a strong correlation.

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
%    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
%    \label{fig:design:pca-explained-variance} 
%\end{figure}

The variables are also more inter-correlated in the temporal domain shown by principal component analysis. For 95\% of the explained variance of PCA 3 components (98.69\%) are needed in the temporal domain whereas 4 in the spectral domain (95.26\%). Figure \ref{fig:design:pca-explained-variance} visualizes cumulative explained variance with an increasing number of principal components.

%\begin{figure}[h!]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
%        \caption{Temporal features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
%        \caption{Spectral features}
%    \end{subfigure}
%    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
%    \label{fig:design:pca-loading-plot} 
%\end{figure}

PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions. Loading plots of PCA (Fig. \ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components. The first PC in the temporal domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing}. The second PC focuses more on the amplitude range: \emph{rms, p-p, aac}.

However, the groups are not as clear-cut for spectral features. Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.

\subsection{Data volume savings}
The apparent advantage of feature discovery is reducing the amount of data downstream. Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN). The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.

The machinery monitoring system relies on determining several parameters:
\begin{itemize}
\itemsep0pt
\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise. The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem. At a minimum, it should be 15 kHz to 20 kHz.
\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure. The more critical the machine is, the interval should be shorter. The bigger the machine parts, the slower the defect evolves.
\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp. Duration should cover at least 3 windows for spectral estimation. The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
\end{itemize}

Equation \ref{equ:compression-ratio-features} expresses the lossy compression ratio ($\mathcal{C}$) formula if trend indicators are stored instead of full recording. The number of raw channels ($S_{\mathrm{in}}$) can differ from those extracted in features ($S_{\mathrm{out}}$). Parameter $D = 0.5$ when we use frequency bins with 1 Hz resolution.

\myequations{Lossy compression ratio with features}
\begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
\mathcal{C} = \frac{D \cdot f_s \cdot S_{\mathrm{in}}}{F \cdot S_{\mathrm{out}}}
\end{align}\end{ceqn}

\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1. If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.

As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}. The station has 3 pumps and 3 electric motors.

A pump and motor pair have 4 bearings together for drive end and non-drive end positions. Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}. The sampling frequency at each position is set to \emph{20 kHz}. The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).

In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution. Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year. On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1. Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices. The entire machine's history can be kept in a small flash memory module.

\subsection{Feature selection}
The objective of feature selection is to find a subset of the most relevant predictors in each domain. As a starting point, the set consists of 3 non-correlated attributes under diverse conditions. Ultimately, a number of chosen features are to be tweaked to increase prediction accuracy. Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:

In feature evaluation for fault prediction, we use hold-out validation in batch models and progressive valuation in online models. Classes in observations for batch models are rebalanced to the majority class with a random oversampling strategy. The training and testing set split ratio is 80 to 20. Classes for incremental learning are ordered by relative severity level and shuffled within levels.

The best group of attributes is elected based on a training set with multiple methods. We compute the mean of the absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable. The features are then ordered in descending order by the received score. These individual ranks are combined by rank product to create an ensemble out of the metrics. Reference implementation of feature selection metrics uses Python packages Scikit Learn\footnote{SciKit Learn: \url{https://scikit-learn.org/}} in batch learning and RiverML\footnote{RiverML: \url{https://riverml.xyz/}} for online learning.

The choice of features is very sensitive to experimental conditions. Tendencies are demonstrated by counting how many triplets the indicator appears in across all possible situations. The results of approval voting are shown in Figure~\ref{fig:design:approval-rating-features}. The most occurring attributes in the temporal domain are zero-crossing rate, peak-to-peak distance, and average amplitude change. the features dominating in the spectral domain are centroid, roll-off, and roll-on.

\section{K-nearest neighbor classifier}
We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets. The k-NN classifier being a lazy learner means it can be adapted easily from offline to online context. Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values. Voronoi diagrams can display these regions and explain the model in that way. Batch learning in k-NN serves here as a target performance whose attainment is desirable with online learning.

\subsection{Batch models}
Three types of k-NN model experiments run with hold-out validation in a batch setting. First, the model learns all extracted features, so no feature selection occurs. Then, the brute-force method searches for a combination of three features with the highest training accuracy. In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.

Two models are created for the target variable in classification with all 10 temporal and 11 spectral features. The subset of records includes all rotational speeds on bearing position A. Either six fault labels or anomalies above 0.9 severity level are guessed by the model with the same hold-out validation split as before.

Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:KNN-confusion-matrix}. In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree. The most inaccuracies in the temporal domain are between misalignment and bearing race faults. In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.

In anomaly prediction, the error of the first degree is 7 times more prevalent than the error of the second degree. False positives are preferable, since we do not want the machine to fail prematurely and not know about it. In all cases, spectral features maintain better prediction metrics than all temporal features because of less interdependency among features. Bearing B exhibits overall worse classification performance because of more noise in the original signal.

%\begin{table}[h]
%\centering
%\renewcommand{\arraystretch}{1.2}
%\begin{adjustbox}{width=\textwidth}
%
%\end{tabular}
%\end{adjustbox}
%\caption{k-NN model performance trained on all extracted features}
%\label{tab:design:all-extracted-features}
%\end{table}

Accuracies and F1 scores in both bearing positions with all extracted features are shown in Table \ref{tab:design:all-extracted-features}. Models are overtrained, especially for temporal features, because of the substantial difference between accuracy on training and validation sets. Binary classification of anomalies is unsurprisingly more precise in general than the multi-class case. Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 90\% for bearing B.

Next, we exhaustively list all combinations of three features and look at the range of model performances generated. There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate k-NN models for temporal domain features and 165 for the spectral domain. The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques. The accuracy of the k-NN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.

Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}. The worst accuracy occurs for temporal features in multi-class classification, 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features. An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.

\begin{table}[ht!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{zero-crossing, aac, rms\}         & 0.9843                & 0.9792 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}         & 0.9701  & 0.9475 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{zero-crossing, aac, rms\}            & 0.9570                & 0.9227 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}     & 0.9173 & 0.8738 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Features with the highest accuracies on the training set found combinatorically}
\label{tab:design:feature-combinations-KNN}
\end{table}

The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}. Their prediction accuracies in k-NN models are subpar to optimal sets. However, the advantage is that the feature election process is not so computationally taxing. On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains. Because of the low k hyperparameter value, models are overtrained either way.

\begin{table}[ht!]
\centering
\renewcommand{\arraystretch}{1.2}
\begin{adjustbox}{width=\textwidth}
\begin{tabular}{|r|r|r|l|r|r|}
\hline
\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{zero-crossing, rms, shape\}              & 0.9743 &	0.9633 \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, rms, shape\}               & 0.9592 & 0.9274                                     \\ \cline{3-6} 
                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        &             \{zero-crossing, rms, shape\} & 0.9265	 & 0.8835                \\ \cline{3-6} 
                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6} 
                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, p-p, aac\}           & 0.9113 &	0.8614                                      \\ \cline{3-6} 
                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
\end{tabular}
\end{adjustbox}
\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated k-NN accuracies.}
\label{tab:design:best-3-features-KNN}
\end{table}

Lowering the number of attributes allows visualization of labels in planar scatter plots. The data points in 3-dimensional cross-sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}. We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.

Cluster overlaps of various defect types are also confirmed by silhouette scores around zero. Therefore, the k hyperparameter cannot be increased much, as it would cause the merge of mutually confused categories. Low-severity faults should be relabeled as a class without fault to watch out just for alert conditions.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
%        \caption{Temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
%        \caption{Spectral domain features}
%    \end{subfigure} 
%    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
%    \label{fig:design:feature-space-scatter}
%\end{figure}

Model performance of the k-NN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}. The best combination of 3 features always achieves better than when the model is trained on all features. This has to do with curse of dimensionality phenomenon.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
%        \caption{Testing set}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
%        \caption{Training set}
%    \end{subfigure} 
%    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
%    \label{fig:design:KNN-accuracy-batch}
%\end{figure}

We suspected that the PCA property of maximizing variances in each of the few dimensions would support more separation of clustered groups and would be beneficial in classification. The bar chart supports this assumption. PCA always produces greater model accuracy than any other method of feature selection. The rank product of the three scoring techniques is not better every time, but it balances out aggregated methods to achieve more stable results across testing sets.

In every instance, a subset of spectral features is responsible for better accuracy than a subset of temporal features. Presumably, it is so because of many correlated pairs of attributes in the temporal domain. Further tests should be made to determine optimal feature subsets and the impact of altering the feature election process.

\clearpage
\subsection{Online models}
Online learning imitates hardened conditions for machinery diagnostics that appear in deployment. Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification. The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.

The k-NN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context. In this manner, we can compare the training accuracies in the last sample for both models. k-NN is set to 5 nearest neighbors and a proximity metric of Euclidian distance. Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.

The \textbf{stream of events is sorted} by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}) which ensures steady increments in label counts throughout the whole duration of the simulation (Fig.~\ref{fig:design:online-event-order}). This constructed event sequence is a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths. It is meant to approximate the gradual overall degradation of the machine.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
%        \caption{Event ordering of faults}
%        \label{fig:design:online-event-order}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
%        \caption{Fault severity levels ordering}
%        \label{fig:design:online-count-severity-level}
%    \end{subfigure}
%    \caption{Label sequencing for progressive evaluation}
%\end{figure}

Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process. Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement. The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments. The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.

During gradual learning, the correct label is supplied after a fixed period passes after its prediction. This \textbf{sliding window} simulation examines accuracy every 100 iterations. Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
%        \caption{Principal components from temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
%        \caption{Principal components from spectral domain features}
%    \end{subfigure}
%    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
%    \label{fig:design:scatter-plot-online}
%\end{figure}

Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly. Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components. Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
%        \caption{Temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
%        \caption{Spectral domain features}
%    \end{subfigure}
%    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
%    \label{fig:design:online-fault-delay-sliding}
%\end{figure}

The \textbf{tumbling window} simulates regular expert visits annotating observations recorded until that moment. Labels for the whole previous window are supplied at once. In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
%        \caption{Temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
%        \caption{Spectral domain features}
%    \end{subfigure}
%    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
%    \label{fig:design:online-fault-delay-tumbling}
%\end{figure}

A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end. Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows. The true labels are unknown. After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.

Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset. In the simulation of missing labels, the equal-length gaps are skipped before another observation is annotated. This approach of choosing samples to annotate without considering their representativeness results in severe harm to predictions.

%\begin{figure}[ht]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
%        \caption{Temporal domain features}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
%        \caption{Spectral domain features}
%    \end{subfigure}
%    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
%    \label{fig:design:online-label-skip}
%\end{figure}

Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}). Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.  More missing labels require recording more observations before the equivalent accuracy is reached.

\chapter{Implementation} \label{section:implementation} 
The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment. Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}).

We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes. The collection of the novel dataset is accompanied by an agreed upon schedule.

\section{Machinery for monitoring}
Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.17\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
        \caption{\footnotesize Fan}
        \label{fig:machine:fan}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.25\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/sensor/copeland-compressor.jpg}
        \caption{\footnotesize Compressor}
        \label{fig:machine:compressor}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/sensor/ksb-pump.jpg}
        \caption{\footnotesize Water pump KSB}
        \label{fig:machine:pump-ksb}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/sensor/sigma-pump.jpg}
        \caption{\footnotesize Water pump Sigma}
        \label{fig:machine:pump-sigma}
    \end{subfigure}
    \caption{Machines dedicated for vibration measurements}
\end{figure}

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the sensor unit development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}). Altogether, two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.

\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station. The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.

The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz). The electric motor provides 400~kW of power (class~\rom{3}).

The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986. It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}). Each pump and motor have 2 bearings. Therefore, there are 4 measurement positions in total.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
        \caption{Vibration rms velocity dashboard}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
        \caption{Vibration spectral analysis dashboard}
    \end{subfigure}
     \caption{KSB Guard cloud monitoring for pumps}
     \label{fig:design:ksb-guard}
\end{figure}

\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}. In addition, we are able to export the entire historical record at hourly intervals. Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).

\section{Sensor hardware and drivers}
In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller. The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 - 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
\textbf{Sensitivity} (mg/LSB)                    & 2.93            & 0.06 - 0.49       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Hardware parameters of previous and proposed sensor units}
\label{tab:design:hw-sensors}
\end{table}

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. It enables us to store all samples from FIFO. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
	\caption{Sensor unit hardware block diagram}
	\label{fig:design:block-diagram-hw}
\end{figure}

The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF SDK\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}. The accelerometer driver is also made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}. Activity diagrams of required firmware functionality are in Appendix~\ref{appendix:technical-docs}.

\section{Firmware}
% Timing is crutial 19ms.
Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

\begin{itemize}
\itemsep0pt
\item begin new recording, 
\item log block of samples into CSV file,
\item finish recording.
\end{itemize}

\begin{figure}[h]
    \centering
	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
\end{figure}

\section{Dataset description}

\section{BVS cloud}

\section{Compressors}

\section{Water pumps}

%\section{Preliminary measurements}
%During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g. 
%
%In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz). The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
%
%
%\begin{figure}[h]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
%        \caption{Acceleration in $\mathrm{m/s}^2$}
%        \label{fig:design:preliminary-acceleration}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
%        \caption{Approximate velocity in $\mathrm{mm/s}$}
%        \label{fig:design:preliminary-velocity}
%    \end{subfigure} 
%    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
%\end{figure} 
%
%Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule. The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks. Envelopes must be tweaked further to achieve more accurate values. The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
%
%\begin{figure}[h]
%    \centering
%    \begin{subfigure}[b]{0.45\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
%		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
%		\label{fig:design:orbital-analysis}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.54\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
%        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
%        \label{fig:design:preliminary-spectrum}
%    \end{subfigure} 
%    \caption{Orbital and spectral methods of vibration signal analysis}
%\end{figure}

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.

In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable. Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning. The features are squished from multiple dimensions using the Euclidian norm. Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset. We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.

Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power. Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%. The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.

The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations. No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively. Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotations can be assigned belatedly or even never. Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions. Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.

The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations. We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards. The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.

Feature selection methods should be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2024-04-28 firmware/main/src/main.c

@@ -100,7 +100,7 @@ void push_trigger(void *args)
                 sensor_enable(&spi, &sensor);
                 vTaskDelay(10 / portTICK_PERIOD_MS);
 
-                esp_timer_start_once(stop_timer, AUTO_TURN_OFF_US);         // TBD
+                esp_timer_start_once(stop_timer, AUTO_TURN_OFF_US);
                 esp_timer_start_periodic(sampler_timer, SAMPLE_RATE);
 
                 led_light(true);

### 2024-04-28 machine-learning/vibrodiagnostics/visualize.py

@@ -10,6 +10,7 @@ from adjustText import adjust_text
 import seaborn as sb
 from sklearn.metrics import silhouette_score
 from sklearn.preprocessing import MinMaxScaler
+from sklearn.preprocessing import PowerTransformer
 from sklearn.decomposition import PCA
 from scipy.signal import freqz
 
@@ -68,8 +69,15 @@ def scatter_features_3d(
         features: list,
         size: tuple = (15, 5),
         boundary=False,
-        model_name='knn'):
+        model_name='knn',
+        power_transform: bool = False):
 
+    if power_transform is True:
+        scaler = PowerTransformer(method='yeo-johnson', standardize=True)
+    else:
+        scaler = MinMaxScaler()
+
+    X = X.copy()
     scaler = MinMaxScaler()
     X[X.columns] = scaler.fit_transform(X)
 
@@ -93,7 +101,11 @@ def scatter_features_3d(
             y_max = q.max() + q.std()
             xx, yy = np.meshgrid(np.arange(x_min, x_max, h),
                                 np.arange(y_min, y_max, h))
-            Z = model.predict(np.c_[xx.ravel(), yy.ravel()])
+            table = np.c_[xx.ravel(), yy.ravel()]
+
+            table = pd.DataFrame(table)
+            table.columns = list(columns)
+            Z = model.predict(table)
             Z = Z.reshape(xx.shape)
             ax[i].pcolormesh(xx, yy, Z, cmap=cmap, alpha=0.5)
 
@@ -119,10 +131,14 @@ def scatter_features_3d_plot(
         Y: pd.DataFrame,
         features: list,
         size: tuple = (8, 8),
-        model_name='knn',
-        boundary=False):
+        model_name: str ='knn',
+        boundary: bool = False,
+        power_transform: bool = False):
 
-    scaler = MinMaxScaler()
+    if power_transform is True:
+        scaler = PowerTransformer(method='yeo-johnson', standardize=True)
+    else:
+        scaler = MinMaxScaler()
     X_scaled = X.copy()
     X_scaled[X_scaled.columns] = scaler.fit_transform(X_scaled)
 

### 2024-04-28 thesis/chapters/02-analysis.tex
Complete assets in thesis

@@
 
-\section{Evaluation datasets} \label{section:evaluation-datasets}
+\section{Datasets of machinery faults} \label{section:evaluation-datasets}
 The experimentally designed features' relevancy is first proven in comparison to comprehensive benchmark datasets.

### 2024-04-28 thesis/chapters/03-design.tex
Complete assets in thesis

@@
 \chapter{Design} \label{chapter:design}
+The design phase sets out to elaborate on the scenarios for experiments with IoT device.
+In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
+Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
 
@@
 % Questions
+% Goals
+% Project risk management
+This thesis aims to provide answers to four research questions.
+The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
+The \textbf{research questions} are:
+\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
+    \itemsep0pt
+	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
+	\item What is the reduction in transmission goodput when chosen signal features are used?
+	\item What accuracy of prediction models can be achieved with various feature subsets?
+	\item How can machinery faults be continuously identified and predicted based upon collected events?
+\end{enumerate}
 
-% Goals
+\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
+\begin{todolist}
+    \itemsep0pt
+    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
+    \item Establish a list of conditions that should be later investigated in the experimental setting.
+    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
+    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
+    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
+    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
+    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
+\end{todolist}
 
-% Risks in the table (probability vs. impact)
-% Project risk management
+However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain.
+The reason is that we did not find a way to represent extracted features more succinctly as a single number.
+We also did not discover a strategy for choosing only the relevant frequency bins.
+The assembled description is retained to lead further research on that topic.
+
+The goals are impacted by certain \textbf{risks} that are assessed and tracked:
+
+\begin{enumerate}[label=R-\arabic*., font=\bfseries]
+\itemsep0pt
+\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
+\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
+\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
+\item Fault modes can not be reliably differentiated and labeled in the dataset.
+\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
+\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
+\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
+\end{enumerate}
 
@@
 
-% Experimental scenarios - domain, dim, bearings, severity
+Dataset scenarios - 24 scenarios
+\begin{itemize}
+\item domain - TD, FD
+\item dim - 1, 3
+\item bearing - A, B, A+B
+\item severity - No, Yes
+\end{itemize}
+
+\begin{figure}[h]
+    \centering
+	\includegraphics[width=\textwidth]{assets/design/pipeline-design.png}
+\end{figure}
 
 % Experiments and metrics:
-% - All features
-% - Feature combinations
-% - Feature selection methods
-% - Incremental learning
-% - Clustering
+\begin{itemize}
+\item Complete feature sets
+\item Feature combinations
+\item Feature selection methods
+\item Incremental learning
+\item Clustering - Silouette score
+\end{itemize}
 
@@
 % Fault counts
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\hline
+\textbf{Bearings} & \textbf{Severity} & \textbf{Misalignment} & \textbf{Imbalance} & \textbf{Cage fault} & \textbf{Ball fault} & \textbf{Outer race fault} & \textbf{Normal} & \textbf{$\Sigma$} \\ \hline
+A                 & No                & 498                   & 333                & 188                 & 186                 & 184                       & 49              & 1438              \\ \hline
+B                 & No                & 498                   & 333                & 188                 & 137                 & 188                       & 49              & 1393              \\ \hline
+A+B               & No                & 996                   & 666                & 376                 & 323                 & 372                       & 98              & 2831              \\ \hline
+A                 & Yes               & 248                   & 188                & 91                  & 87                  & 86                        & 738             & 1438              \\ \hline
+B                 & Yes               & 248                   & 188                & 90                  & 45                  & 90                        & 732             & 1393              \\ \hline
+A+B               & Yes               & 496                   & 376                & 181                 & 132                 & 176                       & 1470            & 2831              \\ \hline
+\end{tabular}
+\end{table}
+
 % Correlation to RPM
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
+    \caption{Correlation of features to RPM over all experiments}
+\end{figure}
+
 % Features Range
+% Mafaulda
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A+B.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A+B.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A+B.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A+B.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature range in MaFaulDa}
+\end{figure}
+
+% PCA plot of labels
+% Clusters with true labels
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{PCA of all features to 2 components}
+\end{figure}
+
 % Time domain waveforms of different faults
-% Bearing defect frequencies
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-TD-A.png}
+        \caption{Time domain}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-faults.png}
+        \caption{Frequency domain (around 2500 rpm)}
+    \end{subfigure}
+    \caption{MaFaulDa}
+\end{figure}
+
 % PCA loading plots
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/PCA-explained-variance.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/PCA-TD-loading-plot.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/PCA-FD-loading-plot.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure} 
+    \caption{PCA explained variance and loading plots (A bearing)}
+\end{figure}
 
@@
 % HW parameters and mention temporary device
+\begin{table}[ht]
+\renewcommand{\arraystretch}{1.2}
+\centering
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Accelerometer}                           & \textbf{IIS3DWB}   \\ \hline
+\textbf{Vendor}                                  & STMicroelectronics \\ \hline
+\textbf{Bus}                                     & SPI                \\ \hline
+\textbf{Axis}                                    & 1 or 3             \\ \hline
+\textbf{Range} (g)                               & $\pm$ 2 - 16      \\ \hline
+\textbf{Bandwidth} (kHz)                          & 5 - 6.3            \\ \hline
+\textbf{Sensitivity} (mg/LSB)                    & 0.06 - 0.49       \\ \hline
+\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 75                 \\ \hline
+\textbf{Microcontroller}                         & ESP32-PoE-ISO      \\ \hline
+\textbf{CPU SoC}                                 & ESP32-WROOM-32     \\ \hline
+\textbf{Output data rate} (kHz)                  & 26.7               \\ \hline
+\textbf{ADC resolution} (bit)                    & 16                 \\ \hline
+\textbf{FIFO}                                    & 3 kB (512 samples) \\ \hline
+\end{tabular}
+\caption{Hardware parameters of previous and proposed sensor units}
+\label{tab:design:hw-sensors}
+\end{table}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
+	\caption{Sensor unit hardware block diagram}
+	\label{fig:design:block-diagram-hw}
+\end{figure}
 
@@
 % Firmware
+% Timing is crutial 19ms.
+Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
+
+\begin{itemize}
+\itemsep0pt
+\item begin new recording, 
+\item log block of samples into CSV file,
+\item finish recording.
+\end{itemize}
+
+\begin{figure}[h]
+    \centering
+	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
+\end{figure}
 
 \section{Industrial equipment}
-% Description of machines
+Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
+
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.17\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
+        \caption{\footnotesize Fan}
+        \label{fig:machine:fan}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.25\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/sensor/copeland-compressor.jpg}
+        \caption{\footnotesize Compressor}
+        \label{fig:machine:compressor}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/sensor/ksb-pump.jpg}
+        \caption{\footnotesize Water pump KSB}
+        \label{fig:machine:pump-ksb}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.31\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/sensor/sigma-pump.jpg}
+        \caption{\footnotesize Water pump Sigma}
+        \label{fig:machine:pump-sigma}
+    \end{subfigure}
+    \caption{Machines dedicated for vibration measurements}
+\end{figure}
+
+\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
+It serves as a test bed during the sensor unit development.
+The sensor is placed on the plastic casing at the back of the drive motor.
+The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
+It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
+
+\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
+Altogether, two units are available in two independent air conditioning units for the data center.
+The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
+Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
+
+\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
+The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
+
+The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
+The electric motor provides 400~kW of power (class~\rom{3}).
+
+The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
+It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}).
+Each pump and motor have 2 bearings.
+Therefore, there are 4 measurement positions in total.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
+        \caption{Vibration rms velocity dashboard}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
+        \caption{Vibration spectral analysis dashboard}
+    \end{subfigure}
+     \caption{KSB Guard cloud monitoring for pumps}
+     \label{fig:design:ksb-guard}
+\end{figure}
+
+\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
+In addition, we are able to export the entire historical record at hourly intervals.
+Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
+
+\section{Data volume savings}
+The apparent advantage of feature discovery is reducing the amount of data downstream.
+Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN).
+The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.
+
+The machinery monitoring system relies on determining several parameters:
+\begin{itemize}
+\itemsep0pt
+\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
+\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
+The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem.
+At a minimum, it should be 15 kHz to 20 kHz.
+\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
+The more critical the machine is, the interval should be shorter.
+The bigger the machine parts, the slower the defect evolves.
+\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp.
+Duration should cover at least 3 windows for spectral estimation.
+The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
+\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
+\end{itemize}
+
+Equation \ref{equ:compression-ratio-features} expresses the lossy compression ratio ($\mathcal{C}$) formula if trend indicators are stored instead of full recording.
+The number of raw channels ($S_{\mathrm{in}}$) can differ from those extracted in features ($S_{\mathrm{out}}$).
+Parameter $D = 0.5$ when we use frequency bins with 1 Hz resolution.
+
+\myequations{Lossy compression ratio with features}
+\begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
+\mathcal{C} = \frac{D \cdot f_s \cdot S_{\mathrm{in}}}{F \cdot S_{\mathrm{out}}}
+\end{align}\end{ceqn}
+
+\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
+If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.
+
+As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
+The station has 3 pumps and 3 electric motors.
+
+A pump and motor pair have 4 bearings together for drive end and non-drive end positions.
+Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
+The sampling frequency at each position is set to \emph{20 kHz}.
+The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
+
+In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution.
+Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
+On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
+Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
+The entire machine's history can be kept in a small flash memory module.
 

### 2024-04-28 thesis/chapters/05-evaluation.tex
Turn outline into section headings
Complete assets in thesis

@@
 \chapter{Evaluation} \label{section:evaluation}
-% Notebooky:
-% MAFAULDA preprocessing - feature extraction and helper
 
-% Vyhodnotenie experimentov - výsledky
+\section{MaFaulDa and k-nearest neighbors}
 
-% Remove anomaly and replace with 2 severity levels - MAFAULDA
+\subsection{Complete feature sets}
+% Confusion matrix
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD-confusion-matrix.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD-confusion-matrix.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Confusion matrix for complete sets of features }
+\end{figure}
 
-% Fan firmware validation
-% Speed estimation - spectroid app, audio
-% Acc from three diffent places
+% Nearest neighbors - how many points have neighbourhood of same class A+B
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/neighborhood.png}
+        \caption{No severity}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/neighborhood-severity.png}
+        \caption{Severity}
+    \end{subfigure}
+    \caption{Neighborhood with same label}
+\end{figure}
 
-% Offline - KNN
-% MafaulDa labeling:
-% Bez aj stĺpce pre B nielen A a zdvojnásob dataset pri A+B
-% A, B, A+B, A-severity-0.5, B-severity-0.5, A+B-severity-0.5
-% main axis / 3 axis
+% Accuracy based on scenario
+% No optimal K - data is noisy
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/all-features/FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Accuracy dependency on k-value}
+\end{figure}
 
-% Explanatory analysis
-	% Korelácia s RPM
-	% Rozsah hodnôt features
-% All features - MaFaulDa: (FD, TD, FD+TD), CWRU: (FD, TD, FD+TD)
-% All combinations - k-values, feature values
-% Feature selection methods - choose best features for all feature values and k-values (in which quantile of distribution of all cominations)
-% 	- Evolution of rank product based on k
-% Scatter plots in 3D and decision boundaries of best features
+\subsection{Feature subset combinations}
+% Boxplots
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-False-False-F3.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-False-False-K5.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-False-False-F3.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-False-False-K5.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \caption{Model accuracy distribution (Bearings A+B, Dim = 3, Severity False)}
+\end{figure}
 
-% DBSCAN - determine parameters (eps, ...), Silhoutte score
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-True-False-F3.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-True-False-K5.png}
+        \caption{Time domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-True-False-F3.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-True-False-K5.png}
+        \caption{Frequency domain features}
+    \end{subfigure}
+    \caption{Model accuracy distribution (Severity True)}
+\end{figure}
 
-% Online - KNN
-% Progressive valuation - severity of how is data sorted
-	% Sorting - postupne rastúca severita u všetkých chýb rovnako
-	% - Náhodne začne vybiehať každá
-% Different kinds of windows
-	% Same experiments as in offline
-	% - All features
-	% - All cominations
-	% - Feature selection methods
+\subsection{Feature selection techniques}
+% Accuracy tables
+% Compare linear complexity accuracy with whole distribution
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
+    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
+\end{figure}
 
-% Uchovať všetky features po neajkú hranicu n generácii
-% Skórovať priebežne cez rank product podľa stability faktora a n-generáciach - koľko generácii si držia poradie a s akým náskokom
+% compare dimensions (table)
+% Please add the following required packages to your document preamble:
+% \usepackage{multirow}
+\begin{table}[]
+\begin{tabular}{|l|rr|rr|r|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{85.56}          & 76.91                              & \multicolumn{1}{r|}{97.58}          & 98.18                              & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{82.83}          & 72.93                              & \multicolumn{1}{r|}{87.88}          & 86.67                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{85.97}          & 78.26                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{81.93}          & 70.88                              & \multicolumn{1}{r|}{80.00}          & 73.94                              & 1                                                   & roll\_off, roll\_on, flux               \\ \hline
+Correlation                           & \multicolumn{1}{r|}{78.85}          & 66.58                              & \multicolumn{1}{r|}{36.36}          & 35.76                              & 1                                                   & roll\_off, kurtosis, skewness           \\ \hline
+F statistic                           & \multicolumn{1}{r|}{81.93}          & 70.88                              & \multicolumn{1}{r|}{80.00}          & 73.94                              & 1                                                   & roll\_on, roll\_off, flux               \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{81.43}          & 69.91                              & \multicolumn{1}{r|}{73.94}          & 64.85                              & 1                                                   & energy, std, roll\_off                  \\ \hline
+All features                          & \multicolumn{1}{r|}{89.34}          & 82.58                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{82.49}          & 71.27                              & \multicolumn{1}{r|}{60.00}          & 57.58                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{88.55}          & 81.07                              & \multicolumn{1}{r|}{100.00}         & 98.79                              & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{83.84}          & 74.88                              & \multicolumn{1}{r|}{78.18}          & 81.21                              & 3                                                   & flux, roll\_off, std                    \\ \hline
+Correlation                           & \multicolumn{1}{r|}{77.58}          & 64.32                              & \multicolumn{1}{r|}{7.27}           & 6.06                               & 3                                                   & flux, skewness, kurtosis                \\ \hline
+F statistic                           & \multicolumn{1}{r|}{80.05}          & 68.02                              & \multicolumn{1}{r|}{30.30}          & 30.30                              & 3                                                   & flux, std, skewness                     \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{84.17}          & 74.63                              & \multicolumn{1}{r|}{80.00}          & 80.61                              & 3                                                   & roll\_off, roll\_on, flux               \\ \hline
+\end{tabular}
+\caption{k=5, f=3, bearing=A+B, severity=False, domain=FD}
+\end{table}
 
-% Analýza vibrácii z čerpadiel
-% kompresory
-% pumpy - ksb
-% pumpy - ksb cloud
-% pumpa - sigma
+\begin{table}[]
+\begin{tabular}{|l|rr|rr|r|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{88.04}          & 81.44                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{84.82}          & 76.42                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & rms, pp, aac                            \\ \hline
+Correlation                           & \multicolumn{1}{r|}{83.86}          & 74.92                              & \multicolumn{1}{r|}{85.00}          & 88.33                              & 1                                                   & rms, pp, shape                          \\ \hline
+F statistic                           & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & rms, pp, aac                            \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & aac, rms, pp                            \\ \hline
+All features                          & \multicolumn{1}{r|}{92.43}          & 88.42                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{87.61}          & 81.66                              & \multicolumn{1}{r|}{96.67}          & 99.17                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{88.06}          & 80.41                              & \multicolumn{1}{r|}{100.00}         & 98.33                              & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{87.03}          & 79.42                              & \multicolumn{1}{r|}{95.00}          & 94.17                              & 3                                                   & pp, rms, zerocross                      \\ \hline
+Correlation                           & \multicolumn{1}{r|}{83.15}          & 73.39                              & \multicolumn{1}{r|}{69.17}          & 68.33                              & 3                                                   & pp, rms, shape                          \\ \hline
+F statistic                           & \multicolumn{1}{r|}{86.21}          & 78.26                              & \multicolumn{1}{r|}{88.33}          & 85.83                              & 3                                                   & pp, rms, aac                            \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{87.03}          & 79.42                              & \multicolumn{1}{r|}{95.00}          & 94.17                              & 3                                                   & zerocross, rms, pp                      \\ \hline
+\end{tabular}
+\caption{k=5, f=3, bearing=A+B, severity=False, domain=TD}
+\end{table}
 
-% Mafaulda
+\begin{table}[h]
+\begin{tabular}{|l|rr|rr|r|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{90.82}          & 84.90                              & \multicolumn{1}{r|}{99.39}          & 98.18                              & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{88.56}          & 82.35                              & \multicolumn{1}{r|}{76.36}          & 76.97                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{90.89}          & 85.56                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & entropy, flux, centroid                 \\ \hline
+Correlation                           & \multicolumn{1}{r|}{88.48}          & 82.26                              & \multicolumn{1}{r|}{74.55}          & 75.76                              & 1                                                   & entropy, flux, noisiness                \\ \hline
+F statistic                           & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & entropy, flux, centroid                 \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & flux, entropy, centroid                 \\ \hline
+All features                          & \multicolumn{1}{r|}{92.67}          & 88.19                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{89.37}          & 83.56                              & \multicolumn{1}{r|}{69.09}          & 67.88                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{91.17}          & 86.97                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, entropy, skewness                 \\ \hline
+Correlation                           & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, entropy, skewness                 \\ \hline
+F statistic                           & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, skewness, entropy                 \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{90.15}          & 84.75                              & \multicolumn{1}{r|}{84.24}          & 86.67                              & 3                                                   & roll\_off, flux, roll\_on               \\ \hline
+\end{tabular}
+\caption{k=5, f=3, bearing=A+B, severity=True, domain=FD}
+\end{table}
 
-% CWRU
+\begin{table}[]
+\begin{tabular}{|l|ll|ll|l|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}              & \multicolumn{2}{l|}{\textbf{Percentile}}            & \multirow{2}{*}{\textbf{Axis}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \textbf{Test} & \multicolumn{1}{l|}{\textbf{Train}} & \textbf{Test} &                                &                                         \\ \hline
+All features                          & \multicolumn{1}{l|}{91.56}          & 86.70         & \multicolumn{1}{l|}{100.00}         & 100.00        & 1                              &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{l|}{89.82}          & 84.25         & \multicolumn{1}{l|}{93.33}          & 95.00         & 1                              &                                         \\ \hline
+Best features                         & \multicolumn{1}{l|}{90.04}          & 84.02         & \multicolumn{1}{l|}{100.00}         & 91.67         & 1                              &                                         \\ \hline
+Rank product                          & \multicolumn{1}{l|}{90.00}          & 83.97         & \multicolumn{1}{l|}{99.17}          & 90.00         & 1                              & zerocross, shape, pp                    \\ \hline
+Correlation                           & \multicolumn{1}{l|}{89.82}          & 83.96         & \multicolumn{1}{l|}{93.33}          & 88.33         & 1                              & shape, zerocross, rms                   \\ \hline
+F statistic                           & \multicolumn{1}{l|}{88.39}          & 82.21         & \multicolumn{1}{l|}{49.17}          & 54.17         & 1                              & pp, rms, shape                          \\ \hline
+Mutual information                    & \multicolumn{1}{l|}{89.84}          & 83.67         & \multicolumn{1}{l|}{95.00}          & 83.33         & 1                              & zerocross, aac, rms                     \\ \hline
+All features                          & \multicolumn{1}{l|}{93.55}          & 90.50         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{l|}{91.66}          & 87.31         & \multicolumn{1}{l|}{99.17}          & 99.17         & 3                              &                                         \\ \hline
+Best features                         & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              &                                         \\ \hline
+Rank product                          & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & shape, zerocross, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & shape, rms, zerocross                   \\ \hline
+F statistic                           & \multicolumn{1}{l|}{89.27}          & 83.54         & \multicolumn{1}{l|}{73.33}          & 67.50         & 3                              & shape, pp, rms                          \\ \hline
+Mutual information                    & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & zerocross, shape, rms                   \\ \hline
+\end{tabular}
+\caption{k=5, f=3, bearing=A+B, severity=True, domain=TD}
+\end{table}
+
+% compare percentiles
+% Feature combinations accuracy
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-accuracy.png}
+        \caption{Accuracy}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
+        \caption{Percentile}
+    \end{subfigure}
+    \caption{Feature selection method choices}
+\end{figure}
+
+% In fsel percentile - mention median from notebook for each method - table
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|r|r|}
+\hline
+\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
+Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
+Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
+F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
+Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
+\end{tabular}
+\end{table}
+
+% Best feature selection methods table (order by best count)
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|r|r|r|}
+\hline
+                            & \multicolumn{1}{l|}{\textbf{Best in scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
+\textbf{Rank product}       & 151                                                     & 69.91                                            & 90.85                                                  \\ \hline
+\textbf{Mutual information} & 46                                                      & 21.30                                            & 90.35                                                  \\ \hline
+\textbf{Correlation}        & 13                                                      & 6.02                                             & 88.88                                                  \\ \hline
+\textbf{F statistic}        & 6                                                       & 2.78                                             & 78.70                                                  \\ \hline
+\textbf{$\Sigma$}           & 216                                                     & 100                                       & -                                                      \\ \hline
+\end{tabular}
+\end{table}
+
+% 2d and 3d plots of best features
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{3 Best features and their ranges}
+\end{figure}
+
+\subsection{Incremental learning}
+% Ordering of severity
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
+        \caption{Order by raising severity}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
+        \caption{Order after relabeing normal class}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
+        \caption{Order of severities}
+    \end{subfigure}
+    \caption{Ordering of faults}
+\end{figure}
+
+% Gradual
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Gradual learning (window = 1, skip = 0)}
+\end{figure}
+
+% Tumbling windows
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Tumbling window in incremental learning}
+\end{figure}
+
+% % Label skips and parts of dataset
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure} 
+    \caption{Skip labels in incremental learning}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD-severity.png}
+        \caption{Time-domain features (severity)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD-severity.png}
+        \caption{Frequency-domain features (severity)}
+    \end{subfigure} 
+    \caption{Skip labels in incremental learning with different sizes}
+\end{figure}
+
+\section{Validation of data logger}
+% Validation of firmware on standing fan - speeds
+\begin{figure}[ht]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
+        \caption{Speed 1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
+        \caption{Speed 2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
+        \caption{Speed 3}
+    \end{subfigure}
+    \caption{Frequency spectrum from sound of standing fan}
+\end{figure}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
+    \caption{Estimation of rotation speed from vibrations}
+\end{figure}
+
+\section{Industrial dataset analysis}
+
+\subsection{Feature ranges}
+% Amplitude histograms
+% Histograms of machinery measurements
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
+        \caption{C1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
+        \caption{C2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
+        \caption{M1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
+        \caption{M2}
+    \end{subfigure} 
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
+        \caption{M3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
+        \caption{P1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
+        \caption{P2}
+    \end{subfigure} 
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
+        \caption{P3}
+    \end{subfigure} 
+    \caption{Histograms}
+\end{figure}
+
+% Box plots of features
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature range in pumps}
+\end{figure}
+
+\subsection{Time-frequency waveforms}
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-motors.png}
+        \caption{Motors frequency domain}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-pumps.png}
+        \caption{Pumps frequency domain}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.33\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-compressors.png}
+        \caption{Compressor frequency domain}
+    \end{subfigure} 
+    \caption{Frequency domain}
+\end{figure}
+
+% Time-frequency spectrum
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT.png}
+        \caption{K3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT.png}
+        \caption{M1-2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT.png}
+        \caption{P1-3}
+    \end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT.png}
+        \caption{P3-3}
+    \end{subfigure}
+	\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/X-P2-Turn-on-Sigma.png}
+        \caption{P2-3 turn off with intererence (X-axis)}
+    \end{subfigure}
+    \caption{Time frequency spectrum}
+\end{figure}
+
+% Low frequencies (under 1KHz)
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT-1kHz.png}
+        \caption{K3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT-1kHz.png}
+        \caption{M1-2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT-1kHz.png}
+        \caption{P1-3}
+    \end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT-1kHz.png}
+        \caption{P3-3}
+    \end{subfigure}
+    \caption{Time frequency spectrum}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
+        \caption{Pump P1 turns off}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
+        \caption{Pump P2 turn on}
+    \end{subfigure}
+\end{figure}
+
+\subsection{Bearing defect frequencies}
+% Domain expert analysis
+% Bearing frequencies table
+\begin{table}[h]
+\centering
+\begin{tabular}{|l|r|r|r|}
+\hline
+\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{Motor \#1}} & \multicolumn{1}{l|}{\textbf{Motor \#2}} & \multicolumn{1}{l|}{\textbf{Pump \#3 \& \#4}} \\ \hline
+\textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
+\textbf{$n$}           & 8                                       & 8                                       & 8                                             \\ \hline
+\textbf{$f_s$}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
+\textbf{$d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
+\textbf{$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
+\textbf{$\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
+\textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
+\textbf{BPFO {[}Hz{]}} & 77.18                                   & 77.91                                   & 77.00                                         \\ \hline
+\textbf{BPFI {[}Hz{]}} & 121.88                                  & 121.16                                  & 122.07                                        \\ \hline
+\textbf{BSF {[}Hz{]}}  & 58.20                                   & 59.97                                   & 57.77                                         \\ \hline
+\textbf{FTF {[}Hz{]}}  & 9.65                                    & 9.74                                    & 9.63                                          \\ \hline
+\end{tabular}
+\end{table}
+
+% Bearing defect frequencies
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/defects/motors.png}
+        \caption{Motors}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/defects/motors-dB.png}
+        \caption{Pumps}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/defects/pumps.png}
+        \caption{Motors}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/defects/pumps-dB.png}
+        \caption{Pumps dB}
+    \end{subfigure}
+\end{figure}
+
+\subsection{Pump long-term monitoring}
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.5\textwidth]{assets/design/sensor/ksb-cloud.jpg}
+    \caption{KSB device}
+\end{figure}
+
+% Total vibration levels - challange - long-live span (5 years)
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p1.png}
+        \caption{Pump P1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/ksb-cloud/p2.png}
+        \caption{Pump P2}
+    \end{subfigure}
+    \caption{Vibration levels}
+\end{figure}
+
+% Reverse engineer of spectra (low resolution)
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.8\textwidth]{assets/results/ksb-cloud/spectrum.png}
+    \caption{Frequency spectrum}
+\end{figure}

### 2024-04-28 thesis/chapters/06-conclusion.tex
Complete assets in thesis

--- 2024-04-13 thesis/chapters/06-conclusion.tex
@@
 \chapter{Conclusion} \label{section:conclusion}  
+%TODO
 In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals.
@@
 The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.
-
-Feature selection methods should be incorporated into incremental learning.
-Hyperparameters shall be adjusted, and the balancing method used to increase model performance.
-The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2024-04-28 thesis/chapters/TEXT.tex
Complete assets in thesis

@@
 \chapter{Design} \label{chapter:design}
-The design phase sets out to elaborate on the scenarios for experiments with IoT device.
-In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
-Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
-
-\section{Research questions}
-This thesis aims to provide answers to four research questions.
-The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
-The \textbf{research questions} are:
-\begin{enumerate}[label=RQ\arabic*., font=\bfseries]
-    \itemsep0pt
-	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
-	\item What is the reduction in transmission goodput when chosen signal features are used?
-	\item What accuracy of prediction models can be achieved with various feature subsets?
-	\item How can machinery faults be continuously identified and predicted based upon collected events?
-\end{enumerate}
-
-\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
-\begin{todolist}
-    \itemsep0pt
-    \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
-    \item Establish a list of conditions that should be later investigated in the experimental setting.
-    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
-    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
-    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
-    \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
-    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
-\end{todolist}
-
-However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain.
-The reason is that we did not find a way to represent extracted features more succinctly as a single number.
-We also did not discover a strategy for choosing only the relevant frequency bins.
-The assembled description is retained to lead further research on that topic.
-
-The goals are impacted by certain \textbf{risks} that are assessed and tracked:
-
-\begin{enumerate}[label=R-\arabic*., font=\bfseries]
-\itemsep0pt
-\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
-\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
-\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
-\item Fault modes can not be reliably differentiated and labeled in the dataset.
-\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
-\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
-\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
-\end{enumerate}
-
-% All features --------------------------------------------------------
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/TD-confusion-matrix.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/FD-confusion-matrix.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \caption{All features confusion matrix}
-\end{figure}
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/FD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{All features accuracy based on k-value}
-\end{figure}
-
-% Standing fan (EDA) --------------------------------------------------------
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
-        \caption{Speed 1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
-        \caption{Speed 2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
-        \caption{Speed 3}
-    \end{subfigure}
-    \caption{Frequency spectrum from sound of standing fan}
-\end{figure}
-
-% Frequency from vibrations
-% Plot
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
-    \caption{Estimation of rotation speed from vibrations}
-\end{figure}
-
-% Clusters with true labels --------------------------------------------------------------
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/PCA-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/PCA-FD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{PCA of all features to 2 components}
-\end{figure}
-
-%TODO fix inverse transform
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{3 Best features and their ranges}
-\end{figure}
-
-% Incremental learning ------------------------------------------------------
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
-        \caption{Order by raising severity}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
-        \caption{Order after relabeing normal class}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
-        \caption{Order of severities}
-    \end{subfigure}
-    \caption{Ordering of faults}
-\end{figure}
-
-% Gradual
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{Gradual learning (window = 1, skip = 0)}
-\end{figure}
-
-% Tumbling windows
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/tumbling-FD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{Tumbling window in incremental learning}
-\end{figure}
-
-% % Label skips and parts of dataset
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure} 
-    \caption{Skip labels in incremental learning}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-label-FD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{Skip labels in incremental learning with different sizes}
-\end{figure}
-
-% Histograms of machinery measurements
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
-        \caption{C1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
-        \caption{C2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
-        \caption{M1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
-        \caption{M2}
-    \end{subfigure} 
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
-        \caption{M3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
-        \caption{P1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
-        \caption{P2}
-    \end{subfigure} 
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
-        \caption{P3}
-    \end{subfigure} 
-    \caption{Histograms}
-\end{figure}
-
-% Correlations to RPM
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
-    \caption{Correlation of features to RPM over all experiments}
-\end{figure}
 
@@
 \end{figure}
-
-% Pumps and compressors
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \caption{Feature range in pumps}
-\end{figure}
-
-% Mafaulda
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A+B.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A+B.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \caption{Feature range in MaFaulDa}
-\end{figure}
-
-% Feature combinations accuracy
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-accuracy.png}
-        \caption{Accuracy}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
-        \caption{Percentile}
-    \end{subfigure}
-    \caption{Feature selection method choices}
-\end{figure}
-
-% In fsel percentile - mention median from notebook for each method - table
-\begin{table}[h]
-\begin{tabular}{|l|r|r|}
-\hline
-\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
-Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
-Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
-F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
-Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-features-A-dim3.png}
-        \caption{Time domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-5-neighbors-A-dim3.png}
-        \caption{Time domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-features-A-dim3.png}
-        \caption{Frequency domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-5-neighbors-A-dim3.png}
-        \caption{Frequency domain features}
-    \end{subfigure}
-    \caption{Model accuracy distribution}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
-    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
-\end{figure}
-
-% Counts table
-
-\begin{table}[h]
-\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-\hline
-\textbf{Bearings} & \textbf{Severity} & \textbf{Misalignment} & \textbf{Imbalance} & \textbf{Cage fault} & \textbf{Ball fault} & \textbf{Outer race fault} & \textbf{Normal} & \textbf{$\Sigma$} \\ \hline
-A                 & No                & 498                   & 333                & 188                 & 186                 & 184                       & 49              & 1438              \\ \hline
-B                 & No                & 498                   & 333                & 188                 & 137                 & 188                       & 49              & 1393              \\ \hline
-A+B               & No                & 996                   & 666                & 376                 & 323                 & 372                       & 98              & 2831              \\ \hline
-A                 & Yes               & 248                   & 188                & 91                  & 87                  & 86                        & 738             & 1438              \\ \hline
-B                 & Yes               & 248                   & 188                & 90                  & 45                  & 90                        & 732             & 1393              \\ \hline
-A+B               & Yes               & 496                   & 376                & 181                 & 132                 & 176                       & 1470            & 2831              \\ \hline
-\end{tabular}
-\end{table}
-
-% Best feature selection methods table (order by best count)
-\begin{table}[]
-\begin{tabular}{|l|r|r|r|}
-\hline
-                            & \multicolumn{1}{l|}{\textbf{Best method for scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
-\textbf{Rank product}       & 151                                                     & 69.91                                            & 90.85                                                  \\ \hline
-\textbf{Mutual information} & 46                                                      & 21.30                                            & 90.35                                                  \\ \hline
-\textbf{Correlation}        & 13                                                      & 6.02                                             & 88.88                                                  \\ \hline
-\textbf{F statistic}        & 6                                                       & 2.78                                             & 78.70                                                  \\ \hline
-\textbf{$\Sigma$}           & 216                                                     & 100.000000                                       & -                                                      \\ \hline
-\end{tabular}
-\end{table}
-
-% Bearing frequencies table
-\begin{table}[h]
-\begin{tabular}{|l|r|r|r|}
-\hline
-\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{Motor \#1}} & \multicolumn{1}{l|}{\textbf{Motor \#2}} & \multicolumn{1}{l|}{\textbf{Pump \#3 \& \#4}} \\ \hline
-\textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
-\textbf{$n$}           & 8                                       & 8                                       & 8                                             \\ \hline
-\textbf{$f_s$}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
-\textbf{$d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
-\textbf{$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
-\textbf{$\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
-\textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
-\textbf{BPFO {[}Hz{]}} & 77.18                                   & 77.91                                   & 77.00                                         \\ \hline
-\textbf{BPFI {[}Hz{]}} & 121.88                                  & 121.16                                  & 122.07                                        \\ \hline
-\textbf{BSF {[}Hz{]}}  & 58.20                                   & 59.97                                   & 57.77                                         \\ \hline
-\textbf{FTF {[}Hz{]}}  & 9.65                                    & 9.74                                    & 9.63                                          \\ \hline
-\end{tabular}
-\end{table}
-
-% Time-frequency spectrum
-% Compare with other pump - same places
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT.png}
-        \caption{K3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT.png}
-        \caption{M1-2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT.png}
-        \caption{P1-3}
-    \end{subfigure}
-    \caption{Time frequency spectrum}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/X-P2-Turn-on-Sigma.png}
-        \caption{P2-3 turn off with intererence (X-axis)}
-    \end{subfigure}
-    \caption{Time frequency spectrum}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
-        \caption{Pump P1 turns off}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
-        \caption{Pump P2 turn on}
-    \end{subfigure}
-\end{figure}
-
-% Dataset scenarios - 24 scenarios
-\begin{itemize}
-\item domain - TD, FD
-\item dim - 1, 3
-\item bearing - A, B, A+B
-\item severity - No, Yes
-\end{itemize}
-
-\clearpage
 
@@
 Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.
-
-\subsection{Data volume savings}
-The apparent advantage of feature discovery is reducing the amount of data downstream.
-Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN).
-The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.
-
-The machinery monitoring system relies on determining several parameters:
-\begin{itemize}
-\itemsep0pt
-\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
-\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
-The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem.
-At a minimum, it should be 15 kHz to 20 kHz.
-\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
-The more critical the machine is, the interval should be shorter.
-The bigger the machine parts, the slower the defect evolves.
-\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp.
-Duration should cover at least 3 windows for spectral estimation.
-The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
-\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
-\end{itemize}
-
-Equation \ref{equ:compression-ratio-features} expresses the lossy compression ratio ($\mathcal{C}$) formula if trend indicators are stored instead of full recording.
-The number of raw channels ($S_{\mathrm{in}}$) can differ from those extracted in features ($S_{\mathrm{out}}$).
-Parameter $D = 0.5$ when we use frequency bins with 1 Hz resolution.
-
-\myequations{Lossy compression ratio with features}
-\begin{ceqn}\begin{align} \label{equ:compression-ratio-features}
-\mathcal{C} = \frac{D \cdot f_s \cdot S_{\mathrm{in}}}{F \cdot S_{\mathrm{out}}}
-\end{align}\end{ceqn}
-
-\textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
-If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.
-
-As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
-The station has 3 pumps and 3 electric motors.
-
-A pump and motor pair have 4 bearings together for drive end and non-drive end positions.
-Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
-The sampling frequency at each position is set to \emph{20 kHz}.
-The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
-
-In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution.
-Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
-On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
-Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
-The entire machine's history can be kept in a small flash memory module.
 
@@
 
-\section{Machinery for monitoring}
-Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.17\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
-        \caption{\footnotesize Fan}
-        \label{fig:machine:fan}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.25\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/sensor/copeland-compressor.jpg}
-        \caption{\footnotesize Compressor}
-        \label{fig:machine:compressor}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/sensor/ksb-pump.jpg}
-        \caption{\footnotesize Water pump KSB}
-        \label{fig:machine:pump-ksb}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/sensor/sigma-pump.jpg}
-        \caption{\footnotesize Water pump Sigma}
-        \label{fig:machine:pump-sigma}
-    \end{subfigure}
-    \caption{Machines dedicated for vibration measurements}
-\end{figure}
-
-\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
-It serves as a test bed during the sensor unit development.
-The sensor is placed on the plastic casing at the back of the drive motor.
-The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
-It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
-
-\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
-Altogether, two units are available in two independent air conditioning units for the data center.
-The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
-Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
-
-\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
-The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
-
-The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
-The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
-The electric motor provides 400~kW of power (class~\rom{3}).
-
-The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
-It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}).
-Each pump and motor have 2 bearings.
-Therefore, there are 4 measurement positions in total.
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/ksb-guard-rms.png}
-        \caption{Vibration rms velocity dashboard}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-    		\centering
-        \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
-        \caption{Vibration spectral analysis dashboard}
-    \end{subfigure}
-     \caption{KSB Guard cloud monitoring for pumps}
-     \label{fig:design:ksb-guard}
-\end{figure}
-
-\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
-In addition, we are able to export the entire historical record at hourly intervals.
-Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
-
 \section{Sensor hardware and drivers}
@@
 The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
-
-\begin{table}[ht]
-\renewcommand{\arraystretch}{1.2}
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
-\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
-\textbf{Bus}                                     & Analog           & SPI                \\ \hline
-\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
-\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 - 16      \\ \hline
-\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
-\textbf{Sensitivity} (mg/LSB)                    & 2.93            & 0.06 - 0.49       \\ \hline
-\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
-\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
-\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
-\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
-\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
-\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
-\end{tabular}
-\caption{Hardware parameters of previous and proposed sensor units}
-\label{tab:design:hw-sensors}
-\end{table}
 
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
-	\caption{Sensor unit hardware block diagram}
-	\label{fig:design:block-diagram-hw}
-\end{figure}
-
 The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF SDK\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
@@
 Activity diagrams of required firmware functionality are in Appendix~\ref{appendix:technical-docs}.
-
-\section{Firmware}
-% Timing is crutial 19ms.
-Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
-
-\begin{itemize}
-\itemsep0pt
-\item begin new recording, 
-\item log block of samples into CSV file,
-\item finish recording.
-\end{itemize}
-
-\begin{figure}[h]
-    \centering
-	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
-\end{figure}
-
-\section{Dataset description}
-
-\section{BVS cloud}
-
-\section{Compressors}
-
-\section{Water pumps}
-
-%\section{Preliminary measurements}
-%During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals.
-Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}.
-The acceleration rarely exceeds 1~g.
-%
-%In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz).
-The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
-%
-%
-%\begin{figure}[h]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
-%        \caption{Acceleration in $\mathrm{m/s}^2$}
-%        \label{fig:design:preliminary-acceleration}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
-%        \caption{Approximate velocity in $\mathrm{mm/s}$}
-%        \label{fig:design:preliminary-velocity}
-%    \end{subfigure} 
-%    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
-%\end{figure} 
-%
-%Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule.
-The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks.
-Envelopes must be tweaked further to achieve more accurate values.
-The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
-%
-%\begin{figure}[h]
-%    \centering
-%    \begin{subfigure}[b]{0.45\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
-%		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
-%		\label{fig:design:orbital-analysis}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.54\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
-%        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
-%        \label{fig:design:preliminary-spectrum}
-%    \end{subfigure} 
-%    \caption{Orbital and spectral methods of vibration signal analysis}
-%\end{figure}
-
-\chapter{Conclusion} \label{section:conclusion}  
-In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals.
-The goal is to enable timely fault detection of machinery parts with as little input data as possible.
-For that purpose, we answer four research questions.
-
-Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343).
-These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.
-
-In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable.
-Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning.
-The features are squished from multiple dimensions using the Euclidian norm.
-Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset.
-We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.
-
-Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power.
-Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%.
-The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.
-
-The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations.
-No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively.
-Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.
-
-The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables.
-Annotations can be assigned belatedly or even never.
-Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
-The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.
-
-Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions.
-Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.
-
-The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations.
-We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards.
-The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.
-
-Feature selection methods should be incorporated into incremental learning.
-Hyperparameters shall be adjusted, and the balancing method used to increase model performance.
-The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2024-04-28 machine-learning/vibrodiagnostics/models.py

@@ -275,7 +275,7 @@ def feature_selection_accuracies(
         ('mi', 'Mutual information')
     ]
     for pos, (name, title) in enumerate(fsel_methods):
-        features = find_best_subset(X, Y, name, members=number_of_features)
+        features = find_best_subset(X, Y, name, members=number_of_features)   # TODO: fix
         y_best = kfold_accuracy(
             X[list(features)], Y, k_neighbors, kfolds, MODEL_TYPE,
             power_transform=power_transform

### 2024-04-29 thesis/chapters/02-analysis.tex
Use bearing A instead of A+B

@@
 \textit{Shannon entropy}      & $H(X) = - \sum_{i} P(X = x_i) \cdot \ln(P(X = x_i)) $                                                  \\ \hline
-\textit{Spectral negentropy}      & $\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}} \cdot \ln\left(\frac{E(k, f, \Delta f)^2}{\frac{1}{N} \sum_{k=0}^{N-1} E(k, f, \Delta f)^2}\right)$                                                \\ \hline
+\textit{Spectral negentropy}      & $\Delta I_E(f, \Delta f) = \sum_{k = 0}^{N - 1}{p \cdot \ln(p); p = \frac{\mathrm{SES}^2}{\frac{1}{N} \sum_{k=0}^{N-1} \mathrm{SES}^2}}$                                                \\ \hline
 \end{tabular}
@@
 The larger \emph{spectral negentropy} suggests more fault-induced impulses.
-$E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
-
+The squared envelope spectrum (SES) is interpreted as $E(k, f, \Delta f)$ which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.
+
+\subsection{Features in harmonic frequencies}
 If a single principal frequency exists, it can be determined by maximum likelihood estimation.
@@
 
+\myequations{Harmonic series search criterion}
+\begin{ceqn}\begin{align}
+v_i^{(r)} = \frac{v_j}{\min{|v_j - r \cdot v_i|}}
+\label{equ:harmonic-search}
+\end{align}\end{ceqn}
+
 Multiple harmonic series and the sidebands can be separated into a discrete set of frequency components, each with a central frequency, uncertainty, and amplitude $C_i(v_i, \Delta v_i, A_i)$ by an exhaustive search algorithm.
@@
 
-\myequations{Harmonic series search criterion}
-\begin{ceqn}\begin{align}
-v_i^{(r)} = \frac{v_j}{\min{|v_j - r \cdot v_i|}}
-\label{equ:harmonic-search}
-\end{align}\end{ceqn}
-
 \subsection{Bearing defect frequencies}
+
 %TODO n = number of balls, d - average of outer ring diameter and outer ring, f_s - rotation speed, beta - contact angle - ball bearings close to 0
 
+% Rolling element bearings have four very important components, two circular races, between which the rolling elements—rollers, tapered rollers, or spherical balls—are held.
+The fourth important element in a rolling element bearing is the cage or the separator.
+The cage ensures that no two rolling elements come in contact with each other
+% The bearing vibration is further complicated when the radial loads on the bearing change during rotation of the shaft, and defects like impurities or scratches, pits, and so on, develop on the bearing element surfaces
+% The characteristic bearing defect frequencies for the different rolling elements of bearings can be determined
+
 \begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{assets/analysis/bearing-parts.jpg}
+    \includegraphics[width=0.7\textwidth]{assets/analysis/bearing-parts.jpg}
     \caption{Bearing parts~\cite{lu_what_is_ball_bearing_2023}}
@@
 Adaptive spectral segmentation is needed to extract separate intrinsic mode functions (IMF).
-
-\subsection{Empirical wavelet features}
-\textbf{Empirical Wavelet Transform} (EWT) constructs adaptive bandpass filters with Meyer wavelet.
-The inner product of the signal with the scaling function $\hat{\phi_n}$ obtains the approximation coefficients and the inner product with the wavelet function results in detail coefficients.
-
-The normalized frequency axis in range $\omega \in [0, \pi]$ is divided by split points $\omega_0, \dots, \omega_N$ where $\omega_n = f_n \cdot 2 \pi\;/\;f_s$ (Fig.~\ref{fig:ewt-spectrum-segmentation}).
-Each segment is bounded between $[\omega_{n-1}, \omega_n]$ with a transition phase of width $2\tau_n$ and polynomial transition function $\beta(x)$.
-A tight frame set of empirical wavelets is built by setting the transition phase proportional to the band boundary: $\tau_n = \lambda \omega_n$, and proportional constant must obey constrain: $\lambda = \min\left(\frac{\omega_{n+1} - \omega_n}{\omega_{n+1} + \omega_n}\right)$.
-The $N$ boundaries defining different portions of the Fourier spectrum are placed at the center between two consecutive local maxima~\cite{gilles_empirical_2013}.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.9\textwidth]{assets/analysis/EWT.png}
-    \caption{Empirical wavelet segmentation of Fourier spectrum~\cite{gilles_empirical_2013}}
-    \label{fig:ewt-spectrum-segmentation}
-\end{figure}
-
-The drawback of EWT is improper segmentation in noisy and non-stationary signals, producing too many uninformative partitions of the spectrum.
-The solutions we discuss fall into two groups that apply improvements before or after the wavelet transformation step.
-
-A combination of \textbf{Maximum Correlated Kurtosis Deconvolution} and improved EWT (MKCD-EWT) favors periodic impacts by dynamically constructing an optimal FIR filter that maximizes the correlation kurtosis of the signal.
-The envelope curve smooths the amplitude spectrum by linear interpolation (Fig.~\ref{fig:mkcd-ewt-segmentation}).
-The threshold accounting for desired SNR modifies the envelope when more than $n$ components are discovered ($A_h$ is maximal amplitude and $A_l$ is minimal amplitude): $\lambda = A_l + \frac{C}{\mathrm{SNR}}(A_h - A_l)$.
-\emph{Squared envelope spectrum} and \emph{Teager energy operator spectrum} are computed as fault features for the IMF with the highest kurtosis~\cite{li_fault_2019}.
-
-The segmentation boundary detection can also be accomplished on the spectral envelope consisting of \textbf{Piecewise Cubic Hermite Interpolating Polynomial} (PCHIP-EWT) instead of scanning the Fourier spectrum directly (Fig.~\ref{fig:pchip-ewt-segmentation}).
-Divisions of the upper cut-off frequency are kept if local power indicates a subband with useful information ($p_i(f) \geq \lambda$)  as in the case of an abrupt level change.
-Local power is the ratio of $n$th local envelope maximum and the difference between indexes of its adjacent local minima:  $p_i(f) = K_{max(i)(f)} \;/\;\left(f_{k_{min(i+1)}} - f_{k_{min(i)}}\right)$.
-The best $\lambda$ is set experimentally~\cite{zhuang_improved_2020}.
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/analysis/MKCD-EWT.png}
-        \caption{MKCD-EWT~\cite{li_fault_2019}}
-        \label{fig:mkcd-ewt-segmentation}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/analysis/PCHIP-EWT.png}
-        \caption{PCHIP-EWT~\cite{zhuang_improved_2020}}
-        \label{fig:pchip-ewt-segmentation}
-    \end{subfigure}
-    \caption{Illustration of improved EWT spectral segmentations}
-\end{figure}
-
-The inspiration for filtering on an adaptive basis comes from \textbf{Empirical mode decomposition} (EMD).
-This procedure locates local maxima and minima in the time waveform that are interpolated with cubic splines to form signal envelopes.
-The average of the upper and lower envelope is repeatedly subtracted from the residuals recovering the higher order and lower frequency IMFs~\cite{wang_computational_2014}.
-
-The EMD is not recommended for practical applications because it suffers from mode mixing problems and lacks rigid theoretical foundations.
-Many improvements based on the mode sifting process, such as Local Mean Decomposition (LMD), Ensemble Empirical Mode Decomposition (EEMD), Concealed Component Decomposition (CCD)~\cite{tiwari_novel_2021}, and Empirical Wavelet Transform, have been devised as being capable of estimating more reasonable modes.
 
@@
 
-\textbf{Half-Space Tree} (HS-Tree) stands upon the concept of Isolation forest.
-It assumes that random splitting of each axis in the feature space will isolate outliers to their separate divisions sooner than non-deviant observations~\cite{gervasi_anomaly_2020, torres_automatic_2022}.
-This ensemble of trees is better suited for batch setting.
-HS-Tree stands out in adapting to changing streams because it is trained solely on normal data, requires constant memory, and is faster than density-based methods~\cite{tan_fast_2011}.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.8\textwidth]{assets/analysis/HS-Tree.png}
-    \caption{Half-space tree~\cite{tan_fast_2011}}
-\end{figure}
-
-A full binary tree is built before the novelty detection begins by splitting tree nodes along the divisions in the randomly chosen perpendicular planes.
-The node stores its depth, value limits of the axis bisection (half-space), count of contained data points (mass) in two consecutive windows, and links to both child nodes~\cite{tan_fast_2011}.
+%\cite{tan_fast_2011}.
 

### 2024-04-29 thesis/chapters/03-design.tex
Use bearing A instead of A+B

@@
 \section{Research questions}
-% Questions
-% Goals
-% Project risk management
 This thesis aims to provide answers to four research questions.
@@
 We also did not discover a strategy for choosing only the relevant frequency bins.
-The assembled description is retained to lead further research on that topic.
-
-The goals are impacted by certain \textbf{risks} that are assessed and tracked:
-
-\begin{enumerate}[label=R-\arabic*., font=\bfseries]
-\itemsep0pt
-\item Machines in the real environment will not be available for vibration measurements. \\ \emph{Mitigation}: Contact and establish collaboration with alternative partners. 
-\item Repeated measurements will not be consistent, and a lack of data is obtained from different classes.
-\\ \emph{Mitigation}: Prepare a plan for measurements and photo document sensor placements. 
-\item Fault modes can not be reliably differentiated and labeled in the dataset.
-\\ \emph{Mitigation}: Consult domain experts and machine maintenance staff.
-\item Suggestions made by exploring the MaFaulDa dataset will not be applicable in practice. \\
-\emph{Mitigation}: When applicable, apply the same procedures as in MaFaulDa to measured data.
-\end{enumerate}
 
@@
 \section{Exploratory data analysis of MaFaulDa}
-% Fault counts
 \begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
 \centering
-\begin{tabular}{|l|l|l|l|l|l|l|l|l|}
+\begin{tabular}{|lr|r|r|r|r|r|r|}
 \hline
-\textbf{Bearings} & \textbf{Severity} & \textbf{Misalignment} & \textbf{Imbalance} & \textbf{Cage fault} & \textbf{Ball fault} & \textbf{Outer race fault} & \textbf{Normal} & \textbf{$\Sigma$} \\ \hline
-A                 & No                & 498                   & 333                & 188                 & 186                 & 184                       & 49              & 1438              \\ \hline
-B                 & No                & 498                   & 333                & 188                 & 137                 & 188                       & 49              & 1393              \\ \hline
-A+B               & No                & 996                   & 666                & 376                 & 323                 & 372                       & 98              & 2831              \\ \hline
-A                 & Yes               & 248                   & 188                & 91                  & 87                  & 86                        & 738             & 1438              \\ \hline
-B                 & Yes               & 248                   & 188                & 90                  & 45                  & 90                        & 732             & 1393              \\ \hline
-A+B               & Yes               & 496                   & 376                & 181                 & 132                 & 176                       & 1470            & 2831              \\ \hline
+\multicolumn{2}{|l|}{\textbf{Bearing}}                                            & \multicolumn{1}{l|}{A}  & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}  & \multicolumn{1}{l|}{A}   & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}   \\ \hline
+\multicolumn{2}{|l|}{\textbf{Relabel by severity}}                                & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{No}  & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} \\ \hline
+\multicolumn{1}{|l|}{\multirow{6}{*}{\textbf{Fault}}} & \textbf{misalignment}     & 498                     & 996                      & 498                     & 248                      & 496                      & 248                      \\ \cline{2-8}
+\multicolumn{1}{|l|}{}                                & \textbf{imbalance}        & 333                     & 666                      & 333                     & 188                      & 376                      & 188                      \\ \cline{2-8}
+\multicolumn{1}{|l|}{}                                & \textbf{cage fault}       & 188                     & 376                      & 188                     & 91                       & 181                      & 90                       \\ \cline{2-8}
+\multicolumn{1}{|l|}{}                                & \textbf{ball fault}       & 186                     & 323                      & 137                     & 87                       & 132                      & 45                       \\ \cline{2-8}
+\multicolumn{1}{|l|}{}                                & \textbf{outer race fault} & 184                     & 372                      & 188                     & 86                       & 176                      & 90                       \\ \cline{2-8}
+\multicolumn{1}{|l|}{}                                & \textbf{normal}           & 49                      & 98                       & 49                      & 738                      & 1470                     & 732                      \\ \hline
+\multicolumn{2}{|l|}{$\Sigma$}                                                    & \textbf{1438}           & \textbf{2831}            & \textbf{1393}           & \textbf{1438}            & \textbf{2831}            & \textbf{1393}            \\ \hline
 \end{tabular}
+\caption{Number of rows in MaFaulDa according to label}
 \end{table}
@@
 
+% Feature correlations
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/corr-A-3-TD.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/corr-A-3-FD.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{Feature correlations in MaFaulDa}
+\end{figure}
+
 % Features Range
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A+B.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A.png}
         \caption{Time-domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A+B.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
         \caption{Frequency-domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A+B.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
         \caption{Time-domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A+B.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A.png}
         \caption{Frequency-domain features}
@@
 % HW parameters and mention temporary device
-\begin{table}[ht]
+\begin{table}[h]
 \renewcommand{\arraystretch}{1.2}
@@
 \end{tabular}
-\caption{Hardware parameters of previous and proposed sensor units}
+\caption{Hardware parameters of accelerometer data logger}
 \label{tab:design:hw-sensors}

### 2024-04-29 thesis/chapters/05-evaluation.tex
Use bearing A instead of A+B

@@
 
-\section{MaFaulDa and k-nearest neighbors}
+\section{MaFaulDa in k-nearest neighbors}
 
@@
     \end{subfigure}
-    \caption{Confusion matrix for complete sets of features }
+    \caption{Confusion matrix for complete sets of features}
 \end{figure}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-False-False-F3.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-False-False-F3.png}
         \caption{Time domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-False-False-K5.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-False-False-K5.png}
         \caption{Time domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-False-False-F3.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-False-False-F3.png}
         \caption{Frequency domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-False-False-K5.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-False-False-K5.png}
         \caption{Frequency domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-True-False-F3.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-True-False-F3.png}
         \caption{Time domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A+B-True-False-K5.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-True-False-K5.png}
         \caption{Time domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-True-False-F3.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-True-False-F3.png}
         \caption{Frequency domain features}
@@
     \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A+B-True-False-K5.png}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-True-False-K5.png}
         \caption{Frequency domain features}
@@
 % Compare linear complexity accuracy with whole distribution
+
 \begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3.png}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-TD-train.png}
+        \caption{Time domain features (train)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-TD-test.png}
+        \caption{Time domain features (test)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-FD-train.png}
+        \caption{Frequency domain features (train)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-FD-test.png}
+        \caption{Frequency domain features (test)}
+    \end{subfigure}
     \caption{Model distibution with feature selection methods (k = 5, f = 3)}
@@
 % compare dimensions (table)
-% Please add the following required packages to your document preamble:
-% \usepackage{multirow}
-\begin{table}[]
+\begin{table}[h]
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{|l|rr|rr|r|l|}
@@
                                       & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{85.56}          & 76.91                              & \multicolumn{1}{r|}{97.58}          & 98.18                              & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{82.83}          & 72.93                              & \multicolumn{1}{r|}{87.88}          & 86.67                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{85.97}          & 78.26                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{81.93}          & 70.88                              & \multicolumn{1}{r|}{80.00}          & 73.94                              & 1                                                   & roll\_off, roll\_on, flux               \\ \hline
-Correlation                           & \multicolumn{1}{r|}{78.85}          & 66.58                              & \multicolumn{1}{r|}{36.36}          & 35.76                              & 1                                                   & roll\_off, kurtosis, skewness           \\ \hline
-F statistic                           & \multicolumn{1}{r|}{81.93}          & 70.88                              & \multicolumn{1}{r|}{80.00}          & 73.94                              & 1                                                   & roll\_on, roll\_off, flux               \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{81.43}          & 69.91                              & \multicolumn{1}{r|}{73.94}          & 64.85                              & 1                                                   & energy, std, roll\_off                  \\ \hline
-All features                          & \multicolumn{1}{r|}{89.34}          & 82.58                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{82.49}          & 71.27                              & \multicolumn{1}{r|}{60.00}          & 57.58                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{88.55}          & 81.07                              & \multicolumn{1}{r|}{100.00}         & 98.79                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{83.84}          & 74.88                              & \multicolumn{1}{r|}{78.18}          & 81.21                              & 3                                                   & flux, roll\_off, std                    \\ \hline
-Correlation                           & \multicolumn{1}{r|}{77.58}          & 64.32                              & \multicolumn{1}{r|}{7.27}           & 6.06                               & 3                                                   & flux, skewness, kurtosis                \\ \hline
-F statistic                           & \multicolumn{1}{r|}{80.05}          & 68.02                              & \multicolumn{1}{r|}{30.30}          & 30.30                              & 3                                                   & flux, std, skewness                     \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{84.17}          & 74.63                              & \multicolumn{1}{r|}{80.00}          & 80.61                              & 3                                                   & roll\_off, roll\_on, flux               \\ \hline
+All features                          & \multicolumn{1}{r|}{92.52}          & 87.68                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{87.90}          & 79.42                              & \multicolumn{1}{r|}{96.67}          & 96.67                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{89.70}          & 81.96                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & zerocross, shape, pp                    \\ \hline
+Correlation                           & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & shape, zerocross, pp                    \\ \hline
+F statistic                           & \multicolumn{1}{r|}{86.95}          & 78.65                              & \multicolumn{1}{r|}{88.33}          & 95.00                              & 1                                                   & pp, zerocross, aac                      \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{86.98}          & 78.28                              & \multicolumn{1}{r|}{89.17}          & 94.17                              & 1                                                   & zerocross, shape, rms                   \\ \hline
+All features                          & \multicolumn{1}{r|}{96.03}          & 92.80                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{91.20}          & 84.67                              & \multicolumn{1}{r|}{95.00}          & 93.33                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{91.93}          & 85.47                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & zerocross, pp, rms                      \\ \hline
+Correlation                           & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, shape, pp                    \\ \hline
+F statistic                           & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & rms, pp, zerocross                      \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, pp, shape                    \\ \hline
 \end{tabular}
-\caption{k=5, f=3, bearing=A+B, severity=False, domain=FD}
+\end{adjustbox}
+\caption{k=5, f=3, bearing=A, severity=False, domain=TD}
 \end{table}
 
-\begin{table}[]
+\begin{table}[h]
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{|l|rr|rr|r|l|}
@@
                                       & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{88.04}          & 81.44                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{84.82}          & 76.42                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & rms, pp, aac                            \\ \hline
-Correlation                           & \multicolumn{1}{r|}{83.86}          & 74.92                              & \multicolumn{1}{r|}{85.00}          & 88.33                              & 1                                                   & rms, pp, shape                          \\ \hline
-F statistic                           & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & rms, pp, aac                            \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{85.72}          & 77.29                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & aac, rms, pp                            \\ \hline
-All features                          & \multicolumn{1}{r|}{92.43}          & 88.42                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{87.61}          & 81.66                              & \multicolumn{1}{r|}{96.67}          & 99.17                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{88.06}          & 80.41                              & \multicolumn{1}{r|}{100.00}         & 98.33                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{87.03}          & 79.42                              & \multicolumn{1}{r|}{95.00}          & 94.17                              & 3                                                   & pp, rms, zerocross                      \\ \hline
-Correlation                           & \multicolumn{1}{r|}{83.15}          & 73.39                              & \multicolumn{1}{r|}{69.17}          & 68.33                              & 3                                                   & pp, rms, shape                          \\ \hline
-F statistic                           & \multicolumn{1}{r|}{86.21}          & 78.26                              & \multicolumn{1}{r|}{88.33}          & 85.83                              & 3                                                   & pp, rms, aac                            \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{87.03}          & 79.42                              & \multicolumn{1}{r|}{95.00}          & 94.17                              & 3                                                   & zerocross, rms, pp                      \\ \hline
+All features                          & \multicolumn{1}{r|}{88.15}          & 79.99                              & \multicolumn{1}{r|}{99.39}          & 98.18                              & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{83.83}          & 74.43                              & \multicolumn{1}{r|}{77.58}          & 83.03                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{88.93}          & 81.86                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & entropy, roll\_off, flux                \\ \hline
+Correlation                           & \multicolumn{1}{r|}{80.54}          & 68.01                              & \multicolumn{1}{r|}{33.33}          & 31.52                              & 1                                                   & kurtosis, roll\_off, skewness           \\ \hline
+F statistic                           & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & flux, entropy, roll\_off                \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{88.11}          & 80.96                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, roll\_off            \\ \hline
+All features                          & \multicolumn{1}{r|}{93.67}          & 88.45                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{86.76}          & 78.51                              & \multicolumn{1}{r|}{64.85}          & 70.91                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{92.86}          & 87.52                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
+Correlation                           & \multicolumn{1}{r|}{84.55}          & 75.10                              & \multicolumn{1}{r|}{38.18}          & 42.42                              & 3                                                   & roll\_off, negentropy, skewness         \\ \hline
+F statistic                           & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{90.73}          & 83.60                              & \multicolumn{1}{r|}{94.55}          & 94.55                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
 \end{tabular}
-\caption{k=5, f=3, bearing=A+B, severity=False, domain=TD}
+\end{adjustbox}
+\caption{k=5, f=3, bearing=A, severity=False, domain=FD}
 \end{table}
@@
 \begin{table}[h]
+\begin{adjustbox}{width=\textwidth}
 \begin{tabular}{|l|rr|rr|r|l|}
@@
                                       & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{90.82}          & 84.90                              & \multicolumn{1}{r|}{99.39}          & 98.18                              & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{88.56}          & 82.35                              & \multicolumn{1}{r|}{76.36}          & 76.97                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{90.89}          & 85.56                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & entropy, flux, centroid                 \\ \hline
-Correlation                           & \multicolumn{1}{r|}{88.48}          & 82.26                              & \multicolumn{1}{r|}{74.55}          & 75.76                              & 1                                                   & entropy, flux, noisiness                \\ \hline
-F statistic                           & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & entropy, flux, centroid                 \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{89.65}          & 84.22                              & \multicolumn{1}{r|}{93.94}          & 96.06                              & 1                                                   & flux, entropy, centroid                 \\ \hline
-All features                          & \multicolumn{1}{r|}{92.67}          & 88.19                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{89.37}          & 83.56                              & \multicolumn{1}{r|}{69.09}          & 67.88                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{91.17}          & 86.97                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, entropy, skewness                 \\ \hline
-Correlation                           & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, entropy, skewness                 \\ \hline
-F statistic                           & \multicolumn{1}{r|}{88.89}          & 82.69                              & \multicolumn{1}{r|}{55.76}          & 53.94                              & 3                                                   & flux, skewness, entropy                 \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{90.15}          & 84.75                              & \multicolumn{1}{r|}{84.24}          & 86.67                              & 3                                                   & roll\_off, flux, roll\_on               \\ \hline
+All features                          & \multicolumn{1}{r|}{94.99}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{92.67}          & 89.20                              & \multicolumn{1}{r|}{84.17}          & 87.50                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{93.99}          & 91.31                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
+F statistic                           & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{91.31}          & 86.99                              & \multicolumn{1}{r|}{67.50}          & 67.50                              & 1                                                   & zerocross, shape, impulse               \\ \hline
+All features                          & \multicolumn{1}{r|}{96.42}          & 94.76                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{94.63}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.58}          & 91.71                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & zerocross, shape, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & zerocross, shape, rms                   \\ \hline
+F statistic                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & shape, zerocross, rms                   \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{91.90}          & 88.51                              & \multicolumn{1}{r|}{72.50}          & 76.67                              & 3                                                   & zerocross, shape, clearance             \\ \hline
 \end{tabular}
-\caption{k=5, f=3, bearing=A+B, severity=True, domain=FD}
+\end{adjustbox}
+\caption{k=5, f=3, bearing=A, severity=True, domain=TD}
 \end{table}
 
-\begin{table}[]
-\begin{tabular}{|l|ll|ll|l|l|}
+\begin{table}[h]
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|l|rr|rr|r|l|}
 \hline
-\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}              & \multicolumn{2}{l|}{\textbf{Percentile}}            & \multirow{2}{*}{\textbf{Axis}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
-                                      & \multicolumn{1}{l|}{\textbf{Train}} & \textbf{Test} & \multicolumn{1}{l|}{\textbf{Train}} & \textbf{Test} &                                &                                         \\ \hline
-All features                          & \multicolumn{1}{l|}{91.56}          & 86.70         & \multicolumn{1}{l|}{100.00}         & 100.00        & 1                              &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{l|}{89.82}          & 84.25         & \multicolumn{1}{l|}{93.33}          & 95.00         & 1                              &                                         \\ \hline
-Best features                         & \multicolumn{1}{l|}{90.04}          & 84.02         & \multicolumn{1}{l|}{100.00}         & 91.67         & 1                              &                                         \\ \hline
-Rank product                          & \multicolumn{1}{l|}{90.00}          & 83.97         & \multicolumn{1}{l|}{99.17}          & 90.00         & 1                              & zerocross, shape, pp                    \\ \hline
-Correlation                           & \multicolumn{1}{l|}{89.82}          & 83.96         & \multicolumn{1}{l|}{93.33}          & 88.33         & 1                              & shape, zerocross, rms                   \\ \hline
-F statistic                           & \multicolumn{1}{l|}{88.39}          & 82.21         & \multicolumn{1}{l|}{49.17}          & 54.17         & 1                              & pp, rms, shape                          \\ \hline
-Mutual information                    & \multicolumn{1}{l|}{89.84}          & 83.67         & \multicolumn{1}{l|}{95.00}          & 83.33         & 1                              & zerocross, aac, rms                     \\ \hline
-All features                          & \multicolumn{1}{l|}{93.55}          & 90.50         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{l|}{91.66}          & 87.31         & \multicolumn{1}{l|}{99.17}          & 99.17         & 3                              &                                         \\ \hline
-Best features                         & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              &                                         \\ \hline
-Rank product                          & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & shape, zerocross, rms                   \\ \hline
-Correlation                           & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & shape, rms, zerocross                   \\ \hline
-F statistic                           & \multicolumn{1}{l|}{89.27}          & 83.54         & \multicolumn{1}{l|}{73.33}          & 67.50         & 3                              & shape, pp, rms                          \\ \hline
-Mutual information                    & \multicolumn{1}{l|}{91.91}          & 87.77         & \multicolumn{1}{l|}{100.00}         & 100.00        & 3                              & zerocross, shape, rms                   \\ \hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{94.17}          & 90.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 1                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{91.49}          & 87.78                              & \multicolumn{1}{r|}{80.00}          & 86.67                              & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.13}          & 91.37                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
+Correlation                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, flux, centroid                 \\ \hline
+F statistic                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & centroid, entropy, flux                 \\ \hline
+All features                          & \multicolumn{1}{r|}{95.20}          & 93.20                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{92.14}          & 88.84                              & \multicolumn{1}{r|}{69.09}          & 73.94                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.64}          & 91.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 3                                                   &                                         \\ \hline
+Rank product                          & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
+Correlation                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
+F statistic                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, flux, centroid                 \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{93.32}          & 90.67                              & \multicolumn{1}{r|}{90.91}          & 91.52                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
 \end{tabular}
-\caption{k=5, f=3, bearing=A+B, severity=True, domain=TD}
+\end{adjustbox}
+\caption{k=5, f=3, bearing=A, severity=True, domain=FD}
 \end{table}
@@
 \subsection{Feature ranges}
-% Amplitude histograms
+% Amplitude histograms - 20m/s^2, 40m/s^2, 150m/s^
 % Histograms of machinery measurements
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/C1.png}
-        \caption{C1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/C2.png}
-        \caption{C2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M1.png}
-        \caption{M1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M2.png}
-        \caption{M2}
-    \end{subfigure} 
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/M3.png}
-        \caption{M3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P1.png}
-        \caption{P1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P2.png}
-        \caption{P2}
-    \end{subfigure} 
-    \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/histograms/P3.png}
-        \caption{P3}
-    \end{subfigure} 
-    \caption{Histograms}
-\end{figure}
 
@@
     \centering
-    \begin{subfigure}[b]{0.33\textwidth}
+    \begin{subfigure}[b]{0.32\textwidth}
         \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-motors.png}
-        \caption{Motors frequency domain}
+        \caption{Motors}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
+    \begin{subfigure}[b]{0.32\textwidth}
         \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-pumps.png}
-        \caption{Pumps frequency domain}
+        \caption{Pumps}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.33\textwidth}
+    \begin{subfigure}[b]{0.32\textwidth}
         \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-compressors.png}
-        \caption{Compressor frequency domain}
+        \caption{Compressor}
     \end{subfigure} 
@@
 % Time-frequency spectrum
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT.png}
-        \caption{K3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT.png}
-        \caption{M1-2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT.png}
-        \caption{P1-3}
-    \end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT.png}
-        \caption{P3-3}
-    \end{subfigure}
-	\hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/X-P2-Turn-on-Sigma.png}
-        \caption{P2-3 turn off with intererence (X-axis)}
-    \end{subfigure}
-    \caption{Time frequency spectrum}
-\end{figure}
 

### 2024-04-29 thesis/chapters/preliminaries/acknowledgments.tex
kNN batch models: all features & comb. subset
BVS cloud analysis for last year
Refactor jupyter
Online knn on all features refactor
Use bearing A instead of A+B

@@
 
-\settowidth\longest{\itshape We must know. We will know.}
-\centering
+\begin{center}
+\settowidth\longest{\itshape ---Wir müssen wissen.---}
 \parbox{\longest}{
@@
   \itshape
-  	We must know. We will know.\par
+  	Wir müssen wissen. \\ Wir werden wissen.\par
   }   
@@
 }
+\end{center}
 
 \vspace*{\fill}
-\section*{Acknowledgement}
-
+\section*{Poďakovanie}
+{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorba omnoho viac než zachytávajú slová na stránkach.
+Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD.
+a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o.
+Obaja boli otvorení mojim všemožným nápadom a podporovali ma v ich realizácii aj cez mnohé ťažkosti.
+Za praktický expertný pohľad na vibrodiagnostiku vďačím prof.
+Ing.~Stanislavovi Žiaranovi,~CSc.
+a Ing.~Ondrejovi Chlebovi,~PhD.
+zo Strojníckej fakulty STU.
+Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s.
+v sprístupnení čerpadiel na merania a súvisiacich podkladov, a to konkrétne Ing.~Peterovi Csókovi a Ing.~Petrovi Kmeťkovi.
+Rovnako ďakujem za ochotu firme VNET,~a.s., konkrétne Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
+Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy.
+Nuž a v konečnom dôsledku som mal niekedy len viac šťastia ako rozumu.}
 \vspace{3cm}

### 2024-04-29 machine-learning/vibrodiagnostics/visualize.py

@@ -496,7 +496,9 @@ def boxplot_enumerate_models_accuracy(results: pd.DataFrame, metric, plots_col: 
             ax[i].boxplot(
                 boxplot_data.values(),
                 labels=boxplot_data.keys(),
-                medianprops = {'linewidth': 2, 'color': 'black'})
+                medianprops={'linewidth': 2, 'color': 'black'},
+                notch=True
+            )
             ax[i].set_ylabel('Accuracy')
             if plots_col == 'f':
                 ax[i].set_xlabel('K-neighbors')

### 2024-04-30 thesis/chapters/01-introduction.tex
Change two time domain features and reevaluate
Analysis finished - page 37

@@
 \chapter{Introduction}
-The industry experiences a shift in traditional asset operational status evaluation and utilization.
+The industry is experiencing a shift in traditional asset operational status evaluation and utilization.
 The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources.
-The secondary aspect in the enterprises' endeavor, but not less important, is to keep track of the equipment's wear and tear.
+The secondary aspect in the enterprises' endeavour, but not less important, is to keep track of the equipment's wear and tear.
 The corrective action, be it repair or replacement, should be done on time in response to the key indicators.
@@
 The goal is to preserve required safety and production efficiency while extending the useful life of rotating mechanical parts.
-In the factories and logistics where this sort of equipment is vital, there is a rising interest in the ability to watch in real time the machine's health status.
+In the factories and logistics where this equipment is vital, there is a rising interest in the ability to watch the machine's health status in real time.
 Proactive fault diagnosis is imperative to initiate a repair without adding unnecessary costs.
@@
 The experts use it to distinguish faulty states and to identify the malfunction's root causes.
-In critical circumstances such as is the case of the large turbines in power plants, the precautions leading to regular machinery check-ups are already in place.
+The precautions leading to regular machinery check-ups are already in place in critical circumstances, as is the case for large turbines in power plants.
 The monitoring solution has to be sufficiently independent, reliable, and accurate to achieve wider acceptance and spread.
 
-The main issue to consider in large-scale machinery monitoring with vibrations is that there are lots of uninformative streams of samples not directly useful for the production line operator.
+The main issue to consider in large-scale machinery monitoring with vibrations is the presence of many uninformative streams of samples not directly usable for the production line operator.
 The dashboard must aggregate these flows into trend variables with severity levels categorized based on industrial standards.
@@
 The complex overview of the mechanical equipment status is attainable only when agent devices and sensors are cheap enough with a long lifespan powered out of the battery pack.
-Preferably these devices should also remain physically small to reduce the additional clutter in the factory.
+The devices should preferably also remain physically small to reduce the additional clutter in the factory.
 
@@
 In addition, failures are relatively rare events that usually occur several months apart.
-In these circumstances, it is hard to quickly obtain a large enough sample of fault events.
+In these circumstances, it is difficult to obtain a large enough sample of fault events.
 Novelty detection is a technique that can be applied in this case.
 
-This progress report on the master's thesis \rom{2} is organized followingly.
-The problem analysis chapter \ref{chapter:problem-analysis} begins by exploring the mechanical maintenance approaches and industry standards on common fault identification.
-Vibration monitoring starts with a section on preprocessing that summarizes basic filters.
+The master's thesis opens with a chapter on problem analysis~\ref{chapter:problem-analysis} where the explanation is given of mechanical maintenance approaches and industry standards on common fault identification.
+Vibration monitoring starts with a section on preprocessing that summarizes digital filters.
 The process of transforming raw samples into features and their meaningful selection is covered in automatic fault pattern recognition with machine learning models trained in offline and online contexts.
@@
 
-Chapter \ref{chapter:design} on solution design starts by posing research questions and establishing goals.
-Then, the MaFaulDa dataset statistical properties and labeling procedure are described on the original samples as well as on extracted attributes.
-Data rates with feature selection are derived based on the MaFaulDa.
-In the section about classification models, we compare the performance for various feature sets in the k-nearest neighbors algorithm.
-Finally, in preparation for the evaluation part, the sensor device is proprosed which is suitable for measurement of designated machines in the industrial environment.
+Chapter~\ref{chapter:design} about solution design poses research questions and establishes goals.
+The statistical properties and labeling procedure of the MaFaulDa dataset are described on the original samples as well as on extracted attributes.
+The data collection procedure and accelerometer data logger for industrial water pumps and air compressor is outlined.
+Data reduction rates with feature selection are derived based on the MaFaulDa dataset.
+Chapter~\ref{chapter:implementation} describes software libraries and tools used in conducting model evaluation and data logger firmware implementation.
+
+The chapter~\ref{chapter:evaluation} on evalution validates the classification accuracy of feature sets from MaFaulDa and strategies for their subset choice in the k-nearest neighbour model.
+The vibration signals in the realistic environment are also analysed and recommendations for practical application and further study are discussed.

### 2024-04-30 thesis/chapters/02-analysis.tex
Analysis finished - page 37

@@
 Many instrumentation methods are practiced to reveal evolving faults: vibration and acoustic noise monitoring, electric supply line measurements, thermography, oil and particle analysis, ultrasonic testing, etc.
-Vibration signals are the preferred tool for rotating machinery monitoring \cite{mohanty_machinery_2015}.
+Vibration signals are the preferred tool for rotating machinery monitoring~\cite{mohanty_machinery_2015}.
 
@@
 The maintenance strategies are chosen according to the machine's importance as a result of potential failure's impact on the system.
-The guide to set appropriate maintenance procedures as outlined in the IEC~60706-2 standard, and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
+The guide to set appropriate maintenance procedures is outlined in the IEC~60706-2 standard and involves reliability-centered maintenance analysis~\cite{el-thalji_predictive_2019}.
 
@@
 In general, the more sophisticated methods are beneficial in a high-stakes environment.
-The unexpected machine shutdown can have a negative economic impact on the enterprise, resulting in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
+The unexpected machine shutdown can have a negative economic impact on the enterprise which results in decreased product quality and demands for spare parts to be ready in the supply inventory at all times.
 In certain situations, it suffices to utilize a simpler maintenance program, but predictive maintenance gains attraction in Industry 4.0 to optimize usage of assets~\cite{cinar_machine_2020}.
 
-\textbf{Reactive maintenance} allows machinery to run until a complete failure.
-This is the most inappropriate way to maintain the production line, but it is straightforward enough.
-It requires a large stock of replacement parts on-site and breakage inflicts a ``crisis management mode'' upon the plant \cite{scheffer_practical_2004}.
+\textbf{Reactive maintenance} allows machinery to run until a complete failure which is the most inappropriate way to maintain the production line, but it is straightforward enough.
+It requires a large stock of replacement parts on-site.
+Any breakage inflicts crisis management upon the plant \cite{scheffer_practical_2004}.
 On-demand repairs are justified when short downtime is acceptable, full and swift replacement of a broken machine with a backup is possible, or there is a negligible threat to the surrounding environment from failure~\cite{ziaran_technicka_2013}.
@@
 \textbf{Preventive maintenance} is performed before any issue is detected.
-Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time (MTTF - Mean Time To Failure).
+Maintenance occurs at regular intervals derived from a predetermined period in the calendar or expected machine running time and its mean time to failure (MTTF).
 The schedule is crucial but can result in components being replaced in good condition, creating waste.
 The parts can occasionally stay in operation too long, and the machine breaks as a result.
-Conservative planning is usually the norm to keep the machines always in a perfect state, and therefore more frequent interventions are required~\cite{mohanty_machinery_2015}.
-
-\textbf{Predictive maintenance} known as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates waste in overall resource utilization of cautious prevention.
+Conservative planning is usually the norm to keep the machines in perfect shape.
+Therefore, more frequent interventions are required~\cite{mohanty_machinery_2015}.
+
+\textbf{Predictive maintenance} (PdM) known also as condition-based maintenance (CbM), improves the predictability of reactive maintenance and eliminates waste in overall resource utilization of cautious prevention.
 The machine downtime is scheduled after the detection of unhealthy trends in fault monitoring with sensors and the identification of troublesome components.
@@
 
-The \emph{P-F curve} is a widespread representation of equipment degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
+The \emph{P-F curve} is a widespread representation of equipment's degradation over time based on historical records (Fig.~\ref{fig:p-f-curve}).
 Corrective action should be taken between the event of potential failure (P), when the fault detection is activated, and functional failure point (F) in the P-F interval~\cite{bousdekis_enterprise_2021}.
-These division points are not exactly set but have a statistical distribution to them.
-
-The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the ``run-to-failure'' histories, and usage parameters~\cite{okoh_overview_2014}.
-Predictive condition monitoring aims to extend lifespan to the maximum by predicting expected RUL.
+These division points are not set precisely but have a statistical distribution.
+
+The \emph{Remaining Useful Life} (RUL) of the specific running machine in the given instance can be merely estimated analytically, with the survival probabilities of the individual components, based on the model of the ``run-to-failure'' history and usage parameters~\cite{okoh_overview_2014}.
+Predictive condition monitoring aims to extend the lifespan to the maximum by predicting expected RUL.
 
@@
 
-A high failure rate is present not only at the worn-out stage when the parts are fatigued or corroded, but also in the early stages soon after assembly.
-Manufacturing or material defects, inadequate installation, or improper start-up procedures, are all suspected causes.
+A high failure rate is present at the worn-out stage when the parts are fatigued or corroded.
+It can also be registered in the early stages soon after assembly.
+Manufacturing or material defects, inadequate installation, or improper start-up procedures are all suspected causes.
 During the stable middle phase, malfunction can occur after the machine's excessive overload.
@@
 These defects are broadly categorized as \textbf{unbalance, misalignment, looseness, eccentricity, deformation, crack, and influence of the external force} (friction)~\cite{davies_handbook_2012}.
-It is important to stress that our concern is not the underlying deformities in mechanical parts, but the correct fault classification based on the signal waveform.
+It is important to stress that our concern are not the underlying deformities in mechanical parts but the correct fault classification based on the signal waveform.
 
@@
 One of the methods vibration experts utilize in the identification of the damaged part, according to the frequency spectrum, is \textbf{order analysis}.
-The excessive peaks at harmonic frequencies are of interest.
+The excessive peaks in harmonic frequencies are of interest.
 Harmonics are integer multiples of fundamental frequency (1x rpm)~(Tab.~\ref{tab:vibration-causes}):
@@
 
-%TODO bearing image / equations
+The mechanical properties of bearings are instrumental in identifying the characteristic frequencies of their components~\cite{mohanty_machinery_2015, ziaran_technicka_2013}.
+Bearings are composed of outer and inner circular races between which the rolling elements are held inside the cage to avoid mutual contact~(Fig.\ref{fig:bearing-parts}).
+The developing scratches or pits can appear as increases in amplitude around characteristic frequencies and their harmonics but sometimes this is not enough for accurate diagnostics~\cite{brito_fault_2021}.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{assets/analysis/bearing-parts.jpg}
+    \caption{Bearing parts~\cite{lu_what_is_ball_bearing_2023}}
+    \label{fig:bearing-parts}
+\end{figure}
+
+The table \ref{tab:bearing-defect-features} provides formulas for rolling bearing defect frequencies at rotational speed $f_s$ where $n$ is a number of rolling elements, $d$ is the average of outer and inner ring diameters, and contact angle $\beta$.
+Because the frequencies of components depend on shaft rotational speed the values are supplied as its multiplication factors alongside datasets.
+
+\begin{table}[h]
+\centering
+\renewcommand{\arraystretch}{2}
+\begin{tabular}{|l|l|l|l|}
+\hline
+\textbf{Feature}            & \textbf{Equation}                                                                   
+ \\ \hline
+\textit{Outer race fault frequency} & $ BPFO = f_s \cdot \frac{n}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right)$               
+\\ \hline
+\textit{Inner race fault frequency} & $ BPFI = f_s \cdot \frac{n}{2} \cdot \left(1 + \frac{d}{D}\cos \beta \right)$
+\\ \hline
+\textit{Cage rotation frequency}    & $ FTF = f_s \cdot \frac{1}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right) $      
+\\ \hline
+\textit{Ball defect frequencies} & $ BSF = f_s \cdot \frac{D}{d} \cdot \left(1 + \left(\frac{D}{d}\cos \beta\right)^2 \right) $
+\\ \hline
+\end{tabular}
+\caption{Characteristic frequencies of bearings}
+\label{tab:bearing-defect-features}
+\end{table}
 
@@
 Criteria introduced to judge vibration severity are absolute vibration magnitude, change in the magnitude vector, and rate of change.
-In terms of maximal magnitudes, the machines of varying sizes are split into four severity zones defined in the chart ~(Tab.~\ref{tab:iso20816-vibration-severity}).
-The values in this table serve as guidelines towards realistic requirements between machine manufacturers and their customers.
+In terms of maximal magnitudes, the machines of varying sizes are split into four severity zones defined in the chart~(Tab.~\ref{tab:iso20816-vibration-severity}).
+The values in this table serve as guidelines for realistic requirements between machine manufacturers and their customers.
 
@@
 Trips in between zones C and D urge immediate action or machine shut down.
-Both limits should not exceed 1.25 times the upper boundary of the lower zones and initially are set based on previous experience with the machine~\cite{noauthor_iso_2002}.
-
-\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in terms of the vocabulary in ISO 20186.
-According to the standard, the data collection operates in continuous or periodic observation modes which follow an event or interval.
+Both limits should not exceed 1.25 times the upper boundary of the lower zones and are initially set based on previous experience with the machine~\cite{noauthor_iso_2002}.
+
+\textbf{ISO 13373-1:2002} delves into further nuances of vibration monitoring and expands on procedures outlined in terms of the ISO 20186 vocabulary.
+According to the standard, the data collection operates in continuous or periodic observation modes that follow an event or interval.
 Both designs can be permanently mounted.
@@
 
-The transducer of choice for condition monitoring is the accelerometer, which can provide the acceleration value of the body and velocity after signal integration.
-However, standard advise against double integrating for displacement.
+The transducer of choice for condition monitoring is the accelerometer.
+It measures the acceleration value of the body and velocity after signal integration.
+However, standards advise against double integrating for displacement.
 The recommended frequency range for an accelerometer is 0.1~Hz to 30~kHz.
-The choice of transducer mount significantly lowers its resonance frequency, which is least influenced by the stud mount and stiff cement mount.
-The resonance is reduced to around 8~kHz with the use of soft epoxy or permanent magnet.
+The choice of transducer mount significantly influences its resonance frequency.
+The stud mount and stiff cement mount least lower the effective resonance.
+The resonance is reduced to around 8~kHz when using the soft epoxy or permanent magnet.
 
@@
 The vibration signals in a factory environment are inherently full of disturbances.
-Nearby equipment operation and handling of heavy objects in the surroundings can all contribute to the unwanted chaotic movement in otherwise mostly pure oscillatory motion.
-In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset as a result of slight miscalibration, and bias originating from a constant force of gravity.
-These unavoidable distortions are to some extent suppressable by digital filters.
-In the preprocessing stage, we consider trend removal, noise reduction with adaptive filters, and time synchronous averaging to eliminate external interference.
+Nearby equipment operation and heavy objects handling in the surroundings can all contribute to the unwanted chaotic movement in otherwise mostly pure oscillatory motion.
+In addition, accelerometers suffer from systematic measurement errors in the form of thermal noise, zero-g offset from slight miscalibration, and bias originating from a constant force of gravity.
+These unavoidable distortions are somewhat suppressable by digital filters.
+In the preprocessing stage, we consider trend removal and time synchronous averaging to eliminate external interference.
 
@@
 
-A steeper 3~dB attenuation band can be achieved by increasing the order of the filter.
-Then the cutoff frequency should be such that filter coefficients are fractions to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
+A steeper 3~dB attenuation band is achieved by increasing the order of the filter.
+Then, the cutoff frequency should be such that filter coefficients are fractions to counteract rounding errors~\cite{tittelbach-helmrich_digital_2021}.
 
@@
 Predictive maintenance has ideal prerequisites for the application of feature engineering because the signal is usually pseudo-stationary, and the trend monitoring variables come out of extensive domain expertise in mechanics.
-The advantages of the add-in extraction effort, as opposed to processing samples unmodified, are to gain better classification precision, reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
-
-It is important to note that the design of features is not a standalone step in the machine learning pipeline, but it should be done iteratively to improve the target model.
+The advantages of the add-in extraction effort as opposed to processing unmodified samples are to gain better classification precision and reduce computational burden and storage capacity downstream with dimensionality reduction~\cite{johnson_feature_2019}.
+
+It is important to note that the design of features is not a standalone step in the machine learning pipeline, but it should be performed iteratively to improve the target model.
 Signal features are computed in the time and frequency domain~\cite{brito_fault_2021}.
@@
 
-The other significant time domain attributes are derived as ratios of previous simpler ones.
+The other significant time-domain attributes are derived as ratios of previous simpler ones.
 These ratios are crest, clearance, impulse factor, and shape factor~(Tab.~\ref{tab:td-features})~\cite{nandi_condition_2019}.
@@
 
-In the frequency domain, we can obtain the usual statistical properties of the distribution being spectral centroid, skew and kurtosis.
+In the frequency domain, we can obtain the usual statistical properties of the distribution which are spectral centroid, skew, and kurtosis.
 Additionally, spectral roll-on and roll-off, fundamental frequency, entropy, negentropy, spectral flux, signal-to-noise ratio (noisiness), energy in frequency bands, and energy ratio are extracted (Tab.~\ref{tab:fd-features})~\cite{peeters_large_2004}.
@@
 In geometric terms, the spectral centroid represents the barycenter of the frequency magnitude plot.
-Spectral roll-off gives a notion about the spectral distribution because it identifies the frequency $f_c$ below which 95\% of the signal energy is contained.
-Complementary, the roll-on frequency is chosen so that 5\% of the signal energy is below this value.
-According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra a value of one means the spectra are the most dissimilar.
+Spectral roll-off gives a notion about the spectral distribution because it identifies the frequency $f_c$ below which 85\% of the signal energy is contained.
+The roll-on frequency is chosen so that 5\% of the signal energy is below this value.
+According to the definition, spectral flux is normalized cross-correlation between two successive amplitude spectra.
+A flux value of one means the spectra are the most dissimilar.
 
@@
 All found extrema are commonly filtered with the magnitude of prominences and the width at half prominence.
-In the magnitude-based method, the middle point $x_i$ is compared to two neighboring points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
-The gradient-based method evaluates the first derivative at the point which is equal to zero if the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
+In the magnitude-based method, the middle point $x_i$ is compared to two neighbouring points and the peak is then: $x_{i-1} < x_i > x_{i+1}$.
+The gradient-based method evaluates the first derivative at the point that is equal to zero if the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
 
@@
 
-\subsection{Bearing defect frequencies}
-
-%TODO n = number of balls, d - average of outer ring diameter and outer ring, f_s - rotation speed, beta - contact angle - ball bearings close to 0
-
-% Rolling element bearings have four very important components, two circular races, between which the rolling elements—rollers, tapered rollers, or spherical balls—are held.
-The fourth important element in a rolling element bearing is the cage or the separator.
-The cage ensures that no two rolling elements come in contact with each other
-% The bearing vibration is further complicated when the radial loads on the bearing change during rotation of the shaft, and defects like impurities or scratches, pits, and so on, develop on the bearing element surfaces
-% The characteristic bearing defect frequencies for the different rolling elements of bearings can be determined
-
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.7\textwidth]{assets/analysis/bearing-parts.jpg}
-    \caption{Bearing parts~\cite{lu_what_is_ball_bearing_2023}}
-    \label{fig:bearing-parts}
-\end{figure}
-
-\begin{table}[h]
-\centering
-\renewcommand{\arraystretch}{2}
-\begin{tabular}{|l|l|l|l|}
-\hline
-\textbf{Feature}            & \textbf{Equation}                                                                   
- \\ \hline
-\textit{Outer race fault frequency} & $ BPFO = f_s \cdot \frac{n}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right)$               
-\\ \hline
-\textit{Inner race fault frequency} & $ BPFI = f_s \cdot \frac{n}{2} \cdot \left(1 + \frac{d}{D}\cos \beta \right)$
-\\ \hline
-\textit{Cage rotation frequency}    & $ FTF = f_s \cdot \frac{1}{2} \cdot \left(1 - \frac{d}{D}\cos \beta \right) $      
-\\ \hline
-\textit{Ball defect frequencies} & $ BSF = f_s \cdot \frac{D}{d} \cdot \left(1 + \left(\frac{D}{d}\cos \beta\right)^2 \right) $
-\\ \hline
-\end{tabular}
-\caption{Bearing defect frequencies}
-\label{tab:bearing-defect-features}
-\end{table}
-
 \subsection{Time-frequency domain features}
 The \textbf{Short-time Fourier transform} (STFT) splits the time-domain signal into equal-length intervals.
-Individual chunks have a 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to Fourier transform periodicity assumption.
+Individual chunks have a 50\% overlap and are multiplied with weights of window function to balance scalloping loss and spectral leakage due to the Fourier transform periodicity assumption.
 Traditionally, the Hann window is commonly used instead of the rectangular window~\cite{ziaran_technicka_2013,noauthor_iso_2016_2}.
@@
 
-In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provide features with a combination of approximation (cA5) and detail coefficients (cD1, \dots, cD5).
+In washing machine status classification, the discrete wavelet transform with Daubechies wavelet (db4) and fifth-level decomposition provides features with a combination of approximation (cA5) and detail coefficients (cD1, \dots, cD5).
 Washing machines belong to three categories: no fault, electric motor clamping screws problem, and a loose or broken counterweight.
@@
 The bottom layer contains bands numbered 7 through 14, each with a bandwidth of 62.5 kHz, because of the 1 MHz sampling frequency.
-The feature vector constructed in the article includes other statistical metrics out of power spectral density that has reached a notable correlation with evolving wear.
+The feature vector constructed in the article includes other statistical metrics out of power spectral density that have reached a notable correlation with evolving wear.
 The statistics are \emph{skewness}, \emph{kurtosis}, \emph{shape factor}, and \emph{centroid frequency}~\cite{zhuo_research_2022}.
@@
 
-Wavelet domain features and associated spectral segmentation appear to be a powerful tool in conserving data bandwidth.
+Wavelet domain features and associated spectral segmentation appear to be a powerful tool for conserving data bandwidth.
 These variables turn out to be difficult to communicate and comprehend.
-Therefore, we will use more standardized metrics in further studies.
+Therefore, we further use more standardized metrics.
 
@@
 The codependent variables are of three sorts: quantitative, ordinal, and nominal.
-The choice of coefficient calculation is determined by the type of variables under consideration shown in Table \ref{tab:corr-coef}.
+The choice of coefficient calculation is determined by the type of variables under consideration as shown in Table \ref{tab:corr-coef}.
 
@@
 Mutual information presumes variables are discrete.
-In the case of quantitative variables, mutual information is estimated by binning or nearest neighbors methods~\cite{ross_mutual_2014}.
+In the case of quantitative variables, mutual information is estimated by binning or nearest neighbours methods~\cite{ross_mutual_2014}.
 
@@
 The detection model must deal with the minimal admissible assumptions about the nature of the input events.
-The outliers are derived based on non-parametric statistical models, nearest-neighbor clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
+The outliers are derived based on non-parametric statistical models, nearest-neighbour clustering, and isolation-based approaches~\cite{gervasi_anomaly_2020}.
 \bigbreak
@@
 \textbf{DenStream} is a density-based algorithm adapted from DBSCAN to cluster streaming data of arbitrarily shaped groups.
-Samples it includes in the first step into coherent clusters are core data points in each other's neighborhoods.
-Core points have at least \emph{MinPts} ($\mu$) points in their neighborhood of radius \emph{Eps} ($\varepsilon$) units.
+Samples it includes in the first step into coherent clusters are core data points in each other's neighbourhoods.
+Core points have at least \emph{MinPts} ($\mu$) points in their neighbourhood of radius \emph{Eps} ($\varepsilon$) units.
 Then non-core points in the proximity area of the core point are attached to the cluster containing it~\cite{aggarwal_data_2014}.
@@
 It demands points within clusters to have high cohesion and at the same time to have large separation from other clusters.
-The low score indicates a too small or too large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
+The low score indicates a too-small or too-large number of clusters~\cite{rousseeuw_rousseeuw_1987}.
 
@@
 The (outlier) \emph{o-micro-clusters} can grow into (potential) \emph{p-micro-clusters} when they encompass $\beta \mu$ points.
-The outliers are discounted after some time in accordance to the decay function: $f(t) = 2^{-\lambda t}$ or below the lower weight limit $\xi$.
+The outliers are discounted after some time in accordance with the decay function: $f(t) = 2^{-\lambda t}$ or below the lower weight limit $\xi$.
 The on-demand offline stage runs DBSCAN over the approximate representation in micro-clusters to deliver final apportionment~\cite{cao_density-based_2006}.
-\bigbreak
-
-%\cite{tan_fast_2011}.
 
 \subsection{Classification}
-Accurate multi-class classification of machine fault causes according to the characteristics of known ones is a much more difficult task than novelty detection.
+Accurate multi-class classification of machine faults according to the characteristics of known causes is a much more difficult task than novelty detection.
 Fault combinations have to be recorded and transformed into feature space.
@@
 We are aware of rapid advances in knowledge transfer for deep neural networks~\cite{maurya_condition-based_2021}.
-So far, solutions seem not production-ready and hard to explain.
+So far, solutions seem to be hard to implement.
 Therefore, we opt to use a simpler model.
 
-Performance of classification is estimated by several metrics on the validation set obtained using hold-out or cross-validation techniques.
+The performance of classification is estimated by several metrics on the validation set obtained using hold-out or cross-validation techniques.
 Frequently used quantities for classifier model evaluation include accuracy, precision, recall, f1 score, area under the ROC curve, and counts of hits and misses in a confusion matrix.
@@
 
-\textbf{K-nearest neighbors} (k-NN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
+\textbf{K-nearest neighbours} (k-NN) assigns the data point to the class where the majority of $k$ closest instances belong (Fig.~\ref{fig:KNN}).
 It means it can work in a semi-supervised environment because it can infer labels just from knowing a few annotations.
-The major drawback of k-NN is a preference for the majority class in imbalanced class-size datasets~\cite{shi_improving_2020}.
+The major drawback of k-NN is a preference for the majority class in imbalanced class-size datasets.
 The issue is mitigated with class weights or resampling classes by oversampling or undersampling.
+The model without class balancing drops in precision from 15\% to over 40\% depending on the imbalance ratio~\cite{shi_improving_2020}.
 The k-NN algorithm requires features to be normalized to assign the same importance to each predictor.
@@
     \end{subfigure}
-    \caption{Nearest neighbors classification algorithm~\cite{chen_skyline_2009}}
-\end{figure}
-
-The sense of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
+    \caption{Nearest neighbours classification algorithm~\cite{chen_skyline_2009}}
+\end{figure}
+
+The meaning of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
 (Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
 The optimal $k$ parameter is set by supervised learning according to the breaking point in the elbow curve that plots choices of $k$ against the error rate.
-The demanding neighborhood queries are sped up using spatial index in spatial databases that utilizes search tree such as kd-tree, R-tree, or M-tree.
+The demanding neighbourhood queries are sped up using spatial indexes in databases that utilize search trees such as kd-tree, R-tree, or M-tree.
 
@@
 \textbf{Distance}     & \textbf{$d(\mathbf{x}, \mathbf{y})$}                                   \\ \hline
-Manhatann distance	 & $ |x_i - y_i| $													   \\ \hline
+Manhattan distance	 & $ |x_i - y_i| $													   \\ \hline
 Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
@@
 
-The nearest-neighbor classifier has been successfully applied in machinery fault diagnostics.
-On the CWRU bearing dataset, the k-NN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, time-domain features - k-NN 91.2\%, SVM 88.8\%, and frequency domain features - k-NN (98.8\%), SVM (96.2\%)~\cite{jamil_feature-based_2021}.
-
-Comparison of k-NN and KLDA on a feature set consisting of average, kurtosis, skewness, and standard deviation vectors in each domain has been conducted, achieving a data reduction rate of 95\%.
-Best accuracy was reached for PSD features with 99.13\% with KLDA and 96.64\% with k-NN classifiers and Mahalanobis metric.
-The sampling frequency was set at 40 kHz~\cite{altaf_new_2022}.
-Despite k-NN lagging in accuracy, we have to keep in mind annotations for faults were complete, and machine learning was not tested in a streaming context.
+The nearest-neighbour classifier has been successfully applied in machinery fault diagnostics.
+On the CWRU bearing dataset, the k-NN with the accuracy of 96.2\% slightly outperformed SVM (95\%) on the combination of time and frequency-domain features, on set of time-domain features (k-NN 91.2\%, SVM 88.8\%), and on frequency domain features (k-NN 98.8\%, SVM 96.2)\%~\cite{jamil_feature-based_2021}.
+
+Comparison of SVM, KNN, and KLDA for the classification of three kinds of bearing faults reaches more than 95\% of data reduction decreasing the time complexity of the models.
+The test rig rotates at 800 rpm and is sampled at 40 kHz.
+Their approach uses feature sets of average, kurtosis, skewness, and standard deviation applied on vibration signal after the Fourier transform and its second derivatives over the moving window.
+The best accuracy was reached by 40 thousand \emph{PSD} set with 99.13\% with KLDA compared to 95.64\% with k-NN and Mahalanobis metric.
+The \emph{Statistical} set of 8 $\times$ 228 features has accuracy 98.27\% (KLDA) and 93.53\% (k-NN)~\cite{altaf_new_2022}.
 
@@
 
-Deployment of an online machine learning model alongside supporting services is different from in established MLOps processes.
+Deployment of an online machine learning model alongside supporting services is different from established MLOps processes.
 Model store and Inference service components are supplemented with Labelling and Learning service~\cite{gaia_online_2022}.

### 2024-04-30 thesis/chapters/03-design.tex
Analysis finished - page 37

@@
 \chapter{Design} \label{chapter:design}
-The design phase sets out to elaborate on the scenarios for experiments with IoT device.
-In these experiments, we compare and combine approaches from industry standards and papers presented in the analysis section.
-Conclusions are taken into consideration in establishing the plan of measurements and in the construction of the sensor unit.
+%TODO
 
@@
     \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
-    \item Find the best subsets of features in the temporal and spectral domain with previously analyzed feature extraction and selection methods.
+    \item Find the best subsets of features in the time and frequnecy domain with previously analyzed feature extraction and selection methods.
     \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
@@
 \end{todolist}
-
-However, we leave out from our efforts experiments on the data features calculated from wavelets and peaks in the spectral domain.
-The reason is that we did not find a way to represent extracted features more succinctly as a single number.
-We also did not discover a strategy for choosing only the relevant frequency bins.
 
@@
 
+% Describe steps in pipeline
 \begin{figure}[h]
@@
 \item Incremental learning
-\item Clustering - Silouette score
 \end{itemize}

### 2024-04-30 thesis/chapters/TEXT.tex
Analysis finished - page 37

@@
 \chapter{Design} \label{chapter:design}
+
+\section{Návrh metód s MaFaulDa}
+Súbor údajov MaFaulDa používame ako smerodajný pri určovaní metód schopných nasadenia na senzorovú jednotku.
+MaFaulda obsahuje 1951 záznamov so vzorkovaciu frekvenciu 50 kHz a označenými simulovanými poruchami rôznej závažnosti.
+Nahrávky obsahujú časové rady z dvoch trojosích piezoelektrických akcelerometrov.
+Po úprave ponechávame 6 typov značiek: referenčný bezporuchový stav, dve poruchy hriadeľa (nevyváženosť, nesúososť) a tri poruchy ložísk (poruchy klietky, guľôčok, vonkajšieho krúžku).
+
+Zo signálov rozdeleních na päť jednosekundových častí sa odstraňuje jednosmerná zložka odčítaním priemernej akcelerácie, po ktorej nasleduje dolnopriepustný 10 kHz filter.
+Z častí signálu je potom vytvorených 10 časových a 11 spektrálnych premenných.
+Euklidovská norma trojrozmerných atribútov eliminuje závislosť na smere merania.
+Pri výbere atribútov nie je do množiny pridaná taká dvojica, ak ich absolútna hodnota korelácie presahuje 0.95.
+
+Predpokladáme, že dátové body rozprestreté v každej dimenzii priestoru môžu dobre rozlíšiť skupiny.
+Ukazuje sa, že premenné sú navzájom viac korelované v časovej doméne ako ilustruje analýza hlavných komponentov.
+Pre 95\% vysvetleného rozptylu PCA sú v časovej doméne potrebné 3 zložky, zatiaľ čo vo frekvenčnej doméne 4 zložky.
+PCA efektívne vyjadruje atribúty v menej rozmernom priestore, ale ich výslednou lineárnou kombináciou sa ťažko odôvodňujú rozhodnutia modelu.
+
+Pri posudzovaní všeobecne najdôležitejších atribútov vychádzame z trojíc nekorelovaných atribútov vytvorených v 24 scenároch.
+Podmienky scenárov vznikli kombináciou štyroch kritérií: dávkové alebo inkrementálne učenie, pozícia ložiska, predikovaná premenná, limit na rotačnú rýchlosť.
+Na základe schvaľovacieho hlasovania sú najčastejšie sa vyskytujúcimi atribútmi v časovej doméne: špička-špička, faktor tvaru, faktor výkyvu.
+Vo frekvenčnej doméne sú to spektrálne ťažisko, roll-on a roll-off.
+
+Tri typy experimentov s modelom k-NN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
+Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou.
+Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov.
+Dávkový model k-NN slúži ako referenčný, podľa ktorého sa posudzuje k-NN v postupnom učení.
+
+Online učenie napodobňuje sťažené podmienky diagnostiky strojov, ktoré sa objavujú v praxi.
+Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie.
+Modely k-NN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi.
+Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie.
+k-NN sme nastavili na 5 susedov a euklidovskú vzdialenosť.
+Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.
+
+\section{Zber vibrácií v priemysle}
+Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia.
+Pri monitorovaní zužitkujeme mierne prispôsobený postup z noriem.
+Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.
+Zber nového súboru údajov sprevádza vopred dohodnutý harmonogram.
+
+Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
+Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
+Ako senzor vibrácii použijeme MEMS akcelerometer IIS3DWB.
+Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
+
+\section{Záver}
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
+Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.
+
+Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
+Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne.
+Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%.
+Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
+
+Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
+Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.
+Doteraz boli urobené závery podľa súboru údajov MaFaulDa, ktoré plánujeme overiť na súbore údajov získaných v priemysle počas DP3.
 

### 2024-04-30 thesis/chapters/appendix/A-resume.tex
Analysis finished - page 37

@@
 
-\section{Návrh metód s MaFaulDa}
-Súbor údajov MaFaulDa používame ako smerodajný pri určovaní metód schopných nasadenia na senzorovú jednotku.
-MaFaulda obsahuje 1951 záznamov so vzorkovaciu frekvenciu 50 kHz a označenými simulovanými poruchami rôznej závažnosti.
-Nahrávky obsahujú časové rady z dvoch trojosích piezoelektrických akcelerometrov.
-Po úprave ponechávame 6 typov značiek: referenčný bezporuchový stav, dve poruchy hriadeľa (nevyváženosť, nesúososť) a tri poruchy ložísk (poruchy klietky, guľôčok, vonkajšieho krúžku).
-
-Zo signálov rozdeleních na päť jednosekundových častí sa odstraňuje jednosmerná zložka odčítaním priemernej akcelerácie, po ktorej nasleduje dolnopriepustný 10 kHz filter.
-Z častí signálu je potom vytvorených 10 časových a 11 spektrálnych premenných.
-Euklidovská norma trojrozmerných atribútov eliminuje závislosť na smere merania.
-Pri výbere atribútov nie je do množiny pridaná taká dvojica, ak ich absolútna hodnota korelácie presahuje 0.95.
-
-Predpokladáme, že dátové body rozprestreté v každej dimenzii priestoru môžu dobre rozlíšiť skupiny.
-Ukazuje sa, že premenné sú navzájom viac korelované v časovej doméne ako ilustruje analýza hlavných komponentov.
-Pre 95\% vysvetleného rozptylu PCA sú v časovej doméne potrebné 3 zložky, zatiaľ čo vo frekvenčnej doméne 4 zložky.
-PCA efektívne vyjadruje atribúty v menej rozmernom priestore, ale ich výslednou lineárnou kombináciou sa ťažko odôvodňujú rozhodnutia modelu.
-
-Pri posudzovaní všeobecne najdôležitejších atribútov vychádzame z trojíc nekorelovaných atribútov vytvorených v 24 scenároch.
-Podmienky scenárov vznikli kombináciou štyroch kritérií: dávkové alebo inkrementálne učenie, pozícia ložiska, predikovaná premenná, limit na rotačnú rýchlosť.
-Na základe schvaľovacieho hlasovania sú najčastejšie sa vyskytujúcimi atribútmi v časovej doméne: špička-špička, faktor tvaru, faktor výkyvu.
-Vo frekvenčnej doméne sú to spektrálne ťažisko, roll-on a roll-off.
-
-Tri typy experimentov s modelom k-NN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov.
-Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou.
-Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov.
-Dávkový model k-NN slúži ako referenčný, podľa ktorého sa posudzuje k-NN v postupnom učení.
-
-Online učenie napodobňuje sťažené podmienky diagnostiky strojov, ktoré sa objavujú v praxi.
-Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie.
-Modely k-NN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi.
-Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie.
-k-NN sme nastavili na 5 susedov a euklidovskú vzdialenosť.
-Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.
+\section{Návrh spracovania pre MaFaulDa}
 
 \section{Zber vibrácií v priemysle}
-Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia.
-Pri monitorovaní zužitkujeme mierne prispôsobený postup z noriem.
-Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.
-Zber nového súboru údajov sprevádza vopred dohodnutý harmonogram.
 
-Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
-Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
-Ako senzor vibrácii použijeme MEMS akcelerometer IIS3DWB.
-Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
+\section{Vyhodnotenie presnosti diagnostiky}
+
+\section{Rozbor dátovej sady z priemyslu}
 
 \section{Záver}
-V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
-Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.
-
-Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
-Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne.
-Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%.
-Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
-
-Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
-Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.
-Doteraz boli urobené závery podľa súboru údajov MaFaulDa, ktoré plánujeme overiť na súbore údajov získaných v priemysle počas DP3.
 

### 2024-04-30 thesis/chapters/preliminaries/annotation.tex
Analysis finished - page 37

@@
 
-Master's thesis deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.
+Master's thesis focuses on condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.
 

### 2024-04-30 thesis/chapters/03-design.tex
Describe ML pipeline

@@
 \chapter{Design} \label{chapter:design}
-%TODO
+During the design stage, we set out research questions and detail the steps of the machine learning pipeline for diagnosing fault types in the MaFaulDa dataset.
+The explanatory analysis of MaFaulDa hints at the underlying dependencies with feature sets that can degrade the machine learning model of choice.
+We adapt the methodology for measurements from standards and apply it to data logger requirements and data acquisition from industrial equipment.
 
 \section{Research questions}
-This thesis aims to provide answers to four research questions.
+The thesis aims to provide answers to four research questions.
 The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
@@
 \section{Machine learning pipeline}
-% UML pipeline (fig.) and parameters
+The similar data processing framework we adopt can be found elsewhere in the literature.
+It generally consists of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015}.
+However, the realization of the steps must be decomposed closer to suit the dataset structure, desired processing goals, and investigated parameters.
+The entire design of the data flow can be seen in Fig.~\ref{fig:design:ml-pipeline}.
 
-Dataset scenarios - 24 scenarios
+\begin{figure}[h]
+    \centering
+	\includegraphics[width=0.9\textwidth]{assets/design/pipeline-design.png}
+	\caption{Machine learning pipeline for MaFaulDa dataset}
+	\label{fig:design:ml-pipeline}
+\end{figure}
+\afterpage{\clearpage}
+
+\textbf{In preprocessing step}, the signals stored in columns of CSV files within the MaFaulDa ZIP archive are first associated with metadata according to the file's path in the directory structure.
+The hierarchically topmost folder describes the simulated defect.
+There is directory for \emph{normal}, \emph{imbalance}, \emph{horizontal-misalignment}, \emph{vertical-misalignment}, \emph{overhang} (outer bearing), \emph{underhang} (inner bearing).
+Each bearing has an additional folder layer for dividing bearing faults: \emph{ball\_fault}, \emph{cage\_fault}, \emph{outer\_race}.
+Each fault category except the normal class contains various fault severities with units of grams or millimeters.
+The severities in turn consist of individual files with different rpm speeds.
+
+We neglect the acceleration sensor orientation, therefore, the labels for shaft misalignment in vertical and horizontal directions are merged into the same group.
+In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
+
+Depending on the chosen bearing position, only time series associated with that bearing are retained because the standards demand each bearing be assessed separately.
+Fault classification concerns bearing in direct contact and shaft mechanically passing through it.
+
+The strength of the recorded response to the underlying defect is dependent on the shaft \textbf{rotational speed}.
+Speed in units of rpm is calculated from pulsed speedometer output.
+It is the average distance between two successive rising edges:
+\begin{ceqn}\begin{align}
+\mathrm{rpm} = 60 \;/\; \overline{\Delta t}
+\end{align}\end{ceqn}
+
+The final \textbf{file description} is the triplet of \textbf{fault}, \textbf{severity}, and \textbf{rpm}.
+
+After labeling we insert a step to split the time series into parts when the duration is long enough to introduce more observations artificially.
+This assumption is not met for MaFaulDa because, for the desired frequency resolution for features of close to 1~Hz, we need a window size of 32768 samples.
+Variation reduction in spectral estimation brings the necessity to average at least 12 overlapping windows.
+The full length of 5 seconds provides 15 whole overlapping windows.
+
+The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
+Immediately follows a digital IIR Butterworth low pass filter of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
+Before the usage of a low pass filter, the peak at 20 kHz with a sideband was present as an unwanted artifact.
+It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
+At the same time, such a frequency is outside the range of any feasible MEMS accelerometer.
+
+Initial labels can be exchanged for a label of fault-free state when the severity is low.
+The count of severity levels is not identical in every group.
+The numerical amounts for each level are sorted in ascending order within each fault and then these levels are normalized using a min-max scaler.
+
+The preprocessed signal from each axis of accelerometer is packed up to two base feature sets in time domain (TD) and frequency domain (FD).
+The feature extraction formulas are is identical with formulas presented in the section \ref{section:feature-extraction} of analysis chapter.
+The frequency transform is Welch's method averaging FFT vectors from 32768 samples after Hann windowing and 50\% overlap.
+The feature sets are:
 \begin{itemize}
-\item domain - TD, FD
-\item dim - 1, 3
-\item bearing - A, B, A+B
-\item severity - No, Yes
+\item \textbf{TD has 10 time-domain features}: peak-to-peak amplitude (\emph{pp}), zero-crossing rate (\emph{zerocross}), root mean square (\emph{rms}), skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change (aac),
+\item \textbf{FD has 11 frequency-domain features}: spectral centroid, standard deviation (\emph{std}), skewness, kurtosis, roll-on frequency, roll-off frequency, spectral flux, noisiness, spectral negentropy, energy, entropy.
 \end{itemize}
 
-% Describe steps in pipeline
-\begin{figure}[h]
-    \centering
-	\includegraphics[width=\textwidth]{assets/design/pipeline-design.png}
-\end{figure}
+The four conditions is applied in the instance of the pipeline to filter observations with calculated features to create 24 scenarios:
+\begin{itemize}
+\item \textbf{source bearings}: keep samples and fault labels either just for the inner bearing (A), for only the outer bearing (B), or both bearings (A+B).
+\item \textbf{feature domain}: change the set of extracted features an input to downstream models and those can be time-domain (TD) and frequency-domain (FD) features,
+\item \textbf{accelerometer axis}: consider either one principal direction of motion or all three dimensions to aggregate under same feature name,
+\item \textbf{high severity faults}: to more precisely capture fault frequencies found in real environment the low severity defects can be considered as normal operation.
+\end{itemize}
 
-% Experiments and metrics:
+The fault classification performance metrics are judged after balancing classes with random oversampling using strategy to resample all but majority class, feature normalization and 5-fold cross-validation validation on k-nearest neighbor classifier.
+In the multi-class classification the micro-averaged performance metrics of accuracy, precision, and recall results in the same number, therefore accuracy is only one on the output.
+
+The hyperparameters of k-neighbours and subset of utilzed features is tweaked and results are compared under different initial conditions from preprocessing and in multiple experiments.
+
 \begin{itemize}
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{assets/results/feature-values/corr-to-rpm.png}
+    \includegraphics[width=0.8\textwidth]{assets/results/feature-values/corr-to-rpm.png}
     \caption{Correlation of features to RPM over all experiments}

### 2024-04-30 thesis/chapters/TEXT.tex
Describe ML pipeline

@@
 \subsection{Fault annotations}
-The MaFaulDa has annotations altogether for 10 classes of faults, of which there is 1 class for fault-free baseline operation, 3 classes for shaft defects, 3 classes for inner bearing defects, and 3 for outer bearing defects.
-Some categories are redundant or irrelevant for a given sensor position.
-
-Therefore, rotor shaft misalignement in vertical and horizontal directions are merged into one joint group.
-Depending on the chosen bearing position, only records having relevant labels are considered.
-
-This means that fault classification solely concerns bearing in direct contact and shaft mechanically passing through it.
-The bearings affect each other, but the effect on the opposite side should appear via a common interconnection shaft.
-
-In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
-In the step of choosing the accelerometer location, records pointing to the other bearing as a source of the malfunction are discarded.
-Then the next action renames the labels to be better recognizable and unite the same phenomena.
-
-Groups of identified machine defects are additionally characterized by altered masses attached or motor shaft displacement shifts.
-The set amount is sorted in ascending order, separating \textbf{multiple event severities}.
-However, the count of severity levels is not identical in every group.
-Levels are hence scaled into the range between zero and one using a min-max scaler.
-Scaling is applied to classes separately.
-
-The strength of the recorded response to the underlying defect is also dependent on the shaft \textbf{rotational speed}.
-Speed in rpm units is calculated from pulsed speedometer output.
-It is the average distance between two successive rising edges:
-\begin{ceqn}\begin{align}
-\mathrm{rpm} = 60 \;/\; \overline{\Delta t}
-\end{align}\end{ceqn}
-
-\textbf{One specimen waveform} is picked from each fault class to illustrate their superficial differences.
-Recordings are filtered to get the highest severity levels and around a mean rotation speed of 2500 rpm (42 Hz) to see the patterns most pronounced.
-The baseline class sample is chosen according to fixed rotor speed.
 
 \subsection{Signal filters}
-The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
-Immediately follows a digital IIR Butterworth \textbf{low pass filter} of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
-
-Before the low pass filter usage, the peak at 20 kHz with a sideband was present as an unwanted artifact.
-It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
-At the same time, such a frequency is outside the range of any feasible MEMS accelerometer.
 

### 2024-04-30 thesis/chapters/03-design.tex
Finish pipeline description in design

@@
 \begin{itemize}
-\item \textbf{TD has 10 time-domain features}: peak-to-peak amplitude (\emph{pp}), zero-crossing rate (\emph{zerocross}), root mean square (\emph{rms}), skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change (aac),
-\item \textbf{FD has 11 frequency-domain features}: spectral centroid, standard deviation (\emph{std}), skewness, kurtosis, roll-on frequency, roll-off frequency, spectral flux, noisiness, spectral negentropy, energy, entropy.
+\itemsep0pt
+\item \textbf{TD has 10 time-domain features} - peak-to-peak amplitude (\emph{pp}), zero-crossing rate (\emph{zerocross}), root mean square (\emph{rms}), skewness, kurtosis, shape factor, crest factor, impulse factor, clearance factor, average amplitude change (aac),
+\item \textbf{FD has 11 frequency-domain features} - spectral centroid, standard deviation (\emph{std}), skewness, kurtosis, roll-on frequency, roll-off frequency, spectral flux, noisiness, spectral negentropy, energy, entropy.
 \end{itemize}
 
-The four conditions is applied in the instance of the pipeline to filter observations with calculated features to create 24 scenarios:
+The four conditions are applied in the instance of the pipeline to filter observations with calculated features to create 24 scenarios:
 \begin{itemize}
-\item \textbf{source bearings}: keep samples and fault labels either just for the inner bearing (A), for only the outer bearing (B), or both bearings (A+B).
-\item \textbf{feature domain}: change the set of extracted features an input to downstream models and those can be time-domain (TD) and frequency-domain (FD) features,
-\item \textbf{accelerometer axis}: consider either one principal direction of motion or all three dimensions to aggregate under same feature name,
-\item \textbf{high severity faults}: to more precisely capture fault frequencies found in real environment the low severity defects can be considered as normal operation.
+\itemsep0pt
+\item \textbf{Source bearings} - samples and fault labels are left in either just for the inner bearing (A), for only the outer bearing (B), or for both bearings (A+B).
+\item \textbf{Feature domain} - the set of extracted features as an input to downstream models is changed either to TD or FD set,
+\item \textbf{Accelerometer axis} - Either one principal direction of motion or all three dimensions is aggregated under same feature name (1 or 3),
+\item \textbf{High severity faults} - to more precisely simulate fault frequencies found in real environment the low severity defects can be considered as normal operation (Yes or No).
 \end{itemize}
 
-The fault classification performance metrics are judged after balancing classes with random oversampling using strategy to resample all but majority class, feature normalization and 5-fold cross-validation validation on k-nearest neighbor classifier.
-In the multi-class classification the micro-averaged performance metrics of accuracy, precision, and recall results in the same number, therefore accuracy is only one on the output.
+The fault classification performance metrics are evaluated after balancing classes feature normalization, and 5-fold cross-validation validation on the k-nearest neighbor classifier with Euclidean distance metric.
+The population of classes is evened out with random oversampling using a strategy to resample all but the majority class.
+In the multi-class classification, the micro-averaged performance metrics of accuracy, precision, and recall result in the same number.
+Therefore, accuracy is only one on the output.
 
-The hyperparameters of k-neighbours and subset of utilzed features is tweaked and results are compared under different initial conditions from preprocessing and in multiple experiments.
+The hyperparameter of k-neighbours and a subset of features are tweaked, and results are compared under different preprocessing conditions and in multiple experiments:
 
 \begin{itemize}
-\item Complete feature sets
-\item Feature combinations
-\item Feature selection methods
-\item Incremental learning
+\itemsep0pt
+\item \textbf{Complete feature sets}: compare the accuracy of the k-NN model in relation to the k-value as an odd number in the range from 1 to 37 on the dataset under different conditions.
+The TD and FD sets are treated separately.
+
+\item \textbf{Feature combinations} - every combination of feature subsets with 2, 3, and 4 members are evaluated to obtain the statistical distribution of all possible k-NN models.
+The k-value is sequentially increased from options 3, 5, and 11 neighbours.
+The single k-value generates $\sum_{j=2}^{4}{\binom{n}{j}}$ where $n$ is number of members in complete feature set.
+In total 375 models for TD and 550 models for FD are tested under identical conditions.
+
+The observed effect is a rate of decrease in accuracy while shrinking the number of features to the bare minimum.
+The side product is finding the global optimum by brute force of the most informative attributes in predicting the defect.
+
+\item \textbf{Feature selection methods} - the choice of feature subset is performed in linear time complexity as opposed to exponential in combinatorial case.
+The dimensionality reduction using \textbf{principal components analysis} (PCA) does further extraction and retains only the components that best explain the variance.
+The disadvantage is that the resulting linear combination cannot be interpreted easily.
+
+The best feature subset from complete sets is picked after ranking the features according to their importance.
+The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}.
+The rank product combines the three latter scores into the ensemble.
+The comparison for the accuracy of the feature selection strategy is made in relation to the entire model accuracy distribution.
+
+\item \textbf{Incremental learning} - the order of samples tries to simulate the gradually worsening state of the machine and delayed annotation of defects.
+Observations are sorted based on increasing relative severity.
+The faults with the same severity are lined up randomly.
+
+The \textbf{tumbling window} of lengths 1, 10, 100 measurements imitates regular expert visits annotating observations recorded until that moment.
+Labels for the whole previous window are supplied at once.
+
+Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset.
+The equal-length gaps of 0, 2, 10, and 50 labels are skipped before another observation is annotated.
+This approach of skipping samples without considering their representativeness can result in harm to predictions.
 \end{itemize}
 
+The experimental design involves the filter conditions that create 24 forms of the original MaFaulDa.
+The four main experiments test hyperparameters on each dataset variation.
+Those are k-neighbors, a number and kind of features in batch learning tumbling windows, and label skips in incremental learning.
+
 \section{Exploratory data analysis of MaFaulDa}
+% To better explain the behavior of the models we examine number of observation per fault category and spatial separability of the groups, ranges and interdependecies of the features.
+
+% Out of 1951 time series, just xx is for inner bearing (A) and xx for outer bearing.
+We can see taht by merging the vertical and horizontal misalignment this label has the most occurence with xx\%.
+Normal class is the less populous with just xx\%.
 \begin{table}[h]
@@
 
+% The inner and outer bearings each have diffent number of recodings made so the total counts differ: xx for bearing A and xx for bearing B.
+After relabeling the normal class became the largest taking up xx\%.
+Bearing A+B just concatanes observations from both beraings so the value is the sum.
+Inbalance ratio as a largest to smallest numbered class is xx \% for original labels and xx \% after relabeling
+
 % Correlation to RPM
@@
     \centering
-    \includegraphics[width=0.8\textwidth]{assets/results/feature-values/corr-to-rpm.png}
+    \includegraphics[width=\textwidth]{assets/results/feature-values/corr-to-rpm.png}
     \caption{Correlation of features to RPM over all experiments}
@@
 \end{figure}
+
+% silhouette score
 

### 2024-04-30 thesis/chapters/preliminaries/acknowledgments.tex
Finish pipeline description in design

@@
 \section*{Poďakovanie}
-{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorba omnoho viac než zachytávajú slová na stránkach.
+{\linespread{1.0}\small Napriek tomu, že tento text je len kvapka v mori záverečných prác, pre mňa bol proces tvorby omnoho viac než zachytávajú slová na stránkach.
 Srdečná vďaka patrí školiteľovi Ing.~Marcelovi Balážovi,~PhD.

### 2024-05-01 thesis/chapters/03-design.tex
Complete MaFaulDa EDA

@@
 The best feature subset from complete sets is picked after ranking the features according to their importance.
+An additional rule is that attributes cannot be added to the same set when they correlate very strongly  $|\mathrm{corr}| > 0.95$.
+The feature with a lower rank is added instead to the set.
+
 The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}.
+The correlation among features can reduce model's prediction power.
 The rank product combines the three latter scores into the ensemble.
@@
 Observations are sorted based on increasing relative severity.
-The faults with the same severity are lined up randomly.
+The faults within levels are shuffled randomly.
 
@@
 The equal-length gaps of 0, 2, 10, and 50 labels are skipped before another observation is annotated.
-This approach of skipping samples without considering their representativeness can result in harm to predictions.
+This approach of skipping samples without considering their representativeness can harm the predictions.
 \end{itemize}
@@
 \section{Exploratory data analysis of MaFaulDa}
-% To better explain the behavior of the models we examine number of observation per fault category and spatial separability of the groups, ranges and interdependecies of the features.
+A better explanation for model behavior is arranged by examining the number of observations per fault category, spatial separability of the distinguished groups, and scales of the attributes and their interdependencies.
 
-% Out of 1951 time series, just xx is for inner bearing (A) and xx for outer bearing.
-We can see taht by merging the vertical and horizontal misalignment this label has the most occurence with xx\%.
-Normal class is the less populous with just xx\%.
+Out of the 1951 time series, the inner bearing (A) has 1438, and the outer bearing (B) has 1393~(Tab.~\ref{tab:design:label-count}).
+Sorce bearing A+B just concatanes observations from both postions so the column sums their counts together.
+The observations for shaft defects are shared regardless of the bearing.
 \begin{table}[h]
@@
 \centering
-\begin{tabular}{|lr|r|r|r|r|r|r|}
+\begin{tabular}{|ll|r|r|r|r|r|r|}
 \hline
-\multicolumn{2}{|l|}{\textbf{Bearing}}                                            & \multicolumn{1}{l|}{A}  & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}  & \multicolumn{1}{l|}{A}   & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}   \\ \hline
-\multicolumn{2}{|l|}{\textbf{Relabel by severity}}                                & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{No}  & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} \\ \hline
+\multicolumn{2}{|l|}{\textbf{Source bearing}}                                            & \multicolumn{1}{l|}{A}  & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}  & \multicolumn{1}{l|}{A}   & \multicolumn{1}{l|}{A+B} & \multicolumn{1}{l|}{B}   \\ \hline
+\multicolumn{2}{|l|}{\textbf{High severity faults}}                                & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{No}  & \multicolumn{1}{l|}{No} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} & \multicolumn{1}{l|}{Yes} \\ \hline
 \multicolumn{1}{|l|}{\multirow{6}{*}{\textbf{Fault}}} & \textbf{misalignment}     & 498                     & 996                      & 498                     & 248                      & 496                      & 248                      \\ \cline{2-8}
@@
 \end{tabular}
-\caption{Number of rows in MaFaulDa according to label}
+\caption{Number of observation in MaFaulDa split by class label according to source bearing}
+\label{tab:design:label-count}
 \end{table}
 
-% The inner and outer bearings each have diffent number of recodings made so the total counts differ: xx for bearing A and xx for bearing B.
-After relabeling the normal class became the largest taking up xx\%.
-Bearing A+B just concatanes observations from both beraings so the value is the sum.
-Inbalance ratio as a largest to smallest numbered class is xx \% for original labels and xx \% after relabeling
+The fusion of vertical and horizontal misalignment gives rise to the label that occurs the most at 34.63\%.
+The baseline class is the least populous at 3.4\% for the inner bearing.
+After relacing low severity faults with the normal status it became the largest with 51.32\%.
+The imbalance ratio as a proportion of the largest to the smallest classes is 10.16 for original labels and 8.58 after relabeling.
 
-% Correlation to RPM
+Exemplary waveforms from each fault class illustrate their
+superficial differences in oscillatory behavior. The files with the highest severity levels and around an average rotational speed of 2500 rpm (42 Hz) are displayed to discern patterns.
 \begin{figure}[h]
     \centering
-    \includegraphics[width=\textwidth]{assets/results/feature-values/corr-to-rpm.png}
-    \caption{Correlation of features to RPM over all experiments}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-TD-A.png}
+        \caption{Time domain for all axis}
+        \label{fig:design:fault-temporal-waveform}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.50\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-faults.png}
+        \caption{Frequency domain in radial direction}
+        \label{fig:design:fault-spectral-waveform}
+    \end{subfigure}
+    \caption{Vibrations from inner bearing (A) for every fault class with the highest fault severity at 2500 rpm}
 \end{figure}
 
-% Feature correlations
+Time-domain waveforms of the 300 ms signal slice are shown in the graphs in Figure \ref{fig:design:fault-temporal-waveform}.
+Subplots for radial, tangential, and axial directions are in columns from left to right.
+Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
+
+The frequency spectrum in Figure \ref{fig:design:fault-spectral-waveform} is obtained by FFT and Hann window of 16384 samples.
+The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz.
+The graph has been cropped in variables to make the most important peaks visible.
+
+The numeric scale of distinct attributes calculated out of signals for bearing A widely differs ~(Fig.~\ref{fig:design:feature-range}).
+The magnitude of three spatial dimensions stretches the scale towards larger values or introduces more outliers.
+Many of the indicators used for fault detection are dimensionless numbers but for others, the information about units of measurement is still attainable.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A.png}
+        \caption{Time-domain features for 1 axis}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
+        \caption{Frequency-domain features for 3 axes}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
+        \caption{Time-domain features for 1 axis}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A.png}
+        \caption{Frequency-domain features for 3 axes}
+    \end{subfigure}
+    \caption{The value ranges of attributes for bearing A, depending on the number of directions that feature is aggregated out of}
+    \label{fig:design:feature-range}
+\end{figure}
+
+Inside the interquartile range of three axis features the peak-to-peak is approximately between 2 - 22 $\mathrm{m/s}^2$, root-mean-square is 0.4 - 2.5 $\mathrm{m/s}^2$, average amplitude change represents 0.05 - 0.45 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$.
+In the frequency domain, the spectral centroid is 100 - 5900 Hz, roll-off frequencies arise below 5000 Hz, roll-on frequencies are below 400 Hz, and entropy occurs from 4 to 12 nats.
+
+Despite the differences in ranges in some instances by several orders of magnitude, there are still dependencies among variables in the complete feature sets.
+The TD set~(Fig.~\ref{fig:design:corr-td}) appears to have less strongly correlated pairs than the FD set~(Fig.~\ref{fig:design:corr-fd}) in terms of Pearson correlation coefficient.
+
 \begin{figure}[h]
@@
         \caption{Time-domain features}
+        \label{fig:design:corr-td}
     \end{subfigure}
@@
         \caption{Frequency-domain features}
+        \label{fig:design:corr-fd}
     \end{subfigure}
-    \caption{Feature correlations in MaFaulDa}
+    \caption{Pearson correlations of variables from inner bearing (A) in feature sets aggregated out of 3 axes}
 \end{figure}
 
-% Features Range
-% Mafaulda
+Crest, impulse, and clearance in TD have correlations of 100\%.
+Other very strongly positively correlated variables are peak-to-peak to root-mean-square at 95\% and average amplitude change at 83\%.
+Kurtosis is strongly correlated with skewness at 72\% and with crest, impulse, and clearance at 66\%.
+Shape and zero-crossing rate are also correlated at 72\%.
+In the FD set the roll-on frequency, energy, and standard deviation are the most uncorrelated to all other variables.
+However, the energy and std are highly correlated to each other.
+Skewness and kurtosis of the frequency spectrum have a strong association of 99\%.
+The rest of the attributes have an absolute value of correlation greater than 68\% in pairs amongst themselves.
+
 \begin{figure}[h]
     \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim1-A.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim3-A.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \caption{Feature range in MaFaulDa}
+    \includegraphics[width=0.8\textwidth]{assets/results/feature-values/corr-to-rpm.png}
+    \caption{Correlation of features to rpm over all experiments}
+    \label{fig:design:rpm-corr}
 \end{figure}
 
-% PCA plot of labels
-% Clusters with true labels
+The faults in the MaFaulDa were measured at several rotational speeds.
+This increases the robustness of the machine-learning model.
+In practice, if the model is trained only at one speed and then the speed alters, the features tied to rpm could inhibit the prediction accuracy.
+The distribution of correlations of each predictor to rpm under all experimental conditions is shown in Figure~\ref{fig:design:rpm-corr}.
+
+The overwhelming majority of predictors are weakly correlated to rotational speed.
+The moderate correlation appears for average amplitude change with the median of 54\% and peak-to-peak with median of 31\%.
+These two features are less suited for idenfifying fault types in variable speed situations.
+
 \begin{figure}[h]
@@
     \end{subfigure} 
-    \caption{PCA of all features to 2 components}
+    \caption{PCA of complete feature set into two principal components (bearing A and 3 axis}
+    \label{fig:design:pca-complete-sets}
 \end{figure}
 
-% Time domain waveforms of different faults
+The separability of fault groups into clusters is qualitatively analyzed by projecting normalized complete feature sets onto the plain utilizing two principal components.
+The transformed TD and FD sets are shown in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned ``normal'' class.
+The decision boundaries that color the feature space around the data points are determined in 0.02x0.02 square areas by k-NN with five neighbours.
+
+Shaft misalignment and bearing ball fault look quite lumped together, whereas imbalance is mixed with cage fault.
+The silhouette score quantifies the amount of cluster overlap which indicates a very weak clustering score with values around 0.08.
+The explained variance with two components is 84.7\% for TD and 86.5\% using original labels.
+
 \begin{figure}[h]
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-TD-A.png}
-        \caption{Time domain}
+        \includegraphics[width=\textwidth]{assets/results/eda/PCA-TD-loading-plot.png}
+        \caption{Time-domain features}
     \end{subfigure}
@@
     \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/eda/mafaulda-faults.png}
-        \caption{Frequency domain (around 2500 rpm)}
+        \includegraphics[width=\textwidth]{assets/results/eda/PCA-FD-loading-plot.png}
+        \caption{Frequency-domain features}
     \end{subfigure} 
-    \caption{MaFaulDa}
+    \caption{PCA loading plots for bearing A}
+    \label{fig:design:pca-loading-plot}
 \end{figure}
 
-% PCA loading plots
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/eda/PCA-explained-variance.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/eda/PCA-TD-loading-plot.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/eda/PCA-FD-loading-plot.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure} 
-    \caption{PCA explained variance and loading plots (A bearing)}
-\end{figure}
+Loading plots of PCA (Fig.~\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
+The first PC in the time domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing rate}.
+The second PC focuses more on the amplitude range: \emph{rms, peak-to-peak, aac}.
 
-% silhouette score
+However, the groups are not as clear-cut for frequency-domain features.
+Overall chaos in frequency spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off}.
 

### 2024-05-01 thesis/chapters/TEXT.tex
Complete MaFaulDa EDA

@@
     \end{subfigure} 
-    \caption{Inner bearing vibrations (A) for each fault category with the highest fault severity at 2500 rpm}
+    \caption{}
 \end{figure}
-
-Temporal domain waveforms of the 300 ms signal slice are shown in the graphs in Figure \ref{fig:design:fault-temporal-waveform}.
-Subplots for radial, tangential, and axial directions are laid out in columns from left to right.
-Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
-
-The frequency spectrum in Figure \ref{fig:design:fault-spectral-waveform} is obtained by FFT and Hann window of length $2^{14}$.
-The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz.
-The graph has been cropped in both axes to make the most important peaks visible.
 
@@
 
-The correlation among features can reduce prediction power if a pair is elected where $|\mathrm{corr}| > 0.95$.
-The feature is not added to the subset when the threshold is exceeded.
-High correlations are more substantial in the temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}.
+ temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}.
 In the spectral domain set \{skewness, kurtosis\} has a strong correlation.
@@
 PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
-Loading plots of PCA (Fig.
-\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
-The first PC in the temporal domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing}.
-The second PC focuses more on the amplitude range: \emph{rms, p-p, aac}.
-
-However, the groups are not as clear-cut for spectral features.
-Overall chaos in spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off, centroid}.
 
@@
 Bearing B exhibits overall worse classification performance because of more noise in the original signal.
-
-%\begin{table}[h]
-%\centering
-%\renewcommand{\arraystretch}{1.2}
-%\begin{adjustbox}{width=\textwidth}
-%
-%\end{tabular}
-%\end{adjustbox}
-%\caption{k-NN model performance trained on all extracted features}
-%\label{tab:design:all-extracted-features}
-%\end{table}
 
@@
 
-The \textbf{tumbling window} simulates regular expert visits annotating observations recorded until that moment.
-Labels for the whole previous window are supplied at once.
 In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
@@
 After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
-
-Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset.
-In the simulation of missing labels, the equal-length gaps are skipped before another observation is annotated.
-This approach of choosing samples to annotate without considering their representativeness results in severe harm to predictions.
 

### 2024-05-02 thesis/chapters/03-design.tex
Complete design

@@
 The decision boundaries that color the feature space around the data points are determined in 0.02x0.02 square areas by k-NN with five neighbours.
+We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
 
@@
 Overall chaos in frequency spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off}.
+PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
 
 \section{Accelerometer data logger}
-% Block diagram of device
+Data acquisition of vibrations from industrial machinery necessitates the assembly of the standalone data logger.
+The required hardware modules of the device include a sensor as a triaxial MEMS accelerometer, a fast persistent memory unit, and a microcontroller to control communication with both peripherals.
+The recording starts with a button press, and the indicator LED provides feedback about the operation in progress.
 
-% HW parameters and mention temporary device
+More detailed specification according to standards creates demands especially on the accelerometer, in terms of bandwidth for linear response to at least 1 kHz, ideally more.
+The sampling rate should be greater than 2 kHz for each of the three axes (6 kSps).
+Out of the options available on the market, we opted for the accelerometers with digital communication bus with more than 12-bit sample resolution, high sensitivity, and low noise density.
+
 \begin{table}[h]
@@
 \textbf{Vendor}                          & STMicroelectronics \\ \hline
-\textbf{Bus}                                     & SPI                \\ \hline
+\textbf{Bus}                             & SPI  (to 10 MHz)               \\ \hline
 \textbf{Axis}                            & 1 or 3             \\ \hline
-\textbf{Range} (g)                               & $\pm$ 2 - 16      \\ \hline
-\textbf{Bandwidth} (kHz)                          & 5 - 6.3            \\ \hline
-\textbf{Sensitivity} (mg/LSB)                    & 0.06 - 0.49       \\ \hline
-\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 75                 \\ \hline
-\textbf{Microcontroller}                         & ESP32-PoE-ISO      \\ \hline
+\textbf{Range}                           & $\pm$ 2 - 16 g (19 - 157 $\mathrm{m/s}^2$)   \\ \hline
+\textbf{Bandwidth}                       & 5 - 6.3 kHz           \\ \hline
+\textbf{Sensitivity}                     & 0.06 - 0.49 mg/LSB      \\ \hline
+\textbf{Noise density} & 75 $\mu \mathrm{g} / \sqrt{\mathrm{Hz}}$ rms                \\ \hline
+\textbf{Output data rate}               & 26.8 kHz             \\ \hline
+\textbf{Sample resolution}              & 16 bit                 \\ \hline
+\textbf{FIFO}                           & 3 kB (512 samples) \\ \hline
+\textbf{Microcontroller}                & \textbf{ESP32-PoE-ISO}      \\ \hline
 \textbf{CPU SoC}                                 & ESP32-WROOM-32     \\ \hline
-\textbf{Output data rate} (kHz)                  & 26.7               \\ \hline
-\textbf{ADC resolution} (bit)                    & 16                 \\ \hline
-\textbf{FIFO}                                    & 3 kB (512 samples) \\ \hline
+\textbf{CPU clock rate}                          & 80 MHz     \\ \hline
 \end{tabular}
@@
 
+The hardware configuration we arrived at for the data logger powered with a power bank via USB connector is in Table~\ref{tab:design:hw-sensors}.
+The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
+The evaluation board for the accelerometer STEVAL-MKI208V1K is connected via a ribbon cable that enables proper attachment to designated places.
+
 \begin{figure}[h]
@@
 	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
-	\caption{Sensor unit hardware block diagram}
+	\caption{Data logger hardware block diagram}
 	\label{fig:design:block-diagram-hw}
@@
 
-% Task communication sequence diagram
-
-% Firmware
-% Timing is crutial 19ms.
-Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
-
-\begin{itemize}
-\itemsep0pt
-\item begin new recording, 
-\item log block of samples into CSV file,
-\item finish recording.
-\end{itemize}
+ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via an SD/MMC bus.
+It enables us to store all samples from FIFO.
+The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
+The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
 
@@
 	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
+	\caption{Activity diagram of data logger firmware functions}
+	\label{fig:design:firmware-activity}
 \end{figure}
+
+The firmware's role lies in coordinating hardware adapters and straightforward vibration acquisition for later analysis.
+The provided functionality is hence minimalistic.
+Two user-driven actions, one periodic event, and one timer-generated event satisfy these basic requirements.
+Activity diagrams outline the steps of the firmware actions~(Fig.~\ref{fig:design:firmware-activity}).
 
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
     \centering
-    \begin{subfigure}[b]{0.17\textwidth}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
+        \caption{Fan speed 1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
+        \caption{Fan speed 2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
+        \caption{Fan speed 3}
+    \end{subfigure}
+    \caption{Frequency spectrum of audio recorded in close proximity to the side of the standing fan}
+    \label{fig:design:fan-speed}
+\end{figure}
+
+\begin{figure}[h]
     \centering
-        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/sensor/standing-fan.jpg}
         \caption{\footnotesize Fan}
@@
     \hfill
-    \begin{subfigure}[b]{0.25\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
     		\centering
-        \includegraphics[width=\textwidth]{assets/design/sensor/copeland-compressor.jpg}
+        \includegraphics[width=\textwidth]{assets/design/sensor/compressor.jpg}
         \caption{\footnotesize Compressor}
@@
     \hfill
-    \begin{subfigure}[b]{0.31\textwidth}
+    \begin{subfigure}[b]{0.49\textwidth}
     		\centering
@@
     \caption{Machines dedicated for vibration measurements}
+    \label{fig:design:machines}
 \end{figure}
@@
 \textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us.
-It serves as a test bed during the sensor unit development.
+It serves as a test bed during the data logger development.
 The sensor is placed on the plastic casing at the back of the drive motor.
 The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
-It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).
+It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 23~Hz ($\pm$ 0.18 Hz).
+Speed estimation was done by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.
 
@@
 The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
-Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.
+Possible measurement locations are located on the sides of the compressor atop the bearings, just above the base and below the scroll.
+Steel casing is not in direct contact with the bearing which causes significant alteration to the signal.
 
-\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station.
+\textbf{Water pumps} are available as three units in municipal drinking water pumping station.
 The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
-
-The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The newer primary pumps with bundled wireless cloud monitoring are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
 The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
-The electric motor provides 400~kW of power (class~\rom{3}).
+The motor \emph{WEG W50} provides 400~kW of power (class~\rom{3}).
+The bearing designations at numbered places for defect frequency  calculations are 6319-C3 (1), 6324-C3 (2), and 6317-2Z (3 \& 4)
 
 The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
-It rotates at 1485 rpm (24.75 Hz), and its electric motor has power of 450~kW (class~\rom{3}).
-Each pump and motor have 2 bearings.
-Therefore, there are 4 measurement positions in total.
+It rotates at 1485 rpm (24.75 Hz), and its electric motor has a power of 450~kW (class~\rom{3}).
+Each pump and motor have two bearings, hence there are four measurement positions.
+
+\section{Data collection methodology}
+Vibration measurement for one placement on the machine involves three trials (two for Sigma pump).
+After each trial, the sensor is detached and attached again to introduce ``noise''.
+The sensor is mounted to the machine on a flat surface with adhesive of thin double-sided carpet tape.
+
+Placements are numbered for simplicity (Fig.~\ref{fig:design:machines}) but the precise description follows the notation of MIMOSA convention from ISO~13373-1.
+The sensor is mounted on compressor's placem: \emph{SFTA001AT000TN} (1), \emph{SFTA002AT000TN} (2), on WEG motor's positions: \emph{MTRA001AT000TN} (1), \emph{MTRA002AT045TN} (2), and on KSB pump positions: \emph{PMPA003AT000TN} (3), \emph{PMPA004AT000TN} (4).
+
+\begin{table}[]
+\begin{tabular}{|l|c|c|ccccc|}
+\hline
+\multirow{2}{*}{\textbf{Machine}}           & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Facility code}}} & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Label}}} & \multicolumn{5}{l|}{\textbf{Date}}                                                                                                                                                                                   \\ \cline{4-8}
+                                            & \multicolumn{1}{l|}{}                                           & \multicolumn{1}{l|}{}                                & \multicolumn{1}{l|}{\textbf{20/02/2024}} & \multicolumn{1}{l|}{\textbf{27/02/2024}} & \multicolumn{1}{l|}{\textbf{05/03/2024}} & \multicolumn{1}{l|}{\textbf{19/03/2024}} & \multicolumn{1}{l|}{\textbf{26/03/2024}} \\ \hline
+\multirow{2}{*}{\textbf{Scroll compressor}} & K3                                                              & C1                                                   & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{$\bigtimes$}         &                                          \\ \cline{2-8}
+                                            & K5                                                              & C2                                                   & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{$\bigtimes$}         &                                          \\ \hline
+\multirow{2}{*}{\textbf{Water pump (KSB)}}  & no.
+1                                                           & P1                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \cline{2-8}
+                                            & no.
+7                                                           & P2                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
+\multirow{2}{*}{\textbf{Pump's motor}}      & no.
+1                                                           & M1                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \cline{2-8}
+                                            & no.
+7                                                           & M2                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
+\textbf{Pump (Sigma)}                       & no.
+5                                                           & P3                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
+\textbf{Motor (Sigma)}                      & no.
+5                                                           & M3                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
+\end{tabular}
+\caption{Data collection schedule}
+\label{fig:design:data-schedule}
+\end{table}
+
+The triaxial recording has a duration 60~s (at $f_s$ = 26.8~kHz) and a 16-bit resolution. One file has 24.6~MiB as a binary stream and 48~MiB in TSV format. 
+Measurements were executed and organized into folders according to schedule in Table~\ref{fig:design:data-schedule}.
+It should be noted that because of operational regulations, the second KSB pump was measured the day after the first.
+The estimated total space requirements for all 92 uncompressed raw recordings is 2.21~GiB and approximately 4.31~GiB as TSV files.
 
@@
         \includegraphics[width=\textwidth]{assets/design/ksb-guard-spectrum.png}
-        \caption{Vibration spectral analysis dashboard}
+        \caption{Vibration frequency analysis dashboard}
     \end{subfigure}
@@
 
-\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}.
-In addition, we are able to export the entire historical record at hourly intervals.
 Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
+We were able to export the historical log of vibration velocity for last year at hourly intervals and sample frequency spectra.
 
@@
 Data compression must occur on edge devices to enable the utilization of wireless low-power wide area networks (LPWAN).
-The protocol stack may differ, so goodput is compared without node configuration metadata and keepalive messages.
+The protocol stack may differ, so goodput in this section is compared without node configuration metadata and keepalive messages.
 
-The machinery monitoring system relies on determining several parameters:
+The machinery monitoring system relies on determining a few parameters:
 \begin{itemize}
 \itemsep0pt
-\item \textbf{Number of source channels} ($S$): comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
-\item \textbf{Sampling frequency} ($f_s$): is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
+\item \textbf{Number of source channels} ($S$) - comprises the number of monitored machines, measurement locations for sensors, and active sensor axes.
+\item \textbf{Sampling frequency} ($f_s$) - is set based on the linear response of the accelerometer, the types of faults intended for detection, and how soon they should be noticed after they arise.
 The higher required sensitivity means a higher sampling rate derived according to the Nyquist theorem.
 At a minimum, it should be 15 kHz to 20 kHz.
-\item \textbf{Interval between successive measurements} ($T$): specifies the minimal response time to sudden failure.
-The more critical the machine is, the interval should be shorter.
+\item \textbf{Interval between successive measurements} ($T$) - specifies the minimal response time to sudden failure.
+The more critical the machine is, the shorter the interval should be.
 The bigger the machine parts, the slower the defect evolves.
-\item \textbf{Duration of valid recording} ($D$): is the captured snapshot of machine unaltered behavior associated with a timestamp.
-Duration should cover at least 3 windows for spectral estimation.
-The spectral resolution of 1 Hz amounts to 3 seconds of signal under such assumptions.
-\item \textbf{Number of extracted features} ($F$): are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of 6 features.
+\item \textbf{Duration of valid recording} ($D$) - is the captured snapshot of machine unaltered behavior associated with a timestamp.
+Duration should cover at least twelve windows for spectral estimation.
+\item \textbf{Number of extracted features} ($F$) - are ideally key trend indicators pointing to symptoms of common malfunctions. We aim for a total of six features.
 \end{itemize}
@@
 As an example to approximate required network goodput and storage in practice, we consider continuous vibration \textbf{monitoring for municipal water pumping station}.
-The station has 3 pumps and 3 electric motors.
+The station has three pumps and three electric motors.
 
-A pump and motor pair have 4 bearings together for drive end and non-drive end positions.
-Each position has a sensor mounted in 3 directions that makes a total of \emph{36 source channels}.
+A pump and motor pair have four bearings together for drive end and non-drive end positions.
+Each position has a sensor mounted in three directions that makes a total of \emph{36 source channels}.
 The sampling frequency at each position is set to \emph{20 kHz}.
-The recordings have \emph{duration of 5 seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
+The recordings have \emph{duration of five seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
 
@@
 Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
-The entire machine's history can be kept in a small flash memory module.
-
-\section{Data collection methodology}
-% UML of experiment
-
-% Measurement plan (calendar and folders) - dataset schema
+The entire history of the machine's health could be stored in a small flash memory module.

### 2024-05-02 thesis/chapters/05-evaluation.tex
Analysis finished - page 37
Complete design

@@
-\chapter{Evaluation} \label{section:evaluation}
+\chapter{Evaluation} \label{chapter:evaluation}
 
@@
 
-\section{Validation of data logger}
-% Validation of firmware on standing fan - speeds
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-1.png}
-        \caption{Speed 1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-2.png}
-        \caption{Speed 2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/standing-fan/fan-audio-speed-3.png}
-        \caption{Speed 3}
-    \end{subfigure}
-    \caption{Frequency spectrum from sound of standing fan}
-\end{figure}
+\section{Industrial dataset analysis}
+
+\subsection{Data logger validation}
 
@@
 \end{figure}
-
-\section{Industrial dataset analysis}
 

### 2024-05-02 thesis/chapters/TEXT.tex
Complete design

@@
 
-\subsection{Statistical tests}
-The statistical tests and visual checks are conducted to assess \textbf{normality and stationary} of time series.
-Half a second of amplitude samples are used from every sensor channel.
-These 25 thousand observations are downsampled tenfold to $2500$.
-
-\textbf{Shapiro-Wilk's test} rejects the null hypothesis (${p < 0.05}$) that data is drawn from a normal distribution under most circumstances.
-The signal has normal distribution when it resembles pink noise lacking a regular pattern or weak exhibition of fault symptoms.
-\textbf{Quantile–quantile plots} confirm non-normal distribution because of the striking samples tilt to the diagonal line.
-
-\textbf{Augmented Dickey-Fuller test} rejects the null hypothesis of unit root (${p < 0.001}$).
-The same is confirmed with the \textbf{autocorrelation} function shape.
-It denotes that the stochastic process is stationary as the oscillation is bounded.
-
 \section{Feature relevance}
@@
 The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}.
-
-The Euclidean norm of feature in the triaxial vector eliminates reliance on the direction of measurement. Value ranges are depicted in Figure~\ref{fig:design:feature-range}.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/feature-range-temporal.png}
-%        \caption{Time-domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/feature-range-spectral.png}
-%        \caption{Frequency-domain features}
-%    \end{subfigure}
-%    \caption{Feature value ranges in inner bearing position (A)}
-%    \label{fig:design:feature-range}
-%\end{figure}
-
-Fault labels and their severities come from the directory structure within the dataset.
-The binary target variable indicating whether to initiate a warning is called an anomaly.
-Anomalies are labeled according to relative fault severity level.
-We decided to investigate two fault severities having levels above 0.6 and 0.9.
-The quantity of observation by fault and anomaly severity is shown in Table \ref{tab:observation-counts}.
-The dataset is substantially unbalanced.
-
-Pearson's correlation of features to rpm is very low in the whole dataset.
-In the temporal domain, the correlation coefficient is within an interval of -0.08 to 0.26.
-In the spectral domain, the correlation to rpm for all FFT window sizes from $2^8$ up to $2^{14}$ is mostly very low from -0.14 up to 0.26, except for the centroid being around 0.35.
-
- temporal domain that are present in these pairs (ordered from the most correlated): \{impulse, clearance\}, \{crest, impulse\}, \{crest, clearance\}, \{pp, rms\}.
-In the spectral domain set \{skewness, kurtosis\} has a strong correlation.
-
-%\begin{figure}[h!]
-%    \centering
-%    \includegraphics[width=0.8\textwidth]{assets/design/pca-explained-variance.png}
-%    \caption{Number of principal components to cumulative explained variance percentage in the inner bearing position}
-%    \label{fig:design:pca-explained-variance} 
-%\end{figure}
-
-The variables are also more inter-correlated in the temporal domain shown by principal component analysis.
-For 95\% of the explained variance of PCA 3 components (98.69\%) are needed in the temporal domain whereas 4 in the spectral domain (95.26\%).
-Figure \ref{fig:design:pca-explained-variance} visualizes cumulative explained variance with an increasing number of principal components.
-
-%\begin{figure}[h!]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-temporal.png}
-%        \caption{Temporal features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/pca-loading-plot-spectral.png}
-%        \caption{Spectral features}
-%    \end{subfigure}
-%    \caption{PCA loading plots for min-max scaled features from the inner bearing position}
-%    \label{fig:design:pca-loading-plot} 
-%\end{figure}
-
-PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
 
@@
 
-Lowering the number of attributes allows visualization of labels in planar scatter plots.
-The data points in 3-dimensional cross-sections are colored by true fault classes of all severities in Figure \ref{fig:design:feature-space-scatter}.
-We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
-
-Cluster overlaps of various defect types are also confirmed by silhouette scores around zero.
-Therefore, the k hyperparameter cannot be increased much, as it would cause the merge of mutually confused categories.
-Low-severity faults should be relabeled as a class without fault to watch out just for alert conditions.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-temporal.png}
-%        \caption{Temporal domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/best-features-scatter-fault-A-spectral.png}
-%        \caption{Spectral domain features}
-%    \end{subfigure} 
-%    \caption{Cross sections of 3-dimensional feature spaces with ground truth labels for best attributes. Features are chosen by rank product method.}
-%    \label{fig:design:feature-space-scatter}
-%\end{figure}
-
 Model performance of the k-NN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
@@
 %\end{figure}
-
-We suspected that the PCA property of maximizing variances in each of the few dimensions would support more separation of clustered groups and would be beneficial in classification.
-The bar chart supports this assumption.
-PCA always produces greater model accuracy than any other method of feature selection.
-The rank product of the three scoring techniques is not better every time, but it balances out aggregated methods to achieve more stable results across testing sets.
-
-In every instance, a subset of spectral features is responsible for better accuracy than a subset of temporal features.
-Presumably, it is so because of many correlated pairs of attributes in the temporal domain.
-Further tests should be made to determine optimal feature subsets and the impact of altering the feature election process.
 
@@
 \section{Sensor hardware and drivers}
-In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller.
-The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).
-
-The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
-ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus.
-It enables us to store all samples from FIFO.
-The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
-The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.
 

### 2024-05-02 thesis/chapters/appendix/B-technical-documentation.tex
Refactor jupyter
Complete design

--- 2023-12-28 thesis/chapters/appendix/C-technical-documentation.tex
@@
 \pagenumbering{arabic}
-\renewcommand*{\thepage}{C-\arabic{page}}
+\renewcommand*{\thepage}{B-\arabic{page}}
 
-\section{Data collection plan}
+% Jupyter notebooks
 
-The vibration measurements will occur monthly for pumps and biweekly for compressors from February 2024 until May 2024.
-\begin{table}[ht]
-\centering
-\renewcommand{\arraystretch}{1.1}
-\begin{tabular}{|l|l|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|p{0.6cm}|}
-\hline
-\textbf{Machine}                                                                      & \textbf{Placement \textbackslash Month} & \multicolumn{2}{p{1.2cm}|}{\textbf{02/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{03/2024}} & \multicolumn{2}{p{1.2cm}|}{\textbf{04/2024}} \\ \hline
-\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#3\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &        \\ \cline{2-8} 
-                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
-\multirow{3}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Compressor\\ AC \#5\end{tabular}}} & SFTA001AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & SFTA002AT000TN                          &         &        &       &        &     &         \\ \cline{2-8} 
-                                                                                      & Steel base (noise)                      &         &        &       &        &     &         \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\multirow{6}{*}{\textbf{Pump Sigma}}                                                  & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & MTRA002AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA003AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & PMPA004AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Motor base (noise)                      & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8}
-                                                                                      & Pump base (noise)                       & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \hline
-\end{tabular}
-\end{table}
-Each measurement will involve 3 trials for each position.
-The sensor is mounted to the machine with adhesive on double-sided carpet tape (placement notation follows MIMOSA convention from ISO~13373-1).
-After every trial, the sensor will be detached and attached again.
+% Python function in package (Sphinx)
 
-The plan was consulted and approved by the machinery owners: VNET~a.s.
-and Bratislavská vodárenská spoločnosť,~a.s.
-Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution.
-Total space requirements for 108 recordings are 990 MiB.
-
-\section{Firmware activities}
-
-Activity diagrams describe three basic actions of firmware for logging accelerometer samples:
-
-\begin{itemize}
-\itemsep0pt
-\item begin new recording, 
-\item log block of samples into CSV file,
-\item finish recording.
-\end{itemize}
-
-\begin{figure}[h]
-    \centering
-	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
-\end{figure}
+% C function of firmware

### 2024-05-02 thesis/chapters/03-design.tex
Work on implementation

@@
 
-\begin{table}[]
-\begin{tabular}{|l|c|c|ccccc|}
+\begin{table}[h]
+\renewcommand{\arraystretch}{1.2}
+\begin{adjustbox}{width=\columnwidth,center}
+\begin{tabular}{|ll|cc|ccc|ccc|}
 \hline
-\multirow{2}{*}{\textbf{Machine}}           & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Facility code}}} & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Label}}} & \multicolumn{5}{l|}{\textbf{Date}}                                                                                                                                                                                   \\ \cline{4-8}
-                                            & \multicolumn{1}{l|}{}                                           & \multicolumn{1}{l|}{}                                & \multicolumn{1}{l|}{\textbf{20/02/2024}} & \multicolumn{1}{l|}{\textbf{27/02/2024}} & \multicolumn{1}{l|}{\textbf{05/03/2024}} & \multicolumn{1}{l|}{\textbf{19/03/2024}} & \multicolumn{1}{l|}{\textbf{26/03/2024}} \\ \hline
-\multirow{2}{*}{\textbf{Scroll compressor}} & K3                                                              & C1                                                   & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{$\bigtimes$}         &                                          \\ \cline{2-8}
-                                            & K5                                                              & C2                                                   & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{$\bigtimes$}         &                                          \\ \hline
-\multirow{2}{*}{\textbf{Water pump (KSB)}}  & no.
-1                                                           & P1                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \cline{2-8}
-                                            & no.
-7                                                           & P2                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
-\multirow{2}{*}{\textbf{Pump's motor}}      & no.
-1                                                           & M1                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \cline{2-8}
-                                            & no.
-7                                                           & M2                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{$\bigtimes$}         & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
-\textbf{Pump (Sigma)}                       & no.
-5                                                           & P3                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
-\textbf{Motor (Sigma)}                      & no.
-5                                                           & M3                                                   & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & \multicolumn{1}{c|}{}                    & $\bigtimes$                              \\ \hline
+\multicolumn{2}{|l|}{\textbf{Machine}}                                     & \multicolumn{2}{l|}{\textbf{Scroll compressor}} & \multicolumn{3}{l|}{\textbf{Water pump}}                                          & \multicolumn{3}{l|}{\textbf{Pump's motor}}                                        \\ \hline
+\multicolumn{2}{|l|}{\textbf{Facility code}}                            & \multicolumn{1}{c|}{K3}           & K5          & \multicolumn{1}{c|}{KSB-1}       & \multicolumn{1}{c|}{KSB-7}       & Sigma-5     & \multicolumn{1}{c|}{KSB-1}       & \multicolumn{1}{c|}{KSB-7}       & Sigma-5     \\ \hline
+\multicolumn{2}{|l|}{\textbf{Label}}                                       & \multicolumn{1}{c|}{C1}           & C2          & \multicolumn{1}{c|}{P1}          & \multicolumn{1}{c|}{P2}          & P3          & \multicolumn{1}{c|}{M1}          & \multicolumn{1}{c|}{M2}          & M3          \\ \hline
+\multicolumn{1}{|l|}{\multirow{5}{*}{\textbf{Date}}} & \textbf{20/02/2024} & \multicolumn{1}{c|}{$\bigtimes$}  & $\bigtimes$ & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             \\ \cline{2-10}
+\multicolumn{1}{|l|}{}                               & \textbf{27/02/2024} & \multicolumn{1}{c|}{}             &             & \multicolumn{1}{c|}{$\bigtimes$} & \multicolumn{1}{c|}{$\bigtimes$} &             & \multicolumn{1}{c|}{$\bigtimes$} & \multicolumn{1}{c|}{$\bigtimes$} &             \\ \cline{2-10}
+\multicolumn{1}{|l|}{}                               & \textbf{05/03/2024} & \multicolumn{1}{c|}{$\bigtimes$}  & $\bigtimes$ & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             \\ \cline{2-10}
+\multicolumn{1}{|l|}{}                               & \textbf{19/03/2024} & \multicolumn{1}{c|}{$\bigtimes$}  & $\bigtimes$ & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             & \multicolumn{1}{c|}{}            & \multicolumn{1}{c|}{}            &             \\ \cline{2-10}
+\multicolumn{1}{|l|}{}                               & \textbf{26/03/2024} & \multicolumn{1}{c|}{}             &             & \multicolumn{1}{c|}{$\bigtimes$} & \multicolumn{1}{c|}{$\bigtimes$} & $\bigtimes$ & \multicolumn{1}{c|}{$\bigtimes$} & \multicolumn{1}{c|}{$\bigtimes$} & $\bigtimes$ \\ \hline
 \end{tabular}
+\end{adjustbox}
 \caption{Data collection schedule}
@@
 It should be noted that because of operational regulations, the second KSB pump was measured the day after the first.
-The estimated total space requirements for all 92 uncompressed raw recordings is 2.21~GiB and approximately 4.31~GiB as TSV files.
+The estimated total space requirements for all 92 uncompressed raw recordings is 2.21~GiB and approximately 4.31~GiB as TSV files (Tab-separated values).
+The dataset shall be called \emph{Pump dataset}.
 

### 2024-05-02 thesis/chapters/04-implementation.tex
Complete assets in thesis
Analysis finished - page 37
Work on implementation

@@
-\chapter{Implementation} \label{section:implementation}
+\chapter{Implementation} \label{chapter:implementation}
+The tools implemented include exploration of datasets using statistical overviews and visualizations, experiments of feature selection which involve machine learning pipeline, and firmware for data logger's hardware.
 
 \section{Data analysis}
-% Jupyter notebook - TSFEL, numpy, pandas (data handling),  scipy (signal processing and stats),   | sklearn, imblearn | matplotlib
+The data processing and data mining on the MaFaulDa and Pump dataset takes place in several \emph{JupyterLab} notebooks written in \emph{Python} language.
+The purpose of individual notebooks is described in detail in Appendix~\ref{appendix:technical-docs}.
+Utility functions are located in separate package \emph{vibrodiagnostics} so that the experiments can be realized under multiple conditions.
+
+The tabular data is handled using \emph{Pandas}dataframes that are training batch models from \emph{scikit-learn} library and \emph{imbalanced-learn}, or online models from \emph{RiverML}.
+The wide variety of graphs and other visualizations are stylized with \emph{Matplotlib} and \emph{Seaborn}.
+Feature calculation is crafted according to mathematical formulas atop libraries \emph{Numpy}, \emph{SciPy}, and \emph{Time Series Feature Extraction Library}~(TSFEL).
+
+\begin{lstlisting}[style=pythonstyle,caption=Rank product of feature matrix X to label column Y,label={lst:rank-product},morekeywords={DataFrame,rank,set_index,sort_values,gmean}]
+METRICS = {
+    "corr": selection.corr_classif, 
+    "f_stat": sklearn.feature_selection.f_classif, 
+    "mi": sklearn.feature_selection.mutual_info_classif }
+r = pandas.DataFrame()
+for name, metric in METRICS.items():
+    # Order the features to leaderboard
+    r[name] = leaderboard  
+ranks = r.rank(axis="rows", method="first", ascending=False)
+return ranks.apply(scipy.stats.gmean, axis=1).sort_values()
+\end{lstlisting}
+
+\begin{lstlisting}[style=pythonstyle,caption=Leaderboard of feature importance metric scores,label={lst:feature-leaderboard},morekeywords={DataFrame,rank,set_index,sort_values,metric,gmean}]
+pandas.DataFrame(zip(X.columns, metric(X, Y)), 
+             columns=["feature", "score"])
+      .set_index("feature")
+      .sort_values(by="score", ascending=False))
+\end{lstlisting}
+
+Since the central focus of this work targets feature selection, the source code listing~\ref{lst:rank-product} and \ref{lst:rank-product} demonstrates the ranking scores calculated for features in data frame X.
+Leaderboards are united by geometric mean to produce rank product ordering.
 
 \section{Firmware}
-% In C, ESP-IDF SDK and FreeRTOS tasks
-% Found driver online
-% Problems with timing - binary write (osciloscope pictures)
+The drivers for low-level interfaces of ESP32 microcontroller and FAT32 filesystem are already available in Espressif ESP-IDF SDK.
+The accelerometer driver is made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
+The entry routine of the firmware mounts the SD card, sets up GPIO pins for LED and button, and executes three \emph{FreeRTOS} tasks.
+Procedures in firmware are described in Appendix~\ref{appendix:technical-docs}.
+The hardware (Fig.~\ref{fig:hw-data-logger}) was built by the thesis consultant based on the complete specification supplied by the author.
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{assets/design/sensor/data-logger.jpg}
+    \caption{Accelerometer Data Logger}
+    \label{fig:hw-data-logger}
+\end{figure}
+
+The tasks run on an event-driven basis through notifications and a queue. They have the following purposes:
+\begin{itemize}
+\itemsep0pt
+\item \textbf{Trigger task} - reacts to notification from button's interrupt handler.
+Depending on whether the recording is in progress, it either starts peripherals and creates a file or stops them and closes the file.
+Button debouncing has the form of a two-second delay when interrupts are ignored.
+The task is pinned to core 1 with priority 2 (higher numbers have more priority).
+\item \textbf{Read task} - waits for notification from 9 ms periodic timer to read around half of the accelerometer's FIFO via half-duplex SPI bus at 8 MHz.
+It sends read-out samples to the queue.
+In case of any buffer overrun, it turns off the LED prematurely.
+The task is pinned to core 0 with priority 1.
+\item \textbf{Write task} - reads the samples from the queue, and after locking the mutex for the opened file, it writes them to the card.
+The file is also manipulated within the trigger task, so the lock prevents race conditions.
+The task is pinned to core 1 with priority 1.
+\end{itemize}
+
+The testing process of the firmware revealed two issues that were resolved subsequently.
+The STEVAL evaluation board is plagued with broken hardware interrupt lines.
+The FIFO watermark interrupt on the INT1 pin of the accelerometer stopped firing after a few seconds and stayed at a high logic level.
+We noted the problem first on the digital multimeter, then confirmed it on an oscilloscope and found the same issue in the vendor's forum thread\footnote{IIS3DWB Interrupt stops triggering while sampling for long periods: \url{https://community.st.com/t5/mems-sensors/iis3dwb-interrupt-stops-triggering-while-sampling-for-long/td-p/203630}}.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/oscilloscope/bin-fomat.jpg}
+        \caption{Binary format}
+        \label{fig:implementation:binary-format}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/oscilloscope/tsv-format.jpg}
+        \caption{TSV format}
+        \label{fig:implementation:tsv-format}
+    \end{subfigure}
+    \caption{Timing issue of writing samples to SD card captured on oscilloscope}
+\end{figure}
+
+Other impedement presented the slow string formatting with \emph{printf} family of functions during the sampling of the accelerometer.
+Direct write of columns to TSV is not possible because the real time deadline could not be met due to high sampling rate.
+This is true even if the queue is utilized and the processing takes place in an another task.
+The hardware FIFO of 512 sample vectors fills up in 19.05 ms.
+
+%TODO
+% After GPIO pin was set to change output level on one buffer write completion the TSV rows took around 70 ms to format and write out as evidenced by Figure~ref{fig:implementation:tsv-format}.
+This overextended the time 3.7 times.
+
+% Timing issue
+% $y = 3.7x$ is monotonically increasing function (y is buffers left to process and x is buffers already processed).
+At some point it surpasses the buffer of any size.
+real-time deadline must satisfy condition $t < 2 \cdot n_{FIFO} \cdot \frac{1}{f_s}$ which is 38.1 ms beyond which the samples get dropped.
+
 % tool for convert bin2csv
+
+%TODO
+% Sensor attached to machines with connector up and pressed gently towards the surface.
+
+%TODO - advise you have to store 5 seconds in memory or write binary then process on second pass in constrained system
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/sensor/sensor.jpg}
+        \caption{Sensor on water pump}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/design/sensor/sensor-compressor.jpg}
+        \caption{Sensor on scroll compressor}
+    \end{subfigure}
+    \caption{Data logger on the machines in measurement positions}
+\end{figure}

### 2024-05-02 thesis/chapters/TEXT.tex
Work on implementation

@@
 The second location is around the outer overhang bearing denoted as \emph{B} position.
-
-\subsection{Fault annotations}
-
-\subsection{Signal filters}
-
-\begin{figure}[ht]
-    \centering
-    \begin{subfigure}[b]{0.44\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-time-waveform.png}
-        \caption{Time domain waveforms}
-        \label{fig:design:fault-temporal-waveform}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.55\textwidth}
-        \includegraphics[width=\textwidth]{assets/design/Mafaulda-A-spectrum-Y-axis.png}
-        \caption{Spectra in radial direction}
-        \label{fig:design:fault-spectral-waveform}
-    \end{subfigure} 
-    \caption{}
-\end{figure}
-
-\section{Feature relevance}
-Attributes described in section \ref{section:feature-extraction} are independently summarized from each sensor position and direction.
-Then similarity score of features is ascertained in relation to a predicted variable.
-The subset of the strongest predictors is chosen based on the order of their perceived importance.
-
-\subsection{Feature extraction}
-Each file in the MaFaulDa contains six accelerometer channels.
-In the feature extraction process, the sequence of samples is split into five parts or 1-second intervals.
-The portions are passed through the same DC removal and low pass filters as previously.
-The rotational speed is derived from speedometer pulses within the chunk.
-
-Signal chunks are converted afterward into \textbf{10 temporal and 11 spectral features}.
-Welch's method for spectrum density estimation averaging over $2^{14}$ long FFT segments after Hann windowing is the source for spectral features.
-The reference implementation of feature calculation is crafted according to mathematical formulas atop of Python packages \emph{SciPy}\footnote{SciPy: \url{https://scipy.org/}} and \emph{Time Series Feature Extraction Library} (TSFEL)\footnote{TSFEL: \url{https://tsfel.readthedocs.io/}}.
 
@@
 More missing labels require recording more observations before the equivalent accuracy is reached.
-
-\chapter{Implementation} \label{section:implementation} 
-The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment.
-Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}).
-
-We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes.
-The collection of the novel dataset is accompanied by an agreed upon schedule.
-
-\section{Sensor hardware and drivers}
-
-The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF SDK\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}.
-The accelerometer driver is also made available by the vendor\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.
-Activity diagrams of required firmware functionality are in Appendix~\ref{appendix:technical-docs}.

### 2024-05-02 thesis/chapters/preliminaries/acknowledgments.tex
Work on implementation

@@
 Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s.
-v sprístupnení čerpadiel na merania a súvisiacich podkladov, a to konkrétne Ing.~Peterovi Csókovi a Ing.~Petrovi Kmeťkovi.
-Rovnako ďakujem za ochotu firme VNET,~a.s., konkrétne Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
+v sprístupnení čerpadiel na merania a súvisiacich podkladov, a to konkrétne Ing.~Petrovi Kmeťkovi a Ing.~Peterovi Csókovi.
+Rovnako ďakujem za ochote firme VNET,~a.s., konkrétne Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
 Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy.

### 2024-05-02 firmware/main/src/main.c

@@ -112,6 +112,7 @@ void push_trigger(void *args)
                 // Stop recording
                 switch_disable();
                 // Stop recorder
+                esp_timer_stop(stop_timer);
                 esp_timer_stop(sampler_timer);
                 // wait for transactions to end
                 vTaskDelay(10 / portTICK_PERIOD_MS);
@@ -220,7 +221,7 @@ void app_main(void)
 
     switch_enable(true, isr_switch);
 
-    xTaskCreatePinnedToCore(push_trigger, "trigger", 4000, NULL, 4, &trigger_task, 1);
-    xTaskCreatePinnedToCore(write_card, "write", 32000, NULL, 2, NULL, 1);
+    xTaskCreatePinnedToCore(push_trigger, "trigger", 4000, NULL, 2, &trigger_task, 1);
+    xTaskCreatePinnedToCore(write_card, "write", 32000, NULL, 1, NULL, 1);
     xTaskCreatePinnedToCore(read_accelerometer, "read", 16000, NULL, 1, &sampler_task, 0);
 }

### 2024-05-02 machine-learning/vibrodiagnostics/mafaulda.py

@@ -109,7 +109,10 @@ def lowpass_filter(
     return pd.Series(data=y, index=data.index)
 
 
-def lowpass_filter_extract(dataframes: List[pd.DataFrame], columns: List[str]) -> List[pd.DataFrame]:
+def lowpass_filter_extract(
+            dataframes: List[pd.DataFrame],
+            columns: List[str]
+        ) -> List[pd.DataFrame]:
     for df in dataframes:
         df[columns] = df[columns].apply(lowpass_filter)
     return dataframes
@@ -179,6 +182,7 @@ def get_classes(df: pd.DataFrame, bearing: str) -> pd.DataFrame:
         df['label'] = df.apply(lambda row: FAULTS[bearing].get(row['fault']), axis=1)
     df['label'] = df['label'].astype('category')
     return df
+
 
 def clean_columns(df: pd.DataFrame) -> pd.DataFrame:
     df = df.dropna()

### 2024-05-03 thesis/chapters/04-implementation.tex
Complete implementation

@@
     \caption{Timing issue of writing samples to SD card captured on oscilloscope}
+    \label{fig:implementation:file-write}
 \end{figure}
 
-Other impedement presented the slow string formatting with \emph{printf} family of functions during the sampling of the accelerometer.
-Direct write of columns to TSV is not possible because the real time deadline could not be met due to high sampling rate.
-This is true even if the queue is utilized and the processing takes place in an another task.
+Another impediment presented the slow string formatting with \emph{printf} family of functions during the accelerometer sampling.
+The readings cannot be written to TSV directly because the real-time (RT) deadline is not met due to the high sampling rate.
+It is true even if the queue is utilized and the processing takes place in another task.
+The binary files from the SD card are converted in bulk to TSV with custom Python command line script \verb|bin2tsv.py|.
+
+During debugging, the pin was set to change the output level immediately before the one buffer started file write and after its completion.
+The scopes in Figure~\ref{fig:implementation:file-write} show the time the write took for binary compared to the TSV format.
+In writing to TSV format, the relation of numbers of already processed buffers $x$ to those left to process $y$ is: $y = 3.7x$.
+It is a monotonically increasing function, so the system would eventually overrun any sized assigned queue.
+
 The hardware FIFO of 512 sample vectors fills up in 19.05 ms.
-
-%TODO
-% After GPIO pin was set to change output level on one buffer write completion the TSV rows took around 70 ms to format and write out as evidenced by Figure~ref{fig:implementation:tsv-format}.
-This overextended the time 3.7 times.
-
-% Timing issue
-% $y = 3.7x$ is monotonically increasing function (y is buffers left to process and x is buffers already processed).
-At some point it surpasses the buffer of any size.
-real-time deadline must satisfy condition $t < 2 \cdot n_{FIFO} \cdot \frac{1}{f_s}$ which is 38.1 ms beyond which the samples get dropped.
-
-% tool for convert bin2csv
-
-%TODO
-% Sensor attached to machines with connector up and pressed gently towards the surface.
-
-%TODO - advise you have to store 5 seconds in memory or write binary then process on second pass in constrained system
+The processing time $t$ has to satisfy inequality for deadline: $t \leq 2 \cdot \frac{1}{f_s} \cdot N_{FIFO} $.
+The RT deadline is 38.1 ms, beyond which the samples get dropped.
+In an embedded device, the short recoding burst (80.4 kSps) would need to be written temporarily in binary format to external memory and processed in two passes.
 
@@
     \caption{Data logger on the machines in measurement positions}
+    \label{fig:implementation:sensor-on-machine}
 \end{figure}
+
+Measurement conditions in the industry and axis orientation of the accelerometer are depicted in Figure~\ref{fig:implementation:sensor-on-machine}.
+The sensor is attached in tape to machines with a connector facing up and is pressed gently toward the surface.

### 2024-05-04 thesis/chapters/03-design.tex
Fix accuracies in tables

@@
 The best feature subset from complete sets is picked after ranking the features according to their importance.
-An additional rule is that attributes cannot be added to the same set when they correlate very strongly  $|\mathrm{corr}| > 0.95$.
-The feature with a lower rank is added instead to the set.
-
 The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}.
@@
         \includegraphics[width=\textwidth]{assets/results/feature-values/features-FD-dim1-A.png}
-        \caption{Frequency-domain features for 3 axes}
+        \caption{Frequency-domain features for 1 axes}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-values/features-TD-dim3-A.png}
-        \caption{Time-domain features for 1 axis}
+        \caption{Time-domain features for 3 axes}
     \end{subfigure}
@@
 
-Inside the interquartile range of three axis features the peak-to-peak is approximately between 2 - 22 $\mathrm{m/s}^2$, root-mean-square is 0.4 - 2.5 $\mathrm{m/s}^2$, average amplitude change represents 0.05 - 0.45 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$.
-In the frequency domain, the spectral centroid is 100 - 5900 Hz, roll-off frequencies arise below 5000 Hz, roll-on frequencies are below 400 Hz, and entropy occurs from 4 to 12 nats.
+Inside the interquartile range of three axis features the peak-to-peak is between 4.89 - 11.39 $\mathrm{m/s}^2$, root-mean-square is 0.56 - 1.31 $\mathrm{m/s}^2$, average amplitude change represents 0.08 - 0.23 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$.
+In the frequency domain, the spectral centroid is in range of 1575 - 4175 Hz, roll-off frequencies arise above 246 and below 4476 Hz, roll-on frequencies are from 50 to 207 Hz, and entropy occurs from 7.57 to 10.94 nats.
 
@@
 The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
-It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 23~Hz ($\pm$ 0.18 Hz).
+It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 22.7~Hz ($\Delta f$ = 0.18 Hz).
 Speed estimation was done by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.
@@
     \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+    		\centering
+        \includegraphics[width=\textwidth]{assets/design/sensor/ksb-cloud.jpg}
+        \caption{KSB Guard Sensor Unit}
+        \label{fig:design:ksb-device}
+    \end{subfigure}
      \caption{KSB Guard cloud monitoring for pumps}
@@
 We were able to export the historical log of vibration velocity for last year at hourly intervals and sample frequency spectra.
+The sensor unit (Fig.~\ref{fig:design:ksb-device}) is permanently attached to KSB pumps on bearing in position no.
+3.
 

### 2024-05-04 thesis/chapters/04-implementation.tex
Fix accuracies in tables

@@
 
-The tabular data is handled using \emph{Pandas}dataframes that are training batch models from \emph{scikit-learn} library and \emph{imbalanced-learn}, or online models from \emph{RiverML}.
+The tabular data is handled using \emph{Pandas} dataframes that are training batch models from \emph{scikit-learn} library and \emph{imbalanced-learn}, or online models from \emph{RiverML}.
 The wide variety of graphs and other visualizations are stylized with \emph{Matplotlib} and \emph{Seaborn}.

### 2024-05-04 thesis/chapters/05-evaluation.tex
Fix accuracies in tables

@@
 \chapter{Evaluation} \label{chapter:evaluation} 
+% Accuracy of supervised learning using k-nearest neighbour classifier model targeted on fault indentification in MaFaulDa dataset.
+Performace of feature selection methods on very low memeber feature sets is compared to accuracies of all possible models with taht number of features
+% Data logger mearuremnt abilities are validated / is checked on a standing fan. Analysis of signals from our Pump dataset. Guide in fault labeling based on characteristic bearing frequencies.W
 
 \section{MaFaulDa in k-nearest neighbors}
+% Four types of experiments: on complete feature sets calculated in time or frequency domain, every combination is enumerated/listed of subsets with same number of features, feature selection techniques are emlored to choose features faster using heuristic/metric of similiarity and then compare the result with overall best.
+Simulate gradual label supply in incremental learning  without recreating it from scratch.
 
@@
 % Confusion matrix
+% Knn with 5 neighbours and Euclidean metric
+% On original labels  and oversampled to most populous majority label testing set of 20\% from original dataset.
+for bearing A to see which classes are mistaken/interchanged in prediction.
+There is 598 observations.
+The label ``normal'' is not falsly attributeted to other class in either feature set.
+But aother classes are assigned to be normal.
+Most mistakes happen on predicting outer race fault which is confused with cage fault, imbalance, and less frequency with misaligment and vise vesa.
+Imbalance of shaft is used for generating bearing faults that is underlying natural reason on high error rate.
+(Fig.~\ref{fig:evaluation:all-features-confusion-matrix})
+
 \begin{figure}[h]
@@
     \caption{Confusion matrix for complete sets of features}
+    \label{fig:evaluation:all-features-confusion-matrix}
 \end{figure}
 
-% Nearest neighbors - how many points have neighbourhood of same class A+B
+% Nearest neighbors - how many points have neighbourhood of same class A
+% e.g. we can say that less that 60\% of dataset neighbour with more than 20 taht majority of neighbouring points is in same class as the data point in question.
+% This similiarity tend to favor TD feature set whose curve decreases less quickly for both labelings of MaFaulDa
 \begin{figure}[h]
@@
 
-% Accuracy based on scenario
-% No optimal K - data is noisy
+% Accuracy based on scenario - validation set in k-fold validation
+% No optimal K - data is noisy - to get stable decision boundaries 
+% the features creating out of all three axis reach more accurate prediction that from only the axis of motion.
+% Chosen time-domain feature set is more accuracy which is observed in other experiments - probable explatations lays in large correlation among features in frequency-domain set.
+% Fastest drop between 1 to 5 neighbours - sometimes 10\% decrese
 \begin{figure}[h]
@@
 % Boxplots
+% More features - the greater accuracy - (how much) - two, three, four chosen because they can be reasonably visualized in spatial graphs or cross sections
+% Compare medians of boxplots - differences
+
+% The more neighbours less accuracy which is same as for all featues - stastically significant
+% Range between IQR is between 5 - 10\% and full domain from distribution is almost 20\%
+
+% Compare all features for bearing A to ranges of feature sets
+
+% Std around 6%
+% Maximum
+
+% Adding from 2 to 3 features inreses maximum acheivable accuracy more than adding forth feature.
+It is by one more for TD than FD.
+It is rounded to whole numbers 6\% and 3\% and after rebaleing 3\% to 2\%.
+For small feature sets the FD features are tad bit better average close to 1.92\% for k = 5 but for other values of k it is not not so.
+The fall in accuracy by raising the number of features slows down.
+% TD (no): FT: 2 (78.31), 3 (85.67), 4 (89.55)   | K: 3 (0.943316), 5 (0.917118), 11 (0.876470)
+% FD (no): FT: 2 (81.52), 3 (87.52), 4 (90.26)   | K: 3 (0.940833), 5 (0.921863), 11 (0.871503)
+% TD (yes): 2 (88.89), 3 (91.71), 4 (93.61)   | K: 3, 5, 11
+% FD (yes): 2 (89.45), 3 (92.18), 4 (93.76)   | K: 3, 5, 11
+
 \begin{figure}[h]
@@
 
+% Comparing test accuracy to train accuracy - large difference - the model is likely overfitting, difference is more pronounced in one axis
+
+% In all methods the norm of three axis are better than using a single one.
+% ACC set / all features / best  triplet / rank product
+% Percentile
+
+% Pecentile of best features in test is calculated against train distribution ACC: 84.07 / 99.17 in TD, ACC: 99.39 in FD. [relabel: ]
+% Rank product picks 90.00 in TD (zerocross, pp, rms), 96.36 percentile of accuracies in FD (entropy, centroid, flux) [95.83 (TD) zerocross, shape, rms; 100.00 (FD) entropy, centroid, flux]
+-
+
+% Most feature selection methods choose 
+% - rank product weeds up weaker method - it get overrulled
+
+% Furure work - more features from one recoding - in windows
+% Different election methods and metrics
+% Combine feature selection with 
+% Find other ML model also suitable HoeffdingTreeClassifier - losing original data for labeling - mechnaism of transforming samples to model represntatin
+
 \begin{figure}[h]
@@
 
-% compare dimensions (table)
 \begin{table}[h]
@@
 PCA PC                                & \multicolumn{1}{r|}{87.90}          & 79.42                              & \multicolumn{1}{r|}{96.67}          & 96.67                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{89.70}          & 81.96                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{89.70}          & 81.96                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & zerocross, pp, skewness                 \\ \hline
 Rank product                          & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & zerocross, shape, pp                    \\ \hline
 Correlation                           & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & shape, zerocross, pp                    \\ \hline
-F statistic                           & \multicolumn{1}{r|}{86.95}          & 78.65                              & \multicolumn{1}{r|}{88.33}          & 95.00                              & 1                                                   & pp, zerocross, aac                      \\ \hline
+F statistic                           & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & pp, zerocross, shape                    \\ \hline
 Mutual information                    & \multicolumn{1}{r|}{86.98}          & 78.28                              & \multicolumn{1}{r|}{89.17}          & 94.17                              & 1                                                   & zerocross, shape, rms                   \\ \hline
@@
 PCA PC                                & \multicolumn{1}{r|}{91.20}          & 84.67                              & \multicolumn{1}{r|}{95.00}          & 93.33                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{91.93}          & 85.47                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & zerocross, pp, rms                      \\ \hline
-Correlation                           & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, shape, pp                    \\ \hline
+Best features                         & \multicolumn{1}{r|}{91.93}          & 85.47                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   & zerocross, pp, skewness                 \\ \hline
+Rank product                          & \multicolumn{1}{r|}{91.21}          & 85.04                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & 3                                                   & zerocross, shape, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{r|}{91.21}          & 85.04                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & 3                                                   & shape, zerocross, rms                   \\ \hline
 F statistic                           & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & rms, pp, zerocross                      \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, pp, shape                    \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{88.24}          & 80.62                              & \multicolumn{1}{r|}{75.83}          & 76.67                              & 3                                                   & zerocross, shape, crest                 \\ \hline
 \end{tabular}
@@
 PCA PC                                & \multicolumn{1}{r|}{83.83}          & 74.43                              & \multicolumn{1}{r|}{77.58}          & 83.03                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{88.93}          & 81.86                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & entropy, roll\_off, flux                \\ \hline
-Correlation                           & \multicolumn{1}{r|}{80.54}          & 68.01                              & \multicolumn{1}{r|}{33.33}          & 31.52                              & 1                                                   & kurtosis, roll\_off, skewness           \\ \hline
-F statistic                           & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & flux, entropy, roll\_off                \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{88.11}          & 80.96                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, roll\_off            \\ \hline
+Best features                         & \multicolumn{1}{r|}{88.93}          & 81.86                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & centroid, roll\_off, flux               \\ \hline
+Rank product                          & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & roll\_off, entropy, flux                \\ \hline
+Correlation                           & \multicolumn{1}{r|}{80.54}          & 68.01                              & \multicolumn{1}{r|}{33.33}          & 31.52                              & 1                                                   & roll\_off, skewness, kurtosis           \\ \hline
+F statistic                           & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & roll\_off, entropy, flux                \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{88.11}          & 80.96                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & roll\_off, entropy, centroid            \\ \hline
 All features                          & \multicolumn{1}{r|}{93.67}          & 88.45                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
 PCA PC                                & \multicolumn{1}{r|}{86.76}          & 78.51                              & \multicolumn{1}{r|}{64.85}          & 70.91                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{92.86}          & 87.52                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
-Correlation                           & \multicolumn{1}{r|}{84.55}          & 75.10                              & \multicolumn{1}{r|}{38.18}          & 42.42                              & 3                                                   & roll\_off, negentropy, skewness         \\ \hline
-F statistic                           & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
+Best features                         & \multicolumn{1}{r|}{92.86}          & 87.52                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   & centroid, roll\_off, entropy            \\ \hline
+Rank product                          & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & 3                                                   & roll\_off, flux, skewness               \\ \hline
+Correlation                           & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & 3                                                   & roll\_off, skewness, flux               \\ \hline
+F statistic                           & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & 3                                                   & roll\_off, flux, skewness               \\ \hline
 Mutual information                    & \multicolumn{1}{r|}{90.73}          & 83.60                              & \multicolumn{1}{r|}{94.55}          & 94.55                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
@@
 PCA PC                                & \multicolumn{1}{r|}{92.67}          & 89.20                              & \multicolumn{1}{r|}{84.17}          & 87.50                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{93.99}          & 91.31                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{93.99}          & 91.31                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & zerocross, aac, kurtosis                \\ \hline
 Rank product                          & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
@@
 F statistic                           & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{91.31}          & 86.99                              & \multicolumn{1}{r|}{67.50}          & 67.50                              & 1                                                   & zerocross, shape, impulse               \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
 All features                          & \multicolumn{1}{r|}{96.42}          & 94.76                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
 PCA PC                                & \multicolumn{1}{r|}{94.63}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.58}          & 91.71                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.58}          & 91.71                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   & zerocross, aac, shape                   \\ \hline
 Rank product                          & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & zerocross, shape, rms                   \\ \hline
@@
 PCA PC                                & \multicolumn{1}{r|}{91.49}          & 87.78                              & \multicolumn{1}{r|}{80.00}          & 86.67                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.13}          & 91.37                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.13}          & 91.37                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   & centroid, roll\_off, flux               \\ \hline
 Rank product                          & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
 Correlation                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, flux, centroid                 \\ \hline
-F statistic                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
+F statistic                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, flux, centroid                 \\ \hline
 Mutual information                    & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & centroid, entropy, flux                 \\ \hline
@@
 PCA PC                                & \multicolumn{1}{r|}{92.14}          & 88.84                              & \multicolumn{1}{r|}{69.09}          & 73.94                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.64}          & 91.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.64}          & 91.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 3                                                   & centroid, roll\_off, entropy            \\ \hline
+Rank product                          & \multicolumn{1}{r|}{93.89}          & 91.24                              & \multicolumn{1}{r|}{95.15}          & 97.58                              & 3                                                   & entropy, noisiness, centroid            \\ \hline
 Correlation                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
 F statistic                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, flux, centroid                 \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{93.32}          & 90.67                              & \multicolumn{1}{r|}{90.91}          & 91.52                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{93.32}          & 90.67                              & \multicolumn{1}{r|}{90.91}          & 91.52                              & 3                                                   & noisiness, roll\_off, entropy           \\ \hline
 \end{tabular}
@@
 \textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
-Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
-Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
-F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
-Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
+Rank product       & 88.97                                                    & 79.82                                                 \\ \hline
+Mutual information & 91.81                                                    & 80.87                                                 \\ \hline
+F statistic        & 86.90                                                    & 79.63                                                 \\ \hline
+Correlation        & 84.49                                                    & 79.04                                                  \\ \hline
 \end{tabular}
@@
                             & \multicolumn{1}{l|}{\textbf{Best in scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
-\textbf{Rank product}       & 151                                                     & 69.91                                            & 90.85                                                  \\ \hline
-\textbf{Mutual information} & 46                                                      & 21.30                                            & 90.35                                                  \\ \hline
-\textbf{Correlation}        & 13                                                      & 6.02                                             & 88.88                                                  \\ \hline
-\textbf{F statistic}        & 6                                                       & 2.78                                             & 78.70                                                  \\ \hline
+\textbf{Rank product}       & 94                                                     & 43.52                                            & 92.38 \\ \hline
+\textbf{Mutual information} & 87                                                      & 40.28                                            & 91.79 \\ \hline
+\textbf{Correlation}        & 26                                                      & 12.04                                             & 97.54 \\ \hline
+\textbf{F statistic}        & 9                                                       & 4.16                                             & 96.10 \\ \hline
 \textbf{$\Sigma$}           & 216                                                     & 100                                       & -                                                      \\ \hline
@@
 
+%%%%%%%%%%
+\clearpage
+
 \subsection{Incremental learning}
@@
         \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
-        \caption{Order of severities}
+        \caption{Order of relative severity levels}
     \end{subfigure}
     \caption{Ordering of faults}
-\end{figure}
-
-% Gradual
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{Gradual learning (window = 1, skip = 0)}
 \end{figure}
@@
 
-\begin{figure}[ht]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=0.5\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
-    \caption{Estimation of rotation speed from vibrations}
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/waveform.png}
+        \caption{Time waveform}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/standing-fan/standing-fan-accel.png}
+        \caption{Estimation of rotation speed}
+    \end{subfigure}
+    \caption{Vibrations from the back of a standing fan in radial direction}
 \end{figure}
@@
 \subsection{Pump long-term monitoring}
-\begin{figure}[h]
-    \centering
-    \includegraphics[width=0.5\textwidth]{assets/design/sensor/ksb-cloud.jpg}
-    \caption{KSB device}
-\end{figure}
 

### 2024-05-04 machine-learning/vibrodiagnostics/models.py

@@ -44,29 +44,24 @@ def find_best_subset(
         X: pd.DataFrame,
         Y: pd.DataFrame,
         metric: str,
-        members: int = 3,
+        members: int,
         kfolds: int = 5
     ):
 
     kf = KFold(n_splits=kfolds, shuffle=True, random_state=10)
     elements = []
 
-    for train_idx, test_idx in kf.split(X, Y):
-        x_train, x_test, y_train, y_test = (
-            X.loc[train_idx].copy(), X.loc[test_idx].copy(),
-            Y.loc[train_idx].copy(), Y.loc[test_idx].copy()
-        )
-        ranks = ranking.batch_feature_ranking(x_train, y_train, metric)
-        if metric != 'rank':
-            synonyms = ranking.compute_correlations(x_train, corr_above=0.95)
-            subset = ranking.best_subset(ranks, synonyms, n=members)
-            output = subset
-        else:
-            output = ranks
-
-        output = list(output.reset_index().head(3)['feature'])
-
-    return output
+    train_idx, test_idx = next(kf.split(X, Y))
+    x_train, x_test, y_train, y_test = (
+        X.loc[train_idx].copy(), X.loc[test_idx].copy(),
+        Y.loc[train_idx].copy(), Y.loc[test_idx].copy()
+    )
+    ranks = ranking.batch_feature_ranking(x_train, y_train, metric)
+    # synonyms = ranking.compute_correlations(x_train, corr_above=0.95)
+    synonyms = set()
+    subset = ranking.best_subset(ranks, synonyms, n=members)
+    subset = subset[subset['rank'] == True].index.to_list()
+    return subset
 
 
 def kfold_accuracy(
@@ -105,7 +100,7 @@ def kfold_accuracy(
     
         # Train k-NN model on all features
         if model_name == 'knn':
-            model = KNeighborsClassifier(n_neighbors=k_neighbors, metric=knn_metric)   #, algorithm='kd_tree')
+            model = KNeighborsClassifier(n_neighbors=k_neighbors, metric=knn_metric)
         elif model_name == 'lda':
             model = LinearDiscriminantAnalysis()
         elif model_name == 'bayes':
@@ -225,8 +220,8 @@ def feature_selection_accuracies(
         Y: pd.DataFrame,
         domain: str,
         models_summary: pd.DataFrame,
-        k_neighbors: int = 5,
-        number_of_features: int = 3,
+        k_neighbors: int,
+        number_of_features: int,
[…]

### 2024-05-04 machine-learning/vibrodiagnostics/visualize.py

@@ -491,6 +491,7 @@ def boxplot_enumerate_models_accuracy(results: pd.DataFrame, metric, plots_col: 
 
             boxplot_data = {}
             for k, models in domain.groupby(by=[inplot_col]):
+                print(fnum, k, models[metric].describe())
                 boxplot_data[k[0]] = models[metric].to_list()
 
             ax[i].boxplot(

### 2024-05-05 thesis/chapters/05-evaluation.tex
Feature selection methods evaluated

--- 2024-05-02 thesis/chapters/05-evaluation.tex
@@
 \chapter{Evaluation} \label{chapter:evaluation}
+The verification of proposed solutions for machinery fault diagnostics is focused on two complementary activities, these are vibration measurement and defect identification.
+The accuracy of supervised learning using the k-nearest neighbour classifier is determined by the MaFaulDa dataset under various experiments.
+Data logger recording is compared to the known reference, and the collected Pump dataset is analyzed.
 
 \section{MaFaulDa in k-nearest neighbors}
+The four outlined experiments involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum.
+First, the attributes are left in the complete count after extraction.
+Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.
 
 \subsection{Complete feature sets}
-% Confusion matrix
+The two full sets of features include ten extracted from time-domain and eleven from frequency-domain of the vibrations.
+The feature spaces can incorrectly interchange different fault labels and better separate out some groups than the others.
+
 \begin{figure}[h]
@@
     \caption{Confusion matrix for complete sets of features}
+    \label{fig:evaluation:all-features-confusion-matrix}
 \end{figure}
 
-% Nearest neighbors - how many points have neighbourhood of same class A+B
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/neighborhood.png}
-        \caption{No severity}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.49\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/all-features/neighborhood-severity.png}
-        \caption{Severity}
-    \end{subfigure}
-    \caption{Neighborhood with same label}
-\end{figure}
+The inner bearing observations are selected to train the k-NN with five neighbours and Euclidean distance metric.
+The attributes are normalized beforehand, rows are oversampled to a majority label, and data is split into training and testing sets with an 80:20 proportion.
+The 598 observation of validation data determines the confusion matrix (Fig.~\ref{fig:evaluation:all-features-confusion-matrix}).
 
-% Accuracy based on scenario
-% No optimal K - data is noisy
+The label ``normal'' is not falsely attributed to other classes in either feature set, but other classes can get assigned to be ``normal''.
+Most mistakes happen while predicting outer race fault, which is confused with cage fault, imbalance, and less frequency with misalignment.
+The shaft imbalance is used for simulating bearing faults, which is a natural reason for this high error rate.
+
 \begin{figure}[h]
@@
     \end{subfigure} 
-    \caption{Accuracy dependency on k-value}
+    \caption{Accuracy on complete feature sets depending on the k-value}
+    \label{fig:evaluation:complete-set-k-value}
 \end{figure}
 
+The increasing number of neighbours used for classification in 5-fold cross-validated k-NN shows a substantial decrease in accuracy on validation sets (Fig.~\ref{fig:evaluation:complete-set-k-value}).
+The most prominent drop in performance of around 10\% occurs at the beginning until the k-value of nine, and then the accuracy curves slowly plateau.
+
+Under every circumstance, the magnitude of the triaxial feature vector reaches better accuracy than those from only the axis of motion for the same source domain and bearing.
+The model for inner bearing A is more accurate than outer bearing B.
+The TD set is generally better in predictions than the FD set for the equivalent k-value.
+The relabeled dataset for high severity has a steeper decrease in accuracy for the same value of neighbours.
+
 \subsection{Feature subset combinations}
-% Boxplots
+The complete sets of predictors are even greatly shrunken to representation that could be presented in 3D plot or in perpendicular cross sections.
+These trend variables could be used in distingushing faults the same way as rms amplitude indicates their presence.
+Each possible combinations of pairs, triplets, and quadruplets constructs a separate k-NN model on which prediction accuracy is evaluated.
+
 \begin{figure}[h]
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-False-False-F3.png}
-        \caption{Time domain features}
+        \caption{Three time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-False-False-F3.png}
+        \caption{Three frequency-domain features}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-False-False-K5.png}
-        \caption{Time domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-False-False-F3.png}
-        \caption{Frequency domain features}
+        \caption{Five neighbours in time domain}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-False-False-K5.png}
-        \caption{Frequency domain features}
+        \caption{Five neighbours in frequency domain}
     \end{subfigure}
-    \caption{Model accuracy distribution (Bearings A+B, Dim = 3, Severity False)}
+    \caption{Model accuracy distribution for bearing A and three axis features}
+    \label{fig:evaluation:model-accuracy}
 \end{figure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-True-False-F3.png}
-        \caption{Time domain features}
+        \caption{Three time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-True-False-F3.png}
+        \caption{Three frequency-domain features}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/TD-3-A-True-False-K5.png}
-        \caption{Time domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-True-False-F3.png}
-        \caption{Frequency domain features}
+        \caption{Five neighbours in time domain}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/FD-3-A-True-False-K5.png}
-        \caption{Frequency domain features}
+        \caption{Five neighbours in frequency domain}
     \end{subfigure}
-    \caption{Model accuracy distribution (Severity True)}
+    \caption{Model accuracy distribution from bearing A and three axis features after relabeling for high severity faults}
+    \label{fig:evaluation:model-accuracy-severity}
 \end{figure}
 
+The distribution of model accuracies is documented on features in both domains coined from three dimensions on bearing A with original and high-severity defect labels.
+The boxplots display the relation of the k-value to accuracy when three features are chosen, and the relation of a number of features to accuracy with five neighbours(Fig.~\ref{fig:evaluation:model-accuracy-severity} and \ref{fig:evaluation:model-accuracy-severity}).
+
+The decrease in accuracy with additional neighbours is apparent and similar to the trend in complete sets of features.
+We are interested in maximum accuracy in the distribution because that is the optimal model feature selection method to try to approach.
+Its reduction is more noticeable between three and five features 3 - 5\%, and almost the same amount between five and eleven neighbours.
+
+The complete sets reach better accuracy than subsets when the number of features is at most three and simultaneously the number of neighbours is five or less.
+For more triaxial features and more neighbours, the complete set is only about 2\% percent worse at the most than subsets because the curse of dimensionality is not so substantial for ten dimensions.
+
+The spread in model accuracies in the interquartile range is from 5 to 10 \%, and measured between whiskers is at a maximum of 25\%.
+The standard deviation is about 7\%.
+Overall, the time-domain features are better than frequency-domain features for these specific feature spaces.
+
+The number of features has a direct proportionality effect on the optimal model accuracy.
+An increase from two to three features has more weight than allowing a fourth attribute.
+The contributions of adding features are around 6\% and 3\%, and the relabeled dataset has an increase of 3\% and 2\%.
+The absolute accuracies are consecutively for 2, 3, and 4 features when k is equal to 5: 78.31\%, 85.67\%, and 89.55\% for the time domain and 81.52\%, 87.52\%, 90.26\% in the frequency domain.
+
 \subsection{Feature selection techniques}
-% Accuracy tables
-% Compare linear complexity accuracy with whole distribution
+The predictors chosen with supervised selection strategies are compared in accuracy and location within the accuracy distribution of exhaustive combinations of same-sized sets and the performance of its source superset.
+The metrics for bivariate feature selection are correlation, F statistic, mutual information, and their ensemble by the rank product.
+The PCA of the complete feature set that retains the same number of features and selection methods serves as a benchmark to tell whether the linear combination or subset gets better performance on the MaFaulDa.
+
+\begin{table}[h]
+\centering
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|l|rr|rr|r|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Domain}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{96.03}          & 92.80                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & TD                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{91.20}          & 84.67                              & \multicolumn{1}{r|}{95.00}          & 93.33                              & TD                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{91.93}          & 85.47                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & TD                                                   & zerocross, pp, skewness                 \\ \hline
+Rank product                          & \multicolumn{1}{r|}{91.21}          & 85.04                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & TD                                                   & zerocross, shape, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{r|}{91.21}          & 85.04                              & \multicolumn{1}{r|}{95.83}          & 97.50                              & TD                                                   & shape, zerocross, rms                   \\ \hline
+F statistic                           & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & TD                                                   & rms, pp, zerocross                      \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{88.24}          & 80.62                              & \multicolumn{1}{r|}{75.83}          & 76.67                              & TD                                                   & zerocross, shape, crest                 \\ \hline
+All features                          & \multicolumn{1}{r|}{93.67}          & 88.45                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & FD                                                  &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{86.76}          & 78.51                              & \multicolumn{1}{r|}{64.85}          & 70.91                              & FD                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{92.86}          & 87.52                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & FD                                                   & centroid, roll\_off, entropy            \\ \hline
+Rank product                          & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & FD                                                   & roll\_off, flux, skewness               \\ \hline
+Correlation                           & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & FD                                                   & roll\_off, skewness, flux               \\ \hline
+F statistic                           & \multicolumn{1}{r|}{85.79}          & 77.18                              & \multicolumn{1}{r|}{51.52}          & 57.58                              & FD                                                   & roll\_off, flux, skewness               \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{90.73}          & 83.60                              & \multicolumn{1}{r|}{94.55}          & 94.55                              & FD                                                   & roll\_off, entropy, noisiness           \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Feature selection method accuracy and percentile within accuracy distribution of all three member subsets. (bearing = A, dimension = 3, k=5)}
+\label{tab:evaluation:fsel}
+\end{table}
+
+\begin{table}[h]
+\centering
+\begin{adjustbox}{width=\textwidth}
+\begin{tabular}{|l|rr|rr|r|l|}
+\hline
+\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Domain}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
+                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
+All features                          & \multicolumn{1}{r|}{96.42}          & 94.76                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & TD                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{94.63}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & TD                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.58}          & 91.71                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & TD                                                   & zerocross, aac, shape                   \\ \hline
+Rank product                          & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & TD                                                   & zerocross, shape, rms                   \\ \hline
+Correlation                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & TD                                                   & zerocross, shape, rms                   \\ \hline
+F statistic                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & TD                                                   & shape, zerocross, rms                   \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{91.90}          & 88.51                              & \multicolumn{1}{r|}{72.50}          & 76.67                              & TD                                                   & zerocross, shape, clearance             \\ \hline
+All features                          & \multicolumn{1}{r|}{95.20}          & 93.20                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & FD                                                   &                                         \\ \hline
+PCA PC                                & \multicolumn{1}{r|}{92.14}          & 88.84                              & \multicolumn{1}{r|}{69.09}          & 73.94                              & FD                                                   &                                         \\ \hline
+Best features                         & \multicolumn{1}{r|}{94.64}          & 91.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & FD                                                   & centroid, roll\_off, entropy            \\ \hline
+Rank product                          & \multicolumn{1}{r|}{93.89}          & 91.24                              & \multicolumn{1}{r|}{95.15}          & 97.58                              & FD                                                   & entropy, noisiness, centroid            \\ \hline
+Correlation                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & FD                                                   & entropy, centroid, flux                 \\ \hline
+F statistic                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & FD                                                   & entropy, flux, centroid                 \\ \hline
+Mutual information                    & \multicolumn{1}{r|}{93.32}          & 90.67                              & \multicolumn{1}{r|}{90.91}          & 91.52                              & FD                                                   & noisiness, roll\_off, entropy           \\ \hline
+\end{tabular}
+\end{adjustbox}
+\caption{Feature selection method accuracy and percentile within accuracy distribution of all three member subsets. (severity, bearing = A, dimension = 3, k=5)}
+\label{tab:evaluation:fsel-severity}
+\end{table}
+
+Table~\ref{tab:evaluation:fsel} compares the concrete case of choosing the three features from each domain on bearing A and k-NN with five neighbours.
+Table~\ref{tab:evaluation:fsel-severity} uses labels for high-severity faults.
+There is a significant difference in train and test accuracy, which means the model is likely overfitting.
+The percentile within the distribution is measured to its respective data, the train or validation set.
+However, the percentile of best features in the test is calculated against train distribution.
+
+Combining the rankings from several metrics is necessary to get consistent results.
+This is evidenced by the variability of the success of selected feature sets in final prediction performance under multiple conditions.
+The PCA with 3 components out of complete feature sets is comparable in accuracy to selection methods with original attributes.
+
+The triplet of variables with the best results is from TD set: zero-crossing rate, peak-to-peak, skewness, and from FD set: centroid, roll-off, and entropy.
+With high severity labels, the best attributes for FD stay the same, but average amplitude change and shape factor are preferred along the zero-crossing rate.
+The rank product picked up roll-off, flux, and skewness for the FD set, which is suboptimal.
+The two of the three methods in the ensemble arrive at the same set overruling the superior set produced by mutual information.
+In the TD set, the zero-crossing rate, shape, and rms, are chosen by rank product.
 
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-TD-train.png}
-        \caption{Time domain features (train)}
+        \caption{Time-domain features (train)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-FD-train.png}
+        \caption{Frequency-domain features (train)}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-TD-test.png}
-        \caption{Time domain features (test)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-FD-train.png}
-        \caption{Frequency domain features (train)}
+        \caption{Time-domain features (test)}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/model-distr-fsel-k5-f3-FD-test.png}
-        \caption{Frequency domain features (test)}
+        \caption{Frequency-domain features (test)}
     \end{subfigure}
-    \caption{Model distibution with feature selection methods (k = 5, f = 3)}
+    \caption{Model accuracy statistical distibutions with feature selection methods for three predictors (k = 5)}
+    \label{fig:evaluation:fsel-model-distr}
 \end{figure}
 
-% compare dimensions (table)
+The entire accuracy distribution for the training and testing set for original labels is drawn in the form of the histogram (Fig.~\ref{fig:evaluation:fsel-model-distr}).
+The results of the chosen predictors are mapped out onto the distribution as vertical lines that stack up near the maximum for the time domain or disperse slightly above the median for the frequency domain.
+The accuracy of all features is unreachable for three feature subsets.
+Another noticeable difference between distributions is their shift down and greater spread in testing compared to training sets.
+
 \begin{table}[h]
+\centering
 \begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|rr|rr|r|l|}
+\begin{tabular}{|l|r|r|}
 \hline
-\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
-                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{92.52}          & 87.68                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{87.90}          & 79.42                              & \multicolumn{1}{r|}{96.67}          & 96.67                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{89.70}          & 81.96                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & zerocross, shape, pp                    \\ \hline
-Correlation                           & \multicolumn{1}{r|}{87.51}          & 79.35                              & \multicolumn{1}{r|}{95.83}          & 96.67                              & 1                                                   & shape, zerocross, pp                    \\ \hline
-F statistic                           & \multicolumn{1}{r|}{86.95}          & 78.65                              & \multicolumn{1}{r|}{88.33}          & 95.00                              & 1                                                   & pp, zerocross, aac                      \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{86.98}          & 78.28                              & \multicolumn{1}{r|}{89.17}          & 94.17                              & 1                                                   & zerocross, shape, rms                   \\ \hline
-All features                          & \multicolumn{1}{r|}{96.03}          & 92.80                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{91.20}          & 84.67                              & \multicolumn{1}{r|}{95.00}          & 93.33                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{91.93}          & 85.47                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & zerocross, pp, rms                      \\ \hline
-Correlation                           & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, shape, pp                    \\ \hline
-F statistic                           & \multicolumn{1}{r|}{90.59}          & 84.07                              & \multicolumn{1}{r|}{91.67}          & 90.00                              & 3                                                   & rms, pp, zerocross                      \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{91.63}          & 85.04                              & \multicolumn{1}{r|}{99.17}          & 95.83                              & 3                                                   & zerocross, pp, shape                    \\ \hline
+\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
+Rank product       & 88.97                                                    & 79.82                                                 \\ \hline
+Mutual information & 91.81                                                    & 80.87                                                 \\ \hline
+F statistic        & 86.90                                                    & 79.63                                                 \\ \hline
+Correlation        & 84.49                                                    & 79.04                                                  \\ \hline
 \end{tabular}
 \end{adjustbox}
-\caption{k=5, f=3, bearing=A, severity=False, domain=TD}
+\caption{Feature selection methods evaluated in summary over all experimental conditions}
+\label{tab:evaluation:compare-fsel-accuracy}
 \end{table}
@@
 \begin{table}[h]
+\centering
 \begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|rr|rr|r|l|}
+\begin{tabular}{|l|r|r|r|}
 \hline
-\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
-                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{88.15}          & 79.99                              & \multicolumn{1}{r|}{99.39}          & 98.18                              & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{83.83}          & 74.43                              & \multicolumn{1}{r|}{77.58}          & 83.03                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{88.93}          & 81.86                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & entropy, roll\_off, flux                \\ \hline
-Correlation                           & \multicolumn{1}{r|}{80.54}          & 68.01                              & \multicolumn{1}{r|}{33.33}          & 31.52                              & 1                                                   & kurtosis, roll\_off, skewness           \\ \hline
-F statistic                           & \multicolumn{1}{r|}{86.87}          & 77.51                              & \multicolumn{1}{r|}{95.76}          & 93.33                              & 1                                                   & flux, entropy, roll\_off                \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{88.11}          & 80.96                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, roll\_off            \\ \hline
-All features                          & \multicolumn{1}{r|}{93.67}          & 88.45                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{86.76}          & 78.51                              & \multicolumn{1}{r|}{64.85}          & 70.91                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{92.86}          & 87.52                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
-Correlation                           & \multicolumn{1}{r|}{84.55}          & 75.10                              & \multicolumn{1}{r|}{38.18}          & 42.42                              & 3                                                   & roll\_off, negentropy, skewness         \\ \hline
-F statistic                           & \multicolumn{1}{r|}{90.70}          & 84.74                              & \multicolumn{1}{r|}{94.55}          & 96.36                              & 3                                                   & roll\_off, flux, centroid               \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{90.73}          & 83.60                              & \multicolumn{1}{r|}{94.55}          & 94.55                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
+                            & \multicolumn{1}{l|}{\textbf{Best in scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
+\textbf{Rank product}       & 94                                                     & 43.52                                            & 92.38 \\ \hline
+\textbf{Mutual information} & 87                                                      & 40.28                                            & 91.79 \\ \hline
+\textbf{Correlation}        & 26                                                      & 12.04                                             & 97.54 \\ \hline
+\textbf{F statistic}        & 9                                                       & 4.16                                             & 96.10 \\ \hline
+\textbf{$\Sigma$}           & 216                                                     & 100                                       & -                                                      \\ \hline
 \end{tabular}
 \end{adjustbox}
-\caption{k=5, f=3, bearing=A, severity=False, domain=FD}
+\caption{The experimental scenarios in which the method is found to be the best}
+\label{tab:evaluation:best-selection-method}
 \end{table}
 
-\begin{table}[h]
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|rr|rr|r|l|}
-\hline
-\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
-                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{94.99}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{92.67}          & 89.20                              & \multicolumn{1}{r|}{84.17}          & 87.50                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{93.99}          & 91.31                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
-Correlation                           & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
-F statistic                           & \multicolumn{1}{r|}{92.71}          & 88.55                              & \multicolumn{1}{r|}{85.00}          & 80.83                              & 1                                                   & zerocross, shape, rms                   \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{91.31}          & 86.99                              & \multicolumn{1}{r|}{67.50}          & 67.50                              & 1                                                   & zerocross, shape, impulse               \\ \hline
-All features                          & \multicolumn{1}{r|}{96.42}          & 94.76                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{94.63}          & 92.07                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.58}          & 91.71                              & \multicolumn{1}{r|}{100.00}         & 99.17                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & zerocross, shape, rms                   \\ \hline
-Correlation                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & zerocross, shape, rms                   \\ \hline
-F statistic                           & \multicolumn{1}{r|}{94.31}          & 91.40                              & \multicolumn{1}{r|}{98.33}          & 95.83                              & 3                                                   & shape, zerocross, rms                   \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{91.90}          & 88.51                              & \multicolumn{1}{r|}{72.50}          & 76.67                              & 3                                                   & zerocross, shape, clearance             \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{k=5, f=3, bearing=A, severity=True, domain=TD}
-\end{table}
-
-\begin{table}[h]
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|l|rr|rr|r|l|}
-\hline
-\multirow{2}{*}{\textbf{Feature set}} & \multicolumn{2}{l|}{\textbf{Accuracy}}                                   & \multicolumn{2}{l|}{\textbf{Percentile}}                                 & \multicolumn{1}{l|}{\multirow{2}{*}{\textbf{Axis}}} & \multirow{2}{*}{\textbf{Best features}} \\ \cline{2-5}
-                                      & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{\textbf{Train}} & \multicolumn{1}{l|}{\textbf{Test}} & \multicolumn{1}{l|}{}                               &                                         \\ \hline
-All features                          & \multicolumn{1}{r|}{94.17}          & 90.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 1                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{91.49}          & 87.78                              & \multicolumn{1}{r|}{80.00}          & 86.67                              & 1                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.13}          & 91.37                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 1                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
-Correlation                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, flux, centroid                 \\ \hline
-F statistic                           & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & entropy, centroid, flux                 \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{93.75}          & 90.29                              & \multicolumn{1}{r|}{99.39}          & 99.39                              & 1                                                   & centroid, entropy, flux                 \\ \hline
-All features                          & \multicolumn{1}{r|}{95.20}          & 93.20                              & \multicolumn{1}{r|}{100.00}         & 100.00                             & 3                                                   &                                         \\ \hline
-PCA PC                                & \multicolumn{1}{r|}{92.14}          & 88.84                              & \multicolumn{1}{r|}{69.09}          & 73.94                              & 3                                                   &                                         \\ \hline
-Best features                         & \multicolumn{1}{r|}{94.64}          & 91.94                              & \multicolumn{1}{r|}{100.00}         & 99.39                              & 3                                                   &                                         \\ \hline
-Rank product                          & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
-Correlation                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, centroid, flux                 \\ \hline
-F statistic                           & \multicolumn{1}{r|}{94.50}          & 92.19                              & \multicolumn{1}{r|}{99.39}          & 100.00                             & 3                                                   & entropy, flux, centroid                 \\ \hline
-Mutual information                    & \multicolumn{1}{r|}{93.32}          & 90.67                              & \multicolumn{1}{r|}{90.91}          & 91.52                              & 3                                                   & roll\_off, entropy, noisiness           \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{k=5, f=3, bearing=A, severity=True, domain=FD}
-\end{table}
-
-% compare percentiles
-% Feature combinations accuracy
 \begin{figure}[h]
@@
     \end{subfigure}
-    \caption{Feature selection method choices}
+    \caption{Quality of choice for feature selection methods}
+    \label{fig:evaluation:kde-fsel-perecentile}
 \end{figure}
 
-% In fsel percentile - mention median from notebook for each method - table
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|r|r|}
-\hline
-\textbf{Method}    & \multicolumn{1}{l|}{\textbf{Median percentile {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Median accuracy {[}\%{]}}} \\ \hline
-Rank product       & 93.94                                                    & 81.84                                                  \\ \hline
-Mutual information & 93.33                                                    & 81.33                                                  \\ \hline
-F statistic        & 91.01                                                    & 81.26                                                  \\ \hline
-Correlation        & 84.11                                                    & 79.25                                                  \\ \hline
-\end{tabular}
-\end{table}
+Under 216 scenarios, the mutual information has better median accuracy (80.87\%) and distribution percentile (91.81\%) followed by rank product with an accuracy of 79.82\% of and percentile of 88.97\% (Tab.~\ref{tab:evaluation:compare-fsel-accuracy}).
+The scenarios are composed of 24 base dataset modifications and options for hyperparameters k-value and number of features.
 
-% Best feature selection methods table (order by best count)
-\begin{table}[h]
-\centering
-\begin{tabular}{|l|r|r|r|}
-\hline
-                            & \multicolumn{1}{l|}{\textbf{Best in scenarios}} & \multicolumn{1}{l|}{\textbf{Scenarios {[}\%{]}}} & \multicolumn{1}{l|}{\textbf{Mean percentile {[}\%{]}}} \\ \hline
-\textbf{Rank product}       & 151                                                     & 69.91                                            & 90.85                                                  \\ \hline
-\textbf{Mutual information} & 46                                                      & 21.30                                            & 90.35                                                  \\ \hline
-\textbf{Correlation}        & 13                                                      & 6.02                                             & 88.88                                                  \\ \hline
-\textbf{F statistic}        & 6                                                       & 2.78                                             & 78.70                                                  \\ \hline
-\textbf{$\Sigma$}           & 216                                                     & 100                                       & -                                                      \\ \hline
-\end{tabular}
-\end{table}
+The rank product was the best method in the majority of 43.52\% scenarios.
+Mutual information comes second in 40.28\% cases, where it is deemed the best strategy (Tab.~\ref{tab:evaluation:best-selection-method}).
+The median accuracy in selected cases is also better for rank product 92.38\% compared to 91.79\% mutual information.
 
-% 2d and 3d plots of best features
-\begin{figure}[ht]
+Kernel density estimate plot (Fig.~\ref{fig:evaluation:kde-fsel-perecentile}) shows the distribution of accuracies for the selection methods and percentiles for predictor subsets they chose.
+The feature selection usually picks variables so that they stay in the upper quartile of the distribution above the 75\% percentile.
+The median accuracy of all methods is around the vicinity of 80\%.
+
+\begin{figure}[h]
     \centering
@@
         \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
-        \caption{Time-domain features}
+        \caption{Time-domain features [89.05\%]}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
-        \caption{Frequency-domain features}
+        \caption{Frequency-domain features [77.18\%]}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
-        \caption{Time-domain features (severity)}
+        \caption{Time-domain features (severity) [91.40\%]}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
-        \caption{Frequency-domain features (severity)}
+        \caption{Frequency-domain features (severity) [91.24\%]}
     \end{subfigure} 
-    \caption{3 Best features and their ranges}
+    \caption{Three features chosen by rank product, ranges of attributes, and prediction accuracy in brackets}
 \end{figure}
 
+The features chosen by rank product are visualized as a three-dimensional scatter plot.
+The colors of data points represent correct labels with ex marks for misses.
+The scales on graph axes are inverse transformed of the min-max scaler.
+The visualization of predicted groups suggests another transform should be applied to even out the distances and handle the outliers.
+
 \subsection{Incremental learning}
-% Ordering of severity
-\begin{figure}[ht]
+Online learning imitates hardened conditions for machinery diagnostics that appear in deployment.
+Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
+The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what is the effect on the k-NN model from routine difficulties associated with the continous labeling process.
+
+\begin{figure}[h]
     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
-        \caption{Order by raising severity}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
+        \caption{Relative severity levels}
+        \label{fig:design:online-count-severity-level}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
-        \caption{Order after relabeing normal class}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-natural.png}
+        \caption{Original labels}
+        \label{fig:design:online-event-order}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/severity-levels.png}
-        \caption{Order of severities}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/incremental-learning/order-severity.png}
+        \caption{High severity labels}
+         \label{fig:design:online-event-order-severity}
     \end{subfigure}
-    \caption{Ordering of faults}
+    \caption{Ordering of faults in dataset according to relative severity levels}
 \end{figure}
 
-% Gradual
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Time-domain features (severity)}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/gradual-TD-severity.png}
-        \caption{Frequency-domain features (severity)}
-    \end{subfigure} 
-    \caption{Gradual learning (window = 1, skip = 0)}
-\end{figure}
+The k-NN models in incremental learning experiments learn on the same base training dataset as in batch learning for bearing A with complete sets of extracted features.
+In this manner, we can compare the training accuracies in the last sample for both models.
+Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
+
+The \textbf{stream of events} is ordered by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}), which ensures steady increments in label counts throughout the simulation (Fig.~\ref{fig:design:online-event-order}).
+The same sorting approach is applied to the dataset where low-severity faults are annotated as baseline observations.
+During most of its lifespan, the machine simulator looks to be in a fine operating state.
+Near the end of the simulation, faults start to develop (Fig.~\ref{fig:design:online-event-order-severity}).
+
+These artificially streamlined event sequences are a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
+It is meant to approximate the gradual overall degradation of the machine.
+
+%
+%Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
+Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement.
+The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
+The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.
+%	
+%During gradual learning, the correct label is supplied after a fixed period passes after its prediction.
+This \textbf{sliding window} simulation examines accuracy every 100 iterations.
+Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).
+%
+%
+%Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly.
+Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
+Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
+%
+%	
+%In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
+%
+%A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
+Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows.
+The true labels are unknown.
+After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
+%
+% 
+%Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
+Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.
+More missing labels require recording more observations before the equivalent accuracy is reached.
 

### 2024-05-05 thesis/chapters/TEXT.tex
Feature selection methods evaluated

@@
-\chapter{Design} \label{chapter:design}
-
 \section{Návrh metód s MaFaulDa}
@@
 \end{figure}
-
-%TODO ---------------------------------------------------------------------------
-\section{Dataset exploration}
-In establishing the viability of methods to be deployed on the sensor node, we explore the MaFaulDa dataset.
-It is the largest known machinery fault collection, so it is possible to create multiple subsets based on required conditions.
-
-One representative recording is first selected in each available fault category.
-The sample is visualized and statistically described in both temporal and spectral domains.
-A whole step-by-step procedure is outlined in the activity diagram (Fig.~\ref{fig:design:mafaulda-preprocessing}).
-
-%\begin{figure}[ht]
-%	\centering
-%	\includegraphics[width=\textwidth]{assets/design/activity-data-exploration.png}
-%	\caption{Activity diagram of MaFaulDa dataset preprocessing}
-%	\label{fig:design:mafaulda-preprocessing}
-%\end{figure}
-
-MaFaulda contains 1951 records labeled with inducted faults of increasing severity.
-The defects were set up on the machine simulator as is mentioned in the part about datasets.
-Time series of the triaxial piezoelectric accelerometers in separate files have a sampling frequency of 50 kHz.
-
-These vibration sensors are placed in two positions.
-The first placement is around the inner underhang bearing named \emph{A} which is closer to the motor.
-The second location is around the outer overhang bearing denoted as \emph{B} position.
-
-\subsection{Feature selection}
-The objective of feature selection is to find a subset of the most relevant predictors in each domain.
-As a starting point, the set consists of 3 non-correlated attributes under diverse conditions.
-Ultimately, a number of chosen features are to be tweaked to increase prediction accuracy.
-Four criteria are combined to put together 24 scenarios that filter rows from MaFaulDa:
-
-In feature evaluation for fault prediction, we use hold-out validation in batch models and progressive valuation in online models.
-Classes in observations for batch models are rebalanced to the majority class with a random oversampling strategy.
-The training and testing set split ratio is 80 to 20.
-Classes for incremental learning are ordered by relative severity level and shuffled within levels.
-
-The best group of attributes is elected based on a training set with multiple methods.
-We compute the mean of the absolute value from point-biserial correlation, F statistic, and mutual information to the predicted variable.
-The features are then ordered in descending order by the received score.
-These individual ranks are combined by rank product to create an ensemble out of the metrics.
-Reference implementation of feature selection metrics uses Python packages Scikit Learn\footnote{SciKit Learn: \url{https://scikit-learn.org/}} in batch learning and RiverML\footnote{RiverML: \url{https://riverml.xyz/}} for online learning.
-
-The choice of features is very sensitive to experimental conditions.
-Tendencies are demonstrated by counting how many triplets the indicator appears in across all possible situations.
-The results of approval voting are shown in Figure~\ref{fig:design:approval-rating-features}.
-The most occurring attributes in the temporal domain are zero-crossing rate, peak-to-peak distance, and average amplitude change.
-the features dominating in the spectral domain are centroid, roll-off, and roll-on.
-
-\section{K-nearest neighbor classifier}
-We utilize the k-nearest neighbor algorithm to check machinery diagnostics abilities with reduced feature sets.
-The k-NN classifier being a lazy learner means it can be adapted easily from offline to online context.
-Training labels are min-max scaled and establish nearest-neighbor decision boundaries for attribute values.
-Voronoi diagrams can display these regions and explain the model in that way.
-Batch learning in k-NN serves here as a target performance whose attainment is desirable with online learning.
-
-\subsection{Batch models}
-Three types of k-NN model experiments run with hold-out validation in a batch setting.
-First, the model learns all extracted features, so no feature selection occurs.
-Then, the brute-force method searches for a combination of three features with the highest training accuracy.
-In the end, the model performance for three attributes chosen by feature selection techniques is compared to principal components.
-
-Two models are created for the target variable in classification with all 10 temporal and 11 spectral features.
-The subset of records includes all rotational speeds on bearing position A.
-Either six fault labels or anomalies above 0.9 severity level are guessed by the model with the same hold-out validation split as before.
-
-Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:KNN-confusion-matrix}.
-In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree.
-The most inaccuracies in the temporal domain are between misalignment and bearing race faults.
-In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.
-
-In anomaly prediction, the error of the first degree is 7 times more prevalent than the error of the second degree.
-False positives are preferable, since we do not want the machine to fail prematurely and not know about it.
-In all cases, spectral features maintain better prediction metrics than all temporal features because of less interdependency among features.
-Bearing B exhibits overall worse classification performance because of more noise in the original signal.
-
-Accuracies and F1 scores in both bearing positions with all extracted features are shown in Table \ref{tab:design:all-extracted-features}.
-Models are overtrained, especially for temporal features, because of the substantial difference between accuracy on training and validation sets.
-Binary classification of anomalies is unsurprisingly more precise in general than the multi-class case.
-Defect-type detection with all features reaches accuracy on the testing set above 98\% for bearing A, and above 90\% for bearing B.
-
-Next, we exhaustively list all combinations of three features and look at the range of model performances generated.
-There are $\binom{n}{3}$ combinations of attribute triplets that entail 120 separate k-NN models for temporal domain features and 165 for the spectral domain.
-The feature set with the best evaluation scores serves as a benchmark for attributes picked by selection techniques.
-The accuracy of the k-NN algorithm for different target variables is in Figure \ref{fig:design:feature-combinations-KNN}.
-
-Features picked combinatorically for predictions are listed in Table \ref{tab:design:feature-combinations-KNN}.
-The worst accuracy occurs for temporal features in multi-class classification, 86\% and 77\% depending on bearing position, as compared to 98\% and 91\% accuracy for spectral features.
-An improvement would come with increasing the number of features, using a different base feature set with greater discriminatory power, or using a more sophisticated model.
-
-\begin{table}[ht!]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|r|r|r|l|r|r|}
-\hline
-\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Training \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Testing \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        & \{zero-crossing, aac, rms\}         & 0.9843                & 0.9792 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, noisiness, entropy\} & 0.9818                & 0.9707               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}         & 0.9701  & 0.9475 \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, kurtosis, entropy\}  & 0.9750                & 0.9505               \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}               & temporal        & \{zero-crossing, aac, rms\}            & 0.9570                & 0.9227 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, std, roll-on\}      & 0.9495                & 0.9185               \\ \cline{2-6} 
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, aac, rms\}     & 0.9173 & 0.8738 \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, std, roll-off\}     & 0.9067                & 0.8584               \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{Features with the highest accuracies on the training set found combinatorically}
-\label{tab:design:feature-combinations-KNN}
-\end{table}
-
-The features picked using the rank product method are shown in Table \ref{tab:design:best-3-features-KNN}.
-Their prediction accuracies in k-NN models are subpar to optimal sets.
-However, the advantage is that the feature election process is not so computationally taxing.
-On bearing A, validation set accuracies for fault diagnostics are 85\% and 92\%, for each of the domains.
-Because of the low k hyperparameter value, models are overtrained either way.
-
-\begin{table}[ht!]
-\centering
-\renewcommand{\arraystretch}{1.2}
-\begin{adjustbox}{width=\textwidth}
-\begin{tabular}{|r|r|r|l|r|r|}
-\hline
-\multicolumn{1}{|l|}{\textbf{Place}} & \multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Target \\ variable\end{tabular}}} & \multicolumn{1}{l|}{\textbf{Domain}} & \multicolumn{1}{l|}{\textbf{Best feature triplet}} & \textbf{\begin{tabular}[c]{@{}l@{}}Train \\ accuracy\end{tabular}} & \textbf{\begin{tabular}[c]{@{}l@{}}Test \\ accuracy\end{tabular}} \\ \hline
-\multirow{4}{*}{A} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}                & temporal        & \{zero-crossing, rms, shape\}              & 0.9743 &	0.9633 \\ \cline{3-6}
-                   &                                               & spectral        & \{centroid, flux, entropy\}       & 0.9654                                       & 0.9474                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, rms, shape\}               & 0.9592 & 0.9274                                     \\ \cline{3-6} 
-                   &                                               & spectral        & \{roll-off, centroid, skewness\} & 0.9504                                       & 0.9210                                      \\ \hline
-\multirow{4}{*}{B} & \multirow{2}{*}{\begin{tabular}[c]{@{}r@{}}anomaly\\ (0.9)\end{tabular}}              & temporal        &             \{zero-crossing, rms, shape\} & 0.9265	 & 0.8835                \\ \cline{3-6}
-                   &                                               & spectral        & \{std, noisiness, entropy\}       & 0.9265                                       & 0.8843                                      \\ \cline{2-6}
-                   & \multirow{2}{*}{fault}                        & temporal        & \{zero-crossing, p-p, aac\}           & 0.9113 &	0.8614                                      \\ \cline{3-6} 
-                   &                                               & spectral        & \{centroid, roll-on, roll-off\} & 0.8914                                       & 0.8390                                      \\ \hline
-\end{tabular}
-\end{adjustbox}
-\caption{Three chosen features with rank product of correlation, F statistic, mutual information and their associated k-NN accuracies.}
-\label{tab:design:best-3-features-KNN}
-\end{table}
-
-Model performance of the k-NN algorithm preceeded by a variety of feature selection methods is compared in Figure \ref{fig:design:KNN-accuracy-batch}.
-The best combination of 3 features always achieves better than when the model is trained on all features.
-This has to do with curse of dimensionality phenomenon.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-train.png}
-%        \caption{Testing set}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/KNN-feature-selection-predictions-test.png}
-%        \caption{Training set}
-%    \end{subfigure} 
-%    \caption{Batch k-NN algorithm prediction accuracy with various feature sets.}
-%    \label{fig:design:KNN-accuracy-batch}
-%\end{figure}
-
-\clearpage
-\subsection{Online models}
-Online learning imitates hardened conditions for machinery diagnostics that appear in deployment.
-Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
-The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what the effect of routine difficulties in the ongoing labeling process is.
-
-The k-NN models in incremental learning experiments learn on the same base training dataset for bearing position A and with all extracted features as in a batch context.
-In this manner, we can compare the training accuracies in the last sample for both models.
-k-NN is set to 5 nearest neighbors and a proximity metric of Euclidian distance.
-Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
-
-The \textbf{stream of events is sorted} by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}) which ensures steady increments in label counts throughout the whole duration of the simulation (Fig.~\ref{fig:design:online-event-order}).
-This constructed event sequence is a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
-It is meant to approximate the gradual overall degradation of the machine.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/Online-event-ordering-fault-train.png}
-%        \caption{Event ordering of faults}
-%        \label{fig:design:online-event-order}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/Online-severity-levels.png}
-%        \caption{Fault severity levels ordering}
-%        \label{fig:design:online-count-severity-level}
-%    \end{subfigure}
-%    \caption{Label sequencing for progressive evaluation}
-%\end{figure}
-
-Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
-Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement.
-The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
-The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.
-
-During gradual learning, the correct label is supplied after a fixed period passes after its prediction.
-This \textbf{sliding window} simulation examines accuracy every 100 iterations.
-Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-temporal.png}
-%        \caption{Principal components from temporal domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/pca-scatter-online-fault-spectral.png}
-%        \caption{Principal components from spectral domain features}
-%    \end{subfigure}
-%    \caption{Classification labels in incremental learning \emph{(from left)}: true labels, predicted labels, mistakes in predictions.}
-%    \label{fig:design:scatter-plot-online}
-%\end{figure}
-
-Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly.
-Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
-Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-temporal-domain-fault.png}
-%        \caption{Temporal domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-accuracy-delay-spectral-domain-fault.png}
-%        \caption{Spectral domain features}
-%    \end{subfigure}
-%    \caption{Incremental learning on all extracted feature with delayed reveal of labels in sliding windows}
-%    \label{fig:design:online-fault-delay-sliding}
-%\end{figure}
-
-In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-temporal-domain-fault.png}
-%        \caption{Temporal domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-delay-spectral-domain-fault.png}
-%        \caption{Spectral domain features}
-%    \end{subfigure}
-%    \caption{Incremental learning on all extracted feature with delayed reveal of labels at regular intervals in tumbing windows}
-%    \label{fig:design:online-fault-delay-tumbling}
-%\end{figure}
-
-A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
-Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows.
-The true labels are unknown.
-After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
-
-%\begin{figure}[ht]
-%    \centering
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-temporal-domain-fault.png}
-%        \caption{Temporal domain features}
-%    \end{subfigure}
-%    \hfill
-%    \begin{subfigure}[b]{0.49\textwidth}
-%        \includegraphics[width=\textwidth]{assets/design/gradual-learning-skip-spectral-domain-fault.png}
-%        \caption{Spectral domain features}
-%    \end{subfigure}
-%    \caption{Incremental learning with missing true labels and sliding window delay of 10 observations}
-%    \label{fig:design:online-label-skip}
-%\end{figure}
-
-Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
-Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.
-More missing labels require recording more observations before the equivalent accuracy is reached.

### 2024-05-05 machine-learning/vibrodiagnostics/visualize.py

@@ -485,9 +485,11 @@ def boxplot_enumerate_models_accuracy(results: pd.DataFrame, metric, plots_col: 
             domain_name = DOMAIN_TITLES[domain_name]
             
             if plots_col == 'k':
-                ax[i].set_title(f'K-neighbors: {fnum}, {domain_name}')
+                # ax[i].set_title(f'K-neighbors: {fnum}, {domain_name}')
+                print(f'K-neighbors: {fnum}, {domain_name}')
             if plots_col == 'f':
-                ax[i].set_title(f'Features: {fnum}, {domain_name}')
+                # ax[i].set_title(f'Features: {fnum}, {domain_name}')
+                print(f'Features: {fnum}, {domain_name}')
 
             boxplot_data = {}
             for k, models in domain.groupby(by=[inplot_col]):
@@ -500,6 +502,7 @@ def boxplot_enumerate_models_accuracy(results: pd.DataFrame, metric, plots_col: 
                 medianprops={'linewidth': 2, 'color': 'black'},
                 notch=True
             )
+            ax[i].set_ylim(0.5, 1)
             ax[i].set_ylabel('Accuracy')
             if plots_col == 'f':
                 ax[i].set_xlabel('K-neighbors')

### 2024-05-06 thesis/chapters/05-evaluation.tex
Complete incremental learning

@@
 
-\begin{table}[h]
+\begin{table}[]
 \centering
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
     \centering
@@
         \includegraphics[width=\textwidth]{assets/results/feature-combinations/fsel-percentile.png}
-        \caption{Percentile}
+        \caption{Percentile in distribution of accuracies}
     \end{subfigure}
@@
     \label{fig:evaluation:kde-fsel-perecentile}
+\end{figure}
+
+\begin{figure}[t]
+    \centering
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
+        \caption{TD [89.05\%]}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
+        \caption{FD [77.18\%]}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
+        \caption{TD (s) [91.40\%]}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.24\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
+        \caption{FD (s) [91.24\%]}
+    \end{subfigure} 
+    \caption{Three features in both domains chosen by rank product with prediction accuracy in brackets. Relabeled dataset is marked with (s)}
 \end{figure}
@@
 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/TD.png}
-        \caption{Time-domain features [89.05\%]}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/FD.png}
-        \caption{Frequency-domain features [77.18\%]}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/TD-severity.png}
-        \caption{Time-domain features (severity) [91.40\%]}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/labels/FD-severity.png}
-        \caption{Frequency-domain features (severity) [91.24\%]}
-    \end{subfigure} 
-    \caption{Three features chosen by rank product, ranges of attributes, and prediction accuracy in brackets}
-\end{figure}
-
 The features chosen by rank product are visualized as a three-dimensional scatter plot.
@@
 Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
-The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what is the effect on the k-NN model from routine difficulties associated with the continous labeling process.
+The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what is the effect on the classifier from routine difficulties associated with the continous labeling process.
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 The \textbf{stream of events} is ordered by rising severity levels (Fig.~\ref{fig:design:online-count-severity-level}), which ensures steady increments in label counts throughout the simulation (Fig.~\ref{fig:design:online-event-order}).
-The same sorting approach is applied to the dataset where low-severity faults are annotated as baseline observations.
+The same sorting approach is applied to the dataset where low-severity faults are annotated as baseline.
 During most of its lifespan, the machine simulator looks to be in a fine operating state.
 Near the end of the simulation, faults start to develop (Fig.~\ref{fig:design:online-event-order-severity}).
-
-These artificially streamlined event sequences are a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
+These artificially streamed event sequences are a bit unrealistic because all types of faults never begin to appear simultaneously with equal strengths.
 It is meant to approximate the gradual overall degradation of the machine.
 
-%
-%Major breaking points in the stream are after 1171 observations out of 5751, where all 203 normal conditions are consumed in the training process.
-Counters of other faults show that model predictions are skewed towards more represented classes of imbalance and misalignement.
-The uneven evolution of category counts in a stream impacts the development of accuracy in the remaining experiments.
-The hold-out validation accuracies of comparable batch models are 97.36\% \emph{(temporal features)} and 98.36\% \emph{(spectral features)}.
-%	
-%During gradual learning, the correct label is supplied after a fixed period passes after its prediction.
-This \textbf{sliding window} simulation examines accuracy every 100 iterations.
-Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).
-%
-%
-%Accuracies after sequentially seeing all samples 96.78\% in temporal domain and 89.11\% in spectral domain when labels are shown instantly.
-Scatter plots in Figure~\ref{fig:design:scatter-plot-online} visualize mistakes in predictions projected onto two principal components.
-Labeling delay of 250 observations causes accuracy to drop to 83.94\% \emph{(temporal)} and 78.81\% \emph{(spectral)}.
-%
-%	
-%In the final sample, the accuracies are 89.11\% \emph{(temporal)} and 90.38\% \emph{(spectral)} with immediate feedback, and 83.08\% \emph{(temporal)} and 85.01\% \emph{(spectral)} with window length of 250 samples (Fig.~\ref{fig:design:online-fault-delay-tumbling}).
-%
-%A \textbf{tumbling window} is more accurate according to progressive valuation because the labeling delay decreases towards the window's end.
-Initial 0\% accuracy is caused by a warming-up period in data collection during the span of the first few windows.
-The true labels are unknown.
-After just a handful of windows in the beginning, accuracy jumps above 60\% and stabilizes after 1000 observations.
-%
-% 
-%Labeling just every \nth{5} sample (25\% of the total dataset) with a sliding window delay of 10 samples reduces accuracy for the model out of temporal features by 8.41\% to 80.39\%, and by 7.33\% for spectral features to accuracy of 82.01\% (Fig.~\ref{fig:design:online-label-skip}).
-Even if only 1\% of the dataset is annotated (every \nth{100} sample), the model out of spectral features retained an accuracy of 65.17\% that is 4.41\% better than for temporal features.
-More missing labels require recording more observations before the equivalent accuracy is reached.
+A significant change in the data stream occurs after 294 out of 1438 observations (or after 737 for high severity faults) when all 49 (or 737) normal conditions are consumed in the training process.
+Counters of other faults show that predictions are skewed towards more represented imbalance and misalignement.
+The uneven evolution of categories in a stream impacts the development of accuracy in the remaining experiments.
+The test accuracies of comparable batch models from the three best features are 85.47\% (TD), 87.52\% (FD), 91.71\% (TD severity), and 91.94\% (FD severity).
 
-% Tumbling windows
-\begin{figure}[h]
+\begin{figure}[]
     \centering
@@
     \end{subfigure} 
-    \caption{Tumbling window in incremental learning}
+    \caption{Tumbling window during incremental learning of lengths 1, 10, 100}
+    \label{fig:evaluation:tumbling-window-online}
 \end{figure}
 
-% % Label skips and parts of dataset
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-TD-skip.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/all-features-FD-skip.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-TD.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/incremental-learning/skip-labels-FD.png}
-        \caption{Frequency-domain features}
-    \end{subfigure} 
-    \caption{Skip labels in incremental learning}
-\end{figure}
-
-\begin{figure}[h]
+\begin{figure}[]
     \centering
@@
     \end{subfigure} 
-    \caption{Skip labels in incremental learning with different sizes}
+    \caption{Omission of labels during incremental learning with tumbing window of length 10 and gaps of size 0, 10, and 50 samples}
+    \label{fig:evaluation:label-skips-online}
 \end{figure}
 
+During gradual learning, the correct labels are supplied in bulk at a fixed period.
+Labeling delay in \textbf{tumbling window} decreases towards the window's end.
+Figure~\ref{fig:evaluation:tumbling-window-online} plots the evolution of the k-NN model's distribution of accuracy for windows of size 1, 10, and 100 observations.
+The models consist of three predictors and use five neighbours for prediction.
+Each window length is described with three curves of identical colour.
+The median is drawn with a solid line, the maximum with a dash-dotted line, and the minimum with a dashed line.
+
+Initial zero accuracy is caused by a warming-up period in data collection during the span of the first few windows.
+The true labels are unknown at that point.
+After just a handful of windows in the beginning, accuracy jumps above 60\% for the best triplet of attributes and stabilizes after 400 observations.
+In an alternative labeling scheme, the accuracy for one class is 100\% and only after encountering other fault types, it decreases to a level above 75\% for the best set.
+
+The top accuracies after sequentially seeing samples in the longest tumbling windows of 100 observations are 75.71\% (TD), 76.98\% (FD), 76.98\% (TD severity), and 80.56\% (FD severity).
+The degradations in accuracy when compared to the batch model are by 9.76\% (TD), 10.54\% (FD), 14.73\% (TD severity), and 11.38\% (FD severity).
+The effect of severe performance hit could be attributed to unbalanced data based on the analysis chapter.
+The online multiclass oversampling method would need to be inserted into the pipeline to prove this hypothesis.
+
+Labeling every \nth{10} samples (to 10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels.
+Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}).
+More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.
+
+%TODO
 \section{Industrial dataset analysis}

### 2024-05-06 thesis/chapters/preliminaries/acknowledgments.tex
Complete implementation
Complete incremental learning

@@
 zo Strojníckej fakulty STU.
-Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s.
-v sprístupnení čerpadiel na merania a súvisiacich podkladov, a to konkrétne Ing.~Petrovi Kmeťkovi a Ing.~Peterovi Csókovi.
-Rovnako ďakujem za ochote firme VNET,~a.s., konkrétne Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
+Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petrovi Kmeťkovi a Ing.~Peterovi Csókovi, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
+Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
 Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy.

### 2024-05-07 thesis/chapters/05-evaluation.tex
Complete evaluation

@@
 \section{MaFaulDa in k-nearest neighbors}
-The four outlined experiments involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum.
+The four outlined experiments on MaFaulDa involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum.
 First, the attributes are left in the complete count after extraction.
@@
 
-Labeling every \nth{10} samples (to 10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels.
+Labeling every \nth{10} sample (10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels.
 Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}).
@@
 
-%TODO
 \section{Industrial dataset analysis}
+The latter part of the solution evaluation focuses on signal properties of vibrations from air compressors, water pumps, and electric induction motors.
+At first, the accelerometer data logger functionality is tested, and its precision is checked up in the known situations.
+Our custom dataset is compiled from collected measurements during regular operations of machines.
+The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram.
+The methodology is carried out to diagnose the current status of water pumps.
+The presence of fault is confronted with sensor logs from the pump vendor.
 
-\subsection{Data logger validation}
+\subsection{Data logger verification}
+Data logger capabilities were verified by capturing vibrations on the back of the plastic casing for the electric motor of the standing fan.
+The recording is able to run continuously for more than one minute without dropping any samples.
+The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}).
+The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on Beaglebone Black, albeit with lower sensitivity.
 
@@
         \caption{Time waveform}
+        \label{fig:evaluation:logger-waveform}
     \end{subfigure}
@@
         \caption{Estimation of rotation speed}
+        \label{fig:evaluation:logger-fan-speed}
     \end{subfigure}
-    \caption{Vibrations from the back of a standing fan in radial direction}
+    \caption{Vibrations from the back of a standing fan in the radial direction}
 \end{figure}
 
-\subsection{Feature ranges}
-% Amplitude histograms - 20m/s^2, 40m/s^2, 150m/s^
-% Histograms of machinery measurements
+Time waveform captures mostly regular patterns of oscillatory motion  (Fig.~\ref{fig:evaluation:logger-waveform}).
+At slower speeds, the vibrations are higher because the fan is less stable and wobbles around the support.
+Timestamps from the sensor calibrate the sampling frequency from the theoretical 26667 Hz to the actual 26866 Hz.
+The estimate of fan rotational speed (Fig.~\ref{fig:evaluation:logger-fan-speed}) is accurate within the margin of error.
 
-% Box plots of features
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
-        \caption{Time-domain features}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
-        \caption{Frequency-domain features}
-    \end{subfigure}
-    \caption{Feature range in pumps}
-\end{figure}
-
-\subsection{Time-frequency waveforms}
+\subsection{Signal waveforms}
 \begin{figure}[h]
@@
         \includegraphics[width=\textwidth]{assets/results/eda/frequency-spectrum-compressors.png}
-        \caption{Compressor}
+        \caption{Compressors}
     \end{subfigure} 
-    \caption{Frequency domain}
+    \caption{Wideband frequency waveform of machinery vibartions in Pump dataset}
+    \label{fig:evaluation:wideband-frequencies}
 \end{figure}
 
-% Time-frequency spectrum
+The overview of wideband vibration frequency spectra from various sensor placements shows clear distinctions among the machines.
+The recordings in Figure~\ref{fig:evaluation:wideband-frequencies} present consistent shapes of waveforms found during repeated trials.
+The spectra are Welch's average of 32768 long windows with 50\% overlap over minute of recording.
 
-% Low frequencies (under 1KHz)
+The electric motor signals are polluted by noise from the wind blowing out of a large cooling fan at the back of the motor.
+The M2 in place two compared to M1 has elevated amplitudes above 4 kHz.
+The pumps have richer signal content, likely due to the flow of water split into several frequency bands.
+The outer bearing (4) has a more attenuated amplitude above 1.5 kHz than the inner bearing (3).
+The P2 exhibits less vibration in comparable bands in general.
+The compressor casing produces a series of harmonics of rotational frequency, which are stronger near the scroll and suction valve than near the base.
 
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT-1kHz.png}
-        \caption{K3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT-1kHz.png}
-        \caption{M1-2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT-1kHz.png}
-        \caption{P1-3}
-    \end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT-1kHz.png}
-        \caption{P3-3}
-    \end{subfigure}
-    \caption{Time frequency spectrum}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
-        \caption{Pump P1 turns off}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
-        \caption{Pump P2 turn on}
-    \end{subfigure}
-\end{figure}
-
-\subsection{Bearing defect frequencies}
-% Domain expert analysis
-% Bearing frequencies table
 \begin{table}[h]
@@
 \hline
-\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{Motor \#1}} & \multicolumn{1}{l|}{\textbf{Motor \#2}} & \multicolumn{1}{l|}{\textbf{Pump \#3 \& \#4}} \\ \hline
+\textbf{Placement}     & \multicolumn{1}{l|}{\textbf{M1}} & \multicolumn{1}{l|}{\textbf{M2}} & \multicolumn{1}{l|}{\textbf{P3, P4}} \\ \hline
 \textbf{Bearing}       & \multicolumn{1}{l|}{6319-C3}            & \multicolumn{1}{l|}{6324-C3}            & \multicolumn{1}{l|}{6317-2Z}                  \\ \hline
-\textbf{$n$}           & 8                                       & 8                                       & 8                                             \\ \hline
-\textbf{$f_s$}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
-\textbf{$d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
-\textbf{$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
-\textbf{$\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
+\textbf{Rolling elements $n$}           & 8                                       & 8                                       & 8                                             \\ \hline
+\textbf{Rotational speed $f_s$ {[}rpm{]}}         & 1493                                    & 1493                                    & 1493                                          \\ \hline
+\textbf{Inner diameter $d$ {[}mm{]}}  & 33.12                                   & 41.28                                   & 30.00                                         \\ \hline
+\textbf{Outer diameter$D$ {[}mm{]}}  & 147.5                                   & 190.0                                   & 132.5                                         \\ \hline
+\textbf{Contact angle $\beta$}       & 0                                       & 0                                       & 0                                             \\ \hline
 \textbf{RPM {[}Hz{]}}  & 24.88                                   & 24.88                                   & 24.88                                         \\ \hline
@@
 \end{tabular}
+\caption{Bearing characteristic harmonic frequencies of pumps and their motors}
+\label{tab:evaluation:bearing-freq-pump}
 \end{table}
 
-% Bearing defect frequencies
 \begin{figure}[h]
@@
     \end{subfigure}
+    \caption{Characteric bearing frequencies of pumps}
+    \label{fig:evaluation:bearing-freq}
 \end{figure}
 
-\subsection{Pump long-term monitoring}
+Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and then they approved the following results.
+Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2.
+It can be assumed that those frequencies will be the reason for their damage in the future.
+The absolute acceleration is minuscule in current frequency bands and year-long sensor log of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).
 
-% Total vibration levels - challange - long-live span (5 years)
 \begin{figure}[h]
@@
     \end{subfigure}
-    \caption{Vibration levels}
+    \caption{Vibration rms levels for a period over a year from KSB Guard}
+    \label{fig:evaluation:ksb-guard-rms-vibartions}
 \end{figure}
 
-% Reverse engineer of spectra (low resolution)
+Therefore, the current results suggest that the bearings are in flawless condition.
+During the over five years the pump has been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance.
+This underscores the difficulty of the scarcity of non-faulty states in industrial environments.
+The monitoring is better suited for situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.
+
 \begin{figure}[h]
     \centering
-    \includegraphics[width=0.8\textwidth]{assets/results/ksb-cloud/spectrum.png}
-    \caption{Frequency spectrum}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/K3-z-STFT-1kHz.png}
+        \caption{C1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/M1-2-z-STFT-1kHz.png}
+        \caption{M1-2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-3-z-STFT-1kHz.png}
+        \caption{P1-3}
+    \end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P3-3-z-STFT-1kHz.png}
+        \caption{P3-3}
+    \end{subfigure}
+    \caption{Machinery vibration spectrograms ($f_s$ = 26.8~kHz, $w$ = 8~kS)}
+    \label{fig:evaluation:spectrograms}
 \end{figure}
+
+Spectrograms point out that under constant machine load, the significant frequencies stay more or less unchanged over time (Fig~\ref{fig:evaluation:spectrograms}).
+The resolution of the chart unit area is 306.95 ms and 3.26 Hz.
+Its magnitude is colored for decibel value.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P1-slow-down.png}
+        \caption{P1 turns off ($w$ = 4~kS)}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/time-frequency-spectrum/P2-speed-up.png}
+        \caption{P2 turns on ($w$ = 32~kS)}
+        \label{fig:evaluation-sigma-pump-interference}
+    \end{subfigure}
+    \caption{Vibrations of water pumps during switch over ($f_s$ = 26.8~kHz)}
+    \label{fig:evaluation:pump-switch-over}
+\end{figure}
+
+The water pump switch on and off creates a fast change in shaft speed, which cannot be analyzed for resonance bands with enough time resolution by an automatic system at a chosen sampling rate.
+Due to inertia, slowing down takes about 10 seconds, whereas the speed up is half a second (Fig.~\ref{fig:evaluation:pump-switch-over}.
+The interference from excessive vibrations of the adjacent Sigma pump is picked up by the accelerometer on the KSB pump just before their switchover occurs (Fig~\ref{fig:evaluation-sigma-pump-interference}).
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-TD-dim-3.png}
+        \caption{Time-domain features}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{\textwidth}
+        \includegraphics[width=\textwidth]{assets/results/feature-values/pumps-FD-dim-3.png}
+        \caption{Frequency-domain features}
+    \end{subfigure}
+    \caption{The atrribute value ranges of Pump dataset}
+\end{figure}
+
+The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}).
+The increses can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

### 2024-05-07 thesis/chapters/06-conclusion.tex
Feature selection methods evaluated
Complete evaluation

--- 2024-04-13 thesis/chapters/06-conclusion.tex
@@
 Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343).
-These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.
+These formulas compute ten features summarizing the waveform in the temporal domain and eleven features characterizing spectral density estimation in axis of motion or all three spatial directions \textbf{(RQ1)}.
 
@@
 Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%.
-The spectral features reach higher accuracies than temporal because of their smaller interdependency \textbf{(RQ3)}.
+The time-domain set of features reach higher accuracies than frequency-domain set because of their smaller interdependency \textbf{(RQ3)}.
 
@@
 No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively.
+%TODO wtf
 Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.
@@
 
-Conclusions so far have been made on the MaFaulDa dataset imitating the realistic conditions.
-Therefore, in proper validation of the proposed solution in practice, we will compare it with the custom-made dataset.
-
 The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations.
@@
 
-Feature selection methods should be incorporated into incremental learning.
-Hyperparameters shall be adjusted, and the balancing method used to increase model performance.
-The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.
+%TODO
+% Future work
+% - long term dataset from machinery until failure or propose way for factories to artifically train model for new machinery - make the system machine and placement independent
+% - more diffenent feature set from one recoding - in windows
+% - combine feature selection with incremntal learining
+% - Different election methods and metrics
+% - Find other ML model also suitable HoeffdingTreeClassifier - losing original data for labeling - mechnaism of transforming samples to model represntatin
+% - Monitor more machines and combine their result with federated learning
+% - Monitor faults of different equipment - moving wheels of the train or train tracks
+
+% Main points of the thesis assigments namely effectivness representation of machinery faults in succint fashion and performance in machine learining diagnostics models has been compared extensively.

### 2024-05-07 thesis/chapters/preliminaries/acknowledgments.tex
Complete evaluation

@@
 a konzultantovi Ing.~Lukášovi Doubravskému z firmy R-DAS,~s.r.o.
-Obaja boli otvorení mojim všemožným nápadom a podporovali ma v ich realizácii aj cez mnohé ťažkosti.
+Obaja boli otvorení mojim všemožným nápadom a neochvejne ma podporovali v ich realizácii aj cez mnohé ťažkosti.
 Za praktický expertný pohľad na vibrodiagnostiku vďačím prof.
@@
 zo Strojníckej fakulty STU.
-Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petrovi Kmeťkovi a Ing.~Peterovi Csókovi, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
-Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných strojov na merania v dátových centrách a sprístupnenie kompresorov.
+Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petera Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
+Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov.
 Prácu by som rád venoval rodine a kolegom-kamarátom, ktorí stáli pri mne na ,,šialenej akademickej dráhe'' a podnetné diskusie s nimi prispeli aj k môjmu pohľadu na odborné problémy.

### 2024-05-07 thesis/chapters/appendix/E-work-plan.tex
Contents of digital medium

@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week         & Semester kickoff meeting to set goals, experiments and discuss the status of collaborations with partners.
+\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
 \\ \hline
@@
  \\ \hline
-\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
+\nth{4} week         & Consultation about the plan for a machine to measure in the data center and a better device for measurement.
  \\ \hline
@@
  \\ \hline
-  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Desihn the firmware for new datalogger.
+  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump. Design the firmware for the new datalogger.
  \\ \hline
-  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing chapter on design and implementation.
+  \nth{12} - \nth{15} week         &  Write up design chapter: research questions and visualization export. Finish writing a chapter on design and implementation.
  \\ \hline
@@
 
-In reality, these tasks switched order because between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study.
-Only then from \nth{4} to \nth{11} week the main focus was on experiments with the MaFaulDa.
+In reality, these tasks switched order because, between \nth{1} to \nth{5} week, we needed to acquire alternative partner and check their machiners for viability in our study.
+Only then since \nth{4} until \nth{11} week, the main focus was on experiments with the MaFaulDa.
 
-Lastly, preliminary measurements were conducted, as was the plan. Requirements were presented for the new sensor device and its firmware.
+Lastly, preliminary measurements were conducted, as was the plan. The requirements were presented for the new sensor device and its firmware.
 \clearpage
@@
 \textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
-\nth{1} week  & Build and debug hardware of vibration logger with the consultant. 
+\nth{1} week  & Build and debug hardware of data logger with the consultant. 
 \\ \hline
@@
  \\ \hline
-\nth{4} week & Replace two time domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
+\nth{4} week & Replace two time-domain features and evaluate on MaFaulDa and own dataset. Repeated measurement of compressors (\nth{5} March).
  \\ \hline
@@
 Formulate research goals for scientific paper and create graphs of the model results.
-Experiment with k-value and number of features to reach better accuracy.
+Experiment with the k-value and number of features to reach better accuracy.
 Repeated measurement of compressors (\nth{19} March).
@@
  \\ \hline
- \nth{9} week & Refactor jupyter notebooks nad apply different labeling strategy applied in paper to incremental learning.
+ \nth{9} week & Refactor Jupyter notebooks and apply different labeling strategies applied in paper to incremental learning.
  \\ \hline
-  \nth{10} week & Write up implementation chapter of the thesis.
- \\ \hline
-  \nth{11} week & 
- \\ \hline
-  \nth{12} - \nth{15} week &  
+  \nth{10} - \nth{13} week & Update design chapter and finish text according to figures generated by experiments.
  \\ \hline
@@
 
-The aim of final semestre was to gather own dataset from compressors and water pumps with custom data logger. The k-NN model was validated with diffrent hyperparameters.
+The final semester aimed at gathering dataset from compressors and water pumps with the accelerometer data logger.
+The k-NN model was validated with different hyperparameters.
+The data collection finished sooner in \nth{7} week whereas originally it was planned until \nth{10} week because it became apparent that during a such short period, the change in machine vibrations would be negligible.
+The preparation for IIT.SRC conference was also not originally planned and took time away from finishing the thesis.
 

### 2024-05-07 thesis/chapters/appendix/F-digital-medium.tex
Refactor jupyter
Contents of digital medium

--- 2023-12-28 thesis/chapters/appendix/E-digital-medium.tex
@@
 \setcounter{figure}{0}
-\chapter{Contents of the digital medium}
+\chapter{Digital medium}
 \pagenumbering{arabic}
 \renewcommand*{\thepage}{E-\arabic{page}}
-\par Evidenčné číslo práce v informačnom systéme: \RegNo
-\par Obsah digitálnej časti práce (archív ZIP):
-\par Názov odovzdaného archívu:
+\par Registration number of thesis in AiS: \RegNo
+\par Contents of the digital medium:
+\par Name of submitted archive directory: DP\_MiroslavHajek.zip
+\par Notice: Digital medium has more than 1 GiB and is available to the thesis supervisor.
+\par The MaFaulDa dataset is publically available at: \url{https://www02.smt.ufrj.br/~offshore/mfs/database/mafaulda/full.zip}
+
+\begin{itemize}[noitemsep]
+\item[\textbf{>}] \textbf{datasets} - raw vibration data from machinery, and reports that took long to calculate.
+	\begin{itemize}[noitemsep]
+	\item[\textbf{>}] \textbf{FluidPump.zip} - custom recorded dataset of vibrations from air compressors and water pumps
+	\item[\textbf{>}] \emph{MAFAULDA.zip} - placeholder where the downloaded MaFaulDa dataset should be placed
+	\item[\textbf{>}] \textbf{best-subset} - the subset of features chosen to three-member subsets most frequently
+	\item[\textbf{>}] \textbf{features} - features extracted from datasets in multiple domains
+	\item[\textbf{>}] \textbf{ksb-cloud} - data exported from KSB cloud monitoring of vibration rms velocity and frequency waveform for chosen dates.
+	\item[\textbf{>}] \textbf{misc-fluid-pump} - other non-standard measurements from pumps such as during speed up, slow down, or noise.
+	\item[\textbf{>}] \textbf{knn-accuracy-distribution} - 
+	\item[\textbf{>}] \textbf{knn-incremental-accuracy} - The incremental k-NN model accuracy after each sample for various lengths of tumbling window and gaps between labels 
+	\item[\textbf{>}] \textbf{standing-fan} - audio for an estimate of fan rotational speed and measurements done in firmware verification on the back, side, and front of the fan.
+	\end{itemize}
+\item[\textbf{>}] \textbf{docs} - the documentation generated from source code comments  using automated tool
+	\begin{itemize}[noitemsep]
+	\item[\textbf{>}] \textbf{html-notebooks} - export of Jupyter notebooks for all basic configurations in HTML format
+	\item[\textbf{>}] \textbf{doxygen} - documentation of \emph{firmware} 
+	\item[\textbf{>}] \textbf{sphinx} - documentation of \emph{vibrodiagnostics} package
+	\end{itemize}
+\item[\textbf{>}] \textbf{firmware} - source code in \emph{main} directory for accelerometer data logger firmware written in C language with ESP-IDF SDK.
+The script \emph{bin2tsv.py} converts files saved to SD card in binary format to a tsv file.
+\item[\textbf{>}] \textbf{notebooks} - Jupyter notebooks for data exploration, data analysis, and machine learning on provided datasets
+\item[\textbf{>}] \textbf{vibrodiagnostics} - Python package of commonly used function in Jupyter notebooks for data processing
+\end{itemize}

### 2024-05-07 thesis/chapters/preliminaries/acknowledgments.tex
Contents of digital medium

@@
 zo Strojníckej fakulty STU.
-Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petera Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
+Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petra Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
 Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov.

### 2024-05-07 thesis/chapters/appendix/C-user-guide.tex
User guide

@@
 \renewcommand*{\thepage}{C-\arabic{page}}
+
+\section{Installation guide}
+The development platform was Acer Aspire A515-47 laptop with Linux distribution \emph{Manjaro 23.1.4.} and kernel version 6.1.
+The installation process consists of getting the Python 3.11.
+packages for dataset analysis and development tools for building and flashing firmware for data logger.
+The paths are written relative to the root directory of the digital medium after unzipping.
+
+The dependencies for running Jupyter notebooks can be installed by simply executing the following command ideally under a Python virtual environment:
+\begin{lstlisting}[style=messages]
+$ pip install -r docs/requirements.txt
+\end{lstlisting}
+
+To run the Jupyter environment and view notebooks run:
+\begin{lstlisting}[style=messages]
+$ jupyter lab
+\end{lstlisting}
+
+Building and uploading firmware of the data logger demands the following to be installed:
+\begin{enumerate}
+\item {Install system prerequisites and download ESP-IDF:
+\begin{lstlisting}[style=messages]
+$ sudo pacman -S --needed gcc git make flex bison gperf python cmake ninja ccache dfu-util libusb
+$ mkdir -p ~/esp
+$ cd ~/esp
+$ git clone -b v5.2.1 --recursive https://github.com/espressif/esp-idf.git
+\end{lstlisting}}
+
+\item {Install the tools used by ESP-IDF which are compiler, debugger, etc:
+\begin{lstlisting}[style=messages]
+$ cd ~/esp/esp-idf
+$ ./install.sh esp32
+\end{lstlisting}}
+
+\item {
+Connect ESP32 microcontroller via USB and flash firmware onto the device:
+\begin{lstlisting}[style=messages]
+$ . ~/esp/esp-idf/esp-idf/export.sh
+$ cd firmware
+$ idf.py build
+$ idf.py -p /dev/ttyUSB0 flash
+\end{lstlisting}}
+
+\end{enumerate}
+
+\section{Data logger guide}
+To measure vibrations with a data logger follow these steps:
+
+\begin{enumerate}[noitemsep]
+\item insert empty microSD card to the data logger,
+\item attach the accelerometer sensor to the surface of measurement,
+\item press the button and watch the LED light up,
+\item when the light turns off sooner before the minute mark, the buffer was dropped, and the final file can be incomplete,
+\item wait until the LED turns off, the recording is saved to file numbered sequentially from \emph{1.tsv} upwards,
+\item {move files from microSD card to a separate directory e.g. \emph{abc} and run for conversion to tsv files:
+\begin{lstlisting}[style=messages]
+$ python bin2tsv.py abc 4
+\end{lstlisting}}
+\end{enumerate}

### 2024-05-08 thesis/chapters/appendix/C-user-guide.tex
Generate doxygen docs and prepare Sphinx

@@
 \end{lstlisting}}
-
 \end{enumerate}
@@
 \end{enumerate}
+
+\section{Documentation guide}
+Built documentation is located in directory \emph{docs} of digital medium.
+It can be rebuild using documentation tools \emph{Doxygen} for firmware C source code and \emph{Sphinx} for data analysis Python code.
+The steps of generating documentation from souce codes are as follows:
+
+\begin{enumerate}[noitemsep]
+\item {install necessary documentation tools:
+\begin{lstlisting}[style=messages]
+$ sudo pacman -S doxygen
+$ pip install sphinx
+\end{lstlisting}}
+\item {rebuild the documentation using Doxygen and Sphinx:
+\begin{lstlisting}[style=messages]
+$ doxygen docs/firmware/doxygen.conf
+$ cd docs/vibrodiagnostics
+$ make html
+\end{lstlisting}}
+\item {View Doxygen docs in \emph{docs/firmware/html/topics.html} and Sphinx docs in \emph{docs/vibrodiagnostics/build/html/index.html}}
+\end{enumerate}

### 2024-05-08 DP_MiroslavHajek-zip/firmware/main/include/pinout.h

@@ -1,3 +1,12 @@
+#ifndef PINOUT_H
+#define PINOUT_H
+
+/**
+ * @defgroup datalogger Accelerometer Data logger
+ * @brief Data flow control from the sensor to the memory card
+ *  @{
+ */
+
 #include <stdio.h>
 #include <string.h>
 #include <stdbool.h>
@@ -13,64 +22,251 @@
 #include "freertos/semphr.h"
 #include "freertos/FreeRTOS.h"
 
-
+/**
+ * @brief Maximum length of the file name buffer
+ */
 #define MAX_FILENAME            256
+/**
+ * @brief Directory in virtual file system (VFS) where microSD card gets mounted
+ */
 #define MOUNT_POINT             "/sd"
+/**
+ * @brief Path prefix of the directory where recordings are saved
+ */
 #define LOG_FOLDER              MOUNT_POINT"/"
+/**
+ * @brief Minimal possible delay in milliseconds for using a synchronization primitive
+ */
 #define NO_WAIT                 10 / portTICK_PERIOD_MS
+/**
+ * @brief Period in milliseconds for which the button is disabled after the press to prevent the bouncing effect
+ */
 #define SWITCH_DEBOUNCE         2000 / portTICK_PERIOD_MS
 
+/**
+ * @brief SD/MMC bus GPIO pin for CLK
+ */
 #define CARD_CLK_PIN            14
+/**
+ * @brief SD/MMC bus GPIO pin for CMD
+ */
 #define CARD_CMD_PIN            15
+/**
+ * @brief SD/MMC bus GPIO pin for D0
+ */
 #define CARD_D0_PIN             2
 
+/**
+ * @brief GPIO pin for a button that starts and stops recording
+ */
 #define RECORD_SWITCH_PIN       34
+/**
+ * @brief GPIO pin for the indicator LED
+ */
 #define RECORD_LED_PIN          32
 
-// UEXT connector
+/**
+ * @brief GPIO pin for accelerometer SPI Master In Slave Out
+ */
 #define SENSOR_MISO             13
+/**
+ * @brief GPIO pin for accelerometer SPI Master Out Slave In
+ */
 #define SENSOR_MOSI             16
+/**
+ * @brief GPIO pin for accelerometer SPI Clock
+ */
 #define SENSOR_CLK              4
+/**
+ * @brief GPIO pin for accelerometer SPI Chip Select
+ */
 #define SENSOR_CS               5
+/**
+ * @brief GPIO pin for accelerometer interrupt pin
+ */
[…]

### 2024-05-08 DP_MiroslavHajek-zip/firmware/main/src/main.c

@@ -1,26 +1,62 @@
 #include "pinout.h"
 
-// RTOS primitives
+/**
+ * @defgroup main Firmware Tasks
+ * @brief Main program of the firmware execution
+ *  @{
+ */
+
+/**
+ * @brief Task handler for notification of button press
+ */
 TaskHandle_t trigger_task;
+/**
+ * @brief Task handler for notification from sampling timer
+ */
 TaskHandle_t sampler_task;
+/**
+ * @brief Queue for sending samples from the sensor read task to the memory card write task
+ */
 QueueHandle_t samples;
 
-// HW device
+
+/**
+ * @brief SPI bus hanle
+ */
 spi_device_handle_t spi;
+/**
+ * @brief Accelerometer sensor device
+ */
 stmdev_ctx_t sensor;
+/**
+ * @brief SD memory card handle
+ */
 sdmmc_card_t *card = NULL;
 
-// File and its mutex
-SemaphoreHandle_t file_mutex;
-FILE *file = NULL;
 
-// Is recording flag
+/**
+ * @brief Currently opened file handle
+ */
+FILE *file = NULL;
+/**
+ * @brief Mutex to protect file handle
+ */
+SemaphoreHandle_t file_mutex;
+
+
+/**
+ * @brief Flag for active recording in progress
+ */
 bool is_recording = false;
-// Write only from read_accelerometer when sensor is enabled
+/**
+ * @brief Last seen accelerometer timestamp 
+ */
 int32_t sensor_timestamp = 0;
 
 
-// Sampler timer
+/**
+ * @brief Timer interrupt handler for reading samples from accelerometer
+ */
 static void isr_sample(void* args)
 {
     xTaskNotifyGive(sampler_task);
@@ -32,6 +68,9 @@ const esp_timer_create_args_t sampler_timer_conf = {
 esp_timer_handle_t sampler_timer;
 
 
+/**
+ * @brief Interrupt handler for button press
+ */
 static void IRAM_ATTR isr_switch(void *args)
 {
     BaseType_t higher_priority_woken = pdFALSE;
@@ -39,7 +78,9 @@ static void IRAM_ATTR isr_switch(void *args)
     portYIELD_FROM_ISR(higher_priority_woken);
 }
 
-// Stop timer
+/**
+ * @brief Action on stop recording
+ */
 static void stop_timer_run(void* args)
 {
     // Stop recording
@@ -66,13 +107,18 @@ static void stop_timer_run(void* args)
[…]

### 2024-05-08 DP_MiroslavHajek-zip/firmware/main/src/sensor.c

@@ -41,7 +41,7 @@ static esp_err_t spi_enable(spi_device_handle_t *spi_dev)
         .quadhd_io_num = -1,
         .max_transfer_sz = SENSOR_SPI_LENGTH
     };
-    err = spi_bus_initialize(SPI_BUS, &spi_bus, SPI_DMA_CH_AUTO); // SPI_DMA_DISABLED
+    err = spi_bus_initialize(SPI_BUS, &spi_bus, SPI_DMA_CH_AUTO);
     ESP_ERROR_CHECK(err);
     spi_device_interface_config_t spi_iface = {
         .clock_speed_hz=SPI_BUS_FREQUENCY,
@@ -80,10 +80,7 @@ int sensor_enable(spi_device_handle_t *spi_dev, stmdev_ctx_t *dev)
     } while (rst);
 
     iis3dwb_block_data_update_set(dev, PROPERTY_ENABLE);
-
-    // Resolution: 4g
-    iis3dwb_xl_full_scale_set(dev, IIS3DWB_4g);
-    //iis3dwb_xl_full_scale_set(dev,  IIS3DWB_16g);
+    iis3dwb_xl_full_scale_set(dev, ACC_RESOLUTION);
 
     iis3dwb_fifo_watermark_set(dev, FIFO_WATERMARK);
     iis3dwb_fifo_xl_batch_set(dev, IIS3DWB_XL_BATCHED_AT_26k7Hz);

### 2024-05-08 DP_MiroslavHajek-zip/firmware/main/src/storage.c

@@ -12,7 +12,7 @@
 sdmmc_card_t *storage_enable(const char *mount_point)
 {
     esp_vfs_fat_sdmmc_mount_config_t mount = {
-        .format_if_mount_failed = true,     // Set to false
+        .format_if_mount_failed = true,
         .max_files = 1,                     // Maximum number of opened files
         .allocation_unit_size = 16 * 1024   // Useful only for format
     };

### 2024-05-08 DP_MiroslavHajek-zip/vibrodiagnostics/mafaulda.py

@@ -62,7 +62,12 @@ FAULTS = {
 }
 
 
-def bearing_frequencies(rpm: int) -> Dict[str, float]: 
+def bearing_frequencies(rpm: int) -> Dict[str, float]:
+    """Calculate bearring characteristic frequencies for MaFaulDa machine simulator
+
+    :param rpm: Rotational speed of the machine
+    :return: Bearing defect frequencies
+    """
     machine = {}
     rpm /= 60
     machine['RPM'] = rpm
@@ -74,6 +79,11 @@ def bearing_frequencies(rpm: int) -> Dict[str, float]:
 
 
 def parse_filename(filename: str) -> Tuple[str, str, str]:
+    """Split path of file within dataset structure to label the time series
+
+    :param filename: path to file inside of zip archive 
+    :return: fault type, severity conditions, and file number
+    """
     path = filename.split('/')
 
     if path[0].strip() in ('overhang', 'underhang'):
@@ -91,6 +101,11 @@ def parse_filename(filename: str) -> Tuple[str, str, str]:
 
 
 def rpm_calc(tachometer: pd.Series) -> float:
+    """Extract rotational speed in rpm units from tachometer pulse signal
+
+    :param tachometer: tachometer signal
+    :return: rotational speed in rpm
+    """
     t = tachometer.index.to_numpy()
     y = tachometer.to_numpy()
     peaks, _ = find_peaks(y, prominence=3, width=50)
@@ -103,6 +118,14 @@ def lowpass_filter(
         cutoff: int = SAMPLING_RATE // 5,
         fs: int = SAMPLING_RATE,
         order: int = 5) -> pd.Series:
+    """Low-pass filter of n-th order the input signal at the cutoff frequency
+
+    :param data: input signal
+    :param cutoff: cutoff frequency
+    :param fs: sampling frequency in Hz of the input signal
+    :param order: steps of the fileter
+    :return: output signal after filtering
+    """
     
     b, a = butter(order, cutoff, fs=fs, btype='lowpass')
     y = lfilter(b, a, data.to_numpy())
@@ -113,12 +136,24 @@ def lowpass_filter_extract(
             dataframes: List[pd.DataFrame],
             columns: List[str]
         ) -> List[pd.DataFrame]:
+    """Apply low-pass to columns in multiple dataframes
+
+    :param dataframes: list of input datafrmaes to which filter is applied to
+    :param columns: columns that filter is applied to
+    :return: list of dataframes after filtering
+    """
     for df in dataframes:
[…]

### 2024-05-08 DP_MiroslavHajek-zip/vibrodiagnostics/models.py

@@ -318,13 +318,14 @@ def knn_online_learn(
         Y: pd.DataFrame,
         window_len: int = 1,
         learn_skip: int = 0,
-        clusters: int = False) -> pd.DataFrame:
+        clusters: int = False,
+        n_neighbors: int = 5) -> pd.DataFrame:
     # Buffer true samples for learning for later: simulate delayed annotation
     learning_window = []
 
     # Model consists of scaler to give approximately same weight to all features and kNN
     scaler = preprocessing.MinMaxScaler() 
-    knn = neighbors.KNNClassifier(n_neighbors=5)
+    knn = neighbors.KNNClassifier(n_neighbors=n_neighbors)
 
     scores = []                 # List of tuples with accuracy, precision and recall score on each iteration
     v_true = []                 # Append y true sample on each iteration

### 2024-05-08 DP_MiroslavHajek-zip/vibrodiagnostics/pumps.py

@@ -54,7 +54,6 @@ def features_by_domain(
         parts: int = None
     ):
 
-    # print(f'Processing: {filename}')
     fs = SAMPLING_RATE
     columns = BEARINGS_COLUMNS
 
@@ -87,7 +86,6 @@ def features_by_domain_no_metadata(
         parts: int = None
     ):
 
-    # print(f'Processing: {filename}')
     fs = SAMPLING_RATE
     columns = BEARINGS_COLUMNS
 

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__button.tex
Export documentation from Sphinx and Doxygen

\doxysubsubsection{Button}
\hypertarget{group__button}{}\label{group__button}\index{Button@{Button}}

Configuation of the recording button.

\doxysubsubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
void \mbox{\hyperlink{group__button_ga6a537b9fc1207aed1c9c0a96b325f8c6}{switch\+\_\+enable}} (bool on, gpio\+\_\+isr\+\_\+t isr\+\_\+handler)
\begin{DoxyCompactList}\small\item\em Configure GPIO input pin and interrupt handler for button press. \end{DoxyCompactList}\item 
\Hypertarget{group__button_ga46afed7fc6e15a5c6d9475e46997b3da}\label{group__button_ga46afed7fc6e15a5c6d9475e46997b3da} 
void {\bfseries switch\+\_\+disable} (void)
\begin{DoxyCompactList}\small\item\em Remove interrupt handler for button press. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsubsection{Detailed Description}
Configuation of the recording button.

\doxysubsubsubsection{Function Documentation}
\Hypertarget{group__button_ga6a537b9fc1207aed1c9c0a96b325f8c6}\label{group__button_ga6a537b9fc1207aed1c9c0a96b325f8c6} 
\index{Button@{Button}!switch\_enable@{switch\_enable}}
\index{switch\_enable@{switch\_enable}!Button@{Button}}
\doxyparagraph{\texorpdfstring{switch\_enable()}{switch\_enable()}}
{\footnotesize\ttfamily void switch\+\_\+enable (\begin{DoxyParamCaption}\item[{bool}]{on,  }\item[{gpio\+\_\+isr\+\_\+t}]{isr\+\_\+handler }\end{DoxyParamCaption})}

Configure GPIO input pin and interrupt handler for button press.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em on} & decides whether the button is enabled or disabled \\
\hline
\mbox{\texttt{ in}}  & {\em isr\+\_\+handler} & handler function for button press in interrupt context \\
\hline
\end{DoxyParams}

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__datalogger.tex
Export documentation from Sphinx and Doxygen

\doxysubsection{Accelerometer Data logger}
\hypertarget{group__datalogger}{}\label{group__datalogger}\index{Accelerometer Data logger@{Accelerometer Data logger}}

Data flow control from the sensor to the memory card.

\doxysubsubsubsection*{Topics}
\begin{DoxyCompactItemize}
\item 
\mbox{\hyperlink{group__sensor}{Accelerometer}}
\begin{DoxyCompactList}\small\item\em Configuration of the accelerometer sensor. \end{DoxyCompactList}\item 
\mbox{\hyperlink{group__storage}{Memory card}}
\begin{DoxyCompactList}\small\item\em Filesystem operations of the SD card. \end{DoxyCompactList}\item 
\mbox{\hyperlink{group__button}{Button}}
\begin{DoxyCompactList}\small\item\em Configuation of the recording button. \end{DoxyCompactList}\item 
\mbox{\hyperlink{group__led}{LED}}
\begin{DoxyCompactList}\small\item\em Configuation of the indicator LED light. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__datalogger_gabe0ec333b60117063f9b9fd9f849cb08}\label{group__datalogger_gabe0ec333b60117063f9b9fd9f849cb08} 
\#define {\bfseries MAX\+\_\+\+FILENAME}~256
\begin{DoxyCompactList}\small\item\em Maximum length of the file name buffer. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaa085d60d609300a74cbf0b9aed796358}\label{group__datalogger_gaa085d60d609300a74cbf0b9aed796358} 
\#define {\bfseries MOUNT\+\_\+\+POINT}~"{}/sd"{}
\begin{DoxyCompactList}\small\item\em Directory in virtual file system (VFS) where micro\+SD card gets mounted. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga55d2d6d3e142179fde12db3235b28706}\label{group__datalogger_ga55d2d6d3e142179fde12db3235b28706} 
\#define {\bfseries LOG\+\_\+\+FOLDER}~MOUNT\+\_\+\+POINT"{}/"{}
\begin{DoxyCompactList}\small\item\em Path prefix of the directory where recordings are saved. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga3507cbe64443191d510ae7e093d37036}\label{group__datalogger_ga3507cbe64443191d510ae7e093d37036} 
\#define {\bfseries NO\+\_\+\+WAIT}~10 / port\+TICK\+\_\+\+PERIOD\+\_\+\+MS
\begin{DoxyCompactList}\small\item\em Minimal possible delay in milliseconds for using a synchronization primitive. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga89fca36db938a8ea9f4d82c6b8b7f053}\label{group__datalogger_ga89fca36db938a8ea9f4d82c6b8b7f053} 
\#define {\bfseries SWITCH\+\_\+\+DEBOUNCE}~2000 / port\+TICK\+\_\+\+PERIOD\+\_\+\+MS
\begin{DoxyCompactList}\small\item\em Period in milliseconds for which the button is disabled after the press to prevent the bouncing effect. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaf1e61d86b7a3eeca24be7bf31e0425cc}\label{group__datalogger_gaf1e61d86b7a3eeca24be7bf31e0425cc} 
\#define {\bfseries CARD\+\_\+\+CLK\+\_\+\+PIN}~14
\begin{DoxyCompactList}\small\item\em SD/\+MMC bus GPIO pin for CLK. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga53bd8075b5cff93003d075bfbf5be04a}\label{group__datalogger_ga53bd8075b5cff93003d075bfbf5be04a} 
\#define {\bfseries CARD\+\_\+\+CMD\+\_\+\+PIN}~15
\begin{DoxyCompactList}\small\item\em SD/\+MMC bus GPIO pin for CMD. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaff51dd2f233a4637cb10ac6ef51eb1b4}\label{group__datalogger_gaff51dd2f233a4637cb10ac6ef51eb1b4} 
\#define {\bfseries CARD\+\_\+\+D0\+\_\+\+PIN}~2
\begin{DoxyCompactList}\small\item\em SD/\+MMC bus GPIO pin for D0. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga56c3b62dd9b8045281b343e62880b0ca}\label{group__datalogger_ga56c3b62dd9b8045281b343e62880b0ca} 
\#define {\bfseries RECORD\+\_\+\+SWITCH\+\_\+\+PIN}~34
\begin{DoxyCompactList}\small\item\em GPIO pin for a button that starts and stops recording. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga63ef077ec9bea5b9b4bf1ea75170ab51}\label{group__datalogger_ga63ef077ec9bea5b9b4bf1ea75170ab51} 
\#define {\bfseries RECORD\+\_\+\+LED\+\_\+\+PIN}~32
\begin{DoxyCompactList}\small\item\em GPIO pin for the indicator LED. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga58d5dc1a48e87a9f69c3b9031fa887fb}\label{group__datalogger_ga58d5dc1a48e87a9f69c3b9031fa887fb} 
\#define {\bfseries SENSOR\+\_\+\+MISO}~13
\begin{DoxyCompactList}\small\item\em GPIO pin for accelerometer SPI Master In Slave Out. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaf3662b79560ba2a493a42be244ed3c8a}\label{group__datalogger_gaf3662b79560ba2a493a42be244ed3c8a} 
\#define {\bfseries SENSOR\+\_\+\+MOSI}~16
\begin{DoxyCompactList}\small\item\em GPIO pin for accelerometer SPI Master Out Slave In. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga33c8db114b90a3730e2c78abc505c6a5}\label{group__datalogger_ga33c8db114b90a3730e2c78abc505c6a5} 
\#define {\bfseries SENSOR\+\_\+\+CLK}~4
\begin{DoxyCompactList}\small\item\em GPIO pin for accelerometer SPI Clock. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gab5c2fca97ed28557c495c7edc058653b}\label{group__datalogger_gab5c2fca97ed28557c495c7edc058653b} 
\#define {\bfseries SENSOR\+\_\+\+CS}~5
\begin{DoxyCompactList}\small\item\em GPIO pin for accelerometer SPI Chip Select. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga843d60b6b33b264cccf6adcfa5885c72}\label{group__datalogger_ga843d60b6b33b264cccf6adcfa5885c72} 
\#define {\bfseries SENSOR\+\_\+\+INT1}~33
\begin{DoxyCompactList}\small\item\em GPIO pin for accelerometer interrupt pin. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaebb434d5c5030f5655e4f74082c85bac}\label{group__datalogger_gaebb434d5c5030f5655e4f74082c85bac} 
\#define {\bfseries SPI\+\_\+\+BUS\+\_\+\+FREQUENCY}~SPI\+\_\+\+MASTER\+\_\+\+FREQ\+\_\+8M
\begin{DoxyCompactList}\small\item\em SPI master bus frequency. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}\label{group__datalogger_gaf759d6c69e76948f9933f3872d997adb} 
\#define {\bfseries FIFO\+\_\+\+LENGTH}~512
\begin{DoxyCompactList}\small\item\em Length of accelerometer FIFO buffer. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga47fb7049ab7d76ae664f360e90cfc680}\label{group__datalogger_ga47fb7049ab7d76ae664f360e90cfc680} 
\#define {\bfseries FIFO\+\_\+\+WATERMARK}~\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}} / 2
\begin{DoxyCompactList}\small\item\em Half length of accelerometer FIFO buffer. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga5191aff7ba21d7863df87206a27d4013}\label{group__datalogger_ga5191aff7ba21d7863df87206a27d4013} 
\#define {\bfseries NUM\+\_\+\+OF\+\_\+\+FIELDS}~4
\begin{DoxyCompactList}\small\item\em Number of columns per acceleration vector. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga640ecdfbff5ebeda0889c24421c7688d}\label{group__datalogger_ga640ecdfbff5ebeda0889c24421c7688d} 
\#define {\bfseries SENSOR\+\_\+\+SPI\+\_\+\+LENGTH}~\mbox{\hyperlink{group__datalogger_ga5191aff7ba21d7863df87206a27d4013}{NUM\+\_\+\+OF\+\_\+\+FIELDS}} \texorpdfstring{$\ast$}{*} \mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}}
\begin{DoxyCompactList}\small\item\em Length of buffer for SPI transaction. \end{DoxyCompactList}\item 
\Hypertarget{group__datalogger_ga055729a37bf543876e2ce9d57b95ab7b}\label{group__datalogger_ga055729a37bf543876e2ce9d57b95ab7b} 
\#define {\bfseries QUEUE\+\_\+\+LENGTH}~16
\begin{DoxyCompactList}\small\item\em Number of FIFO buffers that can be pushed to Queue before file write. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
void \mbox{\hyperlink{group__datalogger_gae496e529dd495b07dfadcb591230220d}{panic}} (int delay)
\begin{DoxyCompactList}\small\item\em Signal fatal error of system occuring by blinking indicator LED and halting execution. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsection{Detailed Description}
Data flow control from the sensor to the memory card.

\doxysubsubsection{Function Documentation}
\Hypertarget{group__datalogger_gae496e529dd495b07dfadcb591230220d}\label{group__datalogger_gae496e529dd495b07dfadcb591230220d} 
\index{Accelerometer Data logger@{Accelerometer Data logger}!panic@{panic}}
\index{panic@{panic}!Accelerometer Data logger@{Accelerometer Data logger}}
\doxyparagraph{\texorpdfstring{panic()}{panic()}}
{\footnotesize\ttfamily void panic (\begin{DoxyParamCaption}\item[{int}]{delay }\end{DoxyParamCaption})}

Signal fatal error of system occuring by blinking indicator LED and halting execution.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em delay} & Interval in milliseconds for LED blink \\
\hline
\end{DoxyParams}
\input{group__sensor}
\input{group__storage}
\input{group__button}
\input{group__led}

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__led.tex
Export documentation from Sphinx and Doxygen

\doxysubsubsection{LED}
\hypertarget{group__led}{}\label{group__led}\index{LED@{LED}}

Configuation of the indicator LED light.

\doxysubsubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__led_gaf7f119ca34573b73818f4acfed6d97f6}\label{group__led_gaf7f119ca34573b73818f4acfed6d97f6} 
void {\bfseries led\+\_\+enable} (void)
\begin{DoxyCompactList}\small\item\em Configure GPIO for LED to output mode. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__led_gaf3828ebdb3bbb5daebe93e79689fa36b}{led\+\_\+light}} (bool on)
\begin{DoxyCompactList}\small\item\em Set the LED state. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsubsection{Detailed Description}
Configuation of the indicator LED light.

\doxysubsubsubsection{Function Documentation}
\Hypertarget{group__led_gaf3828ebdb3bbb5daebe93e79689fa36b}\label{group__led_gaf3828ebdb3bbb5daebe93e79689fa36b} 
\index{LED@{LED}!led\_light@{led\_light}}
\index{led\_light@{led\_light}!LED@{LED}}
\doxyparagraph{\texorpdfstring{led\_light()}{led\_light()}}
{\footnotesize\ttfamily void led\+\_\+light (\begin{DoxyParamCaption}\item[{bool}]{on }\end{DoxyParamCaption})}

Set the LED state.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em on} & turns LED light to be either on or off \\
\hline
\end{DoxyParams}

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__main.tex
Export documentation from Sphinx and Doxygen

\doxysubsection{Firmware Tasks}
\hypertarget{group__main}{}\label{group__main}\index{Firmware Tasks@{Firmware Tasks}}

Main program of the firmware execution.

\doxysubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__main_ga0ec5d28752074ca54a70acc838f672e4}\label{group__main_ga0ec5d28752074ca54a70acc838f672e4} 
void {\bfseries push\+\_\+trigger} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to start or stop recoding after siganl from button press. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0}\label{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0} 
void {\bfseries read\+\_\+accelerometer} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to read FIFO buffer of the accelerometer and write it to Queue. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4}\label{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4} 
void {\bfseries write\+\_\+card} (void \texorpdfstring{$\ast$}{*}args)
\begin{DoxyCompactList}\small\item\em Task to write accelerations vectors from Queue to the memory card. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70}\label{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70} 
void {\bfseries app\+\_\+main} (void)
\begin{DoxyCompactList}\small\item\em Entrypoint of firmware to setup hardware peripherals and run tasks. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsection*{Variables}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a}\label{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a} 
Task\+Handle\+\_\+t {\bfseries trigger\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification of button press. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga768ac04522700fd0788f959b1c7510cb}\label{group__main_ga768ac04522700fd0788f959b1c7510cb} 
Task\+Handle\+\_\+t {\bfseries sampler\+\_\+task}
\begin{DoxyCompactList}\small\item\em Task handler for notification from sampling timer. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaa6b473c01115f6c0fd05415b7ca3a287}\label{group__main_gaa6b473c01115f6c0fd05415b7ca3a287} 
Queue\+Handle\+\_\+t {\bfseries samples}
\begin{DoxyCompactList}\small\item\em Queue for sending samples from the sensor read task to the memory card write task. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaf04b0de520c6e42f039c5edf47b13dc2}\label{group__main_gaf04b0de520c6e42f039c5edf47b13dc2} 
spi\+\_\+device\+\_\+handle\+\_\+t {\bfseries spi}
\begin{DoxyCompactList}\small\item\em SPI bus handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga21408672a588f2b1db6f8f620eecbc59}\label{group__main_ga21408672a588f2b1db6f8f620eecbc59} 
stmdev\+\_\+ctx\+\_\+t {\bfseries sensor}
\begin{DoxyCompactList}\small\item\em Accelerometer sensor device. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gad85cb86f6cbc94b88b09c3315c9028f1}\label{group__main_gad85cb86f6cbc94b88b09c3315c9028f1} 
sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} {\bfseries card} = NULL
\begin{DoxyCompactList}\small\item\em SD memory card handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga702945180aa732857b380a007a7e2a21}\label{group__main_ga702945180aa732857b380a007a7e2a21} 
FILE \texorpdfstring{$\ast$}{*} {\bfseries file} = NULL
\begin{DoxyCompactList}\small\item\em Currently opened file handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_ga94544252c41b06346dc45f70cbd48d63}\label{group__main_ga94544252c41b06346dc45f70cbd48d63} 
Semaphore\+Handle\+\_\+t {\bfseries file\+\_\+mutex}
\begin{DoxyCompactList}\small\item\em Mutex to protect file handle. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gaf409115fcaa12619a90c9b581bafa64a}\label{group__main_gaf409115fcaa12619a90c9b581bafa64a} 
bool {\bfseries is\+\_\+recording} = false
\begin{DoxyCompactList}\small\item\em Flag for active recording in progress. \end{DoxyCompactList}\item 
\Hypertarget{group__main_gad70a27ce9ba8cfa78153904f05e38c44}\label{group__main_gad70a27ce9ba8cfa78153904f05e38c44} 
int32\+\_\+t {\bfseries sensor\+\_\+timestamp} = 0
\begin{DoxyCompactList}\small\item\em Last seen accelerometer timestamp. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}{sampler\+\_\+timer\+\_\+conf}}
\item 
\Hypertarget{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1}\label{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1} 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries sampler\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Periodic timer to signal when to read FIFO buffer from accelerometer. \end{DoxyCompactList}\item 
const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t \mbox{\hyperlink{group__main_gacb077cf1ef581c961e7e5222a98f6897}{stop\+\_\+timer\+\_\+conf}}
\item 
\Hypertarget{group__main_gab1d567cca0836a894a9577ba45fac511}\label{group__main_gab1d567cca0836a894a9577ba45fac511} 
esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries stop\+\_\+timer}
\begin{DoxyCompactList}\small\item\em Timer to stop recording after fixed amount of time. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsection{Detailed Description}
Main program of the firmware execution.

\doxysubsubsection{Variable Documentation}
\Hypertarget{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}\label{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64} 
\index{Firmware Tasks@{Firmware Tasks}!sampler\_timer\_conf@{sampler\_timer\_conf}}
\index{sampler\_timer\_conf@{sampler\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
\doxyparagraph{\texorpdfstring{sampler\_timer\_conf}{sampler\_timer\_conf}}
{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t sampler\+\_\+timer\+\_\+conf}

{\bfseries Initial value\+:}
\begin{DoxyCode}{0}
\DoxyCodeLine{=\ \{}
\DoxyCodeLine{\ \ \ \ \ \ \ \ .callback\ =\ \&isr\_sample}
\DoxyCodeLine{\}}

\end{DoxyCode}
\Hypertarget{group__main_gacb077cf1ef581c961e7e5222a98f6897}\label{group__main_gacb077cf1ef581c961e7e5222a98f6897} 
\index{Firmware Tasks@{Firmware Tasks}!stop\_timer\_conf@{stop\_timer\_conf}}
\index{stop\_timer\_conf@{stop\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
\doxyparagraph{\texorpdfstring{stop\_timer\_conf}{stop\_timer\_conf}}
{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t stop\+\_\+timer\+\_\+conf}

{\bfseries Initial value\+:}
\begin{DoxyCode}{0}
\DoxyCodeLine{=\ \{}
\DoxyCodeLine{\ \ \ \ .callback\ =\ \&stop\_timer\_run}
\DoxyCodeLine{\}}

\end{DoxyCode}

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__storage.tex
Export documentation from Sphinx and Doxygen

\doxysubsubsection{Memory card}
\hypertarget{group__storage}{}\label{group__storage}\index{Memory card@{Memory card}}

Filesystem operations of the SD card.

\doxysubsubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} \mbox{\hyperlink{group__storage_ga79585e9fc7f44b32f4e1a653de5bbe3d}{storage\+\_\+enable}} (const char \texorpdfstring{$\ast$}{*}mount\+\_\+point)
\begin{DoxyCompactList}\small\item\em Configure SD/\+MMC bus and mount SD memory card to FAT filesystem. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__storage_ga29baf561c143b595123045253ab58f45}{storage\+\_\+disable}} (sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*}\mbox{\hyperlink{group__main_gad85cb86f6cbc94b88b09c3315c9028f1}{card}}, const char \texorpdfstring{$\ast$}{*}mount\+\_\+point)
\begin{DoxyCompactList}\small\item\em Disable and unmount SD memory card from FAT filesystem. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__storage_gae29b193e928219e1f41be6b1ac1abea5}{get\+\_\+recording\+\_\+filename}} (char \texorpdfstring{$\ast$}{*}filename, const char \texorpdfstring{$\ast$}{*}path)
\begin{DoxyCompactList}\small\item\em Get file name for new recording with sequentially higher unused number. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsubsection{Detailed Description}
Filesystem operations of the SD card.

\doxysubsubsubsection{Function Documentation}
\Hypertarget{group__storage_gae29b193e928219e1f41be6b1ac1abea5}\label{group__storage_gae29b193e928219e1f41be6b1ac1abea5} 
\index{Memory card@{Memory card}!get\_recording\_filename@{get\_recording\_filename}}
\index{get\_recording\_filename@{get\_recording\_filename}!Memory card@{Memory card}}
\doxyparagraph{\texorpdfstring{get\_recording\_filename()}{get\_recording\_filename()}}
{\footnotesize\ttfamily void get\+\_\+recording\+\_\+filename (\begin{DoxyParamCaption}\item[{char \texorpdfstring{$\ast$}{*}}]{filename,  }\item[{const char \texorpdfstring{$\ast$}{*}}]{path }\end{DoxyParamCaption})}

Get file name for new recording with sequentially higher unused number.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ out}}  & {\em filename} & Available file name for new file \\
\hline
\mbox{\texttt{ in}}  & {\em path} & Base path prefix for saving the recording \\
\hline
\end{DoxyParams}
\Hypertarget{group__storage_ga29baf561c143b595123045253ab58f45}\label{group__storage_ga29baf561c143b595123045253ab58f45} 
\index{Memory card@{Memory card}!storage\_disable@{storage\_disable}}
\index{storage\_disable@{storage\_disable}!Memory card@{Memory card}}
\doxyparagraph{\texorpdfstring{storage\_disable()}{storage\_disable()}}
{\footnotesize\ttfamily void storage\+\_\+disable (\begin{DoxyParamCaption}\item[{sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*}}]{card,  }\item[{const char \texorpdfstring{$\ast$}{*}}]{mount\+\_\+point }\end{DoxyParamCaption})}

Disable and unmount SD memory card from FAT filesystem.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em card} & SD/\+MMC card information structure \\
\hline
\mbox{\texttt{ in}}  & {\em mount\+\_\+point} & path where partition is registered\\
\hline
\end{DoxyParams}
\begin{DoxyReturn}{Returns}
c 
\end{DoxyReturn}
\Hypertarget{group__storage_ga79585e9fc7f44b32f4e1a653de5bbe3d}\label{group__storage_ga79585e9fc7f44b32f4e1a653de5bbe3d} 
\index{Memory card@{Memory card}!storage\_enable@{storage\_enable}}
\index{storage\_enable@{storage\_enable}!Memory card@{Memory card}}
\doxyparagraph{\texorpdfstring{storage\_enable()}{storage\_enable()}}
{\footnotesize\ttfamily sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} storage\+\_\+enable (\begin{DoxyParamCaption}\item[{const char \texorpdfstring{$\ast$}{*}}]{mount\+\_\+point }\end{DoxyParamCaption})}

Configure SD/\+MMC bus and mount SD memory card to FAT filesystem.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em mount\+\_\+point} & path where the partition will be registered ~\newline
\\
\hline
\end{DoxyParams}
\begin{DoxyReturn}{Returns}
SD/\+MMC card information structure 
\end{DoxyReturn}

### 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/pinout_8h_source.tex
Export documentation from Sphinx and Doxygen

\doxysubsection{pinout.\+h}
\hypertarget{pinout_8h_source}{}\label{pinout_8h_source}\index{firmware/main/include/pinout.h@{firmware/main/include/pinout.h}}

\begin{DoxyCode}{0}
\DoxyCodeLine{00001\ \textcolor{preprocessor}{\#ifndef\ PINOUT\_H}}
\DoxyCodeLine{00002\ \textcolor{preprocessor}{\#define\ PINOUT\_H}}
\DoxyCodeLine{00003\ }
\DoxyCodeLine{00010\ \textcolor{preprocessor}{\#include\ <stdio.h>}}
\DoxyCodeLine{00011\ \textcolor{preprocessor}{\#include\ <string.h>}}
\DoxyCodeLine{00012\ \textcolor{preprocessor}{\#include\ <stdbool.h>}}
\DoxyCodeLine{00013\ }
\DoxyCodeLine{00014\ \textcolor{preprocessor}{\#include\ "{}iis3dwb.h"{}}}
\DoxyCodeLine{00015\ \textcolor{preprocessor}{\#include\ "{}hal/gpio\_types.h"{}}}
\DoxyCodeLine{00016\ \textcolor{preprocessor}{\#include\ "{}driver/sdmmc\_host.h"{}}}
\DoxyCodeLine{00017\ \textcolor{preprocessor}{\#include\ "{}driver/spi\_master.h"{}}}
\DoxyCodeLine{00018\ \textcolor{preprocessor}{\#include\ "{}esp\_err.h"{}}}
\DoxyCodeLine{00019\ \textcolor{preprocessor}{\#include\ "{}esp\_log.h"{}}}
\DoxyCodeLine{00020\ \textcolor{preprocessor}{\#include\ "{}esp\_timer.h"{}}}
\DoxyCodeLine{00021\ \textcolor{preprocessor}{\#include\ "{}freertos/task.h"{}}}
\DoxyCodeLine{00022\ \textcolor{preprocessor}{\#include\ "{}freertos/semphr.h"{}}}
\DoxyCodeLine{00023\ \textcolor{preprocessor}{\#include\ "{}freertos/FreeRTOS.h"{}}}
\DoxyCodeLine{00024\ }
\DoxyCodeLine{00028\ \textcolor{preprocessor}{\#define\ MAX\_FILENAME\ \ \ \ \ \ \ \ \ \ \ \ 256}}
\DoxyCodeLine{00032\ \textcolor{preprocessor}{\#define\ MOUNT\_POINT\ \ \ \ \ \ \ \ \ \ \ \ \ "{}/sd"{}}}
\DoxyCodeLine{00036\ \textcolor{preprocessor}{\#define\ LOG\_FOLDER\ \ \ \ \ \ \ \ \ \ \ \ \ \ MOUNT\_POINT"{}/"{}}}
\DoxyCodeLine{00040\ \textcolor{preprocessor}{\#define\ NO\_WAIT\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 10\ /\ portTICK\_PERIOD\_MS}}
\DoxyCodeLine{00044\ \textcolor{preprocessor}{\#define\ SWITCH\_DEBOUNCE\ \ \ \ \ \ \ \ \ 2000\ /\ portTICK\_PERIOD\_MS}}
\DoxyCodeLine{00045\ }
\DoxyCodeLine{00049\ \textcolor{preprocessor}{\#define\ CARD\_CLK\_PIN\ \ \ \ \ \ \ \ \ \ \ \ 14}}
\DoxyCodeLine{00053\ \textcolor{preprocessor}{\#define\ CARD\_CMD\_PIN\ \ \ \ \ \ \ \ \ \ \ \ 15}}
\DoxyCodeLine{00057\ \textcolor{preprocessor}{\#define\ CARD\_D0\_PIN\ \ \ \ \ \ \ \ \ \ \ \ \ 2}}
\DoxyCodeLine{00058\ }
\DoxyCodeLine{00062\ \textcolor{preprocessor}{\#define\ RECORD\_SWITCH\_PIN\ \ \ \ \ \ \ 34}}
\DoxyCodeLine{00066\ \textcolor{preprocessor}{\#define\ RECORD\_LED\_PIN\ \ \ \ \ \ \ \ \ \ 32}}
\DoxyCodeLine{00067\ }
\DoxyCodeLine{00071\ \textcolor{preprocessor}{\#define\ SENSOR\_MISO\ \ \ \ \ \ \ \ \ \ \ \ \ 13}}
\DoxyCodeLine{00075\ \textcolor{preprocessor}{\#define\ SENSOR\_MOSI\ \ \ \ \ \ \ \ \ \ \ \ \ 16}}
\DoxyCodeLine{00079\ \textcolor{preprocessor}{\#define\ SENSOR\_CLK\ \ \ \ \ \ \ \ \ \ \ \ \ \ 4}}
\DoxyCodeLine{00083\ \textcolor{preprocessor}{\#define\ SENSOR\_CS\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ 5}}
\DoxyCodeLine{00087\ \textcolor{preprocessor}{\#define\ SENSOR\_INT1\ \ \ \ \ \ \ \ \ \ \ \ \ 33}}
\DoxyCodeLine{00091\ \textcolor{preprocessor}{\#define\ SPI\_BUS\_FREQUENCY\ \ \ \ \ \ \ SPI\_MASTER\_FREQ\_8M}}
\DoxyCodeLine{00095\ \textcolor{preprocessor}{\#define\ FIFO\_LENGTH\ \ \ \ \ \ \ \ \ \ \ \ \ 512}}
\DoxyCodeLine{00099\ \textcolor{preprocessor}{\#define\ FIFO\_WATERMARK\ \ \ \ \ \ \ \ \ \ FIFO\_LENGTH\ /\ 2}}
\DoxyCodeLine{00100\ }
\DoxyCodeLine{00104\ \textcolor{preprocessor}{\#define\ NUM\_OF\_FIELDS\ \ \ \ \ \ \ \ \ \ \ 4}}
\DoxyCodeLine{00108\ \textcolor{preprocessor}{\#define\ SENSOR\_SPI\_LENGTH\ \ \ \ \ \ \ NUM\_OF\_FIELDS\ *\ FIFO\_LENGTH}}
\DoxyCodeLine{00112\ \textcolor{preprocessor}{\#define\ QUEUE\_LENGTH\ \ \ \ \ \ \ \ \ \ \ \ 16}}
\DoxyCodeLine{00113\ }
\DoxyCodeLine{00114\ }
\DoxyCodeLine{00124\ \textcolor{preprocessor}{\#define\ SAMPLE\_RATE\ \ \ \ \ \ \ \ \ \ \ \ \ 9000}}
\DoxyCodeLine{00128\ \textcolor{preprocessor}{\#define\ SPI\_BUS\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ SPI3\_HOST}}
\DoxyCodeLine{00132\ \textcolor{preprocessor}{\#define\ AUTO\_TURN\_OFF\_US\ \ \ \ \ \ \ \ 60000000}}
\DoxyCodeLine{00136\ \textcolor{preprocessor}{\#define\ ACC\_RESOLUTION\ \ \ \ \ \ \ \ \ \ IIS3DWB\_4g}}
\DoxyCodeLine{00137\ }
\DoxyCodeLine{00141\ \textcolor{keyword}{typedef}\ \textcolor{keyword}{struct\ }\{}
\DoxyCodeLine{00142\ \ \ \ \ uint16\_t\ \mbox{\hyperlink{structAcceleration_a08d970081c96582d6484a1dbb795be88}{len}};\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
\DoxyCodeLine{00143\ \ \ \ \ int32\_t\ t[\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\_LENGTH}}];\ \ \ \ \ }
\DoxyCodeLine{00144\ \ \ \ \ int32\_t\ x[\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\_LENGTH}}];\ \ \ \ \ }
\DoxyCodeLine{00145\ \ \ \ \ int32\_t\ y[\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\_LENGTH}}];\ \ \ \ \ }
\DoxyCodeLine{00146\ \ \ \ \ int32\_t\ z[\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\_LENGTH}}];\ \ \ \ \ }
\DoxyCodeLine{00147\ \}\ \mbox{\hyperlink{structAcceleration}{Acceleration}};}
\DoxyCodeLine{00148\ }
\DoxyCodeLine{00157\ \textcolor{keywordtype}{int}\ \mbox{\hyperlink{group__sensor_ga844ea677736e4310ff9a9bee3935330a}{sensor\_enable}}(spi\_device\_handle\_t\ *spi\_dev,\ stmdev\_ctx\_t\ *dev);}
\DoxyCodeLine{00158\ }
\DoxyCodeLine{00164\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__sensor_ga774ff5ef12bc72ef4d96e2ebef38d279}{sensor\_disable}}(spi\_device\_handle\_t\ spi\_dev);}
\DoxyCodeLine{00165\ }
\DoxyCodeLine{00171\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__sensor_ga3a4369193c5acef70192d32950bd4db5}{sensor\_events\_enable}}(stmdev\_ctx\_t\ *dev);}
\DoxyCodeLine{00172\ }
\DoxyCodeLine{00178\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__sensor_gafee0ba0827fd9f252c480faccdee0a97}{sensor\_events\_disable}}(stmdev\_ctx\_t\ *dev);}
\DoxyCodeLine{00179\ }
\DoxyCodeLine{00189\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__datalogger_gae496e529dd495b07dfadcb591230220d}{panic}}(\textcolor{keywordtype}{int}\ delay);}
\DoxyCodeLine{00190\ }
\DoxyCodeLine{00191\ }
\DoxyCodeLine{00205\ sdmmc\_card\_t\ *\mbox{\hyperlink{group__storage_ga79585e9fc7f44b32f4e1a653de5bbe3d}{storage\_enable}}(\textcolor{keyword}{const}\ \textcolor{keywordtype}{char}\ *mount\_point);}
\DoxyCodeLine{00206\ }
\DoxyCodeLine{00215\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__storage_ga29baf561c143b595123045253ab58f45}{storage\_disable}}(sdmmc\_card\_t\ *\mbox{\hyperlink{group__main_gad85cb86f6cbc94b88b09c3315c9028f1}{card}},\ \textcolor{keyword}{const}\ \textcolor{keywordtype}{char}\ *mount\_point);}
\DoxyCodeLine{00216\ }
\DoxyCodeLine{00223\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__storage_gae29b193e928219e1f41be6b1ac1abea5}{get\_recording\_filename}}(\textcolor{keywordtype}{char}\ *filename,\ \textcolor{keyword}{const}\ \textcolor{keywordtype}{char}\ *path);}
\DoxyCodeLine{00224\ }
\DoxyCodeLine{00240\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__button_ga6a537b9fc1207aed1c9c0a96b325f8c6}{switch\_enable}}(\textcolor{keywordtype}{bool}\ on,\ gpio\_isr\_t\ isr\_handler);}
\DoxyCodeLine{00241\ }
\DoxyCodeLine{00245\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__button_ga46afed7fc6e15a5c6d9475e46997b3da}{switch\_disable}}(\textcolor{keywordtype}{void});}
\DoxyCodeLine{00246\ }
\DoxyCodeLine{00259\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__led_gaf7f119ca34573b73818f4acfed6d97f6}{led\_enable}}(\textcolor{keywordtype}{void});}
\DoxyCodeLine{00265\ \textcolor{keywordtype}{void}\ \mbox{\hyperlink{group__led_gaf3828ebdb3bbb5daebe93e79689fa36b}{led\_light}}(\textcolor{keywordtype}{bool}\ on);}
\DoxyCodeLine{00266\ }
\DoxyCodeLine{00272\ \textcolor{preprocessor}{\#endif}}

\end{DoxyCode}

### 2024-05-11 thesis/chapters/appendix/A-resume.tex
Export documentation from Sphinx and Doxygen

@@
 \section{Zber vibrácií v priemysle}
+Doteraz uplatnená metodika pre súbor údajov zaznamenaných v laboratóriu sa aplikuje na vibračných signáloch z priemyselného prostredia.
+Pri monitorovaní zužitkujeme mierne prispôsobený postup z noriem.
+Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie podľa technických štandardov, predbežné merania a vývoj senzorovej jednotky.
+
+Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektrometrami v prečerpávacej stanici na pitnú vodu.
+Dlhodobejšie merania uskutočníme vlastným vnoreným systémom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
+Ako senzor vibrácii použijeme MEMS akcelerometer IIS3DWB.
+Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
 
@@
 \section{Záver}
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
+Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov a technických noriem vibrodiagnostiky.
+
+Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
+Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne.
+Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%.
+Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.
+
+Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov.
+Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.
 

### 2024-05-11 thesis/chapters/appendix/B-technical-documentation.tex
Export documentation from Sphinx and Doxygen

@@
 \renewcommand*{\thepage}{B-\arabic{page}}
+The documentation contains a description of Jupyter Notebooks, Python package \verb|vibrodiagnostics| with utility functions for machine learning, and data logger firmware.
+Pages of \LaTeX \; documentation for Python were autogenerated by documentation tool \textbf{Sphinx}.
+Pages from C source code were created by \textbf{Doxygen}.
 
-% Jupyter notebooks
+\section{Jupyter notebooks}
+\begin{itemize}[noitemsep]
 
-% Python function in package (Sphinx)
+\item \textbf{cluster-dbscan.ipynb} - The clustering feasibility of the DBSCAN algorithm in the MaFaulDa dataset.
+Experiments to find the best epsilon parameter for complete sets of time-domain and frequency-domain features.
+Epsilon is estimated by localizing the knee on the curve of nearest neighbours.
+The method turned out to be unreliable in separating different groups of fault types.
+The clustering produced too many or too few samples based on the choice of minimal samples.
 
-% C function of firmware
+\item \textbf{eda-bearing-faults.ipynb} - Mark the bearing characteristic frequencies in the frequency spectrum in the axis of motion for chosen recordings from the MaFaulDa dataset, scroll compressors, water pumps, and electric motors.
+The bearing frequencies are calculated from coefficients or physical dimensions for the bearing designation.
+
+\item \textbf{eda-files.ipynb} - Time-domain vibration signal waveforms are charted for acceleration values and velocity after integration.
+Measurements are compared between fault types or measurement positions.
+Statistical tests for normality and stationarity of oscillations are conducted.
+Comparisons from all axes for peak finding MMS algorithm, cumulative frequency spectrum, and time-frequency spectrum.
+Orbitals of detected fundamental frequency are shown in the spatial graph.
+Options are to view signals for chosen files from the MaFaulDa dataset on the inner bearing, outer bearing, or for the Pumps industrial dataset.
+
+\item \textbf{eda-ksb-cloud.ipynb} - Overall vibration rms velocities in hourly intervals for two identical water pumps are shown in ISO severity levels.
+Total running time is summed from periods when each pump has been operational.
+Frequency spectra are also compared but are proven to have too low resolution for any conclusive result in fault recognition.
+
+\item \textbf{eda-pumps.ipynb}
+\item \textbf{eda-standing-fan.ipynb}
+\item \textbf{extraction-mafaulda.ipynb}
+\item \textbf{extraction-pumps.ipynb}
+\item \textbf{feature-summary.ipynb}
+\item \textbf{iit-src-paper.ipynb}
+\item \textbf{knn-batch.ipynb}
+\item \textbf{knn-mafaulda.ipynb}
+\item \textbf{knn-online.ipynb}
+\item \textbf{wavelets.ipynb}
+\end{itemize}
+
+\section{Data analysis package}
+\includepdf[pages=3-20,scale=0.9,clip,trim=0mm 20mm 0mm 20mm,pagecommand={}]{chapters/appendix/sphinx-vibrodiagnostics}
+
+\section{Data logger firmware}
+\includepdf[pages=2-10,scale=0.9,clip,trim=0mm 20mm 0mm 20mm,pagecommand={}]{chapters/appendix/doxygen-firmware}

### 2024-05-11 thesis/chapters/appendix/C-user-guide.tex
Export documentation from Sphinx and Doxygen

@@
 \section{Data logger guide}
-To measure vibrations with a data logger follow these steps:
+To measure vibrations with a data logger follow these steps.
 
 \begin{enumerate}[noitemsep]
-\item insert empty microSD card to the data logger,
-\item attach the accelerometer sensor to the surface of measurement,
-\item press the button and watch the LED light up,
-\item when the light turns off sooner before the minute mark, the buffer was dropped, and the final file can be incomplete,
-\item wait until the LED turns off, the recording is saved to file numbered sequentially from \emph{1.tsv} upwards,
-\item {move files from microSD card to a separate directory e.g. \emph{abc} and run for conversion to tsv files:
+\item Insert empty microSD card to the data logger.
+\item Attach the accelerometer sensor to the surface of measurement.
+\item Press the button and watch the LED light up.
+\item When the light turns off sooner before the minute mark, the buffer was dropped, and the final file can be incomplete.
+\item Wait until the LED turns off, the recording is saved to file numbered sequentially from \emph{1.tsv} upwards.
+\item {Move files from microSD card to a separate directory e.g. \emph{abc} and run for conversion to tsv files:
 \begin{lstlisting}[style=messages]
@@
 \section{Documentation guide}
-Built documentation is located in directory \emph{docs} of digital medium.
+Built documentation is located in directory \emph{docs} of the digital medium.
 It can be rebuild using documentation tools \emph{Doxygen} for firmware C source code and \emph{Sphinx} for data analysis Python code.
-The steps of generating documentation from souce codes are as follows:
+The steps of generating documentation from souce codes are as follows.
 
 \begin{enumerate}[noitemsep]
-\item {install necessary documentation tools:
+\item {Install necessary documentation tools:
 \begin{lstlisting}[style=messages]
 $ sudo pacman -S doxygen
-$ pip install sphinx
+$ pip install sphinx sphinx-rtd-theme sphinx_autodoc_defaultargs
 \end{lstlisting}}
-\item {rebuild the documentation using Doxygen and Sphinx:
+\item {Rebuild the documentation using Doxygen and Sphinx:
 \begin{lstlisting}[style=messages]

### 2024-05-11 DP_MiroslavHajek-zip/docs/vibrodiagnostics/source/conf.py

@@ -15,10 +15,11 @@ sys.path.append(os.path.abspath(
     os.path.join(__file__, '../../../../vibrodiagnostics')
 ))
 
-project = 'Machinery vibrodiagnostics with the IIOT'
+project = 'vibrodiagnostics'
 copyright = '2024, Miroslav Hájek'
 author = 'Miroslav Hájek'
 release = '1.0'
+
 
 # -- General configuration ---------------------------------------------------
 # https://www.sphinx-doc.org/en/master/usage/configuration.html#general-configuration
@@ -28,14 +29,30 @@ extensions = [
     'sphinx.ext.autosummary',  # Create neat summary tables
 ]
 autosummary_generate = True  # Turn on sphinx.ext.autosummary
+
 autodoc_typehints = 'description'
+
 
 templates_path = ['_templates']
 exclude_patterns = []
+
+latex_elements = {
+'papersize': 'a4paper',
+'pointsize': '10pt',
+'fontpkg': r"""
+\PassOptionsToPackage{bookmarksnumbered}{hyperref}
+""",
+# Additional stuff for the LaTeX preamble.
+'preamble': r"""
+\usepackage{setspace}
+""",
+
+'maketitle': "",
+}
 
 
 # -- Options for HTML output -------------------------------------------------
 # https://www.sphinx-doc.org/en/master/usage/configuration.html#options-for-html-output
 
-html_theme = 'alabaster'
+html_theme = 'sphinx_rtd_theme'
 html_static_path = ['_static']

### 2024-05-11 DP_MiroslavHajek-zip/vibrodiagnostics/extraction.py

@@ -17,49 +17,80 @@ from scipy.stats import entropy
 from scipy.signal import (
     find_peaks,
     windows,
-    welch
+    welch,
+    iirfilter,
+    lfilter,
+    decimate
 )
 from scipy.fft import rfft
 from scipy.interpolate import interp1d
 from tsfel import feature_extraction as ft
 import pywt
-from scipy.signal import iirfilter, lfilter, decimate
+
 
 from vibrodiagnostics import mafaulda
 
 
-def energy(pxx: np.array) -> float:
-    return np.sum(pxx ** 2)
+def energy(x: np.array) -> float:
+    """Calculate energy of the signal
+
+    :param x: input signal
+
+    :return: energy of the signal 
+    """
+    return np.sum(x ** 2)
 
 
 def negentropy(x: np.array) -> float:
+    """Calculate negentropy of the signal
+
+    :param x: input signal
+
+    :return: negentropy of the signal 
+    """
     if len(x) == 0:
         return np.nan
     return -entropy((x ** 2) / np.mean(x ** 2))
 
 
 def signal_to_noise(x: np.array) -> float:
-    # https://dsp.stackexchange.com/questions/76291/how-to-extract-noise-from-a-signal-in-order-to-get-both-noise-power-and-signal-p
-    # https://www.geeksforgeeks.org/signal-to-noise-ratio-formula/
-    # https://saturncloud.io/blog/calculating-signaltonoise-ratio-in-python-with-scipy-v11/
+    """Calculate estimated signal to noise ratio (noisiness) of the signal.
+    Formula is taken from: https://www.geeksforgeeks.org/signal-to-noise-ratio-formula/
+
+    :param x: input signal
+
+    :return: SNR of the signal 
+    """
     m = np.mean(x)
     sd = np.std(x)
     return np.where(sd == 0, 0, m / sd)
 
 
-def spectral_roll_off_frequency(f: np.array, Pxx: np.array, percentage: float) -> float:
-    """Roll-off: Cumulative sum of energy in spectral bins and find index in f array
-    'percentage' % of total energy below this frequency
+def spectral_roll_off_frequency(f: np.array, pxx: np.array, percentage: float) -> float:
+    """Calculate roll-off frequency. Cumulative sum of energy in spectral bins 
+    below roll-off frequency is percentage of total energy
+
+    :param f: array of frequency bins
+    :param pxx: array of amplitudes at frequency bins
+    :param percentage: ratio of total energy below the roll-off frequency
+
+    :return: roll-off frequency in Hz
     """
[…]

### 2024-05-11 DP_MiroslavHajek-zip/vibrodiagnostics/mafaulda.py

@@ -24,11 +24,16 @@ from vibrodiagnostics import extraction
 
 
 SAMPLING_RATE = 50000
+"""Sampling frequency in Hz of the sensors
+"""
 BEARING_A_COLUMNS = ['ax', 'ay', 'az']
 BEARING_B_COLUMNS = ['bx', 'by', 'bz']
 BEARINGS_COLUMNS = BEARING_A_COLUMNS + BEARING_B_COLUMNS
 COLUMNS = ['tachometer'] + BEARINGS_COLUMNS + ['mic']
 LABEL_COLUMNS = ['fault', 'severity', 'rpm']
+"""Metadata columns extracted from file path witin dataset
+"""
+
 
 BEARINGS = {
     'balls': 8,
@@ -39,6 +44,9 @@ BEARINGS = {
     'bsf_factor': 1.8710,
     'ftf_factor': 0.3750
 }
+"""Coeficients for bearing characteristic frequencies
+"""
+
 
 FAULTS = {
     'A': {
@@ -60,12 +68,15 @@ FAULTS = {
         'overhang-ball_fault': 'ball fault',
     }
 }
+"""Annotation of fault types by bearing placement
+"""
 
 
 def bearing_frequencies(rpm: int) -> Dict[str, float]:
-    """Calculate bearring characteristic frequencies for MaFaulDa machine simulator
+    """Calculate bearing characteristic frequencies for MaFaulDa machine simulator
 
     :param rpm: Rotational speed of the machine
+
     :return: Bearing defect frequencies
     """
     machine = {}
@@ -81,7 +92,8 @@ def bearing_frequencies(rpm: int) -> Dict[str, float]:
 def parse_filename(filename: str) -> Tuple[str, str, str]:
     """Split path of file within dataset structure to label the time series
 
-    :param filename: path to file inside of zip archive 
+    :param filename: path to file inside of zip archive
+
     :return: fault type, severity conditions, and file number
     """
     path = filename.split('/')
@@ -90,7 +102,7 @@ def parse_filename(filename: str) -> Tuple[str, str, str]:
         fault = f'{path[0]}-{path[1]}'
         severity = path[2]
         seq = path[3]
-    
+
     elif path[0].strip() == 'normal':
         fault, severity, seq = path[0], '0', path[1]
 
@@ -104,6 +116,7 @@ def rpm_calc(tachometer: pd.Series) -> float:
     """Extract rotational speed in rpm units from tachometer pulse signal
 
[…]

### 2024-05-11 DP_MiroslavHajek-zip/vibrodiagnostics/models.py

@@ -30,7 +30,13 @@ from river import preprocessing
 from river import neighbors, utils, evaluate, stream
 
 
-def transform_to_pca(X, n):
+def transform_to_pca(X: pd.DataFrame, n: int) -> pd.DataFrame:
+    """Transform features to their principal components after normalization
+
+    :param dataset: data frame with columns only for predictors
+    :param n: number of principal components
+    :return: data frames with rows of features replaced for principal components
+    """
     scaler = MinMaxScaler()
     X[X.columns] = scaler.fit_transform(X)
 
@@ -41,12 +47,21 @@ def transform_to_pca(X, n):
 
 
 def find_best_subset(
-        X: pd.DataFrame,
-        Y: pd.DataFrame,
-        metric: str,
-        members: int,
-        kfolds: int = 5
-    ):
+            X: pd.DataFrame,
+            Y: pd.Series,
+            metric: str,
+            members: int,
+            kfolds: int = 5
+        ) -> List[str]:
+    """Find the best subset of features based on supplied feature selection metric name
+
+    :param X: data frame of predictor features
+    :param Y: column of labels
+    :param metric: name of the bivariate similarity metric to compute for each feature and label
+    :param members: number of features in the subset
+    :param kfolds: number of splits for k-fold cross validation
+    :return: list of the best features according to feature selection metric
+    """
 
     kf = KFold(n_splits=kfolds, shuffle=True, random_state=10)
     elements = []
@@ -65,13 +80,30 @@ def find_best_subset(
 
 
 def kfold_accuracy(
-        X: pd.DataFrame,
-        Y: pd.DataFrame,
-        k_neighbors: int,
-        kfolds: int,
-        model_name: str, 
-        power_transform: bool = True,
-        knn_metric='euclidean') -> Dict[str, float]:
+            X: pd.DataFrame,
+            Y: pd.Series,
+            k_neighbors: int,
+            kfolds: int,
+            model_name: str = 'knn', 
+            power_transform: bool = True,
+            knn_metric='euclidean'
+        ) -> Dict[str, float]:
+
+    """Evaluate classifier accuracy in k-fold validation on a data frame of features after
+    oversampling to the majority class
+
+    :param X: data frame of predictor features
+    :param Y: column of labels
+    :param k_neighbors: number of neighbours for k-nearest neighbours model
+    :param model_name: name of the machine learning model to evaluate. 
+        Options are: "knn", "lda", "bayes", "svm"
[…]

### 2024-05-11 DP_MiroslavHajek-zip/vibrodiagnostics/pumps.py

@@ -14,13 +14,24 @@ from vibrodiagnostics import extraction
 
 
 SAMPLING_RATE = 26866
+"""Sampling frequency in Hz of the sensors
+"""
 BEARINGS_COLUMNS = ['x', 'y', 'z']
 COLUMNS = ['t'] +  BEARINGS_COLUMNS
 LABEL_COLUMNS = ['date', 'device', 'position']
+"""Metadata columns extracted from file path witin dataset
+"""
 G_CONSTANT = 9.80665
 
 
 def csv_import(dataset: ZipFile, filename: str) -> pd.DataFrame:
+    """Open a CSV file from Pump zip archive
+
+    :param dataset: ZIP archive of Pump industrial dataset
+    :param filename: path to the file within dataset
+
+    :return: data frame of the imported file
+    """
     if dataset is not None:
         name = dataset.open(filename)
     else:
@@ -33,7 +44,6 @@ def csv_import(dataset: ZipFile, filename: str) -> pd.DataFrame:
         header=0,
         names=COLUMNS
     ) 
-
     columns = BEARINGS_COLUMNS
     ts[columns] = ts[columns].apply(lambda x: G_CONSTANT * (x / 1000))
 
@@ -47,12 +57,24 @@ def csv_import(dataset: ZipFile, filename: str) -> pd.DataFrame:
 
 
 def features_by_domain(
-        features_calc: Callable,
-        dataset: ZipFile,
-        filename: str, 
-        window: int = None,
-        parts: int = None
-    ):
+            features_calc: Callable,
+            dataset: ZipFile,
+            filename: str, 
+            window: int = None,
+            parts: int = None
+        ) -> pd.DataFrame:
+    """Open a CSV file from Pump zip archive
+
+    :param features_calc: callback feature extraction function that
+        has parameters for data frame, column to process in data frame,
+        sampling frequency, window length of segment
+    :param dataset: ZIP archive of Pump dataset
+    :param filename: path to the file within dataset
+    :param window: length of window (usually for FFT)
+    :param parts: number of parts the input time series is split into
+
+    :return: row(s) of features extracted from the file
+    """
 
     fs = SAMPLING_RATE
     columns = BEARINGS_COLUMNS
@@ -80,11 +102,11 @@ def features_by_domain(
 
 
 def features_by_domain_no_metadata(
-        features_calc: Callable,
-        filename: str, 
-        window: int = None,
-        parts: int = None
-    ):
[…]

### 2024-05-11 DP_MiroslavHajek-zip/vibrodiagnostics/ranking.py

@@ -28,6 +28,8 @@ from vibrodiagnostics import selection
 
 
 class ExperimentOutput(Enum):
+    """Types of experimental scenarios for feature selection techniques
+    """
     COUNTS = auto()
     BEST_SET = auto()
     RANKS = auto()
@@ -40,12 +42,25 @@ class ExperimentOutput(Enum):
 
 
 def silhouette_scores(
-        X_train: pd.DataFrame,
-        X_test: pd.DataFrame,
-        Y_train: pd.DataFrame,
-        Y_test: pd.DataFrame,
-        best_features: list,
-        pc: int) -> Dict[str, float]:
+            X_train: pd.DataFrame,
+            X_test: pd.DataFrame,
+            Y_train: pd.DataFrame,
+            Y_test: pd.DataFrame,
+            best_features: List[str],
+            pc: int
+        ) -> Dict[str, float]:
+    """Calculate silhouette score of data points after normalization
+    of training and testing set with and without the pricipal components analysis
+
+    :param X_train: data points of the training set
+    :param X_test: data points of the testing set
+    :param Y_train: labels for the training set
+    :param Y_test: labels for the testing set
+    :param best_features: list of chosen feature names
+    :param pc: number of principal components
+
+    :return: silhouette scores for data points
+    """
     Y_train = Y_train.reset_index(drop=True).astype('category')
     Y_test = Y_test.reset_index(drop=True).astype('category')
 
@@ -66,13 +81,36 @@ def silhouette_scores(
 
 
 def pca_explained_variances(X_train: pd.DataFrame, pc: int) -> Dict[str, float]:
+    """Explained variances of the principal components 
+
+    :param X_train: data points of the training set
+    :param pc: number of principal components
+
+    :return: dictionary of principal components and explained variances
+    """
     scaler = MinMaxScaler()
     X_train[X_train.columns] = scaler.fit_transform(X_train)
     model = PCA(n_components=pc).fit(X_train)    
-    return {f'PC{pc}': var for pc, var in enumerate(model.explained_variance_ratio_, start=1)}
+    return {
+        f'PC{pc}': var 
+        for pc, var in enumerate(model.explained_variance_ratio_, start=1)
+    }
 
 
-def batch_feature_ranking(X: pd.DataFrame, Y: pd.DataFrame, mode: str = 'rank') -> pd.DataFrame:
+def batch_feature_ranking(
+            X: pd.DataFrame,
[…]

### 2024-05-11 thesis/chapters/appendix/B-technical-documentation.tex
Complete technical docs

@@
 
-\item \textbf{eda-pumps.ipynb}
-\item \textbf{eda-standing-fan.ipynb}
-\item \textbf{extraction-mafaulda.ipynb}
-\item \textbf{extraction-pumps.ipynb}
-\item \textbf{feature-summary.ipynb}
-\item \textbf{iit-src-paper.ipynb}
-\item \textbf{knn-batch.ipynb}
-\item \textbf{knn-mafaulda.ipynb}
-\item \textbf{knn-online.ipynb}
-\item \textbf{wavelets.ipynb}
+\item \textbf{eda-pumps.ipynb} - It visualizes amplitude histograms and frequency spectrum of every time series in the Pump dataset next to one another.
+Spectrograms of selected situations are depicted, such as rotation speed up or slow down.
+This notebook is instrumental in spotting patterns between different places and dates and checking for signal clipping.
+
+\item \textbf{eda-standing-fan.ipynb} - Estimate the rotational speed of the standing fan based on the audio recording and compare it to the estimate from vibrations.
+The accelerometer is attached to the back, side, and front of the shaft.
+
+\item \textbf{extraction-mafaulda.ipynb} - Feature extraction of a complete set of features from the entire MaFaulDa in time and frequency domain (TD and FD sets) to CSV files.
+Enable variable \emph{EXTRACT} to proceed with a lengthy calculation that takes around ten minutes for each set.
+When the extraction flag is disabled, the notebook loads the already extracted files with attributes.
+
+\item \textbf{extraction-pumps.ipynb} - Feature extraction of a complete set of features from Pump datatset in time and frequency domain (TD and FD sets) to CSV files.
+Enable variable \emph{EXTRACT} to proceed with calculation.
+
+\item \textbf{feature-summary.ipynb} - Count the occurrences of predictors in the best triplets over setup experimental conditions.
+Feature selection techniques produce bar charts with different orderings.
+The explained variance of complete feature sets is shown alongside the separability of clusters measured by silhouette score.
+This notebook generates CSV files of the best feature sets used in \emph{knn-batch.ipynb}.
+
+\item \textbf{iit-src-paper.ipynb} - Run the experiments described in IIT.SRC 2024 paper in Appendix~\ref{appendix:iit-src-paper}.
+Set variables \emph{USE\_ONE\_AXIS} and \emph{MAFAULDA\_ LABEL\_METHOD} to one of the allowed options to generate all possible results.
+Running the experiments and not reading precomputing results requires enabling \emph{GENERATE} variable.
+Additionally, the hyperparameters of the model can be changed to tune the accuracy.
+
+\item \textbf{knn-batch.ipynb} - Train k-NN classifiers with k = 5 on three members' best subsets of features found in \emph{feature-summary.ipynb}.
+Evaluate a wide range of performance metrics.
+Plot relation of k-neighbours on error rate for subset picked by the rank product method.
+
+\item \textbf{knn-mafaulda.ipynb} - The results of the experiments are described in the Exploratory analysis of MaFaulDa and the evaluation chapter.
+The setup of experimental scenarios for batch and incremental learning is followed by scales of features and their correlations.
+Every combination of parameters put into k-NN is captured in graphs of accuracy.
+Feature selection methods are compared under experimental conditions.
+Incremental learning on subset combinations is carried out in the gradual evolution of relative fault severities.
+
+\item \textbf{knn-online.ipynb} - Simulate incremental learning process for the complete feature sets.
+The source domain for features is chosen in variable \emph{DOMAIN}.
+The progressive valuation of k-NN accuracy compares situations with varied sliding windows and gaps between annotated observations.
+The performance at the end of the training is written in tables.
+
+\item \textbf{wavelets.ipynb} - Features computed from wavelet packet coefficients are chosen and sorted using feature selection scores.
+The effect of varying the depth of decomposition is viewed in stacked plots.
+The difference in scores between feature coefficients is plotted in bar charts.
 \end{itemize}

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/group__datalogger.tex
Thesis send to feedback

--- 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__datalogger.tex
@@
 \mbox{\hyperlink{group__button}{Button}}
-\begin{DoxyCompactList}\small\item\em Configuation of the recording button. \end{DoxyCompactList}\item 
+\begin{DoxyCompactList}\small\item\em Configuration of the recording button. \end{DoxyCompactList}\item 
 \mbox{\hyperlink{group__led}{LED}}
-\begin{DoxyCompactList}\small\item\em Configuation of the indicator LED light. \end{DoxyCompactList}\end{DoxyCompactItemize}
+\begin{DoxyCompactList}\small\item\em Configuration of the indicator LED light. \end{DoxyCompactList}\end{DoxyCompactItemize}
 \doxysubsubsubsection*{Macros}
@@
 void \mbox{\hyperlink{group__datalogger_gae496e529dd495b07dfadcb591230220d}{panic}} (int delay)
-\begin{DoxyCompactList}\small\item\em Signal fatal error of system occuring by blinking indicator LED and halting execution. \end{DoxyCompactList}\end{DoxyCompactItemize}
+\begin{DoxyCompactList}\small\item\em Signal fatal error of system indiacted by blinking LED and halting execution. \end{DoxyCompactList}\end{DoxyCompactItemize}
 
@@
 
-Signal fatal error of system occuring by blinking indicator LED and halting execution.
+Signal fatal error of system indiacted by blinking LED and halting execution.
 

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/group__sensor.tex
Thesis send to feedback

\doxysubsubsection{Accelerometer}
\hypertarget{group__sensor}{}\label{group__sensor}\index{Accelerometer@{Accelerometer}}

Configuration of the accelerometer sensor.

\doxysubsubsubsubsection*{Data Structures}
\begin{DoxyCompactItemize}
\item 
struct \mbox{\hyperlink{structAcceleration}{Acceleration}}
\begin{DoxyCompactList}\small\item\em Unprocessed data packet for storing samples from accelerometer. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsubsection*{Macros}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{group__sensor_ga4b76a0c2859cfd819a343a780070ee2b}\label{group__sensor_ga4b76a0c2859cfd819a343a780070ee2b} 
\#define {\bfseries SAMPLE\+\_\+\+RATE}~9000
\begin{DoxyCompactList}\small\item\em Interval of the periodic timer in milliseconds that reads out circa half of accelerometer FIFO. \end{DoxyCompactList}\item 
\Hypertarget{group__sensor_gabc52a50e07f79a25a6de181238b9d9aa}\label{group__sensor_gabc52a50e07f79a25a6de181238b9d9aa} 
\#define {\bfseries SPI\+\_\+\+BUS}~SPI3\+\_\+\+HOST
\begin{DoxyCompactList}\small\item\em Hardware bus for accelerometer SPI interface. \end{DoxyCompactList}\item 
\Hypertarget{group__sensor_ga0d440d9222595a142f2d3a4e9e69b11f}\label{group__sensor_ga0d440d9222595a142f2d3a4e9e69b11f} 
\#define {\bfseries AUTO\+\_\+\+TURN\+\_\+\+OFF\+\_\+\+US}~60000000
\begin{DoxyCompactList}\small\item\em Duration of recoding in microseconds (60 s) \end{DoxyCompactList}\item 
\Hypertarget{group__sensor_gac637c5a9d90797796a32b29b70e3a691}\label{group__sensor_gac637c5a9d90797796a32b29b70e3a691} 
\#define {\bfseries ACC\+\_\+\+RESOLUTION}~IIS3\+DWB\+\_\+4g
\begin{DoxyCompactList}\small\item\em Resolution of the accelerometer in a unit of g. \end{DoxyCompactList}\end{DoxyCompactItemize}
\doxysubsubsubsubsection*{Functions}
\begin{DoxyCompactItemize}
\item 
int \mbox{\hyperlink{group__sensor_ga844ea677736e4310ff9a9bee3935330a}{sensor\+\_\+enable}} (spi\+\_\+device\+\_\+handle\+\_\+t \texorpdfstring{$\ast$}{*}spi\+\_\+dev, stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}dev)
\begin{DoxyCompactList}\small\item\em Configure SPI bus and set accelerometer to required parameters. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__sensor_ga774ff5ef12bc72ef4d96e2ebef38d279}{sensor\+\_\+disable}} (spi\+\_\+device\+\_\+handle\+\_\+t spi\+\_\+dev)
\begin{DoxyCompactList}\small\item\em Remove accelerometer from the SPI bus and disable it. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__sensor_ga3a4369193c5acef70192d32950bd4db5}{sensor\+\_\+events\+\_\+enable}} (stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}dev)
\begin{DoxyCompactList}\small\item\em Enable accelerometer interrupts. \end{DoxyCompactList}\item 
void \mbox{\hyperlink{group__sensor_gafee0ba0827fd9f252c480faccdee0a97}{sensor\+\_\+events\+\_\+disable}} (stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}dev)
\begin{DoxyCompactList}\small\item\em Disable accelerometer interrupts. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsubsection{Detailed Description}
Configuration of the accelerometer sensor.

\doxysubsubsubsection{Function Documentation}
\Hypertarget{group__sensor_ga774ff5ef12bc72ef4d96e2ebef38d279}\label{group__sensor_ga774ff5ef12bc72ef4d96e2ebef38d279} 
\index{Accelerometer@{Accelerometer}!sensor\_disable@{sensor\_disable}}
\index{sensor\_disable@{sensor\_disable}!Accelerometer@{Accelerometer}}
\doxyparagraph{\texorpdfstring{sensor\_disable()}{sensor\_disable()}}
{\footnotesize\ttfamily void sensor\+\_\+disable (\begin{DoxyParamCaption}\item[{spi\+\_\+device\+\_\+handle\+\_\+t}]{spi\+\_\+dev }\end{DoxyParamCaption})}

Remove accelerometer from the SPI bus and disable it.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em spi\+\_\+dev} & SPI bus \\
\hline
\end{DoxyParams}
\Hypertarget{group__sensor_ga844ea677736e4310ff9a9bee3935330a}\label{group__sensor_ga844ea677736e4310ff9a9bee3935330a} 
\index{Accelerometer@{Accelerometer}!sensor\_enable@{sensor\_enable}}
\index{sensor\_enable@{sensor\_enable}!Accelerometer@{Accelerometer}}
\doxyparagraph{\texorpdfstring{sensor\_enable()}{sensor\_enable()}}
{\footnotesize\ttfamily int sensor\+\_\+enable (\begin{DoxyParamCaption}\item[{spi\+\_\+device\+\_\+handle\+\_\+t \texorpdfstring{$\ast$}{*}}]{spi\+\_\+dev,  }\item[{stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}}]{dev }\end{DoxyParamCaption})}

Configure SPI bus and set accelerometer to required parameters.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em spi\+\_\+dev} & SPI bus \\
\hline
\mbox{\texttt{ in}}  & {\em dev} & Accelerometer sensor\\
\hline
\end{DoxyParams}
\begin{DoxyReturn}{Returns}
Status code of successful setup 
\end{DoxyReturn}
\Hypertarget{group__sensor_gafee0ba0827fd9f252c480faccdee0a97}\label{group__sensor_gafee0ba0827fd9f252c480faccdee0a97} 
\index{Accelerometer@{Accelerometer}!sensor\_events\_disable@{sensor\_events\_disable}}
\index{sensor\_events\_disable@{sensor\_events\_disable}!Accelerometer@{Accelerometer}}
\doxyparagraph{\texorpdfstring{sensor\_events\_disable()}{sensor\_events\_disable()}}
{\footnotesize\ttfamily void sensor\+\_\+events\+\_\+disable (\begin{DoxyParamCaption}\item[{stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}}]{dev }\end{DoxyParamCaption})}

Disable accelerometer interrupts.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em dev} & Accelerometer sensor \\
\hline
\end{DoxyParams}
\Hypertarget{group__sensor_ga3a4369193c5acef70192d32950bd4db5}\label{group__sensor_ga3a4369193c5acef70192d32950bd4db5} 
\index{Accelerometer@{Accelerometer}!sensor\_events\_enable@{sensor\_events\_enable}}
\index{sensor\_events\_enable@{sensor\_events\_enable}!Accelerometer@{Accelerometer}}
\doxyparagraph{\texorpdfstring{sensor\_events\_enable()}{sensor\_events\_enable()}}
{\footnotesize\ttfamily void sensor\+\_\+events\+\_\+enable (\begin{DoxyParamCaption}\item[{stmdev\+\_\+ctx\+\_\+t \texorpdfstring{$\ast$}{*}}]{dev }\end{DoxyParamCaption})}

Enable accelerometer interrupts.

\begin{DoxyParams}[1]{Parameters}
\mbox{\texttt{ in}}  & {\em dev} & Accelerometer sensor \\
\hline
\end{DoxyParams}

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/main_8c.tex
Thesis send to feedback

--- 2024-05-11 DP_MiroslavHajek-zip/docs/firmware/latex/group__main.tex
@@
-\doxysubsection{Firmware Tasks}
-\hypertarget{group__main}{}\label{group__main}\index{Firmware Tasks@{Firmware Tasks}}
-
-Main program of the firmware execution.
-
+\doxysubsection{firmware/main/src/main.c File Reference}
+\hypertarget{main_8c}{}\label{main_8c}\index{firmware/main/src/main.c@{firmware/main/src/main.c}}
+{\ttfamily \#include "{}pinout.\+h"{}}\newline
 \doxysubsubsubsection*{Functions}
@@
 \item 
-\Hypertarget{group__main_ga0ec5d28752074ca54a70acc838f672e4}\label{group__main_ga0ec5d28752074ca54a70acc838f672e4} 
 void {\bfseries push\+\_\+trigger} (void \texorpdfstring{$\ast$}{*}args)
 \begin{DoxyCompactList}\small\item\em Task to start or stop recoding after siganl from button press. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0}\label{group__main_gac6ec22d4c97c0c96e99f3379d88cc6c0} 
 void {\bfseries read\+\_\+accelerometer} (void \texorpdfstring{$\ast$}{*}args)
 \begin{DoxyCompactList}\small\item\em Task to read FIFO buffer of the accelerometer and write it to Queue. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4}\label{group__main_gaeec34572dd8cb6da1ffaa4e74db0bca4} 
 void {\bfseries write\+\_\+card} (void \texorpdfstring{$\ast$}{*}args)
 \begin{DoxyCompactList}\small\item\em Task to write accelerations vectors from Queue to the memory card. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70}\label{group__main_ga630544a7f0a2cc40d8a7fefab7e2fe70} 
 void {\bfseries app\+\_\+main} (void)
@@
 \item 
-\Hypertarget{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a}\label{group__main_ga4bfd79880585a6aa3c7110a75dc0c82a} 
 Task\+Handle\+\_\+t {\bfseries trigger\+\_\+task}
 \begin{DoxyCompactList}\small\item\em Task handler for notification of button press. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_ga768ac04522700fd0788f959b1c7510cb}\label{group__main_ga768ac04522700fd0788f959b1c7510cb} 
 Task\+Handle\+\_\+t {\bfseries sampler\+\_\+task}
 \begin{DoxyCompactList}\small\item\em Task handler for notification from sampling timer. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gaa6b473c01115f6c0fd05415b7ca3a287}\label{group__main_gaa6b473c01115f6c0fd05415b7ca3a287} 
 Queue\+Handle\+\_\+t {\bfseries samples}
 \begin{DoxyCompactList}\small\item\em Queue for sending samples from the sensor read task to the memory card write task. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gaf04b0de520c6e42f039c5edf47b13dc2}\label{group__main_gaf04b0de520c6e42f039c5edf47b13dc2} 
 spi\+\_\+device\+\_\+handle\+\_\+t {\bfseries spi}
 \begin{DoxyCompactList}\small\item\em SPI bus handle. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_ga21408672a588f2b1db6f8f620eecbc59}\label{group__main_ga21408672a588f2b1db6f8f620eecbc59} 
 stmdev\+\_\+ctx\+\_\+t {\bfseries sensor}
 \begin{DoxyCompactList}\small\item\em Accelerometer sensor device. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gad85cb86f6cbc94b88b09c3315c9028f1}\label{group__main_gad85cb86f6cbc94b88b09c3315c9028f1} 
 sdmmc\+\_\+card\+\_\+t \texorpdfstring{$\ast$}{*} {\bfseries card} = NULL
 \begin{DoxyCompactList}\small\item\em SD memory card handle. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_ga702945180aa732857b380a007a7e2a21}\label{group__main_ga702945180aa732857b380a007a7e2a21} 
 FILE \texorpdfstring{$\ast$}{*} {\bfseries file} = NULL
 \begin{DoxyCompactList}\small\item\em Currently opened file handle. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_ga94544252c41b06346dc45f70cbd48d63}\label{group__main_ga94544252c41b06346dc45f70cbd48d63} 
 Semaphore\+Handle\+\_\+t {\bfseries file\+\_\+mutex}
 \begin{DoxyCompactList}\small\item\em Mutex to protect file handle. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gaf409115fcaa12619a90c9b581bafa64a}\label{group__main_gaf409115fcaa12619a90c9b581bafa64a} 
 bool {\bfseries is\+\_\+recording} = false
 \begin{DoxyCompactList}\small\item\em Flag for active recording in progress. \end{DoxyCompactList}\item 
-\Hypertarget{group__main_gad70a27ce9ba8cfa78153904f05e38c44}\label{group__main_gad70a27ce9ba8cfa78153904f05e38c44} 
 int32\+\_\+t {\bfseries sensor\+\_\+timestamp} = 0
@@
 \item 
-\Hypertarget{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1}\label{group__main_ga5e17ddc2ef9d796aedaa59e618c49af1} 
 esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries sampler\+\_\+timer}
@@
 \item 
-\Hypertarget{group__main_gab1d567cca0836a894a9577ba45fac511}\label{group__main_gab1d567cca0836a894a9577ba45fac511} 
 esp\+\_\+timer\+\_\+handle\+\_\+t {\bfseries stop\+\_\+timer}
@@
 \doxysubsubsection{Detailed Description}
-Main program of the firmware execution.
-
-\doxysubsubsection{Variable Documentation}
-\Hypertarget{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64}\label{group__main_ga6bc19a77e2c149ca9b7e86d2ad25ef64} 
-\index{Firmware Tasks@{Firmware Tasks}!sampler\_timer\_conf@{sampler\_timer\_conf}}
-\index{sampler\_timer\_conf@{sampler\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
-\doxyparagraph{\texorpdfstring{sampler\_timer\_conf}{sampler\_timer\_conf}}
-{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t sampler\+\_\+timer\+\_\+conf}
-
-{\bfseries Initial value\+:}
-\begin{DoxyCode}{0}
-\DoxyCodeLine{=\ \{}
-\DoxyCodeLine{\ \ \ \ \ \ \ \ .callback\ =\ \&isr\_sample}
-\DoxyCodeLine{\}}
-
-\end{DoxyCode}
-\Hypertarget{group__main_gacb077cf1ef581c961e7e5222a98f6897}\label{group__main_gacb077cf1ef581c961e7e5222a98f6897} 
-\index{Firmware Tasks@{Firmware Tasks}!stop\_timer\_conf@{stop\_timer\_conf}}
-\index{stop\_timer\_conf@{stop\_timer\_conf}!Firmware Tasks@{Firmware Tasks}}
-\doxyparagraph{\texorpdfstring{stop\_timer\_conf}{stop\_timer\_conf}}
-{\footnotesize\ttfamily const esp\+\_\+timer\+\_\+create\+\_\+args\+\_\+t stop\+\_\+timer\+\_\+conf}
-
-{\bfseries Initial value\+:}
-\begin{DoxyCode}{0}
-\DoxyCodeLine{=\ \{}
-\DoxyCodeLine{\ \ \ \ .callback\ =\ \&stop\_timer\_run}
-\DoxyCodeLine{\}}
-
-\end{DoxyCode}
+Application setup

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/structAcceleration.tex
Thesis send to feedback

\doxysubsection{Acceleration Struct Reference}
\hypertarget{structAcceleration}{}\label{structAcceleration}\index{Acceleration@{Acceleration}}

Unprocessed data packet for storing samples from accelerometer.

{\ttfamily \#include $<$pinout.\+h$>$}

\doxysubsubsubsection*{Data Fields}
\begin{DoxyCompactItemize}
\item 
\Hypertarget{structAcceleration_a08d970081c96582d6484a1dbb795be88}\label{structAcceleration_a08d970081c96582d6484a1dbb795be88} 
uint16\+\_\+t {\bfseries len}
\begin{DoxyCompactList}\small\item\em Number of samples in every array in the structure. \end{DoxyCompactList}\item 
\Hypertarget{structAcceleration_ab7a417b34f3fc19dc3ae14fa5ac4c0b6}\label{structAcceleration_ab7a417b34f3fc19dc3ae14fa5ac4c0b6} 
int32\+\_\+t {\bfseries t} \mbox{[}\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}}\mbox{]}
\begin{DoxyCompactList}\small\item\em Array of timestamps relative to time when sensor was enabled. \end{DoxyCompactList}\item 
\Hypertarget{structAcceleration_a4744bf8f88deaa5ae9f2e58ebb244dc7}\label{structAcceleration_a4744bf8f88deaa5ae9f2e58ebb244dc7} 
int32\+\_\+t {\bfseries x} \mbox{[}\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}}\mbox{]}
\begin{DoxyCompactList}\small\item\em Accelerometer samples for X axis. \end{DoxyCompactList}\item 
\Hypertarget{structAcceleration_abe8b39739af95fa91287e19c9b9ac3c6}\label{structAcceleration_abe8b39739af95fa91287e19c9b9ac3c6} 
int32\+\_\+t {\bfseries y} \mbox{[}\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}}\mbox{]}
\begin{DoxyCompactList}\small\item\em Accelerometer samples for Y axis. \end{DoxyCompactList}\item 
\Hypertarget{structAcceleration_aba0250b0210d700100bccaa29ff4ffa4}\label{structAcceleration_aba0250b0210d700100bccaa29ff4ffa4} 
int32\+\_\+t {\bfseries z} \mbox{[}\mbox{\hyperlink{group__datalogger_gaf759d6c69e76948f9933f3872d997adb}{FIFO\+\_\+\+LENGTH}}\mbox{]}
\begin{DoxyCompactList}\small\item\em Accelerometer samples for Z axis. \end{DoxyCompactList}\end{DoxyCompactItemize}

\doxysubsubsection{Detailed Description}
Unprocessed data packet for storing samples from accelerometer.

The documentation for this struct was generated from the following file\+:\begin{DoxyCompactItemize}
\item 
firmware/main/include/pinout.\+h\end{DoxyCompactItemize}

### 2024-05-13 DP_MiroslavHajek/docs/firmware/latex/topics.tex
Thesis send to feedback

\doxysubsection{Topics}
Here is a list of all topics with brief descriptions\+:\begin{DoxyCompactList}
\item \contentsline{section}{Accelerometer Data logger}{\pageref{group__datalogger}}{}
\begin{DoxyCompactList}
\item \contentsline{section}{Accelerometer}{\pageref{group__sensor}}{}
\item \contentsline{section}{Memory card}{\pageref{group__storage}}{}
\item \contentsline{section}{Button}{\pageref{group__button}}{}
\item \contentsline{section}{LED}{\pageref{group__led}}{}
\end{DoxyCompactList}
\item \contentsline{section}{Firmware Tasks}{\pageref{group__main}}{}
\end{DoxyCompactList}

### 2024-05-13 thesis/chapters/01-introduction.tex
Thesis send to feedback

@@
 
-The chapter~\ref{chapter:evaluation} on evalution validates the classification accuracy of feature sets from MaFaulDa and strategies for their subset choice in the k-nearest neighbour model.
+The chapter~\ref{chapter:evaluation} on evaluation validates the classification accuracy of feature sets from MaFaulDa and strategies for their subset choice in the k-nearest neighbour model.
 The vibration signals in the realistic environment are also analysed and recommendations for practical application and further study are discussed.

### 2024-05-13 thesis/chapters/02-analysis.tex
Complete evaluation
Thesis send to feedback

@@
 Models have to be resilient to any slight inclination or sensor orientation.
-To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidian norm is computed~\cite{kamminga_robust_2018}.
-
-\myequations{Feature euclidian norm}
+To satisfy this prerequisite, feature $f$ extracted from all three dimensions is first composed into a single vector and the Euclidean norm is computed~\cite{kamminga_robust_2018}.
+
+\myequations{Feature euclidean norm}
 \begin{ceqn}\begin{align}
@@
 
-\emph{Pearson correlation} coeficient expresses similarity between two quantitative features: $f_i$ and $f_j$.
-In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coeficient}.
+\emph{Pearson correlation} coefficient expresses similarity between two quantitative features: $f_i$ and $f_j$.
+In the classification setting, the correlation of feature $f$ makes sense only with dichotomous target class label $c$ using \emph{point biserial coefficient}.
 Mathematically, this is equivalent to the Pearson coefficient.
@@
 \end{adjustbox}
-\caption{Correlation coeficients}
+\caption{Correlation coefficients}
 \label{tab:corr-coef}
@@
 
-\item \textbf{Mutal information} - quantifies the dependence between features, or between features and class labels.
+\item \textbf{Mutual information} - quantifies the dependence between features, or between features and class labels.
 It is almost identical to Information Gain.
@@
 
-\myequations{Mutal information}
+\myequations{Mutual information}
 \begin{ceqn}\begin{align}
@@
 
-The meaning of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidian distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
+The meaning of distance between feature vectors $\mathbf{x}$, $\mathbf{y}$ have to be defined, so several metrics are available like \emph{Euclidean distance}, \emph{Mahalanobis distance}, \emph{Manhatann distance} etc.
 (Tab.~\ref{tab:KNN-distance})~\cite{sheng_review_2020, abu_alfeilat_effects_2019}.
@@
 Manhattan distance	 & $ |x_i - y_i| $													   \\ \hline
-Euclidian distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
+Euclidean distance    & $ \sqrt{\sum_{i = 1}^{n}(x_i - y_i)^2} $                               \\ \hline
 Mahalanobis distance  & $ (\mathbf{x} - \mathbf{y})^T C^{-1} (\mathbf{x} - \mathbf{y}) $       \\ \hline

### 2024-05-13 thesis/chapters/03-design.tex
Thesis send to feedback

@@
 During the design stage, we set out research questions and detail the steps of the machine learning pipeline for diagnosing fault types in the MaFaulDa dataset.
-The explanatory analysis of MaFaulDa hints at the underlying dependencies with feature sets that can degrade the machine learning model of choice.
-We adapt the methodology for measurements from standards and apply it to data logger requirements and data acquisition from industrial equipment.
+The explanatory analysis of MaFaulDa hints at the underlying dependencies within feature sets that can degrade the machine learning model of choice.
+We apply the methodology for vibration measurements from standards to the data logger requirements and data acquisition from industrial equipment.
 
 \section{Research questions}
-The thesis aims to provide answers to four research questions.
-The focus is primarily on making data flow more efficient in an industrial sensor network that monitors rotating machines.
+The thesis aims to provide answers to five research questions.
+The main focus is on making data flow more efficient in an industrial sensor network that monitors rotating machines.
 The \textbf{research questions} are:
@@
     \itemsep0pt
-	\item Which temporal and spectral features can be extracted from vibration signals to provide the most accurate record of machinery faults?
-	\item What is the reduction in transmission goodput when chosen signal features are used?
-	\item What accuracy of prediction models can be achieved with various feature subsets?
-	\item How can machinery faults be continuously identified and predicted based upon collected events?
+	\item Which time-domain and frequency-domain features are extractable from vibrations to provide the most accurate record of machinery faults?
+	\item What is the reduction in transmission goodput with signal features?
+	\item What accuracies of fault classification are achievable with tiny feature subsets?
+	\item How do the vibration signals collected on the industrial machinery behave?
+	\item How can machinery faults be identified over time from collected events?
 \end{enumerate}
 
-\noindent In accomplishing the objectives of our research we propose several \textbf{goals}:
+\noindent In accomplishing the objectives of our research, we propose several \textbf{goals}:
 \begin{todolist}
@@
     \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
-    \item Establish a list of conditions that should be later investigated in the experimental setting.
-    \item Prepare dataset to be used in conjunction with machine learning models, namely by identifying labels and balancing classes.
-    \item Find the best subsets of features in the time and frequnecy domain with previously analyzed feature extraction and selection methods.
+    \item Establish a list of conditions that will be investigated later in the experimental setting.
+    \item Prepare the dataset to be used in conjunction with machine learning models namely by identifying labels and balancing classes.
+    \item Find the best subsets of features in the time and frequency domain with previously analyzed feature extraction and selection methods.
     \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
@@
 
-We neglect the acceleration sensor orientation, therefore, the labels for shaft misalignment in vertical and horizontal directions are merged into the same group.
+We neglect the \textbf{acceleration sensor orientation}, therefore, the labels for shaft misalignment in vertical and horizontal directions are merged into the same group.
 In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
 
-Depending on the chosen bearing position, only time series associated with that bearing are retained because the standards demand each bearing be assessed separately.
+Depending on the \textbf{chosen bearing position}, only time series associated with that bearing are retained because the standards demand each bearing be assessed separately.
 Fault classification concerns bearing in direct contact and shaft mechanically passing through it.
@@
 
-The final \textbf{file description} is the triplet of \textbf{fault}, \textbf{severity}, and \textbf{rpm}.
+\textbf{File description} is the triplet of \textbf{fault}, \textbf{severity}, and \textbf{rpm}.
 
 After labeling we insert a step to split the time series into parts when the duration is long enough to introduce more observations artificially.
-This assumption is not met for MaFaulDa because, for the desired frequency resolution for features of close to 1~Hz, we need a window size of 32768 samples.
+This assumption for splitting is not met for MaFaulDa because, for the desired frequency resolution for features of close to 1~Hz, we need a window size of 32768 samples.
 Variation reduction in spectral estimation brings the necessity to average at least 12 overlapping windows.
@@
 
-The DC component in the three-dimensional vibration signal is removed by subtracting the global mean.
+The \textbf{DC component} in the three-dimensional vibration signal is removed by subtracting the global mean.
 Immediately follows a digital IIR Butterworth low pass filter of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
@@
 
-Initial labels can be exchanged for a label of fault-free state when the severity is low.
+\textbf{Initial labels can be exchanged} for a label of fault-free state when the severity is low.
 The count of severity levels is not identical in every group.
@@
 
-The preprocessed signal from each axis of accelerometer is packed up to two base feature sets in time domain (TD) and frequency domain (FD).
+The preprocessed signal from each axis of accelerometer is packed up to \textbf{two base feature sets} in time domain (TD) and frequency domain (FD).
 The feature extraction formulas are is identical with formulas presented in the section \ref{section:feature-extraction} of analysis chapter.
@@
 
-The four conditions are applied in the instance of the pipeline to filter observations with calculated features to create 24 scenarios:
+The four conditions are applied in the instance of the pipeline to filter observations with calculated features to create \textbf{24 scenarios}:
 \begin{itemize}
@@
 
-The fault classification performance metrics are evaluated after balancing classes feature normalization, and 5-fold cross-validation validation on the k-nearest neighbor classifier with Euclidean distance metric.
+The \textbf{fault classification} performance metrics are evaluated after balancing classes feature normalization, and 5-fold cross-validation validation on the k-nearest neighbor classifier with Euclidean distance metric.
 The population of classes is evened out with random oversampling using a strategy to resample all but the majority class.
@@
 
-The hyperparameter of k-neighbours and a subset of features are tweaked, and results are compared under different preprocessing conditions and in multiple experiments:
+The hyperparameter of k-neighbours and a feature subset size are tweaked, and results are compared under different preprocessing conditions and in multiple experiments:
 
@@
 Out of the 1951 time series, the inner bearing (A) has 1438, and the outer bearing (B) has 1393~(Tab.~\ref{tab:design:label-count}).
-Sorce bearing A+B just concatanes observations from both postions so the column sums their counts together.
+Source bearing A+B just concatanes observations from both postions so the column sums their counts together.
 The observations for shaft defects are shared regardless of the bearing.

### 2024-05-13 thesis/chapters/05-evaluation.tex
Thesis send to feedback

@@
 \chapter{Evaluation} \label{chapter:evaluation}
-The verification of proposed solutions for machinery fault diagnostics is focused on two complementary activities, these are vibration measurement and defect identification.
+The verification of proposed solutions for machinery fault diagnostics is focused on two activities, these are vibration measurement and defect identification.
 The accuracy of supervised learning using the k-nearest neighbour classifier is determined by the MaFaulDa dataset under various experiments.
@@
 
-\section{MaFaulDa in k-nearest neighbors}
+\section{Fault classifiction in MaFaulDa}
 The four outlined experiments on MaFaulDa involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum.
@@
 The label ``normal'' is not falsely attributed to other classes in either feature set, but other classes can get assigned to be ``normal''.
-Most mistakes happen while predicting outer race fault, which is confused with cage fault, imbalance, and less frequency with misalignment.
+Most mistakes happen while predicting outer race fault, which is confused with cage fault, imbalance, and less often with misalignment.
 The shaft imbalance is used for simulating bearing faults, which is a natural reason for this high error rate.
@@
 The TD set is generally better in predictions than the FD set for the equivalent k-value.
-The relabeled dataset for high severity has a steeper decrease in accuracy for the same value of neighbours.
+The relabeled dataset for high severity has a steeper decrease in accuracy for the same number of neighbours.
 
@@
 The complete sets of predictors are even greatly shrunken to representation that could be presented in 3D plot or in perpendicular cross sections.
-These trend variables could be used in distingushing faults the same way as rms amplitude indicates their presence.
+These trend variables could be used in distinguishing faults the same way as rms amplitude indicates their presence.
 Each possible combinations of pairs, triplets, and quadruplets constructs a separate k-NN model on which prediction accuracy is evaluated.
@@
 The decrease in accuracy with additional neighbours is apparent and similar to the trend in complete sets of features.
-We are interested in maximum accuracy in the distribution because that is the optimal model feature selection method to try to approach.
-Its reduction is more noticeable between three and five features 3 - 5\%, and almost the same amount between five and eleven neighbours.
+We are interested in comparing maximum accuracies of the accuracy distribution because the optimal feature selection method tries to approach them.
+The reduction in maximal accuracy is more noticeable between three and five features 3 - 5\%, and almost the same amount between five and eleven neighbours.
 
@@
 The percentile within the distribution is measured to its respective data, the train or validation set.
-However, the percentile of best features in the test is calculated against train distribution.
+However, the percentile of best features in the test data is calculated against train distribution.
 
@@
 This is evidenced by the variability of the success of selected feature sets in final prediction performance under multiple conditions.
-The PCA with 3 components out of complete feature sets is comparable in accuracy to selection methods with original attributes.
+The PCA with 3 components transformed from the complete feature sets is comparable in accuracy to selection methods with original attributes.
 
@@
     \end{subfigure}
-    \caption{Model accuracy statistical distibutions with feature selection methods for three predictors (k = 5)}
+    \caption{Model accuracy statistical distributions with feature selection methods for three predictors (k = 5)}
     \label{fig:evaluation:fsel-model-distr}
@@
 
-Under 216 scenarios, the mutual information has better median accuracy (80.87\%) and distribution percentile (91.81\%) followed by rank product with an accuracy of 79.82\% of and percentile of 88.97\% (Tab.~\ref{tab:evaluation:compare-fsel-accuracy}).
+In 216 scenarios, the mutual information has better median accuracy (80.87\%) and distribution percentile (91.81\%) followed by rank product with an accuracy of 79.82\% of and percentile of 88.97\% (Tab.~\ref{tab:evaluation:compare-fsel-accuracy}).
 The scenarios are composed of 24 base dataset modifications and options for hyperparameters k-value and number of features.
 
-The rank product was the best method in the majority of 43.52\% scenarios.
+The rank product is the best method in the majority of 43.52\% scenarios.
 Mutual information comes second in 40.28\% cases, where it is deemed the best strategy (Tab.~\ref{tab:evaluation:best-selection-method}).
-The median accuracy in selected cases is also better for rank product 92.38\% compared to 91.79\% mutual information.
+The median accuracy, in cases where they are the best method, is also better for rank product 92.38\% compared to 91.79\% mutual information.
 
@@
 Delayed provision or omission of actual labels undoubtedly degrades the reliability of the classification.
-The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what is the effect on the classifier from routine difficulties associated with the continous labeling process.
+The question is how quickly the accuracy approaches the optimal one from the nearest neighbors trained in batch and what is the effect on the classifier from routine difficulties associated with the continuous labeling process.
 
@@
 
-The k-NN models in incremental learning experiments learn on the same base training dataset as in batch learning for bearing A with complete sets of extracted features.
-In this manner, we can compare the training accuracies in the last sample for both models.
+The k-NN models in incremental learning experiments learn on the same base training dataset as in batch learning for bearing A.
 Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
+In this manner, we can compare the training accuracies in the last sample of online models to their batch counterparts.
 
@@
 A significant change in the data stream occurs after 294 out of 1438 observations (or after 737 for high severity faults) when all 49 (or 737) normal conditions are consumed in the training process.
-Counters of other faults show that predictions are skewed towards more represented imbalance and misalignement.
+Counters of other faults show that predictions are skewed towards more represented imbalance and misalignment.
 The uneven evolution of categories in a stream impacts the development of accuracy in the remaining experiments.
@@
 The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram.
-The methodology is carried out to diagnose the current status of water pumps.
+The domain expert methodology is carried out to diagnose the current status of water pumps.
 The presence of fault is confronted with sensor logs from the pump vendor.
@@
 The M2 in place two compared to M1 has elevated amplitudes above 4 kHz.
-The pumps have richer signal content, likely due to the flow of water split into several frequency bands.
+The pumps have richer signal content than motors split into several frequency bands, likely due to the flow of water.
 The outer bearing (4) has a more attenuated amplitude above 1.5 kHz than the inner bearing (3).
@@
 
-Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and then they approved the following results.
+Domain experts recommended the procedure for fault identification by calculation of bearing characteristic frequencies (Tab.~\ref{tab:evaluation:bearing-freq-pump}), and they approved the following results.
 Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2.
@@
 During the over five years the pump has been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance.
-This underscores the difficulty of the scarcity of non-faulty states in industrial environments.
+This underscores the scarcity of recording faulty states in industrial environments.
 The monitoring is better suited for situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.
@@
     \end{subfigure}
-    \caption{The atrribute value ranges of Pump dataset}
+    \caption{The attribute value ranges of Pump dataset}
 \end{figure}
@@
 The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}).
-The increses can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).
+The increases can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

### 2024-05-13 thesis/chapters/06-conclusion.tex
Export documentation from Sphinx and Doxygen
Thesis send to feedback

--- 2024-04-28 thesis/chapters/06-conclusion.tex
@@
 \chapter{Conclusion} \label{section:conclusion}  
+The focus of this master's thesis is on the optimal choice of trend indicators from vibration signals in an inexpensive industrial condition monitoring solution.
+The goal is to enable timely fault detection of machinery parts with as little input data as possible.
+We answer five proposed \textbf{research questions} (RQ) for those purposes.
+
+The variables to describe machine behaviour come from mechanical properties of bearings, descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards: ISO 20816 and ISO 13373.
+The formulas compute a complete set of features that are ten features summarizing the waveform in the time domain (\emph{TD}) and eleven features describing spectral density estimation (\emph{FD}).
+The features are obtained in the axis of the jitter or are aggregated from all three spatial directions (\textbf{RQ1}).
+
+The groups of three features are chosen in each domain to achieve even more pronounced data savings.
+We strive to keep the predictors that together have the most resemblance to the target variable.
+Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are computed in supervised learning scenarios.
+The features are squished from multiple dimensions using the Euclidian norm.
+Lossy compression ratios attained are 2381:1 for all features and 25000:1 for six features from the MaFaulDa dataset.
+We managed to discard more than 99.995\% of the irrelevant data (\textbf{RQ2}).
+
+The designed preprocessing pipeline creates the attributes from time series.
+The k-nearest neighbour classifier ascertains their relative fault detection power by five-fold cross-validation.
+The experiments for k-NN model evaluation include complete feature sets with one for each domain, the exhaustively enumerated feature subset combinations, and features subset chosen by filtering feature selection methods.
+
+We found that the time-domain features reach higher accuracies than the frequency-domain set because of less intercorrelations.
+Increase in the number of neighbours for k-NN used on complete sets, the smaller the model accuracy.
+Above the k-value of thirteen, the trend for complete feature sets flattens out gradually.
+Predictors aggregated from tri-axis recording performed better in classification than those from one axis.
+
+The k-NN accuracy with different feature subset combinations pulled out of the complete sets has a standard deviation of 7\%, and it is 10\% within IQR.
+Within such range, the feature selection methods can pick, in most cases, a group with accuracy above the upper quartile of accuracy distribution of every attribute combination with the same cardinality.
+Training k-NN on three principal components produced worse accuracy than filtering feature selection.
+
+The ensemble feature selection methods as the rank product are necessary to balance the adverse effect of individual selection metrics.
+In the slight majority of 44\% of 216 dataset alterations, the rank product found the best-performing attributes closely followed by mutual information.
+The rank product also reaches the 97.50\% percentile in the accuracy distribution in the same-sized sets.
+Mutual information has a better distribution percentile of 2.84\% from rank product \textbf{(RQ3)}.
+
+The number of features has a direct proportionality effect accuracy but at most 6\% increase is observed in moving from two to three features.
+The absolute best predictor triplets for MaFaulDa are in TD (accuracy of 85.47\%): zero-crossing rate, peak-to-peak, skewness, and in FD (accuracy of 87.52\%): spectral centroid, roll-off frequency, and entropy \textbf{(RQ3)}.
+
+The vibrations were also collected for over a month with a custom assembled accelerometer data logger.
+The designated machines were air conditioning compressors and water pumps with motors in municipal pumping station.
+The data logger firmware reads samples from the accelerometer at 26.8 kHz and stores them onto a MicroSD card.
+
+Collected dataset analysis confirmed the stationarity of the signal spectrum of the signal and length of five-second time series as satisfactory for feature extraction.
+The dataset serves as a practical demonstartion of labeling potentialy future faults from bearing defect frequency amplitudes.
+It also proved the immense difficulty of obtaining observations of faulty machinery parts in the field without purposefully damaging bearings and offsetting the shaft \textbf{(RQ4)}.
+
+The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables.
+Annotations can be assigned belatedly or even never.
+Incremental learning k-NN algorithm on an unbalanced dataset of three member feature sets achieves at best 77\% accuracy with labels coming in 100 samples long tumbling windows.
+The accuracy of 67\% is reached for the online model when just 10\% of observations stay associated with the label.
+The comparable model trained in batch reaches an accuracy of 88\% \textbf{(RQ5)}.
+
+\textbf{Future work} can extend various aspects and additional questions arising from the experiments in the thesis.
+The natural extension is to confirm that the results hold in other publicly available datasets of machinery faults, e.g.
+in CWRU.
+The other alteration is to use more different starting base feature sets.
+Harmonic frequencies or wavelet coefficients can generate predictors that could be further reduced to the smallest possible subsets.
+
+Ensemble strategies inspired by classical election systems may be utilized in the task of feature selection.
+Different feasible types of classifiers for online learning could be compared to k-nearest neighbours, e.g.
+Hoeffding tree.
+A data logger could be combined with the classifier model and a mechanism to annotate observation either automatically depending on the overall vibration level or manually during maintenance or after an unexpected failure.
+
+The strategic aim would be to connect sensors on a large scale on multiple test rigs to train individual models on each bearing and combine them in a federative learning approach.
+Of course, vibration monitoring can be employed in other diagnostic tasks with no direct expert knowledge, such as train wheel or rail degradation due to wear and tear.

### 2024-05-13 thesis/chapters/appendix/A-resume.tex
Thesis send to feedback

--- 2024-04-30 thesis/chapters/appendix/A-resume.tex
@@
 Vibroakustická diagnostika sa preto považuje za jednu z najdôležitejších metód pri včasnej identifikácii porúch komponentov.
-Najbežnejšie sa vyskytujúcimi poruchami sú nevyváženosť, nesúososť, vôľa, excentricita, deformácia, trhlina a nadmerné trenie.
+Najbežnejšie sa vyskytujúcimi poruchami sú nevyváženosť, nesúosovosť, vôľa, excentricita, deformácia, trhlina a nadmerné trenie.
 
@@
 Najrozšírenejšími používanými atribútmi sú štatistické miery centrálneho momentu: priemer, rozptyl, štandardná odchýlka, šikmosť a špicatosť.
-Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička a maximum.
+Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička, maximum, absolútnu zmenu amplitúdy (AAC), a početnosť prechodov nulou.
 Ostatné významné atribúty časovej oblasti sú odvodené ako pomery a sú nim: faktor výkyvu, faktor rozpätia, faktor impulzu a faktor tvaru.
@@
 \section{Diagnostické prístupy}
-Identifikácia porúch v rotujúcich strojoch je binárny alebo viactriedny klasifikačný problém, ktorý pracuje na princípe učenia čiastočne s učiteľom, pretože označenia pre degradované stavy stroja sú v praxi zriedkavé.
+Identifikácia porúch v rotujúcich strojoch je binárny alebo viac triedny klasifikačný problém, ktorý pracuje na princípe učenia čiastočne s učiteľom, pretože označenia pre degradované stavy stroja sú v praxi zriedkavé.
 Ciele automatizácie monitorovania možno rozdeliť na detekciu anomálií a rozpoznanie typu poruchy.
@@
 DenStream je algoritmus zhlukovania založený na hustote prispôsobený z DBSCAN na zhlukovanie prúdových dát do ľubovoľne tvarovaných skupín.
-Half-space strom predpokladá, že náhodné delenie v každej osi v priestore atribútov izoluje odľahlé hodnoty do samostatných oddielov skôr ako nedeviantné pozorovania.
 
-Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
+Presná viac triedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
 Algoritmus k-najbližších susedov (k-NN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
@@
 \section{Výskumné otázky}
-Cieľom tejto práce je poskytnúť odpovede na štyri výskumné otázky:
+Cieľom tejto práce je poskytnúť odpovede na päť výskumných otázok:
 \begin{enumerate}
@@
 \item Aké budú presnosti diagnostiky porúch s rôznymi sadami atribútov?
+\item Ako sa správajú vibračné signály zozbierané na priemyselných strojoch?
 \item Ako môžeme priebežne označovať poruchové stavy?
@@
 \section{Návrh spracovania pre MaFaulDa}
+Vo všeobecnosti pozostáva spracovanie signálov vibrácií zo získavania signálu, extrakcie atribútov, redukcie rozmerov a rozpoznávania vzorov alebo detekcie porúch.
+Realizácia uvedeného postupu je dekomponovaná podľa štruktúry dát a parametrov jednotlivých fáz.
+
+Predspracovanie najskôr priradí metadáta časovým radom v CSV súboroch z MaFaulDa podľa ich cesty v adresárovej štruktúre.
+Na základe pôvodného označenia porúch a polohy ložiska je ponechaných šesť tried: bezporuchový stav, nevyváženosť, nesúosovosť, porucha klietky, guľôčok a vonkajšej dráhy ložiska.
+Každé ložisko sa posudzuje zvlášť.
+Každú nahrávku popisuje trojica typu poruchy, závažnosti a rýchlosti otáčok.
+
+Nasleduje rozdelenie časových radov na menšie rovnako veľké časti, ak je ich trvanie dlhšie ako dvanásť okien s rozlíšením okolo 1 Hz, to však neplatí pre MaFaulDa.
+Jednosmerná zložka a frekvencie nad 10 kHz sú odfiltrované z pôvodných signálov vibrácií.
+Pôvodne priradené triedy porúch sú pri niektorých experimentoch vymenené za bezporuchový stav, keď je zaznamenaná závažnosť poruchy nízka.
+
+Z predspracovaného signálu v každej osi akcelerometra sú vypočítané dve základné sady atribútov v časovej (TD) a frekvenčnej doméne (FD).
+Na filtrovanie pozorovaní sa používajú štyri podmienky: umiestnenie ložiska (A alebo B), doména základnej sady (TD alebo FD) atribútov, osi akcelerometra použité na výpočet atribútu (jedna alebo tri), ponechanie označení iba pre poruchy vyššej závažnosti (áno alebo nie).
+Uvedené podmienky vytvárajú dohromady 24 scenárov.
+
+Úspešnosť klasifikácie porúch strojov sa vyhodnocuje po normalizácii atribútov, vyvážení mohutnosti tried a päťnásobnej krížovej validácii na klasifikátore k-najbližších susedov s euklidovskou metrikou vzdialenosti.
+Presnosti sa porovnávajú pre rôzne hodnoty hyperparametrov k-susedov a veľkosti podmnožiny atribútov podľa uvedených scenárov.
+
+Návrh experimentov zahŕňa popísané filtračné podmienky, ktoré upravia MaFaulDa do 24 podôb.
+Navyše v postupnom učení sa porovnávajú dĺžka oneskorovania anotácii a ich vynechávanie.
+Štyri hlavné experimenty pre porovnanie výberu podmnožiny atribútov zahŕňajú klasifikáciu porúch na základných sád atribútov, na všetkých kombinácií podmnožín prediktorov s určitou veľkosťou, na najlepších atribútoch vybraných cez metriky podobnosti s cieľovou premennou a pomocou modeloch postupného učenia s sťaženým prístupom k pravdivým označeniam tried.
 
 \section{Zber vibrácií v priemysle}
+Metodiku uplatnenú na súbore údajov MaFaulDa z laboratórneho prostredia aplikujeme na vibrácie z priemyslu.
+Pri monitorovaní je zužitkovaný postup podľa technických noriem.
+Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie, predbežné merania a vývoj senzorovej jednotky.
+
+Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektromotormi v prečerpávacej stanici na pitnú vodu.
+Merania sú uskutočnené vlastným data loggerom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu s mesačným rozostupom.
+Ako senzor vibrácii je použitý MEMS akcelerometer IIS3DWB.
+Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
+
+Meranie vibrácií na jednom ložisku stroja zahŕňa tri pokusy s nahrávkou o dĺžke 60 sekúnd.
+Po každom zázname je akcelerometer znova pripevnený na meraciu pozíciu.
+Snímač je pripevnený k stroju na rovnom povrchu s obojstrannou kobercovou páskou.
 
 \section{Vyhodnotenie presnosti diagnostiky}
+Overovanie navrhovaných riešení diagnostiky porúch strojov sa zameriava na dve činnosti, ktorými sú meranie vibrácií a identifikácia porúch.
+
+Väčšina zámen pri odhaľovaní porúch spraví model pri poruche vonkajšieho krúžku ložiska vonkajšej rasy, ktorá sa označuje za poruchu klietky ložiska, nerovnováhu hriadeľa a menej často za nesúosovosť.
+Nevyváženosť hriadeľa zabezpečuje v laboratóriu simuláciu porúch ložísk, čiže tam nastáva prirodzene k veľkej zámene typov porúch.
+
+Zvyšujúci sa počet susedov použitých na klasifikáciu s k-NN ukazuje podstatné zníženie presnosti na testovacích dátach.
+Najvýraznejší pokles o približne 10\% nastáva na po deväť susedov.
+Atribúty vytvorené z trojosového vektora dosahujú lepšiu presnosť ako tie výhradne z osi pohybu pre rovnakú zdrojovú doménu a ložisko.
+Model pre vnútorné ložisko A je presnejší ako vonkajšie ložisko B.
+Sada TD je lepšia v identifikácii porúch ako sada FD pre ekvivalentnú hodnotu k.
+Dátová sada s anotáciami pre poruchy vysokej závažnosti má prudšie zníženie presnosti pre rovnaký počet susedov.
+
+Základné sady prediktorov sú ešte značne zmenšené na reprezentáciu, ktorá by mohla byť prezentovaná v 3D grafe alebo v rovinných rezoch.
+Každá možná kombinácia párov, trojíc a štvoríc natrénuje samostatný k-NN model, na ktorom sa hodnotí presnosť klasifikácie.
+Zníženie presnosti so zvzšujúcim sa počtom susedov je zrejmé a podobné trendu v základných sadách atribútov.
+Zníženie maximálnej presnosti je výraznejšie medzi tromi a piatimi susedmi a takmer o rovnaké množstvo sa degraduje model medzi piatimi a jedenástimi susedmi.
+
+Základné množiny atribútov dosahujú lepšiu presnosť ako ich podmnožiny, keď počet prvkov je najviac tri a súčasne počet susedov je päť alebo menej.
+Počet prvkov má priamy úmerný vplyv na presnosť optimálneho modelu. Presun z dvoch na tri atribúty má väčšiu váhu ako povolenie štvrtého atribútu.
+
+Prediktory vybrané pomocou stratégií výberu sú porovnané s presnosťou klasifikácie kombinácie skupín atribútov rovnakej veľkosti a s presnosťou ich zdrojovej nadmnožiny.
+Na získanie konzistentnej presnosti je potrebné kombinovať hodnotenia z niekoľkých metrík výberu atribútov.
+PCA o troch komponentoch transformovaných zo základných sád atribútov je presnosťou porovnateľná s metódami výberu s pôvodnými atribútmi.
+Trojica prediktorov s najlepšími výsledkami zo sady TD sú: početnosť prechodov nulou, vzdialenosť špička-špička, šikmosť a zo sady FD: spektrálne ťažisko, roll-off frekvencia a entropia.
+
+Metrika vzájomnej informácie dosahuje lepšiu strednú presnosť (80,87\%) a percentil v distribúcii presností (91,81\%).
+Nasledovaná je súčinom poradí s presnosťou 79,82\% a percentilom 88,97\% Súčin poradí je najlepšou metódou v 43,52\% scenárov, kde je považovaný za najlepšiu stratégiu.
+Vzájomné informácie je na druhom mieste s 40,28\% prípadov.
+Stredná presnosť vo prípadoch, kde je zvolená metóda výberu najlepšia je tiež lepšia pre súčin poradí s 92,38\% v porovnaní s 91,79\% pri vzájomnej informácii.
+Výber atribútov zvyčajne vyberá premenné tak, aby sa ich presnosť objavila v hornom kvartile distribúcie.
+
+Postupné učenie napodobňuje sprísnené podmienky pre diagnostiku strojov, ktoré sa objavujú pri nasadení v praxi.
+Oneskorené poskytnutie alebo vynechanie skutočných označení nepochybne znižuje spoľahlivosť klasifikácie.
+Modely k-NN v experimentoch s postupným učením sa učia na rovnakom základnom súbore trénovacích údajov ako pri dávkovom učení pre ložisko A.
+Metriky online vzdelávania sa vyhodnocujú progresívnym vyhodnotením na nevyváženom súbore údajov.
+Presnosti klasifikácie medzi postupným a dávkovým učením sa porovnáva na finálnej presnosti online modelu.
+
+Udalosti sú usporiadané podľa stúpajúcej úrovne relatívnej závažnosti, čím simulujeme postupnú celkovú degradáciu stroja.
+Presnosť testov porovnateľných dávkových modelov z troch najlepších vlastností je 85,47\% (TD), 87,52\% (FD), 91,71\% (TD, závažnosť) a 91,94\% (FD, závažnosť).
+Najvyššie presnosti po postupnom zhliadnutí vzoriek v najdlhších posuvných oknách s dĺžkou 100 pozorovaní sú znížené v porovnaní s dávkovým modelom o 9,76\% (TD), 10,54\% (FD), 14,73\% (TD, závažnosť) a 11,38\% (FD, závažnosť).
+Ponechanie 10\% anotácii ich rovnomerným vynechávaním a trénovanie modelu s oknom 10 vzoriek zníži maximálnu presnosť modelu s tromi prediktormi v časovej doméne o 9,9\% na 66,78\% a o 14,93\%  na 67,00\% vo frekvenčnej doméne.
 
 \section{Rozbor dátovej sady z priemyslu}
+Správanie sa rôznych strojov je porovnaná vo frekvenčnej doméne a cez časovo-frekvenčné spektrogramy.
+Aktuálny stav čerpadiel nameraný vlastným data loggerom je obohatený o záznamy so senzora vibrácii od výrobcu.
+Potenciálne poruchy sú diagnostikované podľa postupu od doménových expertov.
+
+Motor M2 na pozícii dva má zvýšené amplitúdy nad 4 kHz v porovnaní s motorom M1.
+Čerpadlá majú členitejší obsah frekvenčného signálu ako motory, pravdepodobne v dôsledku toku vody.
+Vonkajšie ložisko čerpadla (4) vykazuje nižšiu amplitúdu vibrácií nad 1,5 kHz ako vnútorné ložisko (3).
+Čerpadlo P2 vo všeobecnosti vykazuje menšie vibrácie v porovnateľných pásmach.
+Skriňa kompresora vytvára sériu harmonických frekvencií, ktoré sú silnejšie v blízkosti sacieho ventilu ako v blízkosti základne.
+
+Doménoví experti odporučili postup identifikácie porúch výpočtom charakteristických frekvencií ložísk.
+Vo frekvenciách sú viditeľné harmonické frekvencie rýchlosti rotácie frekvencie BPFO pri každom stroji a BPFI pre M2-2.
+Dá sa predpokladať, že práve tieto frekvencie budú v budúcnosti dôvodom poškodenia strojov.
+
+Aktuálne výsledky naznačujú, že ložiská sú v bezchybnom stave.
+Počas viac ako piatich rokov prevádzky čerpadla sa nevyskytol ani jeden prípad poruchy ložiska v dôsledku ich dlhej životnosti a každoročnej profylaktickej údržby.
+To podčiarkuje náročnosť záznau poruchových stavov v priemyselnom prostredí.
 
 \section{Záver}
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
+Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov, mechanických vlastností ložísk a technických noriem vibrodiagnostiky.
 
+Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
+Podarilo sa nám dosiahnuť úsporu dát o viac ako 99,995\%.
+Zistili sme, že nami použitá základaná sada atribútov z časovej domény dosahuje vyššiu presnosť ako sada frekvenčnej domény kvôli menším vzájomným koreláciám.
+Zvýšenie počtu susedov pre k-NN vedie k menšej presnosti modelu.
+Prediktory agregované z trojosového záznamu dosiahli lepšie výsledky v klasifikácii ako prediktory z jednej osi.
+
+Metódy výberu prvkov vo väčšine prípadov sú schopné vybrať skupinu s presnosťou nad horným kvartilom rozdelenia presnosti z každej kombinácie atribútov rovnakej mohutnosti.
+Súčin poradí troch metód na výber atribútov je najlepší v 44\% experimentálnych prípadov nasledovaný metrikou vzájomnej informácie.
+Súčin poradí tiež dosiahol percentil 97,50\% v rozdelení presnosti na trojprvkových množinách prediktorov.
+
+Algoritmus inkrementálneho učenia k-NN na nevyváženej množine údajov trojíc atribútov dosahuje presnosť prinajlepšom 77\% so anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou 100 pozorovaní.
+Presnosť 67\% dosahuje online k-NN model, keď len 10\% pozorovaní zostane označených.
+Porovnateľný model trénovaný v dávkach dosahuje presnosť 88\%.
+
+Analýza zhromaždených dátových súborov potvrdila stacionárnosť spektra signálu pri konštantnej záťaži a dĺžku päť-sekundových časových radov ako vyhovujúce pre extrakciu znakov.
+Potvrdila sa tiež náročnosť získavania pozorovaní porúch častí stroja bez zámerného poškodenia ložísk a vychýlenia hriadeľa.
+
+Ďalším rozšírením diplomovej práce je potvrdenie platnosti výsledkov aj v iných verejne dostupných dátových sadách porúch strojov, napr.
+v CWRU.
+Ďalej je možné použitie rôznych počiatočných základných sád atribútov.
+Súborové metódy inšpirované volebnými systémami možno využiť pri úlohe výberu prvkov.
+Data loger môže byť skombinovaný s modelom klasifikátora a mechanizmom na anotáciu pozorovania buď automaticky v závislosti od celkovej úrovne vibrácií, alebo manuálne počas údržby alebo po neočakávanej poruche.
 \clearpage

### 2024-05-13 thesis/chapters/appendix/B-technical-documentation.tex
Thesis send to feedback

@@
 
-\item \textbf{extraction-pumps.ipynb} - Feature extraction of a complete set of features from Pump datatset in time and frequency domain (TD and FD sets) to CSV files.
+\item \textbf{extraction-pumps.ipynb} - Feature extraction of a complete set of features from Pump dataset in time and frequency domain (TD and FD sets) to CSV files.
 Enable variable \emph{EXTRACT} to proceed with calculation.

### 2024-05-13 thesis/chapters/preliminaries/acknowledgments.tex
Thesis send to feedback

@@
 zo Strojníckej fakulty STU.
-Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Kmeťka a Ing.~Petra Csóku, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
+Cením si ústretovosť Bratislavskej vodárenskej spoločnosti,~a.s., konkrétne Ing.~Petra Csóku a Ing.~Petra Kmeťka, v sprístupnení čerpadiel na merania a súvisiacich podkladov.
 Rovnako ďakujem za ochotu firme VNET,~a.s., a síce Michalovi Országovi a Mgr.~Vladimírovi Kupčovi za odporúčania možných prvkov na merania v klimatizáciach pre dátové centrá a sprístupnenie kompresorov.

### 2024-05-13 thesis/chapters/preliminaries/annotation.tex
Thesis send to feedback

@@
 The similarity of features to a dependent variable describing fault types is assessed by supervised feature selection metrics individually and in the ensemble.
-The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve data rates of the monitoring solution.
-The incremental learning model is compared to its batch counterpart when truthful labels are delayed or missing.
+The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve the data rates of the monitoring solution.
+The incremental learning models are compared to their batch counterparts when truthful labels are delayed or missing.
+An extendible software toolkit of vibrodiagnostics is implemented as a Python package.
 
-Based on the MaFaulDa dataset, classification metrics are evaluated in several scenarios, and lossy compression ratios are expressed.
-The measurement plan and sensor device are designed to enable collection of novel dataset of machinery behavior for compressors and pumps.
-The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.
+Classification metrics are evaluated in scenarios of the MaFaulDa dataset, and lossy compression ratios are expressed.
+Our accelerometer data logger collects a novel dataset of machinery behavior for compressors and pumps in the industrial environment.
+The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but its cause, too.
 \emptypage
@@
 Z vibračných signálov sú odvodené trendové indikátory a tak vytvárajú sumarizujúce číselné atribúty.
-Podobnosť atribútov so závislou premennou popisujúcou typy porúch sa posudzuje metrikami výberu atribútov v učení s učiteľom.
-Metriky sú hodnotené individuálne a súborovo.
+Podobnosť atribútov so závislou premennou popisujúcou typy porúch sa posudzuje individuálne a súborovými metrikami výberu atribútov v učení s učiteľom.
 Presnosť detekcie porúch algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
 Tým sa znížia požiadavky na objem prenosu dát v monitorovacom riešení.
-Model prírastkového učenia sa porovnáva s učením v dávkach, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
+Modely prírastkového učenia sú porované s učením v dávkach, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
+Rozšíriteľná sada funkcií pre vibrodiagnostiku je implementovaná ako balík v jazyku Python.
 
-Na základe súboru údajov MaFaulDa sú klasifikačné metriky vyhodnotené podľa viacerých scenárov a tiež sú vyjdrené stratové kompresné pomery.
-Plán merania a senzorové zariadenie sú navrhnuté na zber nového súboru údajov o správaní sa strojov ako sú kompresory a čerpadlá.
+Metriky kladifikácie sú vyhodnotené v scenároch na dátovej sade MaFaulDa a tiež sú vyjdrené stratové kompresné pomery Náš záznamník údajov akcelerometra zhromažďuje nový súbor údajov o správaní sa strojov pre kompresory a čerpadlá v priemyselnom prostredí.
 Prínos tejto práce spočíva v identifikácii možnosti použitia iba pár veličín na opis nielen prítomnosti poruchy, ale aj jej príčiny.

### 2024-05-13 DP_MiroslavHajek/firmware/bin2tsv.py

@@ -8,7 +8,7 @@ import argparse
 parser = argparse.ArgumentParser()
 parser.add_argument('path', type=str, help='Folder with .bin files')
 # Default resolution in firmware is 4g
-parser.add_argument('res', type=int, help='Resolution in g') 
+parser.add_argument('res', type=int, help='Resolution in g')
 args = parser.parse_args()
 print(f'Path: "{args.path}"')
 

### 2024-05-13 DP_MiroslavHajek/firmware/main/include/pinout.h

@@ -107,7 +107,7 @@
  */
 #define SENSOR_SPI_LENGTH       NUM_OF_FIELDS * FIFO_LENGTH
 /**
- * @brief Number of FIFO buffers that can be pushed to Queue before file write 
+ * @brief Number of FIFO buffers that can be pushed to Queue before file write
  */
 #define QUEUE_LENGTH            16
 
@@ -182,7 +182,7 @@ void sensor_events_disable(stmdev_ctx_t *dev);
 
 
 /**
- * @brief Signal fatal error of system occuring by blinking indicator LED and halting execution
+ * @brief Signal fatal error of system indiacted by blinking LED and halting execution
  *
  * @param[in]   delay   Interval in milliseconds for LED blink
  */
@@ -198,24 +198,24 @@ void panic(int delay);
 /**
  * @brief Configure SD/MMC bus and mount SD memory card to FAT filesystem
  *
- * @param[in]   mount_point     path where the partition will be registered    
+ * @param[in]   mount_point     path where the partition will be registered
  *
  * @return SD/MMC card information structure
  */
 sdmmc_card_t *storage_enable(const char *mount_point);
 
 /**
- * @brief Disable and unmount SD memory card from FAT filesystem 
+ * @brief Disable and unmount SD memory card from FAT filesystem
  *
  * @param[in]   card             SD/MMC card information structure
- * @param[in]   mount_point      path where partition is registered 
+ * @param[in]   mount_point      path where partition is registered
  *
  * @return c
  */
 void storage_disable(sdmmc_card_t *card, const char *mount_point);
 
 /**
- * @brief Get file name for new recording with sequentially higher unused number 
+ * @brief Get file name for new recording with sequentially higher unused number
  *
  * @param[out]  filename   Available file name for new file
  * @param[in]   path       Base path prefix for saving the recording
@@ -227,7 +227,7 @@ void get_recording_filename(char *filename, const char *path);
 
 /**
  * @defgroup button Button
- * @brief Configuation of the recording button
+ * @brief Configuration of the recording button
  *  @{
  */
 
@@ -249,7 +249,7 @@ void switch_disable(void);
 
 /**
  * @defgroup led LED
- * @brief Configuation of the indicator LED light
+ * @brief Configuration of the indicator LED light
  *  @{
  */
 

### 2024-05-13 DP_MiroslavHajek/firmware/main/src/iis3dwb.c

@@ -421,12 +421,12 @@ int32_t iis3dwb_xl_axis_selection_get(stmdev_ctx_t *ctx,
 {
   iis3dwb_ctrl4_c_t ctrl4_c;
   iis3dwb_ctrl6_c_t ctrl6_c;
- 
+
   *val = IIS3DWB_ENABLE_ALL;
 
   int32_t ret = iis3dwb_read_reg(ctx, IIS3DWB_CTRL4_C, (uint8_t *)&ctrl4_c, 1);
   if (ret != 0) { return ret; }
-  
+
   ret = iis3dwb_read_reg(ctx, IIS3DWB_CTRL6_C, (uint8_t *)&ctrl6_c, 1);
   if (ret != 0) { return ret; }
 
@@ -555,7 +555,7 @@ int32_t iis3dwb_temp_flag_data_ready_get(stmdev_ctx_t *ctx,
 }
 
 /**
-  * @brief  Enables the accelerometer user offset correction block, can be enabled 
+  * @brief  Enables the accelerometer user offset correction block, can be enabled
   * by setting the USR_OFF_ON_OUT bit of the CTRL7_C register.[set]
   *
   * @param  ctx    Read / write interface definitions.(ptr)
@@ -579,7 +579,7 @@ int32_t iis3dwb_usr_offset_block_set(stmdev_ctx_t *ctx, uint8_t val)
 }
 
 /**
-  * @brief  Enables the accelerometer user offset correction block, can be enabled 
+  * @brief  Enables the accelerometer user offset correction block, can be enabled
   * by setting the USR_OFF_ON_OUT bit of the CTRL7_C register.[get]
   *
   * @param  ctx    Read / write interface definitions.(ptr)
@@ -1415,10 +1415,10 @@ int32_t iis3dwb_xl_filt_path_on_out_get(stmdev_ctx_t *ctx,
   iis3dwb_ctrl8_xl_t ctrl8_xl;
 
   *val = IIS3DWB_HP_REF_MODE;
-  
+
   int32_t ret = iis3dwb_read_reg(ctx, IIS3DWB_CTRL1_XL, (uint8_t *)&ctrl1_xl, 1);
   if (ret != 0) { return ret; }
-  
+
[…]

### 2024-05-13 DP_MiroslavHajek/firmware/main/src/main.c

@@ -54,7 +54,7 @@ SemaphoreHandle_t file_mutex;
  */
 bool is_recording = false;
 /**
- * @brief Last seen accelerometer timestamp 
+ * @brief Last seen accelerometer timestamp
  */
 int32_t sensor_timestamp = 0;
 

### 2024-05-13 DP_MiroslavHajek/firmware/main/src/storage.c

@@ -35,20 +35,20 @@ sdmmc_card_t *storage_enable(const char *mount_point)
     return card;
 }
 
-void storage_disable(sdmmc_card_t *card, const char *mount_point) 
+void storage_disable(sdmmc_card_t *card, const char *mount_point)
 {
     esp_vfs_fat_sdcard_unmount(mount_point, card);
 }
 
-static unsigned long get_new_recording_name(const char *path) 
+static unsigned long get_new_recording_name(const char *path)
 {
     uint32_t seq = 0;
     char filename[MAX_FILENAME];
 
     DIR *folder = opendir(path);        // Needs trailing slash
-    if (folder == NULL) 
+    if (folder == NULL)
         return seq;
-    
+
     struct dirent *entry;
 
     while ((entry = readdir(folder)) != NULL) {
@@ -63,7 +63,7 @@ static unsigned long get_new_recording_name(const char *path)
         if (name > seq)
             seq = name;
     }
-        
+
     closedir(folder);
     return seq + 1;
 }

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/extraction.py

@@ -36,7 +36,7 @@ def energy(x: np.array) -> float:
 
     :param x: input signal
 
-    :return: energy of the signal 
+    :return: energy of the signal
     """
     return np.sum(x ** 2)
 
@@ -46,7 +46,7 @@ def negentropy(x: np.array) -> float:
 
     :param x: input signal
 
-    :return: negentropy of the signal 
+    :return: negentropy of the signal
     """
     if len(x) == 0:
         return np.nan
@@ -59,7 +59,7 @@ def signal_to_noise(x: np.array) -> float:
 
     :param x: input signal
 
-    :return: SNR of the signal 
+    :return: SNR of the signal
     """
     m = np.mean(x)
     sd = np.std(x)
@@ -67,7 +67,7 @@ def signal_to_noise(x: np.array) -> float:
 
 
 def spectral_roll_off_frequency(f: np.array, pxx: np.array, percentage: float) -> float:
-    """Calculate roll-off frequency. Cumulative sum of energy in spectral bins 
+    """Calculate roll-off frequency. Cumulative sum of energy in spectral bins
     below roll-off frequency is percentage of total energy
 
     :param f: array of frequency bins
@@ -108,7 +108,7 @@ def envelope_signal(f: np.array, pxx: np.array) -> np.array:
     :param f: array of frequency bins
     :param pxx: array of amplitudes at frequency bins
 
-    :return: envelope of the amplitudes 
+    :return: envelope of the amplitudes
     """
     # peaks = mms_peak_finder(pxx)
     peaks, _ = find_peaks(pxx)
@@ -130,7 +130,7 @@ def spectral_transform(x: pd.Series, window: int, fs: int) -> Tuple[np.array, np
     :param window: length of Hann FFT window
     :param fs: sampling frequency in Hz of the input signal
 
-    :return: envelope of the amplitudes 
+    :return: envelope of the amplitudes
     """
     overlap = 0.5
     step = int(window * overlap)
@@ -195,7 +195,7 @@ def frequency_features_calc(
     :param fs: sampling frequency in Hz of the time series
     :param window: length of FFT window
 
-    :return: list of frequency-domain features in pairs of feature name 
+    :return: list of frequency-domain features in pairs of feature name
         with column prefix and its value
     """
     f, pxx = spectral_transform(df[col], window, fs)
@@ -224,8 +224,8 @@ def wavelet_features_calc(
             fs: int,
             window: int
[…]

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/mafaulda.py

@@ -31,7 +31,7 @@ BEARING_B_COLUMNS = ['bx', 'by', 'bz']
 BEARINGS_COLUMNS = BEARING_A_COLUMNS + BEARING_B_COLUMNS
 COLUMNS = ['tachometer'] + BEARINGS_COLUMNS + ['mic']
 LABEL_COLUMNS = ['fault', 'severity', 'rpm']
-"""Metadata columns extracted from file path witin dataset
+"""Metadata columns extracted from file path within dataset
 """
 
 
@@ -44,7 +44,7 @@ BEARINGS = {
     'bsf_factor': 1.8710,
     'ftf_factor': 0.3750
 }
-"""Coeficients for bearing characteristic frequencies
+"""Coefficients for bearing characteristic frequencies
 """
 
 
@@ -150,7 +150,7 @@ def lowpass_filter_extract(
             dataframes: List[pd.DataFrame],
             columns: List[str]
         ) -> List[pd.DataFrame]:
-    """Apply low-pass to columns in multiple data frames
+    """Apply low-pass filter to columns in multiple data frames
 
     :param data frames: list of input datafrmaes to which filter is applied to
     :param columns: columns that filter is applied to
@@ -354,7 +354,7 @@ def load_source(domain: str, row: dict, train_size: float = 0.8) -> tuple:
 
     :param domain: complete feature set ("TD", "FD")
     :param row: parameters for data filtering, e.g.: {"placement": "A", online: False}
-    :param train_size: ratio of traing set to testing set
+    :param train_size: ratio of training set to testing set
 
     :return: X_train, X_test, Y_train, Y_test
     """

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/models.py

@@ -84,7 +84,7 @@ def kfold_accuracy(
             Y: pd.Series,
             k_neighbors: int,
             kfolds: int,
-            model_name: str = 'knn', 
+            model_name: str = 'knn',
             power_transform: bool = True,
             knn_metric='euclidean'
         ) -> Dict[str, float]:
@@ -95,10 +95,10 @@ def kfold_accuracy(
     :param X: data frame of predictor features
     :param Y: column of labels
     :param k_neighbors: number of neighbours for k-nearest neighbours model
-    :param model_name: name of the machine learning model to evaluate. 
+    :param model_name: name of the machine learning model to evaluate.
         Options are: "knn", "lda", "bayes", "svm"
     :param kfolds: number of splits for k-fold cross-validation
-    :param power_transform: apply power transform of features in preprocessing instead 
+    :param power_transform: apply power transform of features in preprocessing instead
         of normalization
     :param knn_metric: distance metric name for k-nearest neighbours model
 
@@ -129,7 +129,7 @@ def kfold_accuracy(
 
         x_train[x_train.columns] = transform.fit_transform(x_train)
         x_test[x_test.columns] = transform.transform(x_test)
-    
+
         # Train k-NN model on all features
         if model_name == 'knn':
             model = KNeighborsClassifier(n_neighbors=k_neighbors, metric=knn_metric)
@@ -146,7 +146,7 @@ def kfold_accuracy(
 
         round_train_acc.append(skmetrics.accuracy_score(y_train, y_predict_train))
         round_test_acc.append(skmetrics.accuracy_score(y_test, y_predict_test))
-    
+
     return {
         'train': np.array(round_train_acc).mean(),
         'test': np.array(round_test_acc).mean()
@@ -166,13 +166,13 @@ def all_features(
 
     :param X: data frame of predictor features
     :param Y: column of labels
-    :param model_name: name of the machine learning model to evaluate. 
+    :param model_name: name of the machine learning model to evaluate.
         Options are: "knn", "lda", "bayes", "svm"
-    :param power_transform: apply power transform of features in preprocessing instead 
+    :param power_transform: apply power transform of features in preprocessing instead
         of normalization
     :param k_neighbors: number of neighbours for k-nearest neighbours model
     :param kfolds: number of splits for k-fold cross-validation
-    
+
     :return: training and testing accuracy for each value of k-neighbours
     """
     train_accuracy = []
@@ -203,7 +203,7 @@ def feature_combinations(
             model: str,
             power_transform: bool = False
[…]

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/pumps.py

@@ -19,7 +19,7 @@ SAMPLING_RATE = 26866
 BEARINGS_COLUMNS = ['x', 'y', 'z']
 COLUMNS = ['t'] +  BEARINGS_COLUMNS
 LABEL_COLUMNS = ['date', 'device', 'position']
-"""Metadata columns extracted from file path witin dataset
+"""Metadata columns extracted from file path within dataset
 """
 G_CONSTANT = 9.80665
 
@@ -156,7 +156,7 @@ def get_classes(df: pd.DataFrame, labels: Dict[str, dict], keep: bool = False) -
 
 
 def assign_labels(df: pd.DataFrame) -> pd.DataFrame:
-    """Assign labels to fault types into "label" column based on meaurement placement
+    """Assign labels to fault types into "label" column based on measurement placement
 
     :param df: data frame after feature extraction with column "fault"
 

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/ranking.py

@@ -50,7 +50,7 @@ def silhouette_scores(
             pc: int
         ) -> Dict[str, float]:
     """Calculate silhouette score of data points after normalization
-    of training and testing set with and without the pricipal components analysis
+    of training and testing set with and without the principal components analysis
 
     :param X_train: data points of the training set
     :param X_test: data points of the testing set
@@ -66,7 +66,7 @@ def silhouette_scores(
 
     scaler = MinMaxScaler()
     X_train[X_train.columns] = scaler.fit_transform(X_train)
-    X_test[X_test.columns] = scaler.transform(X_test)    
+    X_test[X_test.columns] = scaler.transform(X_test)
 
     model = PCA(n_components=pc).fit(X_train)
     X_train_pca = pd.DataFrame(model.transform(X_train))
@@ -81,7 +81,7 @@ def silhouette_scores(
 
 
 def pca_explained_variances(X_train: pd.DataFrame, pc: int) -> Dict[str, float]:
-    """Explained variances of the principal components 
+    """Explained variances of the principal components
 
     :param X_train: data points of the training set
     :param pc: number of principal components
@@ -90,9 +90,9 @@ def pca_explained_variances(X_train: pd.DataFrame, pc: int) -> Dict[str, float]:
     """
     scaler = MinMaxScaler()
     X_train[X_train.columns] = scaler.fit_transform(X_train)
-    model = PCA(n_components=pc).fit(X_train)    
+    model = PCA(n_components=pc).fit(X_train)
     return {
-        f'PC{pc}': var 
+        f'PC{pc}': var
         for pc, var in enumerate(model.explained_variance_ratio_, start=1)
     }
 
@@ -113,7 +113,7 @@ def batch_feature_ranking(
     """
     metric_ranks = pd.DataFrame()
     METRICS_OFFLINE = {
-        'corr': selection.corr_classif, 
+        'corr': selection.corr_classif,
         'f_stat': f_classif,
         'mi': mutual_info_classif
     }
@@ -141,10 +141,10 @@ def batch_feature_ranking(
                 .sort_values(by='score', ascending=False)
             )
             metric_ranks[metric_name] = leaderboard
-        
+
         ranks = metric_ranks.rank(axis='rows', method='first', ascending=False)
         return ranks.apply(gmean, axis=1).sort_values().to_frame(name='rank')
-    
+
 
 def online_feature_ranking(
             X: pd.DataFrame,
@@ -161,7 +161,7 @@ def online_feature_ranking(
     :return: leaderboard of the features
     """
[…]

### 2024-05-13 DP_MiroslavHajek/vibrodiagnostics/visualize.py

@@ -30,7 +30,7 @@ Titles for signal source domain abbreviation
 def evolution_of_severity_levels(df: pd.DataFrame):
     """Line chart of the amount of observations at relative severity levels
 
-    :param df: data frame with sorted "severity" level column 
+    :param df: data frame with sorted "severity" level column
     """
     fig, ax = plt.subplots(1, 1, figsize=(10, 5))
     ax.plot(np.arange(0, len(df)), df['severity_level'], color='red')
@@ -82,17 +82,17 @@ def scatter_features_3d(
         boundary: bool = False,
         model_name: str = 'knn',
         power_transform: bool = False):
-    """Scatter plot of data points in 3D feature space shown 
-    in planar cross-sections through coordinate axes 
+    """Scatter plot of data points in 3D feature space shown
+    in planar cross-sections through coordinate axes
 
     :param X: data frame of features
     :param Y: labels of observations
     :param features: names of three features to display
     :param size: figure size
     :param boundary: show decision boundary for k-NN model with 5 neighbours
-    :param model_name: name of the machine learning model to evaluate. 
+    :param model_name: name of the machine learning model to evaluate.
         Options are: "knn", "lda", "bayes", "svm"
-    :param power_transform: apply power transform of features in preprocessing instead 
+    :param power_transform: apply power transform of features in preprocessing instead
         of normalization
     """
 
@@ -115,7 +115,7 @@ def scatter_features_3d(
         a, b = dims
         columns = [features[a], features[b]]
         p, q = X[columns[0]], X[columns[1]]
- 
+
         if boundary:
             h = .02
             model = models.model_boundaries(X[columns], Y.cat.codes, model_name=model_name)
@@ -165,9 +165,9 @@ def scatter_features_3d_plot(
     :param features: names of three features to display
     :param size: figure size
     :param boundary: show decision boundary for k-NN model with 5 neighbours
-    :param model_name: name of the machine learning model to evaluate. 
+    :param model_name: name of the machine learning model to evaluate.
         Options are: "knn", "lda", "bayes", "svm"
-    :param power_transform: apply power transform of features in preprocessing instead 
+    :param power_transform: apply power transform of features in preprocessing instead
         of normalization
     """
 
[…]

### 2024-05-14 thesis/chapters/03-design.tex
Move Resume to main thesis

@@
 \chapter{Design} \label{chapter:design}
-During the design stage, we set out research questions and detail the steps of the machine learning pipeline for diagnosing fault types in the MaFaulDa dataset.
+During the design stage, we set out research questions and explain the machine learning pipeline for machinery defects diagnostics in the MaFaulDa dataset.
 The explanatory analysis of MaFaulDa hints at the underlying dependencies within feature sets that can degrade the machine learning model of choice.
-We apply the methodology for vibration measurements from standards to the data logger requirements and data acquisition from industrial equipment.
+We apply the methodology for vibration measurements found in technical standards to requirements for the data logger and data acquisition procedures for the industrial equipment.
 
@@
 The thesis aims to provide answers to five research questions.
-The main focus is on making data flow more efficient in an industrial sensor network that monitors rotating machines.
+The main focus is on making data flow more efficient in an industrial sensor network that could monitor rotating machines.
 The \textbf{research questions} are:
@@
 	\item How do the vibration signals collected on the industrial machinery behave?
-	\item How can machinery faults be identified over time from collected events?
+	\item How can machinery faults be identified incrementally from collected events?
 \end{enumerate}
@@
     \item Statistically and visually describe vibration signals from the Machinery fault database (MauFaulDa).
-    \item Establish a list of conditions that will be investigated later in the experimental setting.
+    \item Establish a list of conditions that will be investigated in the experiments.
     \item Prepare the dataset to be used in conjunction with machine learning models namely by identifying labels and balancing classes.
-    \item Find the best subsets of features in the time and frequency domain with previously analyzed feature extraction and selection methods.
-    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbor algorithm.
+    \item Find the best subsets of features in the time and frequency domain using previously analyzed feature extraction and selection methods.
+    \item Evaluate the performance of models described in the diagnostics section with a significant focus on the k-nearest neighbours algorithm.
     \item Acquire measurements of vibrations from machines in the real environment to form a novel dataset of machinery behavior.
-    \item Develop hardware and implement its firmware to obtain such measurements of the quality demanded by vibrodiagnostics standards.
+    \item Develop hardware for a sensor unit and implement its firmware to obtain vibration measurements with the quality demanded by vibrodiagnostics standards.
 \end{todolist}
@@
 \section{Machine learning pipeline}
-The similar data processing framework we adopt can be found elsewhere in the literature.
+We adopt a similar data processing framework found also elsewhere in the literature.
 It generally consists of signal acquisition, feature extraction, dimensionality reduction, and pattern recognition or fault detection~\cite{wang_bearing_2015}.
 However, the realization of the steps must be decomposed closer to suit the dataset structure, desired processing goals, and investigated parameters.
-The entire design of the data flow can be seen in Fig.~\ref{fig:design:ml-pipeline}.
+The entire design of the data flow is in Figure~\ref{fig:design:ml-pipeline}.
 
@@
 
-\textbf{In preprocessing step}, the signals stored in columns of CSV files within the MaFaulDa ZIP archive are first associated with metadata according to the file's path in the directory structure.
+The signals are in columns of CSV files within the MaFaulDa ZIP archive.
+\textbf{In preprocessing step}, they are first associated with metadata according to their file's path in the directory structure.
 The hierarchically topmost folder describes the simulated defect.
 There is directory for \emph{normal}, \emph{imbalance}, \emph{horizontal-misalignment}, \emph{vertical-misalignment}, \emph{overhang} (outer bearing), \emph{underhang} (inner bearing).
-Each bearing has an additional folder layer for dividing bearing faults: \emph{ball\_fault}, \emph{cage\_fault}, \emph{outer\_race}.
-Each fault category except the normal class contains various fault severities with units of grams or millimeters.
-The severities in turn consist of individual files with different rpm speeds.
+Each bearing has an additional folder layer for dividing up bearing faults: \emph{ball\_fault}, \emph{cage\_fault}, \emph{outer\_race}.
+Fault categories, except the normal class, contain various fault severities marked with units of grams or millimeters.
+Severities, in turn, consist of individual files with different rpm speeds.
 
-We neglect the \textbf{acceleration sensor orientation}, therefore, the labels for shaft misalignment in vertical and horizontal directions are merged into the same group.
-In the end, that leaves \textbf{6 types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
+The labels for shaft misalignment in vertical and horizontal directions are merged into the same group because we neglect the \textbf{acceleration sensor orientation}.
+In the end, that leaves \textbf{six types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
 
 Depending on the \textbf{chosen bearing position}, only time series associated with that bearing are retained because the standards demand each bearing be assessed separately.
-Fault classification concerns bearing in direct contact and shaft mechanically passing through it.
+Fault classification concerns with bearing in direct contact and shaft mechanically passing through it.
 
@@
 \textbf{File description} is the triplet of \textbf{fault}, \textbf{severity}, and \textbf{rpm}.
-
-After labeling we insert a step to split the time series into parts when the duration is long enough to introduce more observations artificially.
+After labeling, we insert a step to split the time series into parts when the duration is long enough to introduce more observations artificially.
 This assumption for splitting is not met for MaFaulDa because, for the desired frequency resolution for features of close to 1~Hz, we need a window size of 32768 samples.
-Variation reduction in spectral estimation brings the necessity to average at least 12 overlapping windows.
-The full length of 5 seconds provides 15 whole overlapping windows.
+Variation reduction in spectral estimation necessitates averaging at least twelve overlapping windows.
+The full length of five seconds provides fifteen complete windows.
 
@@
 The preprocessed signal from each axis of accelerometer is packed up to \textbf{two base feature sets} in time domain (TD) and frequency domain (FD).
-The feature extraction formulas are is identical with formulas presented in the section \ref{section:feature-extraction} of analysis chapter.
-The frequency transform is Welch's method averaging FFT vectors from 32768 samples after Hann windowing and 50\% overlap.
+The feature extraction formulas are identical with formulas presented in the section \ref{section:feature-extraction} of analysis chapter.
+The frequency transform is Welch's method averaging of FFT vectors from 32768 samples after Hann windowing and 50\% overlap.
 The feature sets are:
@@
 
-The four conditions are applied in the instance of the pipeline to filter observations with calculated features to create \textbf{24 scenarios}:
+The four conditions are applied in each instance of the pipeline to filter observations with calculated features to create \textbf{24 scenarios}:
 \begin{itemize}
@@
 \item \textbf{Feature domain} - the set of extracted features as an input to downstream models is changed either to TD or FD set,
-\item \textbf{Accelerometer axis} - Either one principal direction of motion or all three dimensions is aggregated under same feature name (1 or 3),
+\item \textbf{Accelerometer axis} - Either one principal direction of motion or all three dimensions are aggregated under same feature name (1 or 3),
 \item \textbf{High severity faults} - to more precisely simulate fault frequencies found in real environment the low severity defects can be considered as normal operation (Yes or No).

### 2024-05-14 thesis/chapters/04-implementation.tex
Move Resume to main thesis

@@
 \chapter{Implementation} \label{chapter:implementation}
-The tools implemented include exploration of datasets using statistical overviews and visualizations, experiments of feature selection which involve machine learning pipeline, and firmware for data logger's hardware.
+The tools we implement include the exploration of datasets using statistical overviews and visualizations, feature selection experiments that involve a machine learning pipeline, and firmware for the data logger's hardware.
 
@@
 Procedures in firmware are described in Appendix~\ref{appendix:technical-docs}.
-The hardware (Fig.~\ref{fig:hw-data-logger}) was built by the thesis consultant based on the complete specification supplied by the author.
+The hardware (Fig.~\ref{fig:hw-data-logger}) was built by the thesis consultant based on the detailed specification supplied by the author.
 
@@
 
-Another impediment presented the slow string formatting with \emph{printf} family of functions during the accelerometer sampling.
+Slow string formatting with \emph{printf} family of functions during the accelerometer sampling presented another impediment.
 The readings cannot be written to TSV directly because the real-time (RT) deadline is not met due to the high sampling rate.
-It is true even if the queue is utilized and the processing takes place in another task.
-The binary files from the SD card are converted in bulk to TSV with custom Python command line script \verb|bin2tsv.py|.
+This is true even if the queue is utilized and the processing takes place in another task.
+The binary files from the SD card are converted in bulk to TSV with custom Python script \verb|bin2tsv.py|.
 
 During debugging, the pin was set to change the output level immediately before the one buffer started file write and after its completion.
-The scopes in Figure~\ref{fig:implementation:file-write} show the time the write took for binary compared to the TSV format.
-In writing to TSV format, the relation of numbers of already processed buffers $x$ to those left to process $y$ is: $y = 3.7x$.
-It is a monotonically increasing function, so the system would eventually overrun any sized assigned queue.
+Waveforms in Figure~\ref{fig:implementation:file-write} show the time it took to write in binary format compared to the TSV format.
+The relation of already processed buffers $x$ to those left to process $y$ is $y = 3.7x$ for TSV format.
+It is a monotonically increasing function, so the system would eventually overrun queue of any size.
 

### 2024-05-14 thesis/chapters/05-evaluation.tex
Move Resume to main thesis

@@
 A significant change in the data stream occurs after 294 out of 1438 observations (or after 737 for high severity faults) when all 49 (or 737) normal conditions are consumed in the training process.
-Counters of other faults show that predictions are skewed towards more represented imbalance and misalignment.
+Counters of other faults show that predictions are skewed towards more represented classes of imbalance and misalignment.
 The uneven evolution of categories in a stream impacts the development of accuracy in the remaining experiments.
@@
     \end{subfigure} 
-    \caption{Omission of labels during incremental learning with tumbing window of length 10 and gaps of size 0, 10, and 50 samples}
+    \caption{Omission of labels during incremental learning with tumbling window of length 10 and gaps of size 0, 10, and 50 samples}
     \label{fig:evaluation:label-skips-online}
@@
         \includegraphics[width=\textwidth]{assets/results/defects/motors-dB.png}
-        \caption{Pumps}
+        \caption{Motors (dB)}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/defects/pumps.png}
-        \caption{Motors}
+        \caption{Pumps}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{assets/results/defects/pumps-dB.png}
-        \caption{Pumps dB}
+        \caption{Pumps (dB)}
     \end{subfigure}
@@
 Figure~\ref{fig:evaluation:bearing-freq} identifies harmonics of rotational speed and BPFO frequency in every machine and BPFI for M2-2.
-It can be assumed that those frequencies will be the reason for their damage in the future.
+It can be assumed that those frequencies will be the reason for damage in the future.
 The absolute acceleration is minuscule in current frequency bands and year-long sensor log of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).

### 2024-05-14 thesis/chapters/06-conclusion.tex
Move Resume to main thesis

@@
 Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are computed in supervised learning scenarios.
-The features are squished from multiple dimensions using the Euclidian norm.
+The features are squished from multiple dimensions using the Euclidean norm.
 Lossy compression ratios attained are 2381:1 for all features and 25000:1 for six features from the MaFaulDa dataset.
@@
 The k-nearest neighbour classifier ascertains their relative fault detection power by five-fold cross-validation.
-The experiments for k-NN model evaluation include complete feature sets with one for each domain, the exhaustively enumerated feature subset combinations, and features subset chosen by filtering feature selection methods.
+The experiments for k-NN model evaluation include complete feature sets with one for each domain, the exhaustively enumerated feature subset combinations, and feature subsets chosen by filtering feature selection methods.
 
-We found that the time-domain features reach higher accuracies than the frequency-domain set because of less intercorrelations.
-Increase in the number of neighbours for k-NN used on complete sets, the smaller the model accuracy.
-Above the k-value of thirteen, the trend for complete feature sets flattens out gradually.
+We found that the chosen time-domain features have reached higher accuracies than the frequency-domain set because of fewer intercorrelations.
+An increase in the number of neighbours for k-NN used on complete sets lessens the model accuracy because class boundaries overlap and are relatively noisy.
+Above the k-value of thirteen, the trend for complete feature sets of accuracy decrease flattens out gradually.
 Predictors aggregated from tri-axis recording performed better in classification than those from one axis.
@@
 The k-NN accuracy with different feature subset combinations pulled out of the complete sets has a standard deviation of 7\%, and it is 10\% within IQR.
-Within such range, the feature selection methods can pick, in most cases, a group with accuracy above the upper quartile of accuracy distribution of every attribute combination with the same cardinality.
+The feature selection methods can pick, in most cases, a group with accuracy above the upper quartile of accuracy distribution of every attribute combination with the same cardinality.
 Training k-NN on three principal components produced worse accuracy than filtering feature selection.
@@
 In the slight majority of 44\% of 216 dataset alterations, the rank product found the best-performing attributes closely followed by mutual information.
-The rank product also reaches the 97.50\% percentile in the accuracy distribution in the same-sized sets.
-Mutual information has a better distribution percentile of 2.84\% from rank product \textbf{(RQ3)}.
+The rank product also reaches the 97.50\% percentile in the accuracy distribution of the same-sized sets.
+Mutual information has a better distribution percentile by 2.84\% than the rank product \textbf{(RQ3)}.
 
-The number of features has a direct proportionality effect accuracy but at most 6\% increase is observed in moving from two to three features.
+The number of features has a direct proportionality effect accuracy but at most 6\% increase is observed while moving from two to three features.
 The absolute best predictor triplets for MaFaulDa are in TD (accuracy of 85.47\%): zero-crossing rate, peak-to-peak, skewness, and in FD (accuracy of 87.52\%): spectral centroid, roll-off frequency, and entropy \textbf{(RQ3)}.
@@
 
-Collected dataset analysis confirmed the stationarity of the signal spectrum of the signal and length of five-second time series as satisfactory for feature extraction.
-The dataset serves as a practical demonstartion of labeling potentialy future faults from bearing defect frequency amplitudes.
+Collected dataset analysis confirmed the stationarity of the signal spectrum and the five-second long time series as satisfactory for feature extraction.
+The dataset serves as a practical demonstration of labeling potentially future faults from bearing defect frequency amplitudes.
 It also proved the immense difficulty of obtaining observations of faulty machinery parts in the field without purposefully damaging bearings and offsetting the shaft \textbf{(RQ4)}.
@@
 
-\textbf{Future work} can extend various aspects and additional questions arising from the experiments in the thesis.
+\textbf{Future work} can extend various aspects and answer additional questions arising from the experiments in the thesis.
 The natural extension is to confirm that the results hold in other publicly available datasets of machinery faults, e.g.
 in CWRU.
-The other alteration is to use more different starting base feature sets.
+The other alteration is to use more and different starting base feature sets.
 Harmonic frequencies or wavelet coefficients can generate predictors that could be further reduced to the smallest possible subsets.
@@
 Ensemble strategies inspired by classical election systems may be utilized in the task of feature selection.
-Different feasible types of classifiers for online learning could be compared to k-nearest neighbours, e.g.
+Different types of classifiers for online learning could be compared to k-nearest neighbours, e.g.
 Hoeffding tree.
@@
 
-The strategic aim would be to connect sensors on a large scale on multiple test rigs to train individual models on each bearing and combine them in a federative learning approach.
-Of course, vibration monitoring can be employed in other diagnostic tasks with no direct expert knowledge, such as train wheel or rail degradation due to wear and tear.
+The strategic aim would be to connect sensors on a large scale on multiple test rigs to train individual models on each bearing and combine them in, for example, a federative learning approach.
+Of course, vibration monitoring can be employed in other diagnostic tasks without direct expert knowledge, such as train wheel or rail degradation due to wear and tear.

### 2024-05-14 thesis/chapters/07-resume.tex
Move Resume to main thesis

--- 2024-05-13 thesis/chapters/appendix/A-resume.tex
@@
-\thispagestyle{empty}
 \chapter{Resumé}
-\pagenumbering{arabic}
-\renewcommand*{\thepage}{A-\arabic{page}}
 
@@
 Najrozšírenejšími používanými atribútmi sú štatistické miery centrálneho momentu: priemer, rozptyl, štandardná odchýlka, šikmosť a špicatosť.
-Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička, maximum, absolútnu zmenu amplitúdy (AAC), a početnosť prechodov nulou.
+Charakteristiky amplitúdy zahŕňajú kvadratický priemer (rms), vzdialenosť špička-špička, maximum, absolútnu zmenu amplitúdy (aac), a početnosť prechodov nulou.
 Ostatné významné atribúty časovej oblasti sú odvodené ako pomery a sú nim: faktor výkyvu, faktor rozpätia, faktor impulzu a faktor tvaru.
 
-V spektrálnej oblasti môžeme získať obvyklé štatistické vlastnosti distribúcie, ktorými sú spektrálne ťažisko, šikmosť a špicatosť.
-Okrem toho sa extrahujú roll-on a roll-off, fundamentálna frekvencia, entropia, negentropia, vzájomná korelácia spektier, pomer signálu k šum, energia vo frekvenčných pásmach.
+Vo frekvenčnej oblasti sú získané obvyklé štatistické vlastnosti distribúcie, ktorými sú spektrálne ťažisko, šikmosť a špicatosť.
+Okrem toho sa extrahujú frekvencie roll-on a roll-off, fundamentálna frekvencia, entropia, negentropia, vzájomná korelácia spektier, pomer signálu k šum, a energia vo frekvenčných pásmach.
 
@@
 Výber ich optimálnej podmnožiny je NP-ťažký kombinatorický problém.
-Kroky všeobecného postup pri výbere atribútov metódou filtrovania sú generovanie podmnožín, vyhodnotenie podmnožín, ukončovacie kritérium hľadania, a validácia.
+Kroky všeobecného postupu pri výbere atribútov metódou filtrovania sú generovanie podmnožín, vyhodnotenie podmnožín, ukončovacie kritérium hľadania, a validácia.
 
-Hodnotenie relevancie atribútov sú založené na skórovaní podobnosti s predikovanou premennou.
+Hodnotenie relevancie atribútov je založené na skórovaní podobnosti s predikovanou premennou.
 Často používané spôsoby zoraďovania dôležitosti atribútov sú prah rozptylu, koeficienty korelácie, ANOVA F štatistika, a vzájomná informácia.
@@
 \section{Diagnostické prístupy}
-Identifikácia porúch v rotujúcich strojoch je binárny alebo viac triedny klasifikačný problém, ktorý pracuje na princípe učenia čiastočne s učiteľom, pretože označenia pre degradované stavy stroja sú v praxi zriedkavé.
+Identifikácia porúch rotujúcich strojoch je binárny alebo viac-triedny klasifikačný problém, ktorý pracuje na princípe učenia čiastočne s učiteľom, pretože označenia pre degradované stavy stroja sú v praxi zriedkavé.
 Ciele automatizácie monitorovania možno rozdeliť na detekciu anomálií a rozpoznanie typu poruchy.
@@
 
-Presná viac triedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
+Presná viac-triedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií.
 Algoritmus k-najbližších susedov (k-NN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti.
@@
 
-Nasleduje rozdelenie časových radov na menšie rovnako veľké časti, ak je ich trvanie dlhšie ako dvanásť okien s rozlíšením okolo 1 Hz, to však neplatí pre MaFaulDa.
+Nasleduje rozdelenie časových radov na menšie časti, ak je ich trvanie dlhšie ako dvanásť okien a majú rozlíšenie okolo 1 Hz, čo však neplatí pre MaFaulDa.
 Jednosmerná zložka a frekvencie nad 10 kHz sú odfiltrované z pôvodných signálov vibrácií.
-Pôvodne priradené triedy porúch sú pri niektorých experimentoch vymenené za bezporuchový stav, keď je zaznamenaná závažnosť poruchy nízka.
+Pôvodne priradené triedy porúch sú pri niektorých experimentoch vymenené za bezporuchový stav, keď je závažnosť poruchy nízka.
 
 Z predspracovaného signálu v každej osi akcelerometra sú vypočítané dve základné sady atribútov v časovej (TD) a frekvenčnej doméne (FD).
-Na filtrovanie pozorovaní sa používajú štyri podmienky: umiestnenie ložiska (A alebo B), doména základnej sady (TD alebo FD) atribútov, osi akcelerometra použité na výpočet atribútu (jedna alebo tri), ponechanie označení iba pre poruchy vyššej závažnosti (áno alebo nie).
+Na filtrovanie pozorovaní sa používajú štyri podmienky: umiestnenie ložiska (A alebo B), doména základnej sady atribútov (TD alebo FD), osi akcelerometra použité na výpočet atribútu (jedna alebo tri), ponechanie označení iba pre poruchy vyššej závažnosti (áno alebo nie).
 Uvedené podmienky vytvárajú dohromady 24 scenárov.
@@
 Úspešnosť klasifikácie porúch strojov sa vyhodnocuje po normalizácii atribútov, vyvážení mohutnosti tried a päťnásobnej krížovej validácii na klasifikátore k-najbližších susedov s euklidovskou metrikou vzdialenosti.
-Presnosti sa porovnávajú pre rôzne hodnoty hyperparametrov k-susedov a veľkosti podmnožiny atribútov podľa uvedených scenárov.
+Presnosti sa porovnávajú pre rôzne hodnoty hyperparametrov k-susedov a veľkostí podmnožiny atribútov podľa uvedených scenárov.
 
@@
 Metodiku uplatnenú na súbore údajov MaFaulDa z laboratórneho prostredia aplikujeme na vibrácie z priemyslu.
-Pri monitorovaní je zužitkovaný postup podľa technických noriem.
+Pri monitorovaní je zužitkovaný postup z technických noriem.
 Ten zahŕňa výber strojov určených na monitorovanie, identifikáciu pozícií na meranie, predbežné merania a vývoj senzorovej jednotky.
@@
 Na zber údajov boli vyčlenené dva špirálové kompresory ako súčasť klimatizačných jednotiek pre dátové centrum a tri čerpadlá s troma elektromotormi v prečerpávacej stanici na pitnú vodu.
-Merania sú uskutočnené vlastným data loggerom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu s mesačným rozostupom.
-Ako senzor vibrácii je použitý MEMS akcelerometer IIS3DWB.
+Merania sú uskutočnené s mesačným rozostupom vlastným data loggerom na báze vývojovej dosky ESP32-PoE-ISO so slotom na SD kartu.
+Ako senzor vibrácii je použitý MEMS akcelerometer ST IIS3DWB.
 Vyznačuje sa vysokou šírkou pásma až 6.3 kHz, nízkym šumom, a vysokou výstupným dátovým tokom 26.7 kHz cez SPI zbernicu.
@@
 Po každom zázname je akcelerometer znova pripevnený na meraciu pozíciu.
-Snímač je pripevnený k stroju na rovnom povrchu s obojstrannou kobercovou páskou.
+Snímač je pripevnený k stroju na rovnom povrchu obojstrannou kobercovou páskou.
 
@@
 
-Väčšina zámen pri odhaľovaní porúch spraví model pri poruche vonkajšieho krúžku ložiska vonkajšej rasy, ktorá sa označuje za poruchu klietky ložiska, nerovnováhu hriadeľa a menej často za nesúosovosť.
-Nevyváženosť hriadeľa zabezpečuje v laboratóriu simuláciu porúch ložísk, čiže tam nastáva prirodzene k veľkej zámene typov porúch.
+Väčšinu zámen pri odhaľovaní porúch spraví model pri poruche vonkajšieho krúžku ložiska, ktorú označuje za poruchu klietky ložiska alebo nerovnováhu hriadeľa a menej často za nesúosovosť.
+Nevyváženosť hriadeľa zabezpečuje v laboratóriu simuláciu porúch ložísk, čiže tam nastáva prirodzene k značnej zámene týchto porúch.
 
 Zvyšujúci sa počet susedov použitých na klasifikáciu s k-NN ukazuje podstatné zníženie presnosti na testovacích dátach.
-Najvýraznejší pokles o približne 10\% nastáva na po deväť susedov.
+Najvýraznejší pokles o približne 10\% nastáva po deväť susedov.
 Atribúty vytvorené z trojosového vektora dosahujú lepšiu presnosť ako tie výhradne z osi pohybu pre rovnakú zdrojovú doménu a ložisko.
 Model pre vnútorné ložisko A je presnejší ako vonkajšie ložisko B.
-Sada TD je lepšia v identifikácii porúch ako sada FD pre ekvivalentnú hodnotu k.
+Sada TD je lepšia v identifikácií porúch ako sada FD pre ekvivalentnú hodnotu k.
 Dátová sada s anotáciami pre poruchy vysokej závažnosti má prudšie zníženie presnosti pre rovnaký počet susedov.
@@
 
-Základné množiny atribútov dosahujú lepšiu presnosť ako ich podmnožiny, keď počet prvkov je najviac tri a súčasne počet susedov je päť alebo menej.
-Počet prvkov má priamy úmerný vplyv na presnosť optimálneho modelu. Presun z dvoch na tri atribúty má väčšiu váhu ako povolenie štvrtého atribútu.
+Ak je počet atribútov je najviac tri a súčasne počet susedov je päť alebo menej, základné množiny atribútov dosahujú lepšiu presnosť ako ich podmnožiny.
+Počet prediktorov má priamy úmerný vplyv na presnosť optimálneho modelu. Presun z dvoch na tri atribúty má väčšiu váhu ako pridanie štvrtého prediktora.
 
-Prediktory vybrané pomocou stratégií výberu sú porovnané s presnosťou klasifikácie kombinácie skupín atribútov rovnakej veľkosti a s presnosťou ich zdrojovej nadmnožiny.
+Prediktory vybrané pomocou výberových metód sú porovnané s presnosťou klasifikácie kombinácií skupín atribútov rovnakej veľkosti a s presnosťou ich zdrojovej nadmnožiny.
 Na získanie konzistentnej presnosti je potrebné kombinovať hodnotenia z niekoľkých metrík výberu atribútov.
@@
 Metrika vzájomnej informácie dosahuje lepšiu strednú presnosť (80,87\%) a percentil v distribúcii presností (91,81\%).
-Nasledovaná je súčinom poradí s presnosťou 79,82\% a percentilom 88,97\% Súčin poradí je najlepšou metódou v 43,52\% scenárov, kde je považovaný za najlepšiu stratégiu.
-Vzájomné informácie je na druhom mieste s 40,28\% prípadov.
-Stredná presnosť vo prípadoch, kde je zvolená metóda výberu najlepšia je tiež lepšia pre súčin poradí s 92,38\% v porovnaní s 91,79\% pri vzájomnej informácii.
-Výber atribútov zvyčajne vyberá premenné tak, aby sa ich presnosť objavila v hornom kvartile distribúcie.
+Nasledovaná je súčinom poradí s presnosťou 79,82\% a percentilom 88,97\% Súčin poradí je považovaný za najlepšiu stratégiu v 43,52\% prípadov.
+Vzájomná informácia je na druhom mieste s 40,28\% prípadov.
+Stredná presnosť vo sitáciach, kde je zvolená metóda výberu najlepšia, je tiež lepšia pre súčin poradí s 92,38\% v porovnaní s 91,79\% pri vzájomnej informácii.
+Výber atribútov zvyčajne vyberá premenné tak, že ich presnosť objaví v hornom kvartile distribúcie.
 
@@
 Metriky online vzdelávania sa vyhodnocujú progresívnym vyhodnotením na nevyváženom súbore údajov.
-Presnosti klasifikácie medzi postupným a dávkovým učením sa porovnáva na finálnej presnosti online modelu.
+Presnosti klasifikácie medzi postupným a dávkovým učením sú porovnané na finálnej presnosti online modelu.
 
@@
 Najvyššie presnosti po postupnom zhliadnutí vzoriek v najdlhších posuvných oknách s dĺžkou 100 pozorovaní sú znížené v porovnaní s dávkovým modelom o 9,76\% (TD), 10,54\% (FD), 14,73\% (TD, závažnosť) a 11,38\% (FD, závažnosť).
-Ponechanie 10\% anotácii ich rovnomerným vynechávaním a trénovanie modelu s oknom 10 vzoriek zníži maximálnu presnosť modelu s tromi prediktormi v časovej doméne o 9,9\% na 66,78\% a o 14,93\%  na 67,00\% vo frekvenčnej doméne.
+Ponechanie 10\% anotácií ich rovnomerným vynechávaním a trénovanie modelu s oknom 10 vzoriek zníži maximálnu presnosť modelu s tromi prediktormi v časovej doméne o 9,9\% na 66,78\% a o 14,93\% na 67,00\% vo frekvenčnej doméne.
 
 \section{Rozbor dátovej sady z priemyslu}
-Správanie sa rôznych strojov je porovnaná vo frekvenčnej doméne a cez časovo-frekvenčné spektrogramy.
-Aktuálny stav čerpadiel nameraný vlastným data loggerom je obohatený o záznamy so senzora vibrácii od výrobcu.
+Správanie sa rôznych strojov je porovnané vo frekvenčnej doméne a cez časovo-frekvenčné spektrogramy.
+Aktuálny stav čerpadiel nameraný vlastným data loggerom je obohatený o záznamy zo senzora vibrácií od výrobcu.
 Potenciálne poruchy sú diagnostikované podľa postupu od doménových expertov.
@@
 Motor M2 na pozícii dva má zvýšené amplitúdy nad 4 kHz v porovnaní s motorom M1.
-Čerpadlá majú členitejší obsah frekvenčného signálu ako motory, pravdepodobne v dôsledku toku vody.
+Čerpadlá majú bohatší frekvenčný signál ako motory, pravdepodobne v dôsledku toku vody.
 Vonkajšie ložisko čerpadla (4) vykazuje nižšiu amplitúdu vibrácií nad 1,5 kHz ako vnútorné ložisko (3).
@@
 Vo frekvenciách sú viditeľné harmonické frekvencie rýchlosti rotácie frekvencie BPFO pri každom stroji a BPFI pre M2-2.
-Dá sa predpokladať, že práve tieto frekvencie budú v budúcnosti dôvodom poškodenia strojov.
+Dá sa predpokladať, že práve tieto frekvencie budú v budúcnosti dôvodom poškodenia týchto strojov.
 
@@
 Počas viac ako piatich rokov prevádzky čerpadla sa nevyskytol ani jeden prípad poruchy ložiska v dôsledku ich dlhej životnosti a každoročnej profylaktickej údržby.
-To podčiarkuje náročnosť záznau poruchových stavov v priemyselnom prostredí.
+To podčiarkuje náročnosť záznamu poruchových stavov v priemyselnom prostredí.
 
 \section{Záver}
-V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre riešenie monitorovania prevádzkového stavu a odhaľovanie porúch z vibračných signálov.
-Extrahované premenné pochádzajú hlavne z popisných štatistík, z článkov o spracovaní zvukových signálov, mechanických vlastností ložísk a technických noriem vibrodiagnostiky.
+V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre monitorovanie prevádzkového stavu rotačných strojov a odhaľovanie porúch z vibračných signálov.
+Extrahované premenné pochádzajú hlavne z popisných štatistík, z odborných článkov o spracovaní zvukových signálov, mechanických vlastností ložísk a technických noriem vibrodiagnostiky.
 
@@
 Metódy výberu prvkov vo väčšine prípadov sú schopné vybrať skupinu s presnosťou nad horným kvartilom rozdelenia presnosti z každej kombinácie atribútov rovnakej mohutnosti.
-Súčin poradí troch metód na výber atribútov je najlepší v 44\% experimentálnych prípadov nasledovaný metrikou vzájomnej informácie.
-Súčin poradí tiež dosiahol percentil 97,50\% v rozdelení presnosti na trojprvkových množinách prediktorov.
+Súčin poradí troch metód na výber atribútov je najlepší v 44\% experimentálnych prípadov, nasledovaný metrikou vzájomnej informácie.
+Súčin poradí dosiahol percentil 97,50\% v štatistickom rozdelení presnosti na trojprvkových množinách prediktorov.
 
-Algoritmus inkrementálneho učenia k-NN na nevyváženej množine údajov trojíc atribútov dosahuje presnosť prinajlepšom 77\% so anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou 100 pozorovaní.
+Algoritmus inkrementálneho učenia k-NN na nevyváženej množine údajov trojíc atribútov dosahuje presnosť prinajlepšom 77\% so anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou sto pozorovaní.
 Presnosť 67\% dosahuje online k-NN model, keď len 10\% pozorovaní zostane označených.
@@
 
-Analýza zhromaždených dátových súborov potvrdila stacionárnosť spektra signálu pri konštantnej záťaži a dĺžku päť-sekundových časových radov ako vyhovujúce pre extrakciu znakov.
+Analýza zhromaždených dátových súborov potvrdila stacionárnosť spektra signálu pri konštantnej záťaži a dĺžku päť-sekundových časových radov ako vyhovujúcu pre extrakciu atribútov.
 Potvrdila sa tiež náročnosť získavania pozorovaní porúch častí stroja bez zámerného poškodenia ložísk a vychýlenia hriadeľa.
@@
 Ďalej je možné použitie rôznych počiatočných základných sád atribútov.
-Súborové metódy inšpirované volebnými systémami možno využiť pri úlohe výberu prvkov.
-Data loger môže byť skombinovaný s modelom klasifikátora a mechanizmom na anotáciu pozorovania buď automaticky v závislosti od celkovej úrovne vibrácií, alebo manuálne počas údržby alebo po neočakávanej poruche.
+Súborové metódy inšpirované volebnými systémami je možné využiť pri úlohe výberu prediktorov.
+Data logger môže byť skombinovaný s modelom klasifikátora a mechanizmom na anotáciu pozorovania buď automaticky v závislosti od celkovej úrovne vibrácií, alebo manuálne počas údržby alebo po neočakávanej poruche.
 \clearpage

### 2024-05-14 thesis/chapters/appendix/A-technical-documentation.tex
Move Resume to main thesis

--- 2024-05-13 thesis/chapters/appendix/B-technical-documentation.tex
@@
 \pagenumbering{arabic}
-\renewcommand*{\thepage}{B-\arabic{page}}
+\renewcommand*{\thepage}{A-\arabic{page}}
 The documentation contains a description of Jupyter Notebooks, Python package \verb|vibrodiagnostics| with utility functions for machine learning, and data logger firmware.

### 2024-05-14 thesis/chapters/appendix/E-digital-medium.tex
Move Resume to main thesis

@@
 \setcounter{figure}{0}
-\chapter{Contents of the digital medium}
+\chapter{Digital medium}
 \pagenumbering{arabic}
 \renewcommand*{\thepage}{E-\arabic{page}}
-\par Evidenčné číslo práce v informačnom systéme: \RegNo
-\par Obsah digitálnej časti práce (archív ZIP):
-\par Názov odovzdaného archívu:
+\par Registration number of thesis in AIS: \RegNo
+\par Contents of the digital medium:
+\par Name of submitted archive directory: DP\_MiroslavHajek.zip
+\par Digital medium has more than 1 GiB and is available to the thesis supervisor.
+\par The MaFaulDa dataset is publicly available at: \url{https://www02.smt.ufrj.br/~offshore/mfs/database/mafaulda/full.zip}
+
+\begin{itemize}[noitemsep]
+\item[\textbf{>}] \textbf{datasets} - raw vibration data from machinery, and reports that took long to calculate.
+	\begin{itemize}[noitemsep]
+	\item[\textbf{>}] \textbf{FluidPump.zip} - custom recorded dataset of vibrations from air compressors and water pumps
+	\item[\textbf{>}] \emph{MAFAULDA.zip} - placeholder where the downloaded MaFaulDa dataset should be placed
+	\item[\textbf{>}] \textbf{best-subset} - the subset of features chosen to three-member subsets most frequently
+	\item[\textbf{>}] \textbf{features} - features extracted from datasets in multiple domains
+	\item[\textbf{>}] \textbf{ksb-cloud} - data exported from KSB cloud monitoring of vibration rms velocity and frequency waveform for chosen dates.
+	\item[\textbf{>}] \textbf{misc-fluid-pump} - other non-standard measurements from pumps such as during speed up, slow down, or noise.
+	\item[\textbf{>}] \textbf{knn-accuracy-distribution} - 
+	\item[\textbf{>}] \textbf{knn-incremental-accuracy} - The incremental k-NN model accuracy after each sample for various lengths of tumbling window and gaps between labels 
+	\item[\textbf{>}] \textbf{standing-fan} - audio for an estimate of fan rotational speed and measurements done in firmware verification on the back, side, and front of the fan.
+	\end{itemize}
+\item[\textbf{>}] \textbf{docs} - the documentation generated from source code comments  using automated tool
+	\begin{itemize}[noitemsep]
+	\item[\textbf{>}] \textbf{html-notebooks} - export of Jupyter notebooks for all basic configurations in HTML format
+	\item[\textbf{>}] \textbf{doxygen} - documentation of \emph{firmware} 
+	\item[\textbf{>}] \textbf{sphinx} - documentation of \emph{vibrodiagnostics} package
+	\end{itemize}
+\item[\textbf{>}] \textbf{firmware} - source code in \emph{main} directory for accelerometer data logger firmware written in C language with ESP-IDF SDK.
+The script \emph{bin2tsv.py} converts files saved to SD card in binary format to a tsv file.
+\item[\textbf{>}] \textbf{notebooks} - Jupyter notebooks for data exploration, data analysis, and machine learning on provided datasets
+\item[\textbf{>}] \textbf{vibrodiagnostics} - Python package of commonly used function in Jupyter notebooks for data processing
+\end{itemize}

### 2024-05-14 thesis/chapters/preliminaries/annotation.tex
Move Resume to main thesis

@@
 Trend indicators are derived from vibration signals to form summarizing numerical attributes.
-The similarity of features to a dependent variable describing fault types is assessed by supervised feature selection metrics individually and in the ensemble.
-The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve the data rates of the monitoring solution.
-The incremental learning models are compared to their batch counterparts when truthful labels are delayed or missing.
+The similarity of features to a dependent variable that describes fault types is assessed by supervised feature selection metrics individually and in the ensemble.
+The accuracy of fault classification using the k-nearest neighbour algorithm is evaluated on the best feature subsets.
+The goal is to conserve the data rates of the monitoring solution.
+The incremental learning models are compared to their batch counterparts when true labels are delayed or missing.
 An extendible software toolkit of vibrodiagnostics is implemented as a Python package.
 
-Classification metrics are evaluated in scenarios of the MaFaulDa dataset, and lossy compression ratios are expressed.
+Classification metrics are evaluated on the MaFaulDa dataset, and lossy compression ratios are expressed.
 Our accelerometer data logger collects a novel dataset of machinery behavior for compressors and pumps in the industrial environment.
-The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but its cause, too.
+The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.
 \emptypage
@@
 
-Z vibračných signálov sú odvodené trendové indikátory a tak vytvárajú sumarizujúce číselné atribúty.
+Z vibračných signálov sú odvodené trendové indikátory, ktoré tvoria sumarizujúce číselné atribúty.
 Podobnosť atribútov so závislou premennou popisujúcou typy porúch sa posudzuje individuálne a súborovými metrikami výberu atribútov v učení s učiteľom.
-Presnosť detekcie porúch algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
+Presnosť klasifikácie porúch algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
 Tým sa znížia požiadavky na objem prenosu dát v monitorovacom riešení.
@@
 
-Metriky kladifikácie sú vyhodnotené v scenároch na dátovej sade MaFaulDa a tiež sú vyjdrené stratové kompresné pomery Náš záznamník údajov akcelerometra zhromažďuje nový súbor údajov o správaní sa strojov pre kompresory a čerpadlá v priemyselnom prostredí.
-Prínos tejto práce spočíva v identifikácii možnosti použitia iba pár veličín na opis nielen prítomnosti poruchy, ale aj jej príčiny.
+Metriky klasifikácie sú vyhodnotené v scenároch na dátovej sade MaFaulDa a tiež sú vyjadrené stratové kompresné pomery.
+Náš záznamník údajov z akcelerometra nazhromaždil novú dátovú sadu kompresorov a čerpadiel v priemyselnom prostredí.
+Prínos tejto práce spočíva v overení možnosti použitia iba pár veličín na opis nielen prítomnosti poruchy, ale aj jej príčiny.
 \emptypage

### 2024-05-16 thesis/chapters/03-design.tex
Final

@@
 However, the realization of the steps must be decomposed closer to suit the dataset structure, desired processing goals, and investigated parameters.
-The entire design of the data flow is in Figure~\ref{fig:design:ml-pipeline}.
+The design of the data flow is in Figure~\ref{fig:design:ml-pipeline}.
 
@@
 The hierarchically topmost folder describes the simulated defect.
-There is directory for \emph{normal}, \emph{imbalance}, \emph{horizontal-misalignment}, \emph{vertical-misalignment}, \emph{overhang} (outer bearing), \emph{underhang} (inner bearing).
+There are directories for \emph{normal}, \emph{imbalance}, \emph{horizontal-misalignment}, \emph{vertical-misalignment}, \emph{overhang} (outer bearing), \emph{underhang} (inner bearing).
 Each bearing has an additional folder layer for dividing up bearing faults: \emph{ball\_fault}, \emph{cage\_fault}, \emph{outer\_race}.
-Fault categories, except the normal class, contain various fault severities marked with units of grams or millimeters.
-Severities, in turn, consist of individual files with different rpm speeds.
+Fault categories, except the normal class, contain various fault severities marked with in grams or millimeters.
+Fault severities, in turn, consist of individual files with different rpm speeds.
 
-The labels for shaft misalignment in vertical and horizontal directions are merged into the same group because we neglect the \textbf{acceleration sensor orientation}.
-In the end, that leaves \textbf{six types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
+The labels for shaft misalignment in vertical and horizontal directions are merged into the same group because we neglect the \textbf{accelerometer spatial orientation}.
+This merging leaves \textbf{six types of labels}: baseline, two shaft faults are imbalance and misalignment, and three bearing faults are cage fault, ball fault, and outer race fault.
 
-Depending on the \textbf{chosen bearing position}, only time series associated with that bearing are retained because the standards demand each bearing be assessed separately.
-Fault classification concerns with bearing in direct contact and shaft mechanically passing through it.
+Depending on the \textbf{chosen bearing position}, only time series associated with that bearing are retained because the standards demand that bearings are assessed separately.
+Fault classification is concerned with bearing in direct contact and the shaft mechanically passing through it.
 
-The strength of the recorded response to the underlying defect is dependent on the shaft \textbf{rotational speed}.
+The strength of the vibrations in response to the defect is dependent on the shaft's \textbf{rotational speed}.
 Speed in units of rpm is calculated from pulsed speedometer output.
-It is the average distance between two successive rising edges:
+It is an average distance between two successive rising edges:
 \begin{ceqn}\begin{align}
@@
 \textbf{File description} is the triplet of \textbf{fault}, \textbf{severity}, and \textbf{rpm}.
-After labeling, we insert a step to split the time series into parts when the duration is long enough to introduce more observations artificially.
+After labeling, we insert a step to split the time series into parts when the duration is long enough to introduce more rows artificially.
 This assumption for splitting is not met for MaFaulDa because, for the desired frequency resolution for features of close to 1~Hz, we need a window size of 32768 samples.
@@
 The \textbf{DC component} in the three-dimensional vibration signal is removed by subtracting the global mean.
-Immediately follows a digital IIR Butterworth low pass filter of \nth{5} order with cutoff frequency 10 kHz at -3 dB.
-Before the usage of a low pass filter, the peak at 20 kHz with a sideband was present as an unwanted artifact.
+Digital IIR Butterworth low pass filter of \nth{5} order immediately follows with cutoff frequency 10 kHz at -3 dB.
+Before its use, the peak appeared at 20 kHz with a sideband as an unwanted artifact.
 It could not have been reliably recorded due to the linear frequency response of the sensor up to 10 kHz.
@@
 
-\textbf{Initial labels can be exchanged} for a label of fault-free state when the severity is low.
-The count of severity levels is not identical in every group.
-The numerical amounts for each level are sorted in ascending order within each fault and then these levels are normalized using a min-max scaler.
+\textbf{Initial labels can be exchanged} for a label of fault-free condition when the defect severity is low.
+The severity levels are not identical in every group.
+The numerical amounts for each level are sorted in ascending order within each fault group, and then these levels are normalized using a min-max scaler.
 
@@
 The feature extraction formulas are identical with formulas presented in the section \ref{section:feature-extraction} of analysis chapter.
-The frequency transform is Welch's method averaging of FFT vectors from 32768 samples after Hann windowing and 50\% overlap.
+The frequency transform is Welch's method on FFT vectors from 32768 samples after Hann windowing and 50\% overlap.
 The feature sets are:
@@
 \item \textbf{Feature domain} - the set of extracted features as an input to downstream models is changed either to TD or FD set,
-\item \textbf{Accelerometer axis} - Either one principal direction of motion or all three dimensions are aggregated under same feature name (1 or 3),
-\item \textbf{High severity faults} - to more precisely simulate fault frequencies found in real environment the low severity defects can be considered as normal operation (Yes or No).
+\item \textbf{Accelerometer axis} - either one principal direction of motion or all three dimensions are aggregated under the same feature name (1 or 3),
+\item \textbf{High severity faults} - to more precisely simulate fault frequencies found in the real environment, the low severity defects can be considered as normal machine operation (Yes or No).
 \end{itemize}
 
-The \textbf{fault classification} performance metrics are evaluated after balancing classes feature normalization, and 5-fold cross-validation validation on the k-nearest neighbor classifier with Euclidean distance metric.
-The population of classes is evened out with random oversampling using a strategy to resample all but the majority class.
-In the multi-class classification, the micro-averaged performance metrics of accuracy, precision, and recall result in the same number.
+The \textbf{fault classification} performance metrics are evaluated after balancing classes, feature normalization, and 5-fold cross-validation in the k-nearest neighbour classifier with Euclidean distance metric.
+The population of classes is evened out with random oversampling of all but the majority class.
+In the multi-class classification, the micro-averaged performance metrics of accuracy, precision, and recall give the same number.
 Therefore, accuracy is only one on the output.
 
-The hyperparameter of k-neighbours and a feature subset size are tweaked, and results are compared under different preprocessing conditions and in multiple experiments:
+The hyperparameter of k-neighbours and a feature subset size are tweaked. The results are compared under different preprocessing conditions and in multiple experiments:
 
@@
 \itemsep0pt
-\item \textbf{Complete feature sets}: compare the accuracy of the k-NN model in relation to the k-value as an odd number in the range from 1 to 37 on the dataset under different conditions.
+\item \textbf{Complete feature sets}: compare an accuracy of the k-NN model with k-value as an odd number in the range from 1 to 37 on the dataset under different conditions.
 The TD and FD sets are treated separately.
 
-\item \textbf{Feature combinations} - every combination of feature subsets with 2, 3, and 4 members are evaluated to obtain the statistical distribution of all possible k-NN models.
-The k-value is sequentially increased from options 3, 5, and 11 neighbours.
-The single k-value generates $\sum_{j=2}^{4}{\binom{n}{j}}$ where $n$ is number of members in complete feature set.
+\item \textbf{Feature combinations} - every combination of feature subsets is evaluated with 2, 3, and 4 members to obtain the statistical distribution of all possible k-NN models.
+The most informative attributes for defect identification are found by brute force in the distribution.
+The k-value is chosen from options of 3, 5, and 11 neighbours sequentially.
+The single k-value generates $\sum_{j=2}^{4}{\binom{n}{j}}$ combinations where $n$ is cardinality of complete feature set.
 In total 375 models for TD and 550 models for FD are tested under identical conditions.
-
-The observed effect is a rate of decrease in accuracy while shrinking the number of features to the bare minimum.
-The side product is finding the global optimum by brute force of the most informative attributes in predicting the defect.
+The observed effect is a decrease in accuracy while shrinking the number of features to the bare minimum.
 
 \item \textbf{Feature selection methods} - the choice of feature subset is performed in linear time complexity as opposed to exponential in combinatorial case.
-The dimensionality reduction using \textbf{principal components analysis} (PCA) does further extraction and retains only the components that best explain the variance.
+The dimensionality reduction with \textbf{principal components analysis} (PCA) does further extraction and retains only the components that the best explain the variance.
 The disadvantage is that the resulting linear combination cannot be interpreted easily.
@@
 The best feature subset from complete sets is picked after ranking the features according to their importance.
-The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (F statistic), and \textbf{Mutual information}.
-The correlation among features can reduce model's prediction power.
+The bivariate scores for ranking are the mean of point biserial \textbf{correlation} to every class label as a dichotomous variable, \textbf{Fisher score} (ANOVA F statistic), and \textbf{Mutual information}.
 The rank product combines the three latter scores into the ensemble.
-The comparison for the accuracy of the feature selection strategy is made in relation to the entire model accuracy distribution.
+The accuracy comparison of the feature selection strategies is made in relation to the entire model accuracy distribution.
 
-\item \textbf{Incremental learning} - the order of samples tries to simulate the gradually worsening state of the machine and delayed annotation of defects.
+\item \textbf{Incremental learning} - the order of samples simulates the gradually worsening state of the machine and the delayed annotation of defects.
 Observations are sorted based on increasing relative severity.
-The faults within levels are shuffled randomly.
+The faults within severity levels are shuffled randomly.
 
@@
 Labels for the whole previous window are supplied at once.
-
 Another common problem with online learning is \textbf{missing annotations} due to the size of the dataset.
@@
 
-The experimental design involves the filter conditions that create 24 forms of the original MaFaulDa.
+The experimental design involves the filtering conditions that create 24 forms of the original MaFaulDa.
 The four main experiments test hyperparameters on each dataset variation.
@@
 \section{Exploratory data analysis of MaFaulDa}
-A better explanation for model behavior is arranged by examining the number of observations per fault category, spatial separability of the distinguished groups, and scales of the attributes and their interdependencies.
+A better rationale for future models behaviour is given by examining the number of observations per fault category, spatial separability of the categories, scales of the attributes and their interdependencies.
 
@@
 The baseline class is the least populous at 3.4\% for the inner bearing.
-After relacing low severity faults with the normal status it became the largest with 51.32\%.
+After relacing low severity faults, the normal status became the largest group with 51.32\%.
 The imbalance ratio as a proportion of the largest to the smallest classes is 10.16 for original labels and 8.58 after relabeling.
 
-Exemplary waveforms from each fault class illustrate their
-superficial differences in oscillatory behavior. The files with the highest severity levels and around an average rotational speed of 2500 rpm (42 Hz) are displayed to discern patterns.
+Exemplary waveforms from each fault class illustrate their superficial differences in oscillatory behavior.
+The files with the highest severity levels and around rotational speed of 2500 rpm (42 Hz) are displayed to discern patterns.
 \begin{figure}[h]
@@
 Subplots for radial, tangential, and axial directions are in columns from left to right.
-Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ in baseline and misalignment time series up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
+Amplitudes vary with limits from $\pm 3\; \mathrm{m/s}^2$ for normal condition and misalignment, up to $\pm 11\;\mathrm{m/s}^2$ in case of severe bearing faults.
 
@@
 The signal chunk represents an uncertainty box with a duration of approximately 328 ms and a spectral resolution of little over 3 Hz.
-The graph has been cropped in variables to make the most important peaks visible.
+The graph is cropped to make the most important peaks visible.
 
-The numeric scale of distinct attributes calculated out of signals for bearing A widely differs ~(Fig.~\ref{fig:design:feature-range}).
+The numeric scales of distinct attributes calculated from inner bearing signals differ widely (Fig.~\ref{fig:design:feature-range}).
 The magnitude of three spatial dimensions stretches the scale towards larger values or introduces more outliers.
-Many of the indicators used for fault detection are dimensionless numbers but for others, the information about units of measurement is still attainable.
+Many of the indicators used for fault detection are dimensionless numbers, but for others, the information about units of measurement is still attainable.
 
@@
 
-Inside the interquartile range of three axis features the peak-to-peak is between 4.89 - 11.39 $\mathrm{m/s}^2$, root-mean-square is 0.56 - 1.31 $\mathrm{m/s}^2$, average amplitude change represents 0.08 - 0.23 $\mathrm{m/s}^2$ of amplitude change in 20 $\mu\mathrm{s}$.
-In the frequency domain, the spectral centroid is in range of 1575 - 4175 Hz, roll-off frequencies arise above 246 and below 4476 Hz, roll-on frequencies are from 50 to 207 Hz, and entropy occurs from 7.57 to 10.94 nats.
+Inside the interquartile range of three axis features, the peak-to-peak is between 4.89 - 11.39 $\mathrm{m/s}^2$, root-mean-square is 0.56 - 1.31 $\mathrm{m/s}^2$, average amplitude change represents 0.08 - 0.23 $\mathrm{m/s}^2$ of level jump in 20 $\mu\mathrm{s}$.
+In the frequency domain, the spectral centroid is in the range of 1575 - 4175 Hz, roll-off frequencies arise above 246 and below 4476 Hz, roll-on frequencies are from 50 to 207 Hz, and entropy occurs from 7.57 to 10.94 nats.
 
-Despite the differences in ranges in some instances by several orders of magnitude, there are still dependencies among variables in the complete feature sets.
+Despite the differences in scales, in some instances by several orders of magnitude, there are still dependencies among variables in the complete feature sets.
 The TD set~(Fig.~\ref{fig:design:corr-td}) appears to have less strongly correlated pairs than the FD set~(Fig.~\ref{fig:design:corr-fd}) in terms of Pearson correlation coefficient.
@@
 
-Crest, impulse, and clearance in TD have correlations of 100\%.
+Crest, impulse, and clearance have correlations of 100\% in TD.
 Other very strongly positively correlated variables are peak-to-peak to root-mean-square at 95\% and average amplitude change at 83\%.
@@
 Shape and zero-crossing rate are also correlated at 72\%.
-In the FD set the roll-on frequency, energy, and standard deviation are the most uncorrelated to all other variables.
-However, the energy and std are highly correlated to each other.
+In the FD set, the roll-on frequency, energy, and standard deviation are the most uncorrelated to all other variables.
+However, the energy and standard deviation are highly correlated to each other.
 Skewness and kurtosis of the frequency spectrum have a strong association of 99\%.
@@
 
-The faults in the MaFaulDa were measured at several rotational speeds.
+The faults in the MaFaulDa are observed at several rotational speeds.
 This increases the robustness of the machine-learning model.
 In practice, if the model is trained only at one speed and then the speed alters, the features tied to rpm could inhibit the prediction accuracy.
-The distribution of correlations of each predictor to rpm under all experimental conditions is shown in Figure~\ref{fig:design:rpm-corr}.
+The statistical distribution for correlations between predictors and rpm under all experimental conditions is in Figure~\ref{fig:design:rpm-corr}.
 
-The overwhelming majority of predictors are weakly correlated to rotational speed.
-The moderate correlation appears for average amplitude change with the median of 54\% and peak-to-peak with median of 31\%.
-These two features are less suited for idenfifying fault types in variable speed situations.
+An overwhelming majority of predictors are weakly correlated to rotational speed.
+The moderate correlation appears for average amplitude change with a median of 54\% and peak-to-peak with a median of 31\%.
+These two features are less suited for identifying fault types in variable speed situations.
 
@@
     \end{subfigure} 
-    \caption{PCA of complete feature set into two principal components (bearing A and 3 axis}
+    \caption{PCA of complete feature set into two principal components (bearing A and three axes}
     \label{fig:design:pca-complete-sets}
@@
 
-The separability of fault groups into clusters is qualitatively analyzed by projecting normalized complete feature sets onto the plain utilizing two principal components.
-The transformed TD and FD sets are shown in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned ``normal'' class.
-The decision boundaries that color the feature space around the data points are determined in 0.02x0.02 square areas by k-NN with five neighbours.
+Fault group separability into clusters is qualitatively analyzed by projecting normalized complete feature sets onto the plain utilizing two principal components.
+The transformed TD and FD sets are in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned the normal class.
+The decision boundaries that color the feature space around the data points are determined in 0.02 $times$0.02 square areas by k-NN with five neighbours.
 We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
 
-Shaft misalignment and bearing ball fault look quite lumped together, whereas imbalance is mixed with cage fault.
-The silhouette score quantifies the amount of cluster overlap which indicates a very weak clustering score with values around 0.08.
-The explained variance with two components is 84.7\% for TD and 86.5\% using original labels.
+Shaft misalignment and ball bearing fault look lumped together, whereas imbalance is interweaved with cage fault.
+The silhouette score quantifies the cluster overlap by a weak score of around 0.08.
+The explained variance with two principal components is 84.7\% for TD and 86.5\% with original labels.
 
@@
 
-Loading plots of PCA (Fig.~\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
+The PCA loading plots (Fig.~\ref{fig:design:pca-loading-plot}) illustrate correlations of features to two principal components.
 The first PC in the time domain mainly describes the impulsiveness of the waveform: \emph{shape, impulse, crest, clearance, zero-crossing rate}.
@@
 However, the groups are not as clear-cut for frequency-domain features.
-Overall chaos in frequency spectra can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off}.
+Overall chaos in the frequency spectrum can be attributed to PC1: \emph{flux, entropy, negentropy, noisiness}, and the shape of frequency distribution to PC2: \emph{roll-on, roll-off}.
 PCA efficiently expresses attributes in less dimensional space, but the resulting linear combination is hard to comprehend for explaining decisions.
@@
 Data acquisition of vibrations from industrial machinery necessitates the assembly of the standalone data logger.
-The required hardware modules of the device include a sensor as a triaxial MEMS accelerometer, a fast persistent memory unit, and a microcontroller to control communication with both peripherals.
-The recording starts with a button press, and the indicator LED provides feedback about the operation in progress.
+The required hardware modules of the device include a triaxial MEMS accelerometer as a sensor, a fast persistent memory unit, and a microcontroller to control communication with both peripherals.
+The recording starts after a button press, and the indicator LED provides feedback that the device is recording.
 
-More detailed specification according to standards creates demands especially on the accelerometer, in terms of bandwidth for linear response to at least 1 kHz, ideally more.
-The sampling rate should be greater than 2 kHz for each of the three axes (6 kSps).
-Out of the options available on the market, we opted for the accelerometers with digital communication bus with more than 12-bit sample resolution, high sensitivity, and low noise density.
+Detailed specification according to standards makes demands especially on the accelerometer, in terms of bandwidth for linear response to at least 1 kHz, ideally more.
+The sampling rate should be greater than 2 kHz for each of the three directions (6 kSps).
+Out of the options available on the market, we opted for the accelerometers with digital communication bus, more than 12-bit sample resolution, high sensitivity, and low noise density.
 
@@
 
-The hardware configuration we arrived at for the data logger powered with a power bank via USB connector is in Table~\ref{tab:design:hw-sensors}.
+The hardware configuration we arrived at for the data logger is in Table~\ref{tab:design:hw-sensors}.
+The power bank powers the device via a MicroUSB connector.
 The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring.
-The evaluation board for the accelerometer STEVAL-MKI208V1K is connected via a ribbon cable that enables proper attachment to designated places.
+The evaluation board STEVAL-MKI208V1K with the SMD accelerometer is connected via a ribbon cable to the microcontroller.
+This enables proper attachment of the sensor to designated places.
 
@@
 ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via an SD/MMC bus.
-It enables us to store all samples from FIFO.
 The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin.
@@
 
-The firmware's role lies in coordinating hardware adapters and straightforward vibration acquisition for later analysis.
-The provided functionality is hence minimalistic.
+The firmware acts as a coordinator of hardware adapters and aids in straightforward vibration acquisition for later analysis.
+The provided functionality is consequently minimalistic.
 Two user-driven actions, one periodic event, and one timer-generated event satisfy these basic requirements.
-Activity diagrams outline the steps of the firmware actions~(Fig.~\ref{fig:design:firmware-activity}).
+Activity diagrams outline the functionality of the firmware actions~(Fig.~\ref{fig:design:firmware-activity}).
 
 \section{Industrial equipment}
-Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
+Three kinds of rotating machines are at our disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.
 
@@
 It serves as a test bed during the data logger development.
-The sensor is placed on the plastic casing at the back of the drive motor.
-The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
-It has a switch for 3 rotational speeds, which are approximately 19~Hz, 21~Hz, and 22.7~Hz ($\Delta f$ = 0.18 Hz).
-Speed estimation was done by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.
+The accelerometer is glued to the plastic casing at the back of the drive motor.
+The fan blades have a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}).
+It has a switch for three rotational speeds of approximately 19~Hz, 21~Hz, and 22.7~Hz ($\Delta f$ = 0.18 Hz).
+Speed was estimated by spectral analysis of audio (Fig.~\ref{fig:design:fan-speed}) in \emph{Spectroid} app and confirmed by 240 fps high-speed camera.
 
 \textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}).
-Altogether, two units are available in two independent air conditioning units for the data center.
+In the data center,  two units are part of independent air conditioning units.
 The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz).
-Possible measurement locations are located on the sides of the compressor atop the bearings, just above the base and below the scroll.
-Steel casing is not in direct contact with the bearing which causes significant alteration to the signal.
+Possible measurement placements are located on the sides of the compressor atop the bearings, just above the base and below the scroll.
+Steel casing is not in direct contact with the bearing, which causes significant alteration to the signal.
 
@@
 The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor.
-The newer primary pumps with bundled wireless cloud monitoring are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
-The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz).
+The pump and motor have each two bearings, hence there are four measurement positions.
+
+The newer primary pumps, commissioned in 2018, with bundled wireless cloud monitoring are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}).
+The pumps and motors rotate at 1493 rpm (24.9 Hz).
 The motor \emph{WEG W50} provides 400~kW of power (class~\rom{3}).
-The bearing designations at numbered places for defect frequency  calculations are 6319-C3 (1), 6324-C3 (2), and 6317-2Z (3 \& 4)
-
+The bearing designations at numbered places for bearing defect frequency calculations are 6319-C3 (1), 6324-C3 (2), and 6317-2Z (3 \& 4).
 The secondary pump is one unit named \emph{Sigma~300-OVD-600} (Fig.~\ref{fig:machine:pump-sigma}) installed in 1986.
-It rotates at 1485 rpm (24.75 Hz), and its electric motor has a power of 450~kW (class~\rom{3}).
-Each pump and motor have two bearings, hence there are four measurement positions.
+The Sigma pump rotates at 1485 rpm (24.75 Hz), and its electric motor has a power of 450~kW (class~\rom{3}).
 
@@
 
-Placements are numbered for simplicity (Fig.~\ref{fig:design:machines}) but the precise description follows the notation of MIMOSA convention from ISO~13373-1.
-The sensor is mounted on compressor's placem: \emph{SFTA001AT000TN} (1), \emph{SFTA002AT000TN} (2), on WEG motor's positions: \emph{MTRA001AT000TN} (1), \emph{MTRA002AT045TN} (2), and on KSB pump positions: \emph{PMPA003AT000TN} (3), \emph{PMPA004AT000TN} (4).
+Sensor placements are marked by single digit numbers for simplicity (Fig.~\ref{fig:design:machines}) but the precise description follows the notation of MIMOSA convention from ISO~13373-1.
+The accelerometer is mounted on compressor's positions: \emph{SFTA001AT000TN} (1), \emph{SFTA002AT000TN} (2), on WEG motor's positions: \emph{MTRA001AT000TN} (1), \emph{MTRA002AT045TN} (2), and on KSB pump positions: \emph{PMPA003AT000TN} (3), \emph{PMPA004AT000TN} (4).
 
@@
 Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).
-We were able to export the historical log of vibration velocity for last year at hourly intervals and sample frequency spectra.
+We were able to export the historical measurements of vibration velocity for last year at hourly intervals and sample frequency spectra.
 The sensor unit (Fig.~\ref{fig:design:ksb-device}) is permanently attached to KSB pumps on bearing in position no.
@@
 \textbf{Compression ratio} for MaFaulDa dataset compared to all 21 extracted features in 3 dimensions is 2381:1.
-If 6 features are kept, the compression is 25000:1, which is a saving of the original data by 99.996\%.
+With just six features, the compression is 25000:1, which is a saving of the original data by 99.996\%.
 
@@
 Each position has a sensor mounted in three directions that makes a total of \emph{36 source channels}.
-The sampling frequency at each position is set to \emph{20 kHz}.
-The recordings have \emph{duration of five seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
+The sampling frequency at each position is \emph{20 kHz}.
+The recordings have \emph{five seconds} and are triggered regularly every 1 hour (\emph{8760 times per year}).
 
-In a year, the system gathers 31.54 Gs (gigasamples) which is 58.74 GiB with a 16-bit ADC resolution.
+In a year, the system gathers 31.54 Gs (gigasamples), which is 58.74 GiB with a 16-bit ADC resolution.
 Reasonably precise spectral estimation with 10 thousand bins needs 3.15 Gs per year.
-On the other hand, 6 features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
+On the other hand, six features out of each channel keep only 1.89 Ms per year for a lossy compression ratio of 16667:1.
 Low data volumes potentially enable feature selection and models to be offloaded directly to edge devices.
-The entire history of the machine's health could be stored in a small flash memory module.
+The entire history of machines' health can be saved into a small flash memory module.

### 2024-05-16 thesis/chapters/05-evaluation.tex
Final

@@
 \section{Fault classifiction in MaFaulDa}
-The four outlined experiments on MaFaulDa involve testing sets of features with very few members to see the effects in predictions when reducing the information content about machine status to the minimum.
-First, the attributes are left in the complete count after extraction.
+The four outlined experiments on MaFaulDa involve testing sets of features with very few members.
+The effect in predictions is observed when reducing the information content about machine's status to the minimum.
+First, the attributes are left in full after extraction.
 Then, all of their combinations are enumerated, and the resulting accuracy distribution is matched against accuracy after feature selection with similarity metrics.
@@
 The label ``normal'' is not falsely attributed to other classes in either feature set, but other classes can get assigned to be ``normal''.
-Most mistakes happen while predicting outer race fault, which is confused with cage fault, imbalance, and less often with misalignment.
-The shaft imbalance is used for simulating bearing faults, which is a natural reason for this high error rate.
+Most mistakes happen while predicting outer race fault, which gets confused with cage fault, imbalance, and less often with misalignment.
+The shaft imbalance is applied to simulate bearing faults, which is a natural reason for this high error rate.
 
@@
 
-The increasing number of neighbours used for classification in 5-fold cross-validated k-NN shows a substantial decrease in accuracy on validation sets (Fig.~\ref{fig:evaluation:complete-set-k-value}).
-The most prominent drop in performance of around 10\% occurs at the beginning until the k-value of nine, and then the accuracy curves slowly plateau.
+An increase in the number of neighbours used for classification in five-fold cross-validated k-NN shows a substantial decrease in accuracy on validation sets (Fig.~\ref{fig:evaluation:complete-set-k-value}).
+The most prominent drop in performance of around 10\% occurs at the beginning until the k-value of nine, and then the accuracy curve slowly plateaus.
 
@@
 The TD set is generally better in predictions than the FD set for the equivalent k-value.
-The relabeled dataset for high severity has a steeper decrease in accuracy for the same number of neighbours.
+The dataset relabeled for high severity has a steeper decrease in accuracy for the same number of neighbours.
 
@@
 These trend variables could be used in distinguishing faults the same way as rms amplitude indicates their presence.
-Each possible combinations of pairs, triplets, and quadruplets constructs a separate k-NN model on which prediction accuracy is evaluated.
+Each possible combinations of pairs, triplets, and quadruplets construct a separate k-NN model on which prediction accuracy is evaluated.
 
@@
 The distribution of model accuracies is documented on features in both domains coined from three dimensions on bearing A with original and high-severity defect labels.
-The boxplots display the relation of the k-value to accuracy when three features are chosen, and the relation of a number of features to accuracy with five neighbours(Fig.~\ref{fig:evaluation:model-accuracy-severity} and \ref{fig:evaluation:model-accuracy-severity}).
+The boxplots display the relation of the k-value to accuracy with three features, and the relation of number of features to accuracy with five neighbours (Fig.~\ref{fig:evaluation:model-accuracy-severity} and \ref{fig:evaluation:model-accuracy-severity}).
 
@@
 We are interested in comparing maximum accuracies of the accuracy distribution because the optimal feature selection method tries to approach them.
-The reduction in maximal accuracy is more noticeable between three and five features 3 - 5\%, and almost the same amount between five and eleven neighbours.
+The reduction in maximal accuracy is more noticeable between three and five features of 3\% to 5\%, and almost the same amount between five and eleven neighbours.
 
@@
 
-The spread in model accuracies in the interquartile range is from 5 to 10 \%, and measured between whiskers is at a maximum of 25\%.
+The spread in model accuracies in the interquartile range is from 5 to 10\%, and measured between whiskers is 25\% at a maximum.
 The standard deviation is about 7\%.
@@
 The contributions of adding features are around 6\% and 3\%, and the relabeled dataset has an increase of 3\% and 2\%.
-The absolute accuracies are consecutively for 2, 3, and 4 features when k is equal to 5: 78.31\%, 85.67\%, and 89.55\% for the time domain and 81.52\%, 87.52\%, 90.26\% in the frequency domain.
+The absolute accuracies are consecutively for 2, 3, and 4 features when k is equal to 5: 78.31\%, 85.67\%, and 89.55\% for the time domain and 81.52\%, 87.52\%, 90.26\% for the frequency domain.
 
 \subsection{Feature selection techniques}
-The predictors chosen with supervised selection strategies are compared in accuracy and location within the accuracy distribution of exhaustive combinations of same-sized sets and the performance of its source superset.
+The predictors chosen with supervised selection strategies are compared to the accuracy distribution of  enumerated combinations of same-sized attribute sets and the performance of its source superset.
 The metrics for bivariate feature selection are correlation, F statistic, mutual information, and their ensemble by the rank product.
-The PCA of the complete feature set that retains the same number of features and selection methods serves as a benchmark to tell whether the linear combination or subset gets better performance on the MaFaulDa.
+The PCA of the complete feature set that retains the same number of features as a selection method is a benchmark to tell whether the linear combination or meaningful attributes get better performance on the MaFaulDa.
 
@@
 The percentile within the distribution is measured to its respective data, the train or validation set.
-However, the percentile of best features in the test data is calculated against train distribution.
+However, the percentile of best features in the test data is calculated against distribution of the training data.
 
 Combining the rankings from several metrics is necessary to get consistent results.
-This is evidenced by the variability of the success of selected feature sets in final prediction performance under multiple conditions.
-The PCA with 3 components transformed from the complete feature sets is comparable in accuracy to selection methods with original attributes.
+This is evidenced by the variability in the success of selected feature sets in final prediction performance under multiple conditions.
+The PCA with three components for the complete feature sets is comparable in accuracy to selection methods with original attributes.
 
-The triplet of variables with the best results is from TD set: zero-crossing rate, peak-to-peak, skewness, and from FD set: centroid, roll-off, and entropy.
+The triplet of variables with the best results is in TD set: zero-crossing rate, peak-to-peak, skewness, and in FD set: centroid, roll-off, and entropy.
 With high severity labels, the best attributes for FD stay the same, but average amplitude change and shape factor are preferred along the zero-crossing rate.
@@
 
-The entire accuracy distribution for the training and testing set for original labels is drawn in the form of the histogram (Fig.~\ref{fig:evaluation:fsel-model-distr}).
+The entire accuracy distribution for the training and testing set with original labels is drawn as a histogram (Fig.~\ref{fig:evaluation:fsel-model-distr}).
 The results of the chosen predictors are mapped out onto the distribution as vertical lines that stack up near the maximum for the time domain or disperse slightly above the median for the frequency domain.
 The accuracy of all features is unreachable for three feature subsets.
-Another noticeable difference between distributions is their shift down and greater spread in testing compared to training sets.
+Another noticeable difference between distributions is their shift down and greater spread in testing sets compared to training sets.
 
@@
 
-Kernel density estimate plot (Fig.~\ref{fig:evaluation:kde-fsel-perecentile}) shows the distribution of accuracies for the selection methods and percentiles for predictor subsets they chose.
+Kernel density estimate plot (Fig.~\ref{fig:evaluation:kde-fsel-perecentile}) shows the distribution of accuracies for the selection methods and percentiles for predictor subsets they choose.
 The feature selection usually picks variables so that they stay in the upper quartile of the distribution above the 75\% percentile.
-The median accuracy of all methods is around the vicinity of 80\%.
+The median accuracy of all methods is the vicinity of 80\%.
 
@@
 
-The k-NN models in incremental learning experiments learn on the same base training dataset as in batch learning for bearing A.
-Online learning metrics are evaluated by progressive valuation on a dataset that is left unbalanced.
-In this manner, we can compare the training accuracies in the last sample of online models to their batch counterparts.
+The k-NN models in incremental learning experiments train on the same base training dataset as those in batch learning for bearing A.
+Online learning metrics are evaluated by progressive valuation on a still unbalanced dataset.
+In this manner, we can compare the training accuracies for the last sample of online models to their batch counterparts.
 
@@
 Counters of other faults show that predictions are skewed towards more represented classes of imbalance and misalignment.
-The uneven evolution of categories in a stream impacts the development of accuracy in the remaining experiments.
-The test accuracies of comparable batch models from the three best features are 85.47\% (TD), 87.52\% (FD), 91.71\% (TD severity), and 91.94\% (FD severity).
+The uneven evolution of categories in a stream impacts the evolution of accuracy in the remaining experiments.
+The test accuracies of comparable batch models for three best features are 85.47\% (TD), 87.52\% (FD), 91.71\% (TD severity), and 91.94\% (FD severity).
 
@@
     \end{subfigure} 
-    \caption{Tumbling window during incremental learning of lengths 1, 10, 100}
+    \caption{Tumbling window of lengths 1, 10, 100 during incremental learning}
     \label{fig:evaluation:tumbling-window-online}
@@
 Labeling every \nth{10} sample (10\% of the dataset) with a tumbling window of 10 samples reduces maximum accuracy for the three-predictor model compared to data points without gaps in labels.
-Time-domain features it is decreased by 9.9\% to 66.78\%, and by 14.93\% for frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}).
+In time-domain features, it is decreased by 9.9\% to 66.78\%, and by 14.93\% in frequency-domain features to 67.00\% (Fig.~\ref{fig:evaluation:label-skips-online}).
 More annotations can be scrapped in the case of a relabeled dataset where keeping just 0.02\% of the class labels produces a decrease by 13.7\% to 68.79\% for time domain attributes, and by 16.59\% to 66.25\% for frequency domain attributes.
@@
 The latter part of the solution evaluation focuses on signal properties of vibrations from air compressors, water pumps, and electric induction motors.
-At first, the accelerometer data logger functionality is tested, and its precision is checked up in the known situations.
-Our custom dataset is compiled from collected measurements during regular operations of machines.
+Our custom dataset is compiled from measurements collected during regular operation of machines.
 The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram.
 The domain expert methodology is carried out to diagnose the current status of water pumps.
-The presence of fault is confronted with sensor logs from the pump vendor.
+The presence of fault is confronted with sensor logs from the pump's vendor.
 
@@
 Data logger capabilities were verified by capturing vibrations on the back of the plastic casing for the electric motor of the standing fan.
-The recording is able to run continuously for more than one minute without dropping any samples.
+The recorder is able to run continuously for more than one minute without dropping any samples.
 The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}).
@@
 It can be assumed that those frequencies will be the reason for damage in the future.
-The absolute acceleration is minuscule in current frequency bands and year-long sensor log of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).
+The absolute acceleration is minuscule in current frequency bands and year-long sensor logs of rms velocity (Fig~\ref{fig:evaluation:ksb-guard-rms-vibartions}).
 
@@
 Therefore, the current results suggest that the bearings are in flawless condition.
-During the over five years the pump has been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance.
+During the over five years the pumps have been in service, there is not one instance of bearing fault due to rated lifespan and yearly prophylactic maintenance.
 This underscores the scarcity of recording faulty states in industrial environments.
-The monitoring is better suited for situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.
+The monitoring is better suited in situations without preventive maintenance or with smaller machinery like the plunger pump BC~21/20S we considered during air conditioning inspections.
 
@@
 Spectrograms point out that under constant machine load, the significant frequencies stay more or less unchanged over time (Fig~\ref{fig:evaluation:spectrograms}).
-The resolution of the chart unit area is 306.95 ms and 3.26 Hz.
+The resolution of the uncertainty box is 306.95 ms and 3.26 Hz.
 Its magnitude is colored for decibel value.
@@
 
-The water pump switch on and off creates a fast change in shaft speed, which cannot be analyzed for resonance bands with enough time resolution by an automatic system at a chosen sampling rate.
-Due to inertia, slowing down takes about 10 seconds, whereas the speed up is half a second (Fig.~\ref{fig:evaluation:pump-switch-over}.
+The water pump switch on and off creates a fast change in shaft speed.
+Resonance bands cannot be separated with enough time resolution by an automatic system at a chosen sampling rate.
+Due to inertia, slowing down takes about 10 seconds, whereas the speed up takes just half a second (Fig.~\ref{fig:evaluation:pump-switch-over}.
 The interference from excessive vibrations of the adjacent Sigma pump is picked up by the accelerometer on the KSB pump just before their switchover occurs (Fig~\ref{fig:evaluation-sigma-pump-interference}).
@@
 The range of feature values for compressors and pumps are higher than in MaFaulDa despite most of them describing baseline status (Fig~\ref{fig:evaluation-sigma-pump-interference}).
-The increases can be seen for example on the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).
+The increase can be seen for example in the interquartile range of rms (7.33 - 14.62 $\mathrm{m/s}^2$), centroid (3806 - 6003 Hz) or entropy (9.40 - 13.22 nats).

### 2024-05-16 thesis/chapters/06-conclusion.tex
Final

--- 2024-05-07 thesis/chapters/06-conclusion.tex
@@
 \chapter{Conclusion} \label{section:conclusion}
-In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals.
+The focus of this master's thesis is on the optimal choice of trend indicators from vibration signals in an inexpensive industrial condition monitoring solution.
 The goal is to enable timely fault detection of machinery parts with as little input data as possible.
-For that purpose, we answer four research questions.
+We answer \textbf{five research questions} for those purposes.
 
-Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343).
-These formulas compute ten features summarizing the waveform in the temporal domain and eleven features characterizing spectral density estimation in axis of motion or all three spatial directions \textbf{(RQ1)}.
+\textbf{The first question} is about finding numerical features that can represent machinery behaviour for accurate diagnosis.
+The technical standards in vibrodiagnostics and the descriptive statistics for time-varying phenomena are valuable in that regard.
+Vibrations have to be recorded at a high sampling rate.
+The researched formulas narrow down this massive data stream to groups of a few features.
+We define ten features that summarize the waveform in the time domain (\emph{TD}) and eleven features that describe its spectral density estimation (\emph{FD}).
+The features are either just taken from the axis of the jitter, or aggregated from all three spatial directions.
 
-In order to achieve more pronounced data savings, we choose the subset of 3 features in each domain by keeping the ones with the most similarity to the target variable.
-Feature selection metrics of the correlation coefficient, F statistic, mutual information, and their rank product are applicable in supervised learning.
-The features are squished from multiple dimensions using the Euclidian norm.
-Lossy compression ratios attained are 2381:1 for all features and 25000:1 for 6 features in the MaFaulDa dataset.
-We managed to discard more than 99.995\% of irrelevant data \textbf{(RQ2)}.
+\textbf{The second question} answers the effort to achieve even more pronounced savings in transmission goodput.
+Groups of three predictors are chosen from each base feature set that together have the most similarity to the target variable.
+Feature selection scores of the correlation coefficient, F statistic, mutual information, and their rank product are computed in supervised learning scenarios.
+Lossy compression ratios attained are 2381:1 for all features and 25000:1 for six features from the MaFaulDa dataset.
+We managed to discard more than 99.995\% of the irrelevant data.
 
-Feature subsets are subjected after normalization to a k-nearest neighbor classifier that ascertains their relative fault detection power.
-Because of model overtraining with small k, the feature triplets equal or slightly outperformed the whole set of features on the validation set with accuracy up to 10\%.
-The time-domain set of features reach higher accuracies than frequency-domain set because of their smaller interdependency \textbf{(RQ3)}.
+\textbf{The third question} asks about the accuracy of the machine learning model for machinery fault diagnostics.
+The major constraint put on the model is to provide inference from reduced sets of predictors.
+The k-nearest neighbours classifier is utilized because it works on a simple to-explain assumption that proximate data points mean the same type of fault.
+Additionally, the k-NN retains individual historical observations and can be applied in an incremental learning approach.
 
-The ensemble of feature selection with rank product produces the best model performance out of three combined in the majority of situations.
-No approach could find a triplet of predictors with an accuracy close to optimal one discovered exhaustively.
-%TODO wtf
-Training on three principal components produced better accuracy than filtering feature selection, but PC mapping onto original trend indicators is unclear even in loading plots \textbf{(RQ3)}.
+We implement the \textbf{data processing pipeline} that transforms the MaFaulDa dataset for multiclass classification with the k-NN algorithm and a tiny number of features.
+The fault labels with severity are composed of the file's path from the dataset structure.
+The features are extracted from vibration time series after digital filtering.
+Then, the features are arranged into multiple configurations: complete feature sets, enumerated feature subset combinations, and feature subsets chosen by filtering feature selection methods.
+The accuracy results are validated by five-fold cross-validation.
 
-The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables.
-Annotations can be assigned belatedly or even never.
-Incremental learning k-NN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label.
-The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.
+We found that for this particular dataset, the chosen time-domain features have reached higher accuracies than the chosen frequency-domain set because of fewer intercorrelations.
+An increase in k-neighbours lessens the model accuracy because class boundaries overlap and are relatively noisy.
+Predictors aggregated from tri-axis recording performed better in classification than those from just one axis.
 
-The vibration signals will be gathered on compressors in air conditioning units and water pumps in municipal pumping stations.
-We will develop firmware for sensor units capable of sampling accelerometers and saving measurements onto SD cards.
-The challenge awaits us in labeling samples themselves as it requires substantial expert knowledge.
+The feature selection methods can pick a group of predictors with accuracy above the upper quartile of the statistical distribution of accuracy values for the same-sized sets.
+The rank product method found the best-performing attributes in the majority of 44\% of scenarios, closely followed by mutual information.
+The rank product for the predictor's triplets reaches the 97.50\% percentile from the accuracy distribution.
 
-%TODO
-% Future work
-% - long term dataset from machinery until failure or propose way for factories to artifically train model for new machinery - make the system machine and placement independent
-% - more diffenent feature set from one recoding - in windows
-% - combine feature selection with incremntal learining
-% - Different election methods and metrics
-% - Find other ML model also suitable HoeffdingTreeClassifier - losing original data for labeling - mechnaism of transforming samples to model represntatin
-% - Monitor more machines and combine their result with federated learning
-% - Monitor faults of different equipment - moving wheels of the train or train tracks
+The number of features has a direct proportionality effect on accuracy.
+The absolute best predictor triplets for MaFaulDa are in TD (accuracy of 85.47\%): zero-crossing rate, peak-to-peak, skewness, and in FD (accuracy of 87.52\%): spectral centroid, roll-off frequency, and entropy.
 
-% Main points of the thesis assigments namely effectivness representation of machinery faults in succint fashion and performance in machine learining diagnostics models has been compared extensively.
+\textbf{The fourth question} investigates machinery behavior in an industrial environment using signal processing techniques.
+The vibrations were collected a month apart by an accelerometer data logger according to the specification.
+The designated machines were air conditioning compressors and water pumps with motors in municipal pumping station.
+We implemented a data logger's firmware that reads samples after a button press from the accelerometer at 26.8 kHz and stores them onto a memory card.
+
+Analysis of the collected dataset confirms the stationarity of the signal spectrum under constant load and assures that five-second bursts are indeed satisfactory for feature extraction.
+The dataset provides a practical exercise in labeling potential future faults from bearing defect frequency amplitudes.
+It also demonstrates the immense difficulty of obtaining observations of faulty machinery in the field without purposefully damaging it.
+
+\textbf{The fifth question} is concerned with incremental machine learning because the considerable obstacle in the deployment of an autonomous fault detection system is the availability of annotations that can be assigned belatedly or even never.
+Incremental k-NN algorithm on an unbalanced dataset for three predictors achieves at best 77\% accuracy with labels in tumbling windows of hundred samples.
+The accuracy of 67\% is reached for the online model when just 10\% of observations stay associated with the label.
+The comparable model trained in batch reaches an accuracy of 88\%.
+
+\textbf{We conclude} that an inexpensive industrial condition monitoring solution with low data rates is indeed possible.
+It uses the available accelerometer sensors and feature discovery techniques.
+According to the analysis, the system could diagnose the machine's health with high accuracy in a local model on the edge device.
+
+\section{Future work}
+Future work would focus on the deployment of our machine learning model on a large scale to sensor units and setting up the necessary infrastructure.
+The components for such an endeavour are described in the analysis for incremental learning.
+The way to annotate observations could be introduced, either automatically depending on the overall vibration level or manually during maintenance or after an unexpected failure.
+
+The natural research extension of the thesis is to confirm that the results hold in other publicly available datasets of machinery faults, e.g.
+in CWRU.
+The other alteration is to use more and different starting base feature sets.
+Harmonic frequencies or wavelet coefficients can generate predictors that could be reduced further to the smallest possible subsets.
+
+Ensemble strategies inspired by classical election systems may be utilized in the task of feature selection.
+Different types of classifiers for online learning could be compared to k-nearest neighbours, e.g.
+Hoeffding tree.
+A combination of local models from multiple sensors is desirable, e.g.
+in a federative learning approach.

### 2024-05-16 thesis/chapters/07-resume.tex
Final

@@
 Modely k-NN v experimentoch s postupným učením sa učia na rovnakom základnom súbore trénovacích údajov ako pri dávkovom učení pre ložisko A.
-Metriky online vzdelávania sa vyhodnocujú progresívnym vyhodnotením na nevyváženom súbore údajov.
+Metriky postupného učenia sa vyhodnocujú progresívnym vyhodnotením na nevyváženom súbore údajov.
 Presnosti klasifikácie medzi postupným a dávkovým učením sú porovnané na finálnej presnosti online modelu.
@@
 V diplomovej práci sme sa zamerali na výber trendových ukazovateľov pre monitorovanie prevádzkového stavu rotačných strojov a odhaľovanie porúch z vibračných signálov.  
-Extrahované premenné pochádzajú hlavne z popisných štatistík, z odborných článkov o spracovaní zvukových signálov, mechanických vlastností ložísk a technických noriem vibrodiagnostiky.
+Cieľom je umožniť včasnú detekciu porúch strojných častí s čo najmenším množstvom vstupných údajov, pričom odpovedáme na päť výskumných otázok.
 
+Prvá otázka sa týka hľadania numerických atribútov, ktoré môžu reprezentovať správanie strojov pre ich presnú diagnostiku.
+V tomto ohľade sú dôležitým zdrojom technické normy v oblasti vibrodiagnostiky a popisné štatistiky.
+Definujeme desať atribútov v časovej doméne a jedenásť vo frekvenčnej oblasti.
+
+Druhá otázka odpovedá na snahu dosiahnuť ešte výraznejšie zníženie nárokov na objem prensených dát.
+Výber najdôležitejších atribútov sa hodnotí cez korelačný koeficient, F štatistiku, vzájomnú informáciu a súčin poradí jednotlivých metód.
 Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov.
 Podarilo sa nám dosiahnuť úsporu dát o viac ako 99,995\%.
-Zistili sme, že nami použitá základaná sada atribútov z časovej domény dosahuje vyššiu presnosť ako sada frekvenčnej domény kvôli menším vzájomným koreláciám.
+
+Tretia otázka sa pýta na presnosť modelu strojového učenia na diagnostiku porúch stroja.
+Implementujeme postup spracovania údajov z dátovej sady MaFaulDa, ktorá umožní klasifikáciu algoritmom k-najbližších susedov pri malom počte atribútov.
+Zistili sme, že pre nami použitá dátová sada dosiahla pre zvolené atribúty časovej domény vyššiu presnosť ako zvolená množina z frekvenčnej domény.
 Zvýšenie počtu susedov pre k-NN vedie k menšej presnosti modelu.
-Prediktory agregované z trojosového záznamu dosiahli lepšie výsledky v klasifikácii ako prediktory z jednej osi.
+Prediktory agregované z trojosového záznamu dosiahli lepšie výsledky v klasifikácii ako prediktory len z jednej osi.
+Metódy výberu atribútov dokážu vybrať skupinu prediktorov s presnosťou nad horným kvartilom štatistického rozdelenia hodnôt presnosti.
+Metóda súčinu poradí našla najlepšie výkonné atribúty vo väčšine scenárov a pre trojicu prediktorov dosahuje percentil 97.5\% z rozdelenia presnosti.
 
-Metódy výberu prvkov vo väčšine prípadov sú schopné vybrať skupinu s presnosťou nad horným kvartilom rozdelenia presnosti z každej kombinácie atribútov rovnakej mohutnosti.
-Súčin poradí troch metód na výber atribútov je najlepší v 44\% experimentálnych prípadov, nasledovaný metrikou vzájomnej informácie.
-Súčin poradí dosiahol percentil 97,50\% v štatistickom rozdelení presnosti na trojprvkových množinách prediktorov.
+Štvrtá otázka skúma správanie strojov v priemyselnom prostredí pomocou techník spracovania signálov.
+Vibrácie boli zbierané s odstupom jedného mesiaca pomocou vlastného data loggera.
+Ich analýza potvrdzuje stacionárnosť spektra signálu pri konštantnej záťaži a overuje, že päťsekundové zhluky sú skutočne uspokojivé na extrakciu atribútov.
 
-Algoritmus inkrementálneho učenia k-NN na nevyváženej množine údajov trojíc atribútov dosahuje presnosť prinajlepšom 77\% so anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou sto pozorovaní.
+\textbf{Piata otázka} sa týka postupného učenia, kde k-NN dosahuje presnosť prinajlepšom 77\% s anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou sto pozorovaní.
 Presnosť 67\% dosahuje online k-NN model, keď len 10\% pozorovaní zostane označených.
@@
 
-Analýza zhromaždených dátových súborov potvrdila stacionárnosť spektra signálu pri konštantnej záťaži a dĺžku päť-sekundových časových radov ako vyhovujúcu pre extrakciu atribútov.
-Potvrdila sa tiež náročnosť získavania pozorovaní porúch častí stroja bez zámerného poškodenia ložísk a vychýlenia hriadeľa.
-
-Ďalším rozšírením diplomovej práce je potvrdenie platnosti výsledkov aj v iných verejne dostupných dátových sadách porúch strojov, napr.
-v CWRU.
-Ďalej je možné použitie rôznych počiatočných základných sád atribútov.
-Súborové metódy inšpirované volebnými systémami je možné využiť pri úlohe výberu prediktorov.
-Data logger môže byť skombinovaný s modelom klasifikátora a mechanizmom na anotáciu pozorovania buď automaticky v závislosti od celkovej úrovne vibrácií, alebo manuálne počas údržby alebo po neočakávanej poruche.
+Výber malého počtu trendových ukazovateľov sa ukázal ako dostatočne spoľahlivý na určovanie porúch rotačných strojov.
+Natrénovaný model umožňuje nasadenie na senzorovú jednotku IoT zaradenia pri výraznej úspore posielaných dát.
 \clearpage

### 2024-05-16 thesis/chapters/preliminaries/annotation.tex
Final

@@
 Trend indicators are derived from vibration signals to form summarizing numerical attributes.
-The similarity of features to a dependent variable that describes fault types is assessed by supervised feature selection metrics individually and in the ensemble.
+The similarity of features to a dependent variable that describes fault type is assessed by supervised feature selection metrics individually and in the ensemble.
 The accuracy of fault classification using the k-nearest neighbour algorithm is evaluated on the best feature subsets.
@@
 Z vibračných signálov sú odvodené trendové indikátory, ktoré tvoria sumarizujúce číselné atribúty.
-Podobnosť atribútov so závislou premennou popisujúcou typy porúch sa posudzuje individuálne a súborovými metrikami výberu atribútov v učení s učiteľom.
-Presnosť klasifikácie porúch algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
-Tým sa znížia požiadavky na objem prenosu dát v monitorovacom riešení.
-Modely prírastkového učenia sú porované s učením v dávkach, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
+Podobnosť atribútov so cieľovou premennou popisujúcou typ poruchy sa posudzuje individuálne a súborovo metrikami výberu atribútov v učení s učiteľom.
+Presnosť klasifikácie porúch strojov algoritmom k-najbližších susedov sa vyhodnocuje na podmnožinách najlepších atribútov.
+Tým sa znižujú požiadavky na objem prenosu dát v monitorovacom riešení.
+Modely postupného učenia sú porovnané s učením v dávkach, v situáciach kedy je expertné označenie prevádzkového stavu oneskorené alebo chýbajúce.
 Rozšíriteľná sada funkcií pre vibrodiagnostiku je implementovaná ako balík v jazyku Python.
@@
 Metriky klasifikácie sú vyhodnotené v scenároch na dátovej sade MaFaulDa a tiež sú vyjadrené stratové kompresné pomery.
-Náš záznamník údajov z akcelerometra nazhromaždil novú dátovú sadu kompresorov a čerpadiel v priemyselnom prostredí.
+Nami vytvorený data logger nazhromaždil novú dátovú sadu z kompresorov a čerpadiel v priemyselnom prostredí.
 Prínos tejto práce spočíva v overení možnosti použitia iba pár veličín na opis nielen prítomnosti poruchy, ale aj jej príčiny.

### 2024-05-16 thesis/extract.sh

@@ -1,4 +1,4 @@
 #!/usr/bin/env bash
-pdftk thesis.pdf cat 3-85 output BP_MiroslavHajek.pdf  
-pdftk thesis.pdf cat 86-127 output BP_prilohy_MiroslavHajek.pdf
+pdftk build/thesis.pdf cat 1-126 output DP_MiroslavHajek.pdf
+pdftk build/thesis.pdf cat 127-180 output DP_prilohy_MiroslavHajek.pdf
  

### 2024-05-16 thesis/chapters/05-evaluation.tex
Final fix

@@
 Our custom dataset is compiled from measurements collected during regular operation of machines.
-The behaviour of different machines is compared using static frequency estimation and a time-frequency spectrogram.
+The behaviour of different machines is compared using static frequency estimations and time-frequency spectrograms.
 The domain expert methodology is carried out to diagnose the current status of water pumps.
@@
 The amplitude range after conversion is constrained in the expected range (Fig.~\ref{fig:evaluation:logger-waveform}).
-The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on Beaglebone Black, albeit with lower sensitivity.
+The same amplitudes were obtained previously on a proof-of-concept device using analog accelerometer ADXL335 on BeagleBone Black, albeit with lower sensitivity.
 

### 2024-05-16 thesis/chapters/07-resume.tex
Fix bold

@@
 
-\textbf{Piata otázka} sa týka postupného učenia, kde k-NN dosahuje presnosť prinajlepšom 77\% s anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou sto pozorovaní.
+Piata otázka sa týka postupného učenia, kde k-NN dosahuje presnosť prinajlepšom 77\% s anotáciami, ktoré prichádzajú v posuvných oknách s dĺžkou sto pozorovaní.
 Presnosť 67\% dosahuje online k-NN model, keď len 10\% pozorovaní zostane označených.

### 2024-05-16 thesis/chapters/03-design.tex
Submit

@@
 The transformed TD and FD sets are in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned the normal class.
-The decision boundaries that color the feature space around the data points are determined in 0.02 $times$0.02 square areas by k-NN with five neighbours.
+The decision boundaries that color the feature space around the data points are determined in 0.02$\times$0.02 square areas by k-NN with five neighbours.
 We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
